\begin{document}

\section{Lawntoklian to English dictionary}

lúlōpèmàle̋lȕl am pā poje̋jàpī ē inggless à pèmó ra̋la̋m alúl ó ā lúlōpèmàajőm pe ōpèmēre̋m al inggless al ūl lúl am poje̋jàpī ē űm óroōpèmóēújȍ al latium ō ma̋lrȕ mó ȅ ōpèmēpāra̋m pèmē őmrȅ jèl pèmē jèm pèmó poje̋jàpī ē mȁm mum ó ē

This complete Musical-Djastiz-to-English dictionary gives the part of speech and English meaning of each Musical Djastiz word in latin alphabetical order. A crucial reference for anyone living in this post-Djastiz society.

\subsection{i}
\begin{itemize}

	\item \textbf{ian} \textit{post.} (Swa. \langle njia \rangle [ˈᶮɟia]) by; as; via; \textit{denotes method or manner}

	\item \textbf{im} \textit{post.} (Ara. \langle ??? \rangle [im]) of; -`s; \textit{denotes modifier or associate}

\end{itemize}

\subsection{l}
\begin{itemize}

	\item \textbf{l} \textit{prn.} which; that; \textit{relative}
	\begin{itemize}
		\item \textbf{lian} \textit{prn.} (``l'' + ``ian'') method; way; path; manner; by which
		\item \textbf{lianim} \textit{n.} (``lian'' + ``im'') methodical; formal; instructive
		\item \textbf{lim} \textit{prn.} (``l'' + ``im'') kind; relation; specifier
		\item \textbf{limim} \textit{n.} (``lim'' + ``im'') genitive
	\end{itemize}

\end{itemize}

\subsection{m}
\begin{itemize}
	\item \textbf{men} \textit{prn.} (Pan. \lang ??? \rang [mɛ̃]) I; me; \textit{first person}
	\begin{itemize}
		\item \textbf{menim} \textit{prn.} (``men'' + ``im'') my; mine
	\end{itemize}

	\item \textbf{mef} \textit{num.} (Yor. \lang mefa \rang [mefa]) 6; six
	\begin{itemize}
		\item \textbf{mefim} \textit{n.} (``mef'' + ``im'') sixth; senary
	\end{itemize}

	\item \textbf{mjawf} \textit{n.} (Ono. [mjaw]) feline; cat; lion; tiger
	\begin{itemize}
		\item \textbf{mjawfim} \textit{n.} (``mjawf'' + ``im'') feline
	\end{itemize}

\end{itemize}

\subsection{t}
\begin{itemize}

	\item \textbf{tok} \textit{v. dt.} (Eng. \lang talk \rang [tʰɑlk]) say; convey; \sc{lun} says \sc{lon} to \sc{lam}
	\begin{itemize}
		\item \textbf{toklian} \textit{n.} (``tok'' + ``lian'') language
		\item \textbf{tolklianim} \textit{n.} (``toklian'' + ``im'') linguistic
	\end{itemize}

\end{itemize}

\subsection{p}
\begin{itemize}

	\item \textbf{pon} \textit{prn.} (- ``men"") you; \textit{second person}
	\begin{itemize}
		\item \textbf{ponim} \textit{prn.} (``pon'' + ``im'') your; yours
	\end{itemize}

\end{itemize}

\end{document}