\section{Є}

\textbf{\hypertarget{'e}{'e}} \textit{n.} (ono. [e])
e; /e/; mid front unrounded vowel

\textbf{\hypertarget{'e}{'e}} \textit{n.} (Lat. ⟨e⟩ [eː])
e; Euler’s number; 2.718…

\textbf{\hypertarget{ealwik}{ealwik}} \textit{n.} (Fil. ⟨earwig⟩ [eaɾwiɡ])
earwig; Dermaptera

\textbf{\hypertarget{elehe}{elehe}} \textit{v.} (Spa. ⟨elige⟩ [eˈlixe])
choose; decide; \hyperlink{eleheles}{ʟєꜱ} chooses \hyperlink{elehelon}{ʟᴏᴧ}

\textbf{\hypertarget{eleheestaki}{eleheestaki}} \textit{v.} (\hyperlink{elehe}{elehe}+\allowbreak \hyperlink{estaki}{estaki})
design; \hyperlink{eleheestakiles}{ʟєꜱ} designs \hyperlink{eleheestakilon}{ʟᴏᴧ}

\textbf{\hypertarget{eleheestakiles}{eleheestakiles}} \textit{n.} (\hyperlink{eleheestaki}{eleheestaki}+\allowbreak \hyperlink{les}{les})
designer

\textbf{\hypertarget{eleheestakilon}{eleheestakilon}} \textit{n.} (\hyperlink{eleheestaki}{eleheestaki}+\allowbreak \hyperlink{lon}{lon})
design

\textbf{\hypertarget{eleheles}{eleheles}} \textit{n.} (\hyperlink{elehe}{elehe}+\allowbreak \hyperlink{les}{les})
arbitrator

\textbf{\hypertarget{elehelon}{elehelon}} \textit{n.} (\hyperlink{elehe}{elehe}+\allowbreak \hyperlink{lon}{lon})
choice; decision

\textbf{\hypertarget{elehehau}{elehehau}} \textit{v.} (\hyperlink{elehe}{elehe}+\allowbreak \hyperlink{hau}{hau})
be apprehensive; hesitate; \hyperlink{elehehaulon}{ʟᴏᴧ} is apprehensive to do ʟᴜᴍ

\textbf{\hypertarget{elehehaulon}{elehehaulon}} \textit{n.} (\hyperlink{elehehau}{elehehau}+\allowbreak \hyperlink{lon}{lon})
apprehensive

\textbf{\hypertarget{elehetunciki}{elehetunciki}} \textit{v.} (\hyperlink{elehe}{elehe}+\allowbreak \hyperlink{tunciki}{tunciki})
elect; ʟєꜱ elects ʟᴜᴍ to office over ʟᴏᴧ

\textbf{\hypertarget{elec}{elec}} \textit{n.} (Spa. ⟨helecho⟩ [eˈlet͡ʃo])
fern; Polypodiopsida

\textbf{\hypertarget{'elefen}{'elefen}} \textit{n.} (Lfn. ⟨Elefen⟩ [elefen])
Lingua Franca Nova; LFN; Elefen

\textbf{\hypertarget{'elefenak}{'elefenak}} \textit{n.} (\hyperlink{'elefen}{'elefen}+\allowbreak \hyperlink{ak}{ak})
Lingua Franca Nova; in Lingua Franca Nova

\textbf{\hypertarget{'elefenwon}{'elefenwon}} \textit{n.} (\hyperlink{'elefen}{'elefen}+\allowbreak \hyperlink{won}{won})
Lingua Franca Novist; Lingua Franca Nova speakers

\textbf{\hypertarget{'elin}{'elin}} \textit{n.} (Ell. ⟨Έλλην⟩ [ˈelin])
Greek; Grecian; Hellene; the Greek people

\textbf{\hypertarget{'elinak}{'elinak}} \textit{n.} (\hyperlink{'elin}{'elin}+\allowbreak \hyperlink{ak}{ak})
Greek; Grecian; Hellenic; from Greece

\textbf{\hypertarget{'elin'kilistosfitilip}{'elin'kilistosfitilip}} \textit{n.} (\hyperlink{'elin}{'elin}+\allowbreak \hyperlink{'kilistosfitilip}{'kilistosfitilip})
Greek Orthodoxy; Orthodox Catholicism; Eastern Orthodoxy

\textbf{\hypertarget{'elintec}{'elintec}} \textit{n.} (\hyperlink{'elin}{'elin}+\allowbreak \hyperlink{tec}{tec})
Greece

\textbf{\hypertarget{'elintilip}{'elintilip}} \textit{n.} (\hyperlink{'elin}{'elin}+\allowbreak \hyperlink{tilip}{tilip})
Greek; the Greek language

\textbf{\hypertarget{'elitla}{'elitla}} \textit{n.} (Tir. ⟨{\ethiopic{}ኤርትራ}⟩ [ertra])
Eritrea

\textbf{\hypertarget{'elitlaak}{'elitlaak}} \textit{n.} (\hyperlink{'elitla}{'elitla}+\allowbreak \hyperlink{ak}{ak})
Eritrean; from Eritrea

\textbf{\hypertarget{'elitlawon}{'elitlawon}} \textit{n.} (\hyperlink{'elitla}{'elitla}+\allowbreak \hyperlink{won}{won})
Eritrean; the Eritrean people

\textbf{\hypertarget{'elya}{'elya}} \textit{n.} (Gle. ⟨Éire⟩ [ˈeːɾʲə])
Ireland (landmass)

\textbf{\hypertarget{'elyaak}{'elyaak}} \textit{n.} (\hyperlink{'elya}{'elya}+\allowbreak \hyperlink{ak}{ak})
Irish; from Ireland

\textbf{\hypertarget{'elyawon}{'elyawon}} \textit{n.} (\hyperlink{'elya}{'elya}+\allowbreak \hyperlink{won}{won})
Irishman; the Irish people

\textbf{\hypertarget{'elyatec}{'elyatec}} \textit{n.} (\hyperlink{'elya}{'elya}+\allowbreak \hyperlink{tec}{tec})
Ireland; the Republic of Ireland

\textbf{\hypertarget{'elyatilip}{'elyatilip}} \textit{n.} (\hyperlink{'elya}{'elya}+\allowbreak \hyperlink{tilip}{tilip})
Irish; Gaelic; the Irish language

\textbf{\hypertarget{'ewlo}{'ewlo}} \textit{n.} (Spa. ⟨euro⟩ [ˈewɾo])
euro; €

\textbf{\hypertarget{'ewlope}{'ewlope}} \textit{n.} (Grc. ⟨Εὐρώπη⟩ [ēwrɔ́ːpɛ̄ː])
Europe

\textbf{\hypertarget{'ewlopeak}{'ewlopeak}} \textit{n.} (\hyperlink{'ewlope}{'ewlope}+\allowbreak \hyperlink{ak}{ak})
European; from Europe

\textbf{\hypertarget{'ewlopewon}{'ewlopewon}} \textit{n.} (\hyperlink{'ewlope}{'ewlope}+\allowbreak \hyperlink{won}{won})
European; the European people

\textbf{\hypertarget{en}{en}} \textit{spec.} (Eng. ⟨any⟩ [ˈɛni])
any; one of; \textit{describes a single arbitrary instance of the following noun phrase}

\textbf{\hypertarget{eni}{eni}} \textit{v.} (\hyperlink{oku}{\sout{oku}})
be cold; be cool; \hyperlink{enilon}{ʟᴏᴧ} is colder than ʟᴜᴍ

\textbf{\hypertarget{eniufa}{eniufa}} \textit{v.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{ufa}{ufa})
be snow; be shaved ice; be slush; \hyperlink{eniufalon}{ʟᴏᴧ} is made of snow

\textbf{\hypertarget{eniufalon}{eniufalon}} \textit{n.} (\hyperlink{eniufa}{eniufa}+\allowbreak \hyperlink{lon}{lon})
snow; shaved ice; slush

\textbf{\hypertarget{enilon}{enilon}} \textit{n.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{lon}{lon})
cold; cool

\textbf{\hypertarget{enilono}{enilono}} \textit{v.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{lono}{lono})
be cool-coloured; \hyperlink{enilonolon}{ʟᴏᴧ} is green, blue, purple, or black

\textbf{\hypertarget{enilonolon}{enilonolon}} \textit{n.} (\hyperlink{enilono}{enilono}+\allowbreak \hyperlink{lon}{lon})
cool-coloured

\textbf{\hypertarget{enihila}{enihila}} \textit{v.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{hila}{hila})
shiver; shudder; tremble; quiver; ʟᴏᴧ is shivering

\textbf{\hypertarget{enicipcip}{enicipcip}} \textit{n.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{cipcip}{cipcip})
penguin

\textbf{\hypertarget{enisison}{enisison}} \textit{n.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{sison}{sison})
winter

\textbf{\hypertarget{eniki}{eniki}} \textit{v.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{ki}{ki})
cool; \hyperlink{enikiles}{ʟєꜱ} makes ʟᴏᴧ cool down relative to ʟᴜᴍ

\textbf{\hypertarget{enikiles}{enikiles}} \textit{n.} (\hyperlink{eniki}{eniki}+\allowbreak \hyperlink{les}{les})
cooler; air conditioner

\textbf{\hypertarget{enitayl}{enitayl}} \textit{n.} (\hyperlink{eni}{eni}+\allowbreak \hyperlink{tayl}{tayl})
tundra

\textbf{\hypertarget{'emalati}{'emalati}} \textit{n.} (Ara. ⟨{\arabics{}إماراتيين‎}⟩ [ʔemaːraːti])
Emirati; the Emirati people

\textbf{\hypertarget{'emalatiak}{'emalatiak}} \textit{n.} (\hyperlink{'emalati}{'emalati}+\allowbreak \hyperlink{ak}{ak})
Emirati; Emirian; Emiri; from the United Arab Emirates

\textbf{\hypertarget{'emalatitec}{'emalatitec}} \textit{n.} (\hyperlink{'emalati}{'emalati}+\allowbreak \hyperlink{tec}{tec})
United Arab Emirates

\textbf{\hypertarget{emana}{emana}} \textit{v.} (\hyperlink{opaka}{\sout{opaka}})
be transparent; be see-through; \hyperlink{emanalon}{ʟᴏᴧ} lets unreflected light pass through it

\textbf{\hypertarget{emanalon}{emanalon}} \textit{n.} (\hyperlink{emana}{emana}+\allowbreak \hyperlink{lon}{lon})
window; transparent; see-through

\textbf{\hypertarget{emanaki}{emanaki}} \textit{v.} (\hyperlink{emana}{emana}+\allowbreak \hyperlink{ki}{ki})
transparify; ʟєꜱ makes ʟᴏᴧ become transparent

\textbf{\hypertarget{emanapato}{emanapato}} \textit{v.} (\hyperlink{emana}{emana}+\allowbreak \hyperlink{pato}{pato})
be glass; \hyperlink{emanapatolon}{ʟᴏᴧ} is made of glass

\textbf{\hypertarget{emanapatolon}{emanapatolon}} \textit{n.} (\hyperlink{emanapato}{emanapato}+\allowbreak \hyperlink{lon}{lon})
glass

\textbf{\hypertarget{'emoci}{'emoci}} \textit{n.} (Jpn. ⟨{\japanese{}絵文字}⟩ [emod͡ʑi])
emoji

\textbf{\hypertarget{'empanata}{'empanata}} \textit{n.} (Spa. ⟨empanada⟩ [empaˈnaða])
empanada

\textbf{\hypertarget{ec}{ec}} \textit{n.} (Yor. ⟨ẹṣẹ́⟩ [ɛ̄ʃɛ́])
gland; organ; node; functional organic module

\textbf{\hypertarget{ecak}{ecak}} \textit{n.} (\hyperlink{ec}{ec}+\allowbreak \hyperlink{ak}{ak})
glandular; nodal; bodily; internal

\textbf{\hypertarget{es}{es}} \textit{post.} (∅)
by; \textit{marks agent}

\textbf{\hypertarget{'eskutelya}{'eskutelya}} \textit{n.} (Cat. ⟨escudella⟩ [əskuˈðeʎə])
escudella

\textbf{\hypertarget{este}{este}} \textit{v.} (Spa. ⟨este⟩ [ˈeste])
be east; \hyperlink{estelon}{ʟᴏᴧ} has a higher longitude than \hyperlink{estelum}{ʟᴜᴍ}

\textbf{\hypertarget{estelon}{estelon}} \textit{n.} (\hyperlink{este}{este}+\allowbreak \hyperlink{lon}{lon})
the East; east

\textbf{\hypertarget{estelum}{estelum}} \textit{n.} (\hyperlink{este}{este}+\allowbreak \hyperlink{lum}{lum})
standard meridian; prime meridian

\textbf{\hypertarget{estelyan}{estelyan}} \textit{n.} (\hyperlink{este}{este}+\allowbreak \hyperlink{lyan}{lyan})
longitude

\textbf{\hypertarget{estelyanpucolon}{estelyanpucolon}} \textit{n.} (\hyperlink{estelyan}{estelyan}+\allowbreak \hyperlink{pucolon}{pucolon})
meridian

\textbf{\hypertarget{esteseswicon}{esteseswicon}} \textit{n.} (\hyperlink{este}{este}+\allowbreak \hyperlink{ses}{ses}+\allowbreak \hyperlink{wicon}{wicon})
Sinosphere; East Asia; the East Asian cultural sphere; Asia; the Sinic world

\textbf{\hypertarget{esteki}{esteki}} \textit{v.} (\hyperlink{este}{este}+\allowbreak \hyperlink{ki}{ki})
go east; ʟєꜱ increases the longitude of ʟᴏᴧ relative to ʟᴜᴍ

\textbf{\hypertarget{este'timol}{este'timol}} \textit{n.} (\hyperlink{este}{este}+\allowbreak \hyperlink{'timol}{'timol})
East Timor; Timor-Leste; Democratic Republic of Timor-Leste

\textbf{\hypertarget{este'timolwon}{este'timolwon}} \textit{n.} (\hyperlink{este'timol}{este'timol}+\allowbreak \hyperlink{won}{won})
Timorese; East Timorese; Maubere; the East Timorese people

\textbf{\hypertarget{esta}{esta}} \textit{v.} (Spa. ⟨estar⟩ [estar])
be; exist; have; equal; be the same; \textit{copula}; \hyperlink{estalon}{ʟᴏᴧ} exists and is the same thing as ʟᴜᴍ

\textbf{\hypertarget{estaak}{estaak}} \textit{n.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{ak}{ak})
fair; uniform; equal

\textbf{\hypertarget{estalon}{estalon}} \textit{n.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{lon}{lon})
thing; the same

\textbf{\hypertarget{estaloncolon}{estaloncolon}} \textit{n.} (\hyperlink{estalon}{estalon}+\allowbreak \hyperlink{colon}{colon})
noun

\textbf{\hypertarget{estalyan}{estalyan}} \textit{n.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{lyan}{lyan})
number; count; amount

\textbf{\hypertarget{estalyanhulum}{estalyanhulum}} \textit{n.} (\hyperlink{estalyan}{estalyan}+\allowbreak \hyperlink{hulum}{hulum})
graph; plot

\textbf{\hypertarget{estalyanhulumak}{estalyanhulumak}} \textit{n.} (\hyperlink{estalyanhulum}{estalyanhulum}+\allowbreak \hyperlink{ak}{ak})
graphical

\textbf{\hypertarget{estanu}{estanu}} \textit{v.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{nu}{nu})
delete; destroy; take; disappear; ruin; end; \hyperlink{estanules}{ʟєꜱ} deletes \hyperlink{estanulon}{ʟᴏᴧ}

\textbf{\hypertarget{estanules}{estanules}} \textit{n.} (\hyperlink{estanu}{estanu}+\allowbreak \hyperlink{les}{les})
deleter; destroyer

\textbf{\hypertarget{estanulon}{estanulon}} \textit{n.} (\hyperlink{estanu}{estanu}+\allowbreak \hyperlink{lon}{lon})
deleted; disappeared

\textbf{\hypertarget{estanyolon}{estanyolon}} \textit{n.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{lon}{lon})
other; not; anything but

\textbf{\hypertarget{estaki}{estaki}} \textit{v.} (\hyperlink{esta}{esta}+\allowbreak \hyperlink{ki}{ki})
create; make; give; get; appear; produce; originate; \hyperlink{estakiles}{ʟєꜱ} makes \hyperlink{estakilon}{ʟᴏᴧ} into ʟᴜᴍ

\textbf{\hypertarget{estakiles}{estakiles}} \textit{n.} (\hyperlink{estaki}{estaki}+\allowbreak \hyperlink{les}{les})
creator

\textbf{\hypertarget{estakilon}{estakilon}} \textit{n.} (\hyperlink{estaki}{estaki}+\allowbreak \hyperlink{lon}{lon})
creation

\textbf{\hypertarget{estakilip}{estakilip}} \textit{n.} (\hyperlink{estaki}{estaki}+\allowbreak \hyperlink{lip}{lip})
recipe

\textbf{\hypertarget{estakilyot}{estakilyot}} \textit{n.} (\hyperlink{estaki}{estaki}+\allowbreak \hyperlink{lyot}{lyot})
factory; makery; source

\textbf{\hypertarget{'esti}{'esti}} \textit{n.} (Est. ⟨eesti⟩ [eːsti])
Estonian; the Estonian people

\textbf{\hypertarget{'estiak}{'estiak}} \textit{n.} (\hyperlink{'esti}{'esti}+\allowbreak \hyperlink{ak}{ak})
Estonian; from Estonia

\textbf{\hypertarget{'estitec}{'estitec}} \textit{n.} (\hyperlink{'esti}{'esti}+\allowbreak \hyperlink{tec}{tec})
Estonia

\textbf{\hypertarget{'estitilip}{'estitilip}} \textit{n.} (\hyperlink{'esti}{'esti}+\allowbreak \hyperlink{tilip}{tilip})
Estonian; the Estonian language

\textbf{\hypertarget{'espelanto}{'espelanto}} \textit{n.} (Epo. ⟨Esperanto⟩ [espeˈranto])
Esperanto

\textbf{\hypertarget{'espelantoak}{'espelantoak}} \textit{n.} (\hyperlink{'espelanto}{'espelanto}+\allowbreak \hyperlink{ak}{ak})
Esperanto; Esperantist; Esperanta

\textbf{\hypertarget{'espelantowon}{'espelantowon}} \textit{n.} (\hyperlink{'espelanto}{'espelanto}+\allowbreak \hyperlink{won}{won})
Esperantist; Esperanto speakers

\textbf{\hypertarget{'espanya}{'espanya}} \textit{n.} (Spa. ⟨españa⟩ [espaɲa])
Spain

\textbf{\hypertarget{'espanyaak}{'espanyaak}} \textit{n.} (\hyperlink{'espanya}{'espanya}+\allowbreak \hyperlink{ak}{ak})
Spanish; from Spain

\textbf{\hypertarget{'espanyawon}{'espanyawon}} \textit{n.} (\hyperlink{'espanya}{'espanya}+\allowbreak \hyperlink{won}{won})
Spaniard; the Spanish people

\textbf{\hypertarget{'espanyatilip}{'espanyatilip}} \textit{n.} (\hyperlink{'espanya}{'espanya}+\allowbreak \hyperlink{tilip}{tilip})
the Spanish language

\textbf{\hypertarget{'espaketti}{'espaketti}} \textit{n.} (Ita. ⟨spaghetti⟩ [spaˈɡetti])
spaghetti

\textbf{\hypertarget{efe}{efe}} \textit{v.} (\hyperlink{oso}{\sout{oso}})
be less; be negative; be not enough; be too little; \hyperlink{efelon}{ʟᴏᴧ} is numerically less than ʟᴜᴍ

\textbf{\hypertarget{efelon}{efelon}} \textit{n.} (\hyperlink{efe}{efe}+\allowbreak \hyperlink{lon}{lon})
less; negative; not enough; too little

\textbf{\hypertarget{efeki}{efeki}} \textit{v.} (\hyperlink{efe}{efe}+\allowbreak \hyperlink{ki}{ki})
decrease; diminish; dwindle; consolidate; \hyperlink{efekiles}{ʟєꜱ} makes ʟᴏᴧ decrease relative to ʟᴜᴍ

\textbf{\hypertarget{efekiles}{efekiles}} \textit{n.} (\hyperlink{efeki}{efeki}+\allowbreak \hyperlink{les}{les})
decreaser

\textbf{\hypertarget{'ekwatol}{'ekwatol}} \textit{n.} (Spa. ⟨Écuador⟩ [ˈekwaðoɾ])
Ecuador

\textbf{\hypertarget{'ekwatolak}{'ekwatolak}} \textit{n.} (\hyperlink{'ekwatol}{'ekwatol}+\allowbreak \hyperlink{ak}{ak})
Ecuadorian; from Ecuador

\textbf{\hypertarget{'ekwatolwon}{'ekwatolwon}} \textit{n.} (\hyperlink{'ekwatol}{'ekwatol}+\allowbreak \hyperlink{won}{won})
Ecuadorian; the Equadorian people

\textbf{\hypertarget{et}{et}} \textit{pn.} (Ben. ⟨{\bengali{}টা}⟩ [eʈa])
it; they; them; she; her; he; him; the; that; \textit{third person}; \textit{definite}; \textit{distal}; a previously mentioned noun phrase that is neither the speaker nor listener

\textbf{\hypertarget{et ayf}{et ayf}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{ayf}{ayf})
in that event

\textbf{\hypertarget{etak}{etak}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{ak}{ak})
its; her; hers; his; their; that’s

\textbf{\hypertarget{et ial}{et ial}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{ial}{ial})
therefore; for that reason

\textbf{\hypertarget{et ip}{et ip}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{ip}{ip})
thus; thereby

\textbf{\hypertarget{et uat}{et uat}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{uat}{uat})
with that; thus

\textbf{\hypertarget{et yot}{et yot}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{yot}{yot})
there

\textbf{\hypertarget{etle}{etle}} \textit{v.} (\hyperlink{olto}{\sout{olto}})
be number from the end; be in order from the end; negatively index; \hyperlink{etlelon}{ʟᴏᴧ} has an early position in ʟᴜᴍ

\textbf{\hypertarget{etlelon}{etlelon}} \textit{n.} (\hyperlink{etle}{etle}+\allowbreak \hyperlink{lon}{lon})
number from the end; in order from the end

\textbf{\hypertarget{etlelyan}{etlelyan}} \textit{n.} (\hyperlink{etle}{etle}+\allowbreak \hyperlink{lyan}{lyan})
position from end; negative index; number from end

\textbf{\hypertarget{etleki}{etleki}} \textit{v.} (\hyperlink{etle}{etle}+\allowbreak \hyperlink{ki}{ki})
move up; position; ʟєꜱ moves ʟᴏᴧ up the sequence ʟᴜᴍ

\textbf{\hypertarget{et wel}{et wel}} \textit{n.} (\hyperlink{et}{et}+\allowbreak \hyperlink{wel}{wel})
then

\section{Ƌ}

\textbf{\hypertarget{'a}{'a}} \textit{n.} (ono. [a])
a; /a/; open central unrounded vowel

\textbf{\hypertarget{'aa}{'aa}} \textit{n.} (Haw. ⟨ʻaʻā⟩ [ʔəˈʔaː])
aa

\textbf{\hypertarget{'aikito}{'aikito}} \textit{n.} (Jpn. ⟨{\japanese{}合気道}⟩ [aikidoː])
Aikido

\textbf{\hypertarget{'ayiti}{'ayiti}} \textit{n.} (Hat. ⟨Ayiti⟩ [ajiti])
Haiti

\textbf{\hypertarget{'ayitiak}{'ayitiak}} \textit{n.} (\hyperlink{'ayiti}{'ayiti}+\allowbreak \hyperlink{ak}{ak})
Haitian; from Haiti

\textbf{\hypertarget{'ayitiwon}{'ayitiwon}} \textit{n.} (\hyperlink{'ayiti}{'ayiti}+\allowbreak \hyperlink{won}{won})
Haitian; the Haitian people

\textbf{\hypertarget{'ayititilip}{'ayititilip}} \textit{n.} (\hyperlink{'ayiti}{'ayiti}+\allowbreak \hyperlink{tilip}{tilip})
Haitian creole

\textbf{\hypertarget{ayuta}{ayuta}} \textit{v.} (Spa. ⟨ayuda⟩ [aˈʝuða])
help; be for; ally; support; benefit; work with; assist; be auxiliary; \hyperlink{ayutalon}{ʟᴏᴧ} is working toward the same goal as \hyperlink{ayutalum}{ʟᴜᴍ}

\textbf{\hypertarget{ayutaici}{ayutaici}} \textit{v.} (\hyperlink{ayuta}{ayuta}+\allowbreak \hyperlink{ici}{ici})
synergise; have mutualistic relation; \hyperlink{ayutaicilon}{ʟᴏᴧ} benefits from helping \hyperlink{ayutaicilum}{ʟᴜᴍ}

\textbf{\hypertarget{ayutaicilon}{ayutaicilon}} \textit{n.} (\hyperlink{ayutaici}{ayutaici}+\allowbreak \hyperlink{lon}{lon})
symbiote

\textbf{\hypertarget{ayutaicilum}{ayutaicilum}} \textit{n.} (\hyperlink{ayutaici}{ayutaici}+\allowbreak \hyperlink{lum}{lum})
host

\textbf{\hypertarget{ayutalon}{ayutalon}} \textit{n.} (\hyperlink{ayuta}{ayuta}+\allowbreak \hyperlink{lon}{lon})
helper; assistant; for; auxiliary

\textbf{\hypertarget{ayutalum}{ayutalum}} \textit{n.} (\hyperlink{ayuta}{ayuta}+\allowbreak \hyperlink{lum}{lum})
ally; friend

\textbf{\hypertarget{ayutaki}{ayutaki}} \textit{v.} (\hyperlink{ayuta}{ayuta}+\allowbreak \hyperlink{ki}{ki})
align with; join; team up; \hyperlink{ayutakiles}{ʟєꜱ} makes ʟᴏᴧ ally with ʟᴜᴍ

\textbf{\hypertarget{ayutakiles}{ayutakiles}} \textit{n.} (\hyperlink{ayutaki}{ayutaki}+\allowbreak \hyperlink{les}{les})
alliance forger

\textbf{\hypertarget{ayutapaltolum}{ayutapaltolum}} \textit{n.} (\hyperlink{ayuta}{ayuta}+\allowbreak \hyperlink{paltolum}{paltolum})
team

\textbf{\hypertarget{ayf}{ayf}} \textit{post.} (Eng. ⟨if⟩ [ɪf])
if; for; \textit{marks hypothetical world}

\textbf{\hypertarget{alaktan}{alaktan}} \textit{n.} (Fil. ⟨alakdan⟩ [alakdan])
scorpion; Scorpiones

\textbf{\hypertarget{'alap}{'alap}} \textit{n.} (Ara. ⟨{\arabics{}عرب}⟩ [ˈʕarab])
Arab; the Arabian people

\textbf{\hypertarget{'alapak}{'alapak}} \textit{n.} (\hyperlink{'alap}{'alap}+\allowbreak \hyperlink{ak}{ak})
Saudi; Saudi Arabian; Arabia; from Saudi Arabia

\textbf{\hypertarget{'alaplawt}{'alaplawt}} \textit{n.} (\hyperlink{'alap}{'alap}+\allowbreak \hyperlink{lawt}{lawt})
Arabian Sea

\textbf{\hypertarget{'alapkwelyot}{'alapkwelyot}} \textit{n.} (\hyperlink{'alap}{'alap}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Arabia; the Arabian peninsula

\textbf{\hypertarget{'alaptec}{'alaptec}} \textit{n.} (\hyperlink{'alap}{'alap}+\allowbreak \hyperlink{tec}{tec})
Saudi Arabia

\textbf{\hypertarget{'alaptilip}{'alaptilip}} \textit{n.} (\hyperlink{'alap}{'alap}+\allowbreak \hyperlink{tilip}{tilip})
Arabic; the Arabic language

\textbf{\hypertarget{'alon}{'alon}} \textit{n.} (Oss. ⟨Аллон⟩ [alon])
Ossetian; Ossete; the Ossetian people

\textbf{\hypertarget{'alonak}{'alonak}} \textit{n.} (\hyperlink{'alon}{'alon}+\allowbreak \hyperlink{ak}{ak})
Ossetian; of the Ossetians

\textbf{\hypertarget{'alontilip}{'alontilip}} \textit{n.} (\hyperlink{'alon}{'alon}+\allowbreak \hyperlink{tilip}{tilip})
Ossetian; Ossete; Ossetic; the Ossetian language

\textbf{\hypertarget{'aloha}{'aloha}} \textit{n.} (Haw. ⟨aloha⟩ [əˈloha])
aloha; the Aloha Spirit

\textbf{\hypertarget{alik}{alik}} \textit{n.} (\hyperlink{atun}{\sout{atun}})
adult; fully-grown animal

\textbf{\hypertarget{alikak}{alikak}} \textit{n.} (\hyperlink{alik}{alik}+\allowbreak \hyperlink{ak}{ak})
adult

\textbf{\hypertarget{'aluminium}{'aluminium}} \textit{n.} (Lat. ⟨aluminium⟩ [alʊminɪʊ̃])
aluminium; aluminum

\textbf{\hypertarget{'alhentina}{'alhentina}} \textit{n.} (Spa. ⟨Argentina⟩ [aɾxenˈtina])
Argentina; the Argentine Republic

\textbf{\hypertarget{'alhentinaak}{'alhentinaak}} \textit{n.} (\hyperlink{'alhentina}{'alhentina}+\allowbreak \hyperlink{ak}{ak})
Argentinean; Argentine; from Argentina

\textbf{\hypertarget{'alhentinawon}{'alhentinawon}} \textit{n.} (\hyperlink{'alhentina}{'alhentina}+\allowbreak \hyperlink{won}{won})
Argentinean; Argentine; the Argentinean people

\textbf{\hypertarget{'alsenikum}{'alsenikum}} \textit{n.} (Lat. ⟨arsenicum⟩ [arsenɪkʊ̃])
arsenic

\textbf{\hypertarget{'alsayil}{'alsayil}} \textit{n.} (Ara. ⟨{\arabics{}الدزاير}⟩ [ald͡zaːjiːr])
Algiers

\textbf{\hypertarget{'alsayiltec}{'alsayiltec}} \textit{n.} (\hyperlink{'alsayil}{'alsayil}+\allowbreak \hyperlink{tec}{tec})
Algeria

\textbf{\hypertarget{'alsayiltecwon}{'alsayiltecwon}} \textit{n.} (\hyperlink{'alsayiltec}{'alsayiltec}+\allowbreak \hyperlink{won}{won})
Algerian; the Algerian people

\textbf{\hypertarget{alkas}{alkas}} \textit{n.} (Spa. ⟨algas⟩ [ˈalɣas])
algae; moss; tiny clumping photosynthetic prokaryote

\textbf{\hypertarget{'alkon}{'alkon}} \textit{n.} (Lat. ⟨argon⟩ [arɡɔn])
argon

\textbf{\hypertarget{alkun}{alkun}} \textit{spec.} (Spa. ⟨algunos⟩ [alˈɣunos])
some; \textit{describes an unspecified subset of the following noun phrase}

\textbf{\hypertarget{aw}{aw}} \textit{spec.} (Cmn. ⟨{\chinese{}和}⟩ [xɤ˧˥])
and; and/or; /; \textit{delineates a conjugate phrase}

\textbf{\hypertarget{awila}{awila}} \textit{v.} (\hyperlink{ayuta}{\sout{ayuta}})
hinder; be against; oppose; harm; compete; fight; counter; \hyperlink{awilalon}{ʟᴏᴧ} is working toward a goal contrary to that of \hyperlink{awilalum}{ʟᴜᴍ}

\textbf{\hypertarget{awilaici}{awilaici}} \textit{v.} (\hyperlink{awila}{awila}+\allowbreak \hyperlink{ici}{ici})
mooch; leech; have parasitic relation; \hyperlink{awilaicilon}{ʟᴏᴧ} benefits from hindering \hyperlink{awilaicilum}{ʟᴜᴍ}

\textbf{\hypertarget{awilaicilon}{awilaicilon}} \textit{n.} (\hyperlink{awilaici}{awilaici}+\allowbreak \hyperlink{lon}{lon})
parasite; leech; freeloader

\textbf{\hypertarget{awilaicilum}{awilaicilum}} \textit{n.} (\hyperlink{awilaici}{awilaici}+\allowbreak \hyperlink{lum}{lum})
host

\textbf{\hypertarget{awilalon}{awilalon}} \textit{n.} (\hyperlink{awila}{awila}+\allowbreak \hyperlink{lon}{lon})
opposer; against

\textbf{\hypertarget{awilalum}{awilalum}} \textit{n.} (\hyperlink{awila}{awila}+\allowbreak \hyperlink{lum}{lum})
opponent; competitor; enemy

\textbf{\hypertarget{awilaki}{awilaki}} \textit{v.} (\hyperlink{awila}{awila}+\allowbreak \hyperlink{ki}{ki})
turn against; betray; split up; \hyperlink{awilakiles}{ʟєꜱ} turns \hyperlink{awilakilon}{ʟᴏᴧ} against ʟᴜᴍ

\textbf{\hypertarget{awilakiles}{awilakiles}} \textit{n.} (\hyperlink{awilaki}{awilaki}+\allowbreak \hyperlink{les}{les})
instigator

\textbf{\hypertarget{awilakilon}{awilakilon}} \textit{n.} (\hyperlink{awilaki}{awilaki}+\allowbreak \hyperlink{lon}{lon})
traitor

\textbf{\hypertarget{anemon}{anemon}} \textit{n.} (Epo. ⟨anemono⟩ [aneˈmono])
sea anemone; Actiniaria

\textbf{\hypertarget{ano}{ano}} \textit{v.} (\hyperlink{ake}{\sout{ake}})
be behind; be backward; lag; \hyperlink{anolon}{ʟᴏᴧ} has a negative \textit{y} coordinate from ʟᴜᴍ’s point of view

\textbf{\hypertarget{'anol}{'anol}} \textit{n.} (Fas. ⟨{\arabics{}انار}⟩ [æˈnɒːɾ])
pomegranate; Punica

\textbf{\hypertarget{anolon}{anolon}} \textit{n.} (\hyperlink{ano}{ano}+\allowbreak \hyperlink{lon}{lon})
back; behind; backward

\textbf{\hypertarget{anonoki}{anonoki}} \textit{v.} (\hyperlink{ano}{ano}+\allowbreak \hyperlink{noki}{noki})
primarily educate; elementary school; middle school; \hyperlink{anonokiles}{ʟєꜱ} teaches \hyperlink{anonokilon}{ʟᴏᴧ}

\textbf{\hypertarget{anonokiles}{anonokiles}} \textit{n.} (\hyperlink{anonoki}{anonoki}+\allowbreak \hyperlink{les}{les})
elementary school teacher

\textbf{\hypertarget{anonokilon}{anonokilon}} \textit{n.} (\hyperlink{anonoki}{anonoki}+\allowbreak \hyperlink{lon}{lon})
elementary schooler

\textbf{\hypertarget{anonokilyot}{anonokilyot}} \textit{n.} (\hyperlink{anonoki}{anonoki}+\allowbreak \hyperlink{lyot}{lyot})
elementary school; middle school

\textbf{\hypertarget{anonokilwel}{anonokilwel}} \textit{n.} (\hyperlink{anonoki}{anonoki}+\allowbreak \hyperlink{lwel}{lwel})
primary education

\textbf{\hypertarget{anocalu}{anocalu}} \textit{v.} (\hyperlink{ano}{ano}+\allowbreak \hyperlink{calu}{calu})
follow; trail; ʟєꜱ makes \hyperlink{anocalulon}{ʟᴏᴧ} follow \hyperlink{anocalulum}{ʟᴜᴍ}

\textbf{\hypertarget{anocalulon}{anocalulon}} \textit{n.} (\hyperlink{anocalu}{anocalu}+\allowbreak \hyperlink{lon}{lon})
follower; tail

\textbf{\hypertarget{anocalulum}{anocalulum}} \textit{n.} (\hyperlink{anocalu}{anocalu}+\allowbreak \hyperlink{lum}{lum})
followed

\textbf{\hypertarget{anoki}{anoki}} \textit{v.} (\hyperlink{ano}{ano}+\allowbreak \hyperlink{ki}{ki})
retreat; fall behind; go backward; lose; \hyperlink{anokiles}{ʟєꜱ} makes ʟᴏᴧ move backward from ʟᴜᴍ’s point of view

\textbf{\hypertarget{anokiles}{anokiles}} \textit{n.} (\hyperlink{anoki}{anoki}+\allowbreak \hyperlink{les}{les})
retreater

\textbf{\hypertarget{ani}{ani}} \textit{v.} (Ibo. ⟨anị⟩ [anɪ])
be soil; be dirt; be earth; \hyperlink{anilon}{ʟᴏᴧ} is made out of dirt

\textbf{\hypertarget{anilon}{anilon}} \textit{n.} (\hyperlink{ani}{ani}+\allowbreak \hyperlink{lon}{lon})
soil; dirt; earth

\textbf{\hypertarget{'anime}{'anime}} \textit{n.} (Jpn. ⟨{\japanese{}アニメ}⟩ [aɲime])
anime

\textbf{\hypertarget{animaceki}{animaceki}} \textit{v.} (\hyperlink{ani}{ani}+\allowbreak \hyperlink{maceki}{maceki})
exhume; uncover; ʟєꜱ exhumes ʟᴏᴧ

\textbf{\hypertarget{anicwelon}{anicwelon}} \textit{n.} (\hyperlink{ani}{ani}+\allowbreak \hyperlink{cwelon}{cwelon})
mud

\textbf{\hypertarget{aniki}{aniki}} \textit{v.} (\hyperlink{ani}{ani}+\allowbreak \hyperlink{ki}{ki})
disintigrate; decompose; turn to dirt; ʟєꜱ turns ʟᴏᴧ to dirt

\textbf{\hypertarget{anipahoki}{anipahoki}} \textit{v.} (\hyperlink{ani}{ani}+\allowbreak \hyperlink{pahoki}{pahoki})
bury; ʟєꜱ buries ʟᴏᴧ

\textbf{\hypertarget{anco}{anco}} \textit{v.} (Spa. ⟨ancho⟩ [ˈant͡ʃo])
be broad; be wide; \hyperlink{ancolon}{ʟᴏᴧ} is broad in the dimension that is not length or thickness

\textbf{\hypertarget{ancolon}{ancolon}} \textit{n.} (\hyperlink{anco}{anco}+\allowbreak \hyperlink{lon}{lon})
ribbon; blade; broad; wide

\textbf{\hypertarget{ancolyan}{ancolyan}} \textit{n.} (\hyperlink{anco}{anco}+\allowbreak \hyperlink{lyan}{lyan})
breadth; middle dimension

\textbf{\hypertarget{ancosapu}{ancosapu}} \textit{v.} (\hyperlink{anco}{anco}+\allowbreak \hyperlink{sapu}{sapu})
sweep; ʟєꜱ sweeps ʟᴏᴧ off of ʟᴜᴍ

\textbf{\hypertarget{ancosapuluat}{ancosapuluat}} \textit{n.} (\hyperlink{ancosapu}{ancosapu}+\allowbreak \hyperlink{luat}{luat})
broom

\textbf{\hypertarget{ancoki}{ancoki}} \textit{v.} (\hyperlink{anco}{anco}+\allowbreak \hyperlink{ki}{ki})
broaden; \hyperlink{ancokiles}{ʟєꜱ} broadens ʟᴏᴧ

\textbf{\hypertarget{ancokiles}{ancokiles}} \textit{n.} (\hyperlink{ancoki}{ancoki}+\allowbreak \hyperlink{les}{les})
broadener

\textbf{\hypertarget{'ankola}{'ankola}} \textit{n.} (Por. ⟨Angola⟩ [ɐ̃ˈɡɔlɐ])
Angola

\textbf{\hypertarget{'ankolaak}{'ankolaak}} \textit{n.} (\hyperlink{'ankola}{'ankola}+\allowbreak \hyperlink{ak}{ak})
Angolan; from Angola

\textbf{\hypertarget{'ankolawon}{'ankolawon}} \textit{n.} (\hyperlink{'ankola}{'ankola}+\allowbreak \hyperlink{won}{won})
Angolan; the Angolan people

\textbf{\hypertarget{anta}{anta}} \textit{v.} (\hyperlink{akla}{\sout{akla}})
be dull; be blunt; be blurry; be nebulous; be wide; be gradual; \hyperlink{antalon}{ʟᴏᴧ} has a long radius of curvature

\textbf{\hypertarget{antalon}{antalon}} \textit{n.} (\hyperlink{anta}{anta}+\allowbreak \hyperlink{lon}{lon})
dull; blunt; blurry; nebulous; wide; gradual

\textbf{\hypertarget{antalyan}{antalyan}} \textit{n.} (\hyperlink{anta}{anta}+\allowbreak \hyperlink{lyan}{lyan})
radius of curvature

\textbf{\hypertarget{antaki}{antaki}} \textit{v.} (\hyperlink{anta}{anta}+\allowbreak \hyperlink{ki}{ki})
dull; blur; ʟєꜱ dulls ʟᴏᴧ

\textbf{\hypertarget{'antola}{'antola}} \textit{n.} (Cat. ⟨Andorra⟩ [ənˈdorə])
Andorran; the Andorran people

\textbf{\hypertarget{'antolaak}{'antolaak}} \textit{n.} (\hyperlink{'antola}{'antola}+\allowbreak \hyperlink{ak}{ak})
Andorran; from Andorra

\textbf{\hypertarget{'antolatec}{'antolatec}} \textit{n.} (\hyperlink{'antola}{'antola}+\allowbreak \hyperlink{tec}{tec})
Andorra

\textbf{\hypertarget{'antometa}{'antometa}} \textit{n.} (Grc. ⟨Ἀνδρομέδα⟩ [an˦dro˧me˦da˧])
Andromeda (galaxy)

\textbf{\hypertarget{'antometaak}{'antometaak}} \textit{n.} (\hyperlink{'antometa}{'antometa}+\allowbreak \hyperlink{ak}{ak})
Andromedan

\textbf{\hypertarget{'antika}{'antika}} \textit{n.} (Aig. ⟨Antigua⟩ [ænˈtiːɡə])
Antigua; Waladli; Wadadli

\textbf{\hypertarget{'antikaak}{'antikaak}} \textit{n.} (\hyperlink{'antika}{'antika}+\allowbreak \hyperlink{ak}{ak})
Antiguan

\textbf{\hypertarget{'antikatilip}{'antikatilip}} \textit{n.} (\hyperlink{'antika}{'antika}+\allowbreak \hyperlink{tilip}{tilip})
Antiguan Creole; Leeward Caribbean Creole English

\textbf{\hypertarget{am}{am}} \textit{n.} (Eng. ⟨arm⟩ [ɑɹm])
arm; long appendage used for manipulation

\textbf{\hypertarget{'amelika}{'amelika}} \textit{n.} (Spa. ⟨América⟩ [aˈmeɾika])
America; the Americas; the New World

\textbf{\hypertarget{'amelikaak}{'amelikaak}} \textit{n.} (\hyperlink{'amelika}{'amelika}+\allowbreak \hyperlink{ak}{ak})
American; from America

\textbf{\hypertarget{'amelikatec}{'amelikatec}} \textit{n.} (\hyperlink{'amelika}{'amelika}+\allowbreak \hyperlink{tec}{tec})
America; U.S.A.; the United States of America

\textbf{\hypertarget{'amelikatecwon}{'amelikatecwon}} \textit{n.} (\hyperlink{'amelikatec}{'amelikatec}+\allowbreak \hyperlink{won}{won})
American; the American people

\textbf{\hypertarget{'amelikatulsetupel}{'amelikatulsetupel}} \textit{n.} (\hyperlink{'amelika}{'amelika}+\allowbreak \hyperlink{tulsetupel}{tulsetupel})
sweet potato

\textbf{\hypertarget{ama}{ama}} \textit{v.} (Sot. ⟨ama⟩ [ɑmɑ])
can feel; feel; touch; ʟᴏᴧ can physically feel ʟᴜᴍ

\textbf{\hypertarget{amaec}{amaec}} \textit{n.} (\hyperlink{ama}{ama}+\allowbreak \hyperlink{ec}{ec})
skin

\textbf{\hypertarget{amaak}{amaak}} \textit{n.} (\hyperlink{ama}{ama}+\allowbreak \hyperlink{ak}{ak})
tactile; tactual

\textbf{\hypertarget{amanu}{amanu}} \textit{v.} (\hyperlink{ama}{ama}+\allowbreak \hyperlink{nu}{nu})
hide tactually; ʟєꜱ makes ʟᴏᴧ stop feeling ʟᴜᴍ

\textbf{\hypertarget{amak}{amak}} \textit{n.} (\hyperlink{am}{am}+\allowbreak \hyperlink{ak}{ak})
brachial; appendicular

\textbf{\hypertarget{amaki}{amaki}} \textit{v.} (\hyperlink{ama}{ama}+\allowbreak \hyperlink{ki}{ki})
show tactually; ʟєꜱ shows ʟᴜᴍ to ʟᴏᴧ tactually

\textbf{\hypertarget{amapowi}{amapowi}} \textit{v.} (\hyperlink{ama}{ama}+\allowbreak \hyperlink{powi}{powi})
be tangible; be physical; be objective; \hyperlink{amapowilum}{ʟᴜᴍ} is tangible to \hyperlink{amapowilon}{ʟᴏᴧ}

\textbf{\hypertarget{amapowilon}{amapowilon}} \textit{n.} (\hyperlink{amapowi}{amapowi}+\allowbreak \hyperlink{lon}{lon})
tangible; physical; objective

\textbf{\hypertarget{amapowilum}{amapowilum}} \textit{n.} (\hyperlink{amapowi}{amapowi}+\allowbreak \hyperlink{lum}{lum})
object; thing

\textbf{\hypertarget{amapowilummai}{amapowilummai}} \textit{v.} (\hyperlink{amapowilum}{amapowilum}+\allowbreak \hyperlink{mai}{mai})
buy good; produce; \hyperlink{amapowilummailon}{ʟᴏᴧ} gives \hyperlink{amapowilummailum}{ʟᴜᴍ} to \hyperlink{amapowilummailes}{ʟєꜱ} in exchange for money

\textbf{\hypertarget{amapowilummailwel}{amapowilummailwel}} \textit{n.} (\hyperlink{amapowilummai}{amapowilummai}+\allowbreak \hyperlink{lwel}{lwel})
sale

\textbf{\hypertarget{amapowilummailes}{amapowilummailes}} \textit{n.} (\hyperlink{amapowilummai}{amapowilummai}+\allowbreak \hyperlink{les}{les})
consumer

\textbf{\hypertarget{amapowilummailum}{amapowilummailum}} \textit{n.} (\hyperlink{amapowilummai}{amapowilummai}+\allowbreak \hyperlink{lum}{lum})
good

\textbf{\hypertarget{amapowilummailon}{amapowilummailon}} \textit{n.} (\hyperlink{amapowilummai}{amapowilummai}+\allowbreak \hyperlink{lon}{lon})
producer; vendor

\textbf{\hypertarget{amapowinu}{amapowinu}} \textit{v.} (\hyperlink{amapowi}{amapowi}+\allowbreak \hyperlink{nu}{nu})
scan; abstract; intangiblise; \hyperlink{amapowinules}{ʟєꜱ} takes ʟᴏᴧ out of the physical realm

\textbf{\hypertarget{amapowinules}{amapowinules}} \textit{n.} (\hyperlink{amapowinu}{amapowinu}+\allowbreak \hyperlink{les}{les})
scanner abstracter

\textbf{\hypertarget{amapowinyo}{amapowinyo}} \textit{v.} (\hyperlink{amapowi}{amapowi}+\allowbreak \hyperlink{nyo}{nyo})
be digital; be intangible; be abstract; be nonphysical; \hyperlink{amapowinyolum}{ʟᴜᴍ} is abstract from \hyperlink{amapowinyolon}{ʟᴏᴧ}’s point of view

\textbf{\hypertarget{amapowinyolon}{amapowinyolon}} \textit{n.} (\hyperlink{amapowinyo}{amapowinyo}+\allowbreak \hyperlink{lon}{lon})
digital; intangible; abstract; nonphysical

\textbf{\hypertarget{amapowinyolum}{amapowinyolum}} \textit{n.} (\hyperlink{amapowinyo}{amapowinyo}+\allowbreak \hyperlink{lum}{lum})
concept

\textbf{\hypertarget{amapowiki}{amapowiki}} \textit{v.} (\hyperlink{amapowi}{amapowi}+\allowbreak \hyperlink{ki}{ki})
print; tangiblise; soidify; \hyperlink{amapowikiles}{ʟєꜱ} brings ʟᴏᴧ into the physical realm

\textbf{\hypertarget{amapowikiles}{amapowikiles}} \textit{n.} (\hyperlink{amapowiki}{amapowiki}+\allowbreak \hyperlink{les}{les})
printer

\textbf{\hypertarget{ami}{ami}} \textit{v.} (Epo. ⟨ami⟩ [ˈami])
love; be in love; be infatuated; \hyperlink{amilon}{ʟᴏᴧ} is romantically in love with \hyperlink{amilum}{ʟᴜᴍ}

\textbf{\hypertarget{amiyohau}{amiyohau}} \textit{v.} (\hyperlink{ami}{ami}+\allowbreak \hyperlink{yohau}{yohau})
date; court; ʟᴏᴧ is dating ʟᴜᴍ

\textbf{\hypertarget{amilon}{amilon}} \textit{n.} (\hyperlink{ami}{ami}+\allowbreak \hyperlink{lon}{lon})
lover; in love; infatuated

\textbf{\hypertarget{amilum}{amilum}} \textit{n.} (\hyperlink{ami}{ami}+\allowbreak \hyperlink{lum}{lum})
love; object of affection

\textbf{\hypertarget{amiki}{amiki}} \textit{v.} (\hyperlink{ami}{ami}+\allowbreak \hyperlink{ki}{ki})
set up; fall in love; introduce; infatuate; \hyperlink{amikiles}{ʟєꜱ} makes ʟᴏᴧ fall in love with ʟᴜᴍ

\textbf{\hypertarget{amikiles}{amikiles}} \textit{n.} (\hyperlink{amiki}{amiki}+\allowbreak \hyperlink{les}{les})
matchmaker; cupid

\textbf{\hypertarget{amla}{amla}} \textit{v.} (Jav. ⟨ambra⟩ [ɑmpɽɔ])
be widespread; be prevalent; be expansive; \hyperlink{amlalon}{ʟᴏᴧ} exists in many places

\textbf{\hypertarget{amlalon}{amlalon}} \textit{n.} (\hyperlink{amla}{amla}+\allowbreak \hyperlink{lon}{lon})
widespread; prevalent; expansive

\textbf{\hypertarget{amlalyan}{amlalyan}} \textit{n.} (\hyperlink{amla}{amla}+\allowbreak \hyperlink{lyan}{lyan})
prevalence

\textbf{\hypertarget{amlaki}{amlaki}} \textit{v.} (\hyperlink{amla}{amla}+\allowbreak \hyperlink{ki}{ki})
spread; expand; copy; advertise; \hyperlink{amlakiles}{ʟєꜱ} spreads \hyperlink{amlakilon}{ʟᴏᴧ}

\textbf{\hypertarget{amlakiles}{amlakiles}} \textit{n.} (\hyperlink{amlaki}{amlaki}+\allowbreak \hyperlink{les}{les})
spreader

\textbf{\hypertarget{amlakilon}{amlakilon}} \textit{n.} (\hyperlink{amlaki}{amlaki}+\allowbreak \hyperlink{lon}{lon})
spread

\textbf{\hypertarget{amlakipowi}{amlakipowi}} \textit{v.} (\hyperlink{amlaki}{amlaki}+\allowbreak \hyperlink{powi}{powi})
be contagious; \hyperlink{amlakipowilon}{ʟᴏᴧ} is contagious

\textbf{\hypertarget{amlakipowilon}{amlakipowilon}} \textit{n.} (\hyperlink{amlakipowi}{amlakipowi}+\allowbreak \hyperlink{lon}{lon})
contagious

\textbf{\hypertarget{amlut}{amlut}} \textit{n.} (Hin. ⟨{\devanagari{}अमरूद}⟩ [amruːd])
guava; Psidium

\textbf{\hypertarget{amhila}{amhila}} \textit{v.} (\hyperlink{am}{am}+\allowbreak \hyperlink{hila}{hila})
flail; ʟєꜱ flails \hyperlink{amhilalon}{ʟᴏᴧ}

\textbf{\hypertarget{amhilalon}{amhilalon}} \textit{n.} (\hyperlink{amhila}{amhila}+\allowbreak \hyperlink{lon}{lon})
flail; flailing limb

\textbf{\hypertarget{amhulinoluat}{amhulinoluat}} \textit{n.} (\hyperlink{am}{am}+\allowbreak \hyperlink{hulinoluat}{hulinoluat})
watch; wristwatch

\textbf{\hypertarget{amtokalyot}{amtokalyot}} \textit{n.} (\hyperlink{am}{am}+\allowbreak \hyperlink{tokalyot}{tokalyot})
shoulder

\textbf{\hypertarget{ampoltilum}{ampoltilum}} \textit{n.} (\hyperlink{am}{am}+\allowbreak \hyperlink{poltilum}{poltilum})
sleeve; armband

\textbf{\hypertarget{ahami}{ahami}} \textit{v.} (\hyperlink{acapu}{\sout{acapu}})
be average; be meh; be moderate; \hyperlink{ahamilon}{ʟᴏᴧ} is to a low degree

\textbf{\hypertarget{ahamilon}{ahamilon}} \textit{n.} (\hyperlink{ahami}{ahami}+\allowbreak \hyperlink{lon}{lon})
average; meh; moderate

\textbf{\hypertarget{acapu}{acapu}} \textit{v.} (Swa. ⟨ajabu⟩ [aʄaɓu])
be amazing; be extreme; be incredible; be absurd; \hyperlink{acapulon}{ʟᴏᴧ} is to a very high degree

\textbf{\hypertarget{acapulon}{acapulon}} \textit{n.} (\hyperlink{acapu}{acapu}+\allowbreak \hyperlink{lon}{lon})
amazing; extreme; incredible; absurd

\textbf{\hypertarget{'asalpaycan}{'asalpaycan}} \textit{n.} (Aze. ⟨Azərbaycan⟩ [ɑːzæɾbɑjˈd͡ʒɑn])
Azerbaijan

\textbf{\hypertarget{'asalpaycanak}{'asalpaycanak}} \textit{n.} (\hyperlink{'asalpaycan}{'asalpaycan}+\allowbreak \hyperlink{ak}{ak})
Azerbaijani; from Azerbaijan

\textbf{\hypertarget{'asalpaycantec}{'asalpaycantec}} \textit{n.} (\hyperlink{'asalpaycan}{'asalpaycan}+\allowbreak \hyperlink{tec}{tec})
Azerbaijani; the Azerbaijani people

\textbf{\hypertarget{'asalpaycantilip}{'asalpaycantilip}} \textit{n.} (\hyperlink{'asalpaycan}{'asalpaycan}+\allowbreak \hyperlink{tilip}{tilip})
Azerbaijani; the Azerbaijani language

\textbf{\hypertarget{'assutan}{'assutan}} \textit{n.} (Ara. ⟨{\arabics{}السودان‎}⟩ [assuːdaːn])
Sudan

\textbf{\hypertarget{'assutanak}{'assutanak}} \textit{n.} (\hyperlink{'assutan}{'assutan}+\allowbreak \hyperlink{ak}{ak})
Sudanese; from Sudan

\textbf{\hypertarget{'assutanwon}{'assutanwon}} \textit{n.} (\hyperlink{'assutan}{'assutan}+\allowbreak \hyperlink{won}{won})
Sudanese; the Sudanese people

\textbf{\hypertarget{'aflika}{'aflika}} \textit{n.} (Swa. ⟨Afrika⟩ [afrika])
Africa

\textbf{\hypertarget{'aflikaak}{'aflikaak}} \textit{n.} (\hyperlink{'aflika}{'aflika}+\allowbreak \hyperlink{ak}{ak})
African; from Africa

\textbf{\hypertarget{'aflika'yewlasia}{'aflika'yewlasia}} \textit{n.} (\hyperlink{'aflika}{'aflika}+\allowbreak \hyperlink{'yewlasia}{'yewlasia})
Afro-Eurasia; the Old World

\textbf{\hypertarget{'aflika'yewlasiatulsetupel}{'aflika'yewlasiatulsetupel}} \textit{n.} (\hyperlink{'aflika'yewlasia}{'aflika'yewlasia}+\allowbreak \hyperlink{tulsetupel}{tulsetupel})
yam

\textbf{\hypertarget{'afhan}{'afhan}} \textit{n.} (Prs. ⟨{\arabics{}افغانستان‬}⟩ [avɣɒn])
Afghan; the Afgan people

\textbf{\hypertarget{'afhanak}{'afhanak}} \textit{n.} (\hyperlink{'afhan}{'afhan}+\allowbreak \hyperlink{ak}{ak})
Afghan; from Afghanistan

\textbf{\hypertarget{'afhantec}{'afhantec}} \textit{n.} (\hyperlink{'afhan}{'afhan}+\allowbreak \hyperlink{tec}{tec})
Afghanistan

\textbf{\hypertarget{ak}{ak}} \textit{post.} (Hin. ⟨{\devanagari{}का}⟩ [kaː])
of; -’s; \textit{marks modifier or associate}

\textbf{\hypertarget{ake}{ake}} \textit{v.} (Hin. ⟨{\devanagari{}आगे}⟩ [aːɡe])
be in front; be ahead; be forward; \hyperlink{akelon}{ʟᴏᴧ} has a positive \textit{y} coordinate from ʟᴜᴍ’s point of view

\textbf{\hypertarget{akelon}{akelon}} \textit{n.} (\hyperlink{ake}{ake}+\allowbreak \hyperlink{lon}{lon})
field of view; in front; ahead; forward

\textbf{\hypertarget{akelyan}{akelyan}} \textit{n.} (\hyperlink{ake}{ake}+\allowbreak \hyperlink{lyan}{lyan})
\textit{y} coordinate; progress

\textbf{\hypertarget{akenoki}{akenoki}} \textit{v.} (\hyperlink{ake}{ake}+\allowbreak \hyperlink{noki}{noki})
secondarily educate; high school; middle school; \hyperlink{akenokiles}{ʟєꜱ} teaches \hyperlink{akenokilon}{ʟᴏᴧ}

\textbf{\hypertarget{akenokiles}{akenokiles}} \textit{n.} (\hyperlink{akenoki}{akenoki}+\allowbreak \hyperlink{les}{les})
high school teacher

\textbf{\hypertarget{akenokilon}{akenokilon}} \textit{n.} (\hyperlink{akenoki}{akenoki}+\allowbreak \hyperlink{lon}{lon})
high schooler

\textbf{\hypertarget{akenokilyot}{akenokilyot}} \textit{n.} (\hyperlink{akenoki}{akenoki}+\allowbreak \hyperlink{lyot}{lyot})
high school; middle school

\textbf{\hypertarget{akenokilwel}{akenokilwel}} \textit{n.} (\hyperlink{akenoki}{akenoki}+\allowbreak \hyperlink{lwel}{lwel})
secondary education

\textbf{\hypertarget{akeki}{akeki}} \textit{v.} (\hyperlink{ake}{ake}+\allowbreak \hyperlink{ki}{ki})
advance; go ahead; go forward; progress; gain; \hyperlink{akekiles}{ʟєꜱ} makes ʟᴏᴧ move forward from ʟᴜᴍ’s point of view

\textbf{\hypertarget{akekiles}{akekiles}} \textit{n.} (\hyperlink{akeki}{akeki}+\allowbreak \hyperlink{les}{les})
advancer

\textbf{\hypertarget{akla}{akla}} \textit{v.} (Epo. ⟨akra⟩ [ˈakra])
be sharp; be clear; be tight; \hyperlink{aklalon}{ʟᴏᴧ} has a short radius of curvature

\textbf{\hypertarget{aklalon}{aklalon}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{lon}{lon})
blade; edge; point; sharp; clear; tight

\textbf{\hypertarget{aklalyan}{aklalyan}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{lyan}{lyan})
sharpness; clarity

\textbf{\hypertarget{aklanyec}{aklanyec}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{nyec}{nyec})
porcupine

\textbf{\hypertarget{aklanyamaluat}{aklanyamaluat}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{nyamaluat}{nyamaluat})
fork

\textbf{\hypertarget{aklasapu}{aklasapu}} \textit{v.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{sapu}{sapu})
scratch; ʟєꜱ scratches ʟᴏᴧ

\textbf{\hypertarget{aklasapuluat}{aklasapuluat}} \textit{n.} (\hyperlink{aklasapu}{aklasapu}+\allowbreak \hyperlink{luat}{luat})
scratcher

\textbf{\hypertarget{aklaki}{aklaki}} \textit{v.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{ki}{ki})
sharpen; clarify; ʟєꜱ sharpens ʟᴏᴧ

\textbf{\hypertarget{aklakiluat}{aklakiluat}} \textit{n.} (\hyperlink{aklaki}{aklaki}+\allowbreak \hyperlink{luat}{luat})
sharpener

\textbf{\hypertarget{aklatun}{aklatun}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{tun}{tun})
seaurchin

\textbf{\hypertarget{aklapal}{aklapal}} \textit{n.} (\hyperlink{akla}{akla}+\allowbreak \hyperlink{pal}{pal})
needle

\textbf{\hypertarget{akhe}{akhe}} \textit{v.} (\hyperlink{anco}{\sout{anco}})
be narrow; be thin; \hyperlink{akhelon}{ʟᴏᴧ} is narrow in the dimension that is not length or thickness

\textbf{\hypertarget{akheyehkac}{akheyehkac}} \textit{n.} (\hyperlink{akhe}{akhe}+\allowbreak \hyperlink{yeh}{yeh}+\allowbreak \hyperlink{kac}{kac})
pine tree

\textbf{\hypertarget{akhelon}{akhelon}} \textit{n.} (\hyperlink{akhe}{akhe}+\allowbreak \hyperlink{lon}{lon})
narrow; thin

\textbf{\hypertarget{akheki}{akheki}} \textit{v.} (\hyperlink{akhe}{akhe}+\allowbreak \hyperlink{ki}{ki})
narrow; \hyperlink{akhekiles}{ʟєꜱ} narrows ʟᴏᴧ

\textbf{\hypertarget{akhekiles}{akhekiles}} \textit{n.} (\hyperlink{akheki}{akheki}+\allowbreak \hyperlink{les}{les})
narrower

\textbf{\hypertarget{'aktolos}{'aktolos}} \textit{n.} (Grc. ⟨Ἀρκτοῦρος⟩ [ark˦to˦˨ːros])
Arcturus

\textbf{\hypertarget{aktua}{aktua}} \textit{v.} (Spa. ⟨actúa⟩ [akˈtua])
act; say; voice; fill; \hyperlink{aktuales}{ʟєꜱ} acts as though \hyperlink{aktualon}{ʟᴏᴧ} is true

\textbf{\hypertarget{aktuales}{aktuales}} \textit{n.} (\hyperlink{aktua}{aktua}+\allowbreak \hyperlink{les}{les})
actor

\textbf{\hypertarget{aktualon}{aktualon}} \textit{n.} (\hyperlink{aktua}{aktua}+\allowbreak \hyperlink{lon}{lon})
act; role; charade; character; farce

\textbf{\hypertarget{at}{at}} \textit{n.} (Eng. ⟨art⟩ [ɑɹt])
art

\textbf{\hypertarget{atak}{atak}} \textit{n.} (\hyperlink{at}{at}+\allowbreak \hyperlink{ak}{ak})
artistic

\textbf{\hypertarget{atun}{atun}} \textit{n.} (Cmn. ⟨{\chinese{}儿童}⟩ [ɚ˧˥tʰʊŋ˧˥])
child; youth; girl; boy; adolescent; kid; not fully-grown animal

\textbf{\hypertarget{atunak}{atunak}} \textit{n.} (\hyperlink{atun}{atun}+\allowbreak \hyperlink{ak}{ak})
juvenile; adolescent

\textbf{\hypertarget{'atlas}{'atlas}} \textit{n.} (Ara. ⟨{\arabics{}الأطـلـس‎}⟩ [ʔatˤlas])
Atlas mountains

\textbf{\hypertarget{'atlaslawt}{'atlaslawt}} \textit{n.} (\hyperlink{'atlas}{'atlas}+\allowbreak \hyperlink{lawt}{lawt})
Atlantic Ocean

\textbf{\hypertarget{'atlaslawtak}{'atlaslawtak}} \textit{n.} (\hyperlink{'atlaslawt}{'atlaslawt}+\allowbreak \hyperlink{ak}{ak})
Atlantic

\textbf{\hypertarget{athwok}{athwok}} \textit{n.} (\hyperlink{at}{at}+\allowbreak \hyperlink{hwok}{hwok})
canvas

\textbf{\hypertarget{attilip}{attilip}} \textit{n.} (\hyperlink{at}{at}+\allowbreak \hyperlink{tilip}{tilip})
artlang; artistic language

\textbf{\hypertarget{ap}{ap}} \textit{n.} (Spa. ⟨ave⟩ [ˈaβe])
fowl; duck; swan; goose; chicken; turkey; pheasant; Galloanserae

\textbf{\hypertarget{'apswa}{'apswa}} \textit{n.} (Abk. ⟨Аҧсуа⟩ [apʰswa])
Abkhazian; Abkhaz; the Abkhazian people

\textbf{\hypertarget{'apswaak}{'apswaak}} \textit{n.} (\hyperlink{'apswa}{'apswa}+\allowbreak \hyperlink{ak}{ak})
Abkhazian; Abkhaz; from Abkhazia

\textbf{\hypertarget{'apswatec}{'apswatec}} \textit{n.} (\hyperlink{'apswa}{'apswa}+\allowbreak \hyperlink{tec}{tec})
Abkhazia

\textbf{\hypertarget{'apswatilip}{'apswatilip}} \textit{n.} (\hyperlink{'apswa}{'apswa}+\allowbreak \hyperlink{tilip}{tilip})
Abkhaz; Abkhazian; Abxaz; the Abkhaz language

\textbf{\hypertarget{apta}{apta}} \textit{v.} (\hyperlink{amla}{\sout{amla}})
be confined; be rare; \hyperlink{aptalon}{ʟᴏᴧ} exists in few places

\textbf{\hypertarget{aptalon}{aptalon}} \textit{n.} (\hyperlink{apta}{apta}+\allowbreak \hyperlink{lon}{lon})
confined; rare

\textbf{\hypertarget{aptaki}{aptaki}} \textit{v.} (\hyperlink{apta}{apta}+\allowbreak \hyperlink{ki}{ki})
extinguish; erase; confine; recede; \hyperlink{aptakiles}{ʟєꜱ} makes ʟᴏᴧ less prevalent

\textbf{\hypertarget{aptakiles}{aptakiles}} \textit{n.} (\hyperlink{aptaki}{aptaki}+\allowbreak \hyperlink{les}{les})
extinguisher

\section{O}

\textbf{\hypertarget{'o}{'o}} \textit{n.} (ono. [o])
o; /o/; mid back rounded vowel

\textbf{\hypertarget{oye}{oye}} \textit{v.} (Spa. ⟨oye⟩ [ˈoʝe])
can hear; hear; ʟᴏᴧ hears \hyperlink{oyelum}{ʟᴜᴍ}

\textbf{\hypertarget{oyeec}{oyeec}} \textit{n.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{ec}{ec})
ear

\textbf{\hypertarget{oyeak}{oyeak}} \textit{n.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{ak}{ak})
auditory; acoustic

\textbf{\hypertarget{oyelum}{oyelum}} \textit{n.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{lum}{lum})
sound; audio

\textbf{\hypertarget{oyenu}{oyenu}} \textit{v.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{nu}{nu})
mute; ʟєꜱ makes ʟᴏᴧ stop hearing ʟᴜᴍ

\textbf{\hypertarget{oyemocaki}{oyemocaki}} \textit{v.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{mocaki}{mocaki})
sing; play music; stream; \hyperlink{oyemocakiles}{ʟєꜱ} sings or plays \hyperlink{oyemocakilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{oyemocakiles}{oyemocakiles}} \textit{n.} (\hyperlink{oyemocaki}{oyemocaki}+\allowbreak \hyperlink{les}{les})
musician

\textbf{\hypertarget{oyemocakilum}{oyemocakilum}} \textit{n.} (\hyperlink{oyemocaki}{oyemocaki}+\allowbreak \hyperlink{lum}{lum})
music; song

\textbf{\hypertarget{oyemocakilyot}{oyemocakilyot}} \textit{n.} (\hyperlink{oyemocaki}{oyemocaki}+\allowbreak \hyperlink{lyot}{lyot})
concert hall

\textbf{\hypertarget{oyecolon}{oyecolon}} \textit{n.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{colon}{colon})
onomatopoeia

\textbf{\hypertarget{oyeki}{oyeki}} \textit{v.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{ki}{ki})
listen; ʟєꜱ shows ʟᴜᴍ to ʟᴏᴧ audially

\textbf{\hypertarget{oyepowi}{oyepowi}} \textit{v.} (\hyperlink{oye}{oye}+\allowbreak \hyperlink{powi}{powi})
have hearing; ʟᴏᴧ has hearing

\textbf{\hypertarget{oyepowiluat}{oyepowiluat}} \textit{n.} (\hyperlink{oyepowi}{oyepowi}+\allowbreak \hyperlink{luat}{luat})
hearing aid

\textbf{\hypertarget{oyepowinu}{oyepowinu}} \textit{v.} (\hyperlink{oyepowi}{oyepowi}+\allowbreak \hyperlink{nu}{nu})
deafen; \hyperlink{oyepowinules}{ʟєꜱ} causes ʟᴏᴧ to become deaf

\textbf{\hypertarget{oyepowinules}{oyepowinules}} \textit{n.} (\hyperlink{oyepowinu}{oyepowinu}+\allowbreak \hyperlink{les}{les})
deafening

\textbf{\hypertarget{oyepowinyo}{oyepowinyo}} \textit{v.} (\hyperlink{oyepowi}{oyepowi}+\allowbreak \hyperlink{nyo}{nyo})
be deaf; \hyperlink{oyepowinyolon}{ʟᴏᴧ} is deaf

\textbf{\hypertarget{oyepowinyolon}{oyepowinyolon}} \textit{n.} (\hyperlink{oyepowinyo}{oyepowinyo}+\allowbreak \hyperlink{lon}{lon})
deaf

\textbf{\hypertarget{oyepowiki}{oyepowiki}} \textit{v.} (\hyperlink{oyepowi}{oyepowi}+\allowbreak \hyperlink{ki}{ki})
hearify; restore hearing; ʟєꜱ makes ʟᴏᴧ able to hear

\textbf{\hypertarget{ol}{ol}} \textit{pn.} (\hyperlink{et}{\sout{et}})
this; \textit{proximal}; associated with the time and place of the utterance

\textbf{\hypertarget{ole}{ole}} \textit{v.} (Spa. ⟨huele⟩ [ˈwele])
can smell; smell; ʟᴏᴧ smells \hyperlink{olelum}{ʟᴜᴍ}

\textbf{\hypertarget{oleec}{oleec}} \textit{n.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{ec}{ec})
olfactory gland

\textbf{\hypertarget{oleak}{oleak}} \textit{n.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{ak}{ak})
olfactory

\textbf{\hypertarget{olelih}{olelih}} \textit{n.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{lih}{lih})
skunk

\textbf{\hypertarget{olelum}{olelum}} \textit{n.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{lum}{lum})
scent; odor; aroma; smell

\textbf{\hypertarget{olenu}{olenu}} \textit{v.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{nu}{nu})
smother; suppress odor; ʟєꜱ makes ʟᴏᴧ stop smelling ʟᴜᴍ

\textbf{\hypertarget{oleki}{oleki}} \textit{v.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{ki}{ki})
waft; sniff; smell; show aromatically; ʟєꜱ makes ʟᴏᴧ start smelling ʟᴜᴍ

\textbf{\hypertarget{oletapalon}{oletapalon}} \textit{n.} (\hyperlink{ole}{ole}+\allowbreak \hyperlink{tapalon}{tapalon})
nose

\textbf{\hypertarget{ol ayf}{ol ayf}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{ayf}{ayf})
given this

\textbf{\hypertarget{olak}{olak}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{ak}{ak})
this’s

\textbf{\hypertarget{ol ial}{ol ial}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{ial}{ial})
herefore; because of this

\textbf{\hypertarget{'oliwa}{'oliwa}} \textit{n.} (Lat. ⟨oliva⟩ [ɔˈliwa])
olive; Olea europaea

\textbf{\hypertarget{ol ip}{ol ip}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{ip}{ip})
like so; hereby

\textbf{\hypertarget{ol uat}{ol uat}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{uat}{uat})
with this; like so

\textbf{\hypertarget{ol yot}{ol yot}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{yot}{yot})
here

\textbf{\hypertarget{ol wel}{ol wel}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{wel}{wel})
now

\textbf{\hypertarget{'olsotoksia}{'olsotoksia}} \textit{n.} (Ell. ⟨Ορθοδοξία⟩ [orθoðoˈksia])
Eastern Orthodoxy; Orthodox Catholicism; Greek Orthodoxy

\textbf{\hypertarget{'olsotoksiaak}{'olsotoksiaak}} \textit{n.} (\hyperlink{'olsotoksia}{'olsotoksia}+\allowbreak \hyperlink{ak}{ak})
Eastern Orthodox

\textbf{\hypertarget{olsunkwelwel}{olsunkwelwel}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
today

\textbf{\hypertarget{olto}{olto}} \textit{v.} (Epo. ⟨ordo⟩ [ˈordo])
be number; be in order; be -th; index; \hyperlink{oltolon}{ʟᴏᴧ} has a late position in \hyperlink{oltolum}{ʟᴜᴍ}

\textbf{\hypertarget{oltolon}{oltolon}} \textit{n.} (\hyperlink{olto}{olto}+\allowbreak \hyperlink{lon}{lon})
item; element; number; in order; -th

\textbf{\hypertarget{oltolum}{oltolum}} \textit{n.} (\hyperlink{olto}{olto}+\allowbreak \hyperlink{lum}{lum})
list; order; sequence; queue; line; series

\textbf{\hypertarget{oltolyan}{oltolyan}} \textit{n.} (\hyperlink{olto}{olto}+\allowbreak \hyperlink{lyan}{lyan})
position; index; number

\textbf{\hypertarget{oltolyanak}{oltolyanak}} \textit{n.} (\hyperlink{oltolyan}{oltolyan}+\allowbreak \hyperlink{ak}{ak})
ordinal

\textbf{\hypertarget{oltoki}{oltoki}} \textit{v.} (\hyperlink{olto}{olto}+\allowbreak \hyperlink{ki}{ki})
move down; position; sort; arrange; order; \hyperlink{oltokiles}{ʟєꜱ} moves ʟᴏᴧ down the sequence \hyperlink{oltokilum}{ʟᴜᴍ}

\textbf{\hypertarget{oltokiles}{oltokiles}} \textit{n.} (\hyperlink{oltoki}{oltoki}+\allowbreak \hyperlink{les}{les})
sorter

\textbf{\hypertarget{oltokilip}{oltokilip}} \textit{n.} (\hyperlink{oltoki}{oltoki}+\allowbreak \hyperlink{lip}{lip})
order

\textbf{\hypertarget{oltokilum}{oltokilum}} \textit{n.} (\hyperlink{oltoki}{oltoki}+\allowbreak \hyperlink{lum}{lum})
sorted

\textbf{\hypertarget{oltilip}{oltilip}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{tilip}{tilip})
Ulcwoliel

\textbf{\hypertarget{olpumkwelwel}{olpumkwelwel}} \textit{n.} (\hyperlink{ol}{ol}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
this year

\textbf{\hypertarget{owon}{owon}} \textit{n.} (Yor. ⟨ọwọn⟩ [ɔwɔ̃])
barnacle; copepod; Cirripedia

\textbf{\hypertarget{'owmun}{'owmun}} \textit{n.} (Yue. ⟨{\chinese{}澳門}⟩ [ōu˧muːn˧˥])
Macau; Macao

\textbf{\hypertarget{on}{on}} \textit{post.} (Epo. ⟨-on⟩ [on])
on; to; \textit{marks patient or experiencer}

\textbf{\hypertarget{ona}{ona}} \textit{v.} (Yor. ⟨ọ̀na⟩ [ɔ̀na])
stand structurally; \hyperlink{onalon}{ʟᴏᴧ} stands structurally on \hyperlink{onalum}{ʟᴜᴍ}

\textbf{\hypertarget{onalon}{onalon}} \textit{n.} (\hyperlink{ona}{ona}+\allowbreak \hyperlink{lon}{lon})
structure; building

\textbf{\hypertarget{onalum}{onalum}} \textit{n.} (\hyperlink{ona}{ona}+\allowbreak \hyperlink{lum}{lum})
foundation; site

\textbf{\hypertarget{onanu}{onanu}} \textit{v.} (\hyperlink{ona}{ona}+\allowbreak \hyperlink{nu}{nu})
deconstruct; disassemble; demolish; take apart; \hyperlink{onanules}{ʟєꜱ} deconstructs ʟᴏᴧ

\textbf{\hypertarget{onanules}{onanules}} \textit{n.} (\hyperlink{onanu}{onanu}+\allowbreak \hyperlink{les}{les})
deconstructor

\textbf{\hypertarget{onaki}{onaki}} \textit{v.} (\hyperlink{ona}{ona}+\allowbreak \hyperlink{ki}{ki})
construct; build; assemble; erect; \hyperlink{onakiles}{ʟєꜱ} constructs ʟᴏᴧ

\textbf{\hypertarget{onakiles}{onakiles}} \textit{n.} (\hyperlink{onaki}{onaki}+\allowbreak \hyperlink{les}{les})
constructor; builder

\textbf{\hypertarget{onakiluat}{onakiluat}} \textit{n.} (\hyperlink{onaki}{onaki}+\allowbreak \hyperlink{luat}{luat})
construction tool

\textbf{\hypertarget{'ontulas}{'ontulas}} \textit{n.} (Spa. ⟨Honduras⟩ [onˈduɾas])
Honduras

\textbf{\hypertarget{'ontulasak}{'ontulasak}} \textit{n.} (\hyperlink{'ontulas}{'ontulas}+\allowbreak \hyperlink{ak}{ak})
Honduran; from Honduras

\textbf{\hypertarget{'ontulaswon}{'ontulaswon}} \textit{n.} (\hyperlink{'ontulas}{'ontulas}+\allowbreak \hyperlink{won}{won})
Honduran; Catracho; the Honduran people

\textbf{\hypertarget{'omeyn}{'omeyn}} \textit{n.} (Heb. ⟨{\hebrew{}אָמֵן}⟩ [ɔˈmeɪ̯n])
amen

\textbf{\hypertarget{oso}{oso}} \textit{v.} (Ibo. ⟨ọzọ⟩ [ɒzɒ])
be more; exceed; be positive; be greater; be enough; be too much; \hyperlink{osolon}{ʟᴏᴧ} is numerically greater than \hyperlink{osolum}{ʟᴜᴍ}

\textbf{\hypertarget{osolon}{osolon}} \textit{n.} (\hyperlink{oso}{oso}+\allowbreak \hyperlink{lon}{lon})
more; positive; greater; enough; too much

\textbf{\hypertarget{osolum}{osolum}} \textit{n.} (\hyperlink{oso}{oso}+\allowbreak \hyperlink{lum}{lum})
zero; reference

\textbf{\hypertarget{osolyan}{osolyan}} \textit{n.} (\hyperlink{oso}{oso}+\allowbreak \hyperlink{lyan}{lyan})
numerical value; positiveness

\textbf{\hypertarget{osolyanak}{osolyanak}} \textit{n.} (\hyperlink{osolyan}{osolyan}+\allowbreak \hyperlink{ak}{ak})
numerical; cardinal

\textbf{\hypertarget{osoki}{osoki}} \textit{v.} (\hyperlink{oso}{oso}+\allowbreak \hyperlink{ki}{ki})
increase; multiply; spread; \hyperlink{osokiles}{ʟєꜱ} makes ʟᴏᴧ increase relative to ʟᴜᴍ

\textbf{\hypertarget{osokiles}{osokiles}} \textit{n.} (\hyperlink{osoki}{osoki}+\allowbreak \hyperlink{les}{les})
increaser

\textbf{\hypertarget{osimi}{osimi}} \textit{v.} (Ben. ⟨{\bengali{}অসীম}⟩ [os̪im])
be infinite; \hyperlink{osimilon}{ʟᴏᴧ} is infinitely so

\textbf{\hypertarget{osimilon}{osimilon}} \textit{n.} (\hyperlink{osimi}{osimi}+\allowbreak \hyperlink{lon}{lon})
infinity; infinite

\textbf{\hypertarget{osiminyo}{osiminyo}} \textit{v.} (\hyperlink{osimi}{osimi}+\allowbreak \hyperlink{nyo}{nyo})
be finite; \hyperlink{osiminyolon}{ʟᴏᴧ} is not infinitely so

\textbf{\hypertarget{osiminyouhu}{osiminyouhu}} \textit{v.} (\hyperlink{osiminyo}{osiminyo}+\allowbreak \hyperlink{uhu}{uhu})
be comatose; \hyperlink{osiminyouhulon}{ʟᴏᴧ} is in a coma

\textbf{\hypertarget{osiminyouhulon}{osiminyouhulon}} \textit{n.} (\hyperlink{osiminyouhu}{osiminyouhu}+\allowbreak \hyperlink{lon}{lon})
comatose

\textbf{\hypertarget{osiminyolon}{osiminyolon}} \textit{n.} (\hyperlink{osiminyo}{osiminyo}+\allowbreak \hyperlink{lon}{lon})
finite

\textbf{\hypertarget{osimimota}{osimimota}} \textit{v.} (\hyperlink{osimi}{osimi}+\allowbreak \hyperlink{mota}{mota})
be infinitely large; \hyperlink{osimimotalon}{ʟᴏᴧ} is infinitely large

\textbf{\hypertarget{osimimotalon}{osimimotalon}} \textit{n.} (\hyperlink{osimimota}{osimimota}+\allowbreak \hyperlink{lon}{lon})
infinitely large

\textbf{\hypertarget{osimipela}{osimipela}} \textit{v.} (\hyperlink{osimi}{osimi}+\allowbreak \hyperlink{pela}{pela})
be infinitessimal; \hyperlink{osimipelalon}{ʟᴏᴧ} is infinitessimally small

\textbf{\hypertarget{osimipelalon}{osimipelalon}} \textit{n.} (\hyperlink{osimipela}{osimipela}+\allowbreak \hyperlink{lon}{lon})
infinitessimal

\textbf{\hypertarget{'ostalayc}{'ostalayc}} \textit{n.} (Deu. ⟨Österreich⟩ [ˈøːstɐraɪç])
Austria

\textbf{\hypertarget{'ostalaycak}{'ostalaycak}} \textit{n.} (\hyperlink{'ostalayc}{'ostalayc}+\allowbreak \hyperlink{ak}{ak})
Austrian; from Austria

\textbf{\hypertarget{'ostalaycwon}{'ostalaycwon}} \textit{n.} (\hyperlink{'ostalayc}{'ostalayc}+\allowbreak \hyperlink{won}{won})
Austrian; the Austrian people

\textbf{\hypertarget{'ostwaylya}{'ostwaylya}} \textit{n.} (Eng. ⟨Australia⟩ [əˈstɹʷæɪ̯ljə])
Australia (landmass)

\textbf{\hypertarget{'ostwaylyaak}{'ostwaylyaak}} \textit{n.} (\hyperlink{'ostwaylya}{'ostwaylya}+\allowbreak \hyperlink{ak}{ak})
Australian; from Australia

\textbf{\hypertarget{'ostwaylyaoposum}{'ostwaylyaoposum}} \textit{n.} (\hyperlink{'ostwaylya}{'ostwaylya}+\allowbreak \hyperlink{oposum}{oposum})
possum; glider; cuscus

\textbf{\hypertarget{'ostwaylyawon}{'ostwaylyawon}} \textit{n.} (\hyperlink{'ostwaylya}{'ostwaylya}+\allowbreak \hyperlink{won}{won})
Australian; the Australian people

\textbf{\hypertarget{'ostwaylyatec}{'ostwaylyatec}} \textit{n.} (\hyperlink{'ostwaylya}{'ostwaylya}+\allowbreak \hyperlink{tec}{tec})
Australia; the Commonwealth of Australia

\textbf{\hypertarget{'ospek}{'ospek}} \textit{n.} (Uzb. ⟨Oʻzbek⟩ [ozbek])
Uzbek; the Uzbek people

\textbf{\hypertarget{'ospekak}{'ospekak}} \textit{n.} (\hyperlink{'ospek}{'ospek}+\allowbreak \hyperlink{ak}{ak})
Uzbek; Uzbekistani; from Uzbekistan

\textbf{\hypertarget{'ospektec}{'ospektec}} \textit{n.} (\hyperlink{'ospek}{'ospek}+\allowbreak \hyperlink{tec}{tec})
Uzbekistan

\textbf{\hypertarget{'ospektilip}{'ospektilip}} \textit{n.} (\hyperlink{'ospek}{'ospek}+\allowbreak \hyperlink{tilip}{tilip})
Uzbek; the Uzbek language

\textbf{\hypertarget{ofla}{ofla}} \textit{v.} (\hyperlink{esta}{\sout{esta}})
be opposite; be contrary; \hyperlink{oflalon}{ʟᴏᴧ} is the opposite of ʟᴜᴍ

\textbf{\hypertarget{oflalon}{oflalon}} \textit{n.} (\hyperlink{ofla}{ofla}+\allowbreak \hyperlink{lon}{lon})
opposite; contrary

\textbf{\hypertarget{oflati}{oflati}} \textit{v.} (\hyperlink{ofla}{ofla}+\allowbreak \hyperlink{ti}{ti})
be sarcastic; ʟєꜱ conveys ʟᴜᴍ sarcastically to \hyperlink{oflatilon}{ʟᴏᴧ}

\textbf{\hypertarget{oflatilon}{oflatilon}} \textit{n.} (\hyperlink{oflati}{oflati}+\allowbreak \hyperlink{lon}{lon})
sarcastic

\textbf{\hypertarget{oflo}{oflo}} \textit{v.} (\hyperlink{este}{\sout{este}})
be west; \hyperlink{oflolon}{ʟᴏᴧ} has a lower longitude than ʟᴜᴍ

\textbf{\hypertarget{oflolon}{oflolon}} \textit{n.} (\hyperlink{oflo}{oflo}+\allowbreak \hyperlink{lon}{lon})
the West; west

\textbf{\hypertarget{ofloki}{ofloki}} \textit{v.} (\hyperlink{oflo}{oflo}+\allowbreak \hyperlink{ki}{ki})
go west; ʟєꜱ decreases the longitude of ʟᴏᴧ relative to ʟᴜᴍ

\textbf{\hypertarget{ok}{ok}} \textit{spec.} (\hyperlink{en}{\sout{en}})
each; every; \textit{describes every instance of the following noun phrase individually}

\textbf{\hypertarget{oke}{oke}} \textit{v.} (Eng. ⟨okay⟩ [ˌoʊ̯ˈkʰeɪ̯])
be okay; be fine; be all right; be acceptable; \hyperlink{okelon}{ʟᴏᴧ} is okay

\textbf{\hypertarget{okelon}{okelon}} \textit{n.} (\hyperlink{oke}{oke}+\allowbreak \hyperlink{lon}{lon})
okay; fine; all right; acceptable

\textbf{\hypertarget{okenu}{okenu}} \textit{v.} (\hyperlink{oke}{oke}+\allowbreak \hyperlink{nu}{nu})
make not okay; cross the line; make unacceptable; ʟєꜱ makes ʟᴏᴧ not okay

\textbf{\hypertarget{okeki}{okeki}} \textit{v.} (\hyperlink{oke}{oke}+\allowbreak \hyperlink{ki}{ki})
make okay; make acceptable; ʟєꜱ makes ʟᴏᴧ okay

\textbf{\hypertarget{oketi}{oketi}} \textit{v.} (\hyperlink{oke}{oke}+\allowbreak \hyperlink{ti}{ti})
excuse; pardon; forgive; accept; tolerate; ʟєꜱ excuses ʟᴏᴧ

\textbf{\hypertarget{oku}{oku}} \textit{v.} (Ibo. ⟨ọkụ⟩ [ɒkʊ])
be hot; be warm; \hyperlink{okulon}{ʟᴏᴧ} is hotter than \hyperlink{okulum}{ʟᴜᴍ}

\textbf{\hypertarget{okul}{okul}} \textit{n.} (Ibo. ⟨ọ́kụ̀rụ̀⟩ [ɒ́kʊ̀ɹʊ̀])
okra; ochro; ladies’ fingers; Abelmoschus esculentus

\textbf{\hypertarget{okulon}{okulon}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{lon}{lon})
hot; warm

\textbf{\hypertarget{okulono}{okulono}} \textit{v.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{lono}{lono})
be warm-coloured; \hyperlink{okulonolon}{ʟᴏᴧ} is red, orange, yellow, or white

\textbf{\hypertarget{okulonolon}{okulonolon}} \textit{n.} (\hyperlink{okulono}{okulono}+\allowbreak \hyperlink{lon}{lon})
warm-coloured

\textbf{\hypertarget{okulum}{okulum}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{lum}{lum})
reference temperature; lukewarm

\textbf{\hypertarget{okulyan}{okulyan}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{lyan}{lyan})
temperature

\textbf{\hypertarget{okunoluat}{okunoluat}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{noluat}{noluat})
thermometer

\textbf{\hypertarget{okumihutatuniluhilasoma}{okumihutatuniluhilasoma}} \textit{v.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{mihutatu}{mihutatu}+\allowbreak \hyperlink{nilu}{nilu}+\allowbreak \hyperlink{hila}{hila}+\allowbreak \hyperlink{soma}{soma})
do thermomagnetohydrodynamics; \hyperlink{okumihutatuniluhilasomales}{ʟєꜱ} studies the heat transfer of conductive fluids in magnetic fields to learn about \hyperlink{okumihutatuniluhilasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{okumihutatuniluhilasomalon}{okumihutatuniluhilasomalon}} \textit{n.} (\hyperlink{okumihutatuniluhilasoma}{okumihutatuniluhilasoma}+\allowbreak \hyperlink{lon}{lon})
thermomagnetohydrodynamics

\textbf{\hypertarget{okumihutatuniluhilasomales}{okumihutatuniluhilasomales}} \textit{n.} (\hyperlink{okumihutatuniluhilasoma}{okumihutatuniluhilasoma}+\allowbreak \hyperlink{les}{les})
thermomagnetohydrodynamicist

\textbf{\hypertarget{okucwelon}{okucwelon}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{cwelon}{cwelon})
sweat; perspiration

\textbf{\hypertarget{okucwelonkoki}{okucwelonkoki}} \textit{v.} (\hyperlink{okucwelon}{okucwelon}+\allowbreak \hyperlink{koki}{koki})
sweat; perspire; ʟєꜱ sweats out ʟᴏᴧ

\textbf{\hypertarget{okusison}{okusison}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{sison}{sison})
summer

\textbf{\hypertarget{okuki}{okuki}} \textit{v.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{ki}{ki})
heat; warm; \hyperlink{okukiles}{ʟєꜱ} makes ʟᴏᴧ heat up relative to ʟᴜᴍ

\textbf{\hypertarget{okukiles}{okukiles}} \textit{n.} (\hyperlink{okuki}{okuki}+\allowbreak \hyperlink{les}{les})
heater

\textbf{\hypertarget{okupil}{okupil}} \textit{n.} (\hyperlink{oku}{oku}+\allowbreak \hyperlink{pil}{pil})
volcano

\textbf{\hypertarget{ot}{ot}} \textit{n.} (Mar. ⟨{\devanagari{}ओट}⟩ [oʈ])
oat; Avena

\textbf{\hypertarget{ope}{ope}} \textit{v.} (Eng. ⟨obey⟩ [oʊ̯ˈbeɪ̯])
obey; command; follow; lead; \hyperlink{opeles}{ʟєꜱ} does \hyperlink{opelon}{ʟᴏᴧ} because \hyperlink{opelum}{ʟᴜᴍ} said to do it

\textbf{\hypertarget{opeles}{opeles}} \textit{n.} (\hyperlink{ope}{ope}+\allowbreak \hyperlink{les}{les})
obedient; follower

\textbf{\hypertarget{opelon}{opelon}} \textit{n.} (\hyperlink{ope}{ope}+\allowbreak \hyperlink{lon}{lon})
order; command

\textbf{\hypertarget{opelum}{opelum}} \textit{n.} (\hyperlink{ope}{ope}+\allowbreak \hyperlink{lum}{lum})
leader; commander; manager; authority

\textbf{\hypertarget{opaka}{opaka}} \textit{v.} (Epo. ⟨opaka⟩ [oˈpaka])
be opaque; \hyperlink{opakalon}{ʟᴏᴧ} absorbs light that it does not reflect

\textbf{\hypertarget{opakalon}{opakalon}} \textit{n.} (\hyperlink{opaka}{opaka}+\allowbreak \hyperlink{lon}{lon})
opaque

\textbf{\hypertarget{opakalyan}{opakalyan}} \textit{n.} (\hyperlink{opaka}{opaka}+\allowbreak \hyperlink{lyan}{lyan})
opacity

\textbf{\hypertarget{opakaki}{opakaki}} \textit{v.} (\hyperlink{opaka}{opaka}+\allowbreak \hyperlink{ki}{ki})
opaquify; ʟєꜱ make ʟᴏᴧ become opaque

\textbf{\hypertarget{oposum}{oposum}} \textit{n.} (Fil. ⟨oposum⟩ [oposum])
opossum; Didelphimorphia

\section{I}

\textbf{\hypertarget{'i}{'i}} \textit{n.} (ono. [i])
i; /i/; close front unrounded vowel

\textbf{\hypertarget{ial}{ial}} \textit{post.} (Epo. ⟨ial⟩ [ˈial])
because; since; \textit{marks cause}

\textbf{\hypertarget{iawo}{iawo}} \textit{v.} (Yor. ⟨ìyàwó⟩ [ìjáwó])
be married; \hyperlink{iawolon}{ʟᴏᴧ} is married to \hyperlink{iawolum}{ʟᴜᴍ}

\textbf{\hypertarget{iawolon}{iawolon}} \textit{n.} (\hyperlink{iawo}{iawo}+\allowbreak \hyperlink{lon}{lon})
married

\textbf{\hypertarget{iawolum}{iawolum}} \textit{n.} (\hyperlink{iawo}{iawo}+\allowbreak \hyperlink{lum}{lum})
spouse

\textbf{\hypertarget{iawonu}{iawonu}} \textit{v.} (\hyperlink{iawo}{iawo}+\allowbreak \hyperlink{nu}{nu})
divorce; ʟєꜱ divorces ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{iawoki}{iawoki}} \textit{v.} (\hyperlink{iawo}{iawo}+\allowbreak \hyperlink{ki}{ki})
marry; wed; ʟєꜱ marries ʟᴏᴧ to ʟᴜᴍ

\textbf{\hypertarget{iawokilwel}{iawokilwel}} \textit{n.} (\hyperlink{iawoki}{iawoki}+\allowbreak \hyperlink{lwel}{lwel})
wedding

\textbf{\hypertarget{'ilawankapatay}{'ilawankapatay}} \textit{n.} (Tam. ⟨{\tamil{}இலவங்கப்பட்டை}⟩ [ilʌʋʌŋˈɡʌpːʌʈːʌj])
cinnamon; Cinnamomum

\textbf{\hypertarget{'ilan}{'ilan}} \textit{n.} (Fas. ⟨{\arabics{}ایران‎}⟩ [ʔiːɾɒːn])
Iran

\textbf{\hypertarget{'ilanak}{'ilanak}} \textit{n.} (\hyperlink{'ilan}{'ilan}+\allowbreak \hyperlink{ak}{ak})
Iranian; from Iran

\textbf{\hypertarget{'ilanwon}{'ilanwon}} \textit{n.} (\hyperlink{'ilan}{'ilan}+\allowbreak \hyperlink{won}{won})
Iranian; Persian; the Iranian people

\textbf{\hypertarget{'ilantilip}{'ilantilip}} \textit{n.} (\hyperlink{'ilan}{'ilan}+\allowbreak \hyperlink{tilip}{tilip})
Persian; Farsi; the Persian language

\textbf{\hypertarget{'ilak}{'ilak}} \textit{n.} (Ara. ⟨{\arabics{}عراق}⟩ [ʕiraːq])
Iraq

\textbf{\hypertarget{'ilakak}{'ilakak}} \textit{n.} (\hyperlink{'ilak}{'ilak}+\allowbreak \hyperlink{ak}{ak})
Iraqi; from Iraq

\textbf{\hypertarget{'ilaktilip}{'ilaktilip}} \textit{n.} (\hyperlink{'ilak}{'ilak}+\allowbreak \hyperlink{tilip}{tilip})
Iraqi; the Iraqi people

\textbf{\hypertarget{ilu}{ilu}} \textit{v.} (Ibo. ⟨iru⟩ [iɾu])
face; point; confront; \hyperlink{ilulon}{ʟᴏᴧ} is oriented in the direction toward \hyperlink{ilulum}{ʟᴜᴍ}

\textbf{\hypertarget{ilulon}{ilulon}} \textit{n.} (\hyperlink{ilu}{ilu}+\allowbreak \hyperlink{lon}{lon})
direction

\textbf{\hypertarget{ilulum}{ilulum}} \textit{n.} (\hyperlink{ilu}{ilu}+\allowbreak \hyperlink{lum}{lum})
target; front

\textbf{\hypertarget{ilunu}{ilunu}} \textit{v.} (\hyperlink{ilu}{ilu}+\allowbreak \hyperlink{nu}{nu})
turn away; avert; ʟєꜱ makes ʟᴏᴧ turn away from ʟᴜᴍ

\textbf{\hypertarget{iluki}{iluki}} \textit{v.} (\hyperlink{ilu}{ilu}+\allowbreak \hyperlink{ki}{ki})
turn; face; rotate; point; \hyperlink{ilukiles}{ʟєꜱ} makes ʟᴏᴧ turn toward ʟᴜᴍ

\textbf{\hypertarget{ilukiles}{ilukiles}} \textit{n.} (\hyperlink{iluki}{iluki}+\allowbreak \hyperlink{les}{les})
pointer; guide

\textbf{\hypertarget{ilupoltilum}{ilupoltilum}} \textit{n.} (\hyperlink{ilu}{ilu}+\allowbreak \hyperlink{poltilum}{poltilum})
mask; glasses

\textbf{\hypertarget{ina}{ina}} \textit{v.} (Yor. ⟨iná⟩ [ĩ̄á])
be charged; be electrified; \hyperlink{inalon}{ʟᴏᴧ} has electric energy stored

\textbf{\hypertarget{inaisi}{inaisi}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{isi}{isi})
conduct; be conductive; \hyperlink{inaisilon}{ʟᴏᴧ} conducts electricity

\textbf{\hypertarget{inaisilon}{inaisilon}} \textit{n.} (\hyperlink{inaisi}{inaisi}+\allowbreak \hyperlink{lon}{lon})
conductor; conductive

\textbf{\hypertarget{inaisilyan}{inaisilyan}} \textit{n.} (\hyperlink{inaisi}{inaisi}+\allowbreak \hyperlink{lyan}{lyan})
conductivity

\textbf{\hypertarget{inaufu}{inaufu}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{ufu}{ufu})
insulate; resist; be resistive; \hyperlink{inaufulon}{ʟᴏᴧ} resists electrical current

\textbf{\hypertarget{inaufulon}{inaufulon}} \textit{n.} (\hyperlink{inaufu}{inaufu}+\allowbreak \hyperlink{lon}{lon})
insulator; resistor; resistive

\textbf{\hypertarget{inaufulyan}{inaufulyan}} \textit{n.} (\hyperlink{inaufu}{inaufu}+\allowbreak \hyperlink{lyan}{lyan})
resistance

\textbf{\hypertarget{inalon}{inalon}} \textit{n.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{lon}{lon})
battery; charged; electrified

\textbf{\hypertarget{inalyan}{inalyan}} \textit{n.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{lyan}{lyan})
electric potential; voltage; electricity

\textbf{\hypertarget{inanu}{inanu}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{nu}{nu})
discharge; shock; electrify; power; ʟєꜱ releases the electric energy of ʟᴏᴧ onto \hyperlink{inanulum}{ʟᴜᴍ}

\textbf{\hypertarget{inanulip}{inanulip}} \textit{n.} (\hyperlink{inanu}{inanu}+\allowbreak \hyperlink{lip}{lip})
conduit; wire; circuit; component

\textbf{\hypertarget{inanulum}{inanulum}} \textit{n.} (\hyperlink{inanu}{inanu}+\allowbreak \hyperlink{lum}{lum})
machine; electric circuit

\textbf{\hypertarget{inacyaunyama}{inacyaunyama}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{cyau}{cyau}+\allowbreak \hyperlink{nyama}{nyama})
vape; e-smoke; ʟєꜱ vapes ʟᴏᴧ

\textbf{\hypertarget{inaki}{inaki}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{ki}{ki})
charge; electrify; \hyperlink{inakiles}{ʟєꜱ} imbues ʟᴏᴧ with electric energy

\textbf{\hypertarget{inakiles}{inakiles}} \textit{n.} (\hyperlink{inaki}{inaki}+\allowbreak \hyperlink{les}{les})
charger

\textbf{\hypertarget{inatupan}{inatupan}} \textit{n.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{tupan}{tupan})
thunderstorm

\textbf{\hypertarget{inapowi}{inapowi}} \textit{v.} (\hyperlink{ina}{ina}+\allowbreak \hyperlink{powi}{powi})
be capacitive; \hyperlink{inapowilon}{ʟᴏᴧ} is a capacitor

\textbf{\hypertarget{inapowilon}{inapowilon}} \textit{n.} (\hyperlink{inapowi}{inapowi}+\allowbreak \hyperlink{lon}{lon})
capacitor; capacitive

\textbf{\hypertarget{inapowilyan}{inapowilyan}} \textit{n.} (\hyperlink{inapowi}{inapowi}+\allowbreak \hyperlink{lyan}{lyan})
capacitance

\textbf{\hypertarget{inco}{inco}} \textit{v.} (Cmn. ⟨{\chinese{}应受}⟩ [iŋ˥ʂoʊ̯˥˩])
deserve; be entitled; \hyperlink{incolon}{ʟᴏᴧ} deserves \hyperlink{incolum}{ʟᴜᴍ}

\textbf{\hypertarget{incolon}{incolon}} \textit{n.} (\hyperlink{inco}{inco}+\allowbreak \hyperlink{lon}{lon})
worthy; deserving; entitled

\textbf{\hypertarget{incolum}{incolum}} \textit{n.} (\hyperlink{inco}{inco}+\allowbreak \hyperlink{lum}{lum})
dessert

\textbf{\hypertarget{inconu}{inconu}} \textit{v.} (\hyperlink{inco}{inco}+\allowbreak \hyperlink{nu}{nu})
lose privelage; ʟєꜱ makes ʟᴏᴧ stop deserving ʟᴜᴍ

\textbf{\hypertarget{incoki}{incoki}} \textit{v.} (\hyperlink{inco}{inco}+\allowbreak \hyperlink{ki}{ki})
earn; ʟєꜱ makes ʟᴏᴧ deserve ʟᴜᴍ

\textbf{\hypertarget{'inkil}{'inkil}} \textit{n.} (Eng. ⟨Engl-⟩ [ˈɪŋɡl])
Englishman; the English people

\textbf{\hypertarget{'inkilak}{'inkilak}} \textit{n.} (\hyperlink{'inkil}{'inkil}+\allowbreak \hyperlink{ak}{ak})
English; Anglic; from England

\textbf{\hypertarget{'inkiltec}{'inkiltec}} \textit{n.} (\hyperlink{'inkil}{'inkil}+\allowbreak \hyperlink{tec}{tec})
England

\textbf{\hypertarget{'inkiltilip}{'inkiltilip}} \textit{n.} (\hyperlink{'inkil}{'inkil}+\allowbreak \hyperlink{tilip}{tilip})
English; the English language

\textbf{\hypertarget{'intelinkwe}{'intelinkwe}} \textit{n.} (Ile. ⟨Interlingue⟩ [interlingwe])
Interlingue; Occidental

\textbf{\hypertarget{'intelinkweak}{'intelinkweak}} \textit{n.} (\hyperlink{'intelinkwe}{'intelinkwe}+\allowbreak \hyperlink{ak}{ak})
Interlingue; in Interlingue

\textbf{\hypertarget{'intelinkwewon}{'intelinkwewon}} \textit{n.} (\hyperlink{'intelinkwe}{'intelinkwe}+\allowbreak \hyperlink{won}{won})
Occidentallist; Interlingue speakers

\textbf{\hypertarget{'intelinkwa}{'intelinkwa}} \textit{n.} (Ina. ⟨Interlingua⟩ [inteɾˈliŋɡwa])
Interlingua

\textbf{\hypertarget{'intelinkwaak}{'intelinkwaak}} \textit{n.} (\hyperlink{'intelinkwa}{'intelinkwa}+\allowbreak \hyperlink{ak}{ak})
Interlingua; in Interlingua

\textbf{\hypertarget{'intelinkwawon}{'intelinkwawon}} \textit{n.} (\hyperlink{'intelinkwa}{'intelinkwa}+\allowbreak \hyperlink{won}{won})
Interlinguist; Interlingua speakers

\textbf{\hypertarget{'intanet}{'intanet}} \textit{n.} (Eng. ⟨Internet⟩ [ˈɪntɚnɛt])
The World Wide Web; The Internet; The Cloud

\textbf{\hypertarget{'intanetak}{'intanetak}} \textit{n.} (\hyperlink{'intanet}{'intanet}+\allowbreak \hyperlink{ak}{ak})
Internet; cloud; cyber

\textbf{\hypertarget{'intonesia}{'intonesia}} \textit{n.} (Ind. ⟨Indonesia⟩ [ɪndonesia])
Indonesia (archipelago)

\textbf{\hypertarget{'intonesiaak}{'intonesiaak}} \textit{n.} (\hyperlink{'intonesia}{'intonesia}+\allowbreak \hyperlink{ak}{ak})
Indonesian; from Indonesia

\textbf{\hypertarget{'intonesiawon}{'intonesiawon}} \textit{n.} (\hyperlink{'intonesia}{'intonesia}+\allowbreak \hyperlink{won}{won})
Indonesian; the Indonesian people

\textbf{\hypertarget{'intonesiatec}{'intonesiatec}} \textit{n.} (\hyperlink{'intonesia}{'intonesia}+\allowbreak \hyperlink{tec}{tec})
Indonesia; the Republic of Indonesia

\textbf{\hypertarget{'intonesiatilip}{'intonesiatilip}} \textit{n.} (\hyperlink{'intonesia}{'intonesia}+\allowbreak \hyperlink{tilip}{tilip})
Indonesian; the Indonesian language

\textbf{\hypertarget{ime}{ime}} \textit{v.} (Ibo. ⟨ime⟩ [ime])
be pregnant; be pregant; be gregnant; be pegnate; be pregegnant; be prregnant; be pergert; be pergenat; be peegnant; be pgrenant; be pregananant; \hyperlink{imelon}{ʟᴏᴧ} is pregnant

\textbf{\hypertarget{imeec}{imeec}} \textit{n.} (\hyperlink{ime}{ime}+\allowbreak \hyperlink{ec}{ec})
uterus

\textbf{\hypertarget{'imeyl}{'imeyl}} \textit{n.} (Eng. ⟨email⟩ [ˈiːmeɪ̯l])
email

\textbf{\hypertarget{imelon}{imelon}} \textit{n.} (\hyperlink{ime}{ime}+\allowbreak \hyperlink{lon}{lon})
pregnant; pregant; gregnant; pegnate; pregegnant; prregnant; pergert; pergenat; peegnant; pgrenant; pregananant

\textbf{\hypertarget{imenu}{imenu}} \textit{v.} (\hyperlink{ime}{ime}+\allowbreak \hyperlink{nu}{nu})
abort; get abortion; \hyperlink{imenules}{ʟєꜱ} gives ʟᴏᴧ an abortion

\textbf{\hypertarget{imenules}{imenules}} \textit{n.} (\hyperlink{imenu}{imenu}+\allowbreak \hyperlink{les}{les})
aborter

\textbf{\hypertarget{imeki}{imeki}} \textit{v.} (\hyperlink{ime}{ime}+\allowbreak \hyperlink{ki}{ki})
impregnate; inseminate; get pregnant; \hyperlink{imekiles}{ʟєꜱ} impregnates ʟᴏᴧ

\textbf{\hypertarget{imekiles}{imekiles}} \textit{n.} (\hyperlink{imeki}{imeki}+\allowbreak \hyperlink{les}{les})
impregnator

\textbf{\hypertarget{imal}{imal}} \textit{num.} (Eng. ⟨-imal⟩ [ɪml̩])
radix

\textbf{\hypertarget{imo}{imo}} \textit{v.} (\hyperlink{upe}{\sout{upe}})
lie; be prone; \hyperlink{imolon}{ʟᴏᴧ} is prone

\textbf{\hypertarget{imolon}{imolon}} \textit{n.} (\hyperlink{imo}{imo}+\allowbreak \hyperlink{lon}{lon})
lying down; prone

\textbf{\hypertarget{imoki}{imoki}} \textit{v.} (\hyperlink{imo}{imo}+\allowbreak \hyperlink{ki}{ki})
lie down; knock over; ʟєꜱ lays down ʟᴏᴧ

\textbf{\hypertarget{ihoha}{ihoha}} \textit{v.} (\hyperlink{uceca}{\sout{uceca}})
be normal; be ordinary; be usual; be commonplace; blend in; be average; \hyperlink{ihohalon}{ʟᴏᴧ} is expectable from its surroundings

\textbf{\hypertarget{ihohalon}{ihohalon}} \textit{n.} (\hyperlink{ihoha}{ihoha}+\allowbreak \hyperlink{lon}{lon})
layperson; civilian; normal; ordinary; usual; commonplace; average

\textbf{\hypertarget{ihohaki}{ihohaki}} \textit{v.} (\hyperlink{ihoha}{ihoha}+\allowbreak \hyperlink{ki}{ki})
conform; normalise; ʟєꜱ makes ʟᴏᴧ become normal

\textbf{\hypertarget{ihin}{ihin}} \textit{n.} (ono. [ĩː˥])
fly; housefly; gnat; midge; Muscidae

\textbf{\hypertarget{ice}{ice}} \textit{v.} (Yor. ⟨iṣẹ́⟩ [īʃɛ́])
work; work hard; be productive; be driven; \hyperlink{icelon}{ʟᴏᴧ} is working hard on \hyperlink{icelum}{ʟᴜᴍ}

\textbf{\hypertarget{icelon}{icelon}} \textit{n.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{lon}{lon})
worker; productive; driven

\textbf{\hypertarget{icelum}{icelum}} \textit{n.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{lum}{lum})
job; work

\textbf{\hypertarget{icelyan}{icelyan}} \textit{n.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{lyan}{lyan})
productivity; efficiency; work

\textbf{\hypertarget{icelyot}{icelyot}} \textit{n.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{lyot}{lyot})
workplace; workstation; office

\textbf{\hypertarget{icemai}{icemai}} \textit{v.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{mai}{mai})
employ; contract; work for; \hyperlink{icemailon}{ʟᴏᴧ} works on \hyperlink{icemailum}{ʟᴜᴍ} for \hyperlink{icemailes}{ʟєꜱ} in exchange for money

\textbf{\hypertarget{icemailes}{icemailes}} \textit{n.} (\hyperlink{icemai}{icemai}+\allowbreak \hyperlink{les}{les})
employer; boss

\textbf{\hypertarget{icemailon}{icemailon}} \textit{n.} (\hyperlink{icemai}{icemai}+\allowbreak \hyperlink{lon}{lon})
employee

\textbf{\hypertarget{icemailum}{icemailum}} \textit{n.} (\hyperlink{icemai}{icemai}+\allowbreak \hyperlink{lum}{lum})
job; work

\textbf{\hypertarget{icemailwel}{icemailwel}} \textit{n.} (\hyperlink{icemai}{icemai}+\allowbreak \hyperlink{lwel}{lwel})
employment; career

\textbf{\hypertarget{iceki}{iceki}} \textit{v.} (\hyperlink{ice}{ice}+\allowbreak \hyperlink{ki}{ki})
put to work; make productive; employ; ʟєꜱ makes ʟᴏᴧ start working on ʟᴜᴍ

\textbf{\hypertarget{ici}{ici}} \textit{v.} (Swa. ⟨-ishi⟩ [iʃi])
live; be alive; be lively; survive; reside; \hyperlink{icilon}{ʟᴏᴧ} is alive

\textbf{\hypertarget{iciestaki}{iciestaki}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{estaki}{estaki})
birth; give birth; get born; \hyperlink{iciestakiles}{ʟєꜱ} gives birth to \hyperlink{iciestakilon}{ʟᴏᴧ} by \hyperlink{iciestakilum}{ʟᴜᴍ}’s seed

\textbf{\hypertarget{iciestakiles}{iciestakiles}} \textit{n.} (\hyperlink{iciestaki}{iciestaki}+\allowbreak \hyperlink{les}{les})
biological mother

\textbf{\hypertarget{iciestakilon}{iciestakilon}} \textit{n.} (\hyperlink{iciestaki}{iciestaki}+\allowbreak \hyperlink{lon}{lon})
offspring; biological child; newborn

\textbf{\hypertarget{iciestakilum}{iciestakilum}} \textit{n.} (\hyperlink{iciestaki}{iciestaki}+\allowbreak \hyperlink{lum}{lum})
biological father

\textbf{\hypertarget{iciestakilwel}{iciestakilwel}} \textit{n.} (\hyperlink{iciestaki}{iciestaki}+\allowbreak \hyperlink{lwel}{lwel})
birth; birthdate

\textbf{\hypertarget{iciestakisunkwelwel}{iciestakisunkwelwel}} \textit{n.} (\hyperlink{iciestaki}{iciestaki}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
birthday

\textbf{\hypertarget{icilet}{icilet}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{let}{let})
ecosystem; environment

\textbf{\hypertarget{icilon}{icilon}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{lon}{lon})
life; organism; living thing; alive; lively

\textbf{\hypertarget{icilyot}{icilyot}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{lyot}{lyot})
residence

\textbf{\hypertarget{icilwel}{icilwel}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{lwel}{lwel})
life

\textbf{\hypertarget{icicalu}{icicalu}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{calu}{calu})
save; rescue; sustain; \hyperlink{icicalules}{ʟєꜱ} keeps ʟᴏᴧ from dying

\textbf{\hypertarget{icicalules}{icicalules}} \textit{n.} (\hyperlink{icicalu}{icicalu}+\allowbreak \hyperlink{les}{les})
saver; life support

\textbf{\hypertarget{icicakalum}{icicakalum}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{cakalum}{cakalum})
carbon; coal

\textbf{\hypertarget{icicwelon}{icicwelon}} \textit{n.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{cwelon}{cwelon})
water; dihydrogen monoxide

\textbf{\hypertarget{icicwelonmwonilum}{icicwelonmwonilum}} \textit{n.} (\hyperlink{icicwelon}{icicwelon}+\allowbreak \hyperlink{mwonilum}{mwonilum})
well

\textbf{\hypertarget{icisoma}{icisoma}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{soma}{soma})
do biology; \hyperlink{icisomales}{ʟєꜱ} studies lifeforms to learn about \hyperlink{icisomalon}{ʟᴏᴧ}

\textbf{\hypertarget{icisomales}{icisomales}} \textit{n.} (\hyperlink{icisoma}{icisoma}+\allowbreak \hyperlink{les}{les})
biologist

\textbf{\hypertarget{icisomalon}{icisomalon}} \textit{n.} (\hyperlink{icisoma}{icisoma}+\allowbreak \hyperlink{lon}{lon})
biology

\textbf{\hypertarget{iciki}{iciki}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{ki}{ki})
bring to life; come to life; ʟєꜱ brings ʟᴏᴧ to life

\textbf{\hypertarget{icitutumu}{icitutumu}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{tutumu}{tutumu})
heartbeat; have pulse; ʟᴏᴧ has a heartbeat

\textbf{\hypertarget{icitutumulyan}{icitutumulyan}} \textit{n.} (\hyperlink{icitutumu}{icitutumu}+\allowbreak \hyperlink{lyan}{lyan})
heartrate

\textbf{\hypertarget{icipeta}{icipeta}} \textit{v.} (\hyperlink{ici}{ici}+\allowbreak \hyperlink{peta}{peta})
be undead; \hyperlink{icipetalon}{ʟᴏᴧ} is undead

\textbf{\hypertarget{icipetalon}{icipetalon}} \textit{n.} (\hyperlink{icipeta}{icipeta}+\allowbreak \hyperlink{lon}{lon})
undead

\textbf{\hypertarget{icipetalwel}{icipetalwel}} \textit{n.} (\hyperlink{icipeta}{icipeta}+\allowbreak \hyperlink{lwel}{lwel})
afterlife

\textbf{\hypertarget{'ickip}{'ickip}} \textit{n.} (Alb. ⟨Shqip⟩ [ʃcip])
Albanian; the Albanian people

\textbf{\hypertarget{'ickipak}{'ickipak}} \textit{n.} (\hyperlink{'ickip}{'ickip}+\allowbreak \hyperlink{ak}{ak})
Albanian; from Albania

\textbf{\hypertarget{'ickiptec}{'ickiptec}} \textit{n.} (\hyperlink{'ickip}{'ickip}+\allowbreak \hyperlink{tec}{tec})
Albania

\textbf{\hypertarget{'ickiptilip}{'ickiptilip}} \textit{n.} (\hyperlink{'ickip}{'ickip}+\allowbreak \hyperlink{tilip}{tilip})
Albanian; the Albanian language

\textbf{\hypertarget{ise}{ise}} \textit{v.} (Yor. ⟨isẹ⟩ [isɛ])
function; work; go; ʟᴏᴧ does what it is supposed to do

\textbf{\hypertarget{isepowi}{isepowi}} \textit{v.} (\hyperlink{ise}{ise}+\allowbreak \hyperlink{powi}{powi})
be functional; be effective; work; \hyperlink{isepowilon}{ʟᴏᴧ} works

\textbf{\hypertarget{isepowilon}{isepowilon}} \textit{n.} (\hyperlink{isepowi}{isepowi}+\allowbreak \hyperlink{lon}{lon})
functional; effective

\textbf{\hypertarget{isepowinyo}{isepowinyo}} \textit{v.} (\hyperlink{isepowi}{isepowi}+\allowbreak \hyperlink{nyo}{nyo})
be nonfunctional; be broken; be incapacitated; \hyperlink{isepowinyolon}{ʟᴏᴧ} does not work

\textbf{\hypertarget{isepowinyolon}{isepowinyolon}} \textit{n.} (\hyperlink{isepowinyo}{isepowinyo}+\allowbreak \hyperlink{lon}{lon})
nonfunctional; broken; incapacitated

\textbf{\hypertarget{isa}{isa}} \textit{v.} (\hyperlink{ufa}{\sout{ufa}})
be chunky; be coarse; be granulated; be piled; be in bits; \hyperlink{isalon}{ʟᴏᴧ} is a loose aggregation of fragments of ʟᴜᴍ

\textbf{\hypertarget{isalon}{isalon}} \textit{n.} (\hyperlink{isa}{isa}+\allowbreak \hyperlink{lon}{lon})
chunky; coarse; granulated; piled; in bits

\textbf{\hypertarget{isaseleal}{isaseleal}} \textit{n.} (\hyperlink{isa}{isa}+\allowbreak \hyperlink{seleal}{seleal})
cereal; breakfast cereal

\textbf{\hypertarget{isaki}{isaki}} \textit{v.} (\hyperlink{isa}{isa}+\allowbreak \hyperlink{ki}{ki})
chunk; grind; pile; \hyperlink{isakiles}{ʟєꜱ} turns ʟᴏᴧ into a pile of chunky bits

\textbf{\hypertarget{isakiles}{isakiles}} \textit{n.} (\hyperlink{isaki}{isaki}+\allowbreak \hyperlink{les}{les})
chunker

\textbf{\hypertarget{isi}{isi}} \textit{v.} (Eng. ⟨easy⟩ [ˈiːzi])
be easy; be convenient; \hyperlink{isilum}{ʟᴜᴍ} is easy to ʟᴏᴧ

\textbf{\hypertarget{isilum}{isilum}} \textit{n.} (\hyperlink{isi}{isi}+\allowbreak \hyperlink{lum}{lum})
easy; convenient

\textbf{\hypertarget{isiki}{isiki}} \textit{v.} (\hyperlink{isi}{isi}+\allowbreak \hyperlink{ki}{ki})
facilitate; convenience; make easy; ʟєꜱ makes ʟᴜᴍ easier for ʟᴏᴧ

\textbf{\hypertarget{'islan}{'islan}} \textit{n.} (Isl. ⟨Ísland⟩ [ˈistlant])
Iceland (landmass)

\textbf{\hypertarget{'islanak}{'islanak}} \textit{n.} (\hyperlink{'islan}{'islan}+\allowbreak \hyperlink{ak}{ak})
Icelandic; from Iceland

\textbf{\hypertarget{'islanwon}{'islanwon}} \textit{n.} (\hyperlink{'islan}{'islan}+\allowbreak \hyperlink{won}{won})
Icelander; the Icelandic people

\textbf{\hypertarget{'islantec}{'islantec}} \textit{n.} (\hyperlink{'islan}{'islan}+\allowbreak \hyperlink{tec}{tec})
Iceland (country)

\textbf{\hypertarget{'islantilip}{'islantilip}} \textit{n.} (\hyperlink{'islan}{'islan}+\allowbreak \hyperlink{tilip}{tilip})
Icelandic; the Icelandic language

\textbf{\hypertarget{'islam}{'islam}} \textit{n.} (Ara. ⟨{\arabics{}إسلام}⟩ [ʔɪsˈlaːm])
Islam; Muhammadanism

\textbf{\hypertarget{'islamak}{'islamak}} \textit{n.} (\hyperlink{'islam}{'islam}+\allowbreak \hyperlink{ak}{ak})
Islamic

\textbf{\hypertarget{'islamwon}{'islamwon}} \textit{n.} (\hyperlink{'islam}{'islam}+\allowbreak \hyperlink{won}{won})
Muslim; followers of Islam

\textbf{\hypertarget{'istanpul}{'istanpul}} \textit{n.} (Tur. ⟨İstanbul⟩ [isˈtanbuɫ])
Istanbul

\textbf{\hypertarget{ifen}{ifen}} \textit{spec.} (Eng. ⟨even⟩ [ˈiːvn̩])
even; so; too; neither; \textit{emphasises something surprising}

\textbf{\hypertarget{ifenaw}{ifenaw}} \textit{spec.} (\hyperlink{ifen}{ifen}+\allowbreak \hyperlink{aw}{aw})
but; and even

\textbf{\hypertarget{ifenyo}{ifenyo}} \textit{spec.} (\hyperlink{ifen}{ifen}+\allowbreak \hyperlink{yo}{yo})
despite; though

\textbf{\hypertarget{ikci}{ikci}} \textit{v.} (\hyperlink{unhu}{\sout{unhu}})
be evil; be immoral; be wrong; be bad; if \hyperlink{ikcilon}{ʟᴏᴧ} happens, it will be morally bad

\textbf{\hypertarget{ikcilon}{ikcilon}} \textit{n.} (\hyperlink{ikci}{ikci}+\allowbreak \hyperlink{lon}{lon})
evil; sin; immoral; wrong; bad

\textbf{\hypertarget{ikcinati}{ikcinati}} \textit{v.} (\hyperlink{ikci}{ikci}+\allowbreak \hyperlink{nati}{nati})
tempt; entice to something appealing but immoral; \hyperlink{ikcinatiles}{ʟєꜱ} encourages \hyperlink{ikcinatilum}{ʟᴜᴍ} to do \hyperlink{ikcinatilon}{ʟᴏᴧ}

\textbf{\hypertarget{ikcinatiles}{ikcinatiles}} \textit{n.} (\hyperlink{ikcinati}{ikcinati}+\allowbreak \hyperlink{les}{les})
tempter; temptress

\textbf{\hypertarget{ikcinatilon}{ikcinatilon}} \textit{n.} (\hyperlink{ikcinati}{ikcinati}+\allowbreak \hyperlink{lon}{lon})
temptation

\textbf{\hypertarget{ikcinatilum}{ikcinatilum}} \textit{n.} (\hyperlink{ikcinati}{ikcinati}+\allowbreak \hyperlink{lum}{lum})
temptee

\textbf{\hypertarget{ikciki}{ikciki}} \textit{v.} (\hyperlink{ikci}{ikci}+\allowbreak \hyperlink{ki}{ki})
wrong; turn evil; ʟєꜱ makes ʟᴏᴧ become evil

\textbf{\hypertarget{'ikpo}{'ikpo}} \textit{n.} (Ibo. ⟨Ị̀gbò⟩ [ìɡ͡bò])
Igbo; the Igbo people

\textbf{\hypertarget{'ikpoak}{'ikpoak}} \textit{n.} (\hyperlink{'ikpo}{'ikpo}+\allowbreak \hyperlink{ak}{ak})
Igbo; in Igbo

\textbf{\hypertarget{'ikpotilip}{'ikpotilip}} \textit{n.} (\hyperlink{'ikpo}{'ikpo}+\allowbreak \hyperlink{tilip}{tilip})
Igbo; the Igbo language

\textbf{\hypertarget{itea}{itea}} \textit{v.} (Spa. ⟨idea⟩ [iˈðea])
think of; come up with; invent; have an idea; \hyperlink{iteales}{ʟєꜱ} thinks of \hyperlink{itealon}{ʟᴏᴧ}

\textbf{\hypertarget{iteales}{iteales}} \textit{n.} (\hyperlink{itea}{itea}+\allowbreak \hyperlink{les}{les})
creative; clever; idea person

\textbf{\hypertarget{itealon}{itealon}} \textit{n.} (\hyperlink{itea}{itea}+\allowbreak \hyperlink{lon}{lon})
idea; thought; invention

\textbf{\hypertarget{itealial}{itealial}} \textit{n.} (\hyperlink{itea}{itea}+\allowbreak \hyperlink{lial}{lial})
inspiration

\textbf{\hypertarget{'italya}{'italya}} \textit{n.} (Ita. ⟨Italia⟩ [itaːlja])
Italy

\textbf{\hypertarget{'italyaak}{'italyaak}} \textit{n.} (\hyperlink{'italya}{'italya}+\allowbreak \hyperlink{ak}{ak})
Italian; Italic; from Italy

\textbf{\hypertarget{'italyawon}{'italyawon}} \textit{n.} (\hyperlink{'italya}{'italya}+\allowbreak \hyperlink{won}{won})
Italian; the Italian people

\textbf{\hypertarget{'italyatilip}{'italyatilip}} \textit{n.} (\hyperlink{'italya}{'italya}+\allowbreak \hyperlink{tilip}{tilip})
Italian; the Italian language

\textbf{\hypertarget{'ito}{'ito}} \textit{n.} (Ido. ⟨Ido⟩ [ˈido])
Ido

\textbf{\hypertarget{'itoak}{'itoak}} \textit{n.} (\hyperlink{'ito}{'ito}+\allowbreak \hyperlink{ak}{ak})
Ido; Idist; Ida

\textbf{\hypertarget{'itowon}{'itowon}} \textit{n.} (\hyperlink{'ito}{'ito}+\allowbreak \hyperlink{won}{won})
Idist; Ido speakers

\textbf{\hypertarget{iti}{iti}} \textit{v.} (Yor. ⟨ìdí⟩ [ìdí])
deduce; compute; reason; be reasonable; be logical; figure; figure out; think through; \hyperlink{itiles}{ʟєꜱ} logically deduces \hyperlink{itilon}{ʟᴏᴧ}

\textbf{\hypertarget{itiles}{itiles}} \textit{n.} (\hyperlink{iti}{iti}+\allowbreak \hyperlink{les}{les})
reasonable

\textbf{\hypertarget{itilon}{itilon}} \textit{n.} (\hyperlink{iti}{iti}+\allowbreak \hyperlink{lon}{lon})
conclusion; computation; reasonable; logical

\textbf{\hypertarget{'ityopya}{'ityopya}} \textit{n.} (Amh. ⟨{\ethiopic{}ኢትዮጵያ}⟩ [ʔɨtjoppʼja])
Ethiopia

\textbf{\hypertarget{'ityopyaak}{'ityopyaak}} \textit{n.} (\hyperlink{'ityopya}{'ityopya}+\allowbreak \hyperlink{ak}{ak})
Ethiopian; from Ethiopia

\textbf{\hypertarget{'ityopyawon}{'ityopyawon}} \textit{n.} (\hyperlink{'ityopya}{'ityopya}+\allowbreak \hyperlink{won}{won})
Ethiopian; the Ethiopian people

\textbf{\hypertarget{ip}{ip}} \textit{post.} (∅)
by; as; via; \textit{marks method or manner}

\textbf{\hypertarget{ipa}{ipa}} \textit{v.} (Yor. ⟨ìbá⟩ [ìbá])
should; be fit; be good; be proper; be correct; \hyperlink{ipalon}{ʟᴏᴧ} should happen to make \hyperlink{ipalum}{ʟᴜᴍ} happen

\textbf{\hypertarget{ipalon}{ipalon}} \textit{n.} (\hyperlink{ipa}{ipa}+\allowbreak \hyperlink{lon}{lon})
fit; good; proper; correct

\textbf{\hypertarget{ipalum}{ipalum}} \textit{n.} (\hyperlink{ipa}{ipa}+\allowbreak \hyperlink{lum}{lum})
value function; goal

\textbf{\hypertarget{ipati}{ipati}} \textit{v.} (\hyperlink{ipa}{ipa}+\allowbreak \hyperlink{ti}{ti})
suggest; advise; recommend; \hyperlink{ipatiles}{ʟєꜱ} suggests that \hyperlink{ipatilon}{ʟᴏᴧ} do \hyperlink{ipatilum}{ʟᴜᴍ}

\textbf{\hypertarget{ipatiles}{ipatiles}} \textit{n.} (\hyperlink{ipati}{ipati}+\allowbreak \hyperlink{les}{les})
advisor; recommender

\textbf{\hypertarget{ipatilon}{ipatilon}} \textit{n.} (\hyperlink{ipati}{ipati}+\allowbreak \hyperlink{lon}{lon})
advisee

\textbf{\hypertarget{ipatilum}{ipatilum}} \textit{n.} (\hyperlink{ipati}{ipati}+\allowbreak \hyperlink{lum}{lum})
suggestion; advice; recommendation

\textbf{\hypertarget{ipis}{ipis}} \textit{n.} (Fil. ⟨ipis⟩ [ipis])
cockroach; roach; termite; Blattodea

\section{U}

\textbf{\hypertarget{'u}{'u}} \textit{n.} (ono. [u])
u; /u/; close back rounded vowel

\textbf{\hypertarget{uat}{uat}} \textit{post.} (\hyperlink{ial}{\sout{ial}})
by; with; through; \textit{marks instrument}

\textbf{\hypertarget{ul}{ul}} \textit{n.} (Jav. ⟨wulu⟩ [wuɭu])
feather; plumage; rigid organic extension of a bird or dinosaur lined with hairs

\textbf{\hypertarget{ulak}{ulak}} \textit{n.} (\hyperlink{ul}{ul}+\allowbreak \hyperlink{ak}{ak})
plumal; feathery; feathered

\textbf{\hypertarget{ulu}{ulu}} \textit{v.} (\hyperlink{iti}{\sout{iti}})
act crazy; be unreasonable; be illogical; jump to conclusion; guess; \hyperlink{ulules}{ʟєꜱ} comes to the conclusion \hyperlink{ululon}{ʟᴏᴧ} without any logic

\textbf{\hypertarget{ulules}{ulules}} \textit{n.} (\hyperlink{ulu}{ulu}+\allowbreak \hyperlink{les}{les})
unreasonable; crazy

\textbf{\hypertarget{ululon}{ululon}} \textit{n.} (\hyperlink{ulu}{ulu}+\allowbreak \hyperlink{lon}{lon})
unreasonable; illogical

\textbf{\hypertarget{'ulukway}{'ulukway}} \textit{n.} (Spa. ⟨Uruguay⟩ [uɾuˈɣaj])
Uruguay

\textbf{\hypertarget{'ulukwayak}{'ulukwayak}} \textit{n.} (\hyperlink{'ulukway}{'ulukway}+\allowbreak \hyperlink{ak}{ak})
Uruguayan; from Uruguay

\textbf{\hypertarget{'ulukwaywon}{'ulukwaywon}} \textit{n.} (\hyperlink{'ulukway}{'ulukway}+\allowbreak \hyperlink{won}{won})
Uruguayan; the Uruguayan people

\textbf{\hypertarget{'ulkwanta}{'ulkwanta}} \textit{n.} (Kin. ⟨Rwanda⟩ [ɾɡwanda])
Rwanda

\textbf{\hypertarget{'ulkwantaak}{'ulkwantaak}} \textit{n.} (\hyperlink{'ulkwanta}{'ulkwanta}+\allowbreak \hyperlink{ak}{ak})
Rwandan; Rwandese; from Rwanda

\textbf{\hypertarget{'ulkwantawon}{'ulkwantawon}} \textit{n.} (\hyperlink{'ulkwanta}{'ulkwanta}+\allowbreak \hyperlink{won}{won})
Rwandan; the Rwandan people

\textbf{\hypertarget{'ulkwantatilip}{'ulkwantatilip}} \textit{n.} (\hyperlink{'ulkwanta}{'ulkwanta}+\allowbreak \hyperlink{tilip}{tilip})
Kinyarwanda; Urufumbira; the Kinyarwanda language

\textbf{\hypertarget{'ultun}{'ultun}} \textit{n.} (Ara. ⟨{\arabics{}ْأردن}⟩ [ʔurdunn])
Jordan river

\textbf{\hypertarget{'ultunak}{'ultunak}} \textit{n.} (\hyperlink{'ultun}{'ultun}+\allowbreak \hyperlink{ak}{ak})
Jordanian; from Jordan

\textbf{\hypertarget{'ultunwon}{'ultunwon}} \textit{n.} (\hyperlink{'ultun}{'ultun}+\allowbreak \hyperlink{won}{won})
Jordanian; the Jordanian people

\textbf{\hypertarget{'ultuntec}{'ultuntec}} \textit{n.} (\hyperlink{'ultun}{'ultun}+\allowbreak \hyperlink{tec}{tec})
Jordan; the Hashemite Kingdom of Jordan

\textbf{\hypertarget{unhu}{unhu}} \textit{v.} (Sho. ⟨unhu⟩ [unhu])
be moral; be right; be virtuous; be good; if \hyperlink{unhulon}{ʟᴏᴧ} happens, it will be morally good

\textbf{\hypertarget{unhulon}{unhulon}} \textit{n.} (\hyperlink{unhu}{unhu}+\allowbreak \hyperlink{lon}{lon})
good deed; moral; right; virtuous; good

\textbf{\hypertarget{unhulyan}{unhulyan}} \textit{n.} (\hyperlink{unhu}{unhu}+\allowbreak \hyperlink{lyan}{lyan})
morality; goodness

\textbf{\hypertarget{unhuki}{unhuki}} \textit{v.} (\hyperlink{unhu}{unhu}+\allowbreak \hyperlink{ki}{ki})
rectify; turn good; ʟєꜱ makes ʟᴏᴧ become moral

\textbf{\hypertarget{um}{um}} \textit{post.} (Pan. ⟨{\gurmukhi{}ਨੂੰ}⟩ [nũː])
to; by; \textit{marks theme, stimulus, or recipient}

\textbf{\hypertarget{uma}{uma}} \textit{v.} (\hyperlink{ipa}{\sout{ipa}})
should not; be bad; be unwise; be incorrect; \hyperlink{umalon}{ʟᴏᴧ} should not happen to make ʟᴜᴍ happen

\textbf{\hypertarget{umalon}{umalon}} \textit{n.} (\hyperlink{uma}{uma}+\allowbreak \hyperlink{lon}{lon})
problem; bad; unwise; incorrect

\textbf{\hypertarget{'uman}{'uman}} \textit{n.} (Ara. ⟨{\arabics{}عمان‎}⟩ [ʕʊˈmaːn])
Oman

\textbf{\hypertarget{'umanak}{'umanak}} \textit{n.} (\hyperlink{'uman}{'uman}+\allowbreak \hyperlink{ak}{ak})
Omani; from Oman

\textbf{\hypertarget{'umanwon}{'umanwon}} \textit{n.} (\hyperlink{'uman}{'uman}+\allowbreak \hyperlink{won}{won})
Omani; the Omani people

\textbf{\hypertarget{uho}{uho}} \textit{v.} (\hyperlink{ice}{\sout{ice}})
be unproductive; be lazy; \hyperlink{uholon}{ʟᴏᴧ} is working little on \hyperlink{uholum}{ʟᴜᴍ}

\textbf{\hypertarget{uholon}{uholon}} \textit{n.} (\hyperlink{uho}{uho}+\allowbreak \hyperlink{lon}{lon})
unproductive; lazy

\textbf{\hypertarget{uholum}{uholum}} \textit{n.} (\hyperlink{uho}{uho}+\allowbreak \hyperlink{lum}{lum})
neglected

\textbf{\hypertarget{uhoki}{uhoki}} \textit{v.} (\hyperlink{uho}{uho}+\allowbreak \hyperlink{ki}{ki})
retire; give up; make unproductive; fire; ʟєꜱ makes ʟᴏᴧ become unproductive at ʟᴜᴍ

\textbf{\hypertarget{uhu}{uhu}} \textit{v.} (\hyperlink{ici}{\sout{ici}})
be dead; \hyperlink{uhulon}{ʟᴏᴧ} is dead

\textbf{\hypertarget{uhulon}{uhulon}} \textit{n.} (\hyperlink{uhu}{uhu}+\allowbreak \hyperlink{lon}{lon})
corpse; dead thing; dead

\textbf{\hypertarget{uhulwel}{uhulwel}} \textit{n.} (\hyperlink{uhu}{uhu}+\allowbreak \hyperlink{lwel}{lwel})
death

\textbf{\hypertarget{uhuki}{uhuki}} \textit{v.} (\hyperlink{uhu}{uhu}+\allowbreak \hyperlink{ki}{ki})
kill; murder; die; pass away; \hyperlink{uhukiles}{ʟєꜱ} kills ʟᴏᴧ

\textbf{\hypertarget{uhukiles}{uhukiles}} \textit{n.} (\hyperlink{uhuki}{uhuki}+\allowbreak \hyperlink{les}{les})
killer; murderer

\textbf{\hypertarget{uhutunmailyot}{uhutunmailyot}} \textit{n.} (\hyperlink{uhu}{uhu}+\allowbreak \hyperlink{tun}{tun}+\allowbreak \hyperlink{mailyot}{mailyot})
butchery

\textbf{\hypertarget{uceca}{uceca}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਉਚੇਚਾ}⟩ [ʊt͡ʃet͡ʃɑ])
be special; be unique; be weird; be rare; stand out; be especial; \hyperlink{ucecalon}{ʟᴏᴧ} is distinguished from those around it

\textbf{\hypertarget{ucecalon}{ucecalon}} \textit{n.} (\hyperlink{uceca}{uceca}+\allowbreak \hyperlink{lon}{lon})
specialist; personnel; outlier; special; unique; weird; rare; especial

\textbf{\hypertarget{ucecaki}{ucecaki}} \textit{v.} (\hyperlink{uceca}{uceca}+\allowbreak \hyperlink{ki}{ki})
specialise; customise; ʟєꜱ makes ʟᴏᴧ specially

\textbf{\hypertarget{ufa}{ufa}} \textit{v.} (Nya. ⟨ufa⟩ [ufa])
be powder; be fine; be dust; \hyperlink{ufalon}{ʟᴏᴧ} is a powder

\textbf{\hypertarget{ufalon}{ufalon}} \textit{n.} (\hyperlink{ufa}{ufa}+\allowbreak \hyperlink{lon}{lon})
powder; fine; dust

\textbf{\hypertarget{ufalonsapu}{ufalonsapu}} \textit{v.} (\hyperlink{ufalon}{ufalon}+\allowbreak \hyperlink{sapu}{sapu})
sand; \hyperlink{ufalonsapules}{ʟєꜱ} sands \hyperlink{ufalonsapulon}{ʟᴏᴧ}

\textbf{\hypertarget{ufalonsapules}{ufalonsapules}} \textit{n.} (\hyperlink{ufalonsapu}{ufalonsapu}+\allowbreak \hyperlink{les}{les})
sander

\textbf{\hypertarget{ufalonsapulon}{ufalonsapulon}} \textit{n.} (\hyperlink{ufalonsapu}{ufalonsapu}+\allowbreak \hyperlink{lon}{lon})
sanded

\textbf{\hypertarget{ufaseleal}{ufaseleal}} \textit{n.} (\hyperlink{ufa}{ufa}+\allowbreak \hyperlink{seleal}{seleal})
flour

\textbf{\hypertarget{ufaki}{ufaki}} \textit{v.} (\hyperlink{ufa}{ufa}+\allowbreak \hyperlink{ki}{ki})
pulverise; powder; \hyperlink{ufakiles}{ʟєꜱ} turns ʟᴏᴧ into a powder

\textbf{\hypertarget{ufakiles}{ufakiles}} \textit{n.} (\hyperlink{ufaki}{ufaki}+\allowbreak \hyperlink{les}{les})
pulveriser

\textbf{\hypertarget{ufataka}{ufataka}} \textit{v.} (\hyperlink{ufa}{ufa}+\allowbreak \hyperlink{taka}{taka})
be dusty; ʟᴜᴍ is covered in \hyperlink{ufatakalon}{ʟᴏᴧ} dust

\textbf{\hypertarget{ufatakalon}{ufatakalon}} \textit{n.} (\hyperlink{ufataka}{ufataka}+\allowbreak \hyperlink{lon}{lon})
dusty

\textbf{\hypertarget{ufatakanu}{ufatakanu}} \textit{v.} (\hyperlink{ufataka}{ufataka}+\allowbreak \hyperlink{nu}{nu})
undust; dust; ʟєꜱ removes the ʟᴏᴧ dust from ʟᴜᴍ

\textbf{\hypertarget{ufatakanuluat}{ufatakanuluat}} \textit{n.} (\hyperlink{ufatakanu}{ufatakanu}+\allowbreak \hyperlink{luat}{luat})
duster

\textbf{\hypertarget{ufatakaki}{ufatakaki}} \textit{v.} (\hyperlink{ufataka}{ufataka}+\allowbreak \hyperlink{ki}{ki})
dust; ʟєꜱ covers ʟᴜᴍ in ʟᴏᴧ dust

\textbf{\hypertarget{ufapiac}{ufapiac}} \textit{n.} (\hyperlink{ufa}{ufa}+\allowbreak \hyperlink{piac}{piac})
garlic; Allium sativum

\textbf{\hypertarget{ufu}{ufu}} \textit{v.} (\hyperlink{isi}{\sout{isi}})
be difficult; be hard; be inconvenient; \hyperlink{ufulum}{ʟᴜᴍ} is hard for ʟᴏᴧ

\textbf{\hypertarget{ufulum}{ufulum}} \textit{n.} (\hyperlink{ufu}{ufu}+\allowbreak \hyperlink{lum}{lum})
difficult; hard; inconvenient

\textbf{\hypertarget{ufuki}{ufuki}} \textit{v.} (\hyperlink{ufu}{ufu}+\allowbreak \hyperlink{ki}{ki})
restrict; resist; inconvenience; make difficult; ʟєꜱ makes ʟᴜᴍ harder for ʟᴏᴧ

\textbf{\hypertarget{ukik}{ukik}} \textit{n.} (ono. [u ki ki])
primate; monkey; ape; Primates

\textbf{\hypertarget{ukikak}{ukikak}} \textit{n.} (\hyperlink{ukik}{ukik}+\allowbreak \hyperlink{ak}{ak})
simian

\textbf{\hypertarget{ukikcim}{ukikcim}} \textit{n.} (\hyperlink{ukik}{ukik}+\allowbreak \hyperlink{cim}{cim})
peanut; groundnut; goober

\textbf{\hypertarget{'ukulele}{'ukulele}} \textit{n.} (Haw. ⟨ʻukulele⟩ [ˈʔukuˈlɛlɛ])
ukulele

\textbf{\hypertarget{'uklayina}{'uklayina}} \textit{n.} (Ukr. ⟨Україна⟩ [ukrɑˈjinɑ])
Ukraine; the Ukraine

\textbf{\hypertarget{'uklayinaak}{'uklayinaak}} \textit{n.} (\hyperlink{'uklayina}{'uklayina}+\allowbreak \hyperlink{ak}{ak})
Ukranian; from Ukraine

\textbf{\hypertarget{'uklayinawon}{'uklayinawon}} \textit{n.} (\hyperlink{'uklayina}{'uklayina}+\allowbreak \hyperlink{won}{won})
Ukrainian; the Ukranian people

\textbf{\hypertarget{'uklayinatilip}{'uklayinatilip}} \textit{n.} (\hyperlink{'uklayina}{'uklayina}+\allowbreak \hyperlink{tilip}{tilip})
Ukrainian; the Ukrainian language

\textbf{\hypertarget{ut}{ut}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਊਠ}⟩ [uʈʰ])
camelid; camel; llama; alpaca; guanaco; Camelidae

\textbf{\hypertarget{uto}{uto}} \textit{v.} (Ibo. ⟨uto⟩ [uto])
can taste; taste; ʟᴏᴧ tastes \hyperlink{utolum}{ʟᴜᴍ}

\textbf{\hypertarget{utoec}{utoec}} \textit{n.} (\hyperlink{uto}{uto}+\allowbreak \hyperlink{ec}{ec})
tongue

\textbf{\hypertarget{utoecsapu}{utoecsapu}} \textit{v.} (\hyperlink{utoec}{utoec}+\allowbreak \hyperlink{sapu}{sapu})
lick; \hyperlink{utoecsapules}{ʟєꜱ} licks \hyperlink{utoecsapulon}{ʟᴏᴧ}

\textbf{\hypertarget{utoecsapules}{utoecsapules}} \textit{n.} (\hyperlink{utoecsapu}{utoecsapu}+\allowbreak \hyperlink{les}{les})
licker

\textbf{\hypertarget{utoecsapulon}{utoecsapulon}} \textit{n.} (\hyperlink{utoecsapu}{utoecsapu}+\allowbreak \hyperlink{lon}{lon})
licked

\textbf{\hypertarget{utoak}{utoak}} \textit{n.} (\hyperlink{uto}{uto}+\allowbreak \hyperlink{ak}{ak})
gustatory

\textbf{\hypertarget{utolum}{utolum}} \textit{n.} (\hyperlink{uto}{uto}+\allowbreak \hyperlink{lum}{lum})
taste; flavour

\textbf{\hypertarget{utonu}{utonu}} \textit{v.} (\hyperlink{uto}{uto}+\allowbreak \hyperlink{nu}{nu})
obscure taste; ʟєꜱ makes ʟᴏᴧ stop tasting ʟᴜᴍ

\textbf{\hypertarget{utoki}{utoki}} \textit{v.} (\hyperlink{uto}{uto}+\allowbreak \hyperlink{ki}{ki})
sample; show taste; ʟєꜱ makes ʟᴏᴧ start tasting ʟᴜᴍ

\textbf{\hypertarget{upe}{upe}} \textit{v.} (Mar. ⟨{\devanagari{}उभे}⟩ [ub̤e])
stand; be erect; \hyperlink{upelon}{ʟᴏᴧ} is standing

\textbf{\hypertarget{up}{up}} \textit{n.} (Ibo. ⟨uba⟩ [uba])
flea; Siphonaptera

\textbf{\hypertarget{upelon}{upelon}} \textit{n.} (\hyperlink{upe}{upe}+\allowbreak \hyperlink{lon}{lon})
standing; erect

\textbf{\hypertarget{upelip}{upelip}} \textit{n.} (\hyperlink{upe}{upe}+\allowbreak \hyperlink{lip}{lip})
posture

\textbf{\hypertarget{upeki}{upeki}} \textit{v.} (\hyperlink{upe}{upe}+\allowbreak \hyperlink{ki}{ki})
stand up; erect; \hyperlink{upekiles}{ʟєꜱ} stands up ʟᴏᴧ

\textbf{\hypertarget{upekiles}{upekiles}} \textit{n.} (\hyperlink{upeki}{upeki}+\allowbreak \hyperlink{les}{les})
stand

\section{Y}

\textbf{\hypertarget{'yelucalayim}{'yelucalayim}} \textit{n.} (Heb. ⟨{\hebrew{}יְרוּשָׁלַיִם}⟩ [jeʁuʃaˈlajim])
Jerusalem

\textbf{\hypertarget{'yewlasia}{'yewlasia}} \textit{n.} (Rus. ⟨Евразия⟩ [jɪˈvrazʲɪjə])
Eurasia

\textbf{\hypertarget{'yewlasiaak}{'yewlasiaak}} \textit{n.} (\hyperlink{'yewlasia}{'yewlasia}+\allowbreak \hyperlink{ak}{ak})
Eurasian; from Eurasia

\textbf{\hypertarget{'yewlasiasutaestelawt}{'yewlasiasutaestelawt}} \textit{n.} (\hyperlink{'yewlasia}{'yewlasia}+\allowbreak \hyperlink{sutaeste}{sutaeste}+\allowbreak \hyperlink{lawt}{lawt})
South China Sea

\textbf{\hypertarget{yeh}{yeh}} \textit{n.} (Cmn. ⟨{\chinese{}叶}⟩ [jɛ˥˩])
leaf; blade of grass; photosynthetic structure of a plant

\textbf{\hypertarget{yehak}{yehak}} \textit{n.} (\hyperlink{yeh}{yeh}+\allowbreak \hyperlink{ak}{ak})
foliar; leafy

\textbf{\hypertarget{'yehutim}{'yehutim}} \textit{n.} (Heb. ⟨{\hebrew{}יְהוּדִים}⟩ [jehuˈdim])
Jew; the Jewish people

\textbf{\hypertarget{'yehutimak}{'yehutimak}} \textit{n.} (\hyperlink{'yehutim}{'yehutim}+\allowbreak \hyperlink{ak}{ak})
Jewish; of the Jews

\textbf{\hypertarget{'yehutimfitilip}{'yehutimfitilip}} \textit{n.} (\hyperlink{'yehutim}{'yehutim}+\allowbreak \hyperlink{fitilip}{fitilip})
Judaism

\textbf{\hypertarget{'yehutimfitilipwon}{'yehutimfitilipwon}} \textit{n.} (\hyperlink{'yehutimfitilip}{'yehutimfitilip}+\allowbreak \hyperlink{won}{won})
Jew; religious Jew; followers of Judaism

\textbf{\hypertarget{'yehutimtec}{'yehutimtec}} \textit{n.} (\hyperlink{'yehutim}{'yehutim}+\allowbreak \hyperlink{tec}{tec})
Judah; the Kingdom of Judah

\textbf{\hypertarget{yehcwelon}{yehcwelon}} \textit{n.} (\hyperlink{yeh}{yeh}+\allowbreak \hyperlink{cwelon}{cwelon})
tea

\textbf{\hypertarget{yehkol}{yehkol}} \textit{n.} (\hyperlink{yeh}{yeh}+\allowbreak \hyperlink{kol}{kol})
kale; leaf cabbage

\textbf{\hypertarget{yehpet}{yehpet}} \textit{n.} (\hyperlink{yeh}{yeh}+\allowbreak \hyperlink{pet}{pet})
chard; spinach beet

\textbf{\hypertarget{yehpiac}{yehpiac}} \textit{n.} (\hyperlink{yeh}{yeh}+\allowbreak \hyperlink{piac}{piac})
scallion; green onion; spring onion; salad onion

\textbf{\hypertarget{yek}{yek}} \textit{n.} (\hyperlink{won}{\sout{won}})
beast; wild animal; non-human animal

\textbf{\hypertarget{yekak}{yekak}} \textit{n.} (\hyperlink{yek}{yek}+\allowbreak \hyperlink{ak}{ak})
wild; beastial; animalistic; visceral

\textbf{\hypertarget{yayu}{yayu}} \textit{v.} (\hyperlink{wawi}{\sout{wawi}})
relieve; calm; reassure; \hyperlink{yayulum}{ʟᴜᴍ} gives \hyperlink{yayulon}{ʟᴏᴧ} relieved feelings

\textbf{\hypertarget{yayulon}{yayulon}} \textit{n.} (\hyperlink{yayu}{yayu}+\allowbreak \hyperlink{lon}{lon})
soothed

\textbf{\hypertarget{yayulum}{yayulum}} \textit{n.} (\hyperlink{yayu}{yayu}+\allowbreak \hyperlink{lum}{lum})
relief

\textbf{\hypertarget{yayuki}{yayuki}} \textit{v.} (\hyperlink{yayu}{yayu}+\allowbreak \hyperlink{ki}{ki})
assuage; sooth; relieve; calm; \hyperlink{yayukiles}{ʟєꜱ} causes ʟᴏᴧ to feel relieved by ʟᴜᴍ

\textbf{\hypertarget{yayukiles}{yayukiles}} \textit{n.} (\hyperlink{yayuki}{yayuki}+\allowbreak \hyperlink{les}{les})
reliever

\textbf{\hypertarget{yala}{yala}} \textit{v.} (Yor. ⟨yára⟩ [járā])
be fast; be quick; be frequent; hurry; \hyperlink{yalalon}{ʟᴏᴧ} progresses, oscillates, or decays quickly

\textbf{\hypertarget{yalaiti}{yalaiti}} \textit{v.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{iti}{iti})
differentiate; take derivative; \hyperlink{yalaitiles}{ʟєꜱ} takes the nth derivative of \hyperlink{yalaitilon}{ʟᴏᴧ} with respect to \hyperlink{yalaitilum}{ʟᴜᴍ}

\textbf{\hypertarget{yalaitiles}{yalaitiles}} \textit{n.} (\hyperlink{yalaiti}{yalaiti}+\allowbreak \hyperlink{les}{les})
differentiater

\textbf{\hypertarget{yalaitilon}{yalaitilon}} \textit{n.} (\hyperlink{yalaiti}{yalaiti}+\allowbreak \hyperlink{lon}{lon})
antiderivative; differentiation function

\textbf{\hypertarget{yalaitilum}{yalaitilum}} \textit{n.} (\hyperlink{yalaiti}{yalaiti}+\allowbreak \hyperlink{lum}{lum})
differentiation variable

\textbf{\hypertarget{yalaitilyan}{yalaitilyan}} \textit{n.} (\hyperlink{yalaiti}{yalaiti}+\allowbreak \hyperlink{lyan}{lyan})
derivative order

\textbf{\hypertarget{yalalon}{yalalon}} \textit{n.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{lon}{lon})
fast; quick; frequent

\textbf{\hypertarget{yalalonnyec}{yalalonnyec}} \textit{n.} (\hyperlink{yalalon}{yalalon}+\allowbreak \hyperlink{nyec}{nyec})
rabbit; hare

\textbf{\hypertarget{yalalyan}{yalalyan}} \textit{n.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{lyan}{lyan})
speed; angular velocity

\textbf{\hypertarget{yalamuf}{yalamuf}} \textit{n.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{muf}{muf})
antelope

\textbf{\hypertarget{yalacalunyo}{yalacalunyo}} \textit{v.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{calunyo}{calunyo})
undergo revolution; ʟᴏᴧ goes through a revolution

\textbf{\hypertarget{yalacalunyolwel}{yalacalunyolwel}} \textit{n.} (\hyperlink{yalacalunyo}{yalacalunyo}+\allowbreak \hyperlink{lwel}{lwel})
revolution

\textbf{\hypertarget{yalakunciki}{yalakunciki}} \textit{v.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{kunciki}{kunciki})
launch coup d’etat; seize power; ʟєꜱ suddenly seizes control of ʟᴏᴧ

\textbf{\hypertarget{yalakuncikilwel}{yalakuncikilwel}} \textit{n.} (\hyperlink{yalakunciki}{yalakunciki}+\allowbreak \hyperlink{lwel}{lwel})
coup d’etat; coup; putsch; golpe

\textbf{\hypertarget{yalati}{yalati}} \textit{v.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{ti}{ti})
text; message; instant-message \hyperlink{yalatiles}{ʟєꜱ} sends \hyperlink{yalatilum}{ʟᴜᴍ} to \hyperlink{yalatilon}{ʟᴏᴧ}

\textbf{\hypertarget{yalatiles}{yalatiles}} \textit{n.} (\hyperlink{yalati}{yalati}+\allowbreak \hyperlink{les}{les})
sender of a text

\textbf{\hypertarget{yalatilon}{yalatilon}} \textit{n.} (\hyperlink{yalati}{yalati}+\allowbreak \hyperlink{lon}{lon})
recipient of a text

\textbf{\hypertarget{yalatilum}{yalatilum}} \textit{n.} (\hyperlink{yalati}{yalati}+\allowbreak \hyperlink{lum}{lum})
text message

\textbf{\hypertarget{yalapum}{yalapum}} \textit{n.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{pum}{pum})
Mercury

\textbf{\hypertarget{yalapumak}{yalapumak}} \textit{n.} (\hyperlink{yalapum}{yalapum}+\allowbreak \hyperlink{ak}{ak})
Mercurian

\textbf{\hypertarget{yalapucocalu}{yalapucocalu}} \textit{v.} (\hyperlink{yala}{yala}+\allowbreak \hyperlink{pucocalu}{pucocalu})
fast-walk; ʟᴏᴧ is doing a fast walk on ʟᴜᴍ

\textbf{\hypertarget{yan}{yan}} \textit{post.} (Cmn. ⟨{\chinese{}量}⟩ [ljaŋ˥˩])
than; as; \textit{marks amount or degree}

\textbf{\hypertarget{yam}{yam}} \textit{n.} (Cmn. ⟨{\chinese{}亚麻}⟩ [ja˥˩ma˧˥])
flax; linseed; linen; Linum

\textbf{\hypertarget{'yaman}{'yaman}} \textit{n.} (Ara. ⟨{\arabics{}يمن}⟩ [jaman])
Yemen

\textbf{\hypertarget{'yamanak}{'yamanak}} \textit{n.} (\hyperlink{'yaman}{'yaman}+\allowbreak \hyperlink{ak}{ak})
Yemeni; from Yemen

\textbf{\hypertarget{'yamanwon}{'yamanwon}} \textit{n.} (\hyperlink{'yaman}{'yaman}+\allowbreak \hyperlink{won}{won})
Yemeni; Yemenite; the Yemeni people

\textbf{\hypertarget{'yahwe}{'yahwe}} \textit{n.} (Heb. ⟨{\hebrew{}יהוה‬}⟩ [jahwe])
YHWH; Yahweh; Jehovah; God; Allah; Abrahamic God

\textbf{\hypertarget{yata}{yata}} \textit{v.} (Hin. ⟨{\devanagari{}याद}⟩ [jaːd])
recall; remind; remember; remember to; jog memory; \hyperlink{yatales}{ʟєꜱ} helps \hyperlink{yatalon}{ʟᴏᴧ} recall \hyperlink{yatalum}{ʟᴜᴍ} from memory

\textbf{\hypertarget{yatales}{yatales}} \textit{n.} (\hyperlink{yata}{yata}+\allowbreak \hyperlink{les}{les})
mnemonic

\textbf{\hypertarget{yatalon}{yatalon}} \textit{n.} (\hyperlink{yata}{yata}+\allowbreak \hyperlink{lon}{lon})
recaller

\textbf{\hypertarget{yatalum}{yatalum}} \textit{n.} (\hyperlink{yata}{yata}+\allowbreak \hyperlink{lum}{lum})
factoid; datum

\textbf{\hypertarget{yatapowi}{yatapowi}} \textit{v.} (\hyperlink{yata}{yata}+\allowbreak \hyperlink{powi}{powi})
can remember; remember; know; \hyperlink{yatapowilon}{ʟᴏᴧ} has ʟᴜᴍ stored in memory

\textbf{\hypertarget{yatapowilon}{yatapowilon}} \textit{n.} (\hyperlink{yatapowi}{yatapowi}+\allowbreak \hyperlink{lon}{lon})
knowledgeable; smart

\textbf{\hypertarget{yatapowinu}{yatapowinu}} \textit{v.} (\hyperlink{yatapowi}{yatapowi}+\allowbreak \hyperlink{nu}{nu})
forget; erase memory; \hyperlink{yatapowinules}{ʟєꜱ} makes ʟᴏᴧ forget ʟᴜᴍ

\textbf{\hypertarget{yatapowinules}{yatapowinules}} \textit{n.} (\hyperlink{yatapowinu}{yatapowinu}+\allowbreak \hyperlink{les}{les})
mind-eraser

\textbf{\hypertarget{yatapowiki}{yatapowiki}} \textit{v.} (\hyperlink{yatapowi}{yatapowi}+\allowbreak \hyperlink{ki}{ki})
memorise; drill; remind; \hyperlink{yatapowikiles}{ʟєꜱ} makes ʟᴏᴧ memorise ʟᴜᴍ

\textbf{\hypertarget{yatapowikiles}{yatapowikiles}} \textit{n.} (\hyperlink{yatapowiki}{yatapowiki}+\allowbreak \hyperlink{les}{les})
driller; crammer; memoriser

\textbf{\hypertarget{yato}{yato}} \textit{v.} (Yor. ⟨yàtọ̀⟩ [jàtɔ̀])
differ; be different; be distinct; \hyperlink{yatolon}{ʟᴏᴧ} is different from ʟᴜᴍ

\textbf{\hypertarget{yatolon}{yatolon}} \textit{n.} (\hyperlink{yato}{yato}+\allowbreak \hyperlink{lon}{lon})
different; distinct

\textbf{\hypertarget{yatoki}{yatoki}} \textit{v.} (\hyperlink{yato}{yato}+\allowbreak \hyperlink{ki}{ki})
diverge; make different; ʟєꜱ makes ʟᴏᴧ become different from ʟᴜᴍ

\textbf{\hypertarget{yo}{yo}} \textit{spec.} (Cmn. ⟨{\chinese{}又}⟩ [jow˥˩])
both; \textit{begins a conjugate phrase}

\textbf{\hypertarget{'yo}{'yo}} \textit{n.} (ono. [j])
y; /j/; palatal approximant

\textbf{\hypertarget{'yolupa}{'yolupa}} \textit{n.} (Yor. ⟨Yorùbá⟩ [jōɾùbá])
Yoruba; Ioruba; Joruba; the Yoruba people

\textbf{\hypertarget{'yolupaak}{'yolupaak}} \textit{n.} (\hyperlink{'yolupa}{'yolupa}+\allowbreak \hyperlink{ak}{ak})
Yoruba; of the Yoruba

\textbf{\hypertarget{'yolupatilip}{'yolupatilip}} \textit{n.} (\hyperlink{'yolupa}{'yolupa}+\allowbreak \hyperlink{tilip}{tilip})
Yoruba; the Yoruba language

\textbf{\hypertarget{yohau}{yohau}} \textit{v.} (Cmn. ⟨{\chinese{}友好}⟩ [joʊ̯˧˩˧xɑʊ̯˧˩˧])
be friendly; be nice; be kind; \hyperlink{yohaulon}{ʟᴏᴧ} considers \hyperlink{yohaulum}{ʟᴜᴍ} a friend

\textbf{\hypertarget{yohaulon}{yohaulon}} \textit{n.} (\hyperlink{yohau}{yohau}+\allowbreak \hyperlink{lon}{lon})
friendly; nice; kind

\textbf{\hypertarget{yohaulum}{yohaulum}} \textit{n.} (\hyperlink{yohau}{yohau}+\allowbreak \hyperlink{lum}{lum})
friend

\textbf{\hypertarget{yohaulyan}{yohaulyan}} \textit{n.} (\hyperlink{yohau}{yohau}+\allowbreak \hyperlink{lyan}{lyan})
friendliness; amity

\textbf{\hypertarget{yohauki}{yohauki}} \textit{v.} (\hyperlink{yohau}{yohau}+\allowbreak \hyperlink{ki}{ki})
befriend; introduce; soften; \hyperlink{yohaukiles}{ʟєꜱ} makes ʟᴏᴧ become friends with ʟᴜᴍ

\textbf{\hypertarget{yohaukiles}{yohaukiles}} \textit{n.} (\hyperlink{yohauki}{yohauki}+\allowbreak \hyperlink{les}{les})
friend-arranger

\textbf{\hypertarget{'yok}{'yok}} \textit{n.} (Eng. ⟨York⟩ [jɔːk])
York

\textbf{\hypertarget{yot}{yot}} \textit{post.} (\hyperlink{wel}{\sout{wel}})
on; at; in; \textit{marks location}

\textbf{\hypertarget{'yishael}{'yishael}} \textit{n.} (Heb. ⟨{\hebrew{}ישראל}⟩ [jisʁael])
Israel

\textbf{\hypertarget{'yishaelak}{'yishaelak}} \textit{n.} (\hyperlink{'yishael}{'yishael}+\allowbreak \hyperlink{ak}{ak})
Israeli; from Israel

\textbf{\hypertarget{'yishaelwon}{'yishaelwon}} \textit{n.} (\hyperlink{'yishael}{'yishael}+\allowbreak \hyperlink{won}{won})
Israelite; the Israeli people

\textbf{\hypertarget{'yishaeltilip}{'yishaeltilip}} \textit{n.} (\hyperlink{'yishael}{'yishael}+\allowbreak \hyperlink{tilip}{tilip})
Hebrew; the Hebrew language

\textbf{\hypertarget{'yuan}{'yuan}} \textit{n.} (Cmn. ⟨{\chinese{}元}⟩ [ɥæn˧˥])
yuan; yen; won; ¥; ₩

\textbf{\hypertarget{'yunikowt}{'yunikowt}} \textit{n.} (Eng. ⟨Unicode⟩ [ˈjunɪkoʊ̯d])
Unicode

\section{L}

\textbf{\hypertarget{l}{l}} \textit{pn.} (∅)
which; that; \textit{relative}

\textbf{\hypertarget{le}{le}} \textit{v.} (Cmn. ⟨{\chinese{}累}⟩ [leɪ̯˥˩])
be fatigued; be tired; \hyperlink{lelon}{ʟᴏᴧ} is fatigued

\textbf{\hypertarget{lealac}{lealac}} \textit{n.} (Epo. ⟨realaĵo⟩ [reaˈlaʒo])
reality; universe; dimension; collection of all canonical existing things

\textbf{\hypertarget{lealacak}{lealacak}} \textit{n.} (\hyperlink{lealac}{lealac}+\allowbreak \hyperlink{ak}{ak})
real; realistic; possible

\textbf{\hypertarget{lealacsoma}{lealacsoma}} \textit{v.} (\hyperlink{lealac}{lealac}+\allowbreak \hyperlink{soma}{soma})
do philosophy; \hyperlink{lealacsomales}{ʟєꜱ} uses reasoning and deduction to ponder \hyperlink{lealacsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{lealacsomales}{lealacsomales}} \textit{n.} (\hyperlink{lealacsoma}{lealacsoma}+\allowbreak \hyperlink{les}{les})
philosopher

\textbf{\hypertarget{lealacsomalon}{lealacsomalon}} \textit{n.} (\hyperlink{lealacsoma}{lealacsoma}+\allowbreak \hyperlink{lon}{lon})
philosophy

\textbf{\hypertarget{leyawt}{leyawt}} \textit{n.} (Eng. ⟨layout⟩ [leɪ̯aʊ̯t])
layout; topography; geography

\textbf{\hypertarget{leyawtak}{leyawtak}} \textit{n.} (\hyperlink{leyawt}{leyawt}+\allowbreak \hyperlink{ak}{ak})
topographical; geographical

\textbf{\hypertarget{leyawthulum}{leyawthulum}} \textit{n.} (\hyperlink{leyawt}{leyawt}+\allowbreak \hyperlink{hulum}{hulum})
map

\textbf{\hypertarget{leyawthulumpatililip}{leyawthulumpatililip}} \textit{n.} (\hyperlink{leyawthulum}{leyawthulum}+\allowbreak \hyperlink{patililip}{patililip})
map projection

\textbf{\hypertarget{'leykos}{'leykos}} \textit{n.} (Eng. ⟨Lagos⟩ [ˈleɪ̯ɡɒs])
Lagos

\textbf{\hypertarget{lele}{lele}} \textit{v.} (Yor. ⟨rere⟩ [rērē])
prosper; fare; be-well; be-good; ʟᴏᴧ is doing well

\textbf{\hypertarget{lelon}{lelon}} \textit{n.} (\hyperlink{le}{le}+\allowbreak \hyperlink{lon}{lon})
fatigued; tired

\textbf{\hypertarget{lene}{lene}} \textit{v.} (\hyperlink{toko}{\sout{toko}})
be unsour; \hyperlink{lenelon}{ʟᴏᴧ} is not very sour

\textbf{\hypertarget{lenelon}{lenelon}} \textit{n.} (\hyperlink{lene}{lene}+\allowbreak \hyperlink{lon}{lon})
unsour

\textbf{\hypertarget{leneki}{leneki}} \textit{v.} (\hyperlink{lene}{lene}+\allowbreak \hyperlink{ki}{ki})
desour; ʟєꜱ makes ʟᴏᴧ become less sour

\textbf{\hypertarget{lena}{lena}} \textit{v.} (Hin. ⟨{\devanagari{}लेना}⟩ [lenaː])
take up; consume; hold; occupy; \hyperlink{lenalon}{ʟᴏᴧ} is taken up by \hyperlink{lenalum}{ʟᴜᴍ}

\textbf{\hypertarget{lenalon}{lenalon}} \textit{n.} (\hyperlink{lena}{lena}+\allowbreak \hyperlink{lon}{lon})
slot; space; resource

\textbf{\hypertarget{lenalum}{lenalum}} \textit{n.} (\hyperlink{lena}{lena}+\allowbreak \hyperlink{lum}{lum})
allocation

\textbf{\hypertarget{lenanu}{lenanu}} \textit{v.} (\hyperlink{lena}{lena}+\allowbreak \hyperlink{nu}{nu})
free; revoke; ʟєꜱ frees up ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{lenaki}{lenaki}} \textit{v.} (\hyperlink{lena}{lena}+\allowbreak \hyperlink{ki}{ki})
allocate; allot; spend; ʟєꜱ allocates ʟᴏᴧ to ʟᴜᴍ

\textbf{\hypertarget{lem}{lem}} \textit{n.} (Sot. ⟨lema⟩ [lemɑ])
paleognath; ostrich; emu; rhea; tinamou; kiwi; cassowary; Palaeognathae

\textbf{\hypertarget{les}{les}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{es}{es})
who (relative)

\textbf{\hypertarget{lesla}{lesla}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਲੇਸਲਾ}⟩ [leslɑ])
be viscous; be thick; \hyperlink{leslalon}{ʟᴏᴧ} is viscous

\textbf{\hypertarget{leslalon}{leslalon}} \textit{n.} (\hyperlink{lesla}{lesla}+\allowbreak \hyperlink{lon}{lon})
paste; gel; goop; viscous; thick

\textbf{\hypertarget{leslalyan}{leslalyan}} \textit{n.} (\hyperlink{lesla}{lesla}+\allowbreak \hyperlink{lyan}{lyan})
viscosity

\textbf{\hypertarget{leslaki}{leslaki}} \textit{v.} (\hyperlink{lesla}{lesla}+\allowbreak \hyperlink{ki}{ki})
thicken; increase viscosity; \hyperlink{leslakiles}{ʟєꜱ} makes ʟᴏᴧ more viscous

\textbf{\hypertarget{leslakiles}{leslakiles}} \textit{n.} (\hyperlink{leslaki}{leslaki}+\allowbreak \hyperlink{les}{les})
thickener; viscosity increaser

\textbf{\hypertarget{lef}{lef}} \textit{num.} (\hyperlink{tos}{\sout{tos}})
E; fourteen; only used for hexadecimal

\textbf{\hypertarget{lefak}{lefak}} \textit{n.} (\hyperlink{lef}{lef}+\allowbreak \hyperlink{ak}{ak})
fourteenth

\textbf{\hypertarget{lek}{lek}} \textit{n.} (Eng. ⟨leg⟩ [lɛɡ])
leg; appendage; long appendage used for transportation

\textbf{\hypertarget{lekak}{lekak}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{ak}{ak})
crural; appendicular

\textbf{\hypertarget{leki}{leki}} \textit{v.} (\hyperlink{le}{le}+\allowbreak \hyperlink{ki}{ki})
fatigue; tire; burn out; \hyperlink{lekiles}{ʟєꜱ} makes ʟᴏᴧ tired

\textbf{\hypertarget{lekiles}{lekiles}} \textit{n.} (\hyperlink{leki}{leki}+\allowbreak \hyperlink{les}{les})
tiring

\textbf{\hypertarget{lekcoh}{lekcoh}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{coh}{coh})
foot

\textbf{\hypertarget{lekcohak}{lekcohak}} \textit{n.} (\hyperlink{lekcoh}{lekcoh}+\allowbreak \hyperlink{ak}{ak})
pedal

\textbf{\hypertarget{lekcohtokalyot}{lekcohtokalyot}} \textit{n.} (\hyperlink{lekcoh}{lekcoh}+\allowbreak \hyperlink{tokalyot}{tokalyot})
ankle

\textbf{\hypertarget{lekcohpoltilum}{lekcohpoltilum}} \textit{n.} (\hyperlink{lekcoh}{lekcoh}+\allowbreak \hyperlink{poltilum}{poltilum})
shoe

\textbf{\hypertarget{lekcipcip}{lekcipcip}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{cipcip}{cipcip})
stork

\textbf{\hypertarget{lekcuc}{lekcuc}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{cuc}{cuc})
centipede; millipede

\textbf{\hypertarget{lektokalyot}{lektokalyot}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{tokalyot}{tokalyot})
hip

\textbf{\hypertarget{lekpoltilum}{lekpoltilum}} \textit{n.} (\hyperlink{lek}{lek}+\allowbreak \hyperlink{poltilum}{poltilum})
bottom; pants; shorts; skirt

\textbf{\hypertarget{let}{let}} \textit{n.} (Spa. ⟨red⟩ [reð])
network; net; web; system; collection of interconnected nodes

\textbf{\hypertarget{letak}{letak}} \textit{n.} (\hyperlink{let}{let}+\allowbreak \hyperlink{ak}{ak})
web

\textbf{\hypertarget{letus}{letus}} \textit{n.} (Ben. ⟨{\bengali{}লেটুস}⟩ [l̪etus̪])
lettuce; chicory; Lactuca

\textbf{\hypertarget{letpu}{letpu}} \textit{v.} (\hyperlink{tolmi}{\sout{tolmi}})
be awake; be concious; \hyperlink{letpulon}{ʟᴏᴧ} is awake

\textbf{\hypertarget{letpulon}{letpulon}} \textit{n.} (\hyperlink{letpu}{letpu}+\allowbreak \hyperlink{lon}{lon})
awake; concious

\textbf{\hypertarget{letpuki}{letpuki}} \textit{v.} (\hyperlink{letpu}{letpu}+\allowbreak \hyperlink{ki}{ki})
wake up; come to; ʟєꜱ (alarm clock) wakes ʟᴏᴧ up

\textbf{\hypertarget{lep}{lep}} \textit{n.} (Epo. ⟨rebo⟩ [ˈrebo])
climber; vine; creeper; ivy; long, climbing plant

\textbf{\hypertarget{leptil}{leptil}} \textit{n.} (Spa. ⟨reptil⟩ [repˈtil])
reptile; Reptilia

\textbf{\hypertarget{leptilak}{leptilak}} \textit{n.} (\hyperlink{leptil}{leptil}+\allowbreak \hyperlink{ak}{ak})
reptilian

\textbf{\hypertarget{'la}{'la}} \textit{n.} (ono. [l])
l; /l/; alveolar lateral approximant

\textbf{\hypertarget{lais}{lais}} \textit{n.} (Spa. ⟨raíz⟩ [raˈis])
root; underground component of a plant that gathers nutrients

\textbf{\hypertarget{laisak}{laisak}} \textit{n.} (\hyperlink{lais}{lais}+\allowbreak \hyperlink{ak}{ak})
radical; rooted

\textbf{\hypertarget{laispet}{laispet}} \textit{n.} (\hyperlink{lais}{lais}+\allowbreak \hyperlink{pet}{pet})
garden beet; beetroot

\textbf{\hypertarget{layoh}{layoh}} \textit{n.} (Epo. ⟨rajo⟩ [ˈrajo])
ray; manta ray; stingray; skate; sawfish; Batoidea

\textbf{\hypertarget{layf}{layf}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{ayf}{ayf})
for which

\textbf{\hypertarget{'laypiwia}{'laypiwia}} \textit{n.} (Eng. ⟨Liberia⟩ [laɪ̯ˈbɪɹʷiə])
Liberia

\textbf{\hypertarget{'laypiwiaak}{'laypiwiaak}} \textit{n.} (\hyperlink{'laypiwia}{'laypiwia}+\allowbreak \hyperlink{ak}{ak})
Liberian; from Liberia

\textbf{\hypertarget{'laypiwiawon}{'laypiwiawon}} \textit{n.} (\hyperlink{'laypiwia}{'laypiwia}+\allowbreak \hyperlink{won}{won})
Liberian; the Liberian people

\textbf{\hypertarget{'law}{'law}} \textit{n.} (Lao. ⟨{\lao{}ລາວ}⟩ [laːw˧])
Lao; Laotian; the Lao people

\textbf{\hypertarget{'lawak}{'lawak}} \textit{n.} (\hyperlink{'law}{'law}+\allowbreak \hyperlink{ak}{ak})
Lao; Laotian; from Laos

\textbf{\hypertarget{lawt}{lawt}} \textit{n.} (Msa. ⟨laut⟩ [lawt])
ocean; sea; large interconnected bodies of liquid covering most of a planet

\textbf{\hypertarget{'lawtec}{'lawtec}} \textit{n.} (\hyperlink{'law}{'law}+\allowbreak \hyperlink{tec}{tec})
Laos

\textbf{\hypertarget{lawtalkas}{lawtalkas}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{alkas}{alkas})
algae; alga

\textbf{\hypertarget{lawtak}{lawtak}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{ak}{ak})
marine; oceanic

\textbf{\hypertarget{'lawtilip}{'lawtilip}} \textit{n.} (\hyperlink{'law}{'law}+\allowbreak \hyperlink{tilip}{tilip})
Lao; the Lao language

\textbf{\hypertarget{lawtnyamaeccipcip}{lawtnyamaeccipcip}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{cipcip}{cipcip})
pelican

\textbf{\hypertarget{lawthihin}{lawthihin}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{hihin}{hihin})
seahorse

\textbf{\hypertarget{lawtcic}{lawtcic}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{cic}{cic})
pantopod

\textbf{\hypertarget{lawttayl}{lawttayl}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{tayl}{tayl})
Oceania

\textbf{\hypertarget{lawttaylak}{lawttaylak}} \textit{n.} (\hyperlink{lawttayl}{lawttayl}+\allowbreak \hyperlink{ak}{ak})
Oceanic

\textbf{\hypertarget{lawtpum}{lawtpum}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{pum}{pum})
Neptune

\textbf{\hypertarget{lawtpumak}{lawtpumak}} \textit{n.} (\hyperlink{lawtpum}{lawtpum}+\allowbreak \hyperlink{ak}{ak})
Neptunian

\textbf{\hypertarget{lawtpyah}{lawtpyah}} \textit{n.} (\hyperlink{lawt}{lawt}+\allowbreak \hyperlink{pyah}{pyah})
manatee; sea-cow

\textbf{\hypertarget{lanau}{lanau}} \textit{v.} (\hyperlink{takai}{\sout{takai}})
be turned off; be inanimate; be passive; be closed; \hyperlink{lanaulon}{ʟᴏᴧ} is turned off

\textbf{\hypertarget{lanaulon}{lanaulon}} \textit{n.} (\hyperlink{lanau}{lanau}+\allowbreak \hyperlink{lon}{lon})
turned off; inanimate; passive; closed

\textbf{\hypertarget{lanauki}{lanauki}} \textit{v.} (\hyperlink{lanau}{lanau}+\allowbreak \hyperlink{ki}{ki})
turn off; deactivate; kill; \hyperlink{lanaukiles}{ʟєꜱ} turns off ʟᴏᴧ

\textbf{\hypertarget{lanaukiles}{lanaukiles}} \textit{n.} (\hyperlink{lanauki}{lanauki}+\allowbreak \hyperlink{les}{les})
deactivator

\textbf{\hypertarget{'lanka}{'lanka}} \textit{n.} (Sin. ⟨{\sinhala{}ලංකා}⟩ [laŋkaː])
Sri Lanka (landmass)

\textbf{\hypertarget{'lankaak}{'lankaak}} \textit{n.} (\hyperlink{'lanka}{'lanka}+\allowbreak \hyperlink{ak}{ak})
Sri Lankan; from Sri Lanka

\textbf{\hypertarget{'lankawon}{'lankawon}} \textit{n.} (\hyperlink{'lanka}{'lanka}+\allowbreak \hyperlink{won}{won})
Sri Lankan; the Sri Lankan people

\textbf{\hypertarget{'lankatec}{'lankatec}} \textit{n.} (\hyperlink{'lanka}{'lanka}+\allowbreak \hyperlink{tec}{tec})
Sri Lanka; the Democratic Socialist Republic of Sri Lanka

\textbf{\hypertarget{lama}{lama}} \textit{v.} (Msa. ⟨lama⟩ [lama])
be long; be tall; \hyperlink{lamalon}{ʟᴏᴧ} is long in time or space

\textbf{\hypertarget{lamaaklalon}{lamaaklalon}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{aklalon}{aklalon})
sword

\textbf{\hypertarget{lamalon}{lamalon}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{lon}{lon})
protrusion; length; long; tall

\textbf{\hypertarget{lamalyan}{lamalyan}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{lyan}{lyan})
length; maximum physical dimension; length of time

\textbf{\hypertarget{lamanoluat}{lamanoluat}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{noluat}{noluat})
stopwatch

\textbf{\hypertarget{lamacuc}{lamacuc}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{cuc}{cuc})
dragonfly; damselfly

\textbf{\hypertarget{lamasiklalon}{lamasiklalon}} \textit{n.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{siklalon}{siklalon})
tube

\textbf{\hypertarget{lamafuloki}{lamafuloki}} \textit{v.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{fuloki}{fuloki})
stretch; ʟєꜱ stretches ʟᴏᴧ

\textbf{\hypertarget{lamaki}{lamaki}} \textit{v.} (\hyperlink{lama}{lama}+\allowbreak \hyperlink{ki}{ki})
lengthen; grow; \hyperlink{lamakiles}{ʟєꜱ} lengthens ʟᴏᴧ

\textbf{\hypertarget{lamakiles}{lamakiles}} \textit{n.} (\hyperlink{lamaki}{lamaki}+\allowbreak \hyperlink{les}{les})
lengthener

\textbf{\hypertarget{'lahol}{'lahol}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਲਾਹੌਰ}⟩ [ləˈhɔːɾ])
Lahore

\textbf{\hypertarget{'lasapuac}{'lasapuac}} \textit{n.} (Ltz. ⟨Lëtzebuerg⟩ [lət͡səbuːəɕ])
Luxembourg

\textbf{\hypertarget{'lasapuacak}{'lasapuacak}} \textit{n.} (\hyperlink{'lasapuac}{'lasapuac}+\allowbreak \hyperlink{ak}{ak})
Luxembougish; Luxembourgian; from Luxembourg

\textbf{\hypertarget{'lasapuacwon}{'lasapuacwon}} \textit{n.} (\hyperlink{'lasapuac}{'lasapuac}+\allowbreak \hyperlink{won}{won})
Luxembourger; the Luxembourgish people

\textbf{\hypertarget{'lasapuactilip}{'lasapuactilip}} \textit{n.} (\hyperlink{'lasapuac}{'lasapuac}+\allowbreak \hyperlink{tilip}{tilip})
Luxembourgish; the Luxembourgish language

\textbf{\hypertarget{lasi}{lasi}} \textit{v.} (Swa. ⟨radhi⟩ [ɾaði])
feel pleasure; feel good; feel satisfied; feel euphoria; \hyperlink{lasilon}{ʟᴏᴧ} feels pleased about \hyperlink{lasilum}{ʟᴜᴍ}

\textbf{\hypertarget{lasilon}{lasilon}} \textit{n.} (\hyperlink{lasi}{lasi}+\allowbreak \hyperlink{lon}{lon})
satisfied

\textbf{\hypertarget{lasilum}{lasilum}} \textit{n.} (\hyperlink{lasi}{lasi}+\allowbreak \hyperlink{lum}{lum})
satisfying

\textbf{\hypertarget{lasiki}{lasiki}} \textit{v.} (\hyperlink{lasi}{lasi}+\allowbreak \hyperlink{ki}{ki})
please; satisfy; soothe; ʟєꜱ makes ʟᴏᴧ feel pleased by ʟᴜᴍ

\textbf{\hypertarget{lak}{lak}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{ak}{ak})
whose (relative)

\textbf{\hypertarget{'latium}{'latium}} \textit{n.} (Lat. ⟨Latium⟩ [ˈɫatiũː])
Latium

\textbf{\hypertarget{'latiumak}{'latiumak}} \textit{n.} (\hyperlink{'latium}{'latium}+\allowbreak \hyperlink{ak}{ak})
Latin; of Latin

\textbf{\hypertarget{'latiumwon}{'latiumwon}} \textit{n.} (\hyperlink{'latium}{'latium}+\allowbreak \hyperlink{won}{won})
Latin; the Latin people

\textbf{\hypertarget{'latiumwon'amelika}{'latiumwon'amelika}} \textit{n.} (\hyperlink{'latiumwon}{'latiumwon}+\allowbreak \hyperlink{'amelika}{'amelika})
Latin America

\textbf{\hypertarget{'latiumwon'amelikaak}{'latiumwon'amelikaak}} \textit{n.} (\hyperlink{'latiumwon'amelika}{'latiumwon'amelika}+\allowbreak \hyperlink{ak}{ak})
Latin American

\textbf{\hypertarget{'latiumtilip}{'latiumtilip}} \textit{n.} (\hyperlink{'latium}{'latium}+\allowbreak \hyperlink{tilip}{tilip})
Latin

\textbf{\hypertarget{'latwiya}{'latwiya}} \textit{n.} (Lav. ⟨Latvija⟩ [ˈlatvija])
Latvia

\textbf{\hypertarget{'latwiyaak}{'latwiyaak}} \textit{n.} (\hyperlink{'latwiya}{'latwiya}+\allowbreak \hyperlink{ak}{ak})
Latvian; from Latvia

\textbf{\hypertarget{'latwiyawon}{'latwiyawon}} \textit{n.} (\hyperlink{'latwiya}{'latwiya}+\allowbreak \hyperlink{won}{won})
Latvian; the Latvian people

\textbf{\hypertarget{'latwiyatilip}{'latwiyatilip}} \textit{n.} (\hyperlink{'latwiya}{'latwiya}+\allowbreak \hyperlink{tilip}{tilip})
Latvian; the Latvian language

\textbf{\hypertarget{lo}{lo}} \textit{v.} (\hyperlink{te}{\sout{te}})
erase; overwrite; obscure; \hyperlink{loles}{ʟєꜱ} removes traces of \hyperlink{lolon}{ʟᴏᴧ} from \hyperlink{lolum}{ʟᴜᴍ}

\textbf{\hypertarget{loles}{loles}} \textit{n.} (\hyperlink{lo}{lo}+\allowbreak \hyperlink{les}{les})
one who erases; eraser

\textbf{\hypertarget{lolon}{lolon}} \textit{n.} (\hyperlink{lo}{lo}+\allowbreak \hyperlink{lon}{lon})
erased

\textbf{\hypertarget{loluat}{loluat}} \textit{n.} (\hyperlink{lo}{lo}+\allowbreak \hyperlink{luat}{luat})
eraser

\textbf{\hypertarget{lolum}{lolum}} \textit{n.} (\hyperlink{lo}{lo}+\allowbreak \hyperlink{lum}{lum})
blank slate

\textbf{\hypertarget{lon}{lon}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{on}{on})
which (relative)

\textbf{\hypertarget{lono}{lono}} \textit{v.} (Ben. ⟨{\bengali{}রঙ}⟩ [rɔŋɔ])
be coloured; have colour; \hyperlink{lonolum}{ʟᴜᴍ} is the colour of \hyperlink{lonolon}{ʟᴏᴧ}

\textbf{\hypertarget{lonolon}{lonolon}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{lon}{lon})
coloured

\textbf{\hypertarget{lonolum}{lonolum}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{lum}{lum})
colour

\textbf{\hypertarget{lonowicon}{lonowicon}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{wicon}{wicon})
spot; dot

\textbf{\hypertarget{lonowiconak}{lonowiconak}} \textit{n.} (\hyperlink{lonowicon}{lonowicon}+\allowbreak \hyperlink{ak}{ak})
spotted; dotted

\textbf{\hypertarget{lonowiconmuf}{lonowiconmuf}} \textit{n.} (\hyperlink{lonowicon}{lonowicon}+\allowbreak \hyperlink{muf}{muf})
cow; bull; beef

\textbf{\hypertarget{lononyamaeccipcip}{lononyamaeccipcip}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{cipcip}{cipcip})
toucan; Ramphastidae

\textbf{\hypertarget{lonomilumutihutyeh}{lonomilumutihutyeh}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{milumutihutyeh}{milumutihutyeh})
butterfly

\textbf{\hypertarget{lonositelon}{lonositelon}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{sitelon}{sitelon})
stripe

\textbf{\hypertarget{lonositelonak}{lonositelonak}} \textit{n.} (\hyperlink{lonositelon}{lonositelon}+\allowbreak \hyperlink{ak}{ak})
striped

\textbf{\hypertarget{lonositelonmyawf}{lonositelonmyawf}} \textit{n.} (\hyperlink{lonositelon}{lonositelon}+\allowbreak \hyperlink{myawf}{myawf})
tiger

\textbf{\hypertarget{lonokap}{lonokap}} \textit{n.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{kap}{kap})
koi; koi fish

\textbf{\hypertarget{lonoki}{lonoki}} \textit{v.} (\hyperlink{lono}{lono}+\allowbreak \hyperlink{ki}{ki})
colour; shade; \hyperlink{lonokiles}{ʟєꜱ} colours ʟᴏᴧ ʟᴜᴍ

\textbf{\hypertarget{lonokiles}{lonokiles}} \textit{n.} (\hyperlink{lonoki}{lonoki}+\allowbreak \hyperlink{les}{les})
colourer

\textbf{\hypertarget{'lontan}{'lontan}} \textit{n.} (Eng. ⟨London⟩ [ˈlʌndən])
London

\textbf{\hypertarget{'loma}{'loma}} \textit{n.} (Ita. ⟨Roma⟩ [ˈroːma])
Rome

\textbf{\hypertarget{'loma'kilistosfitilip}{'loma'kilistosfitilip}} \textit{n.} (\hyperlink{'loma}{'loma}+\allowbreak \hyperlink{'kilistosfitilip}{'kilistosfitilip})
Roman Catholicism; Catholicism

\textbf{\hypertarget{'lomatec}{'lomatec}} \textit{n.} (\hyperlink{'loma}{'loma}+\allowbreak \hyperlink{tec}{tec})
Rome; the Roman Empire

\textbf{\hypertarget{'lomin}{'lomin}} \textit{n.} (Ron. ⟨român⟩ [romɨn])
Romanian; the Romanian people

\textbf{\hypertarget{'lominak}{'lominak}} \textit{n.} (\hyperlink{'lomin}{'lomin}+\allowbreak \hyperlink{ak}{ak})
Romanian; from Romania

\textbf{\hypertarget{'lomintec}{'lomintec}} \textit{n.} (\hyperlink{'lomin}{'lomin}+\allowbreak \hyperlink{tec}{tec})
Romania

\textbf{\hypertarget{'lomintilip}{'lomintilip}} \textit{n.} (\hyperlink{'lomin}{'lomin}+\allowbreak \hyperlink{tilip}{tilip})
Romanian; the Romanian language

\textbf{\hypertarget{'locpan}{'locpan}} \textit{n.} (Ljb. ⟨.lojban.⟩ [ˈʔloʒbanʔ])
Lojban

\textbf{\hypertarget{'locpanak}{'locpanak}} \textit{n.} (\hyperlink{'locpan}{'locpan}+\allowbreak \hyperlink{ak}{ak})
Lojban; in Lojban

\textbf{\hypertarget{'locpanwon}{'locpanwon}} \textit{n.} (\hyperlink{'locpan}{'locpan}+\allowbreak \hyperlink{won}{won})
Lojbanist; Lojban speakers

\textbf{\hypertarget{lokfe}{lokfe}} \textit{v.} (\hyperlink{tenso}{\sout{tenso}})
be relaxed; be lax; be chill; \hyperlink{lokfelon}{ʟᴏᴧ} is not under pressure

\textbf{\hypertarget{lokfelon}{lokfelon}} \textit{n.} (\hyperlink{lokfe}{lokfe}+\allowbreak \hyperlink{lon}{lon})
relaxed; lax; chill

\textbf{\hypertarget{lokfeki}{lokfeki}} \textit{v.} (\hyperlink{lokfe}{lokfe}+\allowbreak \hyperlink{ki}{ki})
relax; take off pressure; ʟєꜱ takes pressure off of ʟᴏᴧ

\textbf{\hypertarget{lota}{lota}} \textit{v.} (Spa. ⟨rueda⟩ [ˈrweða])
roll; tumble; be rolling; \hyperlink{lotalon}{ʟᴏᴧ} is rolling

\textbf{\hypertarget{lotalon}{lotalon}} \textit{n.} (\hyperlink{lota}{lota}+\allowbreak \hyperlink{lon}{lon})
wheel; roller; rolling

\textbf{\hypertarget{lotanu}{lotanu}} \textit{v.} (\hyperlink{lota}{lota}+\allowbreak \hyperlink{nu}{nu})
stop rolling; roll into; ʟєꜱ makes ʟᴏᴧ stop rolling

\textbf{\hypertarget{lotaki}{lotaki}} \textit{v.} (\hyperlink{lota}{lota}+\allowbreak \hyperlink{ki}{ki})
start rolling; roll from; \hyperlink{lotakiles}{ʟєꜱ} makes ʟᴏᴧ start rolling

\textbf{\hypertarget{lotakiles}{lotakiles}} \textit{n.} (\hyperlink{lotaki}{lotaki}+\allowbreak \hyperlink{les}{les})
roller

\textbf{\hypertarget{loto}{loto}} \textit{v.} (Spa. ⟨roto⟩ [ˈroto])
be in pieces; be broken; be piecemeal; \hyperlink{lotolon}{ʟᴏᴧ} is in multiple pieces

\textbf{\hypertarget{lotolon}{lotolon}} \textit{n.} (\hyperlink{loto}{loto}+\allowbreak \hyperlink{lon}{lon})
in pieces; broken; piecemeal

\textbf{\hypertarget{lotonu}{lotonu}} \textit{v.} (\hyperlink{loto}{loto}+\allowbreak \hyperlink{nu}{nu})
mend; fix; put back together; \hyperlink{lotonules}{ʟєꜱ} puts ʟᴏᴧ back together

\textbf{\hypertarget{lotonules}{lotonules}} \textit{n.} (\hyperlink{lotonu}{lotonu}+\allowbreak \hyperlink{les}{les})
fixer

\textbf{\hypertarget{lotonyolon}{lotonyolon}} \textit{n.} (\hyperlink{loto}{loto}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{lon}{lon})
whole; entirety; entire

\textbf{\hypertarget{lotonyolonpoltilum}{lotonyolonpoltilum}} \textit{n.} (\hyperlink{lotonyolon}{lotonyolon}+\allowbreak \hyperlink{poltilum}{poltilum})
suit; costume; uniform

\textbf{\hypertarget{lotoki}{lotoki}} \textit{v.} (\hyperlink{loto}{loto}+\allowbreak \hyperlink{ki}{ki})
break; shatter; destroy; \hyperlink{lotokiles}{ʟєꜱ} breaks ʟᴏᴧ into multiple pieces

\textbf{\hypertarget{lotokiles}{lotokiles}} \textit{n.} (\hyperlink{lotoki}{lotoki}+\allowbreak \hyperlink{les}{les})
breaker

\textbf{\hypertarget{lotokihepuki}{lotokihepuki}} \textit{v.} (\hyperlink{lotoki}{lotoki}+\allowbreak \hyperlink{hepuki}{hepuki})
explode; blow up; detonate; \hyperlink{lotokihepukiles}{ʟєꜱ} makes \hyperlink{lotokihepukilon}{ʟᴏᴧ} explode

\textbf{\hypertarget{lotokihepukilon}{lotokihepukilon}} \textit{n.} (\hyperlink{lotokihepuki}{lotokihepuki}+\allowbreak \hyperlink{lon}{lon})
exploded

\textbf{\hypertarget{lotokihepukiles}{lotokihepukiles}} \textit{n.} (\hyperlink{lotokihepuki}{lotokihepuki}+\allowbreak \hyperlink{les}{les})
exploder

\textbf{\hypertarget{lotokicomiki}{lotokicomiki}} \textit{v.} (\hyperlink{lotoki}{lotoki}+\allowbreak \hyperlink{comiki}{comiki})
implode; \hyperlink{lotokicomikiles}{ʟєꜱ} makes \hyperlink{lotokicomikilon}{ʟᴏᴧ} implode

\textbf{\hypertarget{lotokicomikilon}{lotokicomikilon}} \textit{n.} (\hyperlink{lotokicomiki}{lotokicomiki}+\allowbreak \hyperlink{lon}{lon})
imploded

\textbf{\hypertarget{lotokicomikiles}{lotokicomikiles}} \textit{n.} (\hyperlink{lotokicomiki}{lotokicomiki}+\allowbreak \hyperlink{les}{les})
imploder

\textbf{\hypertarget{lotokipowi}{lotokipowi}} \textit{v.} (\hyperlink{lotoki}{lotoki}+\allowbreak \hyperlink{powi}{powi})
be fragile; be structurally weak; be crumbly; be brittle; \hyperlink{lotokipowilon}{ʟᴏᴧ} is easy to break

\textbf{\hypertarget{lotokipowilon}{lotokipowilon}} \textit{n.} (\hyperlink{lotokipowi}{lotokipowi}+\allowbreak \hyperlink{lon}{lon})
fragile; structurally weak; crumbly; brittle

\textbf{\hypertarget{lotokipowinu}{lotokipowinu}} \textit{v.} (\hyperlink{lotokipowi}{lotokipowi}+\allowbreak \hyperlink{nu}{nu})
strengthen; brace; glue; \hyperlink{lotokipowinules}{ʟєꜱ} makes ʟᴏᴧ structurally stronger

\textbf{\hypertarget{lotokipowinules}{lotokipowinules}} \textit{n.} (\hyperlink{lotokipowinu}{lotokipowinu}+\allowbreak \hyperlink{les}{les})
strengthener; glue

\textbf{\hypertarget{lotokipowinyo}{lotokipowinyo}} \textit{v.} (\hyperlink{lotokipowi}{lotokipowi}+\allowbreak \hyperlink{nyo}{nyo})
be unbreaking; be structurally strong; be durable; \hyperlink{lotokipowinyolon}{ʟᴏᴧ} is difficult to break

\textbf{\hypertarget{lotokipowinyolon}{lotokipowinyolon}} \textit{n.} (\hyperlink{lotokipowinyo}{lotokipowinyo}+\allowbreak \hyperlink{lon}{lon})
unbreaking; structurally strong; durable

\textbf{\hypertarget{lotokipowinyolyan}{lotokipowinyolyan}} \textit{n.} (\hyperlink{lotokipowinyo}{lotokipowinyo}+\allowbreak \hyperlink{lyan}{lyan})
structural integrity; strength; durability

\textbf{\hypertarget{lotokipowiki}{lotokipowiki}} \textit{v.} (\hyperlink{lotokipowi}{lotokipowi}+\allowbreak \hyperlink{ki}{ki})
weaken; compromise; sabotage; \hyperlink{lotokipowikiles}{ʟєꜱ} makes ʟᴏᴧ structurally weaker

\textbf{\hypertarget{lotokipowikiles}{lotokipowikiles}} \textit{n.} (\hyperlink{lotokipowiki}{lotokipowiki}+\allowbreak \hyperlink{les}{les})
weakener; saboteur

\textbf{\hypertarget{lotiha}{lotiha}} \textit{v.} (\hyperlink{teluca}{\sout{teluca}})
be disgusted; \hyperlink{lotihalon}{ʟᴏᴧ} is disgusted by ʟᴜᴍ

\textbf{\hypertarget{lotihalon}{lotihalon}} \textit{n.} (\hyperlink{lotiha}{lotiha}+\allowbreak \hyperlink{lon}{lon})
disgusted

\textbf{\hypertarget{lotihaki}{lotihaki}} \textit{v.} (\hyperlink{lotiha}{lotiha}+\allowbreak \hyperlink{ki}{ki})
disgust; make disgusted; ʟєꜱ makes ʟᴏᴧ disgusted by ʟᴜᴍ

\textbf{\hypertarget{'lietuwa}{'lietuwa}} \textit{n.} (Lit. ⟨Lietuva⟩ [lʲɪɛtʊˈvɐ])
Lithuania

\textbf{\hypertarget{'lietuwaak}{'lietuwaak}} \textit{n.} (\hyperlink{'lietuwa}{'lietuwa}+\allowbreak \hyperlink{ak}{ak})
Lithuanian; from Lithuania

\textbf{\hypertarget{'lietuwawon}{'lietuwawon}} \textit{n.} (\hyperlink{'lietuwa}{'lietuwa}+\allowbreak \hyperlink{won}{won})
Lithuanian; the Lithuanian people

\textbf{\hypertarget{'lietuwatilip}{'lietuwatilip}} \textit{n.} (\hyperlink{'lietuwa}{'lietuwa}+\allowbreak \hyperlink{tilip}{tilip})
Lithuanian; the Lithuanian language

\textbf{\hypertarget{lial}{lial}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{ial}{ial})
why (relative); because of which

\textbf{\hypertarget{lialkweki}{lialkweki}} \textit{v.} (\hyperlink{l}{l}+\allowbreak \hyperlink{ial}{ial}+\allowbreak \hyperlink{kweki}{kweki})
result; follow; bear responsibility; bear fault; \hyperlink{lialkwekilon}{ʟᴏᴧ} results from ʟᴜᴍ

\textbf{\hypertarget{lialkwekilon}{lialkwekilon}} \textit{n.} (\hyperlink{lialkweki}{lialkweki}+\allowbreak \hyperlink{lon}{lon})
effect

\textbf{\hypertarget{'lila}{'lila}} \textit{n.} (Vec. ⟨lira⟩ [lira])
pound; lira; libra; £

\textbf{\hypertarget{'liwla}{'liwla}} \textit{n.} (Gmy. ⟨λύρα⟩ [ly˦ra])
lyre

\textbf{\hypertarget{lin}{lin}} \textit{n.} (Cmn. ⟨{\chinese{}鳞}⟩ [lin˧˥])
scale; squame; flake; rigid, external, organic plate used in array with others

\textbf{\hypertarget{linak}{linak}} \textit{n.} (\hyperlink{lin}{lin}+\allowbreak \hyperlink{ak}{ak})
squamous; scaly

\textbf{\hypertarget{linli}{linli}} \textit{v.} (ono. [riŋ riŋ])
ring; trill; coo; chime; SBU makes \hyperlink{linlilon}{ʟᴏᴧ}

\textbf{\hypertarget{linlilon}{linlilon}} \textit{n.} (\hyperlink{linli}{linli}+\allowbreak \hyperlink{lon}{lon})
ring; trill; coo; chime; noisy, concordant sound or action

\textbf{\hypertarget{linmamul}{linmamul}} \textit{n.} (\hyperlink{lin}{lin}+\allowbreak \hyperlink{mamul}{mamul})
pangolin

\textbf{\hypertarget{lim}{lim}} \textit{num.} (Jav. ⟨lima⟩ [lima])
5; five

\textbf{\hypertarget{limak}{limak}} \textit{n.} (\hyperlink{lim}{lim}+\allowbreak \hyperlink{ak}{ak})
fifth

\textbf{\hypertarget{limnul}{limnul}} \textit{num.} (\hyperlink{lim}{lim}+\allowbreak \hyperlink{nul}{nul})
50; fifty

\textbf{\hypertarget{limnulnul}{limnulnul}} \textit{num.} (\hyperlink{lim}{lim}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
500; five hundred

\textbf{\hypertarget{limsunkwelwel}{limsunkwelwel}} \textit{n.} (\hyperlink{lim}{lim}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Friday

\textbf{\hypertarget{limpucolon}{limpucolon}} \textit{n.} (\hyperlink{lim}{lim}+\allowbreak \hyperlink{pucolon}{pucolon})
pentagram; pentalpha; pentangle; star pentagon

\textbf{\hypertarget{lih}{lih}} \textit{n.} (Cmn. ⟨{\chinese{}狸}⟩ [li])
musteloid; red panda; skunk; raccoon; coatis; kinkajou; olingo; olinguito; ringtail; cacomistle; weasel; badger; otter; marten; ferret; mink; stoat; wolverine; Musteloidea

\textbf{\hypertarget{lic}{lic}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਰਿੱਛ}⟩ [ɾɪːt͡ʃʰ])
bear; Ursidae

\textbf{\hypertarget{licak}{licak}} \textit{n.} (\hyperlink{lic}{lic}+\allowbreak \hyperlink{ak}{ak})
ursine

\textbf{\hypertarget{'licilkentawlus}{'licilkentawlus}} \textit{n.} (Lat. ⟨Rigil Centaurus⟩ [rɪd͡ʒɪl kɛntawrʊs])
Alpha Centauri A; Rigil Kentaurus

\textbf{\hypertarget{'lictenectayn}{'lictenectayn}} \textit{n.} (Deu. ⟨Liechtenstein⟩ [lɪçtn̩ʃtaɪ̯n])
Liechtenstein

\textbf{\hypertarget{'lictenectaynak}{'lictenectaynak}} \textit{n.} (\hyperlink{'lictenectayn}{'lictenectayn}+\allowbreak \hyperlink{ak}{ak})
Liechtensteiner; from Liechtenstein

\textbf{\hypertarget{'lictenectaynwon}{'lictenectaynwon}} \textit{n.} (\hyperlink{'lictenectayn}{'lictenectayn}+\allowbreak \hyperlink{won}{won})
Liechtensteiner; the people of Liechtenstein

\textbf{\hypertarget{lisat}{lisat}} \textit{n.} (Eng. ⟨lizard⟩ [ˈlɪzɚd])
lizard; Lacertilia

\textbf{\hypertarget{'litium}{'litium}} \textit{n.} (Lat. ⟨lithium⟩ [lɪtɪʊ̃])
lithium

\textbf{\hypertarget{'lithe}{'lithe}} \textit{n.} (Fra. ⟨litre⟩ [ˈlitʁ])
litre; liter; L

\textbf{\hypertarget{litfo}{litfo}} \textit{v.} (\hyperlink{tulse}{\sout{tulse}})
be unsweet; be unsweetened; \hyperlink{litfolon}{ʟᴏᴧ} is unsweet

\textbf{\hypertarget{litfolon}{litfolon}} \textit{n.} (\hyperlink{litfo}{litfo}+\allowbreak \hyperlink{lon}{lon})
unsweet; unsweetened

\textbf{\hypertarget{litfoki}{litfoki}} \textit{v.} (\hyperlink{litfo}{litfo}+\allowbreak \hyperlink{ki}{ki})
unsweeten; ʟєꜱ makes ʟᴏᴧ become less sweet

\textbf{\hypertarget{lip}{lip}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{ip}{ip})
how (relative); by which

\textbf{\hypertarget{'lipiya}{'lipiya}} \textit{n.} (Ara. ⟨{\arabics{}ليبيا‎}⟩ [liːbija])
Libya

\textbf{\hypertarget{'lipiyaak}{'lipiyaak}} \textit{n.} (\hyperlink{'lipiya}{'lipiya}+\allowbreak \hyperlink{ak}{ak})
Libyan; from Libya

\textbf{\hypertarget{'lipiyawon}{'lipiyawon}} \textit{n.} (\hyperlink{'lipiya}{'lipiya}+\allowbreak \hyperlink{won}{won})
Libyan; the Libyan people

\textbf{\hypertarget{'lipnen}{'lipnen}} \textit{n.} (Ara. ⟨{\arabics{}لبنان‎}⟩ [lɪbˈnɛːn])
Lebanon

\textbf{\hypertarget{'lipnenak}{'lipnenak}} \textit{n.} (\hyperlink{'lipnen}{'lipnen}+\allowbreak \hyperlink{ak}{ak})
Lebanese; from Lebanon

\textbf{\hypertarget{'lipnenwon}{'lipnenwon}} \textit{n.} (\hyperlink{'lipnen}{'lipnen}+\allowbreak \hyperlink{won}{won})
Lebanese; the Lebanese people

\textbf{\hypertarget{lu}{lu}} \textit{v.} (\hyperlink{ti}{\sout{ti}})
consult; look up; reference; refer; read; ʟєꜱ retrieves ʟᴜᴍ from \hyperlink{lulon}{ʟᴏᴧ}

\textbf{\hypertarget{luat}{luat}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{uat}{uat})
with which (relative)

\textbf{\hypertarget{luatkweki}{luatkweki}} \textit{v.} (\hyperlink{l}{l}+\allowbreak \hyperlink{uat}{uat}+\allowbreak \hyperlink{kweki}{kweki})
use; work through; \hyperlink{luatkwekilon}{ʟᴏᴧ} is using ʟᴜᴍ

\textbf{\hypertarget{luatkwekilon}{luatkwekilon}} \textit{n.} (\hyperlink{luatkweki}{luatkweki}+\allowbreak \hyperlink{lon}{lon})
user

\textbf{\hypertarget{luatkwekipowi}{luatkwekipowi}} \textit{v.} (\hyperlink{luatkweki}{luatkweki}+\allowbreak \hyperlink{powi}{powi})
be usable; be practical; \hyperlink{luatkwekipowilon}{ʟᴏᴧ} is usable

\textbf{\hypertarget{luatkwekipowilon}{luatkwekipowilon}} \textit{n.} (\hyperlink{luatkwekipowi}{luatkwekipowi}+\allowbreak \hyperlink{lon}{lon})
usable; practical

\textbf{\hypertarget{luatkwekipowinyo}{luatkwekipowinyo}} \textit{v.} (\hyperlink{luatkwekipowi}{luatkwekipowi}+\allowbreak \hyperlink{nyo}{nyo})
be impractical; be unusable; \hyperlink{luatkwekipowinyolon}{ʟᴏᴧ} is not usable

\textbf{\hypertarget{luatkwekipowinyolon}{luatkwekipowinyolon}} \textit{n.} (\hyperlink{luatkwekipowinyo}{luatkwekipowinyo}+\allowbreak \hyperlink{lon}{lon})
impractical; unusable

\textbf{\hypertarget{luo}{luo}} \textit{v.} (\hyperlink{tie}{\sout{tie}})
be along; be longitudinal; be with; be parallel; \hyperlink{luolon}{ʟᴏᴧ} is along ʟᴜᴍ

\textbf{\hypertarget{luolon}{luolon}} \textit{n.} (\hyperlink{luo}{luo}+\allowbreak \hyperlink{lon}{lon})
along; longitudinal; with; parallel

\textbf{\hypertarget{luoki}{luoki}} \textit{v.} (\hyperlink{luo}{luo}+\allowbreak \hyperlink{ki}{ki})
align; move along; move with; ʟєꜱ makes ʟᴏᴧ go along ʟᴜᴍ

\textbf{\hypertarget{lulon}{lulon}} \textit{n.} (\hyperlink{lu}{lu}+\allowbreak \hyperlink{lon}{lon})
reference; table; source; consult; dictionary

\textbf{\hypertarget{luna}{luna}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਲੂਣਾ}⟩ [luɳɑ])
be salty; \hyperlink{lunalon}{ʟᴏᴧ} is salty

\textbf{\hypertarget{lunaufalon}{lunaufalon}} \textit{n.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{ufalon}{ufalon})
salt

\textbf{\hypertarget{lunalon}{lunalon}} \textit{n.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{lon}{lon})
salty

\textbf{\hypertarget{lunalyan}{lunalyan}} \textit{n.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{lyan}{lyan})
saltiness; salt

\textbf{\hypertarget{lunacakalum}{lunacakalum}} \textit{n.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{cakalum}{cakalum})
sodium

\textbf{\hypertarget{lunacyolyan}{lunacyolyan}} \textit{n.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{cyolyan}{cyolyan})
pickle; ʟєꜱ pickles \hyperlink{lunacyolyanlon}{ʟᴏᴧ}

\textbf{\hypertarget{lunacyolyanlon}{lunacyolyanlon}} \textit{n.} (\hyperlink{lunacyolyan}{lunacyolyan}+\allowbreak \hyperlink{lon}{lon})
pickled; pickle

\textbf{\hypertarget{lunaki}{lunaki}} \textit{v.} (\hyperlink{luna}{luna}+\allowbreak \hyperlink{ki}{ki})
salt; ʟєꜱ makes ʟᴏᴧ become salty

\textbf{\hypertarget{luni}{luni}} \textit{v.} (Cmn. ⟨{\chinese{}容易}⟩ [ɻʊŋ˧˥i˥˩])
be likely; be normal; be unremarkable; be expectable; be common; \hyperlink{lunilon}{ʟᴏᴧ} is likely true

\textbf{\hypertarget{lunilon}{lunilon}} \textit{n.} (\hyperlink{luni}{luni}+\allowbreak \hyperlink{lon}{lon})
likely; normal; unremarkable; expectable; common

\textbf{\hypertarget{lunilyan}{lunilyan}} \textit{n.} (\hyperlink{luni}{luni}+\allowbreak \hyperlink{lyan}{lyan})
P-value

\textbf{\hypertarget{lunisoma}{lunisoma}} \textit{v.} (\hyperlink{luni}{luni}+\allowbreak \hyperlink{soma}{soma})
do statistics; \hyperlink{lunisomales}{ʟєꜱ} studies data to learn about \hyperlink{lunisomalon}{ʟᴏᴧ}

\textbf{\hypertarget{lunisomales}{lunisomales}} \textit{n.} (\hyperlink{lunisoma}{lunisoma}+\allowbreak \hyperlink{les}{les})
statistician

\textbf{\hypertarget{lunisomalon}{lunisomalon}} \textit{n.} (\hyperlink{lunisoma}{lunisoma}+\allowbreak \hyperlink{lon}{lon})
statistics

\textbf{\hypertarget{luniki}{luniki}} \textit{v.} (\hyperlink{luni}{luni}+\allowbreak \hyperlink{ki}{ki})
increase chances; explain away; favour; ʟєꜱ makes ʟᴏᴧ more likely

\textbf{\hypertarget{'lunti}{'lunti}} \textit{n.} (Run. ⟨Rundi⟩ [ˈɾundi])
Burundian; the Rundi people

\textbf{\hypertarget{'luntiak}{'luntiak}} \textit{n.} (\hyperlink{'lunti}{'lunti}+\allowbreak \hyperlink{ak}{ak})
Burundian; from Burundi

\textbf{\hypertarget{'luntitec}{'luntitec}} \textit{n.} (\hyperlink{'lunti}{'lunti}+\allowbreak \hyperlink{tec}{tec})
Burundi

\textbf{\hypertarget{'luntitilip}{'luntitilip}} \textit{n.} (\hyperlink{'lunti}{'lunti}+\allowbreak \hyperlink{tilip}{tilip})
Kirundi; Rundi; the Rundi language

\textbf{\hypertarget{lum}{lum}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{um}{um})
whom (relative)

\textbf{\hypertarget{lumah}{lumah}} \textit{n.} (Jav. ⟨lumah⟩ [ɭumɑh])
surface; plane; layer; two-dimensional locus

\textbf{\hypertarget{lumahak}{lumahak}} \textit{n.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{ak}{ak})
planar; superficial; facial

\textbf{\hypertarget{lumahmwoni}{lumahmwoni}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{mwoni}{mwoni})
draw; \hyperlink{lumahmwoniles}{ʟєꜱ} paints \hyperlink{lumahmwonilum}{ʟᴜᴍ} as \hyperlink{lumahmwonilon}{ʟᴏᴧ}

\textbf{\hypertarget{lumahmwoniles}{lumahmwoniles}} \textit{n.} (\hyperlink{lumahmwoni}{lumahmwoni}+\allowbreak \hyperlink{les}{les})
drawer

\textbf{\hypertarget{lumahmwonilon}{lumahmwonilon}} \textit{n.} (\hyperlink{lumahmwoni}{lumahmwoni}+\allowbreak \hyperlink{lon}{lon})
drawing

\textbf{\hypertarget{lumahmwonilum}{lumahmwonilum}} \textit{n.} (\hyperlink{lumahmwoni}{lumahmwoni}+\allowbreak \hyperlink{lum}{lum})
drawn; drawing subject

\textbf{\hypertarget{lumahhila}{lumahhila}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{hila}{hila})
climb; \hyperlink{lumahhilalon}{ʟᴏᴧ} climbs

\textbf{\hypertarget{lumahhilalon}{lumahhilalon}} \textit{n.} (\hyperlink{lumahhila}{lumahhila}+\allowbreak \hyperlink{lon}{lon})
climber

\textbf{\hypertarget{lumahhilaluat}{lumahhilaluat}} \textit{n.} (\hyperlink{lumahhila}{lumahhila}+\allowbreak \hyperlink{luat}{luat})
ladder; handholds

\textbf{\hypertarget{lumahsikla}{lumahsikla}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{sikla}{sikla})
be spherical; be round; \hyperlink{lumahsiklalon}{ʟᴏᴧ} is spherical

\textbf{\hypertarget{lumahsiklalon}{lumahsiklalon}} \textit{n.} (\hyperlink{lumahsikla}{lumahsikla}+\allowbreak \hyperlink{lon}{lon})
sphere; ball; spherical; round

\textbf{\hypertarget{lumahsiteponto}{lumahsiteponto}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{siteponto}{siteponto})
be polyhedral; \hyperlink{lumahsitepontolon}{ʟᴏᴧ} is polyhedral

\textbf{\hypertarget{lumahsitepontolon}{lumahsitepontolon}} \textit{n.} (\hyperlink{lumahsiteponto}{lumahsiteponto}+\allowbreak \hyperlink{lon}{lon})
polyhedron; gem; polyhedral

\textbf{\hypertarget{lumahfunta}{lumahfunta}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{funta}{funta})
be box-shaped; \hyperlink{lumahfuntalon}{ʟᴏᴧ} is box-shaped

\textbf{\hypertarget{lumahfuntalon}{lumahfuntalon}} \textit{n.} (\hyperlink{lumahfunta}{lumahfunta}+\allowbreak \hyperlink{lon}{lon})
box; rectangular prism; box-shaped

\textbf{\hypertarget{lumahtokanu}{lumahtokanu}} \textit{v.} (\hyperlink{lumah}{lumah}+\allowbreak \hyperlink{tokanu}{tokanu})
slice; ʟєꜱ slices ʟᴏᴧ into \hyperlink{lumahtokanulum}{ʟᴜᴍ}

\textbf{\hypertarget{lumahtokanulum}{lumahtokanulum}} \textit{n.} (\hyperlink{lumahtokanu}{lumahtokanu}+\allowbreak \hyperlink{lum}{lum})
slice

\textbf{\hypertarget{luci}{luci}} \textit{v.} (Epo. ⟨ruĝi⟩ [ˈrud͡ʒi])
be red; \hyperlink{lucilon}{ʟᴏᴧ} reflects short wavelength light

\textbf{\hypertarget{lucilon}{lucilon}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{lon}{lon})
red

\textbf{\hypertarget{lucilyan}{lucilyan}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{lyan}{lyan})
redness

\textbf{\hypertarget{lucimuta}{lucimuta}} \textit{v.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{muta}{muta})
be magenta; be fuchsia; \hyperlink{lucimutalon}{ʟᴏᴧ} looks magenta

\textbf{\hypertarget{lucimutalon}{lucimutalon}} \textit{n.} (\hyperlink{lucimuta}{lucimuta}+\allowbreak \hyperlink{lon}{lon})
magenta; fuchsia

\textbf{\hypertarget{lucimutaki}{lucimutaki}} \textit{v.} (\hyperlink{lucimuta}{lucimuta}+\allowbreak \hyperlink{ki}{ki})
colour magenta; colour fuchsia; ʟєꜱ colours ʟᴏᴧ magenta

\textbf{\hypertarget{lucicipcip}{lucicipcip}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{cipcip}{cipcip})
flamingo

\textbf{\hypertarget{luciki}{luciki}} \textit{v.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{ki}{ki})
redden; colour red; ʟєꜱ colours ʟᴏᴧ red

\textbf{\hypertarget{lucikwah}{lucikwah}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{kwah}{kwah})
watermelon

\textbf{\hypertarget{lucitawh}{lucitawh}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{tawh}{tawh})
peach; nectarine

\textbf{\hypertarget{lucipilapilu}{lucipilapilu}} \textit{v.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{pila}{pila}+\allowbreak \hyperlink{pilu}{pilu})
be brightly coloured; be saturated; be colourful; be vibrant; \hyperlink{lucipilapilulon}{ʟᴏᴧ} reflects some wavelengths of light much more than others

\textbf{\hypertarget{lucipilapilulon}{lucipilapilulon}} \textit{n.} (\hyperlink{lucipilapilu}{lucipilapilu}+\allowbreak \hyperlink{lon}{lon})
brightly coloured; saturated; colourful; vibrant

\textbf{\hypertarget{lucipilapilulyan}{lucipilapilulyan}} \textit{n.} (\hyperlink{lucipilapilu}{lucipilapilu}+\allowbreak \hyperlink{lyan}{lyan})
chroma; saturation; brightness

\textbf{\hypertarget{lucipilapiluki}{lucipilapiluki}} \textit{v.} (\hyperlink{lucipilapilu}{lucipilapilu}+\allowbreak \hyperlink{ki}{ki})
colour; ʟєꜱ brightens the colours of ʟᴏᴧ

\textbf{\hypertarget{lucipum}{lucipum}} \textit{n.} (\hyperlink{luci}{luci}+\allowbreak \hyperlink{pum}{pum})
Mars

\textbf{\hypertarget{lucipumak}{lucipumak}} \textit{n.} (\hyperlink{lucipum}{lucipum}+\allowbreak \hyperlink{ak}{ak})
Martian

\textbf{\hypertarget{luso}{luso}} \textit{v.} (Nya. ⟨-luso⟩ [ɽuso])
be skillful; be apt; be effective; be good; \hyperlink{lusolon}{ʟᴏᴧ} is good at causing ʟᴜᴍ

\textbf{\hypertarget{lusolon}{lusolon}} \textit{n.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{lon}{lon})
skillful; apt; effective; good

\textbf{\hypertarget{lusolyan}{lusolyan}} \textit{n.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{lyan}{lyan})
skill level

\textbf{\hypertarget{lusonitatatu}{lusonitatatu}} \textit{v.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{nitatatu}{nitatatu})
be steel; \hyperlink{lusonitatatulon}{ʟᴏᴧ} is made of steel

\textbf{\hypertarget{lusonitatatulon}{lusonitatatulon}} \textit{n.} (\hyperlink{lusonitatatu}{lusonitatatu}+\allowbreak \hyperlink{lon}{lon})
steel

\textbf{\hypertarget{lusocoh}{lusocoh}} \textit{n.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{coh}{coh})
dominant hand

\textbf{\hypertarget{lusoki}{lusoki}} \textit{v.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{ki}{ki})
train; teach; \hyperlink{lusokiles}{ʟєꜱ} makes \hyperlink{lusokilon}{ʟᴏᴧ} become skillful at ʟᴜᴍ

\textbf{\hypertarget{lusokiles}{lusokiles}} \textit{n.} (\hyperlink{lusoki}{lusoki}+\allowbreak \hyperlink{les}{les})
trainer

\textbf{\hypertarget{lusokilon}{lusokilon}} \textit{n.} (\hyperlink{lusoki}{lusoki}+\allowbreak \hyperlink{lon}{lon})
trainee

\textbf{\hypertarget{lusotihutatu}{lusotihutatu}} \textit{v.} (\hyperlink{luso}{luso}+\allowbreak \hyperlink{tihutatu}{tihutatu})
be bronze; \hyperlink{lusotihutatulon}{ʟᴏᴧ} is made of bronze

\textbf{\hypertarget{lusotihutatulon}{lusotihutatulon}} \textit{n.} (\hyperlink{lusotihutatu}{lusotihutatu}+\allowbreak \hyperlink{lon}{lon})
bronze

\textbf{\hypertarget{'lusi}{'lusi}} \textit{n.} (Rus. ⟨рось⟩ [rusʲ])
Kievan Rus’

\textbf{\hypertarget{'lusiak}{'lusiak}} \textit{n.} (\hyperlink{'lusi}{'lusi}+\allowbreak \hyperlink{ak}{ak})
Russian; from Russia

\textbf{\hypertarget{'lusitec}{'lusitec}} \textit{n.} (\hyperlink{'lusi}{'lusi}+\allowbreak \hyperlink{tec}{tec})
Russia

\textbf{\hypertarget{'lusitecwon}{'lusitecwon}} \textit{n.} (\hyperlink{'lusitec}{'lusitec}+\allowbreak \hyperlink{won}{won})
Russian; the Russian people

\textbf{\hypertarget{'lusitectilip}{'lusitectilip}} \textit{n.} (\hyperlink{'lusitec}{'lusitec}+\allowbreak \hyperlink{tilip}{tilip})
Russian; the Russian language

\textbf{\hypertarget{luti}{luti}} \textit{v.} (Epo. ⟨ludi⟩ [ˈludi])
play; \hyperlink{lutilon}{ʟᴏᴧ} is playing \hyperlink{lutilum}{ʟᴜᴍ}

\textbf{\hypertarget{lutilon}{lutilon}} \textit{n.} (\hyperlink{luti}{luti}+\allowbreak \hyperlink{lon}{lon})
player

\textbf{\hypertarget{lutilum}{lutilum}} \textit{n.} (\hyperlink{luti}{luti}+\allowbreak \hyperlink{lum}{lum})
game; sport

\textbf{\hypertarget{'lupitium}{'lupitium}} \textit{n.} (Lat. ⟨rubidium⟩ [rʊbidɪʊ̃])
rubidium

\textbf{\hypertarget{'lupya}{'lupya}} \textit{n.} (Hin. ⟨{\devanagari{}रुपया}⟩ [ɾʊpjɑː])
rupee; ₹; Rs

\textbf{\hypertarget{'lupli}{'lupli}} \textit{n.} (Rus. ⟨рубль⟩ [rublʲ])
ruble; rouble; ₽

\textbf{\hypertarget{lyan}{lyan}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{yan}{yan})
the amount that

\textbf{\hypertarget{lyon}{lyon}} \textit{num.} (Spa. ⟨-illón⟩ [iˈʝon])
×10\textasciicircum{}; -llion; times the radix to the

\textbf{\hypertarget{lyonlim}{lyonlim}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{lim}{lim})
100~000; one hundred thousand; hundred thousand

\textbf{\hypertarget{lyonmenmes}{lyonmenmes}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{mes}{mes})
.000000001; one billionth; billionth; nano-; n

\textbf{\hypertarget{lyonmencah}{lyonmencah}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{cah}{cah})
.000001; one millionth; millionth; micro-; μ

\textbf{\hypertarget{lyonmencahnoluat}{lyonmencahnoluat}} \textit{n.} (\hyperlink{lyonmencah}{lyonmencah}+\allowbreak \hyperlink{noluat}{noluat})
micrometre; micron

\textbf{\hypertarget{lyonmensan}{lyonmensan}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{san}{san})
.001; one thousandth; thousandth; milli-; m

\textbf{\hypertarget{lyonmensan'lithe}{lyonmensan'lithe}} \textit{n.} (\hyperlink{lyonmensan}{lyonmensan}+\allowbreak \hyperlink{'lithe}{'lithe})
millilitre

\textbf{\hypertarget{lyonmensan'methe}{lyonmensan'methe}} \textit{n.} (\hyperlink{lyonmensan}{lyonmensan}+\allowbreak \hyperlink{'methe}{'methe})
millimetre

\textbf{\hypertarget{lyonmensan'kaham}{lyonmensan'kaham}} \textit{n.} (\hyperlink{lyonmensan}{lyonmensan}+\allowbreak \hyperlink{'kaham}{'kaham})
milligram

\textbf{\hypertarget{lyonmenkan}{lyonmenkan}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{kan}{kan})
.1; one tenth; tenth; deci-; d

\textbf{\hypertarget{lyonmenkantos}{lyonmenkantos}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{kantos}{kantos})
.000000000001; one trillionth; trillionth; pico-; p

\textbf{\hypertarget{lyonmentos}{lyonmentos}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{men}{men}+\allowbreak \hyperlink{tos}{tos})
.01; one hundredth; hundredth; centi-; c

\textbf{\hypertarget{lyonmentos'methe}{lyonmentos'methe}} \textit{n.} (\hyperlink{lyonmentos}{lyonmentos}+\allowbreak \hyperlink{'methe}{'methe})
centimetre

\textbf{\hypertarget{lyonmes}{lyonmes}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{mes}{mes})
1~000~000~000; one billion; billion; giga-; G

\textbf{\hypertarget{lyoncah}{lyoncah}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{cah}{cah})
1~000~000; one million; million; mega-; M

\textbf{\hypertarget{lyoncah'kaham}{lyoncah'kaham}} \textit{n.} (\hyperlink{lyoncah}{lyoncah}+\allowbreak \hyperlink{'kaham}{'kaham})
tonne

\textbf{\hypertarget{lyonsan}{lyonsan}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{san}{san})
1~000; one thousand; thousand; kilo-; k

\textbf{\hypertarget{lyonsan'methe}{lyonsan'methe}} \textit{n.} (\hyperlink{lyonsan}{lyonsan}+\allowbreak \hyperlink{'methe}{'methe})
kilometre

\textbf{\hypertarget{lyonsanmamales}{lyonsanmamales}} \textit{n.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{san}{san}+\allowbreak \hyperlink{mamales}{mamales})
great grandparent

\textbf{\hypertarget{lyonsan'kaham}{lyonsan'kaham}} \textit{n.} (\hyperlink{lyonsan}{lyonsan}+\allowbreak \hyperlink{'kaham}{'kaham})
kilogram

\textbf{\hypertarget{lyonfol}{lyonfol}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{fol}{fol})
10~000; ten thousand

\textbf{\hypertarget{lyonfolmamales}{lyonfolmamales}} \textit{n.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{fol}{fol}+\allowbreak \hyperlink{mamales}{mamales})
great great grandparent

\textbf{\hypertarget{lyonkantos}{lyonkantos}} \textit{num.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{kantos}{kantos})
1~000~000~000~000; one trillion; trillion; terra-; T

\textbf{\hypertarget{lyontosmamales}{lyontosmamales}} \textit{n.} (\hyperlink{lyon}{lyon}+\allowbreak \hyperlink{tos}{tos}+\allowbreak \hyperlink{mamales}{mamales})
grandparent

\textbf{\hypertarget{lyot}{lyot}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{yot}{yot})
where (relative)

\textbf{\hypertarget{lyotkweki}{lyotkweki}} \textit{v.} (\hyperlink{l}{l}+\allowbreak \hyperlink{yot}{yot}+\allowbreak \hyperlink{kweki}{kweki})
be present; attend; be around; be strong; be; \hyperlink{lyotkwekilon}{ʟᴏᴧ} is present at ʟᴜᴍ

\textbf{\hypertarget{lyotkwekilon}{lyotkwekilon}} \textit{n.} (\hyperlink{lyotkweki}{lyotkweki}+\allowbreak \hyperlink{lon}{lon})
presence; present; around; strong

\textbf{\hypertarget{lyotkwekinu}{lyotkwekinu}} \textit{v.} (\hyperlink{lyotkweki}{lyotkweki}+\allowbreak \hyperlink{nu}{nu})
dispose; throw away; get rid; get away; remove; leave; ʟєꜱ disposes of \hyperlink{lyotkwekinulon}{ʟᴏᴧ}

\textbf{\hypertarget{lyotkwekinulon}{lyotkwekinulon}} \textit{n.} (\hyperlink{lyotkwekinu}{lyotkwekinu}+\allowbreak \hyperlink{lon}{lon})
trash; garbage

\textbf{\hypertarget{lyotkwekinyo}{lyotkwekinyo}} \textit{v.} (\hyperlink{lyotkweki}{lyotkweki}+\allowbreak \hyperlink{nyo}{nyo})
be absent; be gone; be away; be weak; \hyperlink{lyotkwekinyolon}{ʟᴏᴧ} is absent

\textbf{\hypertarget{lyotkwekinyolon}{lyotkwekinyolon}} \textit{n.} (\hyperlink{lyotkwekinyo}{lyotkwekinyo}+\allowbreak \hyperlink{lon}{lon})
absent; gone; away; weak

\textbf{\hypertarget{lyotkwekiki}{lyotkwekiki}} \textit{v.} (\hyperlink{lyotkweki}{lyotkweki}+\allowbreak \hyperlink{ki}{ki})
summon; bring forth; pull up; place; ʟєꜱ summons ʟᴏᴧ

\textbf{\hypertarget{lyotkwekikilyotkwekinu}{lyotkwekikilyotkwekinu}} \textit{v.} (\hyperlink{lyotkwekiki}{lyotkwekiki}+\allowbreak \hyperlink{lyotkwekinu}{lyotkwekinu})
replace; substitute; swap; ʟєꜱ removes ʟᴜᴍ and replaces it with ʟᴏᴧ

\textbf{\hypertarget{lyotpensi}{lyotpensi}} \textit{v.} (\hyperlink{lyot}{lyot}+\allowbreak \hyperlink{pensi}{pensi})
be found; \hyperlink{lyotpensilon}{ʟᴏᴧ} knows where ʟєꜱ is

\textbf{\hypertarget{lyotpensilon}{lyotpensilon}} \textit{n.} (\hyperlink{lyotpensi}{lyotpensi}+\allowbreak \hyperlink{lon}{lon})
found

\textbf{\hypertarget{lwel}{lwel}} \textit{n.} (\hyperlink{l}{l}+\allowbreak \hyperlink{wel}{wel})
when (relative)

\textbf{\hypertarget{lwelkweki}{lwelkweki}} \textit{v.} (\hyperlink{l}{l}+\allowbreak \hyperlink{wel}{wel}+\allowbreak \hyperlink{kweki}{kweki})
be at; coincide; \hyperlink{lwelkwekilon}{ʟᴏᴧ} happens at the same time as \hyperlink{lwelkwekilum}{ʟᴜᴍ}

\textbf{\hypertarget{lwelkwekilon}{lwelkwekilon}} \textit{n.} (\hyperlink{lwelkweki}{lwelkweki}+\allowbreak \hyperlink{lon}{lon})
event; at

\textbf{\hypertarget{lwelkwekilum}{lwelkwekilum}} \textit{n.} (\hyperlink{lwelkweki}{lwelkweki}+\allowbreak \hyperlink{lum}{lum})
time of occurence

\textbf{\hypertarget{lwa}{lwa}} \textit{v.} (Xho. ⟨-lwa⟩ [lwa])
fight; battle; \hyperlink{lwalon}{ʟᴏᴧ} is in a violent engagement with \hyperlink{lwalum}{ʟᴜᴍ}

\textbf{\hypertarget{lwalon}{lwalon}} \textit{n.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{lon}{lon})
fighter; warrior

\textbf{\hypertarget{lwaluat}{lwaluat}} \textit{n.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{luat}{luat})
weapon

\textbf{\hypertarget{lwalum}{lwalum}} \textit{n.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{lum}{lum})
adversary; opponent

\textbf{\hypertarget{lwalwel}{lwalwel}} \textit{n.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{lwel}{lwel})
battle

\textbf{\hypertarget{lwanu}{lwanu}} \textit{v.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{nu}{nu})
make peace; call off; deescalate; \hyperlink{lwanules}{ʟєꜱ} causes ʟᴏᴧ to stop fighting ʟᴜᴍ

\textbf{\hypertarget{lwanules}{lwanules}} \textit{n.} (\hyperlink{lwanu}{lwanu}+\allowbreak \hyperlink{les}{les})
peace maker

\textbf{\hypertarget{lwaki}{lwaki}} \textit{v.} (\hyperlink{lwa}{lwa}+\allowbreak \hyperlink{ki}{ki})
attack; sick; aggravate; \hyperlink{lwakiles}{ʟєꜱ} causes ʟᴏᴧ to fight ʟᴜᴍ

\textbf{\hypertarget{lwakiles}{lwakiles}} \textit{n.} (\hyperlink{lwaki}{lwaki}+\allowbreak \hyperlink{les}{les})
attacker

\section{W}

\textbf{\hypertarget{'we}{'we}} \textit{n.} (ono. [w])
w; /w/; labial-velar approximant

\textbf{\hypertarget{wel}{wel}} \textit{post.} (Mar. ⟨{\devanagari{}वेळ}⟩ [ˈʋeɭə])
at; on; in; \textit{marks time}

\textbf{\hypertarget{wecai}{wecai}} \textit{v.} (\hyperlink{yohau}{\sout{yohau}})
be hostile; be mean; be harsh; \hyperlink{wecailon}{ʟᴏᴧ} is hostile toward \hyperlink{wecailum}{ʟᴜᴍ}

\textbf{\hypertarget{wecailon}{wecailon}} \textit{n.} (\hyperlink{wecai}{wecai}+\allowbreak \hyperlink{lon}{lon})
hostile; mean; harsh

\textbf{\hypertarget{wecailum}{wecailum}} \textit{n.} (\hyperlink{wecai}{wecai}+\allowbreak \hyperlink{lum}{lum})
enemy; infamous

\textbf{\hypertarget{wecaiki}{wecaiki}} \textit{v.} (\hyperlink{wecai}{wecai}+\allowbreak \hyperlink{ki}{ki})
drive apart; aggravate; \hyperlink{wecaikiles}{ʟєꜱ} makes ʟᴏᴧ become hostile toward ʟᴜᴍ

\textbf{\hypertarget{wecaikiles}{wecaikiles}} \textit{n.} (\hyperlink{wecaiki}{wecaiki}+\allowbreak \hyperlink{les}{les})
enemy-maker

\textbf{\hypertarget{wep}{wep}} \textit{n.} (Ibo. ⟨wep⟩ [wep])
wasp; Apocrita minus Anthophilia and Formicidae

\textbf{\hypertarget{wa}{wa}} \textit{ptcl.} (Cmn. ⟨{\chinese{}哇}⟩ [wa])
wow; how; \textit{neutral exclamative mood}

\textbf{\hypertarget{wale}{wale}} \textit{v.} (\hyperlink{yato}{\sout{yato}})
be similar; be the same; be like; be alike; \hyperlink{walelon}{ʟᴏᴧ} is similar to ʟᴜᴍ

\textbf{\hypertarget{walelon}{walelon}} \textit{n.} (\hyperlink{wale}{wale}+\allowbreak \hyperlink{lon}{lon})
similar; the same; like; alike

\textbf{\hypertarget{waleswa}{waleswa}} \textit{v.} (\hyperlink{wale}{wale}+\allowbreak \hyperlink{swa}{swa})
empathise; share feelings; ʟᴏᴧ empathises with ʟᴜᴍ

\textbf{\hypertarget{waleki}{waleki}} \textit{v.} (\hyperlink{wale}{wale}+\allowbreak \hyperlink{ki}{ki})
converge; make similar; resolve; ʟєꜱ makes ʟᴏᴧ become smilar to ʟᴜᴍ

\textbf{\hypertarget{walepemamalon}{walepemamalon}} \textit{n.} (\hyperlink{wale}{wale}+\allowbreak \hyperlink{pemamalon}{pemamalon})
twin; triplet; quadruplet

\textbf{\hypertarget{wawi}{wawi}} \textit{v.} (Eng. ⟨worry⟩ [ˈwɚɹʷi])
worry; bother; trouble; concern; \hyperlink{wawilum}{ʟᴜᴍ} troubles \hyperlink{wawilon}{ʟᴏᴧ}

\textbf{\hypertarget{wawilon}{wawilon}} \textit{n.} (\hyperlink{wawi}{wawi}+\allowbreak \hyperlink{lon}{lon})
worried; bothered

\textbf{\hypertarget{wawilum}{wawilum}} \textit{n.} (\hyperlink{wawi}{wawi}+\allowbreak \hyperlink{lum}{lum})
problem; trouble; issue

\textbf{\hypertarget{wawiki}{wawiki}} \textit{v.} (\hyperlink{wawi}{wawi}+\allowbreak \hyperlink{ki}{ki})
make worried; make bothered; \hyperlink{wawikiles}{ʟєꜱ} causes ʟᴏᴧ to be bothered by ʟᴜᴍ

\textbf{\hypertarget{wawikiles}{wawikiles}} \textit{n.} (\hyperlink{wawiki}{wawiki}+\allowbreak \hyperlink{les}{les})
\url{https://xkcd.com/1015/}

\textbf{\hypertarget{wan}{wan}} \textit{pn.} (Eng. ⟨one⟩ [wən])
something; someone; one; \textit{indefinite}; a noun not afformentioned

\textbf{\hypertarget{'wan}{'wan}} \textit{n.} (Eng. ⟨rand⟩ [ɹʷɑnd])
rand; R

\textbf{\hypertarget{wan ayf}{wan ayf}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{ayf}{ayf})
in some event

\textbf{\hypertarget{'wanatium}{'wanatium}} \textit{n.} (Lat. ⟨vanadium⟩ [vanadɪʊ̃])
vanadium

\textbf{\hypertarget{wan ial}{wan ial}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{ial}{ial})
for some reason

\textbf{\hypertarget{wan ip}{wan ip}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{ip}{ip})
somehow

\textbf{\hypertarget{wan uat}{wan uat}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{uat}{uat})
with something; somehow

\textbf{\hypertarget{wan yot}{wan yot}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{yot}{yot})
somewhere

\textbf{\hypertarget{wan wel}{wan wel}} \textit{n.} (\hyperlink{wan}{wan}+\allowbreak \hyperlink{wel}{wel})
one day; sometime; at some point

\textbf{\hypertarget{wahauti}{wahauti}} \textit{v.} (\hyperlink{wa}{wa}+\allowbreak \hyperlink{hau}{hau}+\allowbreak \hyperlink{ti}{ti})
complain; denounce; condemn; \hyperlink{wahautiles}{ʟєꜱ} makes a negative utterance of \hyperlink{wahautilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{wahautiles}{wahautiles}} \textit{n.} (\hyperlink{wahauti}{wahauti}+\allowbreak \hyperlink{les}{les})
complainer

\textbf{\hypertarget{wahautilum}{wahautilum}} \textit{n.} (\hyperlink{wahauti}{wahauti}+\allowbreak \hyperlink{lum}{lum})
complaint; denouncee

\textbf{\hypertarget{wacaiti}{wacaiti}} \textit{v.} (\hyperlink{wa}{wa}+\allowbreak \hyperlink{cai}{cai}+\allowbreak \hyperlink{ti}{ti})
praise; celebrate; \hyperlink{wacaitiles}{ʟєꜱ} makes a positive utterance of \hyperlink{wacaitilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{wacaitiles}{wacaitiles}} \textit{n.} (\hyperlink{wacaiti}{wacaiti}+\allowbreak \hyperlink{les}{les})
praiser

\textbf{\hypertarget{wacaitilum}{wacaitilum}} \textit{n.} (\hyperlink{wacaiti}{wacaiti}+\allowbreak \hyperlink{lum}{lum})
praised; occasion

\textbf{\hypertarget{'wacintontisi}{'wacintontisi}} \textit{n.} (Eng. ⟨Washington D.C.⟩ [ˈwɑʃiŋtɪn diː siː])
Washington D.C.; Washington

\textbf{\hypertarget{'wake}{'wake}} \textit{n.} (Ara. ⟨{\arabics{}واقع‎}⟩ [wɑːqeʔ])
Vega

\textbf{\hypertarget{wata}{wata}} \textit{v.} (\hyperlink{yala}{\sout{yala}})
be slow; be gradual; be periodic; \hyperlink{watalon}{ʟᴏᴧ} progresses, oscillates, or decays slowly

\textbf{\hypertarget{'wataiko}{'wataiko}} \textit{n.} (Jpn. ⟨{\japanese{}和太鼓}⟩ [ɰadaikɔː])
taiko; taiko drum

\textbf{\hypertarget{watalon}{watalon}} \textit{n.} (\hyperlink{wata}{wata}+\allowbreak \hyperlink{lon}{lon})
slow; gradual; periodic

\textbf{\hypertarget{watalyan}{watalyan}} \textit{n.} (\hyperlink{wata}{wata}+\allowbreak \hyperlink{lyan}{lyan})
period; time constant

\textbf{\hypertarget{watamamul}{watamamul}} \textit{n.} (\hyperlink{wata}{wata}+\allowbreak \hyperlink{mamul}{mamul})
sloth

\textbf{\hypertarget{watafepucocalu}{watafepucocalu}} \textit{v.} (\hyperlink{wata}{wata}+\allowbreak \hyperlink{fepucocalu}{fepucocalu})
jog; ʟᴏᴧ jogs on ʟᴜᴍ

\textbf{\hypertarget{wati}{wati}} \textit{v.} (\hyperlink{wa}{wa}+\allowbreak \hyperlink{ti}{ti})
exclaim; \hyperlink{watiles}{ʟєꜱ} makes an exclamatory utterance of \hyperlink{watilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{'watian}{'watian}} \textit{n.} (Eng. ⟨radian⟩ [ˈɹʷeɪdiɪn])
radian; rad

\textbf{\hypertarget{watiles}{watiles}} \textit{n.} (\hyperlink{wati}{wati}+\allowbreak \hyperlink{les}{les})
exclaimer

\textbf{\hypertarget{watilum}{watilum}} \textit{n.} (\hyperlink{wati}{wati}+\allowbreak \hyperlink{lum}{lum})
exclamation

\textbf{\hypertarget{'watikana}{'watikana}} \textit{n.} (Lat. ⟨Vāticāna⟩ [vatiˈkaːna])
Vatican Hill

\textbf{\hypertarget{'watikanaak}{'watikanaak}} \textit{n.} (\hyperlink{'watikana}{'watikana}+\allowbreak \hyperlink{ak}{ak})
Vatican; of the Vatican City

\textbf{\hypertarget{'watikanatec}{'watikanatec}} \textit{n.} (\hyperlink{'watikana}{'watikana}+\allowbreak \hyperlink{tec}{tec})
Vatican City

\textbf{\hypertarget{'wolfamium}{'wolfamium}} \textit{n.} (Lat. ⟨wolframium⟩ [wɔlframɪʊ̃])
tungsten; wolfram

\textbf{\hypertarget{won}{won}} \textit{n.} (Jav. ⟨wong⟩ [wɔŋ])
person; woman; man; human; Homo sapiens

\textbf{\hypertarget{wonak}{wonak}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{ak}{ak})
personal; humanistic; domesticated

\textbf{\hypertarget{wonmocaki}{wonmocaki}} \textit{v.} (\hyperlink{won}{won}+\allowbreak \hyperlink{mocaki}{mocaki})
perform; play; \hyperlink{wonmocakiles}{ʟєꜱ} performs \hyperlink{wonmocakilum}{ʟᴜᴍ} for ʟᴏᴧ

\textbf{\hypertarget{wonmocakiles}{wonmocakiles}} \textit{n.} (\hyperlink{wonmocaki}{wonmocaki}+\allowbreak \hyperlink{les}{les})
player; performer; actor

\textbf{\hypertarget{wonmocakilum}{wonmocakilum}} \textit{n.} (\hyperlink{wonmocaki}{wonmocaki}+\allowbreak \hyperlink{lum}{lum})
performance; show; play

\textbf{\hypertarget{wonmocakilyot}{wonmocakilyot}} \textit{n.} (\hyperlink{wonmocaki}{wonmocaki}+\allowbreak \hyperlink{lyot}{lyot})
theatre; amphitheater

\textbf{\hypertarget{wonmyawf}{wonmyawf}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{myawf}{myawf})
cat

\textbf{\hypertarget{wonhihin}{wonhihin}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{hihin}{hihin})
horse

\textbf{\hypertarget{wonhulilon}{wonhulilon}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{hulilon}{hulilon})
legacy

\textbf{\hypertarget{wonsulak}{wonsulak}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{sulak}{sulak})
pig; pork

\textbf{\hypertarget{wonsun}{wonsun}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{sun}{sun})
Sol; The Sun

\textbf{\hypertarget{wonfolmo}{wonfolmo}} \textit{v.} (\hyperlink{won}{won}+\allowbreak \hyperlink{folmo}{folmo})
be humanoid; be human-shaped; \hyperlink{wonfolmolon}{ʟᴏᴧ} is a bipedal entity with two legs, two arms, and a head

\textbf{\hypertarget{wonfolmolon}{wonfolmolon}} \textit{n.} (\hyperlink{wonfolmo}{wonfolmo}+\allowbreak \hyperlink{lon}{lon})
humanoid; human-shaped

\textbf{\hypertarget{wonfik}{wonfik}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{fik}{fik})
Luna; The Moon

\textbf{\hypertarget{won'kalasias}{won'kalasias}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{'kalasias}{'kalasias})
Milky Way

\textbf{\hypertarget{won'kalasiasak}{won'kalasiasak}} \textit{n.} (\hyperlink{won'kalasias}{won'kalasias}+\allowbreak \hyperlink{ak}{ak})
Milky

\textbf{\hypertarget{wonki}{wonki}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{ki}{ki})
personify; humanise; anthropomorphise

\textbf{\hypertarget{wonkio}{wonkio}} \textit{v.} (\hyperlink{won}{won}+\allowbreak \hyperlink{kio}{kio})
be plastic; \hyperlink{wonkiolon}{ʟᴏᴧ} is made of plastic

\textbf{\hypertarget{wonkiolon}{wonkiolon}} \textit{n.} (\hyperlink{wonkio}{wonkio}+\allowbreak \hyperlink{lon}{lon})
plastic

\textbf{\hypertarget{wonpawaf}{wonpawaf}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{pawaf}{pawaf})
dog

\textbf{\hypertarget{wonpatolon}{wonpatolon}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{patolon}{patolon})
ceramic

\textbf{\hypertarget{wonpum}{wonpum}} \textit{n.} (\hyperlink{won}{won}+\allowbreak \hyperlink{pum}{pum})
Earth

\textbf{\hypertarget{wonpumak}{wonpumak}} \textit{n.} (\hyperlink{wonpum}{wonpum}+\allowbreak \hyperlink{ak}{ak})
global; earthling; terran

\textbf{\hypertarget{wompa}{wompa}} \textit{v.} (ono. [wumba])
rumble; flicker; ʟєꜱ makes \hyperlink{wompalon}{ʟᴏᴧ}

\textbf{\hypertarget{wompalon}{wompalon}} \textit{n.} (\hyperlink{wompa}{wompa}+\allowbreak \hyperlink{lon}{lon})
rumble; flicker; noisy, low-pitched sound or action

\textbf{\hypertarget{'wotka}{'wotka}} \textit{n.} (Rus. ⟨водка⟩ [ˈvotkə])
vodka

\textbf{\hypertarget{'wino}{'wino}} \textit{n.} (Kat. ⟨{\georgian{}ღვინო}⟩ [ɣvinɔ])
wine

\textbf{\hypertarget{wicon}{wicon}} \textit{n.} (Eng. ⟨region⟩ [ˈɹʷiːd͡ʒən])
region; volume; interval; continuous locus bounded on all sides

\textbf{\hypertarget{wiconak}{wiconak}} \textit{n.} (\hyperlink{wicon}{wicon}+\allowbreak \hyperlink{ak}{ak})
regional; volumetric; periodic

\textbf{\hypertarget{'wicnu}{'wicnu}} \textit{n.} (San. ⟨{\devanagari{}विष्णु}⟩ [ʋɪʂɳʊ])
Vishnu

\textbf{\hypertarget{'wicnufitilip}{'wicnufitilip}} \textit{n.} (\hyperlink{'wicnu}{'wicnu}+\allowbreak \hyperlink{fitilip}{fitilip})
Vaishnavism

\textbf{\hypertarget{'wicnufitilipak}{'wicnufitilipak}} \textit{n.} (\hyperlink{'wicnufitilip}{'wicnufitilip}+\allowbreak \hyperlink{ak}{ak})
Vaishnist; of Vaishnavism

\textbf{\hypertarget{'wicnufitilipwon}{'wicnufitilipwon}} \textit{n.} (\hyperlink{'wicnufitilip}{'wicnufitilip}+\allowbreak \hyperlink{won}{won})
Vaishnava; Vaishnavite; followers of Vishnu

\textbf{\hypertarget{wit}{wit}} \textit{n.} (Eng. ⟨wheat⟩ [wiːt])
wheat; Triticum

\textbf{\hypertarget{witsekal}{witsekal}} \textit{n.} (\hyperlink{wit}{wit}+\allowbreak \hyperlink{sekal}{sekal})
triticale

\textbf{\hypertarget{'wipaplikan}{'wipaplikan}} \textit{n.} (Eng. ⟨republican⟩ [ɹʷɪˈpʰɜblɪkɪn])
Republican Party (United States); the Grand Old Party

\textbf{\hypertarget{'wulpes}{'wulpes}} \textit{n.} (Lat. ⟨vulpes⟩ [ˈwʊɫpɛs])
fox; dog; vixen; Vulpes

\section{Λ}

\textbf{\hypertarget{ne}{ne}} \textit{v.} (Cmn. ⟨{\chinese{}内}⟩ [neɪ̯˥˩])
be inside; be in; contain; be inner; be central; be in the middle; \hyperlink{nelon}{ʟᴏᴧ} is inside \hyperlink{nelum}{ʟᴜᴍ}

\textbf{\hypertarget{ne'aflika}{ne'aflika}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{'aflika}{'aflika})
Central Africa

\textbf{\hypertarget{ne'aflikatec}{ne'aflikatec}} \textit{n.} (\hyperlink{ne'aflika}{ne'aflika}+\allowbreak \hyperlink{tec}{tec})
Central African Republic

\textbf{\hypertarget{ne'aflikatecwon}{ne'aflikatecwon}} \textit{n.} (\hyperlink{ne'aflikatec}{ne'aflikatec}+\allowbreak \hyperlink{won}{won})
Central African; the Central African people

\textbf{\hypertarget{'neon}{'neon}} \textit{n.} (Lat. ⟨neon⟩ [neɔ̃])
neon

\textbf{\hypertarget{'neopatwa}{'neopatwa}} \textit{n.} (Npt. ⟨Neo Patwa⟩ [neˈo paˈtwa])
Neo Patwa; Neo Patwah

\textbf{\hypertarget{'neopatwaak}{'neopatwaak}} \textit{n.} (\hyperlink{'neopatwa}{'neopatwa}+\allowbreak \hyperlink{ak}{ak})
Neo Patwa; in Neo Patwa

\textbf{\hypertarget{'neopatwawon}{'neopatwawon}} \textit{n.} (\hyperlink{'neopatwa}{'neopatwa}+\allowbreak \hyperlink{won}{won})
Neo Patwist; Neo Patwa speakers

\textbf{\hypertarget{nelon}{nelon}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{lon}{lon})
indoors; room; content; center; middle; heart; bowels; inside; in; inner; central; in the middle

\textbf{\hypertarget{nelum}{nelum}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{lum}{lum})
container

\textbf{\hypertarget{nelyan}{nelyan}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{lyan}{lyan})
innerness

\textbf{\hypertarget{nemuctayl}{nemuctayl}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{muctayl}{muctayl})
subcontinent; subsection of a continent bounded by divisors of geographical and cultural significance, e.g. Europe, South Asia

\textbf{\hypertarget{nehu}{nehu}} \textit{v.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{hu}{hu})
be private; ʟᴜᴍ is privately concealed from \hyperlink{nehulon}{ʟᴏᴧ}

\textbf{\hypertarget{nehulon}{nehulon}} \textit{n.} (\hyperlink{nehu}{nehu}+\allowbreak \hyperlink{lon}{lon})
private

\textbf{\hypertarget{nesicalwel}{nesicalwel}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{sicalwel}{sicalwel})
midnight

\textbf{\hypertarget{nefilalum}{nefilalum}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{filalum}{filalum})
equator

\textbf{\hypertarget{nefilalum'kine}{nefilalum'kine}} \textit{n.} (\hyperlink{nefilalum}{nefilalum}+\allowbreak \hyperlink{'kine}{'kine})
Equatorial Guinea; the Republic of Equatorial Guinea

\textbf{\hypertarget{nefilalum'kinewon}{nefilalum'kinewon}} \textit{n.} (\hyperlink{nefilalum'kine}{nefilalum'kine}+\allowbreak \hyperlink{won}{won})
Equatorial Guinean; Equatoguinean; the Equatorial Guinean people

\textbf{\hypertarget{nefilalum'kineak}{nefilalum'kineak}} \textit{n.} (\hyperlink{nefilalum'kine}{nefilalum'kine}+\allowbreak \hyperlink{ak}{ak})
Equatorial Guinean; from Equatorial Guinea

\textbf{\hypertarget{nefuhalwel}{nefuhalwel}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{fuhalwel}{fuhalwel})
noon; midday

\textbf{\hypertarget{neflu}{neflu}} \textit{v.} (\hyperlink{kosti}{\sout{kosti}})
be cheap; \hyperlink{neflulon}{ʟᴏᴧ} does not cost a lot

\textbf{\hypertarget{neflulon}{neflulon}} \textit{n.} (\hyperlink{neflu}{neflu}+\allowbreak \hyperlink{lon}{lon})
cheap

\textbf{\hypertarget{nefluki}{nefluki}} \textit{v.} (\hyperlink{neflu}{neflu}+\allowbreak \hyperlink{ki}{ki})
discount; mark down; ʟєꜱ decreases the cost of ʟᴏᴧ

\textbf{\hypertarget{nefwes}{nefwes}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{fwes}{fwes})
parenthetical; side note

\textbf{\hypertarget{neki}{neki}} \textit{v.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{ki}{ki})
enter; insert; put in; go in; ʟєꜱ moves ʟᴏᴧ into ʟᴜᴍ

\textbf{\hypertarget{nekikoki}{nekikoki}} \textit{v.} (\hyperlink{neki}{neki}+\allowbreak \hyperlink{koki}{koki})
go through; ʟᴏᴧ moves into and then out of \hyperlink{nekikokilum}{ʟᴜᴍ}

\textbf{\hypertarget{nekikokilum}{nekikokilum}} \textit{n.} (\hyperlink{nekikoki}{nekikoki}+\allowbreak \hyperlink{lum}{lum})
tube; hallway; corridor

\textbf{\hypertarget{nekwelon}{nekwelon}} \textit{n.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{kwelon}{kwelon})
province; state; territory; constituent country; sub-polity

\textbf{\hypertarget{nekwelonak}{nekwelonak}} \textit{n.} (\hyperlink{nekwelon}{nekwelon}+\allowbreak \hyperlink{ak}{ak})
provincial; state; territorial

\textbf{\hypertarget{neta}{neta}} \textit{v.} (Epo. ⟨neta⟩ [ˈneta])
be neat; be orderly; be organised; be clean; be tidy; \hyperlink{netalon}{ʟᴏᴧ} is neat

\textbf{\hypertarget{'netalan}{'netalan}} \textit{n.} (Nld. ⟨Nederland⟩ [neːdərlɑnt])
Netherlands; Holland; the Low Countries

\textbf{\hypertarget{'netalanak}{'netalanak}} \textit{n.} (\hyperlink{'netalan}{'netalan}+\allowbreak \hyperlink{ak}{ak})
Dutch; Netherlandic; from the Netherlands

\textbf{\hypertarget{'netalanwon}{'netalanwon}} \textit{n.} (\hyperlink{'netalan}{'netalan}+\allowbreak \hyperlink{won}{won})
Dutch; Netherlander; the Dutch people

\textbf{\hypertarget{'netalankwelyot}{'netalankwelyot}} \textit{n.} (\hyperlink{'netalan}{'netalan}+\allowbreak \hyperlink{kwelyot}{kwelyot})
the Low Countries; the Low Lands; the Netherlands

\textbf{\hypertarget{'netalantilip}{'netalantilip}} \textit{n.} (\hyperlink{'netalan}{'netalan}+\allowbreak \hyperlink{tilip}{tilip})
Dutch; the Dutch language

\textbf{\hypertarget{netalon}{netalon}} \textit{n.} (\hyperlink{neta}{neta}+\allowbreak \hyperlink{lon}{lon})
neat; orderly; organised; clean; tidy

\textbf{\hypertarget{netalyan}{netalyan}} \textit{n.} (\hyperlink{neta}{neta}+\allowbreak \hyperlink{lyan}{lyan})
order; neatness; organisation; cleanliness

\textbf{\hypertarget{netacoto}{netacoto}} \textit{v.} (\hyperlink{neta}{neta}+\allowbreak \hyperlink{coto}{coto})
be woven; \hyperlink{netacotolon}{ʟᴏᴧ} is woven

\textbf{\hypertarget{netacotolon}{netacotolon}} \textit{n.} (\hyperlink{netacoto}{netacoto}+\allowbreak \hyperlink{lon}{lon})
woven

\textbf{\hypertarget{netacotonu}{netacotonu}} \textit{v.} (\hyperlink{netacoto}{netacoto}+\allowbreak \hyperlink{nu}{nu})
unweave; ʟєꜱ unweaves ʟᴏᴧ

\textbf{\hypertarget{netacotoki}{netacotoki}} \textit{v.} (\hyperlink{netacoto}{netacoto}+\allowbreak \hyperlink{ki}{ki})
weave; \hyperlink{netacotokiles}{ʟєꜱ} weaves ʟᴏᴧ

\textbf{\hypertarget{netacotokiles}{netacotokiles}} \textit{n.} (\hyperlink{netacotoki}{netacotoki}+\allowbreak \hyperlink{les}{les})
weaver

\textbf{\hypertarget{netaki}{netaki}} \textit{v.} (\hyperlink{neta}{neta}+\allowbreak \hyperlink{ki}{ki})
order; organise; clean; tidy; sort; put in order; structure; finalise; \hyperlink{netakiles}{ʟєꜱ} puts ʟᴏᴧ in order

\textbf{\hypertarget{netakiles}{netakiles}} \textit{n.} (\hyperlink{netaki}{netaki}+\allowbreak \hyperlink{les}{les})
organiser; cleaner; tidier

\textbf{\hypertarget{netakiluat}{netakiluat}} \textit{n.} (\hyperlink{netaki}{netaki}+\allowbreak \hyperlink{luat}{luat})
organisation tool

\textbf{\hypertarget{'nepal}{'nepal}} \textit{n.} (Nep. ⟨{\devanagari{}नेपाल}⟩ [neˈpal])
Nepal

\textbf{\hypertarget{'nepalak}{'nepalak}} \textit{n.} (\hyperlink{'nepal}{'nepal}+\allowbreak \hyperlink{ak}{ak})
Nepalese; Nepali; from Nepal

\textbf{\hypertarget{'nepalwon}{'nepalwon}} \textit{n.} (\hyperlink{'nepal}{'nepal}+\allowbreak \hyperlink{won}{won})
Nepalese; Nepali; the Nepalese people

\textbf{\hypertarget{'nepaltilip}{'nepaltilip}} \textit{n.} (\hyperlink{'nepal}{'nepal}+\allowbreak \hyperlink{tilip}{tilip})
Nepali; the Nepali language

\textbf{\hypertarget{nepuci}{nepuci}} \textit{v.} (\hyperlink{ne}{ne}+\allowbreak \hyperlink{puci}{puci})
squeeze; compress; ʟєꜱ squeezes ʟᴏᴧ

\textbf{\hypertarget{na}{na}} \textit{ptcl.} (Hin. ⟨{\devanagari{}ना}⟩ [nɑː])
>>; let; do it.; \textit{imperative mood}

\textbf{\hypertarget{'na}{'na}} \textit{n.} (ono. [n])
n; /n/; alveolar nasal

\textbf{\hypertarget{'naoelo}{'naoelo}} \textit{n.} (Nau. ⟨Naoero⟩ [naoero])
Nauru; Pleasant Island (landmass)

\textbf{\hypertarget{'naoeloak}{'naoeloak}} \textit{n.} (\hyperlink{'naoelo}{'naoelo}+\allowbreak \hyperlink{ak}{ak})
Nauruan; from Nauru

\textbf{\hypertarget{'naoelowon}{'naoelowon}} \textit{n.} (\hyperlink{'naoelo}{'naoelo}+\allowbreak \hyperlink{won}{won})
Nauruan; the Nauruan people

\textbf{\hypertarget{'naoelotec}{'naoelotec}} \textit{n.} (\hyperlink{'naoelo}{'naoelo}+\allowbreak \hyperlink{tec}{tec})
Nauru; the Republic of Nauru

\textbf{\hypertarget{'naoelotilip}{'naoelotilip}} \textit{n.} (\hyperlink{'naoelo}{'naoelo}+\allowbreak \hyperlink{tilip}{tilip})
Nauruan; the Nauruan language

\textbf{\hypertarget{'nayciwia}{'nayciwia}} \textit{n.} (Eng. ⟨Nigeria⟩ [naɪ̯ˈd͡ʒɪɹʷiə])
Nigeria; the Federal Republic of Nigeria

\textbf{\hypertarget{'nayciwiaak}{'nayciwiaak}} \textit{n.} (\hyperlink{'nayciwia}{'nayciwia}+\allowbreak \hyperlink{ak}{ak})
Nigerian; from Nigeria

\textbf{\hypertarget{'nayciwiawon}{'nayciwiawon}} \textit{n.} (\hyperlink{'nayciwia}{'nayciwia}+\allowbreak \hyperlink{won}{won})
Nigerian; the Nigerian people

\textbf{\hypertarget{nalkas}{nalkas}} \textit{n.} (Spa. ⟨nalgas⟩ [ˈnalɣas])
buttocks; butt; bum; soft region between the back of an animal’s legs and torso

\textbf{\hypertarget{nalkasak}{nalkasak}} \textit{n.} (\hyperlink{nalkas}{nalkas}+\allowbreak \hyperlink{ak}{ak})
gluteal; posterial

\textbf{\hypertarget{nalkaskutilon}{nalkaskutilon}} \textit{n.} (\hyperlink{nalkas}{nalkas}+\allowbreak \hyperlink{kutilon}{kutilon})
feces; excrement; poop; manure; guano

\textbf{\hypertarget{nalkaskutilonec}{nalkaskutilonec}} \textit{n.} (\hyperlink{nalkaskutilon}{nalkaskutilon}+\allowbreak \hyperlink{ec}{ec})
rectum

\textbf{\hypertarget{nalkaskutilonkoki}{nalkaskutilonkoki}} \textit{v.} (\hyperlink{nalkaskutilon}{nalkaskutilon}+\allowbreak \hyperlink{koki}{koki})
defecate; poop; ʟєꜱ defecates out ʟᴏᴧ

\textbf{\hypertarget{nalkaskutilonkokilyot}{nalkaskutilonkokilyot}} \textit{n.} (\hyperlink{nalkaskutilon}{nalkaskutilon}+\allowbreak \hyperlink{kokilyot}{kokilyot})
anus; asshole

\textbf{\hypertarget{'nawatla}{'nawatla}} \textit{n.} (Nah. ⟨Nahuatl⟩ [ˈnaːwat͡ɬ])
Nahuatl; the Nahuatl language

\textbf{\hypertarget{'nawatlaak}{'nawatlaak}} \textit{n.} (\hyperlink{'nawatla}{'nawatla}+\allowbreak \hyperlink{ak}{ak})
Nahua; of the Nahuas

\textbf{\hypertarget{'nawatlawon}{'nawatlawon}} \textit{n.} (\hyperlink{'nawatla}{'nawatla}+\allowbreak \hyperlink{won}{won})
Nahua; Aztec; the Nahua people

\textbf{\hypertarget{'nawatlatec}{'nawatlatec}} \textit{n.} (\hyperlink{'nawatla}{'nawatla}+\allowbreak \hyperlink{tec}{tec})
Aztec Empire

\textbf{\hypertarget{nawtil}{nawtil}} \textit{n.} (Epo. ⟨naŭtilo⟩ [nawˈtilo])
nautilus; Nautilidae

\textbf{\hypertarget{namo}{namo}} \textit{v.} (\hyperlink{kape}{\sout{kape}})
ignore; disregard; ʟᴏᴧ pays little attention to ʟᴜᴍ

\textbf{\hypertarget{namooyemocakilum}{namooyemocakilum}} \textit{n.} (\hyperlink{namo}{namo}+\allowbreak \hyperlink{oyemocakilum}{oyemocakilum})
background music; soundtrack

\textbf{\hypertarget{namoki}{namoki}} \textit{v.} (\hyperlink{namo}{namo}+\allowbreak \hyperlink{ki}{ki})
distract; ʟєꜱ makes ʟᴏᴧ stop paying attention to ʟᴜᴍ

\textbf{\hypertarget{'namipia}{'namipia}} \textit{n.} (Naq. ⟨namib⟩ [naˈmip])
Namib desert

\textbf{\hypertarget{'namipiaak}{'namipiaak}} \textit{n.} (\hyperlink{'namipia}{'namipia}+\allowbreak \hyperlink{ak}{ak})
Namibian; from Namibia

\textbf{\hypertarget{'namipiawon}{'namipiawon}} \textit{n.} (\hyperlink{'namipia}{'namipia}+\allowbreak \hyperlink{won}{won})
Namibian; the Namibian people

\textbf{\hypertarget{'namipiatec}{'namipiatec}} \textit{n.} (\hyperlink{'namipia}{'namipia}+\allowbreak \hyperlink{tec}{tec})
Namibia; Republic of Namibia

\textbf{\hypertarget{nak}{nak}} \textit{num.} (\hyperlink{kan}{\sout{kan}})
F; fifteen; only used for hexadecimal

\textbf{\hypertarget{nakak}{nakak}} \textit{n.} (\hyperlink{nak}{nak}+\allowbreak \hyperlink{ak}{ak})
fifteenth

\textbf{\hypertarget{nata}{nata}} \textit{v.} (\hyperlink{kala}{\sout{kala}})
be gentle; be flat; be shallow; be gradual; \hyperlink{natalon}{ʟᴏᴧ} is not very steep

\textbf{\hypertarget{natalon}{natalon}} \textit{n.} (\hyperlink{nata}{nata}+\allowbreak \hyperlink{lon}{lon})
gentle; flat; shallow; gradual

\textbf{\hypertarget{nataki}{nataki}} \textit{v.} (\hyperlink{nata}{nata}+\allowbreak \hyperlink{ki}{ki})
flatten; right; ʟєꜱ makes ʟᴏᴧ less steep

\textbf{\hypertarget{nati}{nati}} \textit{v.} (\hyperlink{na}{na}+\allowbreak \hyperlink{ti}{ti})
tell; implore; command; instruct; lead; \hyperlink{natiles}{ʟєꜱ} tells \hyperlink{natilon}{ʟᴏᴧ} to make \hyperlink{natilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{natiles}{natiles}} \textit{n.} (\hyperlink{nati}{nati}+\allowbreak \hyperlink{les}{les})
boss; commander

\textbf{\hypertarget{natilon}{natilon}} \textit{n.} (\hyperlink{nati}{nati}+\allowbreak \hyperlink{lon}{lon})
instructee

\textbf{\hypertarget{natilum}{natilum}} \textit{n.} (\hyperlink{nati}{nati}+\allowbreak \hyperlink{lum}{lum})
command; instruction

\textbf{\hypertarget{'natiwitas}{'natiwitas}} \textit{n.} (Lat. ⟨nātīvitās⟩ [naːˈtiːwɪtaːs])
Christmas

\textbf{\hypertarget{natula}{natula}} \textit{v.} (Epo. ⟨natura⟩ [naˈtura])
be natural; \hyperlink{natulalon}{ʟᴏᴧ} is natural

\textbf{\hypertarget{natulalon}{natulalon}} \textit{n.} (\hyperlink{natula}{natula}+\allowbreak \hyperlink{lon}{lon})
nature; natural

\textbf{\hypertarget{natulaki}{natulaki}} \textit{v.} (\hyperlink{natula}{natula}+\allowbreak \hyperlink{ki}{ki})
naturalise; ʟєꜱ makes ʟᴏᴧ become natural

\textbf{\hypertarget{natulapet}{natulapet}} \textit{n.} (\hyperlink{natula}{natula}+\allowbreak \hyperlink{pet}{pet})
sea beet; wild spinach

\textbf{\hypertarget{no}{no}} \textit{v.} (Eng. ⟨know⟩ [noʊ̯])
know; be informed; be educated; \hyperlink{nolon}{ʟᴏᴧ} remembers \hyperlink{nolum}{ʟᴜᴍ}, believes and thinks it to be true, and correctly understands why it is true

\textbf{\hypertarget{nolon}{nolon}} \textit{n.} (\hyperlink{no}{no}+\allowbreak \hyperlink{lon}{lon})
knower; smart; informed; educated

\textbf{\hypertarget{noluat}{noluat}} \textit{n.} (\hyperlink{no}{no}+\allowbreak \hyperlink{luat}{luat})
meter; measure; readout; measuring device

\textbf{\hypertarget{nolum}{nolum}} \textit{n.} (\hyperlink{no}{no}+\allowbreak \hyperlink{lum}{lum})
knowledge

\textbf{\hypertarget{'nolka}{'nolka}} \textit{n.} (Nor. ⟨Norge⟩ [nʊɾɡə])
Norway

\textbf{\hypertarget{'nolkaak}{'nolkaak}} \textit{n.} (\hyperlink{'nolka}{'nolka}+\allowbreak \hyperlink{ak}{ak})
Norwegian; from Norway

\textbf{\hypertarget{'nolkawon}{'nolkawon}} \textit{n.} (\hyperlink{'nolka}{'nolka}+\allowbreak \hyperlink{won}{won})
Norwegian; the Norwegian people

\textbf{\hypertarget{'nolkatilip}{'nolkatilip}} \textit{n.} (\hyperlink{'nolka}{'nolka}+\allowbreak \hyperlink{tilip}{tilip})
Norwegian; the Norwegian language

\textbf{\hypertarget{'nowial}{'nowial}} \textit{n.} (Nov. ⟨novial⟩ [novial])
Novial

\textbf{\hypertarget{'nowialak}{'nowialak}} \textit{n.} (\hyperlink{'nowial}{'nowial}+\allowbreak \hyperlink{ak}{ak})
Novial; in Novial

\textbf{\hypertarget{'nowialwon}{'nowialwon}} \textit{n.} (\hyperlink{'nowial}{'nowial}+\allowbreak \hyperlink{won}{won})
Novialist; Novial speakers

\textbf{\hypertarget{non}{non}} \textit{n.} (Nya. ⟨ng’ona⟩ [ŋona])
crocodilian; crocodile; alligator; Crocodilia

\textbf{\hypertarget{nonu}{nonu}} \textit{v.} (\hyperlink{no}{no}+\allowbreak \hyperlink{nu}{nu})
unteach; unlearn; confound; \hyperlink{nonules}{ʟєꜱ} makes \hyperlink{nonulum}{ʟᴜᴍ} unlearn what they thought they knew about ʟᴏᴧ

\textbf{\hypertarget{nonules}{nonules}} \textit{n.} (\hyperlink{nonu}{nonu}+\allowbreak \hyperlink{les}{les})
unteacher

\textbf{\hypertarget{nonulum}{nonulum}} \textit{n.} (\hyperlink{nonu}{nonu}+\allowbreak \hyperlink{lum}{lum})
unlearner

\textbf{\hypertarget{nonyo}{nonyo}} \textit{v.} (\hyperlink{no}{no}+\allowbreak \hyperlink{nyo}{nyo})
be unknown; ʟᴏᴧ does not know \hyperlink{nonyolum}{ʟᴜᴍ}

\textbf{\hypertarget{nonyolum}{nonyolum}} \textit{n.} (\hyperlink{nonyo}{nonyo}+\allowbreak \hyperlink{lum}{lum})
unknown

\textbf{\hypertarget{nonfut}{nonfut}} \textit{n.} (\hyperlink{non}{non}+\allowbreak \hyperlink{fut}{fut})
avocado

\textbf{\hypertarget{nosyon}{nosyon}} \textit{n.} (Spa. ⟨noción⟩ [noˈsjon])
notion; idea; information; data; number; intangible facts or falsehoods

\textbf{\hypertarget{nosyonak}{nosyonak}} \textit{n.} (\hyperlink{nosyon}{nosyon}+\allowbreak \hyperlink{ak}{ak})
conceptual; ideal; theoretical; informational

\textbf{\hypertarget{nosyonmailyot}{nosyonmailyot}} \textit{n.} (\hyperlink{nosyon}{nosyon}+\allowbreak \hyperlink{mailyot}{mailyot})
call shop

\textbf{\hypertarget{noki}{noki}} \textit{v.} (\hyperlink{no}{no}+\allowbreak \hyperlink{ki}{ki})
teach; learn; study; inform; \hyperlink{nokiles}{ʟєꜱ} teaches ʟᴜᴍ to \hyperlink{nokilon}{ʟᴏᴧ}

\textbf{\hypertarget{nokiles}{nokiles}} \textit{n.} (\hyperlink{noki}{noki}+\allowbreak \hyperlink{les}{les})
teacher; professor; master

\textbf{\hypertarget{nokilon}{nokilon}} \textit{n.} (\hyperlink{noki}{noki}+\allowbreak \hyperlink{lon}{lon})
student; learner

\textbf{\hypertarget{nokilyot}{nokilyot}} \textit{n.} (\hyperlink{noki}{noki}+\allowbreak \hyperlink{lyot}{lyot})
school; college; university

\textbf{\hypertarget{nokilwel}{nokilwel}} \textit{n.} (\hyperlink{noki}{noki}+\allowbreak \hyperlink{lwel}{lwel})
lesson; education

\textbf{\hypertarget{nokisoma}{nokisoma}} \textit{v.} (\hyperlink{noki}{noki}+\allowbreak \hyperlink{soma}{soma})
do pedagogy; \hyperlink{nokisomales}{ʟєꜱ} studies pedagogy to learn about \hyperlink{nokisomalon}{ʟᴏᴧ}

\textbf{\hypertarget{nokisomales}{nokisomales}} \textit{n.} (\hyperlink{nokisoma}{nokisoma}+\allowbreak \hyperlink{les}{les})
pedagologist

\textbf{\hypertarget{nokisomalon}{nokisomalon}} \textit{n.} (\hyperlink{nokisoma}{nokisoma}+\allowbreak \hyperlink{lon}{lon})
pedagogy

\textbf{\hypertarget{nota}{nota}} \textit{v.} (Spa. ⟨nota⟩ [ˈnota])
notice; be aware; \hyperlink{notalon}{ʟᴏᴧ} is conciously aware of the presence of \hyperlink{notalum}{ʟᴜᴍ}

\textbf{\hypertarget{notalon}{notalon}} \textit{n.} (\hyperlink{nota}{nota}+\allowbreak \hyperlink{lon}{lon})
noticer; aware

\textbf{\hypertarget{notalum}{notalum}} \textit{n.} (\hyperlink{nota}{nota}+\allowbreak \hyperlink{lum}{lum})
noticed

\textbf{\hypertarget{notalyan}{notalyan}} \textit{n.} (\hyperlink{nota}{nota}+\allowbreak \hyperlink{lyan}{lyan})
awareness

\textbf{\hypertarget{notaki}{notaki}} \textit{v.} (\hyperlink{nota}{nota}+\allowbreak \hyperlink{ki}{ki})
point out; notify; call attention; wave; ʟєꜱ calls ʟᴏᴧ’s attention to ʟᴜᴍ

\textbf{\hypertarget{nopowi}{nopowi}} \textit{v.} (\hyperlink{no}{no}+\allowbreak \hyperlink{powi}{powi})
be apparent; be obvious; be knowable; be deducable; be notorious; be famous; be smart; \hyperlink{nopowilum}{ʟᴜᴍ} is apparent to \hyperlink{nopowilon}{ʟᴏᴧ}

\textbf{\hypertarget{nopowilon}{nopowilon}} \textit{n.} (\hyperlink{nopowi}{nopowi}+\allowbreak \hyperlink{lon}{lon})
fast learner; smart

\textbf{\hypertarget{nopowilum}{nopowilum}} \textit{n.} (\hyperlink{nopowi}{nopowi}+\allowbreak \hyperlink{lum}{lum})
apparent; obvious; knowable; deducable; notorious; famous

\textbf{\hypertarget{nopowinyo}{nopowinyo}} \textit{v.} (\hyperlink{nopowi}{nopowi}+\allowbreak \hyperlink{nyo}{nyo})
be unapparent; be secret; be unknowable; be concealed; be obscure; be anonymous; be stupid; \hyperlink{nopowinyolum}{ʟᴜᴍ} is not easily apparent to \hyperlink{nopowinyolon}{ʟᴏᴧ}

\textbf{\hypertarget{nopowinyolon}{nopowinyolon}} \textit{n.} (\hyperlink{nopowinyo}{nopowinyo}+\allowbreak \hyperlink{lon}{lon})
\url{https://forum.tfes.org/index.php?topic=6098.msg132382\#msg132382}; stupid

\textbf{\hypertarget{nopowinyolum}{nopowinyolum}} \textit{n.} (\hyperlink{nopowinyo}{nopowinyo}+\allowbreak \hyperlink{lum}{lum})
unapparent; secret; unknowable; concealed; obscure; anonymous

\textbf{\hypertarget{ni}{ni}} \textit{v.} (\hyperlink{ku}{\sout{ku}})
be unbitter; \hyperlink{nilon}{ʟᴏᴧ} is not very bitter

\textbf{\hypertarget{'niukini}{'niukini}} \textit{n.} (Tpi. ⟨Niugini⟩ [niuɡini])
Papua; New Guinea; Irian

\textbf{\hypertarget{'niukiniak}{'niukiniak}} \textit{n.} (\hyperlink{'niukini}{'niukini}+\allowbreak \hyperlink{ak}{ak})
Papua New Guinean; Papuan; from Papua New Guinea

\textbf{\hypertarget{'niukiniwon}{'niukiniwon}} \textit{n.} (\hyperlink{'niukini}{'niukini}+\allowbreak \hyperlink{won}{won})
Papuan; the Papuan people

\textbf{\hypertarget{'niukinitec}{'niukinitec}} \textit{n.} (\hyperlink{'niukini}{'niukini}+\allowbreak \hyperlink{tec}{tec})
Papua New Guinea; Independent State of Papua New Guinea

\textbf{\hypertarget{'niukinitilip}{'niukinitilip}} \textit{n.} (\hyperlink{'niukini}{'niukini}+\allowbreak \hyperlink{tilip}{tilip})
Tok Pisin

\textbf{\hypertarget{nilon}{nilon}} \textit{n.} (\hyperlink{ni}{ni}+\allowbreak \hyperlink{lon}{lon})
unbitter

\textbf{\hypertarget{nilu}{nilu}} \textit{v.} (\hyperlink{kuti}{\sout{kuti}})
be fluid; be amorphous; \hyperlink{nilulon}{ʟᴏᴧ} is fluid

\textbf{\hypertarget{nilulon}{nilulon}} \textit{n.} (\hyperlink{nilu}{nilu}+\allowbreak \hyperlink{lon}{lon})
fluid; amorphous

\textbf{\hypertarget{niluhila}{niluhila}} \textit{v.} (\hyperlink{nilu}{nilu}+\allowbreak \hyperlink{hila}{hila})
flow; ʟєꜱ makes \hyperlink{niluhilalon}{ʟᴏᴧ} \hyperlink{niluhilalon}{ʟᴏᴧ}

\textbf{\hypertarget{niluhilalon}{niluhilalon}} \textit{n.} (\hyperlink{niluhila}{niluhila}+\allowbreak \hyperlink{lon}{lon})
current; stream

\textbf{\hypertarget{niluhilalip}{niluhilalip}} \textit{n.} (\hyperlink{niluhila}{niluhila}+\allowbreak \hyperlink{lip}{lip})
streamline

\textbf{\hypertarget{niluhilamace}{niluhilamace}} \textit{v.} (\hyperlink{niluhila}{niluhila}+\allowbreak \hyperlink{mace}{mace})
be upstream; be upwind; \hyperlink{niluhilamacelon}{ʟᴏᴧ} is upstream of ʟᴜᴍ

\textbf{\hypertarget{niluhilamacelon}{niluhilamacelon}} \textit{n.} (\hyperlink{niluhilamace}{niluhilamace}+\allowbreak \hyperlink{lon}{lon})
upstream; upwind

\textbf{\hypertarget{niluhilasoma}{niluhilasoma}} \textit{v.} (\hyperlink{nilu}{nilu}+\allowbreak \hyperlink{hila}{hila}+\allowbreak \hyperlink{soma}{soma})
do hydrodynamics; \hyperlink{niluhilasomales}{ʟєꜱ} studies the motion of fluids to learn about \hyperlink{niluhilasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{niluhilasomalon}{niluhilasomalon}} \textit{n.} (\hyperlink{niluhilasoma}{niluhilasoma}+\allowbreak \hyperlink{lon}{lon})
hydrodynamics

\textbf{\hypertarget{niluhilasomales}{niluhilasomales}} \textit{n.} (\hyperlink{niluhilasoma}{niluhilasoma}+\allowbreak \hyperlink{les}{les})
hydrodynamicist

\textbf{\hypertarget{niluhilapaho}{niluhilapaho}} \textit{v.} (\hyperlink{niluhila}{niluhila}+\allowbreak \hyperlink{paho}{paho})
be downstream; be downwind; \hyperlink{niluhilapaholon}{ʟᴏᴧ} is downstream of ʟᴜᴍ

\textbf{\hypertarget{niluhilapaholon}{niluhilapaholon}} \textit{n.} (\hyperlink{niluhilapaho}{niluhilapaho}+\allowbreak \hyperlink{lon}{lon})
downstream; downwind

\textbf{\hypertarget{niluki}{niluki}} \textit{v.} (\hyperlink{nilu}{nilu}+\allowbreak \hyperlink{ki}{ki})
melt; sublimate; \hyperlink{nilukiles}{ʟєꜱ} melts \hyperlink{nilukilon}{ʟᴏᴧ}

\textbf{\hypertarget{nilukiles}{nilukiles}} \textit{n.} (\hyperlink{niluki}{niluki}+\allowbreak \hyperlink{les}{les})
melter

\textbf{\hypertarget{nilukilon}{nilukilon}} \textit{n.} (\hyperlink{niluki}{niluki}+\allowbreak \hyperlink{lon}{lon})
molten

\textbf{\hypertarget{nilututumu}{nilututumu}} \textit{v.} (\hyperlink{nilu}{nilu}+\allowbreak \hyperlink{tutumu}{tutumu})
ripple; wave; waves ripple through ʟᴏᴧ

\textbf{\hypertarget{nilututumulwel}{nilututumulwel}} \textit{n.} (\hyperlink{nilututumu}{nilututumu}+\allowbreak \hyperlink{lwel}{lwel})
wave

\textbf{\hypertarget{'niwe}{'niwe}} \textit{n.} (Niu. ⟨Niuē⟩ [niweː])
Niue (landmass)

\textbf{\hypertarget{'niweak}{'niweak}} \textit{n.} (\hyperlink{'niwe}{'niwe}+\allowbreak \hyperlink{ak}{ak})
Niuean; from Niue

\textbf{\hypertarget{'niwewon}{'niwewon}} \textit{n.} (\hyperlink{'niwe}{'niwe}+\allowbreak \hyperlink{won}{won})
Niuean; the Niuean people

\textbf{\hypertarget{'niwetec}{'niwetec}} \textit{n.} (\hyperlink{'niwe}{'niwe}+\allowbreak \hyperlink{tec}{tec})
Niue (country)

\textbf{\hypertarget{'niwetilip}{'niwetilip}} \textit{n.} (\hyperlink{'niwe}{'niwe}+\allowbreak \hyperlink{tilip}{tilip})
Niuean; the Niuean language

\textbf{\hypertarget{ninap}{ninap}} \textit{n.} (\hyperlink{kukam}{\sout{kukam}})
senior citizen; elder; very old and decrepit animal

\textbf{\hypertarget{ninapak}{ninapak}} \textit{n.} (\hyperlink{ninap}{ninap}+\allowbreak \hyperlink{ak}{ak})
elder

\textbf{\hypertarget{nihu}{nihu}} \textit{v.} (\hyperlink{kuci}{\sout{kuci}})
be sad; be sorrowful; be anguished; be distressed; \hyperlink{nihulon}{ʟᴏᴧ} feels sad

\textbf{\hypertarget{nihulon}{nihulon}} \textit{n.} (\hyperlink{nihu}{nihu}+\allowbreak \hyperlink{lon}{lon})
sad; sorrowful; anguished; distressed

\textbf{\hypertarget{nihucalu}{nihucalu}} \textit{v.} (\hyperlink{nihu}{nihu}+\allowbreak \hyperlink{calu}{calu})
be depressed; \hyperlink{nihucalulon}{ʟᴏᴧ} is chronically sad

\textbf{\hypertarget{nihucalulon}{nihucalulon}} \textit{n.} (\hyperlink{nihucalu}{nihucalu}+\allowbreak \hyperlink{lon}{lon})
depressed

\textbf{\hypertarget{nihucwelon}{nihucwelon}} \textit{n.} (\hyperlink{nihu}{nihu}+\allowbreak \hyperlink{cwelon}{cwelon})
tears

\textbf{\hypertarget{nihucwelonkoki}{nihucwelonkoki}} \textit{v.} (\hyperlink{nihucwelon}{nihucwelon}+\allowbreak \hyperlink{koki}{koki})
cry; weep; sob; tear; ʟєꜱ cries out ʟᴏᴧ

\textbf{\hypertarget{nihuki}{nihuki}} \textit{v.} (\hyperlink{nihu}{nihu}+\allowbreak \hyperlink{ki}{ki})
sadden; anguish; distress; ʟєꜱ makes ʟᴏᴧ sadder

\textbf{\hypertarget{nice}{nice}} \textit{v.} (Ben. ⟨{\bengali{}নিচে}⟩ [n̪it͡ɕe])
be below; be down; be low; \hyperlink{niceles}{ʟєꜱ} appears below \hyperlink{nicelon}{ʟᴏᴧ} from the point of view of ʟᴜᴍ

\textbf{\hypertarget{niceles}{niceles}} \textit{n.} (\hyperlink{nice}{nice}+\allowbreak \hyperlink{les}{les})
header; top

\textbf{\hypertarget{nicelon}{nicelon}} \textit{n.} (\hyperlink{nice}{nice}+\allowbreak \hyperlink{lon}{lon})
below; down; low

\textbf{\hypertarget{nicelumah}{nicelumah}} \textit{n.} (\hyperlink{nice}{nice}+\allowbreak \hyperlink{lumah}{lumah})
layer

\textbf{\hypertarget{nicelyan}{nicelyan}} \textit{n.} (\hyperlink{nice}{nice}+\allowbreak \hyperlink{lyan}{lyan})
altitude angle; distance down page

\textbf{\hypertarget{'niceh}{'niceh}} \textit{n.} (Fra. ⟨Niger⟩ [niʒɛʁ])
Niger river; the Republic of the Niger

\textbf{\hypertarget{'nicehtec}{'nicehtec}} \textit{n.} (\hyperlink{'niceh}{'niceh}+\allowbreak \hyperlink{tec}{tec})
Niger;

\textbf{\hypertarget{'nicehtecwon}{'nicehtecwon}} \textit{n.} (\hyperlink{'nicehtec}{'nicehtec}+\allowbreak \hyperlink{won}{won})
Nigerien; the Nigerien people

\textbf{\hypertarget{niceki}{niceki}} \textit{v.} (\hyperlink{nice}{nice}+\allowbreak \hyperlink{ki}{ki})
go down; lower; sink; \hyperlink{nicekiles}{ʟєꜱ} makes ʟᴏᴧ appear to move down from the point of view of ʟᴜᴍ

\textbf{\hypertarget{nicekiles}{nicekiles}} \textit{n.} (\hyperlink{niceki}{niceki}+\allowbreak \hyperlink{les}{les})
one who moves down

\textbf{\hypertarget{'nifis}{'nifis}} \textit{n.} (Aig. ⟨Nevis⟩ [ˈnivis])
Nevis

\textbf{\hypertarget{'nifisak}{'nifisak}} \textit{n.} (\hyperlink{'nifis}{'nifis}+\allowbreak \hyperlink{ak}{ak})
Nevisian; from Nevis

\textbf{\hypertarget{'nikelium}{'nikelium}} \textit{n.} (Lat. ⟨nichelium⟩ [nɪkelɪʊ̃])
nickel (substance)

\textbf{\hypertarget{'nikalakwa}{'nikalakwa}} \textit{n.} (Spa. ⟨Nicaragua⟩ [nikaˈɾaɣwa])
Nicaragua

\textbf{\hypertarget{'nikalakwaak}{'nikalakwaak}} \textit{n.} (\hyperlink{'nikalakwa}{'nikalakwa}+\allowbreak \hyperlink{ak}{ak})
Nicaraguan; from Nicaragua

\textbf{\hypertarget{'nikalakwawon}{'nikalakwawon}} \textit{n.} (\hyperlink{'nikalakwa}{'nikalakwa}+\allowbreak \hyperlink{won}{won})
Nicaraguan; the Nicaraguan people

\textbf{\hypertarget{niki}{niki}} \textit{v.} (\hyperlink{ni}{ni}+\allowbreak \hyperlink{ki}{ki})
debitter; ʟєꜱ makes ʟᴏᴧ become less bitter

\textbf{\hypertarget{nikhu}{nikhu}} \textit{v.} (\hyperlink{kunci}{\sout{kunci}})
be free; be independent; be weak; \hyperlink{nikhulum}{ʟᴜᴍ} cannot tell \hyperlink{nikhulon}{ʟᴏᴧ} what to do

\textbf{\hypertarget{nikhulon}{nikhulon}} \textit{n.} (\hyperlink{nikhu}{nikhu}+\allowbreak \hyperlink{lon}{lon})
free; independent

\textbf{\hypertarget{nikhulum}{nikhulum}} \textit{n.} (\hyperlink{nikhu}{nikhu}+\allowbreak \hyperlink{lum}{lum})
weak

\textbf{\hypertarget{nikhuki}{nikhuki}} \textit{v.} (\hyperlink{nikhu}{nikhu}+\allowbreak \hyperlink{ki}{ki})
lose control; release; free; \hyperlink{nikhukiles}{ʟєꜱ} releases \hyperlink{nikhukilon}{ʟᴏᴧ} from ʟᴜᴍ’s control

\textbf{\hypertarget{nikhukiles}{nikhukiles}} \textit{n.} (\hyperlink{nikhuki}{nikhuki}+\allowbreak \hyperlink{les}{les})
releaser

\textbf{\hypertarget{nikhukilon}{nikhukilon}} \textit{n.} (\hyperlink{nikhuki}{nikhuki}+\allowbreak \hyperlink{lon}{lon})
freed

\textbf{\hypertarget{nita}{nita}} \textit{v.} (\hyperlink{kula}{\sout{kula}})
be hard; be rigid; be firm; be strong; be unforgiving; the surface of \hyperlink{nitalon}{ʟᴏᴧ} feels hard

\textbf{\hypertarget{nitaec}{nitaec}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{ec}{ec})
bone

\textbf{\hypertarget{nitaicilon}{nitaicilon}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{icilon}{icilon})
coral

\textbf{\hypertarget{nitaicilonlawt}{nitaicilonlawt}} \textit{n.} (\hyperlink{nitaicilon}{nitaicilon}+\allowbreak \hyperlink{lawt}{lawt})
Coral Sea

\textbf{\hypertarget{nitalon}{nitalon}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{lon}{lon})
hard; rigid; firm; strong; unforgiving

\textbf{\hypertarget{nitamamul}{nitamamul}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{mamul}{mamul})
armadillo

\textbf{\hypertarget{nitafut}{nitafut}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{fut}{fut})
gourd; Cucurbitaceae with rigid shells

\textbf{\hypertarget{nitak}{nitak}} \textit{pn.} (\hyperlink{kulan}{\sout{kulan}})
previous; last

\textbf{\hypertarget{nitaki}{nitaki}} \textit{v.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{ki}{ki})
harden; firm; ʟєꜱ makes ʟᴏᴧ become hard

\textbf{\hypertarget{nitakio}{nitakio}} \textit{v.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{kio}{kio})
be diamond; \hyperlink{nitakiolon}{ʟᴏᴧ} is made of diamond

\textbf{\hypertarget{nitakiolon}{nitakiolon}} \textit{n.} (\hyperlink{nitakio}{nitakio}+\allowbreak \hyperlink{lon}{lon})
diamond

\textbf{\hypertarget{nitakuhol}{nitakuhol}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{kuhol}{kuhol})
snail

\textbf{\hypertarget{nitaksunkwelwel}{nitaksunkwelwel}} \textit{n.} (\hyperlink{nitak}{nitak}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
yesterday

\textbf{\hypertarget{nitakpumkwelwel}{nitakpumkwelwel}} \textit{n.} (\hyperlink{nitak}{nitak}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
last year

\textbf{\hypertarget{nitatatu}{nitatatu}} \textit{v.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{tatu}{tatu})
be iron; \hyperlink{nitatatulon}{ʟᴏᴧ} is made of iron

\textbf{\hypertarget{nitatatulon}{nitatatulon}} \textit{n.} (\hyperlink{nitatatu}{nitatatu}+\allowbreak \hyperlink{lon}{lon})
iron

\textbf{\hypertarget{nitatun}{nitatun}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{tun}{tun})
vertebrate

\textbf{\hypertarget{nitapic}{nitapic}} \textit{n.} (\hyperlink{nita}{nita}+\allowbreak \hyperlink{pic}{pic})
nut

\textbf{\hypertarget{nito}{nito}} \textit{v.} (\hyperlink{kule}{\sout{kule}})
be near; be close; be before; be approximately; be almost; be like; \hyperlink{nitolon}{ʟᴏᴧ} is physically or numerically close to ʟᴜᴍ

\textbf{\hypertarget{nitoesta}{nitoesta}} \textit{v.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{esta}{esta})
coexist; tolerate; ʟᴏᴧ coexists with ʟᴜᴍ

\textbf{\hypertarget{nitoam}{nitoam}} \textit{n.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{am}{am})
bicep; upper arm

\textbf{\hypertarget{nitolek}{nitolek}} \textit{n.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{lek}{lek})
thigh; upper leg

\textbf{\hypertarget{nitolon}{nitolon}} \textit{n.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{lon}{lon})
near; close; before; approximately; almost; like

\textbf{\hypertarget{nitolwel}{nitolwel}} \textit{n.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{lwel}{lwel})
meeting

\textbf{\hypertarget{nitoki}{nitoki}} \textit{v.} (\hyperlink{nito}{nito}+\allowbreak \hyperlink{ki}{ki})
approach; go toward; meet; draw close; bring together; gather; go to; go in; \hyperlink{nitokiles}{ʟєꜱ} moves ʟᴏᴧ toward ʟᴜᴍ

\textbf{\hypertarget{nitokiles}{nitokiles}} \textit{n.} (\hyperlink{nitoki}{nitoki}+\allowbreak \hyperlink{les}{les})
gatherer; joiner

\textbf{\hypertarget{nitokiti}{nitokiti}} \textit{v.} (\hyperlink{nitoki}{nitoki}+\allowbreak \hyperlink{ti}{ti})
greet; bid hello; salute; \hyperlink{nitokitiles}{ʟєꜱ} says hello to ʟᴏᴧ

\textbf{\hypertarget{nitokitiles}{nitokitiles}} \textit{n.} (\hyperlink{nitokiti}{nitokiti}+\allowbreak \hyperlink{les}{les})
greeter

\textbf{\hypertarget{nitu}{nitu}} \textit{v.} (\hyperlink{kuli}{\sout{kuli}})
be unsavoury; \hyperlink{nitulon}{ʟᴏᴧ} is not very savoury

\textbf{\hypertarget{nitulon}{nitulon}} \textit{n.} (\hyperlink{nitu}{nitu}+\allowbreak \hyperlink{lon}{lon})
unsavoury

\textbf{\hypertarget{nituki}{nituki}} \textit{v.} (\hyperlink{nitu}{nitu}+\allowbreak \hyperlink{ki}{ki})
desavoury; ʟєꜱ makes ʟᴏᴧ become less savoury

\textbf{\hypertarget{'nipon}{'nipon}} \textit{n.} (Jpn. ⟨{\japanese{}日本}⟩ [ɲipːoɴ])
Japan

\textbf{\hypertarget{'niponak}{'niponak}} \textit{n.} (\hyperlink{'nipon}{'nipon}+\allowbreak \hyperlink{ak}{ak})
Japanese; from Japan

\textbf{\hypertarget{'niponwon}{'niponwon}} \textit{n.} (\hyperlink{'nipon}{'nipon}+\allowbreak \hyperlink{won}{won})
Japanese person; the Japanese people

\textbf{\hypertarget{'nipontilip}{'nipontilip}} \textit{n.} (\hyperlink{'nipon}{'nipon}+\allowbreak \hyperlink{tilip}{tilip})
Japanese; the Japanese language

\textbf{\hypertarget{nu}{nu}} \textit{v.} (\hyperlink{ki}{\sout{ki}})
end; stop; cease; cancel; unbecome; come from; go from; change from; send; leave; depart; from; de- -ify; \textit{cessative}; \hyperlink{nules}{ʟєꜱ} makes \hyperlink{nulon}{ʟᴏᴧ} transitions from truth to falsehood

\textbf{\hypertarget{nul}{nul}} \textit{num.} (Epo. ⟨nulo⟩ [nulo])
0; zero; none; no

\textbf{\hypertarget{nules}{nules}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{les}{les})
stopper

\textbf{\hypertarget{nulak}{nulak}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{ak}{ak})
zeroth

\textbf{\hypertarget{nulon}{nulon}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{lon}{lon})
complete; finished

\textbf{\hypertarget{nulyot}{nulyot}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{lyot}{lyot})
end; edge

\textbf{\hypertarget{nulwel}{nulwel}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{lwel}{lwel})
ending

\textbf{\hypertarget{nulwelak}{nulwelak}} \textit{n.} (\hyperlink{nulwel}{nulwel}+\allowbreak \hyperlink{ak}{ak})
final

\textbf{\hypertarget{nulnokipumkwelwel}{nulnokipumkwelwel}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
kindergarden

\textbf{\hypertarget{nulnyolon}{nulnyolon}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{nyolon}{nyolon})
at all; nonzero

\textbf{\hypertarget{nulfitilip}{nulfitilip}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{fitilip}{fitilip})
agnosticism; secularism; religious nonaffiliation

\textbf{\hypertarget{nulkot}{nulkot}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{kot}{kot})
athiesm

\textbf{\hypertarget{nultunnyamales}{nultunnyamales}} \textit{n.} (\hyperlink{nul}{nul}+\allowbreak \hyperlink{tun}{tun}+\allowbreak \hyperlink{nyamales}{nyamales})
vegetarian; something that does not eat meat

\textbf{\hypertarget{nucolon}{nucolon}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{colon}{colon})
cessative (linguistics)

\textbf{\hypertarget{nusison}{nusison}} \textit{n.} (\hyperlink{nu}{nu}+\allowbreak \hyperlink{sison}{sison})
autumn

\textbf{\hypertarget{nyec}{nyec}} \textit{n.} (Cmn. ⟨{\chinese{}啮齿}⟩ [njɛ˥˩ʈ͡ʂʰɨ˧˩˧])
rodent; treeshrew; rabbit; hare; pika; hedgehog; mole; shrew; Glires

\textbf{\hypertarget{nyecak}{nyecak}} \textit{n.} (\hyperlink{nyec}{nyec}+\allowbreak \hyperlink{ak}{ak})
murine

\textbf{\hypertarget{nyama}{nyama}} \textit{v.} (ono. [njam njam])
eat; drink; take; \hyperlink{nyamales}{ʟєꜱ} eats \hyperlink{nyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{nyamaec}{nyamaec}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{ec}{ec})
mouth

\textbf{\hypertarget{nyamaecnepuci}{nyamaecnepuci}} \textit{v.} (\hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{nepuci}{nepuci})
bite; \hyperlink{nyamaecnepuciles}{ʟєꜱ} bites \hyperlink{nyamaecnepucilon}{ʟᴏᴧ}

\textbf{\hypertarget{nyamaecnepucilon}{nyamaecnepucilon}} \textit{n.} (\hyperlink{nyamaecnepuci}{nyamaecnepuci}+\allowbreak \hyperlink{lon}{lon})
bitten

\textbf{\hypertarget{nyamaecnepuciles}{nyamaecnepuciles}} \textit{n.} (\hyperlink{nyamaecnepuci}{nyamaecnepuci}+\allowbreak \hyperlink{les}{les})
biter

\textbf{\hypertarget{nyamaecmat}{nyamaecmat}} \textit{n.} (\hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{mat}{mat})
hard palate

\textbf{\hypertarget{nyamaechwok}{nyamaechwok}} \textit{n.} (\hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{hwok}{hwok})
soft palate; velum

\textbf{\hypertarget{nyamaecsapu}{nyamaecsapu}} \textit{v.} (\hyperlink{nyamaec}{nyamaec}+\allowbreak \hyperlink{sapu}{sapu})
suck; \hyperlink{nyamaecsapules}{ʟєꜱ} sucks on \hyperlink{nyamaecsapulon}{ʟᴏᴧ}

\textbf{\hypertarget{nyamaecsapules}{nyamaecsapules}} \textit{n.} (\hyperlink{nyamaecsapu}{nyamaecsapu}+\allowbreak \hyperlink{les}{les})
sucker

\textbf{\hypertarget{nyamaecsapulon}{nyamaecsapulon}} \textit{n.} (\hyperlink{nyamaecsapu}{nyamaecsapu}+\allowbreak \hyperlink{lon}{lon})
sucked

\textbf{\hypertarget{nyamales}{nyamales}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{les}{les})
eater

\textbf{\hypertarget{nyamalon}{nyamalon}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{lon}{lon})
food; drink; meal

\textbf{\hypertarget{nyamalonestakilyot}{nyamalonestakilyot}} \textit{n.} (\hyperlink{nyamalon}{nyamalon}+\allowbreak \hyperlink{estakilyot}{estakilyot})
kitchen

\textbf{\hypertarget{nyamaloncyauki}{nyamaloncyauki}} \textit{v.} (\hyperlink{nyamalon}{nyamalon}+\allowbreak \hyperlink{cyauki}{cyauki})
cook; fry; bake; boil; simmer; grill; \hyperlink{nyamaloncyaukiles}{ʟєꜱ} cooks \hyperlink{nyamaloncyaukilon}{ʟᴏᴧ}

\textbf{\hypertarget{nyamaloncyaukilon}{nyamaloncyaukilon}} \textit{n.} (\hyperlink{nyamaloncyauki}{nyamaloncyauki}+\allowbreak \hyperlink{lon}{lon})
cooking

\textbf{\hypertarget{nyamaloncyaukiles}{nyamaloncyaukiles}} \textit{n.} (\hyperlink{nyamaloncyauki}{nyamaloncyauki}+\allowbreak \hyperlink{les}{les})
cook; chef; baker

\textbf{\hypertarget{nyamaluat}{nyamaluat}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{luat}{luat})
eating utensil; silverware

\textbf{\hypertarget{nyamalyot}{nyamalyot}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{lyot}{lyot})
dining room; dining hall

\textbf{\hypertarget{nyamalwel}{nyamalwel}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{lwel}{lwel})
meal; mealtime

\textbf{\hypertarget{nyamanitalon}{nyamanitalon}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{nitalon}{nitalon})
tooth

\textbf{\hypertarget{nyamanitalontapalon}{nyamanitalontapalon}} \textit{n.} (\hyperlink{nyamanitalon}{nyamanitalon}+\allowbreak \hyperlink{tapalon}{tapalon})
alveolar ridge; alveolar margin

\textbf{\hypertarget{nyamamai}{nyamamai}} \textit{v.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{mai}{mai})
dine out; \hyperlink{nyamamailon}{ʟᴏᴧ} buys \hyperlink{nyamamailum}{ʟᴜᴍ} from \hyperlink{nyamamailes}{ʟєꜱ}

\textbf{\hypertarget{nyamamailes}{nyamamailes}} \textit{n.} (\hyperlink{nyamamai}{nyamamai}+\allowbreak \hyperlink{les}{les})
restaurant; server

\textbf{\hypertarget{nyamamailon}{nyamamailon}} \textit{n.} (\hyperlink{nyamamai}{nyamamai}+\allowbreak \hyperlink{lon}{lon})
diner

\textbf{\hypertarget{nyamamailum}{nyamamailum}} \textit{n.} (\hyperlink{nyamamai}{nyamamai}+\allowbreak \hyperlink{lum}{lum})
restaurant meal

\textbf{\hypertarget{nyamamailyot}{nyamamailyot}} \textit{n.} (\hyperlink{nyamamai}{nyamamai}+\allowbreak \hyperlink{lyot}{lyot})
restaurant; food court; dining area

\textbf{\hypertarget{nyamamat}{nyamamat}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{mat}{mat})
platter; plate

\textbf{\hypertarget{nyamahwok}{nyamahwok}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{hwok}{hwok})
lip

\textbf{\hypertarget{nyamacai}{nyamacai}} \textit{v.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{cai}{cai})
feel hungry; ʟᴏᴧ is hungry for ʟᴜᴍ

\textbf{\hypertarget{nyamacohtuelon}{nyamacohtuelon}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{cohtuelon}{cohtuelon})
bowl

\textbf{\hypertarget{nyamaciuh}{nyamaciuh}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{ciuh}{ciuh})
venus fly-trap

\textbf{\hypertarget{nyamacwelon}{nyamacwelon}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{cwelon}{cwelon})
saliva

\textbf{\hypertarget{nyamacwelonkae}{nyamacwelonkae}} \textit{v.} (\hyperlink{nyamacwelon}{nyamacwelon}+\allowbreak \hyperlink{kae}{kae})
drool; ʟєꜱ drools ʟᴏᴧ

\textbf{\hypertarget{nyamacwelonkoki}{nyamacwelonkoki}} \textit{v.} (\hyperlink{nyamacwelon}{nyamacwelon}+\allowbreak \hyperlink{koki}{koki})
expectorate; spit; salivate; ʟєꜱ spits ʟᴏᴧ out

\textbf{\hypertarget{nyamakulalon}{nyamakulalon}} \textit{n.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{kulalon}{kulalon})
gums

\textbf{\hypertarget{nyamapowi}{nyamapowi}} \textit{v.} (\hyperlink{nyama}{nyama}+\allowbreak \hyperlink{powi}{powi})
be edible; be potable; \hyperlink{nyamapowilon}{ʟᴏᴧ} is edible to ʟєꜱ

\textbf{\hypertarget{nyamapowilon}{nyamapowilon}} \textit{n.} (\hyperlink{nyamapowi}{nyamapowi}+\allowbreak \hyperlink{lon}{lon})
edible; potable

\textbf{\hypertarget{nyo}{nyo}} \textit{v.} (Ben. ⟨{\bengali{}না}⟩ [naː])
no; not; be false; be wrong; be incorrect; be not happening; be fake; \textit{negative}; \hyperlink{nyolon}{ʟᴏᴧ} is not happening

\textbf{\hypertarget{nyoayfhaumailyot}{nyoayfhaumailyot}} \textit{n.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{ayf}{ayf}+\allowbreak \hyperlink{hau}{hau}+\allowbreak \hyperlink{mailyot}{mailyot})
grocery store

\textbf{\hypertarget{nyoaw}{nyoaw}} \textit{spec.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{aw}{aw})
instead; rather

\textbf{\hypertarget{nyolon}{nyolon}} \textit{n.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{lon}{lon})
falsehood; fiction; false; wrong; incorrect; not happening; fake

\textbf{\hypertarget{nyonoki}{nyonoki}} \textit{v.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{noki}{noki})
disprove; falsify; compromise; log out; ʟєꜱ proves ʟᴏᴧ false

\textbf{\hypertarget{nyotewi}{nyotewi}} \textit{v.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{tewi}{tewi})
be forbidden; be against the rules; be illegal; be prohibited; ʟᴏᴧ is not allowed to make \hyperlink{nyotewilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{nyotewilum}{nyotewilum}} \textit{n.} (\hyperlink{nyotewi}{nyotewi}+\allowbreak \hyperlink{lum}{lum})
banned; forbidden; against the rules; illegal; prohibited

\textbf{\hypertarget{nyotewinu}{nyotewinu}} \textit{v.} (\hyperlink{nyotewi}{nyotewi}+\allowbreak \hyperlink{nu}{nu})
allow; permit; ʟєꜱ permits ʟᴏᴧ to make ʟᴜᴍ happen

\textbf{\hypertarget{nyotewinyo}{nyotewinyo}} \textit{v.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{tewinyo}{tewinyo})
may; be allowed; be legal; be permitted; ʟᴏᴧ is allowed to make \hyperlink{nyotewinyolum}{ʟᴜᴍ} happen

\textbf{\hypertarget{nyotewinyolum}{nyotewinyolum}} \textit{n.} (\hyperlink{nyotewinyo}{nyotewinyo}+\allowbreak \hyperlink{lum}{lum})
allowed; legal; permitted

\textbf{\hypertarget{nyotewiki}{nyotewiki}} \textit{v.} (\hyperlink{nyotewi}{nyotewi}+\allowbreak \hyperlink{ki}{ki})
forbid; pass rules against; prohibit; ban; \hyperlink{nyotewikiles}{ʟєꜱ} forbids ʟᴏᴧ from making ʟᴜᴍ happen

\textbf{\hypertarget{nyotewikiles}{nyotewikiles}} \textit{n.} (\hyperlink{nyotewiki}{nyotewiki}+\allowbreak \hyperlink{les}{les})
authority

\textbf{\hypertarget{nyoti}{nyoti}} \textit{v.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{ti}{ti})
lie; be dishonest; ʟєꜱ expresses \hyperlink{nyotilon}{ʟᴏᴧ}, which they think to be false

\textbf{\hypertarget{nyotilon}{nyotilon}} \textit{n.} (\hyperlink{nyoti}{nyoti}+\allowbreak \hyperlink{lon}{lon})
lie; feint; falsehood; dishonest

\textbf{\hypertarget{nyotikolwa}{nyotikolwa}} \textit{v.} (\hyperlink{nyoti}{nyoti}+\allowbreak \hyperlink{kolwa}{kolwa})
mistrust; find untrustworthy; ʟᴏᴧ does not trust ʟᴜᴍ

\textbf{\hypertarget{nyopensi}{nyopensi}} \textit{v.} (\hyperlink{nyo}{nyo}+\allowbreak \hyperlink{pensi}{pensi})
be wrong; be incorrect; \hyperlink{nyopensilon}{ʟᴏᴧ} thinks \hyperlink{nyopensilum}{ʟᴜᴍ} to be true even though it is not

\textbf{\hypertarget{nyopensilon}{nyopensilon}} \textit{n.} (\hyperlink{nyopensi}{nyopensi}+\allowbreak \hyperlink{lon}{lon})
wrong; incorrect

\textbf{\hypertarget{nyopensilum}{nyopensilum}} \textit{n.} (\hyperlink{nyopensi}{nyopensi}+\allowbreak \hyperlink{lum}{lum})
myth

\textbf{\hypertarget{nyopensiki}{nyopensiki}} \textit{v.} (\hyperlink{nyopensi}{nyopensi}+\allowbreak \hyperlink{ki}{ki})
decorrect; wrong; ʟєꜱ feeds ʟᴏᴧ false information about ʟᴜᴍ

\textbf{\hypertarget{nwes}{nwes}} \textit{n.} (Spa. ⟨nuez⟩ [nwes])
walnut; Juglans

\section{M}

\textbf{\hypertarget{'me}{'me}} \textit{n.} (ono. [m])
m; /m/; labial nasal

\textbf{\hypertarget{'melanesi}{'melanesi}} \textit{n.} (Fra. ⟨Mélanésie⟩ [ˈmelɐnezi])
Melanesia

\textbf{\hypertarget{'melanesiak}{'melanesiak}} \textit{n.} (\hyperlink{'melanesi}{'melanesi}+\allowbreak \hyperlink{ak}{ak})
Melanesian; from Melanesia

\textbf{\hypertarget{'melanesiwon}{'melanesiwon}} \textit{n.} (\hyperlink{'melanesi}{'melanesi}+\allowbreak \hyperlink{won}{won})
Melanesian; the Melanesian people

\textbf{\hypertarget{men}{men}} \textit{num.} (Spa. ⟨menos⟩ [ˈmenos])
minus; negative; -

\textbf{\hypertarget{meha}{meha}} \textit{v.} (\hyperlink{poca}{\sout{poca}})
be fresh; \hyperlink{mehalon}{ʟᴏᴧ} is fresh

\textbf{\hypertarget{mehalon}{mehalon}} \textit{n.} (\hyperlink{meha}{meha}+\allowbreak \hyperlink{lon}{lon})
fresh

\textbf{\hypertarget{mehaki}{mehaki}} \textit{v.} (\hyperlink{meha}{meha}+\allowbreak \hyperlink{ki}{ki})
freshen; ʟєꜱ freshens ʟᴏᴧ

\textbf{\hypertarget{'mehiko}{'mehiko}} \textit{n.} (Spa. ⟨México⟩ [ˈmexiko])
Mexico

\textbf{\hypertarget{'mehikoak}{'mehikoak}} \textit{n.} (\hyperlink{'mehiko}{'mehiko}+\allowbreak \hyperlink{ak}{ak})
Mexican; from Mexico

\textbf{\hypertarget{'mehikolawt}{'mehikolawt}} \textit{n.} (\hyperlink{'mehiko}{'mehiko}+\allowbreak \hyperlink{lawt}{lawt})
Gulf of Mexico

\textbf{\hypertarget{'mehikowon}{'mehikowon}} \textit{n.} (\hyperlink{'mehiko}{'mehiko}+\allowbreak \hyperlink{won}{won})
Mexican; the Mexican people

\textbf{\hypertarget{mes}{mes}} \textit{num.} (Yor. ⟨mẹsan⟩ [mɛsan])
9; nine

\textbf{\hypertarget{mesak}{mesak}} \textit{n.} (\hyperlink{mes}{mes}+\allowbreak \hyperlink{ak}{ak})
ninth

\textbf{\hypertarget{mesnokipumkwelwel}{mesnokipumkwelwel}} \textit{n.} (\hyperlink{mes}{mes}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
freshman year of high school

\textbf{\hypertarget{mesnul}{mesnul}} \textit{num.} (\hyperlink{mes}{mes}+\allowbreak \hyperlink{nul}{nul})
90; ninety

\textbf{\hypertarget{mesnulnul}{mesnulnul}} \textit{num.} (\hyperlink{mes}{mes}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
900; nine hundred

\textbf{\hypertarget{mekle}{mekle}} \textit{v.} (\hyperlink{ponto}{\sout{ponto}})
be open; be cupped; be U-shaped; be confined; \hyperlink{meklelon}{ʟᴏᴧ} is open on one side

\textbf{\hypertarget{meklelekpoltilum}{meklelekpoltilum}} \textit{n.} (\hyperlink{mekle}{mekle}+\allowbreak \hyperlink{lekpoltilum}{lekpoltilum})
skirt

\textbf{\hypertarget{meklelon}{meklelon}} \textit{n.} (\hyperlink{mekle}{mekle}+\allowbreak \hyperlink{lon}{lon})
cup; bowl; corner; hole; bay; dip; U; open; cupped; U-shaped; confined

\textbf{\hypertarget{meklesaman}{meklesaman}} \textit{n.} (\hyperlink{mekle}{mekle}+\allowbreak \hyperlink{saman}{saman})
door

\textbf{\hypertarget{mekleki}{mekleki}} \textit{v.} (\hyperlink{mekle}{mekle}+\allowbreak \hyperlink{ki}{ki})
open; dig; cup; divot; carve out; \hyperlink{meklekiles}{ʟєꜱ} makes ʟᴏᴧ open

\textbf{\hypertarget{meklekiles}{meklekiles}} \textit{n.} (\hyperlink{mekleki}{mekleki}+\allowbreak \hyperlink{les}{les})
opener

\textbf{\hypertarget{meklepowi}{meklepowi}} \textit{v.} (\hyperlink{mekle}{mekle}+\allowbreak \hyperlink{powi}{powi})
be unlocked; \hyperlink{meklepowilon}{ʟᴏᴧ} is unlocked

\textbf{\hypertarget{meklepowilon}{meklepowilon}} \textit{n.} (\hyperlink{meklepowi}{meklepowi}+\allowbreak \hyperlink{lon}{lon})
unlocked

\textbf{\hypertarget{meklepowinu}{meklepowinu}} \textit{v.} (\hyperlink{meklepowi}{meklepowi}+\allowbreak \hyperlink{nu}{nu})
lock; close; ʟєꜱ locks ʟᴏᴧ

\textbf{\hypertarget{meklepowinyo}{meklepowinyo}} \textit{v.} (\hyperlink{meklepowi}{meklepowi}+\allowbreak \hyperlink{nyo}{nyo})
be locked; \hyperlink{meklepowinyolon}{ʟᴏᴧ} is locked

\textbf{\hypertarget{meklepowinyolon}{meklepowinyolon}} \textit{n.} (\hyperlink{meklepowinyo}{meklepowinyo}+\allowbreak \hyperlink{lon}{lon})
locked

\textbf{\hypertarget{meklepowiki}{meklepowiki}} \textit{v.} (\hyperlink{meklepowi}{meklepowi}+\allowbreak \hyperlink{ki}{ki})
unlock; open; ʟєꜱ unlocks ʟᴏᴧ

\textbf{\hypertarget{metus}{metus}} \textit{n.} (Epo. ⟨meduzo⟩ [meˈduzo])
jellyfish; medusa; Medusozoa

\textbf{\hypertarget{'methe}{'methe}} \textit{n.} (Fra. ⟨mètre⟩ [ˈmɛtʁ])
metre; meter; m

\textbf{\hypertarget{'maoli}{'maoli}} \textit{n.} (Mri. ⟨Māori⟩ [maːɔɾi])
Maori; the Maori people

\textbf{\hypertarget{'maoliak}{'maoliak}} \textit{n.} (\hyperlink{'maoli}{'maoli}+\allowbreak \hyperlink{ak}{ak})
Maori; of the Maori

\textbf{\hypertarget{'maolitec}{'maolitec}} \textit{n.} (\hyperlink{'maoli}{'maoli}+\allowbreak \hyperlink{tec}{tec})
New Zealand; Aotearoa

\textbf{\hypertarget{'maolitilip}{'maolitilip}} \textit{n.} (\hyperlink{'maoli}{'maoli}+\allowbreak \hyperlink{tilip}{tilip})
Maori; Te Reo; the Maori language

\textbf{\hypertarget{mai}{mai}} \textit{v.} (Cmn. ⟨{\chinese{}卖}⟩ [maɪ̯˥˩])
sell; buy; vend; purchase; \hyperlink{mailon}{ʟᴏᴧ} legally obtains \hyperlink{mailum}{ʟᴜᴍ} from \hyperlink{mailes}{ʟєꜱ}

\textbf{\hypertarget{mailes}{mailes}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{les}{les})
vendor; salesperson

\textbf{\hypertarget{mailesak}{mailesak}} \textit{n.} (\hyperlink{mailes}{mailes}+\allowbreak \hyperlink{ak}{ak})
private

\textbf{\hypertarget{mailet}{mailet}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{let}{let})
economy

\textbf{\hypertarget{mailetsoma}{mailetsoma}} \textit{v.} (\hyperlink{mailet}{mailet}+\allowbreak \hyperlink{soma}{soma})
do economics; \hyperlink{mailetsomales}{ʟєꜱ} studies economies to learn about \hyperlink{mailetsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{mailetsomales}{mailetsomales}} \textit{n.} (\hyperlink{mailetsoma}{mailetsoma}+\allowbreak \hyperlink{les}{les})
economist

\textbf{\hypertarget{mailetsomalon}{mailetsomalon}} \textit{n.} (\hyperlink{mailetsoma}{mailetsoma}+\allowbreak \hyperlink{lon}{lon})
economics

\textbf{\hypertarget{mailon}{mailon}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{lon}{lon})
buyer; customer

\textbf{\hypertarget{mailuat}{mailuat}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{luat}{luat})
money; currency

\textbf{\hypertarget{mailum}{mailum}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{lum}{lum})
good; service

\textbf{\hypertarget{mailyot}{mailyot}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{lyot}{lyot})
store; shop

\textbf{\hypertarget{mailwel}{mailwel}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{lwel}{lwel})
financial transaction

\textbf{\hypertarget{maih}{maih}} \textit{n.} (Cmn. ⟨{\chinese{}蚂蚁}⟩ [ma˧˩˧i˧˩˧])
ant; Formicidae

\textbf{\hypertarget{maihwok}{maihwok}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{hwok}{hwok})
ticket; voucher

\textbf{\hypertarget{maihwokmailyot}{maihwokmailyot}} \textit{n.} (\hyperlink{maihwok}{maihwok}+\allowbreak \hyperlink{mailyot}{mailyot})
ticket booth

\textbf{\hypertarget{maihnyamamamul}{maihnyamamamul}} \textit{n.} (\hyperlink{maih}{maih}+\allowbreak \hyperlink{nyama}{nyama}+\allowbreak \hyperlink{mamul}{mamul})
anteater

\textbf{\hypertarget{maicuaki}{maicuaki}} \textit{v.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{cuaki}{cuaki})
advertise; \hyperlink{maicuakiles}{ʟєꜱ} advertises \hyperlink{maicuakilum}{ʟᴜᴍ} to \hyperlink{maicuakilon}{ʟᴏᴧ}

\textbf{\hypertarget{maicuakiles}{maicuakiles}} \textit{n.} (\hyperlink{maicuaki}{maicuaki}+\allowbreak \hyperlink{les}{les})
advertiser

\textbf{\hypertarget{maicuakilon}{maicuakilon}} \textit{n.} (\hyperlink{maicuaki}{maicuaki}+\allowbreak \hyperlink{lon}{lon})
advertisee

\textbf{\hypertarget{maicuakilum}{maicuakilum}} \textit{n.} (\hyperlink{maicuaki}{maicuaki}+\allowbreak \hyperlink{lum}{lum})
advertisement

\textbf{\hypertarget{mais}{mais}} \textit{n.} (Spa. ⟨maíz⟩ [maˈis])
corn; maize; Zea mays

\textbf{\hypertarget{maipaltolum}{maipaltolum}} \textit{n.} (\hyperlink{mai}{mai}+\allowbreak \hyperlink{paltolum}{paltolum})
corporation; company; business

\textbf{\hypertarget{mayo}{mayo}} \textit{v.} (\hyperlink{pawe}{\sout{pawe}})
leave bare; expose; leave open; ʟᴏᴧ covers little of \hyperlink{mayolum}{ʟᴜᴍ}

\textbf{\hypertarget{mayolum}{mayolum}} \textit{n.} (\hyperlink{mayo}{mayo}+\allowbreak \hyperlink{lum}{lum})
bare; open; exposed

\textbf{\hypertarget{mayoki}{mayoki}} \textit{v.} (\hyperlink{mayo}{mayo}+\allowbreak \hyperlink{ki}{ki})
uncover; bare; expose; open; \hyperlink{mayokiles}{ʟєꜱ} makes ʟᴏᴧ stop surrounding ʟᴜᴍ

\textbf{\hypertarget{mayokiles}{mayokiles}} \textit{n.} (\hyperlink{mayoki}{mayoki}+\allowbreak \hyperlink{les}{les})
uncoverer

\textbf{\hypertarget{'malayu}{'malayu}} \textit{n.} (Msa. ⟨Melayu⟩ [məlaju])
Malaysian; Malay; the Malaysian people

\textbf{\hypertarget{'malayuak}{'malayuak}} \textit{n.} (\hyperlink{'malayu}{'malayu}+\allowbreak \hyperlink{ak}{ak})
Malaysian; from Malaysia

\textbf{\hypertarget{'malayutec}{'malayutec}} \textit{n.} (\hyperlink{'malayu}{'malayu}+\allowbreak \hyperlink{tec}{tec})
Malaysia

\textbf{\hypertarget{'malayutilip}{'malayutilip}} \textit{n.} (\hyperlink{'malayu}{'malayu}+\allowbreak \hyperlink{tilip}{tilip})
Malay; Malaysian; the Malay language

\textbf{\hypertarget{'malakasi}{'malakasi}} \textit{n.} (Mlg. ⟨malagasy⟩ [ˌmalaˈɡasʲ])
Malagasy; the Malagasy people

\textbf{\hypertarget{'malakasiak}{'malakasiak}} \textit{n.} (\hyperlink{'malakasi}{'malakasi}+\allowbreak \hyperlink{ak}{ak})
Malagasy; from Madagascar

\textbf{\hypertarget{'malakasikwelyot}{'malakasikwelyot}} \textit{n.} (\hyperlink{'malakasi}{'malakasi}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Madagascar (island)

\textbf{\hypertarget{'malakasitec}{'malakasitec}} \textit{n.} (\hyperlink{'malakasi}{'malakasi}+\allowbreak \hyperlink{tec}{tec})
Madagascar (country); Republic of Madagascar

\textbf{\hypertarget{'malakasitilip}{'malakasitilip}} \textit{n.} (\hyperlink{'malakasi}{'malakasi}+\allowbreak \hyperlink{tilip}{tilip})
Malagasy; the Malagasy language

\textbf{\hypertarget{'malata}{'malata}} \textit{n.} (Mar. ⟨{\devanagari{}मराठा}⟩ [məˈɾaʈʰa])
Marathi; Maratha; the Marathi people

\textbf{\hypertarget{'malataak}{'malataak}} \textit{n.} (\hyperlink{'malata}{'malata}+\allowbreak \hyperlink{ak}{ak})
Marathi; of the Marathi

\textbf{\hypertarget{'malatatec}{'malatatec}} \textit{n.} (\hyperlink{'malata}{'malata}+\allowbreak \hyperlink{tec}{tec})
Maharashtra

\textbf{\hypertarget{'malatatilip}{'malatatilip}} \textit{n.} (\hyperlink{'malata}{'malata}+\allowbreak \hyperlink{tilip}{tilip})
Marathi; the Marathi language

\textbf{\hypertarget{'mali}{'mali}} \textit{n.} (Bam. ⟨Mali⟩ [mali])
Mali

\textbf{\hypertarget{'maliak}{'maliak}} \textit{n.} (\hyperlink{'mali}{'mali}+\allowbreak \hyperlink{ak}{ak})
Malian; Malinese; from Mali

\textbf{\hypertarget{'maliwon}{'maliwon}} \textit{n.} (\hyperlink{'mali}{'mali}+\allowbreak \hyperlink{won}{won})
Malian; the Malian people

\textbf{\hypertarget{'malta}{'malta}} \textit{n.} (Mlt. ⟨Malta⟩ [mɐlta])
Malta

\textbf{\hypertarget{'maltaak}{'maltaak}} \textit{n.} (\hyperlink{'malta}{'malta}+\allowbreak \hyperlink{ak}{ak})
Maltese; from Malta

\textbf{\hypertarget{'maltawon}{'maltawon}} \textit{n.} (\hyperlink{'malta}{'malta}+\allowbreak \hyperlink{won}{won})
Maltese; the Maltese people

\textbf{\hypertarget{'maltatilip}{'maltatilip}} \textit{n.} (\hyperlink{'malta}{'malta}+\allowbreak \hyperlink{tilip}{tilip})
Maltese; the Maltese language

\textbf{\hypertarget{manca}{manca}} \textit{v.} (Nya. ⟨-manja⟩ [mand͡ʒa])
be to the right; \hyperlink{mancalon}{ʟᴏᴧ} has a positive \textit{x} coordinate from ʟᴜᴍ’s point of view

\textbf{\hypertarget{mancalon}{mancalon}} \textit{n.} (\hyperlink{manca}{manca}+\allowbreak \hyperlink{lon}{lon})
right side; to the right

\textbf{\hypertarget{mancalyan}{mancalyan}} \textit{n.} (\hyperlink{manca}{manca}+\allowbreak \hyperlink{lyan}{lyan})
\textit{x} coordinate

\textbf{\hypertarget{mancaki}{mancaki}} \textit{v.} (\hyperlink{manca}{manca}+\allowbreak \hyperlink{ki}{ki})
go right; ʟєꜱ makes ʟᴏᴧ move right from ʟᴜᴍ’s point of view

\textbf{\hypertarget{'manka}{'manka}} \textit{n.} (Jpn. ⟨{\japanese{}漫画}⟩ [maŋɡa])
manga

\textbf{\hypertarget{'mankanum}{'mankanum}} \textit{n.} (Lat. ⟨manganum⟩ [manɡanʊ̃])
manganese

\textbf{\hypertarget{mantis}{mantis}} \textit{n.} (Spa. ⟨mantis⟩ [ˈmantis])
mantis; Mantodea

\textbf{\hypertarget{mama}{mama}} \textit{v.} (ono. [mama])
raise; parent; \hyperlink{mamales}{ʟєꜱ} raises \hyperlink{mamalon}{ʟᴏᴧ}

\textbf{\hypertarget{mamaec}{mamaec}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{ec}{ec})
mamary gland

\textbf{\hypertarget{mamales}{mamales}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{les}{les})
parent; mother; father; guardian; mentor

\textbf{\hypertarget{mamalon}{mamalon}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{lon}{lon})
child; daughter; son; tutee

\textbf{\hypertarget{mamacwelon}{mamacwelon}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{cwelon}{cwelon})
milk

\textbf{\hypertarget{mamacwekutilon}{mamacwekutilon}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{cwe}{cwe}+\allowbreak \hyperlink{kutilon}{kutilon})
cheese

\textbf{\hypertarget{mamatapalon}{mamatapalon}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{tapalon}{tapalon})
breast; bussom; boob; nipple

\textbf{\hypertarget{mamapemamalon}{mamapemamalon}} \textit{n.} (\hyperlink{mama}{mama}+\allowbreak \hyperlink{pemamalon}{pemamalon})
anticle; aunt; uncle

\textbf{\hypertarget{mamul}{mamul}} \textit{n.} (Epo. ⟨mamulo⟩ [maˈmulo])
mammal; Mammalia

\textbf{\hypertarget{mamulak}{mamulak}} \textit{n.} (\hyperlink{mamul}{mamul}+\allowbreak \hyperlink{ak}{ak})
mammalian

\textbf{\hypertarget{'mampalam}{'mampalam}} \textit{n.} (Tam. ⟨{\tamil{}மாம்பழம்}⟩ [maːmpɐɻɐm])
mango; Mangifera

\textbf{\hypertarget{'mahlep}{'mahlep}} \textit{n.} (Ara. ⟨{\arabics{}مغرب‎}⟩ [mɑɣreb])
Maghreb; Maghrib

\textbf{\hypertarget{'mahlepak}{'mahlepak}} \textit{n.} (\hyperlink{'mahlep}{'mahlep}+\allowbreak \hyperlink{ak}{ak})
Maghrebi; Maghreb; from the Maghreb

\textbf{\hypertarget{'mahleptec}{'mahleptec}} \textit{n.} (\hyperlink{'mahlep}{'mahlep}+\allowbreak \hyperlink{tec}{tec})
Morocco; the Kingdom of Morocco

\textbf{\hypertarget{'mahleptecwon}{'mahleptecwon}} \textit{n.} (\hyperlink{'mahleptec}{'mahleptec}+\allowbreak \hyperlink{won}{won})
Moroccan; the Moroccan people

\textbf{\hypertarget{'mahleptilip}{'mahleptilip}} \textit{n.} (\hyperlink{'mahlep}{'mahlep}+\allowbreak \hyperlink{tilip}{tilip})
Berber; Amazigh; Tamazight; the Berber languages

\textbf{\hypertarget{mace}{mace}} \textit{v.} (\hyperlink{paho}{\sout{paho}})
be high; be over; \hyperlink{macelon}{ʟᴏᴧ} has a higher altitude than ʟᴜᴍ

\textbf{\hypertarget{macelek}{macelek}} \textit{n.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{lek}{lek})
stilt

\textbf{\hypertarget{macelon}{macelon}} \textit{n.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{lon}{lon})
top; heights; high; over

\textbf{\hypertarget{maceki}{maceki}} \textit{v.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{ki}{ki})
lift; heighten; ascend; elevate; \hyperlink{macekiles}{ʟєꜱ} increases ʟᴏᴧ’s altitude relative to ʟᴜᴍ

\textbf{\hypertarget{macekiles}{macekiles}} \textit{n.} (\hyperlink{maceki}{maceki}+\allowbreak \hyperlink{les}{les})
one who heightens

\textbf{\hypertarget{macetayl}{macetayl}} \textit{n.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{tayl}{tayl})
plateau; highlands

\textbf{\hypertarget{macetielon}{macetielon}} \textit{n.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{tielon}{tielon})
go over; cross; ʟєꜱ moves ʟᴏᴧ over ʟᴜᴍ

\textbf{\hypertarget{macepoltilum}{macepoltilum}} \textit{n.} (\hyperlink{mace}{mace}+\allowbreak \hyperlink{poltilum}{poltilum})
blazer

\textbf{\hypertarget{macin}{macin}} \textit{n.} (Eng. ⟨machine⟩ [məˈʃiːn])
machine; robot; automaton; artificial mechanical structure

\textbf{\hypertarget{'maclek}{'maclek}} \textit{n.} (Ara. ⟨{\arabics{}مـشـرِق‎‎}⟩ [maʃreq])
Mashriq; Mashreq

\textbf{\hypertarget{'maclekak}{'maclekak}} \textit{n.} (\hyperlink{'maclek}{'maclek}+\allowbreak \hyperlink{ak}{ak})
Mashriqi; Mashriq; from the Mashriq

\textbf{\hypertarget{'macpus}{'macpus}} \textit{n.} (Ara. ⟨{\arabics{}مچبوس}⟩ [mɑt͡ʃˈbuːs])
makbūs

\textbf{\hypertarget{'masyel}{'masyel}} \textit{n.} (Mah. ⟨M̧ajeļ⟩ [mˠɑzʲɛʌ̯ɫ])
Marshall Islands (archipelago)

\textbf{\hypertarget{'masyelak}{'masyelak}} \textit{n.} (\hyperlink{'masyel}{'masyel}+\allowbreak \hyperlink{ak}{ak})
Marshallese; Marshall Islander; from the Marshall Islands

\textbf{\hypertarget{'masyelwon}{'masyelwon}} \textit{n.} (\hyperlink{'masyel}{'masyel}+\allowbreak \hyperlink{won}{won})
Marshallese; the Marshallese people

\textbf{\hypertarget{'masyeltec}{'masyeltec}} \textit{n.} (\hyperlink{'masyel}{'masyel}+\allowbreak \hyperlink{tec}{tec})
Marshall Islands

\textbf{\hypertarget{'masyeltilip}{'masyeltilip}} \textit{n.} (\hyperlink{'masyel}{'masyel}+\allowbreak \hyperlink{tilip}{tilip})
Marshallese; Ebon; the Marshallese language

\textbf{\hypertarget{'masli}{'masli}} \textit{n.} (Ara. ⟨{\arabics{}مصر}⟩ [mɑsˁɾ])
Egypt; the Arab Republic of Egypt

\textbf{\hypertarget{'masliak}{'masliak}} \textit{n.} (\hyperlink{'masli}{'masli}+\allowbreak \hyperlink{ak}{ak})
Egyptian; from Egypt

\textbf{\hypertarget{'masliwon}{'masliwon}} \textit{n.} (\hyperlink{'masli}{'masli}+\allowbreak \hyperlink{won}{won})
Egyptian; the Egyptian people

\textbf{\hypertarget{'maskwa}{'maskwa}} \textit{n.} (Rus. ⟨Москва́⟩ [mɐˈskva])
Moscow

\textbf{\hypertarget{'masta}{'masta}} \textit{n.} (Ave. ⟨{\avestan{}𐬨𐬀𐬰𐬛𐬁}⟩ [mazdaː])
Ahura Mazda; Ohrmazd; Ahuramazda; Hourmazd; Hormazd; Hurmuz

\textbf{\hypertarget{'mastafitilip}{'mastafitilip}} \textit{n.} (\hyperlink{'masta}{'masta}+\allowbreak \hyperlink{fitilip}{fitilip})
Zoroastrianism; Mazdayasna

\textbf{\hypertarget{'mastafitilipak}{'mastafitilipak}} \textit{n.} (\hyperlink{'mastafitilip}{'mastafitilip}+\allowbreak \hyperlink{ak}{ak})
Zoroastrian; Zarathustrian; of Zoroastrianism

\textbf{\hypertarget{'mastafitilipwon}{'mastafitilipwon}} \textit{n.} (\hyperlink{'mastafitilip}{'mastafitilip}+\allowbreak \hyperlink{won}{won})
Zoroastrian; Zarathustrian; followers of Zoroastrianism

\textbf{\hypertarget{'maketon}{'maketon}} \textit{n.} (Mkd. ⟨Македон⟩ [makɛdɔn])
Macedon; Macedonia

\textbf{\hypertarget{'maketonak}{'maketonak}} \textit{n.} (\hyperlink{'maketon}{'maketon}+\allowbreak \hyperlink{ak}{ak})
Macedonian; from Macedonia

\textbf{\hypertarget{'maketonwon}{'maketonwon}} \textit{n.} (\hyperlink{'maketon}{'maketon}+\allowbreak \hyperlink{won}{won})
Macedonian; the Macedonian people

\textbf{\hypertarget{'maketontilip}{'maketontilip}} \textit{n.} (\hyperlink{'maketon}{'maketon}+\allowbreak \hyperlink{tilip}{tilip})
Macedonian; the Macedonian language

\textbf{\hypertarget{'makahiki}{'makahiki}} \textit{n.} (Haw. ⟨makahiki⟩ [makɐˈhiki])
Makahiki; the Makahiki season

\textbf{\hypertarget{'makyal}{'makyal}} \textit{n.} (Hun. ⟨maygar⟩ [mɒɟɒr])
Hungarian; the Hungarian people

\textbf{\hypertarget{'makyalak}{'makyalak}} \textit{n.} (\hyperlink{'makyal}{'makyal}+\allowbreak \hyperlink{ak}{ak})
Hungarian; from Hungary

\textbf{\hypertarget{'makyaltec}{'makyaltec}} \textit{n.} (\hyperlink{'makyal}{'makyal}+\allowbreak \hyperlink{tec}{tec})
Hungary

\textbf{\hypertarget{'makyaltilip}{'makyaltilip}} \textit{n.} (\hyperlink{'makyal}{'makyal}+\allowbreak \hyperlink{tilip}{tilip})
Hungarian; the Hungarian language

\textbf{\hypertarget{'maknesium}{'maknesium}} \textit{n.} (Lat. ⟨magnesium⟩ [maɡnezɪʊ̃])
magnesium

\textbf{\hypertarget{mat}{mat}} \textit{n.} (\hyperlink{pal}{\sout{pal}})
plate; board; wall; rigid two-dimensional object

\textbf{\hypertarget{matu}{matu}} \textit{v.} (\hyperlink{pali}{\sout{pali}})
be light; \hyperlink{matulon}{ʟᴏᴧ} is light

\textbf{\hypertarget{matulon}{matulon}} \textit{n.} (\hyperlink{matu}{matu}+\allowbreak \hyperlink{lon}{lon})
lightweight; light

\textbf{\hypertarget{matuki}{matuki}} \textit{v.} (\hyperlink{matu}{matu}+\allowbreak \hyperlink{ki}{ki})
lighten; ʟєꜱ lightens ʟᴏᴧ

\textbf{\hypertarget{mapametlo}{mapametlo}} \textit{v.} (\hyperlink{pamapolte}{\sout{pamapolte}})
be turned clockwise; \hyperlink{mapametlolon}{ʟᴏᴧ} appears rotated clockwise from the orientation \hyperlink{mapametlolon}{ʟᴏᴧ} from the point of view of ʟᴜᴍ

\textbf{\hypertarget{mapametlolon}{mapametlolon}} \textit{n.} (\hyperlink{mapametlo}{mapametlo}+\allowbreak \hyperlink{lon}{lon})
turned clockwise

\textbf{\hypertarget{mapametloki}{mapametloki}} \textit{v.} (\hyperlink{mapametlo}{mapametlo}+\allowbreak \hyperlink{ki}{ki})
rotate clockwise; \hyperlink{mapametlokiles}{ʟєꜱ} turns ʟᴏᴧ clockwise from ʟᴜᴍ’s point of view

\textbf{\hypertarget{mapametlokiles}{mapametlokiles}} \textit{n.} (\hyperlink{mapametloki}{mapametloki}+\allowbreak \hyperlink{les}{les})
clockwise turner

\textbf{\hypertarget{mo}{mo}} \textit{v.} (\hyperlink{pe}{\sout{pe}})
be without; be apart; be away; \hyperlink{molon}{ʟᴏᴧ} does not accompany ʟєꜱ

\textbf{\hypertarget{moye}{moye}} \textit{v.} (Yor. ⟨mòye⟩ [mòjē])
understand; comprehend; be sensical; know; be smart; \hyperlink{moyelon}{ʟᴏᴧ} understands \hyperlink{moyelum}{ʟᴜᴍ} well

\textbf{\hypertarget{moyelon}{moyelon}} \textit{n.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{lon}{lon})
understander; smart

\textbf{\hypertarget{moyelum}{moyelum}} \textit{n.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{lum}{lum})
understood; sensical

\textbf{\hypertarget{moyelyan}{moyelyan}} \textit{n.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{lyan}{lyan})
level of understanding

\textbf{\hypertarget{moyecai}{moyecai}} \textit{v.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{cai}{cai})
feel curious; wonder; ʟᴏᴧ is curious about ʟᴜᴍ

\textbf{\hypertarget{moyeki}{moyeki}} \textit{v.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{ki}{ki})
explain; describe; \hyperlink{moyekiles}{ʟєꜱ} teaches \hyperlink{moyekilon}{ʟᴏᴧ} to understand ʟᴜᴍ

\textbf{\hypertarget{moyekiles}{moyekiles}} \textit{n.} (\hyperlink{moyeki}{moyeki}+\allowbreak \hyperlink{les}{les})
tutor; teacher

\textbf{\hypertarget{moyekilon}{moyekilon}} \textit{n.} (\hyperlink{moyeki}{moyeki}+\allowbreak \hyperlink{lon}{lon})
tutee; student

\textbf{\hypertarget{moyetiluat}{moyetiluat}} \textit{n.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{tiluat}{tiluat})
smart phone; phone

\textbf{\hypertarget{moyepatili}{moyepatili}} \textit{v.} (\hyperlink{moye}{moye}+\allowbreak \hyperlink{patili}{patili})
decode; parse; ʟєꜱ decodes ʟᴏᴧ into ʟᴜᴍ

\textbf{\hypertarget{mola}{mola}} \textit{v.} (\hyperlink{peta}{\sout{peta}})
reverse; do back; return from; ʟєꜱ makes ʟᴏᴧ happen in reverse after having happened

\textbf{\hypertarget{molon}{molon}} \textit{n.} (\hyperlink{mo}{mo}+\allowbreak \hyperlink{lon}{lon})
without; apart; away

\textbf{\hypertarget{'moltofa}{'moltofa}} \textit{n.} (Ron. ⟨Moldova⟩ [moldova])
Moldova river

\textbf{\hypertarget{'moltofaak}{'moltofaak}} \textit{n.} (\hyperlink{'moltofa}{'moltofa}+\allowbreak \hyperlink{ak}{ak})
Moldovan; from Moldova

\textbf{\hypertarget{'moltofawon}{'moltofawon}} \textit{n.} (\hyperlink{'moltofa}{'moltofa}+\allowbreak \hyperlink{won}{won})
Moldovan; the Moldovan people

\textbf{\hypertarget{'moltofatec}{'moltofatec}} \textit{n.} (\hyperlink{'moltofa}{'moltofa}+\allowbreak \hyperlink{tec}{tec})
Moldova

\textbf{\hypertarget{'moltofatilip}{'moltofatilip}} \textit{n.} (\hyperlink{'moltofa}{'moltofa}+\allowbreak \hyperlink{tilip}{tilip})
Moldovan; the Moldovan language

\textbf{\hypertarget{'monako}{'monako}} \textit{n.} (Fra. ⟨Monaco⟩ [mɔnako])
Monaco

\textbf{\hypertarget{'monakoak}{'monakoak}} \textit{n.} (\hyperlink{'monako}{'monako}+\allowbreak \hyperlink{ak}{ak})
Monacan; Monégasque; from Monaco

\textbf{\hypertarget{'monakowon}{'monakowon}} \textit{n.} (\hyperlink{'monako}{'monako}+\allowbreak \hyperlink{won}{won})
Monégasque; Monacan; the Monacan people

\textbf{\hypertarget{'monkol}{'monkol}} \textit{n.} (Mon. ⟨{\mongolian{}ᠮᠣᠩᠭᠣᠯ}⟩ [mɔŋɢɔɮ])
Mongol; the Mongolian people

\textbf{\hypertarget{'monkolak}{'monkolak}} \textit{n.} (\hyperlink{'monkol}{'monkol}+\allowbreak \hyperlink{ak}{ak})
Mongolian; from Mongolia

\textbf{\hypertarget{'monkoltec}{'monkoltec}} \textit{n.} (\hyperlink{'monkol}{'monkol}+\allowbreak \hyperlink{tec}{tec})
Mongolia

\textbf{\hypertarget{'monkoltilip}{'monkoltilip}} \textit{n.} (\hyperlink{'monkol}{'monkol}+\allowbreak \hyperlink{tilip}{tilip})
Mongolian; the Mongolian language

\textbf{\hypertarget{monta}{monta}} \textit{v.} (Spa. ⟨monta⟩ [ˈmonta])
ride; transport; \hyperlink{montales}{ʟєꜱ} rides on \hyperlink{montalon}{ʟᴏᴧ}

\textbf{\hypertarget{montales}{montales}} \textit{n.} (\hyperlink{monta}{monta}+\allowbreak \hyperlink{les}{les})
passenger

\textbf{\hypertarget{montalon}{montalon}} \textit{n.} (\hyperlink{monta}{monta}+\allowbreak \hyperlink{lon}{lon})
vehicle

\textbf{\hypertarget{'mohis}{'mohis}} \textit{n.} (Mfe. ⟨Moris⟩ [moʁis])
Mauritius

\textbf{\hypertarget{'mohisak}{'mohisak}} \textit{n.} (\hyperlink{'mohis}{'mohis}+\allowbreak \hyperlink{ak}{ak})
Mauritian; from Mauritius

\textbf{\hypertarget{'mohiswon}{'mohiswon}} \textit{n.} (\hyperlink{'mohis}{'mohis}+\allowbreak \hyperlink{won}{won})
Mauritian; the Mauritian people

\textbf{\hypertarget{'mohistilip}{'mohistilip}} \textit{n.} (\hyperlink{'mohis}{'mohis}+\allowbreak \hyperlink{tilip}{tilip})
Mauritian creole; Morisien

\textbf{\hypertarget{moc}{moc}} \textit{n.} (Ben. ⟨{\bengali{}মশা}⟩ [mɔɕa])
mosquito; Culicidae

\textbf{\hypertarget{moca}{moca}} \textit{v.} (Ben. ⟨{\bengali{}মজা}⟩ [mɔd͡ʑa])
have fun; be amused; play; entertain; \hyperlink{mocalon}{ʟᴏᴧ} is entertained by \hyperlink{mocalum}{ʟᴜᴍ}

\textbf{\hypertarget{mocaufu}{mocaufu}} \textit{v.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{ufu}{ufu})
challenge; be challenging; \hyperlink{mocaufules}{ʟєꜱ} challenges \hyperlink{mocaufulon}{ʟᴏᴧ} with \hyperlink{mocaufulum}{ʟᴜᴍ}

\textbf{\hypertarget{mocaufules}{mocaufules}} \textit{n.} (\hyperlink{mocaufu}{mocaufu}+\allowbreak \hyperlink{les}{les})
challenger

\textbf{\hypertarget{mocaufulon}{mocaufulon}} \textit{n.} (\hyperlink{mocaufu}{mocaufu}+\allowbreak \hyperlink{lon}{lon})
challenged; challenging

\textbf{\hypertarget{mocaufulum}{mocaufulum}} \textit{n.} (\hyperlink{mocaufu}{mocaufu}+\allowbreak \hyperlink{lum}{lum})
challenge

\textbf{\hypertarget{mocalon}{mocalon}} \textit{n.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{lon}{lon})
entertained; audience; amused

\textbf{\hypertarget{mocalum}{mocalum}} \textit{n.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{lum}{lum})
show; entertainment

\textbf{\hypertarget{mocalwel}{mocalwel}} \textit{n.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{lwel}{lwel})
performance; game; show

\textbf{\hypertarget{mocacwelon}{mocacwelon}} \textit{n.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{cwelon}{cwelon})
alcohol

\textbf{\hypertarget{mocacwelonak}{mocacwelonak}} \textit{n.} (\hyperlink{mocacwelon}{mocacwelon}+\allowbreak \hyperlink{ak}{ak})
alcoholic

\textbf{\hypertarget{mocafake}{mocafake}} \textit{v.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{fake}{fake})
be drunk; be intoxicated; \hyperlink{mocafakelon}{ʟᴏᴧ} is drunk

\textbf{\hypertarget{mocafakelon}{mocafakelon}} \textit{n.} (\hyperlink{mocafake}{mocafake}+\allowbreak \hyperlink{lon}{lon})
drunk; intoxicated

\textbf{\hypertarget{mocafakenu}{mocafakenu}} \textit{v.} (\hyperlink{mocafake}{mocafake}+\allowbreak \hyperlink{nu}{nu})
sober; ʟєꜱ makes ʟᴏᴧ become sober

\textbf{\hypertarget{mocafakeki}{mocafakeki}} \textit{v.} (\hyperlink{mocafake}{mocafake}+\allowbreak \hyperlink{ki}{ki})
drink; get drunk; intoxicate; ʟєꜱ makes ʟᴏᴧ drunk

\textbf{\hypertarget{mocaki}{mocaki}} \textit{v.} (\hyperlink{moca}{moca}+\allowbreak \hyperlink{ki}{ki})
entertain; make fun; \hyperlink{mocakiles}{ʟєꜱ} makes ʟᴏᴧ be entertained by ʟᴜᴍ

\textbf{\hypertarget{mocakiles}{mocakiles}} \textit{n.} (\hyperlink{mocaki}{mocaki}+\allowbreak \hyperlink{les}{les})
entertainer

\textbf{\hypertarget{mota}{mota}} \textit{v.} (Mar. ⟨{\devanagari{}मोठा}⟩ [moʈʰaː])
be big; be large; be spacious; \hyperlink{motalon}{ʟᴏᴧ} has a high volume

\textbf{\hypertarget{motaipis}{motaipis}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{ipis}{ipis})
cockroach

\textbf{\hypertarget{motayeh}{motayeh}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{yeh}{yeh})
taro; elephant ears

\textbf{\hypertarget{motalamasiklalonkil}{motalamasiklalonkil}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{lamasiklalon}{lamasiklalon}+\allowbreak \hyperlink{kil}{kil})
beard worm

\textbf{\hypertarget{motalon}{motalon}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{lon}{lon})
big; large; spacious

\textbf{\hypertarget{motalonicelum}{motalonicelum}} \textit{n.} (\hyperlink{motalon}{motalon}+\allowbreak \hyperlink{icelum}{icelum})
project

\textbf{\hypertarget{motalyan}{motalyan}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{lyan}{lyan})
size; volume

\textbf{\hypertarget{motanilututumulwel}{motanilututumulwel}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{nilututumulwel}{nilututumulwel})
tsunami; tidal wave; ʟᴏᴧ is struck by a tsunami from \hyperlink{motanilututumulwelles}{ʟєꜱ}

\textbf{\hypertarget{motanilututumulwelles}{motanilututumulwelles}} \textit{n.} (\hyperlink{motanilututumulwel}{motanilututumulwel}+\allowbreak \hyperlink{les}{les})
oceanic earthquake

\textbf{\hypertarget{motamontalon}{motamontalon}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{montalon}{montalon})
truck

\textbf{\hypertarget{motacim}{motacim}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{cim}{cim})
fava bean; broad bean; horse bean; Vicia faba

\textbf{\hypertarget{motacutalawt}{motacutalawt}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{cuta}{cuta}+\allowbreak \hyperlink{lawt}{lawt})
Pacific Ocean

\textbf{\hypertarget{motacutalawtak}{motacutalawtak}} \textit{n.} (\hyperlink{motacutalawt}{motacutalawt}+\allowbreak \hyperlink{ak}{ak})
Pacific

\textbf{\hypertarget{motaswa}{motaswa}} \textit{v.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{swa}{swa})
feel awe; \hyperlink{motaswalon}{ʟᴏᴧ} feels awe at \hyperlink{motaswalum}{ʟᴜᴍ}

\textbf{\hypertarget{motaswalon}{motaswalon}} \textit{n.} (\hyperlink{motaswa}{motaswa}+\allowbreak \hyperlink{lon}{lon})
awed

\textbf{\hypertarget{motaswalum}{motaswalum}} \textit{n.} (\hyperlink{motaswa}{motaswa}+\allowbreak \hyperlink{lum}{lum})
awesome; awful

\textbf{\hypertarget{mota'kanta}{mota'kanta}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{'kanta}{'kanta})
Ugandan; the Ugandan people

\textbf{\hypertarget{mota'kantaak}{mota'kantaak}} \textit{n.} (\hyperlink{mota'kanta}{mota'kanta}+\allowbreak \hyperlink{ak}{ak})
Ugandan; from Uganda

\textbf{\hypertarget{mota'kantatec}{mota'kantatec}} \textit{n.} (\hyperlink{mota'kanta}{mota'kanta}+\allowbreak \hyperlink{tec}{tec})
Uganda

\textbf{\hypertarget{motaki}{motaki}} \textit{v.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{ki}{ki})
grow; expand; dilate; swell; \hyperlink{motakiles}{ʟєꜱ} grows \hyperlink{motakilon}{ʟᴏᴧ}

\textbf{\hypertarget{motakiah}{motakiah}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{kiah}{kiah})
condor

\textbf{\hypertarget{motakiles}{motakiles}} \textit{n.} (\hyperlink{motaki}{motaki}+\allowbreak \hyperlink{les}{les})
grower

\textbf{\hypertarget{motakilon}{motakilon}} \textit{n.} (\hyperlink{motaki}{motaki}+\allowbreak \hyperlink{lon}{lon})
balloon; swollen; bulb

\textbf{\hypertarget{motakilonpes}{motakilonpes}} \textit{n.} (\hyperlink{motakilon}{motakilon}+\allowbreak \hyperlink{pes}{pes})
pufferfish

\textbf{\hypertarget{motapum}{motapum}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{pum}{pum})
Jupiter

\textbf{\hypertarget{motapumak}{motapumak}} \textit{n.} (\hyperlink{motapum}{motapum}+\allowbreak \hyperlink{ak}{ak})
Jovian

\textbf{\hypertarget{motapus}{motapus}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{pus}{pus})
pumpkin

\textbf{\hypertarget{mota'pwitan}{mota'pwitan}} \textit{n.} (\hyperlink{mota}{mota}+\allowbreak \hyperlink{'pwitan}{'pwitan})
Great Brittan

\textbf{\hypertarget{mila}{mila}} \textit{v.} (Sho. ⟨mira⟩ [mira])
wait; \hyperlink{milalon}{ʟᴏᴧ} is waiting for ʟᴜᴍ

\textbf{\hypertarget{milalon}{milalon}} \textit{n.} (\hyperlink{mila}{mila}+\allowbreak \hyperlink{lon}{lon})
in wait

\textbf{\hypertarget{milalwel}{milalwel}} \textit{n.} (\hyperlink{mila}{mila}+\allowbreak \hyperlink{lwel}{lwel})
wait; wait period

\textbf{\hypertarget{milu}{milu}} \textit{v.} (\hyperlink{puti}{\sout{puti}})
be black; be dark; be tan; \hyperlink{milulon}{ʟᴏᴧ} reflects little light

\textbf{\hypertarget{miluilulih}{miluilulih}} \textit{n.} (\hyperlink{milu}{milu}+\allowbreak \hyperlink{ilu}{ilu}+\allowbreak \hyperlink{lih}{lih})
raccoon

\textbf{\hypertarget{milulon}{milulon}} \textit{n.} (\hyperlink{milu}{milu}+\allowbreak \hyperlink{lon}{lon})
black; dark; tan

\textbf{\hypertarget{milumuti}{milumuti}} \textit{v.} (\hyperlink{milu}{milu}+\allowbreak \hyperlink{muti}{muti})
be brown; be murky; \hyperlink{milumutilon}{ʟᴏᴧ} looks brown

\textbf{\hypertarget{milumutilon}{milumutilon}} \textit{n.} (\hyperlink{milumuti}{milumuti}+\allowbreak \hyperlink{lon}{lon})
brown; murky

\textbf{\hypertarget{milumutihutyeh}{milumutihutyeh}} \textit{n.} (\hyperlink{milumuti}{milumuti}+\allowbreak \hyperlink{hutyeh}{hutyeh})
moth

\textbf{\hypertarget{milumutiki}{milumutiki}} \textit{v.} (\hyperlink{milumuti}{milumuti}+\allowbreak \hyperlink{ki}{ki})
brown; colour brown; ʟєꜱ colours ʟᴏᴧ brown

\textbf{\hypertarget{miluki}{miluki}} \textit{v.} (\hyperlink{milu}{milu}+\allowbreak \hyperlink{ki}{ki})
blacken; darken; shade; burn; tan; ʟєꜱ darkens ʟᴏᴧ

\textbf{\hypertarget{min}{min}} \textit{pn.} (Pan. ⟨{\gurmukhi{}ਮੈਂ}⟩ [mɛ̃ː])
I; me; \textit{first person}; the speaker

\textbf{\hypertarget{minet}{minet}} \textit{pn.} (\hyperlink{min}{min}+\allowbreak \hyperlink{et}{et})
us; \textit{first person plural exclusive}; the speaker and others

\textbf{\hypertarget{minetak}{minetak}} \textit{n.} (\hyperlink{minet}{minet}+\allowbreak \hyperlink{ak}{ak})
our

\textbf{\hypertarget{minak}{minak}} \textit{n.} (\hyperlink{min}{min}+\allowbreak \hyperlink{ak}{ak})
my; mine

\textbf{\hypertarget{minpuk}{minpuk}} \textit{pn.} (\hyperlink{min}{min}+\allowbreak \hyperlink{puk}{puk})
us all; \textit{first person plural inclusive}; the speaker, the listener, and possibly others

\textbf{\hypertarget{minpukak}{minpukak}} \textit{n.} (\hyperlink{minpuk}{minpuk}+\allowbreak \hyperlink{ak}{ak})
all our

\textbf{\hypertarget{mih}{mih}} \textit{n.} (Spa. ⟨mijo⟩ [ˈmixo])
millet; resilient, productive cereal crop

\textbf{\hypertarget{'mihowtaw}{'mihowtaw}} \textit{n.} (Cmn. ⟨{\chinese{}猕猴桃}⟩ [mi˧˥xoʊ̯˧˥tʰaʊ̯˧˥])
kiwifruit; kiwi; Chinese gooseberry; Actinidia

\textbf{\hypertarget{mihu}{mihu}} \textit{v.} (\hyperlink{puci}{\sout{puci}})
pull; attract; \hyperlink{mihules}{ʟєꜱ} pulls on \hyperlink{mihulon}{ʟᴏᴧ}

\textbf{\hypertarget{mihules}{mihules}} \textit{n.} (\hyperlink{mihu}{mihu}+\allowbreak \hyperlink{les}{les})
attraction

\textbf{\hypertarget{mihulon}{mihulon}} \textit{n.} (\hyperlink{mihu}{mihu}+\allowbreak \hyperlink{lon}{lon})
pulled

\textbf{\hypertarget{mihutatu}{mihutatu}} \textit{v.} (\hyperlink{mihu}{mihu}+\allowbreak \hyperlink{tatu}{tatu})
be magnetic; \hyperlink{mihutatulon}{ʟᴏᴧ} is magnetic

\textbf{\hypertarget{mihutatulon}{mihutatulon}} \textit{n.} (\hyperlink{mihutatu}{mihutatu}+\allowbreak \hyperlink{lon}{lon})
magnet; magnetic

\textbf{\hypertarget{mihutatuniluhilasoma}{mihutatuniluhilasoma}} \textit{v.} (\hyperlink{mihutatu}{mihutatu}+\allowbreak \hyperlink{nilu}{nilu}+\allowbreak \hyperlink{hila}{hila}+\allowbreak \hyperlink{soma}{soma})
do magnetohydrodynamics; \hyperlink{mihutatuniluhilasomales}{ʟєꜱ} studies the motion of conductive fluids in magnetic fields to learn about \hyperlink{mihutatuniluhilasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{mihutatuniluhilasomalon}{mihutatuniluhilasomalon}} \textit{n.} (\hyperlink{mihutatuniluhilasoma}{mihutatuniluhilasoma}+\allowbreak \hyperlink{lon}{lon})
magnetohydrodynamics

\textbf{\hypertarget{mihutatuniluhilasomales}{mihutatuniluhilasomales}} \textit{n.} (\hyperlink{mihutatuniluhilasoma}{mihutatuniluhilasoma}+\allowbreak \hyperlink{les}{les})
magnetohydrodynamicist

\textbf{\hypertarget{miclo}{miclo}} \textit{v.} (Ben. ⟨{\bengali{}মিশ্র}⟩ [miɕrɔ])
be mixed; be impure; be tainted; permeate; \hyperlink{miclolum}{ʟᴜᴍ} is mixed into \hyperlink{miclolon}{ʟᴏᴧ}

\textbf{\hypertarget{miclolon}{miclolon}} \textit{n.} (\hyperlink{miclo}{miclo}+\allowbreak \hyperlink{lon}{lon})
solvent; mixed; impure; tainted

\textbf{\hypertarget{miclolum}{miclolum}} \textit{n.} (\hyperlink{miclo}{miclo}+\allowbreak \hyperlink{lum}{lum})
solute

\textbf{\hypertarget{miclolyot}{miclolyot}} \textit{n.} (\hyperlink{miclo}{miclo}+\allowbreak \hyperlink{lyot}{lyot})
mixer; mixing pot

\textbf{\hypertarget{micloki}{micloki}} \textit{v.} (\hyperlink{miclo}{miclo}+\allowbreak \hyperlink{ki}{ki})
mix; taint; pollute; disolve; infuse; ʟєꜱ mixes ʟᴜᴍ into ʟᴏᴧ

\textbf{\hypertarget{'mikhonesi}{'mikhonesi}} \textit{n.} (Fra. ⟨Micronésie⟩ [ˈmikʁonezi])
Micronesia (region)

\textbf{\hypertarget{'mikhonesiak}{'mikhonesiak}} \textit{n.} (\hyperlink{'mikhonesi}{'mikhonesi}+\allowbreak \hyperlink{ak}{ak})
Micronesian; from Micronesia

\textbf{\hypertarget{'mikhonesiwon}{'mikhonesiwon}} \textit{n.} (\hyperlink{'mikhonesi}{'mikhonesi}+\allowbreak \hyperlink{won}{won})
Micronesian; the Micronesian people

\textbf{\hypertarget{'mikhonesitec}{'mikhonesitec}} \textit{n.} (\hyperlink{'mikhonesi}{'mikhonesi}+\allowbreak \hyperlink{tec}{tec})
Micronesia; Federated States of Micronesia

\textbf{\hypertarget{'mikhonesitecwon}{'mikhonesitecwon}} \textit{n.} (\hyperlink{'mikhonesitec}{'mikhonesitec}+\allowbreak \hyperlink{won}{won})
Micronesian; the Micronesian citizenry

\textbf{\hypertarget{mita}{mita}} \textit{v.} (\hyperlink{pula}{\sout{pula}})
be unclean; be dirty; be filthy; be grimy; be gross; be unsanitary; \hyperlink{mitalon}{ʟᴏᴧ} is unclean

\textbf{\hypertarget{mitalon}{mitalon}} \textit{n.} (\hyperlink{mita}{mita}+\allowbreak \hyperlink{lon}{lon})
filth; unclean; dirty; filthy; grimy; gross; unsanitary

\textbf{\hypertarget{mitaki}{mitaki}} \textit{v.} (\hyperlink{mita}{mita}+\allowbreak \hyperlink{ki}{ki})
dirty; grimify; desanitise; \hyperlink{mitakiles}{ʟєꜱ} makes ʟᴏᴧ unclean

\textbf{\hypertarget{mitakiles}{mitakiles}} \textit{n.} (\hyperlink{mitaki}{mitaki}+\allowbreak \hyperlink{les}{les})
dirtier

\textbf{\hypertarget{mitu}{mitu}} \textit{v.} (\hyperlink{puli}{\sout{puli}})
be empty; be blank; \hyperlink{mitulon}{ʟᴏᴧ} is empty of ʟᴜᴍ

\textbf{\hypertarget{mitulon}{mitulon}} \textit{n.} (\hyperlink{mitu}{mitu}+\allowbreak \hyperlink{lon}{lon})
void; vacuum; empty; blank

\textbf{\hypertarget{mituki}{mituki}} \textit{v.} (\hyperlink{mitu}{mitu}+\allowbreak \hyperlink{ki}{ki})
empty; clear; ʟєꜱ empties ʟᴏᴧ of ʟᴜᴍ

\textbf{\hypertarget{mip}{mip}} \textit{n.} (\hyperlink{pum}{\sout{pum}})
sky; atmosphere; weather; heavens; all space above the ground

\textbf{\hypertarget{mipalaktan}{mipalaktan}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{alaktan}{alaktan})
scorpionfly

\textbf{\hypertarget{mipak}{mipak}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{ak}{ak})
celestial; atmospheric; meteorological; aerial; heavenly

\textbf{\hypertarget{mipinanu}{mipinanu}} \textit{v.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{inanu}{inanu})
strike; ʟᴏᴧ is struck by lightning from \hyperlink{mipinanules}{ʟєꜱ}

\textbf{\hypertarget{mipinanules}{mipinanules}} \textit{n.} (\hyperlink{mipinanu}{mipinanu}+\allowbreak \hyperlink{les}{les})
thundercloud; thunderstorm

\textbf{\hypertarget{mipmontalon}{mipmontalon}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{montalon}{montalon})
flying machine; airplane; helicopter; balloon

\textbf{\hypertarget{miphila}{miphila}} \textit{v.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{hila}{hila})
blow; gust; wind blows on ʟᴏᴧ from \hyperlink{miphilales}{ʟєꜱ}

\textbf{\hypertarget{miphilales}{miphilales}} \textit{n.} (\hyperlink{miphila}{miphila}+\allowbreak \hyperlink{les}{les})
wind system

\textbf{\hypertarget{miphyolon}{miphyolon}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{hyolon}{hyolon})
air; atmosphere; nitrogen and oxygen and all that jazz

\textbf{\hypertarget{miphwolon}{miphwolon}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{hwolon}{hwolon})
comet

\textbf{\hypertarget{mipcakalum}{mipcakalum}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{cakalum}{cakalum})
nitrogen

\textbf{\hypertarget{mipkae}{mipkae}} \textit{v.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{kae}{kae})
rain; precipitate; \hyperlink{mipkaelon}{ʟᴏᴧ} falls from the sky

\textbf{\hypertarget{mipkaelon}{mipkaelon}} \textit{n.} (\hyperlink{mipkae}{mipkae}+\allowbreak \hyperlink{lon}{lon})
rain; precipitation

\textbf{\hypertarget{mipkaesilakipowinules}{mipkaesilakipowinules}} \textit{n.} (\hyperlink{mipkae}{mipkae}+\allowbreak \hyperlink{silakipowinules}{silakipowinules})
umbrella

\textbf{\hypertarget{mippes}{mippes}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{pes}{pes})
lungfish

\textbf{\hypertarget{mippum}{mippum}} \textit{n.} (\hyperlink{mip}{mip}+\allowbreak \hyperlink{pum}{pum})
Uranus

\textbf{\hypertarget{mippumak}{mippumak}} \textit{n.} (\hyperlink{mippum}{mippum}+\allowbreak \hyperlink{ak}{ak})
Uranic

\textbf{\hypertarget{muafa}{muafa}} \textit{v.} (\hyperlink{piasa}{\sout{piasa}})
be unfamiliar with; be unaccustomed; be strange; be foreign; \hyperlink{muafalum}{ʟᴜᴍ} is unfamiliar to \hyperlink{muafalon}{ʟᴏᴧ}

\textbf{\hypertarget{muafalon}{muafalon}} \textit{n.} (\hyperlink{muafa}{muafa}+\allowbreak \hyperlink{lon}{lon})
unfamiliar with; unaccustomed; strange; foreign

\textbf{\hypertarget{muafalum}{muafalum}} \textit{n.} (\hyperlink{muafa}{muafa}+\allowbreak \hyperlink{lum}{lum})
unfamiliar to; stranger

\textbf{\hypertarget{muafaki}{muafaki}} \textit{v.} (\hyperlink{muafa}{muafa}+\allowbreak \hyperlink{ki}{ki})
unfamiliarise; get unaccustomed; forget; lose; \hyperlink{muafakiles}{ʟєꜱ} makes ʟᴏᴧ become unfamiliar with ʟᴜᴍ

\textbf{\hypertarget{muafakiles}{muafakiles}} \textit{n.} (\hyperlink{muafaki}{muafaki}+\allowbreak \hyperlink{les}{les})
unfamiliariser

\textbf{\hypertarget{'mulitanya}{'mulitanya}} \textit{n.} (Ara. ⟨{\arabics{}موريتانيا‎}⟩ [muːriːtaːnijaː])
Mauritania

\textbf{\hypertarget{'mulitanyaak}{'mulitanyaak}} \textit{n.} (\hyperlink{'mulitanya}{'mulitanya}+\allowbreak \hyperlink{ak}{ak})
Mauritanian; from Mauritania

\textbf{\hypertarget{'mulitanyawon}{'mulitanyawon}} \textit{n.} (\hyperlink{'mulitanya}{'mulitanya}+\allowbreak \hyperlink{won}{won})
Mauritanian; the Mauritanian people

\textbf{\hypertarget{munaklo}{munaklo}} \textit{v.} (\hyperlink{pikante}{\sout{pikante}})
be mild; be cool; \hyperlink{munaklolon}{ʟᴏᴧ} is not spicy

\textbf{\hypertarget{munaklolon}{munaklolon}} \textit{n.} (\hyperlink{munaklo}{munaklo}+\allowbreak \hyperlink{lon}{lon})
mild; cool

\textbf{\hypertarget{munakloki}{munakloki}} \textit{v.} (\hyperlink{munaklo}{munaklo}+\allowbreak \hyperlink{ki}{ki})
mild; cool; despice; ʟєꜱ makes ʟᴏᴧ become less spicy

\textbf{\hypertarget{mumu}{mumu}} \textit{v.} (ono. [mː])
hum; buzz; ʟєꜱ makes \hyperlink{mumulon}{ʟᴏᴧ}

\textbf{\hypertarget{mumulon}{mumulon}} \textit{n.} (\hyperlink{mumu}{mumu}+\allowbreak \hyperlink{lon}{lon})
hum; buzz; drawn-out, low-pitched sound or action

\textbf{\hypertarget{mumucipcip}{mumucipcip}} \textit{n.} (\hyperlink{mumu}{mumu}+\allowbreak \hyperlink{cipcip}{cipcip})
hummingbird

\textbf{\hypertarget{'mumpai}{'mumpai}} \textit{n.} (Mar. ⟨{\devanagari{}मुंबई}⟩ [mumbaiː])
Mumbai

\textbf{\hypertarget{muc}{muc}} \textit{num.} (Spa. ⟨mucho⟩ [ˈmut͡ʃo])
much; many; very

\textbf{\hypertarget{muconalon}{muconalon}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{onalon}{onalon})
skyscraper; mansion

\textbf{\hypertarget{muclono}{muclono}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{lono}{lono})
be vibrant; be colourful; \hyperlink{muclonolon}{ʟᴏᴧ} has many hues and colours

\textbf{\hypertarget{muclonolon}{muclonolon}} \textit{n.} (\hyperlink{muclono}{muclono}+\allowbreak \hyperlink{lon}{lon})
vibrant; colourful

\textbf{\hypertarget{mucmai}{mucmai}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{mai}{mai})
go shopping; ʟᴏᴧ is going shopping

\textbf{\hypertarget{muccai}{muccai}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{cai}{cai})
love; adore; be attached; \hyperlink{muccailon}{ʟᴏᴧ} platonically loves ʟᴜᴍ

\textbf{\hypertarget{muccailon}{muccailon}} \textit{n.} (\hyperlink{muccai}{muccai}+\allowbreak \hyperlink{lon}{lon})
attached

\textbf{\hypertarget{muccih}{muccih}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{cih}{cih})
megacity; metropole

\textbf{\hypertarget{muccwelon}{muccwelon}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{cwelon}{cwelon})
lake; sea

\textbf{\hypertarget{muccwepucolon}{muccwepucolon}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{cwepucolon}{cwepucolon})
vast river

\textbf{\hypertarget{mucsite}{mucsite}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{site}{site})
be jagged; be zig-zag; be pointy; \hyperlink{mucsitelon}{ʟᴏᴧ} is jagged

\textbf{\hypertarget{mucsitelon}{mucsitelon}} \textit{n.} (\hyperlink{mucsite}{mucsite}+\allowbreak \hyperlink{lon}{lon})
zig-zag; jagged; pointy

\textbf{\hypertarget{muckot}{muckot}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{kot}{kot})
polytheism; pantheon

\textbf{\hypertarget{muctec}{muctec}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{tec}{tec})
empire

\textbf{\hypertarget{muctecak}{muctecak}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{tecak}{tecak})
international

\textbf{\hypertarget{muctecaktilip}{muctecaktilip}} \textit{n.} (\hyperlink{muctecak}{muctecak}+\allowbreak \hyperlink{tilip}{tilip})
auxlang; international auxiliary language

\textbf{\hypertarget{muctayl}{muctayl}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{tayl}{tayl})
continent; large landmass bounded by ocean on most sides, e.g. Eurasia, North America

\textbf{\hypertarget{muctue}{muctue}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{tue}{tue})
be rich; be wealthy; \hyperlink{muctuelon}{ʟᴏᴧ} is financially rich

\textbf{\hypertarget{muctuelon}{muctuelon}} \textit{n.} (\hyperlink{muctue}{muctue}+\allowbreak \hyperlink{lon}{lon})
rich; wealthy

\textbf{\hypertarget{muctunci}{muctunci}} \textit{v.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{tunci}{tunci})
govern as a republic; \hyperlink{muctuncilum}{ʟᴜᴍ} rules ʟᴏᴧ

\textbf{\hypertarget{muctuncilum}{muctuncilum}} \textit{n.} (\hyperlink{muctunci}{muctunci}+\allowbreak \hyperlink{lum}{lum})
representative; house; legislature

\textbf{\hypertarget{muctuncilyot}{muctuncilyot}} \textit{n.} (\hyperlink{muctunci}{muctunci}+\allowbreak \hyperlink{lyot}{lyot})
republic; representative democracy

\textbf{\hypertarget{mucpatolon}{mucpatolon}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{patolon}{patolon})
boulder

\textbf{\hypertarget{mucpil}{mucpil}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{pil}{pil})
vast mountain

\textbf{\hypertarget{mucpihtayl}{mucpihtayl}} \textit{n.} (\hyperlink{muc}{muc}+\allowbreak \hyperlink{pih}{pih}+\allowbreak \hyperlink{tayl}{tayl})
archipelago

\textbf{\hypertarget{'musampiki}{'musampiki}} \textit{n.} (Por. ⟨Moçambique⟩ [musɐ̃ˈbikɨ])
Island of Mozambique

\textbf{\hypertarget{'musampikiak}{'musampikiak}} \textit{n.} (\hyperlink{'musampiki}{'musampiki}+\allowbreak \hyperlink{ak}{ak})
Mozambican; from Mozambique

\textbf{\hypertarget{'musampikitec}{'musampikitec}} \textit{n.} (\hyperlink{'musampiki}{'musampiki}+\allowbreak \hyperlink{tec}{tec})
Mozambique; the Republic of Mozambique

\textbf{\hypertarget{'musampikitecwon}{'musampikitecwon}} \textit{n.} (\hyperlink{'musampikitec}{'musampikitec}+\allowbreak \hyperlink{won}{won})
Mozambican; the Mozambican people

\textbf{\hypertarget{muf}{muf}} \textit{n.} (ono. [muː])
bovid; cow; calf; beef; buffalo; antelope; sheep; lamb; mutton; goat; kid; Bovidae

\textbf{\hypertarget{muk}{muk}} \textit{n.} (Ben. ⟨{\bengali{}মুখ}⟩ [mukʰ])
face; front part of a head

\textbf{\hypertarget{mukak}{mukak}} \textit{n.} (\hyperlink{muk}{muk}+\allowbreak \hyperlink{ak}{ak})
facial

\textbf{\hypertarget{mut}{mut}} \textit{n.} (\hyperlink{pil}{\sout{pil}})
valley; large locally depressed region of a planet’s crust

\textbf{\hypertarget{muta}{muta}} \textit{v.} (\hyperlink{pila}{\sout{pila}})
be purple; be violet; \hyperlink{mutalon}{ʟᴏᴧ} reflects short and long wavelength light

\textbf{\hypertarget{mutalon}{mutalon}} \textit{n.} (\hyperlink{muta}{muta}+\allowbreak \hyperlink{lon}{lon})
purple; violet

\textbf{\hypertarget{mutak}{mutak}} \textit{n.} (\hyperlink{mut}{mut}+\allowbreak \hyperlink{ak}{ak})
valley

\textbf{\hypertarget{mutaki}{mutaki}} \textit{v.} (\hyperlink{muta}{muta}+\allowbreak \hyperlink{ki}{ki})
colour purple; colour violet; ʟєꜱ colours ʟᴏᴧ purple

\textbf{\hypertarget{mutatawh}{mutatawh}} \textit{n.} (\hyperlink{muta}{muta}+\allowbreak \hyperlink{tawh}{tawh})
plum

\textbf{\hypertarget{muti}{muti}} \textit{v.} (\hyperlink{pilu}{\sout{pilu}})
be orange; be warm; \hyperlink{mutilon}{ʟᴏᴧ} reflects long and medium wavelength light

\textbf{\hypertarget{mutilais}{mutilais}} \textit{n.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{lais}{lais})
carrot

\textbf{\hypertarget{mutilon}{mutilon}} \textit{n.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{lon}{lon})
orange; warm

\textbf{\hypertarget{muticeluk}{muticeluk}} \textit{n.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{celuk}{celuk})
orange; mandarin; tangerine

\textbf{\hypertarget{mutiki}{mutiki}} \textit{v.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{ki}{ki})
colour orange; ʟєꜱ colours ʟᴏᴧ orange

\textbf{\hypertarget{mutikwah}{mutikwah}} \textit{n.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{kwah}{kwah})
cantelope

\textbf{\hypertarget{mutitawh}{mutitawh}} \textit{n.} (\hyperlink{muti}{muti}+\allowbreak \hyperlink{tawh}{tawh})
apricot

\textbf{\hypertarget{myawf}{myawf}} \textit{n.} (ono. [mjaw])
feline; cat; kitten; Felidae

\textbf{\hypertarget{myawfak}{myawfak}} \textit{n.} (\hyperlink{myawf}{myawf}+\allowbreak \hyperlink{ak}{ak})
feline

\textbf{\hypertarget{mwe}{mwe}} \textit{v.} (\hyperlink{pyo}{\sout{pyo}})
be angry; be mad; \hyperlink{mwelon}{ʟᴏᴧ} is angry about \hyperlink{mwelum}{ʟᴜᴍ}

\textbf{\hypertarget{mwelon}{mwelon}} \textit{n.} (\hyperlink{mwe}{mwe}+\allowbreak \hyperlink{lon}{lon})
angry; mad

\textbf{\hypertarget{mwelum}{mwelum}} \textit{n.} (\hyperlink{mwe}{mwe}+\allowbreak \hyperlink{lum}{lum})
maddening

\textbf{\hypertarget{mweki}{mweki}} \textit{v.} (\hyperlink{mwe}{mwe}+\allowbreak \hyperlink{ki}{ki})
anger; embolden; ʟєꜱ makes ʟᴏᴧ angry about ʟᴜᴍ

\textbf{\hypertarget{mwepowi}{mwepowi}} \textit{v.} (\hyperlink{mwe}{mwe}+\allowbreak \hyperlink{powi}{powi})
be bold; be courageous; be brave; be brash; be hot-headed; \hyperlink{mwepowilon}{ʟᴏᴧ} is quick to anger

\textbf{\hypertarget{mwepowilon}{mwepowilon}} \textit{n.} (\hyperlink{mwepowi}{mwepowi}+\allowbreak \hyperlink{lon}{lon})
bold; courageous; brave; brash; hot-headed

\textbf{\hypertarget{mwepowiki}{mwepowiki}} \textit{v.} (\hyperlink{mwepowi}{mwepowi}+\allowbreak \hyperlink{ki}{ki})
embolden; encourage; embraven; ʟєꜱ makes ʟᴏᴧ bolder

\textbf{\hypertarget{mwa}{mwa}} \textit{v.} (ono. [mwa])
kiss; snog; make out; \hyperlink{mwales}{ʟєꜱ} kisses \hyperlink{mwalon}{ʟᴏᴧ}

\textbf{\hypertarget{mwales}{mwales}} \textit{n.} (\hyperlink{mwa}{mwa}+\allowbreak \hyperlink{les}{les})
kisser

\textbf{\hypertarget{mwalon}{mwalon}} \textit{n.} (\hyperlink{mwa}{mwa}+\allowbreak \hyperlink{lon}{lon})
kissee

\textbf{\hypertarget{mwoni}{mwoni}} \textit{v.} (Cmn. ⟨{\chinese{}模拟}⟩ [mwɔ˧˥ni˧˩˧])
model; replicate; image; \hyperlink{mwoniles}{ʟєꜱ} makes \hyperlink{mwonilon}{ʟᴏᴧ} after \hyperlink{mwonilum}{ʟᴜᴍ}

\textbf{\hypertarget{mwoniles}{mwoniles}} \textit{n.} (\hyperlink{mwoni}{mwoni}+\allowbreak \hyperlink{les}{les})
modeler

\textbf{\hypertarget{mwonilon}{mwonilon}} \textit{n.} (\hyperlink{mwoni}{mwoni}+\allowbreak \hyperlink{lon}{lon})
model; image

\textbf{\hypertarget{mwonilum}{mwonilum}} \textit{n.} (\hyperlink{mwoni}{mwoni}+\allowbreak \hyperlink{lum}{lum})
source; original

\textbf{\hypertarget{mwok}{mwok}} \textit{n.} (Cmn. ⟨{\chinese{}蘑菇}⟩ [mwɔ˧˥ku])
mushroom; toadstool; superterranean fungus with a stem and cap

\section{H}

\textbf{\hypertarget{'helium}{'helium}} \textit{n.} (Lat. ⟨helium⟩ [hɛlɪʊ̃])
helium

\textbf{\hypertarget{'helsekowina}{'helsekowina}} \textit{n.} (Bos. ⟨Hercegovina⟩ [xɛ̌rtsɛɡov̞ina])
Herzegovina

\textbf{\hypertarget{'helsekowinaak}{'helsekowinaak}} \textit{n.} (\hyperlink{'helsekowina}{'helsekowina}+\allowbreak \hyperlink{ak}{ak})
Herzegovinian; from Herzegovina

\textbf{\hypertarget{'helsekowinawon}{'helsekowinawon}} \textit{n.} (\hyperlink{'helsekowina}{'helsekowina}+\allowbreak \hyperlink{won}{won})
Herzegovinian; the Herzegovinian people

\textbf{\hypertarget{hes}{hes}} \textit{num.} (Eng. ⟨hex⟩ [hɛks])
G; sixteen; only used to describe hexadecimal

\textbf{\hypertarget{hesak}{hesak}} \textit{n.} (\hyperlink{hes}{hes}+\allowbreak \hyperlink{ak}{ak})
sixteenth

\textbf{\hypertarget{heta}{heta}} \textit{v.} (\hyperlink{cola}{\sout{cola}})
be narrow; be acute; be small; be little; \hyperlink{hetalon}{ʟᴏᴧ} spans a narrow angle from the point of view of \hyperlink{hetalum}{ʟᴜᴍ}

\textbf{\hypertarget{hetalon}{hetalon}} \textit{n.} (\hyperlink{heta}{heta}+\allowbreak \hyperlink{lon}{lon})
dot; point; narrow; acute; small; little

\textbf{\hypertarget{hetalum}{hetalum}} \textit{n.} (\hyperlink{heta}{heta}+\allowbreak \hyperlink{lum}{lum})
corner

\textbf{\hypertarget{hetaki}{hetaki}} \textit{v.} (\hyperlink{heta}{heta}+\allowbreak \hyperlink{ki}{ki})
narrow; shrink; contract; ʟєꜱ makes ʟᴏᴧ span a smaller angle from the point of view of ʟᴜᴍ

\textbf{\hypertarget{hetut}{hetut}} \textit{n.} (\hyperlink{colil}{\sout{colil}})
soul; spirit; metaphysical essence

\textbf{\hypertarget{hepu}{hepu}} \textit{v.} (\hyperlink{comi}{\sout{comi}})
be sparse; be spacious; be infrequent; be loosely distributed; be coarse; \hyperlink{hepulon}{ʟᴏᴧ} is few and far between in \hyperlink{hepulum}{ʟᴜᴍ}

\textbf{\hypertarget{hepulon}{hepulon}} \textit{n.} (\hyperlink{hepu}{hepu}+\allowbreak \hyperlink{lon}{lon})
sparse; infrequent; loosely distributed; coarse

\textbf{\hypertarget{hepulum}{hepulum}} \textit{n.} (\hyperlink{hepu}{hepu}+\allowbreak \hyperlink{lum}{lum})
space; room; open space; spacious

\textbf{\hypertarget{hepuki}{hepuki}} \textit{v.} (\hyperlink{hepu}{hepu}+\allowbreak \hyperlink{ki}{ki})
spread out; separate; distribute; ʟєꜱ decreases the spacial frequency of ʟᴏᴧ

\textbf{\hypertarget{hai}{hai}} \textit{v.} (Eng. ⟨high⟩ [hɑɪ̯])
be high-pitched; be shrill; \hyperlink{hailon}{ʟᴏᴧ} is highly pitched

\textbf{\hypertarget{hailon}{hailon}} \textit{n.} (\hyperlink{hai}{hai}+\allowbreak \hyperlink{lon}{lon})
high note; high-pitched; shrill

\textbf{\hypertarget{hailyan}{hailyan}} \textit{n.} (\hyperlink{hai}{hai}+\allowbreak \hyperlink{lyan}{lyan})
pitch; frequency

\textbf{\hypertarget{hailyanoltolum}{hailyanoltolum}} \textit{n.} (\hyperlink{hailyan}{hailyan}+\allowbreak \hyperlink{oltolum}{oltolum})
melody; tune

\textbf{\hypertarget{haiki}{haiki}} \textit{v.} (\hyperlink{hai}{hai}+\allowbreak \hyperlink{ki}{ki})
raise; pitch up; modulate; ʟєꜱ raises the pitch of ʟᴏᴧ

\textbf{\hypertarget{hau}{hau}} \textit{v.} (\hyperlink{cai}{\sout{cai}})
dislike; be averse; be bad; disfavour; be unappealing; be displeasing; want not; be ugly; be gross; be negative; \hyperlink{haulon}{ʟᴏᴧ} has negative inclinations toward \hyperlink{haulum}{ʟᴜᴍ}

\textbf{\hypertarget{haulon}{haulon}} \textit{n.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{lon}{lon})
pessimist; -phobe; averse; unappealing; displeasing; negative

\textbf{\hypertarget{haulum}{haulum}} \textit{n.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{lum}{lum})
unfavourable; anathema; least favourite; bad; ugly; gross

\textbf{\hypertarget{haulyan}{haulyan}} \textit{n.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{lyan}{lyan})
cost

\textbf{\hypertarget{haulyot}{haulyot}} \textit{n.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{lyot}{lyot})
hell

\textbf{\hypertarget{hauki}{hauki}} \textit{v.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{ki}{ki})
discourage; worsen; insult; argue against; negatively impact; \hyperlink{haukiles}{ʟєꜱ} lowers \hyperlink{haukilon}{ʟᴏᴧ}’s opinion of ʟᴜᴍ

\textbf{\hypertarget{haukiles}{haukiles}} \textit{n.} (\hyperlink{hauki}{hauki}+\allowbreak \hyperlink{les}{les})
discourager; worsener

\textbf{\hypertarget{haukilon}{haukilon}} \textit{n.} (\hyperlink{hauki}{hauki}+\allowbreak \hyperlink{lon}{lon})
discouraged

\textbf{\hypertarget{hauti}{hauti}} \textit{v.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{ti}{ti})
dissent; disapprove; ʟєꜱ disapproves of ʟᴜᴍ to ʟᴏᴧ

\textbf{\hypertarget{hautiku}{hautiku}} \textit{v.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{tiku}{tiku})
be unlucky; be unfortunate; that \hyperlink{hautikulon}{ʟᴏᴧ} happens is unlucky

\textbf{\hypertarget{hautikulon}{hautikulon}} \textit{n.} (\hyperlink{hautiku}{hautiku}+\allowbreak \hyperlink{lon}{lon})
unlucky; unfortunate

\textbf{\hypertarget{haupowi}{haupowi}} \textit{v.} (\hyperlink{hau}{hau}+\allowbreak \hyperlink{powi}{powi})
be dangerous; \hyperlink{haupowilum}{ʟᴜᴍ} is dangerous to ʟᴏᴧ

\textbf{\hypertarget{haupowilum}{haupowilum}} \textit{n.} (\hyperlink{haupowi}{haupowi}+\allowbreak \hyperlink{lum}{lum})
danger; dangerous

\textbf{\hypertarget{haupowinyo}{haupowinyo}} \textit{v.} (\hyperlink{haupowi}{haupowi}+\allowbreak \hyperlink{nyo}{nyo})
be safe; be secure; \hyperlink{haupowinyolum}{ʟᴜᴍ} is safe for \hyperlink{haupowinyolon}{ʟᴏᴧ}

\textbf{\hypertarget{haupowinyolon}{haupowinyolon}} \textit{n.} (\hyperlink{haupowinyo}{haupowinyo}+\allowbreak \hyperlink{lon}{lon})
secure

\textbf{\hypertarget{haupowinyolum}{haupowinyolum}} \textit{n.} (\hyperlink{haupowinyo}{haupowinyo}+\allowbreak \hyperlink{lum}{lum})
safe

\textbf{\hypertarget{haupowinyolyan}{haupowinyolyan}} \textit{n.} (\hyperlink{haupowinyo}{haupowinyo}+\allowbreak \hyperlink{lyan}{lyan})
safety

\textbf{\hypertarget{'hayk}{'hayk}} \textit{n.} (Hye. ⟨{\armenian{}Հայք}⟩ [hɑjkʰ])
Armenian; the Armenian people

\textbf{\hypertarget{'haykak}{'haykak}} \textit{n.} (\hyperlink{'hayk}{'hayk}+\allowbreak \hyperlink{ak}{ak})
Armenian; from Armenia

\textbf{\hypertarget{'hayktec}{'hayktec}} \textit{n.} (\hyperlink{'hayk}{'hayk}+\allowbreak \hyperlink{tec}{tec})
Armenia

\textbf{\hypertarget{'hayktilip}{'hayktilip}} \textit{n.} (\hyperlink{'hayk}{'hayk}+\allowbreak \hyperlink{tilip}{tilip})
Armenian; the Armenian language

\textbf{\hypertarget{'halwati}{'halwati}} \textit{n.} (Hrv. ⟨Hrvati⟩ [xr̩ʋăːti])
Croat; the Croat people

\textbf{\hypertarget{'halwatiak}{'halwatiak}} \textit{n.} (\hyperlink{'halwati}{'halwati}+\allowbreak \hyperlink{ak}{ak})
Croatian; from Croatia

\textbf{\hypertarget{'halwatitec}{'halwatitec}} \textit{n.} (\hyperlink{'halwati}{'halwati}+\allowbreak \hyperlink{tec}{tec})
Croatia

\textbf{\hypertarget{'halwatitilip}{'halwatitilip}} \textit{n.} (\hyperlink{'halwati}{'halwati}+\allowbreak \hyperlink{tilip}{tilip})
Croatian; the Croatian language

\textbf{\hypertarget{hawa}{hawa}} \textit{v.} (ono. [ˈha̤ːa̤ː])
yawn; \hyperlink{hawales}{ʟєꜱ} yawns \hyperlink{hawalon}{ʟᴏᴧ}

\textbf{\hypertarget{'hawayi}{'hawayi}} \textit{n.} (Haw. ⟨Hawaiʻi⟩ [həˈvɐjʔi])
Hawaii (landmass)

\textbf{\hypertarget{'hawayiak}{'hawayiak}} \textit{n.} (\hyperlink{'hawayi}{'hawayi}+\allowbreak \hyperlink{ak}{ak})
Hawaiian; Kamaʻaina; from Hawaii

\textbf{\hypertarget{'hawayikwelyot}{'hawayikwelyot}} \textit{n.} (\hyperlink{'hawayi}{'hawayi}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Hawaii (archipelago)

\textbf{\hypertarget{'hawayikwelyotwon}{'hawayikwelyotwon}} \textit{n.} (\hyperlink{'hawayikwelyot}{'hawayikwelyot}+\allowbreak \hyperlink{won}{won})
Hawaiian; the Hawaiian people

\textbf{\hypertarget{'hawayitec}{'hawayitec}} \textit{n.} (\hyperlink{'hawayi}{'hawayi}+\allowbreak \hyperlink{tec}{tec})
Hawaii; the State of Hawaii

\textbf{\hypertarget{'hawayitilip}{'hawayitilip}} \textit{n.} (\hyperlink{'hawayi}{'hawayi}+\allowbreak \hyperlink{tilip}{tilip})
Hawaiian; the Hawaiian language

\textbf{\hypertarget{hawales}{hawales}} \textit{n.} (\hyperlink{hawa}{hawa}+\allowbreak \hyperlink{les}{les})
one who yawns

\textbf{\hypertarget{hawalon}{hawalon}} \textit{n.} (\hyperlink{hawa}{hawa}+\allowbreak \hyperlink{lon}{lon})
yawn

\textbf{\hypertarget{'hawnkon}{'hawnkon}} \textit{n.} (Yue. ⟨{\chinese{}香港}⟩ [hœːŋ˥kɔːŋ˧˥])
Hong Kong

\textbf{\hypertarget{'hawsa}{'hawsa}} \textit{n.} (Hau. ⟨Hausa⟩ [hawsa])
Hausa; Ausa; the Hausa people

\textbf{\hypertarget{'hawsaak}{'hawsaak}} \textit{n.} (\hyperlink{'hawsa}{'hawsa}+\allowbreak \hyperlink{ak}{ak})
Hausa; of the Hausa

\textbf{\hypertarget{'hawsatilip}{'hawsatilip}} \textit{n.} (\hyperlink{'hawsa}{'hawsa}+\allowbreak \hyperlink{tilip}{tilip})
Hausa; the Hausa language

\textbf{\hypertarget{hawku}{hawku}} \textit{v.} (\hyperlink{cayni}{\sout{cayni}})
be matte; be dull; be rough; \hyperlink{hawkulon}{ʟᴏᴧ} reflects light diffusely

\textbf{\hypertarget{hawkulon}{hawkulon}} \textit{n.} (\hyperlink{hawku}{hawku}+\allowbreak \hyperlink{lon}{lon})
matte; dull; rough

\textbf{\hypertarget{hawkuki}{hawkuki}} \textit{v.} (\hyperlink{hawku}{hawku}+\allowbreak \hyperlink{ki}{ki})
matte; ʟєꜱ makes ʟᴏᴧ become matte

\textbf{\hypertarget{'han}{'han}} \textit{n.} (Cmn. ⟨{\chinese{}漢}⟩ [xan˥˩])
Han; the Han people

\textbf{\hypertarget{'hanak}{'hanak}} \textit{n.} (\hyperlink{'han}{'han}+\allowbreak \hyperlink{ak}{ak})
Han; of the Han

\textbf{\hypertarget{'hanfitilip}{'hanfitilip}} \textit{n.} (\hyperlink{'han}{'han}+\allowbreak \hyperlink{fitilip}{fitilip})
Han folk religion; Chinese folk religion

\textbf{\hypertarget{haha}{haha}} \textit{v.} (ono. [ha ha])
laugh; \hyperlink{hahales}{ʟєꜱ} laughs out \hyperlink{hahalon}{ʟᴏᴧ}

\textbf{\hypertarget{hahales}{hahales}} \textit{n.} (\hyperlink{haha}{haha}+\allowbreak \hyperlink{les}{les})
laugher

\textbf{\hypertarget{hahalon}{hahalon}} \textit{n.} (\hyperlink{haha}{haha}+\allowbreak \hyperlink{lon}{lon})
laughter

\textbf{\hypertarget{hacu}{hacu}} \textit{v.} (ono. [haˈt͡ʃuh])
sneeze; \hyperlink{hacules}{ʟєꜱ} sneezes out \hyperlink{haculon}{ʟᴏᴧ}

\textbf{\hypertarget{hacules}{hacules}} \textit{n.} (\hyperlink{hacu}{hacu}+\allowbreak \hyperlink{les}{les})
sneezer

\textbf{\hypertarget{haculon}{haculon}} \textit{n.} (\hyperlink{hacu}{hacu}+\allowbreak \hyperlink{lon}{lon})
sneeze

\textbf{\hypertarget{hat}{hat}} \textit{num.} (Ben. ⟨{\bengali{}আট}⟩ [aʈ])
8; eight

\textbf{\hypertarget{hatak}{hatak}} \textit{n.} (\hyperlink{hat}{hat}+\allowbreak \hyperlink{ak}{ak})
eighth

\textbf{\hypertarget{hatnul}{hatnul}} \textit{num.} (\hyperlink{hat}{hat}+\allowbreak \hyperlink{nul}{nul})
80; eighty

\textbf{\hypertarget{hatnulnul}{hatnulnul}} \textit{num.} (\hyperlink{hat}{hat}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
800; eight hundred

\textbf{\hypertarget{hatcyenlektun}{hatcyenlektun}} \textit{n.} (\hyperlink{hat}{hat}+\allowbreak \hyperlink{cyenlektun}{cyenlektun})
octopus

\textbf{\hypertarget{ho}{ho}} \textit{v.} (Cmn. ⟨{\chinese{}厚}⟩ [xoʊ̯˥˩])
be thick; \hyperlink{holon}{ʟᴏᴧ} is thick in its smallest dimension

\textbf{\hypertarget{'ho}{'ho}} \textit{n.} (ono. [h])
h; /h/; glottal fricative

\textbf{\hypertarget{hol}{hol}} \textit{n.} (Sot. ⟨holo⟩ [holo])
hippopotamus; hippo; Hippopotamidae

\textbf{\hypertarget{holon}{holon}} \textit{n.} (\hyperlink{ho}{ho}+\allowbreak \hyperlink{lon}{lon})
slab; thick

\textbf{\hypertarget{holyan}{holyan}} \textit{n.} (\hyperlink{ho}{ho}+\allowbreak \hyperlink{lyan}{lyan})
thickness; minimum dimension

\textbf{\hypertarget{'honolulu}{'honolulu}} \textit{n.} (Haw. ⟨Honolulu⟩ [honoˈlulu])
Honolulu

\textbf{\hypertarget{hom}{hom}} \textit{n.} (Eng. ⟨home⟩ [hoʊ̯m])
home; place of residence of an individual or family

\textbf{\hypertarget{'homeopati}{'homeopati}} \textit{n.} (Deu. ⟨homöopathie⟩ [hoːmœoːpatiː])
homeopathy

\textbf{\hypertarget{homak}{homak}} \textit{n.} (\hyperlink{hom}{hom}+\allowbreak \hyperlink{ak}{ak})
domestic

\textbf{\hypertarget{hoki}{hoki}} \textit{v.} (\hyperlink{ho}{ho}+\allowbreak \hyperlink{ki}{ki})
thicken; \hyperlink{hokiles}{ʟєꜱ} thickens ʟᴏᴧ

\textbf{\hypertarget{hokiles}{hokiles}} \textit{n.} (\hyperlink{hoki}{hoki}+\allowbreak \hyperlink{les}{les})
thickener

\textbf{\hypertarget{'hokyen}{'hokyen}} \textit{n.} (Nan. ⟨{\chinese{}福建}⟩ [hok˨kjeŋ˨˩˧])
Fujian; Fujien; Min

\textbf{\hypertarget{'hokyenak}{'hokyenak}} \textit{n.} (\hyperlink{'hokyen}{'hokyen}+\allowbreak \hyperlink{ak}{ak})
Fujianese; from Fujian

\textbf{\hypertarget{'hokyenwon}{'hokyenwon}} \textit{n.} (\hyperlink{'hokyen}{'hokyen}+\allowbreak \hyperlink{won}{won})
Fujianese; Fujian; the Fujianese people

\textbf{\hypertarget{'hokyentilip}{'hokyentilip}} \textit{n.} (\hyperlink{'hokyen}{'hokyen}+\allowbreak \hyperlink{tilip}{tilip})
Min Chinese; the Min languages

\textbf{\hypertarget{'hial}{'hial}} \textit{n.} (Por. ⟨real⟩ [ʁɨˈaɫ])
real; R\$

\textbf{\hypertarget{hila}{hila}} \textit{v.} (Hin. ⟨{\devanagari{}हिला}⟩ [ɦilaː])
move; jostle; be energetic; be restless; go; \hyperlink{hilalon}{ʟᴏᴧ} is deforming and moving relative to \hyperlink{hilalum}{ʟᴜᴍ}

\textbf{\hypertarget{hilaec}{hilaec}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{ec}{ec})
muscle

\textbf{\hypertarget{hilalon}{hilalon}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{lon}{lon})
energetic; restless

\textbf{\hypertarget{hilalum}{hilalum}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{lum}{lum})
reference; frame of reference

\textbf{\hypertarget{hilalyan}{hilalyan}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{lyan}{lyan})
motion; energy

\textbf{\hypertarget{hilanoki}{hilanoki}} \textit{v.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{noki}{noki})
explore; probe; ʟєꜱ sends \hyperlink{hilanokilon}{ʟᴏᴧ} to ʟᴜᴍ to learn about it

\textbf{\hypertarget{hilanokilon}{hilanokilon}} \textit{n.} (\hyperlink{hilanoki}{hilanoki}+\allowbreak \hyperlink{lon}{lon})
probe

\textbf{\hypertarget{hilamocaki}{hilamocaki}} \textit{v.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{mocaki}{mocaki})
dance; \hyperlink{hilamocakiles}{ʟєꜱ} dances the \hyperlink{hilamocakilum}{ʟᴜᴍ} for ʟᴏᴧ

\textbf{\hypertarget{hilamocakiles}{hilamocakiles}} \textit{n.} (\hyperlink{hilamocaki}{hilamocaki}+\allowbreak \hyperlink{les}{les})
dancer

\textbf{\hypertarget{hilamocakilum}{hilamocakilum}} \textit{n.} (\hyperlink{hilamocaki}{hilamocaki}+\allowbreak \hyperlink{lum}{lum})
dance; dance move

\textbf{\hypertarget{hilamocakilyot}{hilamocakilyot}} \textit{n.} (\hyperlink{hilamocaki}{hilamocaki}+\allowbreak \hyperlink{lyot}{lyot})
dance floor

\textbf{\hypertarget{hilasoma}{hilasoma}} \textit{v.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{soma}{soma})
do physics; \hyperlink{hilasomales}{ʟєꜱ} studies motion to learn about \hyperlink{hilasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{hilasomales}{hilasomales}} \textit{n.} (\hyperlink{hilasoma}{hilasoma}+\allowbreak \hyperlink{les}{les})
physicist

\textbf{\hypertarget{hilasomalon}{hilasomalon}} \textit{n.} (\hyperlink{hilasoma}{hilasoma}+\allowbreak \hyperlink{lon}{lon})
physics

\textbf{\hypertarget{hilaki}{hilaki}} \textit{v.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{ki}{ki})
set off; set in motion; move; energise; \hyperlink{hilakiles}{ʟєꜱ} makes ʟᴏᴧ start moving relative to ʟᴜᴍ

\textbf{\hypertarget{hilakiles}{hilakiles}} \textit{n.} (\hyperlink{hilaki}{hilaki}+\allowbreak \hyperlink{les}{les})
motor; actuator

\textbf{\hypertarget{hilatiluat}{hilatiluat}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{tiluat}{tiluat})
mobile phone; cellural phone; cell phone

\textbf{\hypertarget{hilapowi}{hilapowi}} \textit{v.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{powi}{powi})
be mobile; be movable; be loose; be portable; \hyperlink{hilapowilon}{ʟᴏᴧ} moves freely and easily relative to ʟᴜᴍ

\textbf{\hypertarget{hilapowilon}{hilapowilon}} \textit{n.} (\hyperlink{hilapowi}{hilapowi}+\allowbreak \hyperlink{lon}{lon})
mobile; movable; loose; portable

\textbf{\hypertarget{hilapowinu}{hilapowinu}} \textit{v.} (\hyperlink{hilapowi}{hilapowi}+\allowbreak \hyperlink{nu}{nu})
stick; bind; tighten; fasten; trap; \hyperlink{hilapowinules}{ʟєꜱ} sticks ʟᴏᴧ to ʟᴜᴍ

\textbf{\hypertarget{hilapowinules}{hilapowinules}} \textit{n.} (\hyperlink{hilapowinu}{hilapowinu}+\allowbreak \hyperlink{les}{les})
tightener

\textbf{\hypertarget{hilapowinuluat}{hilapowinuluat}} \textit{n.} (\hyperlink{hilapowinu}{hilapowinu}+\allowbreak \hyperlink{luat}{luat})
glue; bond; fastener

\textbf{\hypertarget{hilapowinufut}{hilapowinufut}} \textit{n.} (\hyperlink{hilapowinu}{hilapowinu}+\allowbreak \hyperlink{fut}{fut})
banana; plantain

\textbf{\hypertarget{hilapowinyo}{hilapowinyo}} \textit{v.} (\hyperlink{hilapowi}{hilapowi}+\allowbreak \hyperlink{nyo}{nyo})
be stuck; stick; be bound; be immobile; be immovable; be tight; be fixed; be fast; \hyperlink{hilapowinyolon}{ʟᴏᴧ} is bound to \hyperlink{hilapowinyolum}{ʟᴜᴍ}

\textbf{\hypertarget{hilapowinyolon}{hilapowinyolon}} \textit{n.} (\hyperlink{hilapowinyo}{hilapowinyo}+\allowbreak \hyperlink{lon}{lon})
sticker; stuck; bound; immobile; immovable; tight; fixed; fast

\textbf{\hypertarget{hilapowinyolum}{hilapowinyolum}} \textit{n.} (\hyperlink{hilapowinyo}{hilapowinyo}+\allowbreak \hyperlink{lum}{lum})
binding; binder

\textbf{\hypertarget{hilapowiki}{hilapowiki}} \textit{v.} (\hyperlink{hilapowi}{hilapowi}+\allowbreak \hyperlink{ki}{ki})
unstick; unbind; mobilise; loosen; extricate; unfasten; \hyperlink{hilapowikiles}{ʟєꜱ} frees ʟᴏᴧ to move relative to ʟᴜᴍ

\textbf{\hypertarget{hilapowikiles}{hilapowikiles}} \textit{n.} (\hyperlink{hilapowiki}{hilapowiki}+\allowbreak \hyperlink{les}{les})
loosener

\textbf{\hypertarget{hilapic}{hilapic}} \textit{n.} (\hyperlink{hila}{hila}+\allowbreak \hyperlink{pic}{pic})
coffee; Coffea

\textbf{\hypertarget{'hintu}{'hintu}} \textit{n.} (Hin. ⟨{\devanagari{}हिन्दू}⟩ [ɦɪnduː])
India; South Asia; the Hind; the Indian sub-continent

\textbf{\hypertarget{'hintuak}{'hintuak}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{ak}{ak})
Indian; from India

\textbf{\hypertarget{'hintulawt}{'hintulawt}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{lawt}{lawt})
Indian Ocean

\textbf{\hypertarget{'hintulawtak}{'hintulawtak}} \textit{n.} (\hyperlink{'hintulawt}{'hintulawt}+\allowbreak \hyperlink{ak}{ak})
Indian Oceanic

\textbf{\hypertarget{'hintufitilip}{'hintufitilip}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{fitilip}{fitilip})
Hinduism

\textbf{\hypertarget{'hintufitilipwon}{'hintufitilipwon}} \textit{n.} (\hyperlink{'hintufitilip}{'hintufitilip}+\allowbreak \hyperlink{won}{won})
Hindu; followers of Hinduism

\textbf{\hypertarget{'hintutec}{'hintutec}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{tec}{tec})
India; Hindustan; the Republic of India

\textbf{\hypertarget{'hintutecwon}{'hintutecwon}} \textit{n.} (\hyperlink{'hintutec}{'hintutec}+\allowbreak \hyperlink{won}{won})
Indian; the Indian people

\textbf{\hypertarget{'hintutilip}{'hintutilip}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{tilip}{tilip})
Hindi; the Hindi language

\textbf{\hypertarget{'hintu'pakistantilip}{'hintu'pakistantilip}} \textit{n.} (\hyperlink{'hintu}{'hintu}+\allowbreak \hyperlink{'pakistan}{'pakistan}+\allowbreak \hyperlink{tilip}{tilip})
Hindustani; the Hindustani language

\textbf{\hypertarget{'hintu'pakistantilipwon}{'hintu'pakistantilipwon}} \textit{n.} (\hyperlink{'hintu'pakistantilip}{'hintu'pakistantilip}+\allowbreak \hyperlink{won}{won})
Hindustani speakers

\textbf{\hypertarget{hiha}{hiha}} \textit{v.} (ono. [hi̤ːha̤ː])
breathe; ʟєꜱ makes ʟᴏᴧ breathe

\textbf{\hypertarget{hihahyolon}{hihahyolon}} \textit{n.} (\hyperlink{hiha}{hiha}+\allowbreak \hyperlink{hyolon}{hyolon})
oxygen

\textbf{\hypertarget{hihacwelon}{hihacwelon}} \textit{n.} (\hyperlink{hiha}{hiha}+\allowbreak \hyperlink{cwelon}{cwelon})
mucus; snot

\textbf{\hypertarget{hihacwelonkoki}{hihacwelonkoki}} \textit{v.} (\hyperlink{hihacwelon}{hihacwelon}+\allowbreak \hyperlink{koki}{koki})
have runny nose; drip mucus; ʟєꜱ’s nose runs ʟᴏᴧ

\textbf{\hypertarget{hihin}{hihin}} \textit{n.} (ono. [hi hin])
equid; horse; zebra; pony; wild butt; Equidae

\textbf{\hypertarget{hihinak}{hihinak}} \textit{n.} (\hyperlink{hihin}{hihin}+\allowbreak \hyperlink{ak}{ak})
equine

\textbf{\hypertarget{hiki}{hiki}} \textit{v.} (ono. [hik])
hiccup; \hyperlink{hikiles}{ʟєꜱ} hiccups \hyperlink{hikilon}{ʟᴏᴧ}

\textbf{\hypertarget{hikiles}{hikiles}} \textit{n.} (\hyperlink{hiki}{hiki}+\allowbreak \hyperlink{les}{les})
one who hiccups

\textbf{\hypertarget{hikilon}{hikilon}} \textit{n.} (\hyperlink{hiki}{hiki}+\allowbreak \hyperlink{lon}{lon})
hiccup

\textbf{\hypertarget{'hitlocenium}{'hitlocenium}} \textit{n.} (Lat. ⟨hydrogenium⟩ [hidrɔd͡ʒɛnɪʊ̃])
hydrogen

\textbf{\hypertarget{hu}{hu}} \textit{v.} (Ibo. ⟨hụ⟩ [ɦʊ])
can see; see; view; \hyperlink{hulon}{ʟᴏᴧ} sees \hyperlink{hulum}{ʟᴜᴍ}

\textbf{\hypertarget{huec}{huec}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{ec}{ec})
eye; eyeball

\textbf{\hypertarget{huechu}{huechu}} \textit{v.} (\hyperlink{huec}{huec}+\allowbreak \hyperlink{hu}{hu})
make eye contact; ʟᴏᴧ has eye contact with ʟᴜᴍ

\textbf{\hypertarget{huak}{huak}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{ak}{ak})
visual; optic

\textbf{\hypertarget{huylu}{huylu}} \textit{v.} (\hyperlink{ciwti}{\sout{ciwti}})
be general; be vague; \hyperlink{huylulon}{ʟᴏᴧ} is general

\textbf{\hypertarget{huylulon}{huylulon}} \textit{n.} (\hyperlink{huylu}{huylu}+\allowbreak \hyperlink{lon}{lon})
general; vague

\textbf{\hypertarget{huyluki}{huyluki}} \textit{v.} (\hyperlink{huylu}{huylu}+\allowbreak \hyperlink{ki}{ki})
generalise; ʟєꜱ generalises ʟᴏᴧ

\textbf{\hypertarget{hulon}{hulon}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{lon}{lon})
seer

\textbf{\hypertarget{huli}{huli}} \textit{v.} (Fil. ⟨huli⟩ [huli])
be late; be recent; be after; be tardy; positive time; \hyperlink{hulilon}{ʟᴏᴧ} happens after ʟᴜᴍ

\textbf{\hypertarget{hulioleciuh}{hulioleciuh}} \textit{n.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{ole}{ole}+\allowbreak \hyperlink{ciuh}{ciuh})
asparagus; sparrow grass

\textbf{\hypertarget{hulilon}{hulilon}} \textit{n.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{lon}{lon})
future; late; recent; after; tardy

\textbf{\hypertarget{hulilyan}{hulilyan}} \textit{n.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{lyan}{lyan})
lateness

\textbf{\hypertarget{hulinoluat}{hulinoluat}} \textit{n.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{noluat}{noluat})
clock; watch

\textbf{\hypertarget{hulinoki}{hulinoki}} \textit{v.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{noki}{noki})
tertiarily educate; college; university; higher educate; \hyperlink{hulinokiles}{ʟєꜱ} teaches \hyperlink{hulinokilon}{ʟᴏᴧ}

\textbf{\hypertarget{hulinokiles}{hulinokiles}} \textit{n.} (\hyperlink{hulinoki}{hulinoki}+\allowbreak \hyperlink{les}{les})
professor

\textbf{\hypertarget{hulinokilon}{hulinokilon}} \textit{n.} (\hyperlink{hulinoki}{hulinoki}+\allowbreak \hyperlink{lon}{lon})
college student

\textbf{\hypertarget{hulinokilyot}{hulinokilyot}} \textit{n.} (\hyperlink{hulinoki}{hulinoki}+\allowbreak \hyperlink{lyot}{lyot})
college; university

\textbf{\hypertarget{hulinokilwel}{hulinokilwel}} \textit{n.} (\hyperlink{hulinoki}{hulinoki}+\allowbreak \hyperlink{lwel}{lwel})
tertiary education

\textbf{\hypertarget{hulisunnyama}{hulisunnyama}} \textit{v.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{sun}{sun}+\allowbreak \hyperlink{nyama}{nyama})
eat merienda; lunch late; eat linner; \hyperlink{hulisunnyamales}{ʟєꜱ} eats \hyperlink{hulisunnyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{hulisunnyamalwel}{hulisunnyamalwel}} \textit{n.} (\hyperlink{hulisunnyama}{hulisunnyama}+\allowbreak \hyperlink{lwel}{lwel})
linnertime

\textbf{\hypertarget{hulisunnyamalon}{hulisunnyamalon}} \textit{n.} (\hyperlink{hulisunnyama}{hulisunnyama}+\allowbreak \hyperlink{lon}{lon})
late lunch; linner

\textbf{\hypertarget{hulisunnyamales}{hulisunnyamales}} \textit{n.} (\hyperlink{hulisunnyama}{hulisunnyama}+\allowbreak \hyperlink{les}{les})
late luncher

\textbf{\hypertarget{huliki}{huliki}} \textit{v.} (\hyperlink{huli}{huli}+\allowbreak \hyperlink{ki}{ki})
delay; postpone; put off; push back; procrastinate; travel forward through time; \hyperlink{hulikiles}{ʟєꜱ} pushes ʟᴏᴧ forward through time

\textbf{\hypertarget{hulikiles}{hulikiles}} \textit{n.} (\hyperlink{huliki}{huliki}+\allowbreak \hyperlink{les}{les})
postponer

\textbf{\hypertarget{hulum}{hulum}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{lum}{lum})
image; picture; sight; view

\textbf{\hypertarget{hulumah}{hulumah}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{lumah}{lumah})
screen

\textbf{\hypertarget{hunu}{hunu}} \textit{v.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{nu}{nu})
hide; obscure; remove from view; ʟєꜱ makes ʟᴏᴧ stop seeing ʟᴜᴍ

\textbf{\hypertarget{humocaki}{humocaki}} \textit{v.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{mocaki}{mocaki})
screen; stream; show; \hyperlink{humocakiles}{ʟєꜱ} entertains ʟᴏᴧ visually with \hyperlink{humocakilum}{ʟᴜᴍ}

\textbf{\hypertarget{humocakiles}{humocakiles}} \textit{n.} (\hyperlink{humocaki}{humocaki}+\allowbreak \hyperlink{les}{les})
screener; streamer; television network

\textbf{\hypertarget{humocakiluat}{humocakiluat}} \textit{n.} (\hyperlink{humocaki}{humocaki}+\allowbreak \hyperlink{luat}{luat})
screen

\textbf{\hypertarget{humocakilum}{humocakilum}} \textit{n.} (\hyperlink{humocaki}{humocaki}+\allowbreak \hyperlink{lum}{lum})
video; movie; TV show

\textbf{\hypertarget{humocakilyot}{humocakilyot}} \textit{n.} (\hyperlink{humocaki}{humocaki}+\allowbreak \hyperlink{lyot}{lyot})
cinema

\textbf{\hypertarget{'humuhumunukunukuapua}{'humuhumunukunukuapua}} \textit{n.} (Haw. ⟨humuhumunukunukuapuaʻa⟩ [ˈhumuˈhumuˈnukuˈnukuˈwaːpuˈwɐʔə])
reef triggerfish; rectangular triggerfish

\textbf{\hypertarget{huc}{huc}} \textit{n.} (\hyperlink{cih}{\sout{cih}})
countryside; country; large but sparse distribution of human residences

\textbf{\hypertarget{hucalu}{hucalu}} \textit{v.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{calu}{calu})
watch; stare; ʟєꜱ forces ʟᴏᴧ to watch ʟᴜᴍ

\textbf{\hypertarget{hucak}{hucak}} \textit{n.} (\hyperlink{huc}{huc}+\allowbreak \hyperlink{ak}{ak})
rural

\textbf{\hypertarget{husaman}{husaman}} \textit{n.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{saman}{saman})
window

\textbf{\hypertarget{huki}{huki}} \textit{v.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{ki}{ki})
look; reveal; ʟєꜱ shows \hyperlink{hukilum}{ʟᴜᴍ} to ʟᴏᴧ visually

\textbf{\hypertarget{hukilum}{hukilum}} \textit{n.} (\hyperlink{huki}{huki}+\allowbreak \hyperlink{lum}{lum})
show; visualisation

\textbf{\hypertarget{hutyeh}{hutyeh}} \textit{n.} (Cmn. ⟨{\chinese{}蝴蝶}⟩ [xu˧˥tjɛ˧˥])
butterfly; moths; Lepidoptera

\textbf{\hypertarget{hupowi}{hupowi}} \textit{v.} (\hyperlink{hu}{hu}+\allowbreak \hyperlink{powi}{powi})
be sighted; \hyperlink{hupowilon}{ʟᴏᴧ} is sighted

\textbf{\hypertarget{hupowilon}{hupowilon}} \textit{n.} (\hyperlink{hupowi}{hupowi}+\allowbreak \hyperlink{lon}{lon})
sighted

\textbf{\hypertarget{hupowinu}{hupowinu}} \textit{v.} (\hyperlink{hupowi}{hupowi}+\allowbreak \hyperlink{nu}{nu})
blind; \hyperlink{hupowinules}{ʟєꜱ} causes ʟᴏᴧ to become blind

\textbf{\hypertarget{hupowinules}{hupowinules}} \textit{n.} (\hyperlink{hupowinu}{hupowinu}+\allowbreak \hyperlink{les}{les})
blinding

\textbf{\hypertarget{hupowinyo}{hupowinyo}} \textit{v.} (\hyperlink{hupowi}{hupowi}+\allowbreak \hyperlink{nyo}{nyo})
be blind; \hyperlink{hupowinyolon}{ʟᴏᴧ} is blind

\textbf{\hypertarget{hupowinyolon}{hupowinyolon}} \textit{n.} (\hyperlink{hupowinyo}{hupowinyo}+\allowbreak \hyperlink{lon}{lon})
blind

\textbf{\hypertarget{hupowiki}{hupowiki}} \textit{v.} (\hyperlink{hupowi}{hupowi}+\allowbreak \hyperlink{ki}{ki})
sighten; restore sight; ʟєꜱ causes ʟᴏᴧ to become sighted

\textbf{\hypertarget{hyo}{hyo}} \textit{v.} (\hyperlink{cwe}{\sout{cwe}})
be gaseous; be air; \hyperlink{hyolon}{ʟᴏᴧ} is gaseous

\textbf{\hypertarget{hyoyeh}{hyoyeh}} \textit{n.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{yeh}{yeh})
tobacco; Nicotiana

\textbf{\hypertarget{hyolon}{hyolon}} \textit{n.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{lon}{lon})
gas; cloud; gaseous; air

\textbf{\hypertarget{hyomiclo}{hyomiclo}} \textit{v.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{miclo}{miclo})
be arid; be dry; \hyperlink{hyomiclolon}{ʟᴏᴧ} is not humid

\textbf{\hypertarget{hyomiclolon}{hyomiclolon}} \textit{n.} (\hyperlink{hyomiclo}{hyomiclo}+\allowbreak \hyperlink{lon}{lon})
arid; dry

\textbf{\hypertarget{hyoki}{hyoki}} \textit{v.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{ki}{ki})
boil; evaporate; \hyperlink{hyokiles}{ʟєꜱ} boils ʟᴏᴧ

\textbf{\hypertarget{hyokiles}{hyokiles}} \textit{n.} (\hyperlink{hyoki}{hyoki}+\allowbreak \hyperlink{les}{les})
boiler

\textbf{\hypertarget{hyotaka}{hyotaka}} \textit{v.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{taka}{taka})
be dry; ʟᴜᴍ is dry of \hyperlink{hyotakalon}{ʟᴏᴧ}

\textbf{\hypertarget{hyotakalon}{hyotakalon}} \textit{n.} (\hyperlink{hyotaka}{hyotaka}+\allowbreak \hyperlink{lon}{lon})
dry

\textbf{\hypertarget{hyotakaki}{hyotakaki}} \textit{v.} (\hyperlink{hyotaka}{hyotaka}+\allowbreak \hyperlink{ki}{ki})
dry; ʟєꜱ dries ʟᴏᴧ off of ʟᴜᴍ

\textbf{\hypertarget{hyopeka}{hyopeka}} \textit{v.} (\hyperlink{hyo}{hyo}+\allowbreak \hyperlink{peka}{peka})
bake; \hyperlink{hyopekales}{ʟєꜱ} bakes \hyperlink{hyopekalon}{ʟᴏᴧ}

\textbf{\hypertarget{hyopekales}{hyopekales}} \textit{n.} (\hyperlink{hyopeka}{hyopeka}+\allowbreak \hyperlink{les}{les})
baker

\textbf{\hypertarget{hyopekalon}{hyopekalon}} \textit{n.} (\hyperlink{hyopeka}{hyopeka}+\allowbreak \hyperlink{lon}{lon})
pastry; baked good

\textbf{\hypertarget{hwe}{hwe}} \textit{v.} (\hyperlink{cyo}{\sout{cyo}})
be young; be new; \hyperlink{hwelon}{ʟᴏᴧ} is young

\textbf{\hypertarget{hwe'yok}{hwe'yok}} \textit{n.} (\hyperlink{hwe}{hwe}+\allowbreak \hyperlink{'yok}{'yok})
New York City; New York

\textbf{\hypertarget{hwelon}{hwelon}} \textit{n.} (\hyperlink{hwe}{hwe}+\allowbreak \hyperlink{lon}{lon})
kid; girl; boy; young; new

\textbf{\hypertarget{hweki}{hweki}} \textit{v.} (\hyperlink{hwe}{hwe}+\allowbreak \hyperlink{ki}{ki})
renew; update; \hyperlink{hwekiles}{ʟєꜱ} makes ʟᴏᴧ become new

\textbf{\hypertarget{hwekiles}{hwekiles}} \textit{n.} (\hyperlink{hweki}{hweki}+\allowbreak \hyperlink{les}{les})
updater

\textbf{\hypertarget{hwetilum}{hwetilum}} \textit{n.} (\hyperlink{hwe}{hwe}+\allowbreak \hyperlink{tilum}{tilum})
news; current events; media

\textbf{\hypertarget{hwo}{hwo}} \textit{v.} (Cmn. ⟨{\chinese{}火}⟩ [xwɔ˧˩˧])
be on fire; be flaming; \hyperlink{hwolon}{ʟᴏᴧ} is on fire

\textbf{\hypertarget{hwolon}{hwolon}} \textit{n.} (\hyperlink{hwo}{hwo}+\allowbreak \hyperlink{lon}{lon})
fire; flame; on fire; flaming

\textbf{\hypertarget{hwonu}{hwonu}} \textit{v.} (\hyperlink{hwo}{hwo}+\allowbreak \hyperlink{nu}{nu})
douse; put out; extinguish; quench; \hyperlink{hwonules}{ʟєꜱ} puts out the fire on \hyperlink{hwonulon}{ʟᴏᴧ}

\textbf{\hypertarget{hwonules}{hwonules}} \textit{n.} (\hyperlink{hwonu}{hwonu}+\allowbreak \hyperlink{les}{les})
fire extinguisher

\textbf{\hypertarget{hwonulon}{hwonulon}} \textit{n.} (\hyperlink{hwonu}{hwonu}+\allowbreak \hyperlink{lon}{lon})
doused

\textbf{\hypertarget{hwok}{hwok}} \textit{n.} (\hyperlink{cyen}{\sout{cyen}})
sheet; page; flexible two-dimensional object

\textbf{\hypertarget{hwoki}{hwoki}} \textit{v.} (\hyperlink{hwo}{hwo}+\allowbreak \hyperlink{ki}{ki})
ignite; light on fire; \hyperlink{hwokiles}{ʟєꜱ} lights \hyperlink{hwokilon}{ʟᴏᴧ} on fire

\textbf{\hypertarget{hwokiles}{hwokiles}} \textit{n.} (\hyperlink{hwoki}{hwoki}+\allowbreak \hyperlink{les}{les})
fire starter

\textbf{\hypertarget{hwokilon}{hwokilon}} \textit{n.} (\hyperlink{hwoki}{hwoki}+\allowbreak \hyperlink{lon}{lon})
ignited

\textbf{\hypertarget{hwokcyen}{hwokcyen}} \textit{n.} (\hyperlink{hwok}{hwok}+\allowbreak \hyperlink{cyen}{cyen})
strip; ribbon; a shape where all three dimensions are very different

\textbf{\hypertarget{hwoksiltokalyotpoltilum}{hwoksiltokalyotpoltilum}} \textit{n.} (\hyperlink{hwok}{hwok}+\allowbreak \hyperlink{siltokalyotpoltilum}{siltokalyotpoltilum})
scarf

\section{C}

\textbf{\hypertarget{ce}{ce}} \textit{v.} (\hyperlink{ho}{\sout{ho}})
be thin; \hyperlink{celon}{ʟᴏᴧ} is thin in its smallest dimension

\textbf{\hypertarget{celon}{celon}} \textit{n.} (\hyperlink{ce}{ce}+\allowbreak \hyperlink{lon}{lon})
film; thin

\textbf{\hypertarget{celun}{celun}} \textit{n.} (Msa. ⟨jerung⟩ [d͡ʒeruŋ])
shark; Selachimorpha

\textbf{\hypertarget{celuk}{celuk}} \textit{n.} (Msa. ⟨jeruk⟩ [d͡ʒeruk])
citrus; Citrus

\textbf{\hypertarget{'celmanium}{'celmanium}} \textit{n.} (Lat. ⟨germanium⟩ [d͡ʒɛrmanɪʊ̃])
germanium

\textbf{\hypertarget{'cewa}{'cewa}} \textit{n.} (Nya. ⟨Chewa⟩ [t͡ʃewa])
Chewa; Nyanja; Nyasa; the Chewa people

\textbf{\hypertarget{'cewaak}{'cewaak}} \textit{n.} (\hyperlink{'cewa}{'cewa}+\allowbreak \hyperlink{ak}{ak})
Chewa; Malawian; from Malawi

\textbf{\hypertarget{'cewatec}{'cewatec}} \textit{n.} (\hyperlink{'cewa}{'cewa}+\allowbreak \hyperlink{tec}{tec})
Malawi

\textbf{\hypertarget{'cewatilip}{'cewatilip}} \textit{n.} (\hyperlink{'cewa}{'cewa}+\allowbreak \hyperlink{tilip}{tilip})
Chichewa; Chinyanja

\textbf{\hypertarget{'cen}{'cen}} \textit{n.} (San. ⟨{\devanagari{}जैन}⟩ [d͡ʒɛːn])
Jain; follower of Jainism

\textbf{\hypertarget{'cenak}{'cenak}} \textit{n.} (\hyperlink{'cen}{'cen}+\allowbreak \hyperlink{ak}{ak})
Jain; Jainist; of Jainism

\textbf{\hypertarget{'cenfitilip}{'cenfitilip}} \textit{n.} (\hyperlink{'cen}{'cen}+\allowbreak \hyperlink{fitilip}{fitilip})
Jainism

\textbf{\hypertarget{'ceh}{'ceh}} \textit{n.} (Ces. ⟨čech⟩ [ˈt͡ʃɛx])
Czech; the Czech people

\textbf{\hypertarget{'cehak}{'cehak}} \textit{n.} (\hyperlink{'ceh}{'ceh}+\allowbreak \hyperlink{ak}{ak})
Czech; from the Czech Republic

\textbf{\hypertarget{'cehtec}{'cehtec}} \textit{n.} (\hyperlink{'ceh}{'ceh}+\allowbreak \hyperlink{tec}{tec})
Czechia; Czech Republic

\textbf{\hypertarget{'cehtilip}{'cehtilip}} \textit{n.} (\hyperlink{'ceh}{'ceh}+\allowbreak \hyperlink{tilip}{tilip})
Czech; the Czech language

\textbf{\hypertarget{cece}{cece}} \textit{v.} (ono. [t͡ʃət͡ʃə])
chatter; wobble; rustle; rattle; ʟєꜱ makes \hyperlink{cecelon}{ʟᴏᴧ}

\textbf{\hypertarget{cecelon}{cecelon}} \textit{n.} (\hyperlink{cece}{cece}+\allowbreak \hyperlink{lon}{lon})
chatter; wobble; rustle; rattle; noisy, high-pitched sound or action

\textbf{\hypertarget{cecim}{cecim}} \textit{n.} (\hyperlink{ce}{ce}+\allowbreak \hyperlink{cim}{cim})
lentil

\textbf{\hypertarget{ceki}{ceki}} \textit{v.} (\hyperlink{ce}{ce}+\allowbreak \hyperlink{ki}{ki})
thin; \hyperlink{cekiles}{ʟєꜱ} thins ʟᴏᴧ

\textbf{\hypertarget{cekiles}{cekiles}} \textit{n.} (\hyperlink{ceki}{ceki}+\allowbreak \hyperlink{les}{les})
thinner

\textbf{\hypertarget{'ca}{'ca}} \textit{n.} (ono. [t͡ʃ])
c; /t͡ʃ/; post-alveolar affricate

\textbf{\hypertarget{cai}{cai}} \textit{v.} (Ben. ⟨{\bengali{}চাই}⟩ [t͡ɕai])
want; like; be good; desire; favour; be appealing; be pleasing; hunger; have an appetite; hope; be beautiful; be positive; \hyperlink{cailon}{ʟᴏᴧ} has positive inclinations toward \hyperlink{cailum}{ʟᴜᴍ}

\textbf{\hypertarget{cailon}{cailon}} \textit{n.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{lon}{lon})
liker; optimist; hoper; wanter; desirous; hungry; -phile; positive

\textbf{\hypertarget{cailip}{cailip}} \textit{n.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{lip}{lip})
style; stylisation

\textbf{\hypertarget{cailum}{cailum}} \textit{n.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{lum}{lum})
desire; wish; hope; preference; favourite; good; appealing; pleasing; beautiful

\textbf{\hypertarget{cailyan}{cailyan}} \textit{n.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{lyan}{lyan})
value; goodness; preference level

\textbf{\hypertarget{cailyot}{cailyot}} \textit{n.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{lyot}{lyot})
heaven; paradise

\textbf{\hypertarget{caiki}{caiki}} \textit{v.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{ki}{ki})
encourage; improve; defend; argue for; positively impact; \hyperlink{caikiles}{ʟєꜱ} raises \hyperlink{caikilon}{ʟᴏᴧ}’s opinion of ʟᴜᴍ

\textbf{\hypertarget{caikiles}{caikiles}} \textit{n.} (\hyperlink{caiki}{caiki}+\allowbreak \hyperlink{les}{les})
encourager; improver

\textbf{\hypertarget{caikilon}{caikilon}} \textit{n.} (\hyperlink{caiki}{caiki}+\allowbreak \hyperlink{lon}{lon})
encouraged

\textbf{\hypertarget{caiti}{caiti}} \textit{v.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{ti}{ti})
consent; approve; ʟєꜱ approves of ʟᴜᴍ to ʟᴏᴧ

\textbf{\hypertarget{caitiku}{caitiku}} \textit{v.} (\hyperlink{cai}{cai}+\allowbreak \hyperlink{tiku}{tiku})
be lucky; be fortunate; that \hyperlink{caitikulon}{ʟᴏᴧ} happens is lucky

\textbf{\hypertarget{caitikulon}{caitikulon}} \textit{n.} (\hyperlink{caitiku}{caitiku}+\allowbreak \hyperlink{lon}{lon})
lucky; fortunate

\textbf{\hypertarget{cau}{cau}} \textit{v.} (\hyperlink{hai}{\sout{hai}})
be low-pitched; be deep; be sonorous; \hyperlink{caulon}{ʟᴏᴧ} is lowly pitched

\textbf{\hypertarget{caulon}{caulon}} \textit{n.} (\hyperlink{cau}{cau}+\allowbreak \hyperlink{lon}{lon})
low note; low-pitched; deep; sonorous

\textbf{\hypertarget{cauki}{cauki}} \textit{v.} (\hyperlink{cau}{cau}+\allowbreak \hyperlink{ki}{ki})
lower; deepen; ʟєꜱ lowers the pitch of ʟᴏᴧ

\textbf{\hypertarget{cayni}{cayni}} \textit{v.} (Eng. ⟨shiny⟩ [ˈʃɑɪ̯ni])
be shiny; shine; be reflective; be smooth; be metallic; \hyperlink{caynilon}{ʟᴏᴧ} reflects light specularly

\textbf{\hypertarget{caynilon}{caynilon}} \textit{n.} (\hyperlink{cayni}{cayni}+\allowbreak \hyperlink{lon}{lon})
mirror; shiny; reflective; smooth; metallic

\textbf{\hypertarget{caynilyan}{caynilyan}} \textit{n.} (\hyperlink{cayni}{cayni}+\allowbreak \hyperlink{lyan}{lyan})
shininess

\textbf{\hypertarget{cayniki}{cayniki}} \textit{v.} (\hyperlink{cayni}{cayni}+\allowbreak \hyperlink{ki}{ki})
shine; polish; ʟєꜱ makes ʟᴏᴧ become shiny

\textbf{\hypertarget{calu}{calu}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਚਾਲੂ}⟩ [t͡ʃɑˈlu])
continue; be happening; keep; stay; be in progress; undergo; maintain; preserve; \textit{progressive}; \hyperlink{calules}{ʟєꜱ} makes \hyperlink{calulon}{ʟᴏᴧ} hold true for some time

\textbf{\hypertarget{calules}{calules}} \textit{n.} (\hyperlink{calu}{calu}+\allowbreak \hyperlink{les}{les})
maintainer

\textbf{\hypertarget{calulon}{calulon}} \textit{n.} (\hyperlink{calu}{calu}+\allowbreak \hyperlink{lon}{lon})
happening; in progress

\textbf{\hypertarget{calulwel}{calulwel}} \textit{n.} (\hyperlink{calu}{calu}+\allowbreak \hyperlink{lwel}{lwel})
equilibrium

\textbf{\hypertarget{calunyo}{calunyo}} \textit{v.} (\hyperlink{calu}{calu}+\allowbreak \hyperlink{nyo}{nyo})
change; be in flux; switch; \hyperlink{calunyoles}{ʟєꜱ} changes \hyperlink{calunyolon}{ʟᴏᴧ} somehow

\textbf{\hypertarget{calunyoles}{calunyoles}} \textit{n.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{les}{les})
bringer of change

\textbf{\hypertarget{calunyolon}{calunyolon}} \textit{n.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{lon}{lon})
in flux

\textbf{\hypertarget{calunyoluat}{calunyoluat}} \textit{n.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{luat}{luat})
switch

\textbf{\hypertarget{calunyohau}{calunyohau}} \textit{v.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{hau}{hau})
be conservative; resist change; \hyperlink{calunyohaulon}{ʟᴏᴧ} is conservative

\textbf{\hypertarget{calunyohaulon}{calunyohaulon}} \textit{n.} (\hyperlink{calunyohau}{calunyohau}+\allowbreak \hyperlink{lon}{lon})
conservative

\textbf{\hypertarget{calunyocai}{calunyocai}} \textit{v.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{cai}{cai})
be liberal; encourage change; \hyperlink{calunyocailon}{ʟᴏᴧ} is liberal

\textbf{\hypertarget{calunyocailon}{calunyocailon}} \textit{n.} (\hyperlink{calunyocai}{calunyocai}+\allowbreak \hyperlink{lon}{lon})
liberal

\textbf{\hypertarget{calunyocolon}{calunyocolon}} \textit{n.} (\hyperlink{calunyo}{calunyo}+\allowbreak \hyperlink{colon}{colon})
verb

\textbf{\hypertarget{calupowi}{calupowi}} \textit{v.} (\hyperlink{calu}{calu}+\allowbreak \hyperlink{powi}{powi})
be stable; be sustainable; \hyperlink{calupowilon}{ʟᴏᴧ} can continue without changing

\textbf{\hypertarget{calupowilon}{calupowilon}} \textit{n.} (\hyperlink{calupowi}{calupowi}+\allowbreak \hyperlink{lon}{lon})
stable; sustainable

\textbf{\hypertarget{calupowinyo}{calupowinyo}} \textit{v.} (\hyperlink{calupowi}{calupowi}+\allowbreak \hyperlink{nyo}{nyo})
be unstable; be unsustainable; \hyperlink{calupowinyolon}{ʟᴏᴧ} cannot continue forever

\textbf{\hypertarget{calupowinyolon}{calupowinyolon}} \textit{n.} (\hyperlink{calupowinyo}{calupowinyo}+\allowbreak \hyperlink{lon}{lon})
unstable; unsustainable

\textbf{\hypertarget{'cawa}{'cawa}} \textit{n.} (Jav. ⟨Jawa⟩ [d͡ʒɔwɔ])
Java (island)

\textbf{\hypertarget{'cawaak}{'cawaak}} \textit{n.} (\hyperlink{'cawa}{'cawa}+\allowbreak \hyperlink{ak}{ak})
Javanese; from Java

\textbf{\hypertarget{'cawawon}{'cawawon}} \textit{n.} (\hyperlink{'cawa}{'cawa}+\allowbreak \hyperlink{won}{won})
Javanese; the Javanese people

\textbf{\hypertarget{'cawatilip}{'cawatilip}} \textit{n.} (\hyperlink{'cawa}{'cawa}+\allowbreak \hyperlink{tilip}{tilip})
Javanese; the Javanese language

\textbf{\hypertarget{cawh}{cawh}} \textit{n.} (Cmn. ⟨{\chinese{}爪}⟩ [ʈ͡ʂɑʊ̯˧˩˧])
claw; quill; fingernail; rigid, sharp, organic protrusion

\textbf{\hypertarget{cawhak}{cawhak}} \textit{n.} (\hyperlink{cawh}{cawh}+\allowbreak \hyperlink{ak}{ak})
ungual; sharp

\textbf{\hypertarget{cawhcim}{cawhcim}} \textit{n.} (\hyperlink{cawh}{cawh}+\allowbreak \hyperlink{cim}{cim})
cowpea; black-eye pea; yardlong bean; Vigna unguiculata

\textbf{\hypertarget{cawhfut}{cawhfut}} \textit{n.} (\hyperlink{cawh}{cawh}+\allowbreak \hyperlink{fut}{fut})
pineapple

\textbf{\hypertarget{cawku}{cawku}} \textit{v.} (Cmn. ⟨{\chinese{}照顾}⟩ [ʈ͡ʂɑʊ̯˥˩ku])
take care; support; \hyperlink{cawkulon}{ʟᴏᴧ} takes care of \hyperlink{cawkulum}{ʟᴜᴍ}

\textbf{\hypertarget{cawkulon}{cawkulon}} \textit{n.} (\hyperlink{cawku}{cawku}+\allowbreak \hyperlink{lon}{lon})
caretaker; staff

\textbf{\hypertarget{cawkulum}{cawkulum}} \textit{n.} (\hyperlink{cawku}{cawku}+\allowbreak \hyperlink{lum}{lum})
dependent; cared for

\textbf{\hypertarget{cawkunu}{cawkunu}} \textit{v.} (\hyperlink{cawku}{cawku}+\allowbreak \hyperlink{nu}{nu})
abandon; take away; ʟєꜱ makes \hyperlink{cawkunulon}{ʟᴏᴧ} stop taking care of ʟᴜᴍ

\textbf{\hypertarget{cawkunulon}{cawkunulon}} \textit{n.} (\hyperlink{cawkunu}{cawkunu}+\allowbreak \hyperlink{lon}{lon})
abandoner

\textbf{\hypertarget{cawkuki}{cawkuki}} \textit{v.} (\hyperlink{cawku}{cawku}+\allowbreak \hyperlink{ki}{ki})
entrust; take charge; \hyperlink{cawkukiles}{ʟєꜱ} makes ʟᴏᴧ start taking care of ʟᴜᴍ

\textbf{\hypertarget{cawkukiles}{cawkukiles}} \textit{n.} (\hyperlink{cawkuki}{cawkuki}+\allowbreak \hyperlink{les}{les})
entruster

\textbf{\hypertarget{'cawta}{'cawta}} \textit{n.} (Eng. ⟨chowder⟩ [ˈt͡ʃaʊ̯dɚ])
chowder

\textbf{\hypertarget{'cantu}{'cantu}} \textit{n.} (Cmn. ⟨{\chinese{}成都}⟩ [ʈ͡ʂʰə˧˥ŋtu˥])
Chengdu

\textbf{\hypertarget{'cameli}{'cameli}} \textit{n.} (Hin. ⟨{\devanagari{}चमेली}⟩ [t͡ʃəmeːliː])
jasmine; Jasminum

\textbf{\hypertarget{cah}{cah}} \textit{num.} (Hin. ⟨{\devanagari{}छः}⟩ [t͡ʃəɦ])
6; six

\textbf{\hypertarget{cahak}{cahak}} \textit{n.} (\hyperlink{cah}{cah}+\allowbreak \hyperlink{ak}{ak})
sixth

\textbf{\hypertarget{cahnul}{cahnul}} \textit{num.} (\hyperlink{cah}{cah}+\allowbreak \hyperlink{nul}{nul})
60; sixty

\textbf{\hypertarget{cahnulnul}{cahnulnul}} \textit{num.} (\hyperlink{cah}{cah}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
600; six hundred

\textbf{\hypertarget{cahsunkwelwel}{cahsunkwelwel}} \textit{n.} (\hyperlink{cah}{cah}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Saturday

\textbf{\hypertarget{casi}{casi}} \textit{v.} (Epo. ⟨ĉasi⟩ [ˈt͡ʃasi])
hunt; chase; pursue; \hyperlink{casiles}{ʟєꜱ} hunts for \hyperlink{casilon}{ʟᴏᴧ}

\textbf{\hypertarget{casiles}{casiles}} \textit{n.} (\hyperlink{casi}{casi}+\allowbreak \hyperlink{les}{les})
hunter

\textbf{\hypertarget{casilon}{casilon}} \textit{n.} (\hyperlink{casi}{casi}+\allowbreak \hyperlink{lon}{lon})
hunted

\textbf{\hypertarget{caka}{caka}} \textit{v.} (Jav. ⟨saka⟩ [ʂɔkɔ])
be made of; comprise; \hyperlink{cakalon}{ʟᴏᴧ} is made out of \hyperlink{cakalum}{ʟᴜᴍ}

\textbf{\hypertarget{cakalon}{cakalon}} \textit{n.} (\hyperlink{caka}{caka}+\allowbreak \hyperlink{lon}{lon})
construction; object; product; made of

\textbf{\hypertarget{cakalum}{cakalum}} \textit{n.} (\hyperlink{caka}{caka}+\allowbreak \hyperlink{lum}{lum})
material; substance; chemical; element

\textbf{\hypertarget{cakasoma}{cakasoma}} \textit{v.} (\hyperlink{caka}{caka}+\allowbreak \hyperlink{soma}{soma})
do chemistry; do material science; \hyperlink{cakasomales}{ʟєꜱ} studies chemicals to learn about \hyperlink{cakasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{cakasomales}{cakasomales}} \textit{n.} (\hyperlink{cakasoma}{cakasoma}+\allowbreak \hyperlink{les}{les})
chemist

\textbf{\hypertarget{cakasomalon}{cakasomalon}} \textit{n.} (\hyperlink{cakasoma}{cakasoma}+\allowbreak \hyperlink{lon}{lon})
chemistry; material science

\textbf{\hypertarget{cakaki}{cakaki}} \textit{v.} (\hyperlink{caka}{caka}+\allowbreak \hyperlink{ki}{ki})
make out of; turn to; \hyperlink{cakakiles}{ʟєꜱ} changes ʟᴏᴧ to be made out of ʟᴜᴍ

\textbf{\hypertarget{cakakiles}{cakakiles}} \textit{n.} (\hyperlink{cakaki}{cakaki}+\allowbreak \hyperlink{les}{les})
alchemist

\textbf{\hypertarget{'cakti}{'cakti}} \textit{n.} (Hin. ⟨{\devanagari{}शक्ति}⟩ [ʃəkti])
Shakti

\textbf{\hypertarget{'caktifitilip}{'caktifitilip}} \textit{n.} (\hyperlink{'cakti}{'cakti}+\allowbreak \hyperlink{fitilip}{fitilip})
Shaktism

\textbf{\hypertarget{'caktifitilipak}{'caktifitilipak}} \textit{n.} (\hyperlink{'caktifitilip}{'caktifitilip}+\allowbreak \hyperlink{ak}{ak})
Shakta; of Shaktism

\textbf{\hypertarget{'caktifitilipwon}{'caktifitilipwon}} \textit{n.} (\hyperlink{'caktifitilip}{'caktifitilip}+\allowbreak \hyperlink{won}{won})
Shaktist; followers of Shakti

\textbf{\hypertarget{cat}{cat}} \textit{n.} (Hin. ⟨{\devanagari{}छाती}⟩ [t͡ʃʰaːtiː])
chest; breast; bosom; upper front surface of a torso

\textbf{\hypertarget{'cat}{'cat}} \textit{n.} (Fra. ⟨Tshad⟩ [tʃad])
Chad

\textbf{\hypertarget{catak}{catak}} \textit{n.} (\hyperlink{cat}{cat}+\allowbreak \hyperlink{ak}{ak})
chestal; mamillary

\textbf{\hypertarget{'catak}{'catak}} \textit{n.} (\hyperlink{'cat}{'cat}+\allowbreak \hyperlink{ak}{ak})
Chadian; from Chad

\textbf{\hypertarget{catui}{catui}} \textit{v.} (Hin. ⟨{\devanagari{}जादुई}⟩ [d͡ʒaːduiː])
be magical; do magic; \hyperlink{catuiles}{ʟєꜱ} makes \hyperlink{catuilon}{ʟᴏᴧ} happen magically

\textbf{\hypertarget{catuiles}{catuiles}} \textit{n.} (\hyperlink{catui}{catui}+\allowbreak \hyperlink{les}{les})
magician; sorcerer; wizard

\textbf{\hypertarget{catuilon}{catuilon}} \textit{n.} (\hyperlink{catui}{catui}+\allowbreak \hyperlink{lon}{lon})
magic trick; spell; magical

\textbf{\hypertarget{catuiluat}{catuiluat}} \textit{n.} (\hyperlink{catui}{catui}+\allowbreak \hyperlink{luat}{luat})
magic

\textbf{\hypertarget{catuikap}{catuikap}} \textit{n.} (\hyperlink{catui}{catui}+\allowbreak \hyperlink{kap}{kap})
magikarp

\textbf{\hypertarget{'catwon}{'catwon}} \textit{n.} (\hyperlink{'cat}{'cat}+\allowbreak \hyperlink{won}{won})
Chadian; the Chadian people

\textbf{\hypertarget{capa}{capa}} \textit{v.} (Jav. ⟨sap⟩ [ʂɑp])
be stacked; be layered; \hyperlink{capalon}{ʟᴏᴧ} is stacked on \hyperlink{capalum}{ʟᴜᴍ}

\textbf{\hypertarget{capalon}{capalon}} \textit{n.} (\hyperlink{capa}{capa}+\allowbreak \hyperlink{lon}{lon})
layer; stacked; layered

\textbf{\hypertarget{capalum}{capalum}} \textit{n.} (\hyperlink{capa}{capa}+\allowbreak \hyperlink{lum}{lum})
book; stack

\textbf{\hypertarget{capanu}{capanu}} \textit{v.} (\hyperlink{capa}{capa}+\allowbreak \hyperlink{nu}{nu})
unstack; unlayer; \hyperlink{capanules}{ʟєꜱ} unstacks ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{capanules}{capanules}} \textit{n.} (\hyperlink{capanu}{capanu}+\allowbreak \hyperlink{les}{les})
unstacker

\textbf{\hypertarget{capaki}{capaki}} \textit{v.} (\hyperlink{capa}{capa}+\allowbreak \hyperlink{ki}{ki})
stack; layer; \hyperlink{capakiles}{ʟєꜱ} stacks ʟᴏᴧ onto ʟᴜᴍ

\textbf{\hypertarget{capakiles}{capakiles}} \textit{n.} (\hyperlink{capaki}{capaki}+\allowbreak \hyperlink{les}{les})
stacker

\textbf{\hypertarget{capakiciuh}{capakiciuh}} \textit{n.} (\hyperlink{capaki}{capaki}+\allowbreak \hyperlink{ciuh}{ciuh})
onion; bulb onion; common onion; Allium cepa

\textbf{\hypertarget{'caputi}{'caputi}} \textit{n.} (Som. ⟨Jabuuti⟩ [d͡ʒæbuːt])
Djibouti City; Djibouti

\textbf{\hypertarget{'caputiak}{'caputiak}} \textit{n.} (\hyperlink{'caputi}{'caputi}+\allowbreak \hyperlink{ak}{ak})
Djiboutian; from Djibouti

\textbf{\hypertarget{'caputiwon}{'caputiwon}} \textit{n.} (\hyperlink{'caputi}{'caputi}+\allowbreak \hyperlink{won}{won})
Djiboutian; the Djiboutian people

\textbf{\hypertarget{'caputitec}{'caputitec}} \textit{n.} (\hyperlink{'caputi}{'caputi}+\allowbreak \hyperlink{tec}{tec})
Djibouti; the Republic of Djibouti

\textbf{\hypertarget{co}{co}} \textit{v.} (Zul. ⟨-sho⟩ [ʃo])
mean; call; name; be significant; \hyperlink{colon}{ʟᴏᴧ} means \hyperlink{colum}{ʟᴜᴍ} to ʟєꜱ

\textbf{\hypertarget{cola}{cola}} \textit{v.} (Hin. ⟨{\devanagari{}चौड़ा}⟩ [t͡ʃɔːɽaː])
be wide; be obtuse; be big; be large; \hyperlink{colalon}{ʟᴏᴧ} spans a wide angle from the point of view of ʟᴜᴍ

\textbf{\hypertarget{colalon}{colalon}} \textit{n.} (\hyperlink{cola}{cola}+\allowbreak \hyperlink{lon}{lon})
splotch; blotch; wide; obtuse; big; large

\textbf{\hypertarget{colalyan}{colalyan}} \textit{n.} (\hyperlink{cola}{cola}+\allowbreak \hyperlink{lyan}{lyan})
angle;angular size

\textbf{\hypertarget{colaki}{colaki}} \textit{v.} (\hyperlink{cola}{cola}+\allowbreak \hyperlink{ki}{ki})
widen; grow; spread out; dilate; ʟєꜱ makes ʟᴏᴧ span a wider angle from the point of view of ʟᴜᴍ

\textbf{\hypertarget{colon}{colon}} \textit{n.} (\hyperlink{co}{co}+\allowbreak \hyperlink{lon}{lon})
name; signal; word; sememe; significant

\textbf{\hypertarget{colonoltolum}{colonoltolum}} \textit{n.} (\hyperlink{colon}{colon}+\allowbreak \hyperlink{oltolum}{oltolum})
dictionary

\textbf{\hypertarget{colontipalum}{colontipalum}} \textit{n.} (\hyperlink{colon}{colon}+\allowbreak \hyperlink{tipalum}{tipalum})
part-of-speech

\textbf{\hypertarget{colil}{colil}} \textit{n.} (Ben. ⟨{\bengali{}শরীর}⟩ [ɕɔrir])
body; chassis; physical manifestation

\textbf{\hypertarget{colilak}{colilak}} \textit{n.} (\hyperlink{colil}{colil}+\allowbreak \hyperlink{ak}{ak})
bodily; physical; corporal

\textbf{\hypertarget{colip}{colip}} \textit{n.} (\hyperlink{co}{co}+\allowbreak \hyperlink{lip}{lip})
convention; protocol

\textbf{\hypertarget{colum}{colum}} \textit{n.} (\hyperlink{co}{co}+\allowbreak \hyperlink{lum}{lum})
definition; meaning; denotation; named

\textbf{\hypertarget{con}{con}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਜੌਂ}⟩ [d͡ʒɔ̃])
barley; Hordeum

\textbf{\hypertarget{'cona}{'cona}} \textit{n.} (Sna. ⟨Shona⟩ [ʃona])
Shona; the Shona people

\textbf{\hypertarget{'conaak}{'conaak}} \textit{n.} (\hyperlink{'cona}{'cona}+\allowbreak \hyperlink{ak}{ak})
Shona; of the Shona

\textbf{\hypertarget{'conatilip}{'conatilip}} \textit{n.} (\hyperlink{'cona}{'cona}+\allowbreak \hyperlink{tilip}{tilip})
Shona; chiShona; the Shona language

\textbf{\hypertarget{comi}{comi}} \textit{v.} (Cmn. ⟨{\chinese{}稠密}⟩ [ʈ͡ʂʰoʊ̯˧˥mi˥˩])
be dense; be cramped; be frequent; be tightly packed; be fine; be urban; \hyperlink{comilon}{ʟᴏᴧ} occurs frequently and close together in \hyperlink{comilum}{ʟᴜᴍ}

\textbf{\hypertarget{comilon}{comilon}} \textit{n.} (\hyperlink{comi}{comi}+\allowbreak \hyperlink{lon}{lon})
dense; frequent; tightly packed; fine; urban

\textbf{\hypertarget{comilip}{comilip}} \textit{n.} (\hyperlink{comi}{comi}+\allowbreak \hyperlink{lip}{lip})
distribution

\textbf{\hypertarget{comilum}{comilum}} \textit{n.} (\hyperlink{comi}{comi}+\allowbreak \hyperlink{lum}{lum})
cramped

\textbf{\hypertarget{comilyan}{comilyan}} \textit{n.} (\hyperlink{comi}{comi}+\allowbreak \hyperlink{lyan}{lyan})
density; resolution

\textbf{\hypertarget{comiki}{comiki}} \textit{v.} (\hyperlink{comi}{comi}+\allowbreak \hyperlink{ki}{ki})
gather; collect; cluster; densify; ʟєꜱ increases the spacial frequency of ʟᴏᴧ

\textbf{\hypertarget{coh}{coh}} \textit{n.} (Cmn. ⟨{\chinese{}手}⟩ [ʂoʊ̯˧˩˧])
hand; multi-appendaged manipulator

\textbf{\hypertarget{cohak}{cohak}} \textit{n.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{ak}{ak})
manual

\textbf{\hypertarget{cohluso}{cohluso}} \textit{v.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{luso}{luso})
be dexterous; \hyperlink{cohlusolon}{ʟᴏᴧ} is dexterous

\textbf{\hypertarget{cohlusolon}{cohlusolon}} \textit{n.} (\hyperlink{cohluso}{cohluso}+\allowbreak \hyperlink{lon}{lon})
dexterous

\textbf{\hypertarget{cohtokalyot}{cohtokalyot}} \textit{n.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{tokalyot}{tokalyot})
wrist

\textbf{\hypertarget{cohtokalyotpoltilum}{cohtokalyotpoltilum}} \textit{n.} (\hyperlink{cohtokalyot}{cohtokalyot}+\allowbreak \hyperlink{poltilum}{poltilum})
bracelet

\textbf{\hypertarget{cohti}{cohti}} \textit{v.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{ti}{ti})
gesture; sign; ʟєꜱ gestures ʟᴜᴍ to ʟᴏᴧ

\textbf{\hypertarget{cohtilip}{cohtilip}} \textit{n.} (\hyperlink{cohti}{cohti}+\allowbreak \hyperlink{lip}{lip})
gesture

\textbf{\hypertarget{cohtife}{cohtife}} \textit{v.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{tife}{tife})
be clumsy; \hyperlink{cohtifelon}{ʟᴏᴧ} is clumsy

\textbf{\hypertarget{cohtifelon}{cohtifelon}} \textit{n.} (\hyperlink{cohtife}{cohtife}+\allowbreak \hyperlink{lon}{lon})
clumsy

\textbf{\hypertarget{cohtue}{cohtue}} \textit{v.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{tue}{tue})
hold; carry; have with one; have on one’s person; \hyperlink{cohtuelon}{ʟᴏᴧ} holds \hyperlink{cohtuelum}{ʟᴜᴍ}

\textbf{\hypertarget{cohtuelon}{cohtuelon}} \textit{n.} (\hyperlink{cohtue}{cohtue}+\allowbreak \hyperlink{lon}{lon})
holder

\textbf{\hypertarget{cohtuelum}{cohtuelum}} \textit{n.} (\hyperlink{cohtue}{cohtue}+\allowbreak \hyperlink{lum}{lum})
held; accessory

\textbf{\hypertarget{cohtuenu}{cohtuenu}} \textit{v.} (\hyperlink{cohtue}{cohtue}+\allowbreak \hyperlink{nu}{nu})
put down; release; \hyperlink{cohtuenules}{ʟєꜱ} takes ʟᴜᴍ out of ʟᴏᴧ’s hand

\textbf{\hypertarget{cohtuenules}{cohtuenules}} \textit{n.} (\hyperlink{cohtuenu}{cohtuenu}+\allowbreak \hyperlink{les}{les})
putter downer; taker

\textbf{\hypertarget{cohtueki}{cohtueki}} \textit{v.} (\hyperlink{cohtue}{cohtue}+\allowbreak \hyperlink{ki}{ki})
pick up; hand; grab; \hyperlink{cohtuekiles}{ʟєꜱ} puts ʟᴜᴍ in ʟᴏᴧ’s hand

\textbf{\hypertarget{cohtuekiles}{cohtuekiles}} \textit{n.} (\hyperlink{cohtueki}{cohtueki}+\allowbreak \hyperlink{les}{les})
hander; picker upper

\textbf{\hypertarget{cohpoltilum}{cohpoltilum}} \textit{n.} (\hyperlink{coh}{coh}+\allowbreak \hyperlink{poltilum}{poltilum})
glove

\textbf{\hypertarget{coc}{coc}} \textit{n.} (Cmn. ⟨{\chinese{}手指}⟩ [ʂoʊ̯˧˩˧ʈ͡ʂɨ˧˩˧])
finger; toe; small manipulator attached to a hand or foot

\textbf{\hypertarget{cocak}{cocak}} \textit{n.} (\hyperlink{coc}{coc}+\allowbreak \hyperlink{ak}{ak})
digital

\textbf{\hypertarget{cos}{cos}} \textit{n.} (Ben. ⟨{\bengali{}শসা}⟩ [ɕɔs̪a])
cucumber; gherkin; Cucumis sativus

\textbf{\hypertarget{'cosawn}{'cosawn}} \textit{n.} (Kor. ⟨{\korean{}조선}⟩ [t͡ɕosʰʌn])
Korea; the Korean peninsula

\textbf{\hypertarget{'cosawnak}{'cosawnak}} \textit{n.} (\hyperlink{'cosawn}{'cosawn}+\allowbreak \hyperlink{ak}{ak})
Korean; from Korea

\textbf{\hypertarget{'cosawnwon}{'cosawnwon}} \textit{n.} (\hyperlink{'cosawn}{'cosawn}+\allowbreak \hyperlink{won}{won})
Korean; the Korean people

\textbf{\hypertarget{'cosawntilip}{'cosawntilip}} \textit{n.} (\hyperlink{'cosawn}{'cosawn}+\allowbreak \hyperlink{tilip}{tilip})
Korean; the Korean language

\textbf{\hypertarget{cosfolmo}{cosfolmo}} \textit{v.} (\hyperlink{cos}{cos}+\allowbreak \hyperlink{folmo}{folmo})
be cucumiform; be cucumber-shaped; \hyperlink{cosfolmolon}{ʟᴏᴧ} is cylindrical, with rounded tapers on the ends

\textbf{\hypertarget{cosfolmolon}{cosfolmolon}} \textit{n.} (\hyperlink{cosfolmo}{cosfolmo}+\allowbreak \hyperlink{lon}{lon})
cucumiform; cucumber-shaped

\textbf{\hypertarget{costun}{costun}} \textit{n.} (\hyperlink{cos}{cos}+\allowbreak \hyperlink{tun}{tun})
seacucumber

\textbf{\hypertarget{coto}{coto}} \textit{v.} (Ben. ⟨{\bengali{}জট}⟩ [d͡ʑɔtɔ])
be tangled; be knotted; \hyperlink{cotolon}{ʟᴏᴧ} is tangled together with ʟᴜᴍ

\textbf{\hypertarget{cotolon}{cotolon}} \textit{n.} (\hyperlink{coto}{coto}+\allowbreak \hyperlink{lon}{lon})
knot; tangled; knotted

\textbf{\hypertarget{cotonu}{cotonu}} \textit{v.} (\hyperlink{coto}{coto}+\allowbreak \hyperlink{nu}{nu})
untie; unknot; untangle; ʟєꜱ unties ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{cotomeklelon}{cotomeklelon}} \textit{n.} (\hyperlink{coto}{coto}+\allowbreak \hyperlink{meklelon}{meklelon})
basket

\textbf{\hypertarget{cotoki}{cotoki}} \textit{v.} (\hyperlink{coto}{coto}+\allowbreak \hyperlink{ki}{ki})
tie; knot; tangle; ʟєꜱ ties ʟᴏᴧ to ʟᴜᴍ

\textbf{\hypertarget{ci}{ci}} \textit{v.} (Cmn. ⟨{\chinese{}试}⟩ [ʂɨ˥˩])
try; attempt; will; intend; do for; do so; do in order to; \hyperlink{ciles}{ʟєꜱ} makes \hyperlink{cilon}{ʟᴏᴧ} happen in order to make \hyperlink{cilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{ciestaki}{ciestaki}} \textit{v.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{estaki}{estaki})
design; \hyperlink{ciestakiles}{ʟєꜱ} makes \hyperlink{ciestakilon}{ʟᴏᴧ} with the goal of \hyperlink{ciestakilum}{ʟᴜᴍ}

\textbf{\hypertarget{ciestakiles}{ciestakiles}} \textit{n.} (\hyperlink{ciestaki}{ciestaki}+\allowbreak \hyperlink{les}{les})
designer

\textbf{\hypertarget{ciestakilon}{ciestakilon}} \textit{n.} (\hyperlink{ciestaki}{ciestaki}+\allowbreak \hyperlink{lon}{lon})
designed

\textbf{\hypertarget{ciestakilum}{ciestakilum}} \textit{n.} (\hyperlink{ciestaki}{ciestaki}+\allowbreak \hyperlink{lum}{lum})
design goal

\textbf{\hypertarget{ciestakitilip}{ciestakitilip}} \textit{n.} (\hyperlink{ciestaki}{ciestaki}+\allowbreak \hyperlink{tilip}{tilip})
conlang; constructed language

\textbf{\hypertarget{'ciah}{'ciah}} \textit{n.} (Ara. ⟨{\arabics{}شيعة‎}⟩ [ʃiːʔah])
Shia Islam; Shia

\textbf{\hypertarget{'ciahak}{'ciahak}} \textit{n.} (\hyperlink{'ciah}{'ciah}+\allowbreak \hyperlink{ak}{ak})
Shia; of Shia Islam

\textbf{\hypertarget{'ciahwon}{'ciahwon}} \textit{n.} (\hyperlink{'ciah}{'ciah}+\allowbreak \hyperlink{won}{won})
Shia of Ali; Shia; followers of Shia Islam

\textbf{\hypertarget{ciuh}{ciuh}} \textit{n.} (Cmn. ⟨{\chinese{}植物}⟩ [ʈ͡ʂɨ˧˥u˥˩])
plant; vegetable; Plantae

\textbf{\hypertarget{ciuhak}{ciuhak}} \textit{n.} (\hyperlink{ciuh}{ciuh}+\allowbreak \hyperlink{ak}{ak})
botanical; vegetal

\textbf{\hypertarget{ciuhnyamales}{ciuhnyamales}} \textit{n.} (\hyperlink{ciuh}{ciuh}+\allowbreak \hyperlink{nyamales}{nyamales})
herbivore; something that eats plants

\textbf{\hypertarget{ciuhcomiki}{ciuhcomiki}} \textit{v.} (\hyperlink{ciuh}{ciuh}+\allowbreak \hyperlink{comiki}{comiki})
harvest; ʟєꜱ harvests \hyperlink{ciuhcomikilon}{ʟᴏᴧ} from ʟᴜᴍ

\textbf{\hypertarget{ciuhcomikilon}{ciuhcomikilon}} \textit{n.} (\hyperlink{ciuhcomiki}{ciuhcomiki}+\allowbreak \hyperlink{lon}{lon})
crop

\textbf{\hypertarget{ciuhcomikilyot}{ciuhcomikilyot}} \textit{n.} (\hyperlink{ciuhcomiki}{ciuhcomiki}+\allowbreak \hyperlink{lyot}{lyot})
farm

\textbf{\hypertarget{ciuhtayl}{ciuhtayl}} \textit{n.} (\hyperlink{ciuh}{ciuh}+\allowbreak \hyperlink{tayl}{tayl})
jungle; rainforest

\textbf{\hypertarget{'cile}{'cile}} \textit{n.} (Spa. ⟨Chile⟩ [ˈt͡ʃile])
Chile

\textbf{\hypertarget{'cileak}{'cileak}} \textit{n.} (\hyperlink{'cile}{'cile}+\allowbreak \hyperlink{ak}{ak})
Chilean; from Chile

\textbf{\hypertarget{'cilewon}{'cilewon}} \textit{n.} (\hyperlink{'cile}{'cile}+\allowbreak \hyperlink{won}{won})
Chilean; the Chilean people

\textbf{\hypertarget{ciles}{ciles}} \textit{n.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{les}{les})
purposeful; intentful

\textbf{\hypertarget{cilaf}{cilaf}} \textit{n.} (Hin. ⟨{\devanagari{}जिराफ़}⟩ [d͡ʒiraːf])
giraffe; okapi; Giraffidae

\textbf{\hypertarget{cilon}{cilon}} \textit{n.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{lon}{lon})
means

\textbf{\hypertarget{cilum}{cilum}} \textit{n.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{lum}{lum})
purpose; reason; goal; end; intention; beneficiary

\textbf{\hypertarget{'ciwa}{'ciwa}} \textit{n.} (San. ⟨{\devanagari{}शिव}⟩ [ɕiʋɐ́])
Shiva

\textbf{\hypertarget{'ciwafitilip}{'ciwafitilip}} \textit{n.} (\hyperlink{'ciwa}{'ciwa}+\allowbreak \hyperlink{fitilip}{fitilip})
Shaivism

\textbf{\hypertarget{'ciwafitilipak}{'ciwafitilipak}} \textit{n.} (\hyperlink{'ciwafitilip}{'ciwafitilip}+\allowbreak \hyperlink{ak}{ak})
Shaiva; of Shaivism

\textbf{\hypertarget{'ciwafitilipwon}{'ciwafitilipwon}} \textit{n.} (\hyperlink{'ciwafitilip}{'ciwafitilip}+\allowbreak \hyperlink{won}{won})
Shaivite; Saivite; followers of Shiva

\textbf{\hypertarget{ciwn}{ciwn}} \textit{n.} (Cmn. ⟨{\chinese{}菌}⟩ [t͡ɕyn˥])
fungus; Fungi

\textbf{\hypertarget{ciwnak}{ciwnak}} \textit{n.} (\hyperlink{ciwn}{ciwn}+\allowbreak \hyperlink{ak}{ak})
fungal; fungic; fungous

\textbf{\hypertarget{ciwti}{ciwti}} \textit{v.} (Cmn. ⟨{\chinese{}具体}⟩ [t͡ɕy˥˩tʰi˧˩˧])
be specific; be particular; \hyperlink{ciwtilon}{ʟᴏᴧ} is specific

\textbf{\hypertarget{ciwtilon}{ciwtilon}} \textit{n.} (\hyperlink{ciwti}{ciwti}+\allowbreak \hyperlink{lon}{lon})
specific; particular

\textbf{\hypertarget{ciwtiki}{ciwtiki}} \textit{v.} (\hyperlink{ciwti}{ciwti}+\allowbreak \hyperlink{ki}{ki})
specify; identify; ʟєꜱ specifies ʟᴏᴧ

\textbf{\hypertarget{cin}{cin}} \textit{n.} (Cmn. ⟨{\chinese{}鲸}⟩ [t͡ɕiŋ˥])
cetacean; whale; dolphin; porpoise; Cetacea

\textbf{\hypertarget{'cin}{'cin}} \textit{n.} (Eng. ⟨jeans⟩ [d͡ʒiːnz])
jeans

\textbf{\hypertarget{'cinitsel}{'cinitsel}} \textit{n.} (Deu. ⟨schnitzel⟩ [ˈʃnɪtsl̩])
schnitzel

\textbf{\hypertarget{cinu}{cinu}} \textit{v.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{nu}{nu})
give up; quit; stop trying; \hyperlink{cinules}{ʟєꜱ} stops trying to make ʟᴜᴍ happen by doing ʟᴏᴧ

\textbf{\hypertarget{cinules}{cinules}} \textit{n.} (\hyperlink{cinu}{cinu}+\allowbreak \hyperlink{les}{les})
quitter

\textbf{\hypertarget{cinya}{cinya}} \textit{v.} (Cmn. ⟨{\chinese{}惊讶}⟩ [t͡ɕiŋ˥ja˥˩])
surprise; astonish; shock; \hyperlink{cinyales}{ʟєꜱ} surprises \hyperlink{cinyalon}{ʟᴏᴧ} with ʟᴜᴍ

\textbf{\hypertarget{cinyales}{cinyales}} \textit{n.} (\hyperlink{cinya}{cinya}+\allowbreak \hyperlink{les}{les})
surprising

\textbf{\hypertarget{cinyalon}{cinyalon}} \textit{n.} (\hyperlink{cinya}{cinya}+\allowbreak \hyperlink{lon}{lon})
surprised

\textbf{\hypertarget{cinyokweki}{cinyokweki}} \textit{v.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{kweki}{kweki})
mistake; have an accident; ʟєꜱ accidentally makes \hyperlink{cinyokwekilon}{ʟᴏᴧ} happen

\textbf{\hypertarget{cinyokwekilon}{cinyokwekilon}} \textit{n.} (\hyperlink{cinyokweki}{cinyokweki}+\allowbreak \hyperlink{lon}{lon})
mistake; accident

\textbf{\hypertarget{cinci}{cinci}} \textit{v.} (Cmn. ⟨{\chinese{}亲戚}⟩ [t͡ɕʰin˥t͡ɕʰi])
be related; share blood; \hyperlink{cincilon}{ʟᴏᴧ} is genetically related to \hyperlink{cincilum}{ʟᴜᴍ}

\textbf{\hypertarget{cincilon}{cincilon}} \textit{n.} (\hyperlink{cinci}{cinci}+\allowbreak \hyperlink{lon}{lon})
relatee; related

\textbf{\hypertarget{cincilum}{cincilum}} \textit{n.} (\hyperlink{cinci}{cinci}+\allowbreak \hyperlink{lum}{lum})
relative; kin; family; blood; ethnic; ethnicity

\textbf{\hypertarget{cincinu}{cincinu}} \textit{v.} (\hyperlink{cinci}{cinci}+\allowbreak \hyperlink{nu}{nu})
defocus; ʟєꜱ makes ʟᴏᴧ not be about ʟᴜᴍ

\textbf{\hypertarget{cinciki}{cinciki}} \textit{v.} (\hyperlink{cinci}{cinci}+\allowbreak \hyperlink{ki}{ki})
focus; ʟєꜱ makes ʟᴏᴧ about ʟᴜᴍ

\textbf{\hypertarget{cinkul}{cinkul}} \textit{n.} (Hin. ⟨{\devanagari{}झींगुर}⟩ [d͡ʒ̤iːŋɡur])
cricket; grasshopper; locust; tatydid; Orthoptera

\textbf{\hypertarget{cinta}{cinta}} \textit{v.} (Ben. ⟨{\bengali{}চিন্তা}⟩ [t͡ɕin̪t̪a])
ponder; think about; imagine; consider; \hyperlink{cintales}{ʟєꜱ} is thinks about \hyperlink{cintalon}{ʟᴏᴧ}

\textbf{\hypertarget{cintaec}{cintaec}} \textit{n.} (\hyperlink{cinta}{cinta}+\allowbreak \hyperlink{ec}{ec})
brain

\textbf{\hypertarget{cintales}{cintales}} \textit{n.} (\hyperlink{cinta}{cinta}+\allowbreak \hyperlink{les}{les})
thinker; ponderer

\textbf{\hypertarget{cintalon}{cintalon}} \textit{n.} (\hyperlink{cinta}{cinta}+\allowbreak \hyperlink{lon}{lon})
train of thought

\textbf{\hypertarget{cintaluat}{cintaluat}} \textit{n.} (\hyperlink{cinta}{cinta}+\allowbreak \hyperlink{luat}{luat})
mind; imaaagination

\textbf{\hypertarget{'cinto}{'cinto}} \textit{n.} (Jpn. ⟨{\japanese{}神道}⟩ [ɕintoː])
Shintoism

\textbf{\hypertarget{'cintoak}{'cintoak}} \textit{n.} (\hyperlink{'cinto}{'cinto}+\allowbreak \hyperlink{ak}{ak})
Shinto; of Shintoism

\textbf{\hypertarget{'cintowon}{'cintowon}} \textit{n.} (\hyperlink{'cinto}{'cinto}+\allowbreak \hyperlink{won}{won})
Shintoist; followers of Shintoism

\textbf{\hypertarget{cim}{cim}} \textit{n.} (Ben. ⟨{\bengali{}শিম}⟩ [ɕim])
legume; pulse; bean; pea; Fabaceae

\textbf{\hypertarget{cih}{cih}} \textit{n.} (Cmn. ⟨{\chinese{}市}⟩ [ʂɨ˥˩])
settlement; city; town; village; dense collection of human residences

\textbf{\hypertarget{cihak}{cihak}} \textit{n.} (\hyperlink{cih}{cih}+\allowbreak \hyperlink{ak}{ak})
urban; villestial

\textbf{\hypertarget{cihwa}{cihwa}} \textit{v.} (Cmn. ⟨{\chinese{}计划}⟩ [t͡ɕi˥˩xwa˥˩])
plan; expect; \hyperlink{cihwalon}{ʟᴏᴧ} expects \hyperlink{cihwalum}{ʟᴜᴍ} to happen

\textbf{\hypertarget{cihwalon}{cihwalon}} \textit{n.} (\hyperlink{cihwa}{cihwa}+\allowbreak \hyperlink{lon}{lon})
expecting

\textbf{\hypertarget{cihwaluat}{cihwaluat}} \textit{n.} (\hyperlink{cihwa}{cihwa}+\allowbreak \hyperlink{luat}{luat})
planner; planning tool

\textbf{\hypertarget{cihwalum}{cihwalum}} \textit{n.} (\hyperlink{cihwa}{cihwa}+\allowbreak \hyperlink{lum}{lum})
plan; expectation

\textbf{\hypertarget{cihwicon}{cihwicon}} \textit{n.} (\hyperlink{cih}{cih}+\allowbreak \hyperlink{wicon}{wicon})
square; lot; park

\textbf{\hypertarget{cic}{cic}} \textit{n.} (Cmn. ⟨{\chinese{}蜘蛛}⟩ [ʈ͡ʂɨ˥ʈ͡ʂu˥])
spider; Araneae

\textbf{\hypertarget{cicu}{cicu}} \textit{v.} (Cmn. ⟨{\chinese{}技术}⟩ [t͡ɕi˥˩ʂu˥˩])
employ technology; engineer; \hyperlink{cicules}{ʟєꜱ} uses technical skills and fine problem-solving to solve \hyperlink{ciculon}{ʟᴏᴧ}

\textbf{\hypertarget{cicules}{cicules}} \textit{n.} (\hyperlink{cicu}{cicu}+\allowbreak \hyperlink{les}{les})
engineer

\textbf{\hypertarget{ciculesitea}{ciculesitea}} \textit{v.} (\hyperlink{cicules}{cicules}+\allowbreak \hyperlink{itea}{itea})
invent; innovate; \hyperlink{ciculesiteales}{ʟєꜱ} invents \hyperlink{ciculesitealon}{ʟᴏᴧ}

\textbf{\hypertarget{ciculesiteales}{ciculesiteales}} \textit{n.} (\hyperlink{ciculesitea}{ciculesitea}+\allowbreak \hyperlink{les}{les})
inventor

\textbf{\hypertarget{ciculesitealon}{ciculesitealon}} \textit{n.} (\hyperlink{ciculesitea}{ciculesitea}+\allowbreak \hyperlink{lon}{lon})
invention

\textbf{\hypertarget{ciculon}{ciculon}} \textit{n.} (\hyperlink{cicu}{cicu}+\allowbreak \hyperlink{lon}{lon})
technical problem

\textbf{\hypertarget{ciculuat}{ciculuat}} \textit{n.} (\hyperlink{cicu}{cicu}+\allowbreak \hyperlink{luat}{luat})
technology

\textbf{\hypertarget{cik}{cik}} \textit{n.} (Eng. ⟨chick⟩ [t͡ʃɪk])
chickpea; gram; garbanzo; Cicer arietinum

\textbf{\hypertarget{cikweki}{cikweki}} \textit{v.} (\hyperlink{ci}{ci}+\allowbreak \hyperlink{kweki}{kweki})
succeed; ʟєꜱ succeeds at making ʟᴏᴧ happen

\textbf{\hypertarget{citai}{citai}} \textit{v.} (Cmn. ⟨{\chinese{}期待}⟩ [t͡ɕʰi˥taɪ̯˥˩])
anticipate; be prepared; be careful; be cautious; beware; \hyperlink{citailon}{ʟᴏᴧ} anticipates \hyperlink{citailum}{ʟᴜᴍ}

\textbf{\hypertarget{citailon}{citailon}} \textit{n.} (\hyperlink{citai}{citai}+\allowbreak \hyperlink{lon}{lon})
anticipative; prepared; careful; cautious

\textbf{\hypertarget{citailum}{citailum}} \textit{n.} (\hyperlink{citai}{citai}+\allowbreak \hyperlink{lum}{lum})
anticipated

\textbf{\hypertarget{citainu}{citainu}} \textit{v.} (\hyperlink{citai}{citai}+\allowbreak \hyperlink{nu}{nu})
lower anticipation; ʟєꜱ makes ʟᴏᴧ stop anticipating ʟᴜᴍ

\textbf{\hypertarget{citaiki}{citaiki}} \textit{v.} (\hyperlink{citai}{citai}+\allowbreak \hyperlink{ki}{ki})
build anticipation; prepare; caution; ʟєꜱ makes ʟᴏᴧ anticipative about ʟᴜᴍ

\textbf{\hypertarget{citu}{citu}} \textit{v.} (\hyperlink{huli}{\sout{huli}})
be early; be soon; be before; be timely; negative time; \hyperlink{citulon}{ʟᴏᴧ} happens before ʟᴜᴍ

\textbf{\hypertarget{citulon}{citulon}} \textit{n.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{lon}{lon})
past; early; soon; before; timely

\textbf{\hypertarget{citulonsoma}{citulonsoma}} \textit{v.} (\hyperlink{citulon}{citulon}+\allowbreak \hyperlink{soma}{soma})
do history; \hyperlink{citulonsomales}{ʟєꜱ} studies the past to test and update \hyperlink{citulonsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{citulonsomales}{citulonsomales}} \textit{n.} (\hyperlink{citulonsoma}{citulonsoma}+\allowbreak \hyperlink{les}{les})
historian

\textbf{\hypertarget{citulonsomalon}{citulonsomalon}} \textit{n.} (\hyperlink{citulonsoma}{citulonsoma}+\allowbreak \hyperlink{lon}{lon})
history

\textbf{\hypertarget{citulyan}{citulyan}} \textit{n.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{lyan}{lyan})
earliness

\textbf{\hypertarget{citunoluat}{citunoluat}} \textit{n.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{noluat}{noluat})
timer

\textbf{\hypertarget{citunoki}{citunoki}} \textit{v.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{noki}{noki})
pre-educate; \hyperlink{citunokiles}{ʟєꜱ} teaches \hyperlink{citunokilon}{ʟᴏᴧ}

\textbf{\hypertarget{citunokiles}{citunokiles}} \textit{n.} (\hyperlink{citunoki}{citunoki}+\allowbreak \hyperlink{les}{les})
pre-school teacher

\textbf{\hypertarget{citunokilon}{citunokilon}} \textit{n.} (\hyperlink{citunoki}{citunoki}+\allowbreak \hyperlink{lon}{lon})
pre-schooler

\textbf{\hypertarget{citunokilyot}{citunokilyot}} \textit{n.} (\hyperlink{citunoki}{citunoki}+\allowbreak \hyperlink{lyot}{lyot})
pre-school

\textbf{\hypertarget{citunokilwel}{citunokilwel}} \textit{n.} (\hyperlink{citunoki}{citunoki}+\allowbreak \hyperlink{lwel}{lwel})
pre-kindergarden education

\textbf{\hypertarget{citusunnyama}{citusunnyama}} \textit{v.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{sun}{sun}+\allowbreak \hyperlink{nyama}{nyama})
eat brunch; brunch; \hyperlink{citusunnyamales}{ʟєꜱ} eats \hyperlink{citusunnyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{citusunnyamalwel}{citusunnyamalwel}} \textit{n.} (\hyperlink{citusunnyama}{citusunnyama}+\allowbreak \hyperlink{lwel}{lwel})
brunchtime

\textbf{\hypertarget{citusunnyamalon}{citusunnyamalon}} \textit{n.} (\hyperlink{citusunnyama}{citusunnyama}+\allowbreak \hyperlink{lon}{lon})
brunch

\textbf{\hypertarget{citusunnyamales}{citusunnyamales}} \textit{n.} (\hyperlink{citusunnyama}{citusunnyama}+\allowbreak \hyperlink{les}{les})
bruncher

\textbf{\hypertarget{cituki}{cituki}} \textit{v.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{ki}{ki})
pass; advance; move up; travel back in time; \hyperlink{citukiles}{ʟєꜱ} causes \hyperlink{citukilon}{ʟᴏᴧ} to become before ʟᴜᴍ

\textbf{\hypertarget{citukiles}{citukiles}} \textit{n.} (\hyperlink{cituki}{cituki}+\allowbreak \hyperlink{les}{les})
time machine

\textbf{\hypertarget{citukilon}{citukilon}} \textit{n.} (\hyperlink{cituki}{cituki}+\allowbreak \hyperlink{lon}{lon})
passing; present

\textbf{\hypertarget{citukucinihu}{citukucinihu}} \textit{v.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{kucinihu}{kucinihu})
be nostalgic; \hyperlink{citukucinihulon}{ʟᴏᴧ} feels nostalgia about ʟᴜᴍ

\textbf{\hypertarget{citukucinihulon}{citukucinihulon}} \textit{n.} (\hyperlink{citukucinihu}{citukucinihu}+\allowbreak \hyperlink{lon}{lon})
nostalgic

\textbf{\hypertarget{citupensi}{citupensi}} \textit{v.} (\hyperlink{citu}{citu}+\allowbreak \hyperlink{pensi}{pensi})
predict; \hyperlink{citupensilon}{ʟᴏᴧ} predicts \hyperlink{citupensilum}{ʟᴜᴍ}

\textbf{\hypertarget{citupensilon}{citupensilon}} \textit{n.} (\hyperlink{citupensi}{citupensi}+\allowbreak \hyperlink{lon}{lon})
pundit

\textbf{\hypertarget{citupensilum}{citupensilum}} \textit{n.} (\hyperlink{citupensi}{citupensi}+\allowbreak \hyperlink{lum}{lum})
prediction

\textbf{\hypertarget{citupensipowi}{citupensipowi}} \textit{v.} (\hyperlink{citupensi}{citupensi}+\allowbreak \hyperlink{powi}{powi})
be predetermined; be predictable; be deterministic; \hyperlink{citupensipowilon}{ʟᴏᴧ} can be easily predicted

\textbf{\hypertarget{citupensipowilon}{citupensipowilon}} \textit{n.} (\hyperlink{citupensipowi}{citupensipowi}+\allowbreak \hyperlink{lon}{lon})
predetermined; predictable; deterministic

\textbf{\hypertarget{citupensipowinyo}{citupensipowinyo}} \textit{v.} (\hyperlink{citupensipowi}{citupensipowi}+\allowbreak \hyperlink{nyo}{nyo})
be random; be unpredictable; \hyperlink{citupensipowinyolon}{ʟᴏᴧ} cannot possibly be predicted

\textbf{\hypertarget{citupensipowinyolon}{citupensipowinyolon}} \textit{n.} (\hyperlink{citupensipowinyo}{citupensipowinyo}+\allowbreak \hyperlink{lon}{lon})
random; unpredictable

\textbf{\hypertarget{citupensipowinu}{citupensipowinu}} \textit{v.} (\hyperlink{citupensipowi}{citupensipowi}+\allowbreak \hyperlink{nu}{nu})
randomise; scramble; make unpredictable; ʟєꜱ makes ʟᴏᴧ more random

\textbf{\hypertarget{citupensipowinyonyo}{citupensipowinyonyo}} \textit{v.} (\hyperlink{citupensipowinyo}{citupensipowinyo}+\allowbreak \hyperlink{nyo}{nyo})
be pseudorandom; \hyperlink{citupensipowinyonyolon}{ʟᴏᴧ} is pseudorandomly determined

\textbf{\hypertarget{citupensipowinyonyolon}{citupensipowinyonyolon}} \textit{n.} (\hyperlink{citupensipowinyonyo}{citupensipowinyonyo}+\allowbreak \hyperlink{lon}{lon})
pseudorandom

\textbf{\hypertarget{citupensipowiki}{citupensipowiki}} \textit{v.} (\hyperlink{citupensipowi}{citupensipowi}+\allowbreak \hyperlink{ki}{ki})
make predictable; order; determine; ʟєꜱ makes ʟᴏᴧ less random

\textbf{\hypertarget{cipcip}{cipcip}} \textit{n.} (ono. [t͡ʃip t͡ʃip])
bird; Aves

\textbf{\hypertarget{cipcipak}{cipcipak}} \textit{n.} (\hyperlink{cipcip}{cipcip}+\allowbreak \hyperlink{ak}{ak})
avian

\textbf{\hypertarget{cipcippul}{cipcippul}} \textit{n.} (\hyperlink{cipcip}{cipcip}+\allowbreak \hyperlink{pul}{pul})
bird of paradise

\textbf{\hypertarget{cu}{cu}} \textit{ptcl.} (Epo. ⟨ĉu⟩ [t͡ʃu])
?; huh?; \textit{interrogative mood}

\textbf{\hypertarget{cua}{cua}} \textit{v.} (Swa. ⟨jua⟩ [ʄua])
perceive; sense; observe; be perceptible; see; hear; feel; smell; taste; \hyperlink{cualon}{ʟᴏᴧ} perceives \hyperlink{cualum}{ʟᴜᴍ}

\textbf{\hypertarget{cuaec}{cuaec}} \textit{n.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{ec}{ec})
sensor; sense

\textbf{\hypertarget{cuaak}{cuaak}} \textit{n.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{ak}{ak})
perceptual

\textbf{\hypertarget{cualon}{cualon}} \textit{n.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{lon}{lon})
perceiver; observer

\textbf{\hypertarget{cualuat}{cualuat}} \textit{n.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{luat}{luat})
sense; sensor

\textbf{\hypertarget{cualum}{cualum}} \textit{n.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{lum}{lum})
perception; experience; perceptible

\textbf{\hypertarget{cualumak}{cualumak}} \textit{n.} (\hyperlink{cualum}{cualum}+\allowbreak \hyperlink{ak}{ak})
subjective

\textbf{\hypertarget{cuanu}{cuanu}} \textit{v.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{nu}{nu})
obscure; hide; remove; cloud; \hyperlink{cuanules}{ʟєꜱ} makes ʟᴏᴧ stop perceiving \hyperlink{cuanulum}{ʟᴜᴍ}

\textbf{\hypertarget{cuanules}{cuanules}} \textit{n.} (\hyperlink{cuanu}{cuanu}+\allowbreak \hyperlink{les}{les})
cloud

\textbf{\hypertarget{cuanulum}{cuanulum}} \textit{n.} (\hyperlink{cuanu}{cuanu}+\allowbreak \hyperlink{lum}{lum})
cloudy

\textbf{\hypertarget{cuaki}{cuaki}} \textit{v.} (\hyperlink{cua}{cua}+\allowbreak \hyperlink{ki}{ki})
show; look; listen; sniff; taste; read; \hyperlink{cuakiles}{ʟєꜱ} shows \hyperlink{cuakilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{cuakiles}{cuakiles}} \textit{n.} (\hyperlink{cuaki}{cuaki}+\allowbreak \hyperlink{les}{les})
shower; looker; listener

\textbf{\hypertarget{cuakilum}{cuakilum}} \textit{n.} (\hyperlink{cuaki}{cuaki}+\allowbreak \hyperlink{lum}{lum})
thing that is shown

\textbf{\hypertarget{'cun}{'cun}} \textit{n.} (Cmn. ⟨{\chinese{}中}⟩ [ʈ͡ʂʊŋ˥])
Chinese; the Chinese people

\textbf{\hypertarget{'cunak}{'cunak}} \textit{n.} (\hyperlink{'cun}{'cun}+\allowbreak \hyperlink{ak}{ak})
Chinese; from China

\textbf{\hypertarget{'cuncin}{'cuncin}} \textit{n.} (Cmn. ⟨{\chinese{}重庆}⟩ [ʈ͡ʂʰʊŋ˧˥t͡ɕʰi˥˩ŋ])
Chongqing; Chungking

\textbf{\hypertarget{'cuntec}{'cuntec}} \textit{n.} (\hyperlink{'cun}{'cun}+\allowbreak \hyperlink{tec}{tec})
China

\textbf{\hypertarget{'cuntilip}{'cuntilip}} \textit{n.} (\hyperlink{'cun}{'cun}+\allowbreak \hyperlink{tilip}{tilip})
Chinese; the Chinese macrolanguage

\textbf{\hypertarget{'cumieka}{'cumieka}} \textit{n.} (Jam. ⟨Jamaica⟩ [d͡ʒʊmiɛka])
Jamaica (landmass)

\textbf{\hypertarget{'cumiekaak}{'cumiekaak}} \textit{n.} (\hyperlink{'cumieka}{'cumieka}+\allowbreak \hyperlink{ak}{ak})
Jamaican; from Jamaica

\textbf{\hypertarget{'cumiekawon}{'cumiekawon}} \textit{n.} (\hyperlink{'cumieka}{'cumieka}+\allowbreak \hyperlink{won}{won})
Jamaican; the Jamaican people

\textbf{\hypertarget{'cumiekatec}{'cumiekatec}} \textit{n.} (\hyperlink{'cumieka}{'cumieka}+\allowbreak \hyperlink{tec}{tec})
Jamaica (country)

\textbf{\hypertarget{'cumiekatilip}{'cumiekatilip}} \textit{n.} (\hyperlink{'cumieka}{'cumieka}+\allowbreak \hyperlink{tilip}{tilip})
Jamaican Patois; Patwa; Jamaican Creole

\textbf{\hypertarget{cuc}{cuc}} \textit{n.} (Ben. ⟨{\bengali{}জুজু}⟩ [d͡ʑud͡ʑu])
bug; insect; arachnid; myriapod; entognath; small terrestrial invertebrate

\textbf{\hypertarget{cuta}{cuta}} \textit{v.} (\hyperlink{hila}{\sout{hila}})
be still; be unenergetic; move with; \hyperlink{cutalon}{ʟᴏᴧ} is motionless relative to ʟᴜᴍ

\textbf{\hypertarget{cutalon}{cutalon}} \textit{n.} (\hyperlink{cuta}{cuta}+\allowbreak \hyperlink{lon}{lon})
still; unenergetic

\textbf{\hypertarget{cutaki}{cutaki}} \textit{v.} (\hyperlink{cuta}{cuta}+\allowbreak \hyperlink{ki}{ki})
stop; still; settle; deenergise; \hyperlink{cutakiles}{ʟєꜱ} makes ʟᴏᴧ stop moving relative to ʟᴜᴍ

\textbf{\hypertarget{cutakiles}{cutakiles}} \textit{n.} (\hyperlink{cutaki}{cutaki}+\allowbreak \hyperlink{les}{les})
brake

\textbf{\hypertarget{cutakilyot}{cutakilyot}} \textit{n.} (\hyperlink{cutaki}{cutaki}+\allowbreak \hyperlink{lyot}{lyot})
stop; station

\textbf{\hypertarget{cuti}{cuti}} \textit{v.} (\hyperlink{cu}{cu}+\allowbreak \hyperlink{ti}{ti})
ask; interrogate; \hyperlink{cutiles}{ʟєꜱ} asks \hyperlink{cutilon}{ʟᴏᴧ} about \hyperlink{cutilum}{ʟᴜᴍ}

\textbf{\hypertarget{cutiles}{cutiles}} \textit{n.} (\hyperlink{cuti}{cuti}+\allowbreak \hyperlink{les}{les})
curious; interrogator

\textbf{\hypertarget{cutilon}{cutilon}} \textit{n.} (\hyperlink{cuti}{cuti}+\allowbreak \hyperlink{lon}{lon})
interrogatee

\textbf{\hypertarget{cutilum}{cutilum}} \textit{n.} (\hyperlink{cuti}{cuti}+\allowbreak \hyperlink{lum}{lum})
question

\textbf{\hypertarget{cyen}{cyen}} \textit{n.} (Cmn. ⟨{\chinese{}线}⟩ [ɕjɛn˥˩])
string; thread; wire; hair; flexible one-dimensional object

\textbf{\hypertarget{cyenam}{cyenam}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{am}{am})
antenna

\textbf{\hypertarget{cyenut}{cyenut}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{ut}{ut})
alpaca

\textbf{\hypertarget{cyenlek}{cyenlek}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{lek}{lek})
tentacle

\textbf{\hypertarget{cyenlektun}{cyenlektun}} \textit{n.} (\hyperlink{cyenlek}{cyenlek}+\allowbreak \hyperlink{tun}{tun})
molusk; cephalapod

\textbf{\hypertarget{cyenmuf}{cyenmuf}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{muf}{muf})
sheep; mutton

\textbf{\hypertarget{cyenhwok}{cyenhwok}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{hwok}{hwok})
cloth; fabric

\textbf{\hypertarget{cyenciuh}{cyenciuh}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{ciuh}{ciuh})
jute; mallow-leaves

\textbf{\hypertarget{cyencim}{cyencim}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{cim}{cim})
green bean; french bean; string bean; snap

\textbf{\hypertarget{cyenseleal}{cyenseleal}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{seleal}{seleal})
noodle; linguini

\textbf{\hypertarget{cyenfut}{cyenfut}} \textit{n.} (\hyperlink{cyen}{cyen}+\allowbreak \hyperlink{fut}{fut})
coconut

\textbf{\hypertarget{cyau}{cyau}} \textit{v.} (Cmn. ⟨{\chinese{}焦}⟩ [t͡ɕjɑʊ̯˥])
be burnt; be burned; \hyperlink{cyaulon}{ʟᴏᴧ} is burnt

\textbf{\hypertarget{cyaulon}{cyaulon}} \textit{n.} (\hyperlink{cyau}{cyau}+\allowbreak \hyperlink{lon}{lon})
ash; char; charcoal; burnt; burned

\textbf{\hypertarget{cyaunyama}{cyaunyama}} \textit{v.} (\hyperlink{cyau}{cyau}+\allowbreak \hyperlink{nyama}{nyama})
smoke; ʟєꜱ smokes ʟᴏᴧ

\textbf{\hypertarget{cyauhyolon}{cyauhyolon}} \textit{n.} (\hyperlink{cyau}{cyau}+\allowbreak \hyperlink{hyolon}{hyolon})
smoke

\textbf{\hypertarget{cyaufekiluat}{cyaufekiluat}} \textit{n.} (\hyperlink{cyau}{cyau}+\allowbreak \hyperlink{fekiluat}{fekiluat})
firearm; gun

\textbf{\hypertarget{cyauki}{cyauki}} \textit{v.} (\hyperlink{cyau}{cyau}+\allowbreak \hyperlink{ki}{ki})
burn; \hyperlink{cyaukiles}{ʟєꜱ} burns \hyperlink{cyaukilon}{ʟᴏᴧ}

\textbf{\hypertarget{cyaukiufalon}{cyaukiufalon}} \textit{n.} (\hyperlink{cyauki}{cyauki}+\allowbreak \hyperlink{ufalon}{ufalon})
gunpowder

\textbf{\hypertarget{cyaukiles}{cyaukiles}} \textit{n.} (\hyperlink{cyauki}{cyauki}+\allowbreak \hyperlink{les}{les})
burner

\textbf{\hypertarget{cyaukilon}{cyaukilon}} \textit{n.} (\hyperlink{cyauki}{cyauki}+\allowbreak \hyperlink{lon}{lon})
fuel

\textbf{\hypertarget{cyaukicwelon}{cyaukicwelon}} \textit{n.} (\hyperlink{cyauki}{cyauki}+\allowbreak \hyperlink{cwelon}{cwelon})
oil; petroleum

\textbf{\hypertarget{cyaukicwelonkac}{cyaukicwelonkac}} \textit{n.} (\hyperlink{cyaukicwelon}{cyaukicwelon}+\allowbreak \hyperlink{kac}{kac})
oil palm

\textbf{\hypertarget{cyaukicwelonpic}{cyaukicwelonpic}} \textit{n.} (\hyperlink{cyaukicwelon}{cyaukicwelon}+\allowbreak \hyperlink{pic}{pic})
sesame

\textbf{\hypertarget{cyaukipowi}{cyaukipowi}} \textit{v.} (\hyperlink{cyauki}{cyauki}+\allowbreak \hyperlink{powi}{powi})
be flammable; \hyperlink{cyaukipowilon}{ʟᴏᴧ} can burn

\textbf{\hypertarget{cyaukipowilon}{cyaukipowilon}} \textit{n.} (\hyperlink{cyaukipowi}{cyaukipowi}+\allowbreak \hyperlink{lon}{lon})
flammable

\textbf{\hypertarget{cyaukipowinu}{cyaukipowinu}} \textit{v.} (\hyperlink{cyaukipowi}{cyaukipowi}+\allowbreak \hyperlink{nu}{nu})
deflammibify; ʟєꜱ makes ʟᴏᴧ less flammable

\textbf{\hypertarget{cyaukipowinyo}{cyaukipowinyo}} \textit{v.} (\hyperlink{cyaukipowi}{cyaukipowi}+\allowbreak \hyperlink{nyo}{nyo})
be unflammable; be fire-resistant; be flame-retardant; \hyperlink{cyaukipowinyolon}{ʟᴏᴧ} does not burn easily

\textbf{\hypertarget{cyaukipowinyolon}{cyaukipowinyolon}} \textit{n.} (\hyperlink{cyaukipowinyo}{cyaukipowinyo}+\allowbreak \hyperlink{lon}{lon})
unflammable; fire-resistant; flame-retardant

\textbf{\hypertarget{cyaukipowiki}{cyaukipowiki}} \textit{v.} (\hyperlink{cyaukipowi}{cyaukipowi}+\allowbreak \hyperlink{ki}{ki})
flammibify; ʟєꜱ makes ʟᴏᴧ flammable

\textbf{\hypertarget{cyacun}{cyacun}} \textit{n.} (Cmn. ⟨{\chinese{}甲虫}⟩ [t͡ɕja˧˩˧ʈ͡ʂʰʊŋ˧˥])
beetle; Coleoptera

\textbf{\hypertarget{cyatin}{cyatin}} \textit{n.} (Cmn. ⟨{\chinese{}家庭}⟩ [t͡ɕja˥tʰiŋ˧˥])
family; intimate group of people

\textbf{\hypertarget{cyatinak}{cyatinak}} \textit{n.} (\hyperlink{cyatin}{cyatin}+\allowbreak \hyperlink{ak}{ak})
familial

\textbf{\hypertarget{cyo}{cyo}} \textit{v.} (Cmn. ⟨{\chinese{}旧}⟩ [t͡ɕjoʊ̯˥˩])
be old; \hyperlink{cyolon}{ʟᴏᴧ} is old

\textbf{\hypertarget{cyolon}{cyolon}} \textit{n.} (\hyperlink{cyo}{cyo}+\allowbreak \hyperlink{lon}{lon})
elder; senior; adult; grown-up; relic; old

\textbf{\hypertarget{cyolyan}{cyolyan}} \textit{n.} (\hyperlink{cyo}{cyo}+\allowbreak \hyperlink{lyan}{lyan})
age

\textbf{\hypertarget{cyoki}{cyoki}} \textit{v.} (\hyperlink{cyo}{cyo}+\allowbreak \hyperlink{ki}{ki})
age; wear; \hyperlink{cyokiles}{ʟєꜱ} makes ʟᴏᴧ get older

\textbf{\hypertarget{cyokiles}{cyokiles}} \textit{n.} (\hyperlink{cyoki}{cyoki}+\allowbreak \hyperlink{les}{les})
ager; Father Time

\textbf{\hypertarget{cwe}{cwe}} \textit{v.} (Cmn. ⟨{\chinese{}水}⟩ [ʂweɪ̯˧˩˧])
be liquid; be water; \hyperlink{cwelon}{ʟᴏᴧ} is a liquid

\textbf{\hypertarget{cweancosapuluat}{cweancosapuluat}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{ancosapuluat}{ancosapuluat})
mop

\textbf{\hypertarget{cweap}{cweap}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{ap}{ap})
waterfowl; duck; goose; swan

\textbf{\hypertarget{cweufalon}{cweufalon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{ufalon}{ufalon})
mist

\textbf{\hypertarget{cweyeh}{cweyeh}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{yeh}{yeh})
tea; Camellia sinensis

\textbf{\hypertarget{cwelon}{cwelon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{lon}{lon})
body of water; liquid; water

\textbf{\hypertarget{cwelyan}{cwelyan}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{lyan}{lyan})
liquidity

\textbf{\hypertarget{cwenalkaskutilon}{cwenalkaskutilon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{nalkaskutilon}{nalkaskutilon})
diarrhea

\textbf{\hypertarget{cweniceki}{cweniceki}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{niceki}{niceki})
sink; submerge; ʟєꜱ makes ʟᴏᴧ sink in ʟᴜᴍ

\textbf{\hypertarget{cwenyamaluat}{cwenyamaluat}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{nyamaluat}{nyamaluat})
spoon

\textbf{\hypertarget{cwemaceki}{cwemaceki}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{maceki}{maceki})
flood; ʟᴏᴧ is struck by a flood from \hyperlink{cwemacekiles}{ʟєꜱ}

\textbf{\hypertarget{cwemacekiles}{cwemacekiles}} \textit{n.} (\hyperlink{cwemaceki}{cwemaceki}+\allowbreak \hyperlink{les}{les})
floodwaters

\textbf{\hypertarget{cwemontalon}{cwemontalon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{montalon}{montalon})
boat

\textbf{\hypertarget{cwemiclo}{cwemiclo}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{miclo}{miclo})
be humid; be dank; \hyperlink{cwemiclolon}{ʟᴏᴧ} is humid

\textbf{\hypertarget{cwemiclolon}{cwemiclolon}} \textit{n.} (\hyperlink{cwemiclo}{cwemiclo}+\allowbreak \hyperlink{lon}{lon})
humid; dank

\textbf{\hypertarget{cwemwoni}{cwemwoni}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{mwoni}{mwoni})
paint; \hyperlink{cwemwoniles}{ʟєꜱ} paints \hyperlink{cwemwonilum}{ʟᴜᴍ} as \hyperlink{cwemwonilon}{ʟᴏᴧ}

\textbf{\hypertarget{cwemwoniles}{cwemwoniles}} \textit{n.} (\hyperlink{cwemwoni}{cwemwoni}+\allowbreak \hyperlink{les}{les})
painter

\textbf{\hypertarget{cwemwonilon}{cwemwonilon}} \textit{n.} (\hyperlink{cwemwoni}{cwemwoni}+\allowbreak \hyperlink{lon}{lon})
painting

\textbf{\hypertarget{cwemwonilum}{cwemwonilum}} \textit{n.} (\hyperlink{cwemwoni}{cwemwoni}+\allowbreak \hyperlink{lum}{lum})
painting subject

\textbf{\hypertarget{cwehila}{cwehila}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{hila}{hila})
swim; \hyperlink{cwehilalon}{ʟᴏᴧ} swims

\textbf{\hypertarget{cwehilalon}{cwehilalon}} \textit{n.} (\hyperlink{cwehila}{cwehila}+\allowbreak \hyperlink{lon}{lon})
swimmer

\textbf{\hypertarget{cwecai}{cwecai}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{cai}{cai})
feel thirsty; ʟᴏᴧ is thirsty for ʟᴜᴍ

\textbf{\hypertarget{cwecohtuelon}{cwecohtuelon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{cohtuelon}{cohtuelon})
bucket

\textbf{\hypertarget{cwekaelyot}{cwekaelyot}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{kae}{kae}+\allowbreak \hyperlink{lyot}{lyot})
waterfall

\textbf{\hypertarget{cwekaeki}{cwekaeki}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{kaeki}{kaeki})
take shower; shower; ʟєꜱ showers ʟᴏᴧ with \hyperlink{cwekaekilum}{ʟᴜᴍ}

\textbf{\hypertarget{cwekaekilum}{cwekaekilum}} \textit{n.} (\hyperlink{cwekaeki}{cwekaeki}+\allowbreak \hyperlink{lum}{lum})
shower

\textbf{\hypertarget{cweki}{cweki}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{ki}{ki})
condense; liquidify; \hyperlink{cwekiles}{ʟєꜱ} condenses \hyperlink{cwekilon}{ʟᴏᴧ} into a liquid

\textbf{\hypertarget{cwekiles}{cwekiles}} \textit{n.} (\hyperlink{cweki}{cweki}+\allowbreak \hyperlink{les}{les})
condenser

\textbf{\hypertarget{cwekilon}{cwekilon}} \textit{n.} (\hyperlink{cweki}{cweki}+\allowbreak \hyperlink{lon}{lon})
condensed; cloud

\textbf{\hypertarget{cwekuhoki}{cwekuhoki}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{kuhoki}{kuhoki})
float; be buoyant; ʟєꜱ makes \hyperlink{cwekuhokilon}{ʟᴏᴧ} float in ʟᴜᴍ

\textbf{\hypertarget{cwekuhokiicilwel}{cwekuhokiicilwel}} \textit{n.} (\hyperlink{cwekuhoki}{cwekuhoki}+\allowbreak \hyperlink{icilwel}{icilwel})
plankton

\textbf{\hypertarget{cwekuhokilon}{cwekuhokilon}} \textit{n.} (\hyperlink{cwekuhoki}{cwekuhoki}+\allowbreak \hyperlink{lon}{lon})
buoyant

\textbf{\hypertarget{cwekuhokilial}{cwekuhokilial}} \textit{n.} (\hyperlink{cwekuhoki}{cwekuhoki}+\allowbreak \hyperlink{lial}{lial})
buoyant force; buoyancy

\textbf{\hypertarget{cwetayl}{cwetayl}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{tayl}{tayl})
swamp; marsh; bog; wetlands

\textbf{\hypertarget{cwetaka}{cwetaka}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{taka}{taka})
be wet; ʟᴜᴍ is wet with \hyperlink{cwetakalon}{ʟᴏᴧ}

\textbf{\hypertarget{cwetakalon}{cwetakalon}} \textit{n.} (\hyperlink{cwetaka}{cwetaka}+\allowbreak \hyperlink{lon}{lon})
wet

\textbf{\hypertarget{cwetakalyan}{cwetakalyan}} \textit{n.} (\hyperlink{cwetaka}{cwetaka}+\allowbreak \hyperlink{lyan}{lyan})
wetness

\textbf{\hypertarget{cwetakaki}{cwetakaki}} \textit{v.} (\hyperlink{cwetaka}{cwetaka}+\allowbreak \hyperlink{ki}{ki})
wet; wetten; ʟєꜱ wets ʟᴜᴍ with ʟᴏᴧ

\textbf{\hypertarget{cwetatu}{cwetatu}} \textit{v.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{tatu}{tatu})
be mercury; be quicksilver; \hyperlink{cwetatulon}{ʟᴏᴧ} is made of mercury

\textbf{\hypertarget{cwetatulon}{cwetatulon}} \textit{n.} (\hyperlink{cwetatu}{cwetatu}+\allowbreak \hyperlink{lon}{lon})
mercury; quicksilver

\textbf{\hypertarget{cwetyen}{cwetyen}} \textit{num.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{tyen}{tyen})
oasis; watering hole

\textbf{\hypertarget{cwepucolon}{cwepucolon}} \textit{n.} (\hyperlink{cwe}{cwe}+\allowbreak \hyperlink{pucolon}{pucolon})
river; stream; brook

\textbf{\hypertarget{cwal}{cwal}} \textit{n.} (Hin. ⟨{\devanagari{}ज्वार}⟩ [d͡ʒvaːr])
sorghum; great millet; milo; Sorghum bicolor

\section{S}

\textbf{\hypertarget{seyoh}{seyoh}} \textit{n.} (Spa. ⟨sello⟩ [ˈseʝo])
seal; walrus; sea lion; Pinnipedia

\textbf{\hypertarget{'seynfinsen}{'seynfinsen}} \textit{n.} (Svc. ⟨Saint Vincent⟩ [seɪnt ˈvɪnsənt])
Saint Vincent; Yurumei; Hairouna

\textbf{\hypertarget{'seynfinsenak}{'seynfinsenak}} \textit{n.} (\hyperlink{'seynfinsen}{'seynfinsen}+\allowbreak \hyperlink{ak}{ak})
Saint Vincentian; Vincentian; from Saint Vincent

\textbf{\hypertarget{'seynfinsentilip}{'seynfinsentilip}} \textit{n.} (\hyperlink{'seynfinsen}{'seynfinsen}+\allowbreak \hyperlink{tilip}{tilip})
Vincentian Creole

\textbf{\hypertarget{seleal}{seleal}} \textit{n.} (Spa. ⟨cereal⟩ [seɾeˈal])
cereal; grain; cereal grain; grass cultivated for its edible seeds

\textbf{\hypertarget{selealcwelon}{selealcwelon}} \textit{n.} (\hyperlink{seleal}{seleal}+\allowbreak \hyperlink{cwelon}{cwelon})
beer

\textbf{\hypertarget{selealpul}{selealpul}} \textit{n.} (\hyperlink{seleal}{seleal}+\allowbreak \hyperlink{pul}{pul})
buckwheat

\textbf{\hypertarget{'selenium}{'selenium}} \textit{n.} (Lat. ⟨selenium⟩ [selenɪʊ̃])
selenium

\textbf{\hypertarget{selyo}{selyo}} \textit{v.} (Spa. ⟨serio⟩ [ˈseɾjo])
be serious; admire; respect; awe; \hyperlink{selyolon}{ʟᴏᴧ} takes \hyperlink{selyolum}{ʟᴜᴍ} seriously

\textbf{\hypertarget{selyolon}{selyolon}} \textit{n.} (\hyperlink{selyo}{selyo}+\allowbreak \hyperlink{lon}{lon})
in awe; respectful

\textbf{\hypertarget{selyolum}{selyolum}} \textit{n.} (\hyperlink{selyo}{selyo}+\allowbreak \hyperlink{lum}{lum})
admired; awesome; serious

\textbf{\hypertarget{selyoki}{selyoki}} \textit{v.} (\hyperlink{selyo}{selyo}+\allowbreak \hyperlink{ki}{ki})
awe; command respect; ʟєꜱ makes ʟᴏᴧ take ʟᴜᴍ seriously

\textbf{\hypertarget{'selnakola}{'selnakola}} \textit{n.} (Cnr. ⟨Црна Гора⟩ [t͡sr̩ːnaː ɡɔra])
Montenegro

\textbf{\hypertarget{'selnakolaak}{'selnakolaak}} \textit{n.} (\hyperlink{'selnakola}{'selnakola}+\allowbreak \hyperlink{ak}{ak})
Montenegrin; from Montenegro

\textbf{\hypertarget{'selnakolawon}{'selnakolawon}} \textit{n.} (\hyperlink{'selnakola}{'selnakola}+\allowbreak \hyperlink{won}{won})
Montenegrin; the Montenegrin people

\textbf{\hypertarget{'selnakolatilip}{'selnakolatilip}} \textit{n.} (\hyperlink{'selnakola}{'selnakola}+\allowbreak \hyperlink{tilip}{tilip})
Montenegrin; the Montenegrin language

\textbf{\hypertarget{'selsyus}{'selsyus}} \textit{n.} (Swe. ⟨celcius⟩ [ˈsɛːlsjʊs])
degree Celsius; degree centigrade; °C

\textbf{\hypertarget{selti}{selti}} \textit{v.} (Epo. ⟨certi⟩ [ˈt͡serti])
be sure; be certain; be probable; be likely; be easy; \hyperlink{seltilon}{ʟᴏᴧ} is likely to happen according to \hyperlink{seltilum}{ʟᴜᴍ}; see "believe" and "think"

\textbf{\hypertarget{seltilon}{seltilon}} \textit{n.} (\hyperlink{selti}{selti}+\allowbreak \hyperlink{lon}{lon})
sure; certain

\textbf{\hypertarget{seltilum}{seltilum}} \textit{n.} (\hyperlink{selti}{selti}+\allowbreak \hyperlink{lum}{lum})
probable; likely; easy

\textbf{\hypertarget{seltilyan}{seltilyan}} \textit{n.} (\hyperlink{selti}{selti}+\allowbreak \hyperlink{lyan}{lyan})
probability

\textbf{\hypertarget{seltiki}{seltiki}} \textit{v.} (\hyperlink{selti}{selti}+\allowbreak \hyperlink{ki}{ki})
convince; persuade; make sure; ʟєꜱ provides new information that leads ʟᴏᴧ to come to find ʟᴜᴍ probable

\textbf{\hypertarget{'senekal}{'senekal}} \textit{n.} (Wol. ⟨Senegaal⟩ [sɛnɛgaːl])
Senegal

\textbf{\hypertarget{'senekalak}{'senekalak}} \textit{n.} (\hyperlink{'senekal}{'senekal}+\allowbreak \hyperlink{ak}{ak})
Senegalese; from Senegal

\textbf{\hypertarget{'senekalwon}{'senekalwon}} \textit{n.} (\hyperlink{'senekal}{'senekal}+\allowbreak \hyperlink{won}{won})
Senegalese; the Senegalese people

\textbf{\hypertarget{'senliwsi}{'senliwsi}} \textit{n.} (Acf. ⟨Sainte-Lucie⟩ [sɛ̃t lysi])
Saint Lucia (landmass)

\textbf{\hypertarget{'senliwsiak}{'senliwsiak}} \textit{n.} (\hyperlink{'senliwsi}{'senliwsi}+\allowbreak \hyperlink{ak}{ak})
Saint Lucian; from Saint Lucia

\textbf{\hypertarget{'senliwsiwon}{'senliwsiwon}} \textit{n.} (\hyperlink{'senliwsi}{'senliwsi}+\allowbreak \hyperlink{won}{won})
Saint Lucian; the Saint Lucian people

\textbf{\hypertarget{'senliwsitec}{'senliwsitec}} \textit{n.} (\hyperlink{'senliwsi}{'senliwsi}+\allowbreak \hyperlink{tec}{tec})
Saint Lucia (country)

\textbf{\hypertarget{'senliwsitilip}{'senliwsitilip}} \textit{n.} (\hyperlink{'senliwsi}{'senliwsi}+\allowbreak \hyperlink{tilip}{tilip})
Saint Lucian Creole

\textbf{\hypertarget{'senkitsi}{'senkitsi}} \textit{n.} (Aig. ⟨Saint Kitts⟩ [sɛnt kits])
Saint Kitts; Saint Christopher Island; Liamuiga

\textbf{\hypertarget{'senkitsiak}{'senkitsiak}} \textit{n.} (\hyperlink{'senkitsi}{'senkitsi}+\allowbreak \hyperlink{ak}{ak})
Kittitian; from Saint Kitts

\textbf{\hypertarget{'senkitsitilip}{'senkitsitilip}} \textit{n.} (\hyperlink{'senkitsi}{'senkitsi}+\allowbreak \hyperlink{tilip}{tilip})
Saint Kitts Creole; Leeward Caribbean Creole English

\textbf{\hypertarget{ses}{ses}} \textit{n.} (Sot. ⟨setso⟩ [set͡sʼo])
culture; nation; tribe; clan; human social group

\textbf{\hypertarget{'sesel}{'sesel}} \textit{n.} (Crs. ⟨Sesel⟩ [sesɛl])
Seychelles (landmass)

\textbf{\hypertarget{'seselak}{'seselak}} \textit{n.} (\hyperlink{'sesel}{'sesel}+\allowbreak \hyperlink{ak}{ak})
Seychellois; from the Seychelles

\textbf{\hypertarget{'seselwon}{'seselwon}} \textit{n.} (\hyperlink{'sesel}{'sesel}+\allowbreak \hyperlink{won}{won})
Seychellois; the Sechellois people

\textbf{\hypertarget{'seseltec}{'seseltec}} \textit{n.} (\hyperlink{'sesel}{'sesel}+\allowbreak \hyperlink{tec}{tec})
Seychelles

\textbf{\hypertarget{'seseltilip}{'seseltilip}} \textit{n.} (\hyperlink{'sesel}{'sesel}+\allowbreak \hyperlink{tilip}{tilip})
Sechellois Creole

\textbf{\hypertarget{sesak}{sesak}} \textit{n.} (\hyperlink{ses}{ses}+\allowbreak \hyperlink{ak}{ak})
cultural; national; tribal; social

\textbf{\hypertarget{sesyohau}{sesyohau}} \textit{v.} (\hyperlink{ses}{ses}+\allowbreak \hyperlink{yohau}{yohau})
be polite; act appropriately; ʟєꜱ is polite to \hyperlink{sesyohaulon}{ʟᴏᴧ}

\textbf{\hypertarget{sesyohaulon}{sesyohaulon}} \textit{n.} (\hyperlink{sesyohau}{sesyohau}+\allowbreak \hyperlink{lon}{lon})
polite

\textbf{\hypertarget{seswecai}{seswecai}} \textit{v.} (\hyperlink{ses}{ses}+\allowbreak \hyperlink{wecai}{wecai})
be rude; act inappropriately; ʟєꜱ is rude to \hyperlink{seswecailon}{ʟᴏᴧ}

\textbf{\hypertarget{seswecailon}{seswecailon}} \textit{n.} (\hyperlink{seswecai}{seswecai}+\allowbreak \hyperlink{lon}{lon})
rude

\textbf{\hypertarget{sekal}{sekal}} \textit{n.} (Epo. ⟨sekalo⟩ [seˈkalo])
rye; Secale

\textbf{\hypertarget{sekso}{sekso}} \textit{v.} (Spa. ⟨sexo⟩ [ˈsekso])
have sex; make love; ʟєꜱ initiates and has sex with ʟᴏᴧ

\textbf{\hypertarget{seksoec}{seksoec}} \textit{n.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{ec}{ec})
genital

\textbf{\hypertarget{seksonyolon}{seksonyolon}} \textit{n.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{lon}{lon})
virgin

\textbf{\hypertarget{seksomai}{seksomai}} \textit{v.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{mai}{mai})
prostitute; sell one’s body; \hyperlink{seksomailes}{ʟєꜱ} has sex with ʟᴏᴧ for pay

\textbf{\hypertarget{seksomailes}{seksomailes}} \textit{n.} (\hyperlink{seksomai}{seksomai}+\allowbreak \hyperlink{les}{les})
prostitute; whore; harlot

\textbf{\hypertarget{seksocai}{seksocai}} \textit{v.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{cai}{cai})
feel horny; sexually attract; be sexy; ʟᴏᴧ is sexually attracted to \hyperlink{seksocailum}{ʟᴜᴍ}

\textbf{\hypertarget{seksocailum}{seksocailum}} \textit{n.} (\hyperlink{seksocai}{seksocai}+\allowbreak \hyperlink{lum}{lum})
sexy

\textbf{\hypertarget{seksocwelon}{seksocwelon}} \textit{n.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{cwelon}{cwelon})
semen

\textbf{\hypertarget{seksocwelonkoki}{seksocwelonkoki}} \textit{v.} (\hyperlink{seksocwelon}{seksocwelon}+\allowbreak \hyperlink{koki}{koki})
ejaculate; ʟєꜱ ejaculates out ʟᴏᴧ

\textbf{\hypertarget{seksokokilyot}{seksokokilyot}} \textit{n.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{kokilyot}{kokilyot})
vagina

\textbf{\hypertarget{seksopal}{seksopal}} \textit{n.} (\hyperlink{sekso}{sekso}+\allowbreak \hyperlink{pal}{pal})
penis

\textbf{\hypertarget{set}{set}} \textit{num.} (\hyperlink{fol}{\sout{fol}})
C; twelve; dozen; only used for hexadecimal

\textbf{\hypertarget{setak}{setak}} \textit{n.} (\hyperlink{set}{set}+\allowbreak \hyperlink{ak}{ak})
twelfth

\textbf{\hypertarget{setlu}{setlu}} \textit{v.} (\hyperlink{folti}{\sout{folti}})
be weak; be wimpy; \hyperlink{setlulon}{ʟᴏᴧ} is not capable of exerting very much force

\textbf{\hypertarget{setlulon}{setlulon}} \textit{n.} (\hyperlink{setlu}{setlu}+\allowbreak \hyperlink{lon}{lon})
weak; wimpy

\textbf{\hypertarget{setluki}{setluki}} \textit{v.} (\hyperlink{setlu}{setlu}+\allowbreak \hyperlink{ki}{ki})
weaken; \hyperlink{setlukiles}{ʟєꜱ} weakens ʟᴏᴧ

\textbf{\hypertarget{setlukiles}{setlukiles}} \textit{n.} (\hyperlink{setluki}{setluki}+\allowbreak \hyperlink{les}{les})
weakener; junk food

\textbf{\hypertarget{sep}{sep}} \textit{n.} (Hin. ⟨{\devanagari{}सेब}⟩ [seb])
apple; Malus

\textbf{\hypertarget{sepu}{sepu}} \textit{v.} (\hyperlink{fomi}{\sout{fomi}})
be consistent; be solid; be smooth; be filled; \hyperlink{sepulon}{ʟᴏᴧ} is solid all the way through

\textbf{\hypertarget{sepulon}{sepulon}} \textit{n.} (\hyperlink{sepu}{sepu}+\allowbreak \hyperlink{lon}{lon})
consistent; solid; smooth; filled

\textbf{\hypertarget{sepusiklalon}{sepusiklalon}} \textit{n.} (\hyperlink{sepu}{sepu}+\allowbreak \hyperlink{siklalon}{siklalon})
disc

\textbf{\hypertarget{sepuki}{sepuki}} \textit{v.} (\hyperlink{sepu}{sepu}+\allowbreak \hyperlink{ki}{ki})
compress; solidify; smooth; coalesce; \hyperlink{sepukiles}{ʟєꜱ} removes the small pockets from ʟᴏᴧ

\textbf{\hypertarget{sepukiles}{sepukiles}} \textit{n.} (\hyperlink{sepuki}{sepuki}+\allowbreak \hyperlink{les}{les})
defoamer

\textbf{\hypertarget{sa}{sa}} \textit{ptcl.} (Eng. ⟨that⟩ [ðæt])
.; okay.; \textit{indicative mood}

\textbf{\hypertarget{'sa}{'sa}} \textit{n.} (ono. [s])
s; /s/; alveolar fricative

\textbf{\hypertarget{sayhu}{sayhu}} \textit{v.} (Cmn. ⟨{\chinese{}在乎}⟩ [t͡saɪ̯˥˩xu])
care; matter; value; be important; hold dear; \hyperlink{sayhulon}{ʟᴏᴧ} cares about \hyperlink{sayhulum}{ʟᴜᴍ}

\textbf{\hypertarget{sayhulon}{sayhulon}} \textit{n.} (\hyperlink{sayhu}{sayhu}+\allowbreak \hyperlink{lon}{lon})
caring; passionate

\textbf{\hypertarget{sayhulum}{sayhulum}} \textit{n.} (\hyperlink{sayhu}{sayhu}+\allowbreak \hyperlink{lum}{lum})
value; main; primary; important

\textbf{\hypertarget{sayhuki}{sayhuki}} \textit{v.} (\hyperlink{sayhu}{sayhu}+\allowbreak \hyperlink{ki}{ki})
make important; inflate; ʟєꜱ makes ʟᴏᴧ care about ʟᴜᴍ

\textbf{\hypertarget{'salon}{'salon}} \textit{n.} (Kri. ⟨Salone⟩ [salon])
Sierra Leone

\textbf{\hypertarget{'salonak}{'salonak}} \textit{n.} (\hyperlink{'salon}{'salon}+\allowbreak \hyperlink{ak}{ak})
Sierra Leonean; from Sierra Leone

\textbf{\hypertarget{'salonwon}{'salonwon}} \textit{n.} (\hyperlink{'salon}{'salon}+\allowbreak \hyperlink{won}{won})
Sierra Leonean; the Sierra Leonean people

\textbf{\hypertarget{'salontilip}{'salontilip}} \textit{n.} (\hyperlink{'salon}{'salon}+\allowbreak \hyperlink{tilip}{tilip})
Krio; Sierra Leonean Creole

\textbf{\hypertarget{salmon}{salmon}} \textit{n.} (Spa. ⟨salmón⟩ [salˈmon])
salmon; trout; pike; dragonfish; smelt; Protacanthopterygii

\textbf{\hypertarget{'saltenya}{'saltenya}} \textit{n.} (Spa. ⟨salteña⟩ [salˈteɲa])
salteña

\textbf{\hypertarget{'salpatol}{'salpatol}} \textit{n.} (Spa. ⟨Salvador⟩ [salβaˈðor])
El Salvador

\textbf{\hypertarget{'salpatolak}{'salpatolak}} \textit{n.} (\hyperlink{'salpatol}{'salpatol}+\allowbreak \hyperlink{ak}{ak})
Salvadoran; from El Salvador

\textbf{\hypertarget{'salpatolwon}{'salpatolwon}} \textit{n.} (\hyperlink{'salpatol}{'salpatol}+\allowbreak \hyperlink{won}{won})
Salvadoran; Salvadorian; Salvadorean; Guanaco; the Salvadoran people

\textbf{\hypertarget{'salpi}{'salpi}} \textit{n.} (Srp. ⟨Срби⟩ [sr̩̂biː])
Serb; the Serbian people

\textbf{\hypertarget{'salpiak}{'salpiak}} \textit{n.} (\hyperlink{'salpi}{'salpi}+\allowbreak \hyperlink{ak}{ak})
Serbian; from Serbia

\textbf{\hypertarget{'salpitec}{'salpitec}} \textit{n.} (\hyperlink{'salpi}{'salpi}+\allowbreak \hyperlink{tec}{tec})
Serbia

\textbf{\hypertarget{'salpitilip}{'salpitilip}} \textit{n.} (\hyperlink{'salpi}{'salpi}+\allowbreak \hyperlink{tilip}{tilip})
Serbian; the Serbian language

\textbf{\hypertarget{'sawntume}{'sawntume}} \textit{n.} (Por. ⟨São Tomé⟩ [sɐ̃w tuˈmɛ])
São Tomé; São Tomé city

\textbf{\hypertarget{'sawntumetayl}{'sawntumetayl}} \textit{n.} (\hyperlink{'sawntume}{'sawntume}+\allowbreak \hyperlink{tayl}{tayl})
São Tomé Island

\textbf{\hypertarget{'sawntumetaylak}{'sawntumetaylak}} \textit{n.} (\hyperlink{'sawntumetayl}{'sawntumetayl}+\allowbreak \hyperlink{ak}{ak})
São Toméan; Santomean

\textbf{\hypertarget{'sawmpawlu}{'sawmpawlu}} \textit{n.} (Por. ⟨São Paulo⟩ [sɐ̃w̃ ˈpawlu])
São Paulo

\textbf{\hypertarget{san}{san}} \textit{num.} (Cmn. ⟨{\chinese{}三}⟩ [san])
3; three; triple

\textbf{\hypertarget{sanak}{sanak}} \textit{n.} (\hyperlink{san}{san}+\allowbreak \hyperlink{ak}{ak})
third

\textbf{\hypertarget{sano}{sano}} \textit{v.} (Spa. ⟨sano⟩ [ˈsano])
be healthy; \hyperlink{sanolon}{ʟᴏᴧ} is healthy

\textbf{\hypertarget{sanolon}{sanolon}} \textit{n.} (\hyperlink{sano}{sano}+\allowbreak \hyperlink{lon}{lon})
healthy

\textbf{\hypertarget{sanolyan}{sanolyan}} \textit{n.} (\hyperlink{sano}{sano}+\allowbreak \hyperlink{lyan}{lyan})
health

\textbf{\hypertarget{sanoki}{sanoki}} \textit{v.} (\hyperlink{sano}{sano}+\allowbreak \hyperlink{ki}{ki})
heal; treat; \hyperlink{sanokiles}{ʟєꜱ} heals \hyperlink{sanokilon}{ʟᴏᴧ}

\textbf{\hypertarget{sanokiles}{sanokiles}} \textit{n.} (\hyperlink{sanoki}{sanoki}+\allowbreak \hyperlink{les}{les})
doctor; healer

\textbf{\hypertarget{sanokilon}{sanokilon}} \textit{n.} (\hyperlink{sanoki}{sanoki}+\allowbreak \hyperlink{lon}{lon})
patient

\textbf{\hypertarget{sanokiluat}{sanokiluat}} \textit{n.} (\hyperlink{sanoki}{sanoki}+\allowbreak \hyperlink{luat}{luat})
medicine

\textbf{\hypertarget{sannul}{sannul}} \textit{num.} (\hyperlink{san}{san}+\allowbreak \hyperlink{nul}{nul})
30; thirty

\textbf{\hypertarget{sannulnul}{sannulnul}} \textit{num.} (\hyperlink{san}{san}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
300; three hundred

\textbf{\hypertarget{'sanmalino}{'sanmalino}} \textit{n.} (Ita. ⟨San Marino⟩ [san mariːno])
San Marino

\textbf{\hypertarget{'sanmalinoak}{'sanmalinoak}} \textit{n.} (\hyperlink{'sanmalino}{'sanmalino}+\allowbreak \hyperlink{ak}{ak})
Sammarinese; from San Marino

\textbf{\hypertarget{'sanmalinowon}{'sanmalinowon}} \textit{n.} (\hyperlink{'sanmalino}{'sanmalino}+\allowbreak \hyperlink{won}{won})
Sanmarinese; the Sanmarinese people

\textbf{\hypertarget{'sanhe}{'sanhe}} \textit{n.} (Wuu. ⟨{\chinese{}上海}⟩ [zɑ̃hɛ])
Shanghai

\textbf{\hypertarget{'sanhetilip}{'sanhetilip}} \textit{n.} (\hyperlink{'sanhe}{'sanhe}+\allowbreak \hyperlink{tilip}{tilip})
Shanghainese; the Shanghainese language; the Shanghainese dialect; the Hu dialect

\textbf{\hypertarget{sansunkwelwel}{sansunkwelwel}} \textit{n.} (\hyperlink{san}{san}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Wednesday

\textbf{\hypertarget{'sanskaltam}{'sanskaltam}} \textit{n.} (San. ⟨{\devanagari{}संस्कृतम्}⟩ [ˈsɐ̃skr̩tɐm])
Sanskrit; the Sanskrit language

\textbf{\hypertarget{'sanskaltamak}{'sanskaltamak}} \textit{n.} (\hyperlink{'sanskaltam}{'sanskaltam}+\allowbreak \hyperlink{ak}{ak})
Sanskrit; in Sanskrit

\textbf{\hypertarget{'sanskaltamwon}{'sanskaltamwon}} \textit{n.} (\hyperlink{'sanskaltam}{'sanskaltam}+\allowbreak \hyperlink{won}{won})
Sanskrit speakers

\textbf{\hypertarget{sanpelfol}{sanpelfol}} \textit{num.} (\hyperlink{san}{san}+\allowbreak \hyperlink{pel}{pel}+\allowbreak \hyperlink{fol}{fol})
three-quarters; three-fourths; 3/4; .75

\textbf{\hypertarget{sama}{sama}} \textit{v.} (Msa. ⟨sama⟩ [sama])
correspond; match; be respective; \hyperlink{samalon}{ʟᴏᴧ} corresponds to ʟᴜᴍ

\textbf{\hypertarget{samalon}{samalon}} \textit{n.} (\hyperlink{sama}{sama}+\allowbreak \hyperlink{lon}{lon})
respective

\textbf{\hypertarget{saman}{saman}} \textit{n.} (Swa. ⟨samani⟩ [samani])
furniture; large movable equipment used to make a space more livable

\textbf{\hypertarget{'samoa}{'samoa}} \textit{n.} (Smo. ⟨Sāmoa⟩ [ˈsaːmoa])
Samoa (landmass)

\textbf{\hypertarget{'samoaak}{'samoaak}} \textit{n.} (\hyperlink{'samoa}{'samoa}+\allowbreak \hyperlink{ak}{ak})
Samoan; from Samoa

\textbf{\hypertarget{'samoawon}{'samoawon}} \textit{n.} (\hyperlink{'samoa}{'samoa}+\allowbreak \hyperlink{won}{won})
Samoan; the Samoan people

\textbf{\hypertarget{'samoatec}{'samoatec}} \textit{n.} (\hyperlink{'samoa}{'samoa}+\allowbreak \hyperlink{tec}{tec})
Samoa; the Independent State of Samoa

\textbf{\hypertarget{'samoatilip}{'samoatilip}} \textit{n.} (\hyperlink{'samoa}{'samoa}+\allowbreak \hyperlink{tilip}{tilip})
Samoan; the Samoan language

\textbf{\hypertarget{'samliti}{'samliti}} \textit{n.} (San. ⟨{\devanagari{}स्मृति}⟩ [smr̩ti])
Smriti

\textbf{\hypertarget{'samlitifitilip}{'samlitifitilip}} \textit{n.} (\hyperlink{'samliti}{'samliti}+\allowbreak \hyperlink{fitilip}{fitilip})
Smartism; Smarta tradition

\textbf{\hypertarget{'samlitifitilipwon}{'samlitifitilipwon}} \textit{n.} (\hyperlink{'samlitifitilip}{'samlitifitilip}+\allowbreak \hyperlink{won}{won})
Smartism; followers of Smriti

\textbf{\hypertarget{'samlitifitilipak}{'samlitifitilipak}} \textit{n.} (\hyperlink{'samlitifitilip}{'samlitifitilip}+\allowbreak \hyperlink{ak}{ak})
Smarta; of Smartism

\textbf{\hypertarget{'sampesi}{'sampesi}} \textit{n.} (Eng. ⟨Zambezi⟩ [zæmˈbɛzi])
Zambezi river

\textbf{\hypertarget{'sampesiak}{'sampesiak}} \textit{n.} (\hyperlink{'sampesi}{'sampesi}+\allowbreak \hyperlink{ak}{ak})
Zambian

\textbf{\hypertarget{'sampesiwon}{'sampesiwon}} \textit{n.} (\hyperlink{'sampesi}{'sampesi}+\allowbreak \hyperlink{won}{won})
Zambian; the Zambian people

\textbf{\hypertarget{'sampesitec}{'sampesitec}} \textit{n.} (\hyperlink{'sampesi}{'sampesi}+\allowbreak \hyperlink{tec}{tec})
Zambia; the Republic of Zambia

\textbf{\hypertarget{'sahlawi}{'sahlawi}} \textit{n.} (Ara. ⟨{\arabics{}صحراوي}⟩ [sˤaħraːwiː])
Sahrawi; the Sahrawi people

\textbf{\hypertarget{'sahlawiak}{'sahlawiak}} \textit{n.} (\hyperlink{'sahlawi}{'sahlawi}+\allowbreak \hyperlink{ak}{ak})
Sahrawi

\textbf{\hypertarget{'sahlawitec}{'sahlawitec}} \textit{n.} (\hyperlink{'sahlawi}{'sahlawi}+\allowbreak \hyperlink{tec}{tec})
Sahrawi Republic; the Sahrawi Arab Democratic Republic

\textbf{\hypertarget{sas}{sas}} \textit{n.} (ono. [sː])
snake; Serpentes

\textbf{\hypertarget{saskwakwak}{saskwakwak}} \textit{n.} (\hyperlink{sas}{sas}+\allowbreak \hyperlink{kwakwak}{kwakwak})
caecilian

\textbf{\hypertarget{saspes}{saspes}} \textit{n.} (\hyperlink{sas}{sas}+\allowbreak \hyperlink{pes}{pes})
eel

\textbf{\hypertarget{'sakantium}{'sakantium}} \textit{n.} (Lat. ⟨scandium⟩ [skandɪʊ̃])
scandium

\textbf{\hypertarget{sati}{sati}} \textit{v.} (\hyperlink{sa}{sa}+\allowbreak \hyperlink{ti}{ti})
declare; say; tell; answer; give information; \hyperlink{satiles}{ʟєꜱ} tells \hyperlink{satilon}{ʟᴏᴧ} that \hyperlink{satilum}{ʟᴜᴍ} is true

\textbf{\hypertarget{satiles}{satiles}} \textit{n.} (\hyperlink{sati}{sati}+\allowbreak \hyperlink{les}{les})
lecturer; professor

\textbf{\hypertarget{satilon}{satilon}} \textit{n.} (\hyperlink{sati}{sati}+\allowbreak \hyperlink{lon}{lon})
tellee

\textbf{\hypertarget{satilum}{satilum}} \textit{n.} (\hyperlink{sati}{sati}+\allowbreak \hyperlink{lum}{lum})
fact; opinion; notion; sentence

\textbf{\hypertarget{sapu}{sapu}} \textit{v.} (Msa. ⟨sapu⟩ [sapu])
rub; slide; slip; scrub; wipe; ʟєꜱ rubs ʟᴏᴧ

\textbf{\hypertarget{sapuluat}{sapuluat}} \textit{n.} (\hyperlink{sapu}{sapu}+\allowbreak \hyperlink{luat}{luat})
wipe; scrubber

\textbf{\hypertarget{sapupowi}{sapupowi}} \textit{v.} (\hyperlink{sapu}{sapu}+\allowbreak \hyperlink{powi}{powi})
be slippery; be smooth; \hyperlink{sapupowilon}{ʟᴏᴧ} is slippery on ʟᴜᴍ

\textbf{\hypertarget{sapupowilon}{sapupowilon}} \textit{n.} (\hyperlink{sapupowi}{sapupowi}+\allowbreak \hyperlink{lon}{lon})
slippery; smooth

\textbf{\hypertarget{sapupowinyo}{sapupowinyo}} \textit{v.} (\hyperlink{sapupowi}{sapupowi}+\allowbreak \hyperlink{nyo}{nyo})
grip; drag; be grippy; \hyperlink{sapupowinyolon}{ʟᴏᴧ} exerts a frictional force on ʟᴜᴍ

\textbf{\hypertarget{sapupowinyolon}{sapupowinyolon}} \textit{n.} (\hyperlink{sapupowinyo}{sapupowinyo}+\allowbreak \hyperlink{lon}{lon})
grippy

\textbf{\hypertarget{sapupowinyolyan}{sapupowinyolyan}} \textit{n.} (\hyperlink{sapupowinyo}{sapupowinyo}+\allowbreak \hyperlink{lyan}{lyan})
coefficient of friction

\textbf{\hypertarget{sol}{sol}} \textit{spec.} (Spa. ⟨solo⟩ [ˈsolo])
only; just; \textit{describes the following noun phrase and nothing else}

\textbf{\hypertarget{'solowen}{'solowen}} \textit{n.} (Slv. ⟨slovén-⟩ [slɔˈʋeːn])
Slovene; Slovenian; the Slovene people

\textbf{\hypertarget{'solowenak}{'solowenak}} \textit{n.} (\hyperlink{'solowen}{'solowen}+\allowbreak \hyperlink{ak}{ak})
Slovenian; Slovene; from Slovenia

\textbf{\hypertarget{'solowentec}{'solowentec}} \textit{n.} (\hyperlink{'solowen}{'solowen}+\allowbreak \hyperlink{tec}{tec})
Slovenia

\textbf{\hypertarget{'solowentilip}{'solowentilip}} \textit{n.} (\hyperlink{'solowen}{'solowen}+\allowbreak \hyperlink{tilip}{tilip})
Slovene; the Slovene language

\textbf{\hypertarget{'solowak}{'solowak}} \textit{n.} (Slk. ⟨Slovák⟩ [sɫɔʋaːk])
Slovak; Slovakian; the Slovak people

\textbf{\hypertarget{'solowakak}{'solowakak}} \textit{n.} (\hyperlink{'solowak}{'solowak}+\allowbreak \hyperlink{ak}{ak})
Slovak; Slovakian; from Slovakia

\textbf{\hypertarget{'solowaktec}{'solowaktec}} \textit{n.} (\hyperlink{'solowak}{'solowak}+\allowbreak \hyperlink{tec}{tec})
Slovakia

\textbf{\hypertarget{'solowaktilip}{'solowaktilip}} \textit{n.} (\hyperlink{'solowak}{'solowak}+\allowbreak \hyperlink{tilip}{tilip})
Slovak; Slovakian; the Slovak language

\textbf{\hypertarget{'solomon}{'solomon}} \textit{n.} (Pis. ⟨Solomon⟩ [solomon])
Solomon Islands (archipelago)

\textbf{\hypertarget{'solomonak}{'solomonak}} \textit{n.} (\hyperlink{'solomon}{'solomon}+\allowbreak \hyperlink{ak}{ak})
Solomon Island; Solomon Islander; from the Solomon Islands

\textbf{\hypertarget{'solomonwon}{'solomonwon}} \textit{n.} (\hyperlink{'solomon}{'solomon}+\allowbreak \hyperlink{won}{won})
Solomon Islander; the people of the Solomon Islands

\textbf{\hypertarget{'solomontec}{'solomontec}} \textit{n.} (\hyperlink{'solomon}{'solomon}+\allowbreak \hyperlink{tec}{tec})
Solomon Islands (country)

\textbf{\hypertarget{'solomontilip}{'solomontilip}} \textit{n.} (\hyperlink{'solomon}{'solomon}+\allowbreak \hyperlink{tilip}{tilip})
Pijin; Solomons Pidgin

\textbf{\hypertarget{soma}{soma}} \textit{v.} (Swa. ⟨soma⟩ [soma])
study; measure; conduct science; investigate; observe; experiment; test; research; \hyperlink{somales}{ʟєꜱ} uses empirical observation to learn the answer to or more about \hyperlink{somalon}{ʟᴏᴧ}

\textbf{\hypertarget{somales}{somales}} \textit{n.} (\hyperlink{soma}{soma}+\allowbreak \hyperlink{les}{les})
scientist

\textbf{\hypertarget{somalon}{somalon}} \textit{n.} (\hyperlink{soma}{soma}+\allowbreak \hyperlink{lon}{lon})
science; field of study; big question; the body of knowledge formed by the scientific process

\textbf{\hypertarget{'somali}{'somali}} \textit{n.} (Som. ⟨Soomaali⟩ [sɔ̀ːmɑ́ːlì])
Somali; Somalian; the Somali people

\textbf{\hypertarget{'somaliak}{'somaliak}} \textit{n.} (\hyperlink{'somali}{'somali}+\allowbreak \hyperlink{ak}{ak})
Somalian; from Somalia

\textbf{\hypertarget{'somalitec}{'somalitec}} \textit{n.} (\hyperlink{'somali}{'somali}+\allowbreak \hyperlink{tec}{tec})
Somalia

\textbf{\hypertarget{'somalitilip}{'somalitilip}} \textit{n.} (\hyperlink{'somali}{'somali}+\allowbreak \hyperlink{tilip}{tilip})
Somali; the Somali language

\textbf{\hypertarget{somaluat}{somaluat}} \textit{n.} (\hyperlink{soma}{soma}+\allowbreak \hyperlink{luat}{luat})
measuring device; instrument; meter

\textbf{\hypertarget{somalyot}{somalyot}} \textit{n.} (\hyperlink{soma}{soma}+\allowbreak \hyperlink{lyot}{lyot})
laboratory; lab

\textbf{\hypertarget{somasoma}{somasoma}} \textit{v.} (\hyperlink{soma}{soma}+\allowbreak \hyperlink{soma}{soma})
do metrology; \hyperlink{somasomales}{ʟєꜱ} studies instruments and measurement to learn about \hyperlink{somasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{somasomales}{somasomales}} \textit{n.} (\hyperlink{somasoma}{somasoma}+\allowbreak \hyperlink{les}{les})
metrologist

\textbf{\hypertarget{somasomalon}{somasomalon}} \textit{n.} (\hyperlink{somasoma}{somasoma}+\allowbreak \hyperlink{lon}{lon})
qualities of measurement and the scientific method

\textbf{\hypertarget{soh}{soh}} \textit{n.} (Spa. ⟨soja⟩ [ˈsoxa])
soy; soybean; soya bean; Glycine max

\textbf{\hypertarget{sosia}{sosia}} \textit{v.} (Epo. ⟨socia⟩ [soˈt͡sia])
be social; socialise; \hyperlink{sosialon}{ʟᴏᴧ} socialises with \hyperlink{sosialum}{ʟᴜᴍ}

\textbf{\hypertarget{sosialet}{sosialet}} \textit{n.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{let}{let})
society

\textbf{\hypertarget{sosialon}{sosialon}} \textit{n.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{lon}{lon})
extravert; social

\textbf{\hypertarget{sosialum}{sosialum}} \textit{n.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{lum}{lum})
society; community

\textbf{\hypertarget{sosialumsoma}{sosialumsoma}} \textit{v.} (\hyperlink{sosialum}{sosialum}+\allowbreak \hyperlink{soma}{soma})
do sociology; \hyperlink{sosialumsomales}{ʟєꜱ} studies societies to learn about \hyperlink{sosialumsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{sosialumsomalon}{sosialumsomalon}} \textit{n.} (\hyperlink{sosialumsoma}{sosialumsoma}+\allowbreak \hyperlink{lon}{lon})
sociology

\textbf{\hypertarget{sosialumsomales}{sosialumsomales}} \textit{n.} (\hyperlink{sosialumsoma}{sosialumsoma}+\allowbreak \hyperlink{les}{les})
sociologist

\textbf{\hypertarget{sosialuso}{sosialuso}} \textit{v.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{luso}{luso})
be charismatic; \hyperlink{sosialusolon}{ʟᴏᴧ} is charismatic

\textbf{\hypertarget{sosialusolon}{sosialusolon}} \textit{n.} (\hyperlink{sosialuso}{sosialuso}+\allowbreak \hyperlink{lon}{lon})
charismatic

\textbf{\hypertarget{sosialyan}{sosialyan}} \textit{n.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{lyan}{lyan})
extraversion

\textbf{\hypertarget{sosiamoca}{sosiamoca}} \textit{v.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{moca}{moca})
party; throw party; play; hang out; celebrate; \hyperlink{sosiamocales}{ʟєꜱ} initiates a social gathering with \hyperlink{sosiamocalon}{ʟᴏᴧ}

\textbf{\hypertarget{sosiamocales}{sosiamocales}} \textit{n.} (\hyperlink{sosiamoca}{sosiamoca}+\allowbreak \hyperlink{les}{les})
partier; host

\textbf{\hypertarget{sosiamocalon}{sosiamocalon}} \textit{n.} (\hyperlink{sosiamoca}{sosiamoca}+\allowbreak \hyperlink{lon}{lon})
party-goers; attendee

\textbf{\hypertarget{sosiamocalwel}{sosiamocalwel}} \textit{n.} (\hyperlink{sosiamoca}{sosiamoca}+\allowbreak \hyperlink{lwel}{lwel})
party; play-date

\textbf{\hypertarget{sosiaki}{sosiaki}} \textit{v.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{ki}{ki})
integrate; ʟєꜱ socially integrates ʟᴏᴧ with ʟᴜᴍ

\textbf{\hypertarget{sosiatafu}{sosiatafu}} \textit{v.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{tafu}{tafu})
be awkward; be uncomfortable; \hyperlink{sosiatafulon}{ʟᴏᴧ} finds \hyperlink{sosiatafulum}{ʟᴜᴍ} awkward

\textbf{\hypertarget{sosiatafulon}{sosiatafulon}} \textit{n.} (\hyperlink{sosiatafu}{sosiatafu}+\allowbreak \hyperlink{lon}{lon})
uncomfortable

\textbf{\hypertarget{sosiatafulum}{sosiatafulum}} \textit{n.} (\hyperlink{sosiatafu}{sosiatafu}+\allowbreak \hyperlink{lum}{lum})
herp; awkward

\textbf{\hypertarget{sosiatife}{sosiatife}} \textit{v.} (\hyperlink{sosia}{sosia}+\allowbreak \hyperlink{tife}{tife})
be awkward; \hyperlink{sosiatifelon}{ʟᴏᴧ} is habitually awkward with people

\textbf{\hypertarget{sosiatifelon}{sosiatifelon}} \textit{n.} (\hyperlink{sosiatife}{sosiatife}+\allowbreak \hyperlink{lon}{lon})
awkward

\textbf{\hypertarget{'sokot}{'sokot}} \textit{n.} (Sco. ⟨Scot⟩ [skɔt])
Scot; the Scottish people

\textbf{\hypertarget{'sokotak}{'sokotak}} \textit{n.} (\hyperlink{'sokot}{'sokot}+\allowbreak \hyperlink{ak}{ak})
Scottish; from Scotland

\textbf{\hypertarget{'sokot'kealtilip}{'sokot'kealtilip}} \textit{n.} (\hyperlink{'sokot}{'sokot}+\allowbreak \hyperlink{'kealtilip}{'kealtilip})
Scots Gaelic; the Scots Gaelic language

\textbf{\hypertarget{'sokottec}{'sokottec}} \textit{n.} (\hyperlink{'sokot}{'sokot}+\allowbreak \hyperlink{tec}{tec})
Scotland

\textbf{\hypertarget{'sokottilip}{'sokottilip}} \textit{n.} (\hyperlink{'sokot}{'sokot}+\allowbreak \hyperlink{tilip}{tilip})
Scots; Lowland Scots; the Scots language

\textbf{\hypertarget{sota}{sota}} \textit{v.} (Hin. ⟨{\devanagari{}सौदा}⟩ [sɔːdaː])
deal; have deal; do business; \hyperlink{sotalon}{ʟᴏᴧ} has a deal with \hyperlink{sotalum}{ʟᴜᴍ}

\textbf{\hypertarget{sotalon}{sotalon}} \textit{n.} (\hyperlink{sota}{sota}+\allowbreak \hyperlink{lon}{lon})
dealer; entrepreneur

\textbf{\hypertarget{sotalip}{sotalip}} \textit{n.} (\hyperlink{sota}{sota}+\allowbreak \hyperlink{lip}{lip})
agreement; deal

\textbf{\hypertarget{sotalum}{sotalum}} \textit{n.} (\hyperlink{sota}{sota}+\allowbreak \hyperlink{lum}{lum})
business; beauracracy; business partner

\textbf{\hypertarget{sotanu}{sotanu}} \textit{v.} (\hyperlink{sota}{sota}+\allowbreak \hyperlink{nu}{nu})
break deal; violate agreement; cut ties; \hyperlink{sotanules}{ʟєꜱ} causes business to cease between ʟᴏᴧ and \hyperlink{sotanulum}{ʟᴜᴍ}

\textbf{\hypertarget{sotanules}{sotanules}} \textit{n.} (\hyperlink{sotanu}{sotanu}+\allowbreak \hyperlink{les}{les})
deal breaker

\textbf{\hypertarget{sotanulum}{sotanulum}} \textit{n.} (\hyperlink{sotanu}{sotanu}+\allowbreak \hyperlink{lum}{lum})
ex-business partner

\textbf{\hypertarget{sotaki}{sotaki}} \textit{v.} (\hyperlink{sota}{sota}+\allowbreak \hyperlink{ki}{ki})
strike deal; make deal; do business; negotiate; \hyperlink{sotakiles}{ʟєꜱ} causes ʟᴏᴧ to come to a business agreement with ʟᴜᴍ

\textbf{\hypertarget{sotakiles}{sotakiles}} \textit{n.} (\hyperlink{sotaki}{sotaki}+\allowbreak \hyperlink{les}{les})
negotiator

\textbf{\hypertarget{'sotlonsium}{'sotlonsium}} \textit{n.} (Lat. ⟨strontium⟩ [stront͡sɪʊ̃])
strontium

\textbf{\hypertarget{sope}{sope}} \textit{v.} (Mar. ⟨{\devanagari{}सोपे}⟩ [sope])
be simple; be basic; be elementary; \hyperlink{sopelon}{ʟᴏᴧ} is simple

\textbf{\hypertarget{sopelon}{sopelon}} \textit{n.} (\hyperlink{sope}{sope}+\allowbreak \hyperlink{lon}{lon})
simple; basic; elementary

\textbf{\hypertarget{sopeki}{sopeki}} \textit{v.} (\hyperlink{sope}{sope}+\allowbreak \hyperlink{ki}{ki})
simplify; \hyperlink{sopekiles}{ʟєꜱ} simplifies ʟᴏᴧ

\textbf{\hypertarget{sopekiles}{sopekiles}} \textit{n.} (\hyperlink{sopeki}{sopeki}+\allowbreak \hyperlink{les}{les})
simplifier

\textbf{\hypertarget{sil}{sil}} \textit{n.} (Hin. ⟨{\devanagari{}सिर}⟩ [sir])
head; bulge on top of an animal containing many of its sensual and cognitive capabilities

\textbf{\hypertarget{sila}{sila}} \textit{v.} (Fil. ⟨sira⟩ [siɾa])
be damaged; be hurt; be wounded; be in tatters; \hyperlink{silalon}{ʟᴏᴧ} is damaged

\textbf{\hypertarget{silalon}{silalon}} \textit{n.} (\hyperlink{sila}{sila}+\allowbreak \hyperlink{lon}{lon})
damaged; hurt; wounded; in tatters

\textbf{\hypertarget{silanu}{silanu}} \textit{v.} (\hyperlink{sila}{sila}+\allowbreak \hyperlink{nu}{nu})
repair; mend; fix; clean; \hyperlink{silanules}{ʟєꜱ} repairs ʟᴏᴧ

\textbf{\hypertarget{silanules}{silanules}} \textit{n.} (\hyperlink{silanu}{silanu}+\allowbreak \hyperlink{les}{les})
repairperson

\textbf{\hypertarget{silak}{silak}} \textit{n.} (\hyperlink{sil}{sil}+\allowbreak \hyperlink{ak}{ak})
cranial; cephalic

\textbf{\hypertarget{silaki}{silaki}} \textit{v.} (\hyperlink{sila}{sila}+\allowbreak \hyperlink{ki}{ki})
damage; hurt; harm; wear; \hyperlink{silakiles}{ʟєꜱ} damages ʟᴏᴧ

\textbf{\hypertarget{silakiles}{silakiles}} \textit{n.} (\hyperlink{silaki}{silaki}+\allowbreak \hyperlink{les}{les})
harmer

\textbf{\hypertarget{silakipowi}{silakipowi}} \textit{v.} (\hyperlink{silaki}{silaki}+\allowbreak \hyperlink{powi}{powi})
be susceptible; be vulnerable; be exposed; ʟєꜱ can harm \hyperlink{silakipowilon}{ʟᴏᴧ}

\textbf{\hypertarget{silakipowilon}{silakipowilon}} \textit{n.} (\hyperlink{silakipowi}{silakipowi}+\allowbreak \hyperlink{lon}{lon})
susceptible; vulnerable; exposed

\textbf{\hypertarget{silakipowinu}{silakipowinu}} \textit{v.} (\hyperlink{silakipowi}{silakipowi}+\allowbreak \hyperlink{nu}{nu})
protect; defend; guard; \hyperlink{silakipowinules}{ʟєꜱ} prevents ʟᴜᴍ from harming ʟᴏᴧ

\textbf{\hypertarget{silakipowinuec}{silakipowinuec}} \textit{n.} (\hyperlink{silakipowinu}{silakipowinu}+\allowbreak \hyperlink{ec}{ec})
shell

\textbf{\hypertarget{silakipowinules}{silakipowinules}} \textit{n.} (\hyperlink{silakipowinu}{silakipowinu}+\allowbreak \hyperlink{les}{les})
shield; protection; defense; guard

\textbf{\hypertarget{silakipowinuswa}{silakipowinuswa}} \textit{v.} (\hyperlink{silakipowinu}{silakipowinu}+\allowbreak \hyperlink{swa}{swa})
feel defensive; ʟᴏᴧ is defensive about ʟᴜᴍ

\textbf{\hypertarget{silakipowinupolti}{silakipowinupolti}} \textit{v.} (\hyperlink{silakipowinu}{silakipowinu}+\allowbreak \hyperlink{polti}{polti})
be armoured; \hyperlink{silakipowinupoltilum}{ʟᴜᴍ} armours \hyperlink{silakipowinupoltilon}{ʟᴏᴧ}

\textbf{\hypertarget{silakipowinupoltilon}{silakipowinupoltilon}} \textit{n.} (\hyperlink{silakipowinupolti}{silakipowinupolti}+\allowbreak \hyperlink{lon}{lon})
armoured

\textbf{\hypertarget{silakipowinupoltilum}{silakipowinupoltilum}} \textit{n.} (\hyperlink{silakipowinupolti}{silakipowinupolti}+\allowbreak \hyperlink{lum}{lum})
armour

\textbf{\hypertarget{silakipowinupoltiki}{silakipowinupoltiki}} \textit{v.} (\hyperlink{silakipowinu}{silakipowinu}+\allowbreak \hyperlink{poltiki}{poltiki})
armour; \hyperlink{silakipowinupoltikiles}{ʟєꜱ} armours ʟᴏᴧ in ʟᴜᴍ

\textbf{\hypertarget{silakipowinupoltikiles}{silakipowinupoltikiles}} \textit{n.} (\hyperlink{silakipowinupoltiki}{silakipowinupoltiki}+\allowbreak \hyperlink{les}{les})
armourer

\textbf{\hypertarget{silakipowinyo}{silakipowinyo}} \textit{v.} (\hyperlink{silakipowi}{silakipowi}+\allowbreak \hyperlink{nyo}{nyo})
be invulnerable; be invincible; be durable; ʟєꜱ cannot harm \hyperlink{silakipowinyolon}{ʟᴏᴧ}

\textbf{\hypertarget{silakipowinyolon}{silakipowinyolon}} \textit{n.} (\hyperlink{silakipowinyo}{silakipowinyo}+\allowbreak \hyperlink{lon}{lon})
invulnerable; invincible; durable

\textbf{\hypertarget{silakipowiki}{silakipowiki}} \textit{v.} (\hyperlink{silakipowi}{silakipowi}+\allowbreak \hyperlink{ki}{ki})
vulnerate; expose; lower defenses; ʟєꜱ makes ʟᴏᴧ vulnerable to ʟᴜᴍ

\textbf{\hypertarget{'silius}{'silius}} \textit{n.} (Lat. ⟨Sīrius⟩ [sirɪʊs])
Sirius

\textbf{\hypertarget{'silicium}{'silicium}} \textit{n.} (Lat. ⟨silicium⟩ [sɪlit͡ʃɪʊ̃])
silicon

\textbf{\hypertarget{silkol}{silkol}} \textit{n.} (\hyperlink{sil}{sil}+\allowbreak \hyperlink{kol}{kol})
cabbage; brassica

\textbf{\hypertarget{silkiah}{silkiah}} \textit{n.} (\hyperlink{sil}{sil}+\allowbreak \hyperlink{kiah}{kiah})
bald eagle

\textbf{\hypertarget{siltokalyot}{siltokalyot}} \textit{n.} (\hyperlink{sil}{sil}+\allowbreak \hyperlink{tokalyot}{tokalyot})
neck

\textbf{\hypertarget{siltokalyotpoltilum}{siltokalyotpoltilum}} \textit{n.} (\hyperlink{siltokalyot}{siltokalyot}+\allowbreak \hyperlink{poltilum}{poltilum})
necklace

\textbf{\hypertarget{'sinapula}{'sinapula}} \textit{n.} (Msa. ⟨Singapura⟩ [siŋəpurə])
Singapore

\textbf{\hypertarget{'sinapulaak}{'sinapulaak}} \textit{n.} (\hyperlink{'sinapula}{'sinapula}+\allowbreak \hyperlink{ak}{ak})
Singaporean; Singapore; from Singapore

\textbf{\hypertarget{'sinapulawon}{'sinapulawon}} \textit{n.} (\hyperlink{'sinapula}{'sinapula}+\allowbreak \hyperlink{won}{won})
Singaporean; the Singaporean people

\textbf{\hypertarget{'sinkum}{'sinkum}} \textit{n.} (Lat. ⟨zincum⟩ [zincʊ̃])
zinc

\textbf{\hypertarget{'simpapwe}{'simpapwe}} \textit{n.} (Sna. ⟨Zimbabwe⟩ [zimbabwe])
Zimbabwe

\textbf{\hypertarget{'simpapweak}{'simpapweak}} \textit{n.} (\hyperlink{'simpapwe}{'simpapwe}+\allowbreak \hyperlink{ak}{ak})
Zimbabwean; from Zimbabwe

\textbf{\hypertarget{'simpapwewon}{'simpapwewon}} \textit{n.} (\hyperlink{'simpapwe}{'simpapwe}+\allowbreak \hyperlink{won}{won})
Zimbabwean; Zimbo; the Zimbabwean people

\textbf{\hypertarget{sica}{sica}} \textit{v.} (ono. [ʃː])
be quiet; dim; soft; faint; weak; \hyperlink{sicalon}{ʟᴏᴧ} is quiet

\textbf{\hypertarget{sicalon}{sicalon}} \textit{n.} (\hyperlink{sica}{sica}+\allowbreak \hyperlink{lon}{lon})
quiet

\textbf{\hypertarget{sicalwel}{sicalwel}} \textit{n.} (\hyperlink{sica}{sica}+\allowbreak \hyperlink{lwel}{lwel})
nighttime; night

\textbf{\hypertarget{sicalwelkiah}{sicalwelkiah}} \textit{n.} (\hyperlink{sicalwel}{sicalwel}+\allowbreak \hyperlink{kiah}{kiah})
owl

\textbf{\hypertarget{sicaki}{sicaki}} \textit{v.} (\hyperlink{sica}{sica}+\allowbreak \hyperlink{ki}{ki})
dampen; quiet; dim; soften; weaken; decrescendo; \hyperlink{sicakiles}{ʟєꜱ} dampens ʟᴏᴧ

\textbf{\hypertarget{sicakiles}{sicakiles}} \textit{n.} (\hyperlink{sicaki}{sicaki}+\allowbreak \hyperlink{les}{les})
damper

\textbf{\hypertarget{sicakilwel}{sicakilwel}} \textit{n.} (\hyperlink{sicaki}{sicaki}+\allowbreak \hyperlink{lwel}{lwel})
evening; dusk

\textbf{\hypertarget{sicapola}{sicapola}} \textit{v.} (\hyperlink{sica}{sica}+\allowbreak \hyperlink{pola}{pola})
whisper; ʟєꜱ says \hyperlink{sicapolalum}{ʟᴜᴍ} to ʟᴏᴧ without voicing

\textbf{\hypertarget{sicapolalum}{sicapolalum}} \textit{n.} (\hyperlink{sicapola}{sicapola}+\allowbreak \hyperlink{lum}{lum})
whisper

\textbf{\hypertarget{sison}{sison}} \textit{n.} (Eng. ⟨season⟩ [ˈsiːzən])
season; period of time characterised by some thing or event

\textbf{\hypertarget{sisonak}{sisonak}} \textit{n.} (\hyperlink{sison}{sison}+\allowbreak \hyperlink{ak}{ak})
seasonal

\textbf{\hypertarget{sif}{sif}} \textit{pn.} (Zul. ⟨zí-⟩ [z̤í])
self; themself; itself; herself; himself; themselves; myself; yourself; ourselves; yourselves; \textit{reflexive}; a noun phrase mentioned previously in this sentence

\textbf{\hypertarget{sifak}{sifak}} \textit{n.} (\hyperlink{sif}{sif}+\allowbreak \hyperlink{ak}{ak})
its own; her own; his own; their own; my own; your own; our own

\textbf{\hypertarget{siftueki}{siftueki}} \textit{v.} (\hyperlink{sif}{sif}+\allowbreak \hyperlink{tueki}{tueki})
be resourceful; enterprise; \hyperlink{siftuekilon}{ʟᴏᴧ} resourcefully acquires ʟᴜᴍ

\textbf{\hypertarget{siftuekilon}{siftuekilon}} \textit{n.} (\hyperlink{siftueki}{siftueki}+\allowbreak \hyperlink{lon}{lon})
resourceful

\textbf{\hypertarget{'sik}{'sik}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਸਿੱਖ}⟩ [ˈsɪkkʰ])
Sikh; followers of Sikhism

\textbf{\hypertarget{'sikak}{'sikak}} \textit{n.} (\hyperlink{'sik}{'sik}+\allowbreak \hyperlink{ak}{ak})
Sikh; of Sikhism

\textbf{\hypertarget{sikla}{sikla}} \textit{v.} (Epo. ⟨cirkla⟩ [ˈt͡sirkla])
be circular; be round; \hyperlink{siklalon}{ʟᴏᴧ} is circular

\textbf{\hypertarget{siklalon}{siklalon}} \textit{n.} (\hyperlink{sikla}{sikla}+\allowbreak \hyperlink{lon}{lon})
circle; ring; circular; round

\textbf{\hypertarget{siklalonpum}{siklalonpum}} \textit{n.} (\hyperlink{siklalon}{siklalon}+\allowbreak \hyperlink{pum}{pum})
Saturn

\textbf{\hypertarget{siklalonpumak}{siklalonpumak}} \textit{n.} (\hyperlink{siklalonpum}{siklalonpum}+\allowbreak \hyperlink{ak}{ak})
Saturnic

\textbf{\hypertarget{siklaki}{siklaki}} \textit{v.} (\hyperlink{sikla}{sikla}+\allowbreak \hyperlink{ki}{ki})
circularise; round; circle; ʟєꜱ turns ʟᴏᴧ into a circle

\textbf{\hypertarget{siklakio}{siklakio}} \textit{v.} (\hyperlink{sikla}{sikla}+\allowbreak \hyperlink{kio}{kio})
be-pearl; ʟᴏᴧ is made of pearl

\textbf{\hypertarget{'sikfitilip}{'sikfitilip}} \textit{n.} (\hyperlink{'sik}{'sik}+\allowbreak \hyperlink{fitilip}{fitilip})
Sikhism; Sikhi

\textbf{\hypertarget{site}{site}} \textit{v.} (Hin. ⟨{\devanagari{}सीधे}⟩ [siːd̤e])
be straight; be linear; be flat; \hyperlink{sitelon}{ʟᴏᴧ} is straight

\textbf{\hypertarget{sitelon}{sitelon}} \textit{n.} (\hyperlink{site}{site}+\allowbreak \hyperlink{lon}{lon})
line; plane; straightedge; straight; linear; flat

\textbf{\hypertarget{siteki}{siteki}} \textit{v.} (\hyperlink{site}{site}+\allowbreak \hyperlink{ki}{ki})
straighten; flatten; splay; open; \hyperlink{sitekiles}{ʟєꜱ} straightens ʟᴏᴧ

\textbf{\hypertarget{sitekiles}{sitekiles}} \textit{n.} (\hyperlink{siteki}{siteki}+\allowbreak \hyperlink{les}{les})
straightener; flattener

\textbf{\hypertarget{sitetayl}{sitetayl}} \textit{n.} (\hyperlink{site}{site}+\allowbreak \hyperlink{tayl}{tayl})
plains; flatlands

\textbf{\hypertarget{siteponto}{siteponto}} \textit{v.} (\hyperlink{site}{site}+\allowbreak \hyperlink{ponto}{ponto})
be polygonal; \hyperlink{sitepontolon}{ʟᴏᴧ} is polygonal

\textbf{\hypertarget{sitepontolon}{sitepontolon}} \textit{n.} (\hyperlink{siteponto}{siteponto}+\allowbreak \hyperlink{lon}{lon})
polygon; polygonal

\textbf{\hypertarget{sitepontoki}{sitepontoki}} \textit{v.} (\hyperlink{siteponto}{siteponto}+\allowbreak \hyperlink{ki}{ki})
polygonise; ʟєꜱ turns ʟᴏᴧ into a polygon

\textbf{\hypertarget{'sital}{'sital}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਸਿਤਾਰ}⟩ [sɪˈtaːr])
sitar

\textbf{\hypertarget{'sipili}{'sipili}} \textit{n.} (Rus. ⟨Сиби́рь⟩ [sʲɪˈbʲirʲ])
Siberia

\textbf{\hypertarget{'sipiliak}{'sipiliak}} \textit{n.} (\hyperlink{'sipili}{'sipili}+\allowbreak \hyperlink{ak}{ak})
Siberian; from Siberia

\textbf{\hypertarget{'sipiwit}{'sipiwit}} \textit{n.} (Eng. ⟨spirit⟩ [ˈspɪɹʷɪt])
spirit (Spiritualism)

\textbf{\hypertarget{'sipiwitfitilip}{'sipiwitfitilip}} \textit{n.} (\hyperlink{'sipiwit}{'sipiwit}+\allowbreak \hyperlink{fitilip}{fitilip})
Spiritualism

\textbf{\hypertarget{'sipiwitfitilipwon}{'sipiwitfitilipwon}} \textit{n.} (\hyperlink{'sipiwitfitilip}{'sipiwitfitilip}+\allowbreak \hyperlink{won}{won})
Spiritualist; followers of Spiritualism

\textbf{\hypertarget{'sipiwitfitilipak}{'sipiwitfitilipak}} \textit{n.} (\hyperlink{'sipiwitfitilip}{'sipiwitfitilip}+\allowbreak \hyperlink{ak}{ak})
Spiritualist; of Spiritualism

\textbf{\hypertarget{'suomi}{'suomi}} \textit{n.} (Fin. ⟨Suomi⟩ [ˈsuo̯mi])
Finland

\textbf{\hypertarget{'suomiak}{'suomiak}} \textit{n.} (\hyperlink{'suomi}{'suomi}+\allowbreak \hyperlink{ak}{ak})
Finnish; from Finland

\textbf{\hypertarget{'suomiwon}{'suomiwon}} \textit{n.} (\hyperlink{'suomi}{'suomi}+\allowbreak \hyperlink{won}{won})
Finn; the Finnish people

\textbf{\hypertarget{'suomitilip}{'suomitilip}} \textit{n.} (\hyperlink{'suomi}{'suomi}+\allowbreak \hyperlink{tilip}{tilip})
Finnish; the Finnish people

\textbf{\hypertarget{suotu}{suotu}} \textit{v.} (\hyperlink{fieli}{\sout{fieli}})
be ashamed; be sorry; be remorseful; regret; \hyperlink{suotulon}{ʟᴏᴧ} feels ashamed about \hyperlink{suotulum}{ʟᴜᴍ}

\textbf{\hypertarget{suotulon}{suotulon}} \textit{n.} (\hyperlink{suotu}{suotu}+\allowbreak \hyperlink{lon}{lon})
ashamed; sorry; remorseful

\textbf{\hypertarget{suotulum}{suotulum}} \textit{n.} (\hyperlink{suotu}{suotu}+\allowbreak \hyperlink{lum}{lum})
shameful

\textbf{\hypertarget{suotuki}{suotuki}} \textit{v.} (\hyperlink{suotu}{suotu}+\allowbreak \hyperlink{ki}{ki})
shame; ʟєꜱ makes ʟᴏᴧ feel ashamed about ʟᴜᴍ

\textbf{\hypertarget{sul}{sul}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਸੂਰ}⟩ [suɾ])
suid; swine; boar; pig; hog; piglet; pork; Suidae

\textbf{\hypertarget{sulak}{sulak}} \textit{n.} (\hyperlink{sul}{sul}+\allowbreak \hyperlink{ak}{ak})
swine

\textbf{\hypertarget{'suli}{'suli}} \textit{n.} (Ara. ⟨{\arabics{}سوري‎}⟩ [suːriː])
Syria

\textbf{\hypertarget{'suliak}{'suliak}} \textit{n.} (\hyperlink{'suli}{'suli}+\allowbreak \hyperlink{ak}{ak})
Syrian; from Syria

\textbf{\hypertarget{'suliwon}{'suliwon}} \textit{n.} (\hyperlink{'suli}{'suli}+\allowbreak \hyperlink{won}{won})
Syrian; the Syrian people

\textbf{\hypertarget{'sulinama}{'sulinama}} \textit{n.} (Nld. ⟨Suriname⟩ [ˌsyːriˈnaːmə])
Suriname

\textbf{\hypertarget{'sulinamaak}{'sulinamaak}} \textit{n.} (\hyperlink{'sulinama}{'sulinama}+\allowbreak \hyperlink{ak}{ak})
Surinamese; from Suriname

\textbf{\hypertarget{'sulinamawon}{'sulinamawon}} \textit{n.} (\hyperlink{'sulinama}{'sulinama}+\allowbreak \hyperlink{won}{won})
Surinamese; the Surinamese people

\textbf{\hypertarget{'sulu}{'sulu}} \textit{n.} (Zul. ⟨Zulu⟩ [zuːlu])
Zulu; the Zulu people

\textbf{\hypertarget{'suluak}{'suluak}} \textit{n.} (\hyperlink{'sulu}{'sulu}+\allowbreak \hyperlink{ak}{ak})
Zulu; of the Zulu

\textbf{\hypertarget{'sulutilip}{'sulutilip}} \textit{n.} (\hyperlink{'sulu}{'sulu}+\allowbreak \hyperlink{tilip}{tilip})
Zulu; the Zulu language

\textbf{\hypertarget{'sulman}{'sulman}} \textit{n.} (Ara. ⟨{\arabics{}ظلمان}⟩ [zulman])
Alpha Centauri B; Toliman

\textbf{\hypertarget{'sulfulium}{'sulfulium}} \textit{n.} (Lat. ⟨sulphurium⟩ [sʊlfurɪʊ̃])
sulfur; sulphur; brimstone

\textbf{\hypertarget{sun}{sun}} \textit{n.} (Epo. ⟨suno⟩ [ˈsuno])
sun; star; gravitationally-bound mass of burning plasma

\textbf{\hypertarget{sunak}{sunak}} \textit{n.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{ak}{ak})
solar; stellar

\textbf{\hypertarget{'sunnah}{'sunnah}} \textit{n.} (Ara. ⟨{\arabics{}سنة}⟩ [ˈsunnah])
Sunni Islam; Sunniism

\textbf{\hypertarget{'sunnahak}{'sunnahak}} \textit{n.} (\hyperlink{'sunnah}{'sunnah}+\allowbreak \hyperlink{ak}{ak})
Sunni; of Sunni Islam

\textbf{\hypertarget{'sunnahwon}{'sunnahwon}} \textit{n.} (\hyperlink{'sunnah}{'sunnah}+\allowbreak \hyperlink{won}{won})
Sunni; followers of Sunni Islam

\textbf{\hypertarget{sunnunyama}{sunnunyama}} \textit{v.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{nu}{nu}+\allowbreak \hyperlink{nyama}{nyama})
eat supper; eat dinner; sup; dine; \hyperlink{sunnunyamales}{ʟєꜱ} eats \hyperlink{sunnunyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{sunnunyamales}{sunnunyamales}} \textit{n.} (\hyperlink{sunnunyama}{sunnunyama}+\allowbreak \hyperlink{les}{les})
diner; supper

\textbf{\hypertarget{sunnunyamalon}{sunnunyamalon}} \textit{n.} (\hyperlink{sunnunyama}{sunnunyama}+\allowbreak \hyperlink{lon}{lon})
dinner; supper

\textbf{\hypertarget{sunnyama}{sunnyama}} \textit{v.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{nyama}{nyama})
eat lunch; lunch; \hyperlink{sunnyamales}{ʟєꜱ} eats \hyperlink{sunnyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{sunnyamales}{sunnyamales}} \textit{n.} (\hyperlink{sunnyama}{sunnyama}+\allowbreak \hyperlink{les}{les})
luncher

\textbf{\hypertarget{sunnyamalon}{sunnyamalon}} \textit{n.} (\hyperlink{sunnyama}{sunnyama}+\allowbreak \hyperlink{lon}{lon})
lunch

\textbf{\hypertarget{sunnyamalwel}{sunnyamalwel}} \textit{n.} (\hyperlink{sunnyama}{sunnyama}+\allowbreak \hyperlink{lwel}{lwel})
lunchtime

\textbf{\hypertarget{sunfolmo}{sunfolmo}} \textit{v.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{folmo}{folmo})
be stelliform; be star-shaped; \hyperlink{sunfolmolon}{ʟᴏᴧ} is covered in sharp radial points

\textbf{\hypertarget{sunfolmolon}{sunfolmolon}} \textit{n.} (\hyperlink{sunfolmo}{sunfolmo}+\allowbreak \hyperlink{lon}{lon})
star; stelliform; star-shaped

\textbf{\hypertarget{sunkinyama}{sunkinyama}} \textit{v.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{ki}{ki}+\allowbreak \hyperlink{nyama}{nyama})
eat breakfast; breakfast; \hyperlink{sunkinyamales}{ʟєꜱ} eats \hyperlink{sunkinyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{sunkinyamales}{sunkinyamales}} \textit{n.} (\hyperlink{sunkinyama}{sunkinyama}+\allowbreak \hyperlink{les}{les})
fast-breaker

\textbf{\hypertarget{sunkinyamalon}{sunkinyamalon}} \textit{n.} (\hyperlink{sunkinyama}{sunkinyama}+\allowbreak \hyperlink{lon}{lon})
breakfast

\textbf{\hypertarget{sunkinyamalwel}{sunkinyamalwel}} \textit{n.} (\hyperlink{sunkinyama}{sunkinyama}+\allowbreak \hyperlink{lwel}{lwel})
breakfast time

\textbf{\hypertarget{sunkwelwel}{sunkwelwel}} \textit{n.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{kwelwel}{kwelwel})
day; date

\textbf{\hypertarget{sunkwelweltolmicua}{sunkwelweltolmicua}} \textit{v.} (\hyperlink{sunkwelwel}{sunkwelwel}+\allowbreak \hyperlink{tolmicua}{tolmicua})
daydream; hallucinate; \hyperlink{sunkwelweltolmicualon}{ʟᴏᴧ} hallucinates \hyperlink{sunkwelweltolmicualum}{ʟᴜᴍ}

\textbf{\hypertarget{sunkwelweltolmicualum}{sunkwelweltolmicualum}} \textit{n.} (\hyperlink{sunkwelweltolmicua}{sunkwelweltolmicua}+\allowbreak \hyperlink{lum}{lum})
daydream

\textbf{\hypertarget{sunkwelweltolmicualon}{sunkwelweltolmicualon}} \textit{n.} (\hyperlink{sunkwelweltolmicua}{sunkwelweltolmicua}+\allowbreak \hyperlink{lon}{lon})
daydreamer

\textbf{\hypertarget{suntaykunpatolon}{suntaykunpatolon}} \textit{n.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{taykun}{taykun}+\allowbreak \hyperlink{patolon}{patolon})
asteroid

\textbf{\hypertarget{suntun}{suntun}} \textit{n.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{tun}{tun})
seastar; sealily

\textbf{\hypertarget{sunpul}{sunpul}} \textit{n.} (\hyperlink{sun}{sun}+\allowbreak \hyperlink{pul}{pul})
sunflower; Helianthus

\textbf{\hypertarget{sumsum}{sumsum}} \textit{n.} (ono. [zum zum])
bee; Anthophilia

\textbf{\hypertarget{suta}{suta}} \textit{v.} (Epo. ⟨suda⟩ [ˈsuda])
be south; \hyperlink{sutalon}{ʟᴏᴧ} has a lower latitude than ʟᴜᴍ

\textbf{\hypertarget{'suta}{'suta}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਸੁੰਢ}⟩ [suɖə])
ginger; Zingiber

\textbf{\hypertarget{sutaeste}{sutaeste}} \textit{v.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{este}{este})
be southeast; \hyperlink{sutaestelon}{ʟᴏᴧ} is southeast of ʟᴜᴍ

\textbf{\hypertarget{sutaestelon}{sutaestelon}} \textit{n.} (\hyperlink{sutaeste}{sutaeste}+\allowbreak \hyperlink{lon}{lon})
southeast

\textbf{\hypertarget{suta'alon}{suta'alon}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'alon}{'alon})
South Ossetian; Alanian; the South Ossetian people

\textbf{\hypertarget{suta'alonak}{suta'alonak}} \textit{n.} (\hyperlink{suta'alon}{suta'alon}+\allowbreak \hyperlink{ak}{ak})
South Ossetian; of South Ossetia

\textbf{\hypertarget{suta'alontec}{suta'alontec}} \textit{n.} (\hyperlink{suta'alon}{suta'alon}+\allowbreak \hyperlink{tec}{tec})
South Ossetia; Alania

\textbf{\hypertarget{suta'amelika}{suta'amelika}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'amelika}{'amelika})
South America

\textbf{\hypertarget{suta'assutan}{suta'assutan}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'assutan}{'assutan})
South Sudan

\textbf{\hypertarget{suta'assutanak}{suta'assutanak}} \textit{n.} (\hyperlink{suta'assutan}{suta'assutan}+\allowbreak \hyperlink{ak}{ak})
South Sudanese; from South Sudan

\textbf{\hypertarget{suta'assutanwon}{suta'assutanwon}} \textit{n.} (\hyperlink{suta'assutan}{suta'assutan}+\allowbreak \hyperlink{won}{won})
South Sudanese; the South Sudanese people

\textbf{\hypertarget{suta'aflika}{suta'aflika}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'aflika}{'aflika})
Southern Africa

\textbf{\hypertarget{suta'aflikatec}{suta'aflikatec}} \textit{n.} (\hyperlink{suta'aflika}{suta'aflika}+\allowbreak \hyperlink{tec}{tec})
South Africa; the Republic of South Africa

\textbf{\hypertarget{suta'aflikatecwon}{suta'aflikatecwon}} \textit{n.} (\hyperlink{suta'aflikatec}{suta'aflikatec}+\allowbreak \hyperlink{won}{won})
South African; the South African people

\textbf{\hypertarget{sutaoflo}{sutaoflo}} \textit{v.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{oflo}{oflo})
be southwest; \hyperlink{sutaoflolon}{ʟᴏᴧ} is southwest of ʟᴜᴍ

\textbf{\hypertarget{sutaoflolon}{sutaoflolon}} \textit{n.} (\hyperlink{sutaoflo}{sutaoflo}+\allowbreak \hyperlink{lon}{lon})
southwest

\textbf{\hypertarget{sutalawt}{sutalawt}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{lawt}{lawt})
Antarctic Ocean

\textbf{\hypertarget{sutalon}{sutalon}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{lon}{lon})
the South; south

\textbf{\hypertarget{suta'hokyentilip}{suta'hokyentilip}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'hokyentilip}{'hokyentilip})
Southern Min; Minnan; Hokkien-Taiwanese; the Southern Min languages

\textbf{\hypertarget{suta'cosawn}{suta'cosawn}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{'cosawn}{'cosawn})
South Korea; the Democratic Republic of Korea

\textbf{\hypertarget{suta'cosawnak}{suta'cosawnak}} \textit{n.} (\hyperlink{suta'cosawn}{suta'cosawn}+\allowbreak \hyperlink{ak}{ak})
South Korean; from South Korea

\textbf{\hypertarget{suta'cosawnwon}{suta'cosawnwon}} \textit{n.} (\hyperlink{suta'cosawn}{suta'cosawn}+\allowbreak \hyperlink{won}{won})
South Korean; the South Korean people

\textbf{\hypertarget{sutaki}{sutaki}} \textit{v.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{ki}{ki})
go south; ʟєꜱ decreases the latitude of ʟᴏᴧ relative to ʟᴜᴍ

\textbf{\hypertarget{sutatayl}{sutatayl}} \textit{n.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{tayl}{tayl})
Antarctica

\textbf{\hypertarget{sutatyen}{sutatyen}} \textit{num.} (\hyperlink{suta}{suta}+\allowbreak \hyperlink{tyen}{tyen})
south pole

\textbf{\hypertarget{'sutu}{'sutu}} \textit{n.} (Sot. ⟨Sotho⟩ [sʊ́tʰʊ̀])
Basotho; Sotho; the Sotho people

\textbf{\hypertarget{'sutuak}{'sutuak}} \textit{n.} (\hyperlink{'sutu}{'sutu}+\allowbreak \hyperlink{ak}{ak})
Mosotho; from Lesotho

\textbf{\hypertarget{'sututec}{'sututec}} \textit{n.} (\hyperlink{'sutu}{'sutu}+\allowbreak \hyperlink{tec}{tec})
Lesotho

\textbf{\hypertarget{'sututilip}{'sututilip}} \textit{n.} (\hyperlink{'sutu}{'sutu}+\allowbreak \hyperlink{tilip}{tilip})
Sesotho; Sotho; the Sotho language

\textbf{\hypertarget{supot}{supot}} \textit{n.} (\hyperlink{fimel}{\sout{fimel}})
male; man; animal biologically characterised by testicles, penises, and testosterone

\textbf{\hypertarget{supotak}{supotak}} \textit{n.} (\hyperlink{supot}{supot}+\allowbreak \hyperlink{ak}{ak})
male

\textbf{\hypertarget{supotaktua}{supotaktua}} \textit{v.} (\hyperlink{supot}{supot}+\allowbreak \hyperlink{aktua}{aktua})
be masculine; \hyperlink{supotaktualon}{ʟᴏᴧ} is masculine

\textbf{\hypertarget{supotaktualon}{supotaktualon}} \textit{n.} (\hyperlink{supotaktua}{supotaktua}+\allowbreak \hyperlink{lon}{lon})
man; boy; masculine

\textbf{\hypertarget{'swensek}{'swensek}} \textit{n.} (Swe. ⟨svensk⟩ [svɛnːsk])
Swede; the Swedish people

\textbf{\hypertarget{'swensekak}{'swensekak}} \textit{n.} (\hyperlink{'swensek}{'swensek}+\allowbreak \hyperlink{ak}{ak})
Swedish; from Sweden

\textbf{\hypertarget{'swensektec}{'swensektec}} \textit{n.} (\hyperlink{'swensek}{'swensek}+\allowbreak \hyperlink{tec}{tec})
Sweden

\textbf{\hypertarget{'swensektilip}{'swensektilip}} \textit{n.} (\hyperlink{'swensek}{'swensek}+\allowbreak \hyperlink{tilip}{tilip})
Swedish; the Swedish language

\textbf{\hypertarget{swa}{swa}} \textit{v.} (Zul. ⟨-zwa⟩ [zwa])
feel; emote; be emotional; be excited; \hyperlink{swalon}{ʟᴏᴧ} emotionally feels \hyperlink{swalum}{ʟᴜᴍ}

\textbf{\hypertarget{swaec}{swaec}} \textit{n.} (\hyperlink{swa}{swa}+\allowbreak \hyperlink{ec}{ec})
heart (metaphorical); soul; spirit

\textbf{\hypertarget{swalon}{swalon}} \textit{n.} (\hyperlink{swa}{swa}+\allowbreak \hyperlink{lon}{lon})
emotional; excited

\textbf{\hypertarget{swalum}{swalum}} \textit{n.} (\hyperlink{swa}{swa}+\allowbreak \hyperlink{lum}{lum})
emotion; feeling

\textbf{\hypertarget{'swana}{'swana}} \textit{n.} (Tsn. ⟨tswana⟩ [t͡swana])
Batswana; the Tswana people

\textbf{\hypertarget{'swanaak}{'swanaak}} \textit{n.} (\hyperlink{'swana}{'swana}+\allowbreak \hyperlink{ak}{ak})
Botswanan; from Botswana

\textbf{\hypertarget{'swanatec}{'swanatec}} \textit{n.} (\hyperlink{'swana}{'swana}+\allowbreak \hyperlink{tec}{tec})
Botswana

\textbf{\hypertarget{'swanatilip}{'swanatilip}} \textit{n.} (\hyperlink{'swana}{'swana}+\allowbreak \hyperlink{tilip}{tilip})
Setswana; the Tswana language

\textbf{\hypertarget{'swahili}{'swahili}} \textit{n.} (Swa. ⟨swahili⟩ [swahili])
Swahili; the Swahili people

\textbf{\hypertarget{'swahiliak}{'swahiliak}} \textit{n.} (\hyperlink{'swahili}{'swahili}+\allowbreak \hyperlink{ak}{ak})
Swahili; of the Swahili

\textbf{\hypertarget{'swahilitilip}{'swahilitilip}} \textit{n.} (\hyperlink{'swahili}{'swahili}+\allowbreak \hyperlink{tilip}{tilip})
Swahili; the Swahili language

\textbf{\hypertarget{swahulum}{swahulum}} \textit{n.} (\hyperlink{swa}{swa}+\allowbreak \hyperlink{hulum}{hulum})
emoticon; emoji

\textbf{\hypertarget{swakolwa}{swakolwa}} \textit{v.} (\hyperlink{swa}{swa}+\allowbreak \hyperlink{kolwa}{kolwa})
intuit; be intuitive; ʟᴏᴧ intuitively believes \hyperlink{swakolwalum}{ʟᴜᴍ} to be so

\textbf{\hypertarget{swakolwalum}{swakolwalum}} \textit{n.} (\hyperlink{swakolwa}{swakolwa}+\allowbreak \hyperlink{lum}{lum})
intuitive

\textbf{\hypertarget{'swati}{'swati}} \textit{n.} (Ssw. ⟨Swati⟩ [swatˈi])
Swazi; Swati; the Swazi people

\textbf{\hypertarget{'swatiak}{'swatiak}} \textit{n.} (\hyperlink{'swati}{'swati}+\allowbreak \hyperlink{ak}{ak})
Swazi; Swati; from eSwatini

\textbf{\hypertarget{'swatitec}{'swatitec}} \textit{n.} (\hyperlink{'swati}{'swati}+\allowbreak \hyperlink{tec}{tec})
eSwatini; Swaziland

\textbf{\hypertarget{'swatitilip}{'swatitilip}} \textit{n.} (\hyperlink{'swati}{'swati}+\allowbreak \hyperlink{tilip}{tilip})
Swazi; Swati; siSwati; the Swazi language

\textbf{\hypertarget{swape}{swape}} \textit{v.} (Spa. ⟨suave⟩ [ˈswaβe])
be smooth; be polished; be flat; \hyperlink{swapelon}{ʟᴏᴧ} is smooth

\textbf{\hypertarget{swapelon}{swapelon}} \textit{n.} (\hyperlink{swape}{swape}+\allowbreak \hyperlink{lon}{lon})
smooth; polished; flat

\textbf{\hypertarget{swapeki}{swapeki}} \textit{v.} (\hyperlink{swape}{swape}+\allowbreak \hyperlink{ki}{ki})
smoothen; polish; ʟєꜱ smoothens ʟᴏᴧ

\textbf{\hypertarget{swo}{swo}} \textit{v.} (Cmn. ⟨{\chinese{}坐}⟩ [t͡swɔ˥˩])
sit; be sitting; \hyperlink{swolon}{ʟᴏᴧ} is sitting

\textbf{\hypertarget{swolon}{swolon}} \textit{n.} (\hyperlink{swo}{swo}+\allowbreak \hyperlink{lon}{lon})
sitting

\textbf{\hypertarget{swoki}{swoki}} \textit{v.} (\hyperlink{swo}{swo}+\allowbreak \hyperlink{ki}{ki})
sit down; sit up; sit; \hyperlink{swokiles}{ʟєꜱ} sits down ʟᴏᴧ

\textbf{\hypertarget{swokiles}{swokiles}} \textit{n.} (\hyperlink{swoki}{swoki}+\allowbreak \hyperlink{les}{les})
sitter

\textbf{\hypertarget{'swis}{'swis}} \textit{n.} (Roh. ⟨sviz-⟩ [svit͡s])
Swiss; the Swiss people

\textbf{\hypertarget{'swisak}{'swisak}} \textit{n.} (\hyperlink{'swis}{'swis}+\allowbreak \hyperlink{ak}{ak})
Swiss; from Switzerland

\textbf{\hypertarget{'swistec}{'swistec}} \textit{n.} (\hyperlink{'swis}{'swis}+\allowbreak \hyperlink{tec}{tec})
Switzerland

\section{F}

\textbf{\hypertarget{fe}{fe}} \textit{v.} (Cmn. ⟨{\chinese{}飞}⟩ [feɪ̯˥])
fly; soar; \hyperlink{felon}{ʟᴏᴧ} moves through the air, not necessarily of its own accord

\textbf{\hypertarget{'fe}{'fe}} \textit{n.} (ono. [f])
f; /f/; labial fricative

\textbf{\hypertarget{feam}{feam}} \textit{n.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{am}{am})
wing

\textbf{\hypertarget{feammontalon}{feammontalon}} \textit{n.} (\hyperlink{feam}{feam}+\allowbreak \hyperlink{montalon}{montalon})
airplane; jet; plane

\textbf{\hypertarget{'feycuata}{'feycuata}} \textit{n.} (Por. ⟨feijoada⟩ [fejʒuˈadɐ])
feijoada

\textbf{\hypertarget{felon}{felon}} \textit{n.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{lon}{lon})
projectile; bullet

\textbf{\hypertarget{felonak}{felonak}} \textit{n.} (\hyperlink{felon}{felon}+\allowbreak \hyperlink{ak}{ak})
ballistic

\textbf{\hypertarget{fenu}{fenu}} \textit{v.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{nu}{nu})
land; down; ground; take down; alight; ʟєꜱ brings ʟᴏᴧ down from the air

\textbf{\hypertarget{femamul}{femamul}} \textit{n.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{mamul}{mamul})
bat; flying fox

\textbf{\hypertarget{femo}{femo}} \textit{v.} (\hyperlink{sope}{\sout{sope}})
be complex; be complicated; be wicked; \hyperlink{femolon}{ʟᴏᴧ} is complex

\textbf{\hypertarget{femolon}{femolon}} \textit{n.} (\hyperlink{femo}{femo}+\allowbreak \hyperlink{lon}{lon})
complex; complicated; wicked

\textbf{\hypertarget{femoki}{femoki}} \textit{v.} (\hyperlink{femo}{femo}+\allowbreak \hyperlink{ki}{ki})
complicate; \hyperlink{femokiles}{ʟєꜱ} complicates ʟᴏᴧ

\textbf{\hypertarget{femokiles}{femokiles}} \textit{n.} (\hyperlink{femoki}{femoki}+\allowbreak \hyperlink{les}{les})
complicator

\textbf{\hypertarget{fefua}{fefua}} \textit{v.} (\hyperlink{sosia}{\sout{sosia}})
be introverted; be isolated; \hyperlink{fefualon}{ʟᴏᴧ} is socially isolated from ʟᴜᴍ

\textbf{\hypertarget{fefualon}{fefualon}} \textit{n.} (\hyperlink{fefua}{fefua}+\allowbreak \hyperlink{lon}{lon})
introvert; introverted; isolated

\textbf{\hypertarget{fefuaki}{fefuaki}} \textit{v.} (\hyperlink{fefua}{fefua}+\allowbreak \hyperlink{ki}{ki})
isolate; ʟєꜱ socially isolates ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{feki}{feki}} \textit{v.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{ki}{ki})
throw; shoot; take off; jump; launch; \hyperlink{fekiles}{ʟєꜱ} sends ʟᴏᴧ into the air

\textbf{\hypertarget{fekiles}{fekiles}} \textit{n.} (\hyperlink{feki}{feki}+\allowbreak \hyperlink{les}{les})
shooter; launcher

\textbf{\hypertarget{fekiluat}{fekiluat}} \textit{n.} (\hyperlink{feki}{feki}+\allowbreak \hyperlink{luat}{luat})
gun; cannon; launcher

\textbf{\hypertarget{fepucocalu}{fepucocalu}} \textit{v.} (\hyperlink{fe}{fe}+\allowbreak \hyperlink{pucocalu}{pucocalu})
run; ʟᴏᴧ is running on \hyperlink{fepucocalulum}{ʟᴜᴍ}

\textbf{\hypertarget{fepucocalulum}{fepucocalulum}} \textit{n.} (\hyperlink{fepucocalu}{fepucocalu}+\allowbreak \hyperlink{lum}{lum})
treadmill

\textbf{\hypertarget{fawci}{fawci}} \textit{v.} (\hyperlink{sayhu}{\sout{sayhu}})
be unimportant; be indifferent; ignore; \hyperlink{fawcilon}{ʟᴏᴧ} does not care about \hyperlink{fawcilum}{ʟᴜᴍ}

\textbf{\hypertarget{fawcilon}{fawcilon}} \textit{n.} (\hyperlink{fawci}{fawci}+\allowbreak \hyperlink{lon}{lon})
indifferent

\textbf{\hypertarget{fawcilum}{fawcilum}} \textit{n.} (\hyperlink{fawci}{fawci}+\allowbreak \hyperlink{lum}{lum})
fringe; secondary; unimportant

\textbf{\hypertarget{fawciki}{fawciki}} \textit{v.} (\hyperlink{fawci}{fawci}+\allowbreak \hyperlink{ki}{ki})
make unimportant; devalue; ʟєꜱ makes ʟᴏᴧ stop caring about ʟᴜᴍ

\textbf{\hypertarget{fan}{fan}} \textit{n.} (Cmn. ⟨{\chinese{}饭}⟩ [fan˥˩])
rice; Oryza

\textbf{\hypertarget{'fanuatu}{'fanuatu}} \textit{n.} (Bis. ⟨Vanuatu⟩ [vɑnuɑtu])
Vaunatu (archipelago)

\textbf{\hypertarget{'fanuatuak}{'fanuatuak}} \textit{n.} (\hyperlink{'fanuatu}{'fanuatu}+\allowbreak \hyperlink{ak}{ak})
Ni-Vanuatu; Vanuatuan; from Vanuatu

\textbf{\hypertarget{'fanuatuwon}{'fanuatuwon}} \textit{n.} (\hyperlink{'fanuatu}{'fanuatu}+\allowbreak \hyperlink{won}{won})
Ni-Vanuatu; Vanuatuan; the Ni-Vanuatu people

\textbf{\hypertarget{'fanuatutec}{'fanuatutec}} \textit{n.} (\hyperlink{'fanuatu}{'fanuatu}+\allowbreak \hyperlink{tec}{tec})
Vanuatu; the Republic of Vanuatu

\textbf{\hypertarget{'fanuatutilip}{'fanuatutilip}} \textit{n.} (\hyperlink{'fanuatu}{'fanuatu}+\allowbreak \hyperlink{tilip}{tilip})
Bislama; the Bislama language

\textbf{\hypertarget{'fancwey}{'fancwey}} \textit{n.} (Cmn. ⟨{\chinese{}风水}⟩ [fəŋ˥ʂweɪ̯˧˩˥])
feng shui

\textbf{\hypertarget{'fansi}{'fansi}} \textit{n.} (Eng. ⟨fancy⟩ [ˈfænsi])
fancy

\textbf{\hypertarget{'fahan}{'fahan}} \textit{n.} (Fra. ⟨franc⟩ [fʁɑ̃])
franc; ₣

\textbf{\hypertarget{'fahanse}{'fahanse}} \textit{n.} (Fra. ⟨France⟩ [ˈfʁɑ̃s])
France

\textbf{\hypertarget{'fahanseak}{'fahanseak}} \textit{n.} (\hyperlink{'fahanse}{'fahanse}+\allowbreak \hyperlink{ak}{ak})
French; from France

\textbf{\hypertarget{'fahansewon}{'fahansewon}} \textit{n.} (\hyperlink{'fahanse}{'fahanse}+\allowbreak \hyperlink{won}{won})
Frenchman; the French people

\textbf{\hypertarget{'fahansetilip}{'fahansetilip}} \textit{n.} (\hyperlink{'fahanse}{'fahanse}+\allowbreak \hyperlink{tilip}{tilip})
French; the French language

\textbf{\hypertarget{fak}{fak}} \textit{num.} (\hyperlink{san}{\sout{san}})
D; thirteen; baker’s dozen; only used for hexadecimal

\textbf{\hypertarget{fake}{fake}} \textit{v.} (\hyperlink{sano}{\sout{sano}})
be sick; be ill; \hyperlink{fakelon}{ʟᴏᴧ} is sick

\textbf{\hypertarget{fakelon}{fakelon}} \textit{n.} (\hyperlink{fake}{fake}+\allowbreak \hyperlink{lon}{lon})
sick; ill

\textbf{\hypertarget{fakelip}{fakelip}} \textit{n.} (\hyperlink{fake}{fake}+\allowbreak \hyperlink{lip}{lip})
sickness; disease; illness

\textbf{\hypertarget{fakeki}{fakeki}} \textit{v.} (\hyperlink{fake}{fake}+\allowbreak \hyperlink{ki}{ki})
sicken; poison; \hyperlink{fakekiles}{ʟєꜱ} sickens \hyperlink{fakekilon}{ʟᴏᴧ}

\textbf{\hypertarget{fakekiles}{fakekiles}} \textit{n.} (\hyperlink{fakeki}{fakeki}+\allowbreak \hyperlink{les}{les})
poisoner

\textbf{\hypertarget{fakekilon}{fakekilon}} \textit{n.} (\hyperlink{fakeki}{fakeki}+\allowbreak \hyperlink{lon}{lon})
poisoned

\textbf{\hypertarget{fakekiluat}{fakekiluat}} \textit{n.} (\hyperlink{fakeki}{fakeki}+\allowbreak \hyperlink{luat}{luat})
poison

\textbf{\hypertarget{fakekiluatlekcuc}{fakekiluatlekcuc}} \textit{n.} (\hyperlink{fakekiluat}{fakekiluat}+\allowbreak \hyperlink{lekcuc}{lekcuc})
centipede

\textbf{\hypertarget{fakak}{fakak}} \textit{n.} (\hyperlink{fak}{fak}+\allowbreak \hyperlink{ak}{ak})
thirteenth

\textbf{\hypertarget{fol}{fol}} \textit{num.} (Eng. ⟨four⟩ [fɔɹ])
4; four; quadruple

\textbf{\hypertarget{folak}{folak}} \textit{n.} (\hyperlink{fol}{fol}+\allowbreak \hyperlink{ak}{ak})
fourth

\textbf{\hypertarget{folnul}{folnul}} \textit{num.} (\hyperlink{fol}{fol}+\allowbreak \hyperlink{nul}{nul})
40; forty

\textbf{\hypertarget{folnulnul}{folnulnul}} \textit{num.} (\hyperlink{fol}{fol}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
400; four hundred

\textbf{\hypertarget{folmo}{folmo}} \textit{v.} (Epo. ⟨formo⟩ [ˈformo])
be shaped; be shaped like; \hyperlink{folmolon}{ʟᴏᴧ} is shaped like \hyperlink{folmolum}{ʟᴜᴍ}

\textbf{\hypertarget{folmolon}{folmolon}} \textit{n.} (\hyperlink{folmo}{folmo}+\allowbreak \hyperlink{lon}{lon})
sculpture; shaped; shaped like

\textbf{\hypertarget{folmolum}{folmolum}} \textit{n.} (\hyperlink{folmo}{folmo}+\allowbreak \hyperlink{lum}{lum})
shape

\textbf{\hypertarget{folmonu}{folmonu}} \textit{v.} (\hyperlink{folmo}{folmo}+\allowbreak \hyperlink{nu}{nu})
deform; ʟєꜱ makes \hyperlink{folmonulon}{ʟᴏᴧ} lose its shape

\textbf{\hypertarget{folmonulon}{folmonulon}} \textit{n.} (\hyperlink{folmonu}{folmonu}+\allowbreak \hyperlink{lon}{lon})
deformed

\textbf{\hypertarget{folmoki}{folmoki}} \textit{v.} (\hyperlink{folmo}{folmo}+\allowbreak \hyperlink{ki}{ki})
shape; form; sculpt; \hyperlink{folmokiles}{ʟєꜱ} shapes ʟᴏᴧ into ʟᴜᴍ

\textbf{\hypertarget{folmokiles}{folmokiles}} \textit{n.} (\hyperlink{folmoki}{folmoki}+\allowbreak \hyperlink{les}{les})
shaper; sculptor

\textbf{\hypertarget{folsunkwelwel}{folsunkwelwel}} \textit{n.} (\hyperlink{fol}{fol}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Thursday

\textbf{\hypertarget{folti}{folti}} \textit{v.} (Epo. ⟨forti⟩ [ˈforti])
be strong; be forceful; \hyperlink{foltilon}{ʟᴏᴧ} is capable of exerting a lot of force

\textbf{\hypertarget{foltilon}{foltilon}} \textit{n.} (\hyperlink{folti}{folti}+\allowbreak \hyperlink{lon}{lon})
strong; forceful

\textbf{\hypertarget{foltilyan}{foltilyan}} \textit{n.} (\hyperlink{folti}{folti}+\allowbreak \hyperlink{lyan}{lyan})
strength; force

\textbf{\hypertarget{foltimuf}{foltimuf}} \textit{n.} (\hyperlink{folti}{folti}+\allowbreak \hyperlink{muf}{muf})
ox

\textbf{\hypertarget{foltiki}{foltiki}} \textit{v.} (\hyperlink{folti}{folti}+\allowbreak \hyperlink{ki}{ki})
strengthen; exercise; \hyperlink{foltikiles}{ʟєꜱ} strengthens ʟᴏᴧ

\textbf{\hypertarget{foltikiles}{foltikiles}} \textit{n.} (\hyperlink{foltiki}{foltiki}+\allowbreak \hyperlink{les}{les})
strengthener; trainer

\textbf{\hypertarget{foltikwap}{foltikwap}} \textit{n.} (\hyperlink{folti}{folti}+\allowbreak \hyperlink{kwap}{kwap})
mantisshrimp

\textbf{\hypertarget{fomi}{fomi}} \textit{v.} (Eng. ⟨foamy⟩ [ˈfoʊ̯mi])
be foamy; be spongy; be fluffy; \hyperlink{fomilon}{ʟᴏᴧ} is foamy

\textbf{\hypertarget{fomiicilon}{fomiicilon}} \textit{n.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{icilon}{icilon})
sea sponge

\textbf{\hypertarget{fomilon}{fomilon}} \textit{n.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{lon}{lon})
foam; sponge; foamy; spongy; fluffy

\textbf{\hypertarget{fomilono}{fomilono}} \textit{v.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{lono}{lono})
be mottled; be speckled; \hyperlink{fomilonolon}{ʟᴏᴧ} is mottled in colour

\textbf{\hypertarget{fomilonolon}{fomilonolon}} \textit{n.} (\hyperlink{fomilono}{fomilono}+\allowbreak \hyperlink{lon}{lon})
mottled; speckled

\textbf{\hypertarget{fomiciuh}{fomiciuh}} \textit{n.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{ciuh}{ciuh})
cotton

\textbf{\hypertarget{fomiseleal}{fomiseleal}} \textit{n.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{seleal}{seleal})
bread

\textbf{\hypertarget{fomifut}{fomifut}} \textit{n.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{fut}{fut})
eggplant; aubergine; brinjal; Solanum melongena

\textbf{\hypertarget{fomiki}{fomiki}} \textit{v.} (\hyperlink{fomi}{fomi}+\allowbreak \hyperlink{ki}{ki})
foam; froth; rise; air; \hyperlink{fomikiles}{ʟєꜱ} fills ʟᴏᴧ with small pockets

\textbf{\hypertarget{fomikiles}{fomikiles}} \textit{n.} (\hyperlink{fomiki}{fomiki}+\allowbreak \hyperlink{les}{les})
foamer; frother

\textbf{\hypertarget{'fosfolus}{'fosfolus}} \textit{n.} (Lat. ⟨phosphorus⟩ [fosfɔrus])
phosphorus

\textbf{\hypertarget{fotlu}{fotlu}} \textit{v.} (\hyperlink{selti}{\sout{selti}})
be skeptical; be improbable; be unlikely; \hyperlink{fotlulum}{ʟᴜᴍ} is unlikely to happen according to \hyperlink{fotlulon}{ʟᴏᴧ}

\textbf{\hypertarget{fotlulon}{fotlulon}} \textit{n.} (\hyperlink{fotlu}{fotlu}+\allowbreak \hyperlink{lon}{lon})
skeptic; skeptical

\textbf{\hypertarget{fotlulum}{fotlulum}} \textit{n.} (\hyperlink{fotlu}{fotlu}+\allowbreak \hyperlink{lum}{lum})
improbable; unlikely

\textbf{\hypertarget{fotluki}{fotluki}} \textit{v.} (\hyperlink{fotlu}{fotlu}+\allowbreak \hyperlink{ki}{ki})
unconvince; become skeptical; ʟєꜱ provides new information that leads ʟᴜᴍ comes to beI ʟᴏᴧ improbable

\textbf{\hypertarget{fotwe}{fotwe}} \textit{v.} (\hyperlink{selyo}{\sout{selyo}})
be funny; amuse; be silly; be ironic; goof off; \hyperlink{fotwelum}{ʟᴜᴍ} is funny to \hyperlink{fotwelon}{ʟᴏᴧ}

\textbf{\hypertarget{fotwelon}{fotwelon}} \textit{n.} (\hyperlink{fotwe}{fotwe}+\allowbreak \hyperlink{lon}{lon})
goof; ironic

\textbf{\hypertarget{fotwelum}{fotwelum}} \textit{n.} (\hyperlink{fotwe}{fotwe}+\allowbreak \hyperlink{lum}{lum})
amusing; funny; silly

\textbf{\hypertarget{fotweki}{fotweki}} \textit{v.} (\hyperlink{fotwe}{fotwe}+\allowbreak \hyperlink{ki}{ki})
mock; make fun; ʟєꜱ makes ʟᴏᴧ stop taking ʟᴜᴍ seriously

\textbf{\hypertarget{'fi}{'fi}} \textit{n.} (Grc. ⟨φ⟩ [pʰi])
phi; the golden ratio; 1.618…

\textbf{\hypertarget{fieli}{fieli}} \textit{v.} (Epo. ⟨fieri⟩ [fiˈeri])
be proud; \hyperlink{fielilon}{ʟᴏᴧ} feels proud of \hyperlink{fielilum}{ʟᴜᴍ}

\textbf{\hypertarget{fielilon}{fielilon}} \textit{n.} (\hyperlink{fieli}{fieli}+\allowbreak \hyperlink{lon}{lon})
proud

\textbf{\hypertarget{fielilum}{fielilum}} \textit{n.} (\hyperlink{fieli}{fieli}+\allowbreak \hyperlink{lum}{lum})
pride

\textbf{\hypertarget{fieliki}{fieliki}} \textit{v.} (\hyperlink{fieli}{fieli}+\allowbreak \hyperlink{ki}{ki})
make proud; ʟєꜱ makes ʟᴏᴧ feel proud about ʟᴜᴍ

\textbf{\hypertarget{'fiat}{'fiat}} \textit{n.} (Vie. ⟨Việt⟩ [viə̯t˦˨])
Vietnamese; the Vietnamese people

\textbf{\hypertarget{'fiatak}{'fiatak}} \textit{n.} (\hyperlink{'fiat}{'fiat}+\allowbreak \hyperlink{ak}{ak})
Vietnamese; from Vietnam

\textbf{\hypertarget{'fiattec}{'fiattec}} \textit{n.} (\hyperlink{'fiat}{'fiat}+\allowbreak \hyperlink{tec}{tec})
Vietnam

\textbf{\hypertarget{'fiattilip}{'fiattilip}} \textit{n.} (\hyperlink{'fiat}{'fiat}+\allowbreak \hyperlink{tilip}{tilip})
Vietnamese; the Vietnamese people

\textbf{\hypertarget{'fiola}{'fiola}} \textit{n.} (Ita. ⟨viola⟩ [viˈɔːla])
viola

\textbf{\hypertarget{'fiolino}{'fiolino}} \textit{n.} (Ita. ⟨violino⟩ [vioˈlino])
violin

\textbf{\hypertarget{fila}{fila}} \textit{v.} (\hyperlink{suta}{\sout{suta}})
be north; \hyperlink{filalon}{ʟᴏᴧ} has a higher latitude than \hyperlink{filalum}{ʟᴜᴍ}

\textbf{\hypertarget{fila'elyatec}{fila'elyatec}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'elyatec}{'elyatec})
Northern Irish; the Northern Irish people

\textbf{\hypertarget{fila'elyatecak}{fila'elyatecak}} \textit{n.} (\hyperlink{fila'elyatec}{fila'elyatec}+\allowbreak \hyperlink{ak}{ak})
Northern Irish; from Northern Ireland

\textbf{\hypertarget{fila'elyatectec}{fila'elyatectec}} \textit{n.} (\hyperlink{fila'elyatec}{fila'elyatec}+\allowbreak \hyperlink{tec}{tec})
Northern Ireland

\textbf{\hypertarget{filaeste}{filaeste}} \textit{v.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{este}{este})
be northeast; \hyperlink{filaestelon}{ʟᴏᴧ} is northeast of ʟᴜᴍ

\textbf{\hypertarget{filaestelon}{filaestelon}} \textit{n.} (\hyperlink{filaeste}{filaeste}+\allowbreak \hyperlink{lon}{lon})
northeast

\textbf{\hypertarget{fila'amelika}{fila'amelika}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'amelika}{'amelika})
North America

\textbf{\hypertarget{filaoflo}{filaoflo}} \textit{v.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{oflo}{oflo})
be northwest; \hyperlink{filaoflolon}{ʟᴏᴧ} is northwest of ʟᴜᴍ

\textbf{\hypertarget{filaoflolon}{filaoflolon}} \textit{n.} (\hyperlink{filaoflo}{filaoflo}+\allowbreak \hyperlink{lon}{lon})
northwest

\textbf{\hypertarget{filalawt}{filalawt}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{lawt}{lawt})
Arctic Ocean

\textbf{\hypertarget{filalon}{filalon}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{lon}{lon})
the North; north

\textbf{\hypertarget{filalum}{filalum}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{lum}{lum})
standard parallel; usually the equator

\textbf{\hypertarget{filalyan}{filalyan}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{lyan}{lyan})
latitude

\textbf{\hypertarget{filalyanpucolon}{filalyanpucolon}} \textit{n.} (\hyperlink{filalyan}{filalyan}+\allowbreak \hyperlink{pucolon}{pucolon})
parallel

\textbf{\hypertarget{fila'maketon}{fila'maketon}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'maketon}{'maketon})
North Macedonia; the Former Yugoslav Republic of Macedonia

\textbf{\hypertarget{fila'maketonak}{fila'maketonak}} \textit{n.} (\hyperlink{fila'maketon}{fila'maketon}+\allowbreak \hyperlink{ak}{ak})
North Macedonian; from North Macedonia

\textbf{\hypertarget{fila'cosawn}{fila'cosawn}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'cosawn}{'cosawn})
North Korea; the People’s Democratic Republic of Korea

\textbf{\hypertarget{fila'cosawnak}{fila'cosawnak}} \textit{n.} (\hyperlink{fila'cosawn}{fila'cosawn}+\allowbreak \hyperlink{ak}{ak})
North Korean; from North Korea

\textbf{\hypertarget{fila'cosawnwon}{fila'cosawnwon}} \textit{n.} (\hyperlink{fila'cosawn}{fila'cosawn}+\allowbreak \hyperlink{won}{won})
North Korean; the North Korean people

\textbf{\hypertarget{fila'cuntilip}{fila'cuntilip}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'cuntilip}{'cuntilip})
Mandarin; the Mandarin language

\textbf{\hypertarget{'filastin}{'filastin}} \textit{n.} (Ara. ⟨{\arabics{}فلسطين}⟩ [filastˁiːn])
Palestine

\textbf{\hypertarget{'filastinak}{'filastinak}} \textit{n.} (\hyperlink{'filastin}{'filastin}+\allowbreak \hyperlink{ak}{ak})
Palestinian; Palestine; from Palestine

\textbf{\hypertarget{'filastinwon}{'filastinwon}} \textit{n.} (\hyperlink{'filastin}{'filastin}+\allowbreak \hyperlink{won}{won})
Palestinian; the Palestinian people

\textbf{\hypertarget{'filastinkwelyot}{'filastinkwelyot}} \textit{n.} (\hyperlink{'filastin}{'filastin}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Palestine (region)

\textbf{\hypertarget{filaki}{filaki}} \textit{v.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{ki}{ki})
go north; ʟєꜱ increases the latitude of ʟᴏᴧ relative to ʟᴜᴍ

\textbf{\hypertarget{fila'kiplostec}{fila'kiplostec}} \textit{n.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{'kiplostec}{'kiplostec})
Northern Cyprus; Turkish Republic of Northern Cyprus

\textbf{\hypertarget{fila'kiplostecwon}{fila'kiplostecwon}} \textit{n.} (\hyperlink{fila'kiplostec}{fila'kiplostec}+\allowbreak \hyperlink{won}{won})
Northern Cypriot; the Northern Cypriot people

\textbf{\hypertarget{fila'kiplostecak}{fila'kiplostecak}} \textit{n.} (\hyperlink{fila'kiplostec}{fila'kiplostec}+\allowbreak \hyperlink{ak}{ak})
North Cypriot; from Northern Cyprus

\textbf{\hypertarget{filatyen}{filatyen}} \textit{num.} (\hyperlink{fila}{fila}+\allowbreak \hyperlink{tyen}{tyen})
north pole

\textbf{\hypertarget{fimel}{fimel}} \textit{n.} (Eng. ⟨female⟩ [ˈfiːmeɪ̯ɫ])
female; woman; animal biologically characterised by ovaries, vaginas and estrogen

\textbf{\hypertarget{fimelak}{fimelak}} \textit{n.} (\hyperlink{fimel}{fimel}+\allowbreak \hyperlink{ak}{ak})
female

\textbf{\hypertarget{fimelaktua}{fimelaktua}} \textit{v.} (\hyperlink{fimel}{fimel}+\allowbreak \hyperlink{aktua}{aktua})
be feminine; \hyperlink{fimelaktualon}{ʟᴏᴧ} is feminine

\textbf{\hypertarget{fimelaktualon}{fimelaktualon}} \textit{n.} (\hyperlink{fimelaktua}{fimelaktua}+\allowbreak \hyperlink{lon}{lon})
woman; girl; feminine

\textbf{\hypertarget{'fici}{'fici}} \textit{n.} (Fij. ⟨Viti⟩ [ˈβit͡ʃi])
Fiji (archipelago)

\textbf{\hypertarget{'ficiak}{'ficiak}} \textit{n.} (\hyperlink{'fici}{'fici}+\allowbreak \hyperlink{ak}{ak})
Fijian; Fijindian; from Fiji

\textbf{\hypertarget{'ficiwon}{'ficiwon}} \textit{n.} (\hyperlink{'fici}{'fici}+\allowbreak \hyperlink{won}{won})
Fijian; the Fijian people

\textbf{\hypertarget{'ficitec}{'ficitec}} \textit{n.} (\hyperlink{'fici}{'fici}+\allowbreak \hyperlink{tec}{tec})
Fiji; the Republic of Fiji

\textbf{\hypertarget{'ficitilip}{'ficitilip}} \textit{n.} (\hyperlink{'fici}{'fici}+\allowbreak \hyperlink{tilip}{tilip})
Fijian; the Fijian language

\textbf{\hypertarget{fik}{fik}} \textit{n.} (\hyperlink{sun}{\sout{sun}})
moon; satellite; solid object gravitationally orbiting another

\textbf{\hypertarget{fikak}{fikak}} \textit{n.} (\hyperlink{fik}{fik}+\allowbreak \hyperlink{ak}{ak})
lunar

\textbf{\hypertarget{fiknyama}{fiknyama}} \textit{v.} (\hyperlink{fik}{fik}+\allowbreak \hyperlink{nyama}{nyama})
eat dessert; eat midnight snack; \hyperlink{fiknyamales}{ʟєꜱ} eats \hyperlink{fiknyamalon}{ʟᴏᴧ}

\textbf{\hypertarget{fiknyamales}{fiknyamales}} \textit{n.} (\hyperlink{fiknyama}{fiknyama}+\allowbreak \hyperlink{les}{les})
dessert

\textbf{\hypertarget{fiknyamalon}{fiknyamalon}} \textit{n.} (\hyperlink{fiknyama}{fiknyama}+\allowbreak \hyperlink{lon}{lon})
dessert; midnight snack

\textbf{\hypertarget{fikfolmo}{fikfolmo}} \textit{v.} (\hyperlink{fik}{fik}+\allowbreak \hyperlink{folmo}{folmo})
be luniform; be moon-shaped; \hyperlink{fikfolmolon}{ʟᴏᴧ} is long, bent, and pointy on the ends

\textbf{\hypertarget{fikfolmolon}{fikfolmolon}} \textit{n.} (\hyperlink{fikfolmo}{fikfolmo}+\allowbreak \hyperlink{lon}{lon})
crescent; luniform; moon-shaped

\textbf{\hypertarget{fikkwelwel}{fikkwelwel}} \textit{n.} (\hyperlink{fik}{fik}+\allowbreak \hyperlink{kwelwel}{kwelwel})
month

\textbf{\hypertarget{fiti}{fiti}} \textit{v.} (Epo. ⟨fidi⟩ [ˈfidi])
have faith; be faithful; hope; \hyperlink{fitilon}{ʟᴏᴧ} faithfully believes in \hyperlink{fitilum}{ʟᴜᴍ}

\textbf{\hypertarget{fitiici}{fitiici}} \textit{v.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{ici}{ici})
live monastically; \hyperlink{fitiicilon}{ʟᴏᴧ} lives as a monk

\textbf{\hypertarget{fitiicilon}{fitiicilon}} \textit{n.} (\hyperlink{fitiici}{fitiici}+\allowbreak \hyperlink{lon}{lon})
monk; nun; cenobite; hermit; anchorite; hesychast; solitary

\textbf{\hypertarget{fitiicilyot}{fitiicilyot}} \textit{n.} (\hyperlink{fitiici}{fitiici}+\allowbreak \hyperlink{lyot}{lyot})
monastery

\textbf{\hypertarget{fitilon}{fitilon}} \textit{n.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{lon}{lon})
faithful

\textbf{\hypertarget{fitilip}{fitilip}} \textit{n.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{lip}{lip})
religion; faith

\textbf{\hypertarget{fitilippaltolon}{fitilippaltolon}} \textit{n.} (\hyperlink{fitilip}{fitilip}+\allowbreak \hyperlink{paltolon}{paltolon})
sect

\textbf{\hypertarget{fitilippaltolum}{fitilippaltolum}} \textit{n.} (\hyperlink{fitilip}{fitilip}+\allowbreak \hyperlink{paltolum}{paltolum})
church

\textbf{\hypertarget{fitilum}{fitilum}} \textit{n.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{lum}{lum})
faith; belief

\textbf{\hypertarget{fitilyan}{fitilyan}} \textit{n.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{lyan}{lyan})
faith; faithfulness

\textbf{\hypertarget{fitinu}{fitinu}} \textit{v.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{nu}{nu})
lose faith; destroy faith; lose hope; ʟєꜱ causes ʟᴏᴧ to lose faith in ʟᴜᴍ

\textbf{\hypertarget{fiticai}{fiticai}} \textit{v.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{cai}{cai})
be hallowed; worship; \hyperlink{fiticailon}{ʟᴏᴧ} worships ʟᴜᴍ

\textbf{\hypertarget{fiticailon}{fiticailon}} \textit{n.} (\hyperlink{fiticai}{fiticai}+\allowbreak \hyperlink{lon}{lon})
worshiper; hallowed

\textbf{\hypertarget{fitiki}{fitiki}} \textit{v.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{ki}{ki})
give faith; take faith; build up hope; ʟєꜱ causes ʟᴏᴧ to gain faith in ʟᴜᴍ

\textbf{\hypertarget{fititelum}{fititelum}} \textit{n.} (\hyperlink{fiti}{fiti}+\allowbreak \hyperlink{telum}{telum})
holy book; holy text

\textbf{\hypertarget{fulo}{fulo}} \textit{v.} (\hyperlink{site}{\sout{site}})
be wavy; be curly; be bent; be bumpy; \hyperlink{fulolon}{ʟᴏᴧ} is wavy

\textbf{\hypertarget{fulolon}{fulolon}} \textit{n.} (\hyperlink{fulo}{fulo}+\allowbreak \hyperlink{lon}{lon})
squiggle; wave; curl; wavy; curly; bent; bumpy

\textbf{\hypertarget{fuloki}{fuloki}} \textit{v.} (\hyperlink{fulo}{fulo}+\allowbreak \hyperlink{ki}{ki})
bend; flex; curl; kink; \hyperlink{fulokiles}{ʟєꜱ} bends ʟᴏᴧ

\textbf{\hypertarget{fulokiles}{fulokiles}} \textit{n.} (\hyperlink{fuloki}{fuloki}+\allowbreak \hyperlink{les}{les})
bender; curler

\textbf{\hypertarget{fulokipowi}{fulokipowi}} \textit{v.} (\hyperlink{fuloki}{fuloki}+\allowbreak \hyperlink{powi}{powi})
be flexible; be flimsy; be malleable; be soft; \hyperlink{fulokipowilon}{ʟᴏᴧ} bends easily

\textbf{\hypertarget{fulokipowilon}{fulokipowilon}} \textit{n.} (\hyperlink{fulokipowi}{fulokipowi}+\allowbreak \hyperlink{lon}{lon})
flexible; flimsy; malleable; soft

\textbf{\hypertarget{fulokipowinu}{fulokipowinu}} \textit{v.} (\hyperlink{fulokipowi}{fulokipowi}+\allowbreak \hyperlink{nu}{nu})
rigidify; brace; harden; \hyperlink{fulokipowinules}{ʟєꜱ} makes ʟᴏᴧ more rigid

\textbf{\hypertarget{fulokipowinules}{fulokipowinules}} \textit{n.} (\hyperlink{fulokipowinu}{fulokipowinu}+\allowbreak \hyperlink{les}{les})
brace; hardener

\textbf{\hypertarget{fulokipowinyo}{fulokipowinyo}} \textit{v.} (\hyperlink{fulokipowi}{fulokipowi}+\allowbreak \hyperlink{nyo}{nyo})
be unbending; be rigid; be brittle; be firm; \hyperlink{fulokipowinyolon}{ʟᴏᴧ} does not bend

\textbf{\hypertarget{fulokipowinyolon}{fulokipowinyolon}} \textit{n.} (\hyperlink{fulokipowinyo}{fulokipowinyo}+\allowbreak \hyperlink{lon}{lon})
rigid body; unbending; rigid; brittle; firm

\textbf{\hypertarget{fulokipowiki}{fulokipowiki}} \textit{v.} (\hyperlink{fulokipowi}{fulokipowi}+\allowbreak \hyperlink{ki}{ki})
flimsen; weaken; ʟєꜱ makes ʟᴏᴧ more flimsy

\textbf{\hypertarget{fulopucolon}{fulopucolon}} \textit{n.} (\hyperlink{fulo}{fulo}+\allowbreak \hyperlink{pucolon}{pucolon})
tilde

\textbf{\hypertarget{'fuluolum}{'fuluolum}} \textit{n.} (Lat. ⟨fluorum⟩ [flʊorʊ̃])
fluorine

\textbf{\hypertarget{funta}{funta}} \textit{v.} (\hyperlink{sikla}{\sout{sikla}})
be square; be rectangular; be right; \hyperlink{funtalon}{ʟᴏᴧ} is rectangular

\textbf{\hypertarget{funtalet}{funtalet}} \textit{n.} (\hyperlink{funta}{funta}+\allowbreak \hyperlink{let}{let})
grid; hatch

\textbf{\hypertarget{funtalon}{funtalon}} \textit{n.} (\hyperlink{funta}{funta}+\allowbreak \hyperlink{lon}{lon})
rectangle; square; rectangular; right

\textbf{\hypertarget{funtanu}{funtanu}} \textit{v.} (\hyperlink{funta}{funta}+\allowbreak \hyperlink{nu}{nu})
skew; make diagonal; ʟєꜱ makes ʟᴏᴧ stop being rectangular

\textbf{\hypertarget{funtanyopucolon}{funtanyopucolon}} \textit{n.} (\hyperlink{funta}{funta}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{pucolon}{pucolon})
slash

\textbf{\hypertarget{funtaki}{funtaki}} \textit{v.} (\hyperlink{funta}{funta}+\allowbreak \hyperlink{ki}{ki})
square; rectify; right; ʟєꜱ makes ʟᴏᴧ rectangular

\textbf{\hypertarget{fuha}{fuha}} \textit{v.} (\hyperlink{sica}{\sout{sica}})
be loud; be bright; be strong; \hyperlink{fuhalon}{ʟᴏᴧ} is bright

\textbf{\hypertarget{fuhalon}{fuhalon}} \textit{n.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{lon}{lon})
loud; bright; strong

\textbf{\hypertarget{fuhalyan}{fuhalyan}} \textit{n.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{lyan}{lyan})
volume; amplitude; brightness

\textbf{\hypertarget{fuhalwel}{fuhalwel}} \textit{n.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{lwel}{lwel})
daytime; day

\textbf{\hypertarget{fuhaki}{fuhaki}} \textit{v.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{ki}{ki})
amplify; louden; brighten; strengthen; crescendo; \hyperlink{fuhakiles}{ʟєꜱ} amplifies ʟᴏᴧ

\textbf{\hypertarget{fuhakiles}{fuhakiles}} \textit{n.} (\hyperlink{fuhaki}{fuhaki}+\allowbreak \hyperlink{les}{les})
amplifier

\textbf{\hypertarget{fuhakilwel}{fuhakilwel}} \textit{n.} (\hyperlink{fuhaki}{fuhaki}+\allowbreak \hyperlink{lwel}{lwel})
morning; dawn

\textbf{\hypertarget{fuhapola}{fuhapola}} \textit{v.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{pola}{pola})
shout; yell; scream; raise voice; ʟєꜱ shouts ʟᴜᴍ to ʟᴏᴧ

\textbf{\hypertarget{fuhapum}{fuhapum}} \textit{n.} (\hyperlink{fuha}{fuha}+\allowbreak \hyperlink{pum}{pum})
Venus

\textbf{\hypertarget{fuhapumak}{fuhapumak}} \textit{n.} (\hyperlink{fuhapum}{fuhapum}+\allowbreak \hyperlink{ak}{ak})
Venusian

\textbf{\hypertarget{fut}{fut}} \textit{n.} (Eng. ⟨fruit⟩ [fɹʷuːt])
fruit; seed-bearing structure of a flowering plant

\textbf{\hypertarget{futak}{futak}} \textit{n.} (\hyperlink{fut}{fut}+\allowbreak \hyperlink{ak}{ak})
pomonal; fruity

\textbf{\hypertarget{futlep}{futlep}} \textit{n.} (\hyperlink{fut}{fut}+\allowbreak \hyperlink{lep}{lep})
grape

\textbf{\hypertarget{'futpal}{'futpal}} \textit{n.} (Eng. ⟨football⟩ [fʊtbɑl])
American football

\textbf{\hypertarget{'futpol}{'futpol}} \textit{n.} (Eng. ⟨football⟩ [ˈfʊʔbɔːl])
football; soccer

\textbf{\hypertarget{fyamo}{fyamo}} \textit{v.} (\hyperlink{swape}{\sout{swape}})
be rough; be abrasive; be sharp; \hyperlink{fyamolon}{ʟᴏᴧ} is rough

\textbf{\hypertarget{fyamolon}{fyamolon}} \textit{n.} (\hyperlink{fyamo}{fyamo}+\allowbreak \hyperlink{lon}{lon})
rough; abrasive; sharp

\textbf{\hypertarget{fyamohwok}{fyamohwok}} \textit{n.} (\hyperlink{fyamo}{fyamo}+\allowbreak \hyperlink{hwok}{hwok})
sandpaper

\textbf{\hypertarget{fyamoki}{fyamoki}} \textit{v.} (\hyperlink{fyamo}{fyamo}+\allowbreak \hyperlink{ki}{ki})
roughen; rough up; scratch; ʟєꜱ roughens ʟᴏᴧ

\textbf{\hypertarget{'fyoloncelo}{'fyoloncelo}} \textit{n.} (Ita. ⟨violoncello⟩ [vjolonˈt͡ʃɛllo])
cello; vioncello

\textbf{\hypertarget{fwes}{fwes}} \textit{n.} (Eng. ⟨phrase⟩ [fɹʷeɪ̯z])
phrase; sentence; meaningful string of words

\textbf{\hypertarget{fwesak}{fwesak}} \textit{n.} (\hyperlink{fwes}{fwes}+\allowbreak \hyperlink{ak}{ak})
phrasal; sentential

\textbf{\hypertarget{fwi}{fwi}} \textit{v.} (ono. [fwiː])
screech; wail; whistle; ʟєꜱ makes \hyperlink{fwilon}{ʟᴏᴧ}

\textbf{\hypertarget{fwilon}{fwilon}} \textit{n.} (\hyperlink{fwi}{fwi}+\allowbreak \hyperlink{lon}{lon})
screech; wail; whistle; drawn-out, high-pitched sound or action

\section{K}

\textbf{\hypertarget{ke}{ke}} \textit{ptcl.} (Spa. ⟨que⟩ [ke])
would; \textit{subjunctive mood}

\textbf{\hypertarget{'keal}{'keal}} \textit{n.} (Gla. ⟨Gàidheal⟩ [ˈkɛːəɫ])
Gael; the Gaelic people

\textbf{\hypertarget{'kealak}{'kealak}} \textit{n.} (\hyperlink{'keal}{'keal}+\allowbreak \hyperlink{ak}{ak})
Gaelic; of the Gaels

\textbf{\hypertarget{'kealtilip}{'kealtilip}} \textit{n.} (\hyperlink{'keal}{'keal}+\allowbreak \hyperlink{tilip}{tilip})
Goidelic; Gaelic; a Goidelic language

\textbf{\hypertarget{kela}{kela}} \textit{v.} (\hyperlink{nota}{\sout{nota}})
be oblivious; be unaware; \hyperlink{kelalon}{ʟᴏᴧ} fails to notice the presence of \hyperlink{kelalum}{ʟᴜᴍ}

\textbf{\hypertarget{kelalon}{kelalon}} \textit{n.} (\hyperlink{kela}{kela}+\allowbreak \hyperlink{lon}{lon})
oblivious; unaware

\textbf{\hypertarget{kelalum}{kelalum}} \textit{n.} (\hyperlink{kela}{kela}+\allowbreak \hyperlink{lum}{lum})
inconspicuous; stealthy

\textbf{\hypertarget{kelaki}{kelaki}} \textit{v.} (\hyperlink{kela}{kela}+\allowbreak \hyperlink{ki}{ki})
hide; obscure; \hyperlink{kelakiles}{ʟєꜱ} hides ʟᴜᴍ from ʟᴏᴧ

\textbf{\hypertarget{kelakiles}{kelakiles}} \textit{n.} (\hyperlink{kelaki}{kelaki}+\allowbreak \hyperlink{les}{les})
hider; obscurer

\textbf{\hypertarget{'kenya}{'kenya}} \textit{n.} (Swa. ⟨Kenya⟩ [kɛɲɑ])
Mount Kenya

\textbf{\hypertarget{'kenyaak}{'kenyaak}} \textit{n.} (\hyperlink{'kenya}{'kenya}+\allowbreak \hyperlink{ak}{ak})
Kenyan; from Kenya

\textbf{\hypertarget{'kenyawon}{'kenyawon}} \textit{n.} (\hyperlink{'kenya}{'kenya}+\allowbreak \hyperlink{won}{won})
Kenyan; the Kenyan people

\textbf{\hypertarget{'kenyatec}{'kenyatec}} \textit{n.} (\hyperlink{'kenya}{'kenya}+\allowbreak \hyperlink{tec}{tec})
Kenya; the Republic of Kenya

\textbf{\hypertarget{'kento}{'kento}} \textit{n.} (Jpn. ⟨{\japanese{}剣道}⟩ [kɛndoː])
Kendo

\textbf{\hypertarget{kehe}{kehe}} \textit{v.} (ono. [kʰ])
pop; clap; slap; tick; spark; ʟєꜱ makes \hyperlink{kehelon}{ʟᴏᴧ}

\textbf{\hypertarget{kehelon}{kehelon}} \textit{n.} (\hyperlink{kehe}{kehe}+\allowbreak \hyperlink{lon}{lon})
clap; slap; tick; spark; flash; sudden, high-pitched sound or action

\textbf{\hypertarget{kehemais}{kehemais}} \textit{n.} (\hyperlink{kehe}{kehe}+\allowbreak \hyperlink{mais}{mais})
popcorn

\textbf{\hypertarget{kes}{kes}} \textit{n.} (Mar. ⟨{\devanagari{}केस}⟩ [kes])
hair; fur; organically extruded strings

\textbf{\hypertarget{kesak}{kesak}} \textit{n.} (\hyperlink{kes}{kes}+\allowbreak \hyperlink{ak}{ak})
pilar; hairy

\textbf{\hypertarget{kesmyawf}{kesmyawf}} \textit{n.} (\hyperlink{kes}{kes}+\allowbreak \hyperlink{myawf}{myawf})
lion

\textbf{\hypertarget{kescuc}{kescuc}} \textit{n.} (\hyperlink{kes}{kes}+\allowbreak \hyperlink{cuc}{cuc})
louse

\textbf{\hypertarget{keskap}{keskap}} \textit{n.} (\hyperlink{kes}{kes}+\allowbreak \hyperlink{kap}{kap})
catfish

\textbf{\hypertarget{kespoltilum}{kespoltilum}} \textit{n.} (\hyperlink{kes}{kes}+\allowbreak \hyperlink{poltilum}{poltilum})
hat

\textbf{\hypertarget{'ketal}{'ketal}} \textit{n.} (Ara. ⟨{\arabics{}قطر‎}⟩ [ˈɡɪtˤɑr])
Qatar

\textbf{\hypertarget{'ketalak}{'ketalak}} \textit{n.} (\hyperlink{'ketal}{'ketal}+\allowbreak \hyperlink{ak}{ak})
Qatari; from Qatar

\textbf{\hypertarget{'ketalwon}{'ketalwon}} \textit{n.} (\hyperlink{'ketal}{'ketal}+\allowbreak \hyperlink{won}{won})
Qatari; the Qatari people

\textbf{\hypertarget{kae}{kae}} \textit{v.} (Spa. ⟨cae⟩ [ˈkae])
fall; be falling; \hyperlink{kaelon}{ʟᴏᴧ} moves uncontrollably under gravitational forces

\textbf{\hypertarget{kaelon}{kaelon}} \textit{n.} (\hyperlink{kae}{kae}+\allowbreak \hyperlink{lon}{lon})
falling

\textbf{\hypertarget{kaelial}{kaelial}} \textit{n.} (\hyperlink{kae}{kae}+\allowbreak \hyperlink{lial}{lial})
gravity

\textbf{\hypertarget{kaenu}{kaenu}} \textit{v.} (\hyperlink{kae}{kae}+\allowbreak \hyperlink{nu}{nu})
catch; fall on; land; collapse; stop; \hyperlink{kaenules}{ʟєꜱ} makes \hyperlink{kaenulon}{ʟᴏᴧ} stop falling

\textbf{\hypertarget{kaenules}{kaenules}} \textit{n.} (\hyperlink{kaenu}{kaenu}+\allowbreak \hyperlink{les}{les})
catcher; landing

\textbf{\hypertarget{kaenulon}{kaenulon}} \textit{n.} (\hyperlink{kaenu}{kaenu}+\allowbreak \hyperlink{lon}{lon})
caught

\textbf{\hypertarget{kaeki}{kaeki}} \textit{v.} (\hyperlink{kae}{kae}+\allowbreak \hyperlink{ki}{ki})
drop; fall; \hyperlink{kaekiles}{ʟєꜱ} makes \hyperlink{kaekilon}{ʟᴏᴧ} start falling

\textbf{\hypertarget{kaekiles}{kaekiles}} \textit{n.} (\hyperlink{kaeki}{kaeki}+\allowbreak \hyperlink{les}{les})
dropper

\textbf{\hypertarget{kaekilon}{kaekilon}} \textit{n.} (\hyperlink{kaeki}{kaeki}+\allowbreak \hyperlink{lon}{lon})
dropped; fallen

\textbf{\hypertarget{kaepowi}{kaepowi}} \textit{v.} (\hyperlink{kae}{kae}+\allowbreak \hyperlink{powi}{powi})
be precarious; \hyperlink{kaepowilon}{ʟᴏᴧ} is precariously placed

\textbf{\hypertarget{kaepowilon}{kaepowilon}} \textit{n.} (\hyperlink{kaepowi}{kaepowi}+\allowbreak \hyperlink{lon}{lon})
precarious

\textbf{\hypertarget{'kao}{'kao}} \textit{n.} (Cmn. ⟨{\chinese{}刻}⟩ [kʰɤ˨˩])
ke (unit)

\textbf{\hypertarget{'kayana}{'kayana}} \textit{n.} (Eng. ⟨Guyana⟩ [ɡaɪ̯ˈɑːnə])
Guyana

\textbf{\hypertarget{'kayanaak}{'kayanaak}} \textit{n.} (\hyperlink{'kayana}{'kayana}+\allowbreak \hyperlink{ak}{ak})
Guyanese; from Guyana

\textbf{\hypertarget{'kayanawon}{'kayanawon}} \textit{n.} (\hyperlink{'kayana}{'kayana}+\allowbreak \hyperlink{won}{won})
Guyanaese; the Guyanese people

\textbf{\hypertarget{kala}{kala}} \textit{v.} (Ben. ⟨{\bengali{}খাড়া}⟩ [kʰaɽa])
be steep; \hyperlink{kalalon}{ʟᴏᴧ} is steep

\textbf{\hypertarget{kalalon}{kalalon}} \textit{n.} (\hyperlink{kala}{kala}+\allowbreak \hyperlink{lon}{lon})
steep

\textbf{\hypertarget{kalalyan}{kalalyan}} \textit{n.} (\hyperlink{kala}{kala}+\allowbreak \hyperlink{lyan}{lyan})
slope

\textbf{\hypertarget{'kalaci}{'kalaci}} \textit{n.} (Urd. ⟨{\arabics{}کراچی‎}⟩ [kəˈɾaːt͡ʃi])
Karachi

\textbf{\hypertarget{'kalaclit}{'kalaclit}} \textit{n.} (Kal. ⟨Kalaallit⟩ [kalaːɬit])
Greenlander; the Greenlandic people

\textbf{\hypertarget{'kalaclitak}{'kalaclitak}} \textit{n.} (\hyperlink{'kalaclit}{'kalaclit}+\allowbreak \hyperlink{ak}{ak})
Greenlandic; from Greenland

\textbf{\hypertarget{'kalaclittec}{'kalaclittec}} \textit{n.} (\hyperlink{'kalaclit}{'kalaclit}+\allowbreak \hyperlink{tec}{tec})
Greenland

\textbf{\hypertarget{'kalaclittilip}{'kalaclittilip}} \textit{n.} (\hyperlink{'kalaclit}{'kalaclit}+\allowbreak \hyperlink{tilip}{tilip})
Greenlandic; the Greenlandic language

\textbf{\hypertarget{'kalasias}{'kalasias}} \textit{n.} (Gre. ⟨γαλαξίας⟩ [ɡalaksíaːs])
galaxy

\textbf{\hypertarget{kalaki}{kalaki}} \textit{v.} (\hyperlink{kala}{kala}+\allowbreak \hyperlink{ki}{ki})
steepen; tilt; rock; ʟєꜱ steepens ʟᴏᴧ

\textbf{\hypertarget{'kalate}{'kalate}} \textit{n.} (Jpn. ⟨{\japanese{}空手}⟩ [kaɾate])
Karate

\textbf{\hypertarget{'kalinako}{'kalinako}} \textit{n.} (Crb. ⟨Kalinago⟩ [kalinaɡo])
Island Carib; the Carib people; the Kalinago people

\textbf{\hypertarget{'kalinakoak}{'kalinakoak}} \textit{n.} (\hyperlink{'kalinako}{'kalinako}+\allowbreak \hyperlink{ak}{ak})
Island Carib; Carib

\textbf{\hypertarget{'kalinakolawt}{'kalinakolawt}} \textit{n.} (\hyperlink{'kalinako}{'kalinako}+\allowbreak \hyperlink{lawt}{lawt})
Caribbean Sea

\textbf{\hypertarget{'kalinakotilip}{'kalinakotilip}} \textit{n.} (\hyperlink{'kalinako}{'kalinako}+\allowbreak \hyperlink{tilip}{tilip})
Island Carib; Igneri

\textbf{\hypertarget{kalita}{kalita}} \textit{v.} (\hyperlink{natula}{\sout{natula}})
be artificial; be unnatural; \hyperlink{kalitalon}{ʟᴏᴧ} is artificial

\textbf{\hypertarget{kalitalon}{kalitalon}} \textit{n.} (\hyperlink{kalita}{kalita}+\allowbreak \hyperlink{lon}{lon})
artificial; unnatural

\textbf{\hypertarget{kalitaki}{kalitaki}} \textit{v.} (\hyperlink{kalita}{kalita}+\allowbreak \hyperlink{ki}{ki})
process; artificialise; ʟєꜱ makes ʟᴏᴧ become artificial

\textbf{\hypertarget{'kallium}{'kallium}} \textit{n.} (Lat. ⟨gallium⟩ [ɡallɪʊ̃])
gallium

\textbf{\hypertarget{'kalcium}{'kalcium}} \textit{n.} (Lat. ⟨calcium⟩ [kalt͡ʃɪʊ̃])
calcium

\textbf{\hypertarget{'kalsone}{'kalsone}} \textit{n.} (Ita. ⟨calzone⟩ [kalˈt͡soːne])
calzone

\textbf{\hypertarget{'kaltwel}{'kaltwel}} \textit{n.} (Kat. ⟨{\georgian{}ქართველ-}⟩ [kʰɑrtʰvɛl])
Georgian; the Georgian people

\textbf{\hypertarget{'kaltwelak}{'kaltwelak}} \textit{n.} (\hyperlink{'kaltwel}{'kaltwel}+\allowbreak \hyperlink{ak}{ak})
Georgian; from Georgia

\textbf{\hypertarget{'kaltwelkwelyot}{'kaltwelkwelyot}} \textit{n.} (\hyperlink{'kaltwel}{'kaltwel}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Kartli

\textbf{\hypertarget{'kaltweltec}{'kaltweltec}} \textit{n.} (\hyperlink{'kaltwel}{'kaltwel}+\allowbreak \hyperlink{tec}{tec})
Georgia

\textbf{\hypertarget{'kaltweltilip}{'kaltweltilip}} \textit{n.} (\hyperlink{'kaltwel}{'kaltwel}+\allowbreak \hyperlink{tilip}{tilip})
Georgian; the Georgian langauge

\textbf{\hypertarget{'kawai}{'kawai}} \textit{n.} (Jpn. ⟨{\japanese{}かわいい}⟩ [kaɰaiː])
kawaii

\textbf{\hypertarget{'kawtay}{'kawtay}} \textit{n.} (Vie. ⟨Cao Đài⟩ [kaːw˧ ɗaːj˦˨])
Cao Đài; Cao Đài Tiên Ông Đại Bồ Tát Ma Ha Tát

\textbf{\hypertarget{'kawtayfitilip}{'kawtayfitilip}} \textit{n.} (\hyperlink{'kawtay}{'kawtay}+\allowbreak \hyperlink{fitilip}{fitilip})
Caodaism; Đại Đạo Tam Kỳ Phổ Độ; the Cao Đài religion

\textbf{\hypertarget{'kawtayfitilipwon}{'kawtayfitilipwon}} \textit{n.} (\hyperlink{'kawtayfitilip}{'kawtayfitilip}+\allowbreak \hyperlink{won}{won})
Caodaist; followers of Caodaism

\textbf{\hypertarget{'kawtayfitilipak}{'kawtayfitilipak}} \textit{n.} (\hyperlink{'kawtayfitilip}{'kawtayfitilip}+\allowbreak \hyperlink{ak}{ak})
Caodaist; of Caodaism

\textbf{\hypertarget{kan}{kan}} \textit{num.} (Yor. ⟨okan⟩ [okan])
1; one; single; individual

\textbf{\hypertarget{kana}{kana}} \textit{v.} (Spa. ⟨gana⟩ [ˈɡana])
win; beat; lose; \hyperlink{kanales}{ʟєꜱ} wins \hyperlink{kanalon}{ʟᴏᴧ} against \hyperlink{kanalum}{ʟᴜᴍ}

\textbf{\hypertarget{'kana}{'kana}} \textit{n.} (Eng. ⟨Ghana⟩ [ˈɡɑːnə])
Ghana

\textbf{\hypertarget{'kanaak}{'kanaak}} \textit{n.} (\hyperlink{'kana}{'kana}+\allowbreak \hyperlink{ak}{ak})
Ghanian; from Ghana

\textbf{\hypertarget{kanales}{kanales}} \textit{n.} (\hyperlink{kana}{kana}+\allowbreak \hyperlink{les}{les})
winner; victor

\textbf{\hypertarget{kanalon}{kanalon}} \textit{n.} (\hyperlink{kana}{kana}+\allowbreak \hyperlink{lon}{lon})
contest; game

\textbf{\hypertarget{kanalum}{kanalum}} \textit{n.} (\hyperlink{kana}{kana}+\allowbreak \hyperlink{lum}{lum})
loser; defeated

\textbf{\hypertarget{'kanawon}{'kanawon}} \textit{n.} (\hyperlink{'kana}{'kana}+\allowbreak \hyperlink{won}{won})
Ghanian; the Ghanian people

\textbf{\hypertarget{kanak}{kanak}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{ak}{ak})
first; single; unit

\textbf{\hypertarget{'kanata}{'kanata}} \textit{n.} (Eng. ⟨Canada⟩ [ˈkænədə])
Canada

\textbf{\hypertarget{'kanataak}{'kanataak}} \textit{n.} (\hyperlink{'kanata}{'kanata}+\allowbreak \hyperlink{ak}{ak})
Canadian; from Canada

\textbf{\hypertarget{'kanatawon}{'kanatawon}} \textit{n.} (\hyperlink{'kanata}{'kanata}+\allowbreak \hyperlink{won}{won})
Canadaian; the Canadian people

\textbf{\hypertarget{kanol}{kanol}} \textit{n.} (Hin. ⟨{\devanagari{}कैनोला}⟩ [kæːnolaː])
rapeseed; rape; canola; Brassica

\textbf{\hypertarget{kanosolon}{kanosolon}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{osolon}{osolon})
multiple; plural

\textbf{\hypertarget{kanlim}{kanlim}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{lim}{lim})
15; fifteen

\textbf{\hypertarget{kanlimnokipumkwelwel}{kanlimnokipumkwelwel}} \textit{n.} (\hyperlink{kanlim}{kanlim}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
junior year of college

\textbf{\hypertarget{kanwale}{kanwale}} \textit{v.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{wale}{wale})
be unique; be special; \hyperlink{kanwalelon}{ʟᴏᴧ} is unique among ʟᴜᴍ

\textbf{\hypertarget{kanwalelon}{kanwalelon}} \textit{n.} (\hyperlink{kanwale}{kanwale}+\allowbreak \hyperlink{lon}{lon})
unique; special

\textbf{\hypertarget{kannokipumkwelwel}{kannokipumkwelwel}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
first grade

\textbf{\hypertarget{kannu}{kannu}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{nu}{nu})
divide; split up; separate; dissolve; ʟєꜱ divides ʟᴏᴧ into multiple parts

\textbf{\hypertarget{kannul}{kannul}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{nul}{nul})
10; ten

\textbf{\hypertarget{kannulnokipumkwelwel}{kannulnokipumkwelwel}} \textit{n.} (\hyperlink{kannul}{kannul}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
sophomore year of high school

\textbf{\hypertarget{kannulnul}{kannulnul}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
100; one hundred; hundred; hecto

\textbf{\hypertarget{kannulcyenlektun}{kannulcyenlektun}} \textit{n.} (\hyperlink{kannul}{kannul}+\allowbreak \hyperlink{cyenlektun}{cyenlektun})
decapus; squid; cuttlefish

\textbf{\hypertarget{kanmes}{kanmes}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{mes}{mes})
19; nineteen

\textbf{\hypertarget{kanhat}{kanhat}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{hat}{hat})
18; eighteen

\textbf{\hypertarget{kancah}{kancah}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{cah}{cah})
16; sixteen

\textbf{\hypertarget{kancahnokipumkwelwel}{kancahnokipumkwelwel}} \textit{n.} (\hyperlink{kancah}{kancah}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
senior year of college

\textbf{\hypertarget{kanci}{kanci}} \textit{v.} (Cmn. ⟨{\chinese{}感激}⟩ [kan˧˩˧t͡ɕi˥])
be grateful; be thankful; \hyperlink{kancilon}{ʟᴏᴧ} feels grateful to ʟєꜱ

\textbf{\hypertarget{kancilon}{kancilon}} \textit{n.} (\hyperlink{kanci}{kanci}+\allowbreak \hyperlink{lon}{lon})
grateful; thankful

\textbf{\hypertarget{kansan}{kansan}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{san}{san})
13; thirteen

\textbf{\hypertarget{kansannokipumkwelwel}{kansannokipumkwelwel}} \textit{n.} (\hyperlink{kansan}{kansan}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
freshman year of college

\textbf{\hypertarget{kansunkwelwel}{kansunkwelwel}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Monday

\textbf{\hypertarget{kanswa}{kanswa}} \textit{v.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{swa}{swa})
feel lonely; feel alone; ʟᴏᴧ feels alone

\textbf{\hypertarget{kanfol}{kanfol}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{fol}{fol})
14; fourteen

\textbf{\hypertarget{kanfolnokipumkwelwel}{kanfolnokipumkwelwel}} \textit{n.} (\hyperlink{kanfol}{kanfol}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
sophomore year of college

\textbf{\hypertarget{kankan}{kankan}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{kan}{kan})
11; eleven

\textbf{\hypertarget{kankannokipumkwelwel}{kankannokipumkwelwel}} \textit{n.} (\hyperlink{kankan}{kankan}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
junior year of high school

\textbf{\hypertarget{kankatalum}{kankatalum}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{katalum}{katalum})
canon

\textbf{\hypertarget{kankot}{kankot}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{kot}{kot})
monothiesm

\textbf{\hypertarget{kanki}{kanki}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{ki}{ki})
unify; combine; join; ʟєꜱ makes ʟᴏᴧ into one

\textbf{\hypertarget{kankwelwel}{kankwelwel}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{kwelwel}{kwelwel})
minute

\textbf{\hypertarget{'kankwes}{'kankwes}} \textit{n.} (Eng. ⟨congress⟩ [ˈkʰɑŋɡɹʷɨs])
Congress

\textbf{\hypertarget{'kanta}{'kanta}} \textit{n.} (Lug. ⟨-ganda⟩ [ɡâːndá])
Ganda; Muganda; the Ganda people

\textbf{\hypertarget{'kantaak}{'kantaak}} \textit{n.} (\hyperlink{'kanta}{'kanta}+\allowbreak \hyperlink{ak}{ak})
Ganda; from Buganda

\textbf{\hypertarget{'kantatec}{'kantatec}} \textit{n.} (\hyperlink{'kanta}{'kanta}+\allowbreak \hyperlink{tec}{tec})
Buganda

\textbf{\hypertarget{'kantatilip}{'kantatilip}} \textit{n.} (\hyperlink{'kanta}{'kanta}+\allowbreak \hyperlink{tilip}{tilip})
Ganda; Luganda; the Ganda language

\textbf{\hypertarget{kantos}{kantos}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{tos}{tos})
12; twelve

\textbf{\hypertarget{kantosnokipumkwelwel}{kantosnokipumkwelwel}} \textit{n.} (\hyperlink{kantos}{kantos}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
senior year of high school

\textbf{\hypertarget{kantunci}{kantunci}} \textit{v.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{tunci}{tunci})
rule as a monarch; \hyperlink{kantuncilum}{ʟᴜᴍ} rules \hyperlink{kantuncilon}{ʟᴏᴧ}

\textbf{\hypertarget{kantuncilon}{kantuncilon}} \textit{n.} (\hyperlink{kantunci}{kantunci}+\allowbreak \hyperlink{lon}{lon})
peasant; kingdom

\textbf{\hypertarget{kantuncilum}{kantuncilum}} \textit{n.} (\hyperlink{kantunci}{kantunci}+\allowbreak \hyperlink{lum}{lum})
monarch; king; queen

\textbf{\hypertarget{kantuncilyot}{kantuncilyot}} \textit{n.} (\hyperlink{kantunci}{kantunci}+\allowbreak \hyperlink{lyot}{lyot})
kingdom; monarchy

\textbf{\hypertarget{kanpoltilum}{kanpoltilum}} \textit{n.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{poltilum}{poltilum})
dress

\textbf{\hypertarget{kanpit}{kanpit}} \textit{num.} (\hyperlink{kan}{kan}+\allowbreak \hyperlink{pit}{pit})
17; seventeen

\textbf{\hypertarget{'kamae}{'kamae}} \textit{n.} (Khm. ⟨{\khmer{}ខ្មែរ}⟩ [kʰmae])
Khmer; Cambodian; the Khmer people

\textbf{\hypertarget{'kamaeak}{'kamaeak}} \textit{n.} (\hyperlink{'kamae}{'kamae}+\allowbreak \hyperlink{ak}{ak})
Khmer; Cambodian; from Cambodia

\textbf{\hypertarget{'kamaetec}{'kamaetec}} \textit{n.} (\hyperlink{'kamae}{'kamae}+\allowbreak \hyperlink{tec}{tec})
Cambodia

\textbf{\hypertarget{'kamaetilip}{'kamaetilip}} \textit{n.} (\hyperlink{'kamae}{'kamae}+\allowbreak \hyperlink{tilip}{tilip})
Khmer; Cambodian; the Khmer language

\textbf{\hypertarget{'kamli}{'kamli}} \textit{n.} (Cym. ⟨Cymry⟩ [ˈkəmrɨ])
Welsh; the Welsh people

\textbf{\hypertarget{'kamliak}{'kamliak}} \textit{n.} (\hyperlink{'kamli}{'kamli}+\allowbreak \hyperlink{ak}{ak})
Welsh; from Wales

\textbf{\hypertarget{'kamlitec}{'kamlitec}} \textit{n.} (\hyperlink{'kamli}{'kamli}+\allowbreak \hyperlink{tec}{tec})
Wales

\textbf{\hypertarget{'kamlitilip}{'kamlitilip}} \textit{n.} (\hyperlink{'kamli}{'kamli}+\allowbreak \hyperlink{tilip}{tilip})
Welsh; the Welsh language

\textbf{\hypertarget{'kamhun}{'kamhun}} \textit{n.} (Fra. ⟨Cameroun⟩ [kamʁun])
Cameroon

\textbf{\hypertarget{'kamhunak}{'kamhunak}} \textit{n.} (\hyperlink{'kamhun}{'kamhun}+\allowbreak \hyperlink{ak}{ak})
Cameroonian; from Cameroon

\textbf{\hypertarget{'kamhunwon}{'kamhunwon}} \textit{n.} (\hyperlink{'kamhun}{'kamhun}+\allowbreak \hyperlink{won}{won})
Cameroonian; the Cameroonian people

\textbf{\hypertarget{'kampia}{'kampia}} \textit{n.} (Eng. ⟨Gambia⟩ [ˈɡæmbiə])
Gambia river; the River Gambra

\textbf{\hypertarget{'kampiaak}{'kampiaak}} \textit{n.} (\hyperlink{'kampia}{'kampia}+\allowbreak \hyperlink{ak}{ak})
Gambian; from The Gambia

\textbf{\hypertarget{'kampiawon}{'kampiawon}} \textit{n.} (\hyperlink{'kampia}{'kampia}+\allowbreak \hyperlink{won}{won})
Gambian; the Gambian people

\textbf{\hypertarget{'kampiatec}{'kampiatec}} \textit{n.} (\hyperlink{'kampia}{'kampia}+\allowbreak \hyperlink{tec}{tec})
The Gambia; Republic of The Gambia

\textbf{\hypertarget{kaha}{kaha}} \textit{v.} (ono. [ʡah])
cough; \hyperlink{kahales}{ʟєꜱ} coughs up \hyperlink{kahalon}{ʟᴏᴧ}

\textbf{\hypertarget{kahales}{kahales}} \textit{n.} (\hyperlink{kaha}{kaha}+\allowbreak \hyperlink{les}{les})
cougher

\textbf{\hypertarget{kahalon}{kahalon}} \textit{n.} (\hyperlink{kaha}{kaha}+\allowbreak \hyperlink{lon}{lon})
cough

\textbf{\hypertarget{'kaham}{'kaham}} \textit{n.} (Fra. ⟨gramme⟩ [ɡʁam])
gram; g

\textbf{\hypertarget{'kahilah}{'kahilah}} \textit{n.} (Ara. ⟨{\arabics{}قاهرة}⟩ [ˈqaːhiɾah])
Cairo

\textbf{\hypertarget{kac}{kac}} \textit{n.} (Ben. ⟨{\bengali{}গাছ}⟩ [ɡat͡ɕʰ])
tree; tall woody plant structure

\textbf{\hypertarget{kacyeh}{kacyeh}} \textit{n.} (\hyperlink{kac}{kac}+\allowbreak \hyperlink{yeh}{yeh})
palm; palm tree

\textbf{\hypertarget{kaccaka}{kaccaka}} \textit{v.} (\hyperlink{kac}{kac}+\allowbreak \hyperlink{caka}{caka})
be wood; be wooden; \hyperlink{kaccakalon}{ʟᴏᴧ} is made out of wood

\textbf{\hypertarget{kaccakalon}{kaccakalon}} \textit{n.} (\hyperlink{kaccaka}{kaccaka}+\allowbreak \hyperlink{lon}{lon})
wood; wooden

\textbf{\hypertarget{kaccakalonipis}{kaccakalonipis}} \textit{n.} (\hyperlink{kaccakalon}{kaccakalon}+\allowbreak \hyperlink{ipis}{ipis})
termite

\textbf{\hypertarget{kackas}{kackas}} \textit{n.} (\hyperlink{kac}{kac}+\allowbreak \hyperlink{kas}{kas})
bamboo

\textbf{\hypertarget{kackol}{kackol}} \textit{n.} (\hyperlink{kac}{kac}+\allowbreak \hyperlink{kol}{kol})
broccoli

\textbf{\hypertarget{kas}{kas}} \textit{n.} (Hin. ⟨{\devanagari{}घास}⟩ [ɡ̤aːs])
grass; sedge; Poales

\textbf{\hypertarget{'kasak}{'kasak}} \textit{n.} (Kaz. ⟨Kazak⟩ [qɑzɑq])
Kazakh; Kazakhstani; the Kazakhstani people

\textbf{\hypertarget{'kasakak}{'kasakak}} \textit{n.} (\hyperlink{'kasak}{'kasak}+\allowbreak \hyperlink{ak}{ak})
Kazakhstani; from Kazakhstan

\textbf{\hypertarget{'kasaktec}{'kasaktec}} \textit{n.} (\hyperlink{'kasak}{'kasak}+\allowbreak \hyperlink{tec}{tec})
Kazakhstan

\textbf{\hypertarget{'kasaktilip}{'kasaktilip}} \textit{n.} (\hyperlink{'kasak}{'kasak}+\allowbreak \hyperlink{tilip}{tilip})
Kazakh; Kazak; the Kazakh language

\textbf{\hypertarget{kascihwicon}{kascihwicon}} \textit{n.} (\hyperlink{kas}{kas}+\allowbreak \hyperlink{cihwicon}{cihwicon})
park

\textbf{\hypertarget{'kastilya}{'kastilya}} \textit{n.} (Spa. ⟨Castellano⟩ [kasˈtiʎa])
Castile (region)

\textbf{\hypertarget{'kastilyaak}{'kastilyaak}} \textit{n.} (\hyperlink{'kastilya}{'kastilya}+\allowbreak \hyperlink{ak}{ak})
Castillian; from Castile

\textbf{\hypertarget{'kastilyawon}{'kastilyawon}} \textit{n.} (\hyperlink{'kastilya}{'kastilya}+\allowbreak \hyperlink{won}{won})
Castillian; the Castillian people

\textbf{\hypertarget{'kastilyatec}{'kastilyatec}} \textit{n.} (\hyperlink{'kastilya}{'kastilya}+\allowbreak \hyperlink{tec}{tec})
Castile; the Kingdom of Castile

\textbf{\hypertarget{'kastilyatilip}{'kastilyatilip}} \textit{n.} (\hyperlink{'kastilya}{'kastilya}+\allowbreak \hyperlink{tilip}{tilip})
Castillian; the Castillian language

\textbf{\hypertarget{'kaka}{'kaka}} \textit{n.} (Non. ⟨kaka⟩ [kaka])
cake

\textbf{\hypertarget{'kaki}{'kaki}} \textit{n.} (Jpn. ⟨{\japanese{}柿}⟩ [kakʲi])
persimmon; persimon; Diospyros

\textbf{\hypertarget{kaktus}{kaktus}} \textit{n.} (Spa. ⟨cactus⟩ [ˈkaktus])
cactus; Cactaceae

\textbf{\hypertarget{kata}{kata}} \textit{v.} (Mar. ⟨{\devanagari{}कथा}⟩ [kətʰaː])
storytell; \hyperlink{katales}{ʟєꜱ} tells ʟᴏᴧ the story of \hyperlink{katalum}{ʟᴜᴍ}

\textbf{\hypertarget{katales}{katales}} \textit{n.} (\hyperlink{kata}{kata}+\allowbreak \hyperlink{les}{les})
storyteller

\textbf{\hypertarget{katalum}{katalum}} \textit{n.} (\hyperlink{kata}{kata}+\allowbreak \hyperlink{lum}{lum})
story; tale

\textbf{\hypertarget{'katolicismo}{'katolicismo}} \textit{n.} (Lat. ⟨Catholicismo⟩ [kaˈtɔlɪt͡ʃismɔ])
Catholicism; the Catholic Church; the Roman Catholic Church

\textbf{\hypertarget{'katolicismoak}{'katolicismoak}} \textit{n.} (\hyperlink{'katolicismo}{'katolicismo}+\allowbreak \hyperlink{ak}{ak})
Catholic; Roman Catholic; of the Catholic Church

\textbf{\hypertarget{'katolicismowon}{'katolicismowon}} \textit{n.} (\hyperlink{'katolicismo}{'katolicismo}+\allowbreak \hyperlink{won}{won})
Catholic; followers of the Catholic Church

\textbf{\hypertarget{kati}{kati}} \textit{v.} (Swa. ⟨kati⟩ [kati])
be between; be among; \hyperlink{katilon}{ʟᴏᴧ} exists in the space encompassed by the elements of \hyperlink{katilum}{ʟᴜᴍ}

\textbf{\hypertarget{katilon}{katilon}} \textit{n.} (\hyperlink{kati}{kati}+\allowbreak \hyperlink{lon}{lon})
spacing; separation; whitespace; between; among

\textbf{\hypertarget{katilum}{katilum}} \textit{n.} (\hyperlink{kati}{kati}+\allowbreak \hyperlink{lum}{lum})
bounds; boundary; edge

\textbf{\hypertarget{katinu}{katinu}} \textit{v.} (\hyperlink{kati}{kati}+\allowbreak \hyperlink{nu}{nu})
remove from between; pull from; take out of; ʟєꜱ removes ʟᴏᴧ from among ʟᴜᴍ

\textbf{\hypertarget{katiki}{katiki}} \textit{v.} (\hyperlink{kati}{kati}+\allowbreak \hyperlink{ki}{ki})
put between; place among; ʟєꜱ puts ʟᴏᴧ among ʟᴜᴍ

\textbf{\hypertarget{kape}{kape}} \textit{v.} (Jav. ⟨gapé⟩ [kɑ̤pe])
pay attention; focus; watch; occupy; ʟᴏᴧ pays attention to \hyperlink{kapelum}{ʟᴜᴍ}

\textbf{\hypertarget{kap}{kap}} \textit{n.} (Eng. ⟨carp⟩ [kʰɑɹp])
carp; koi; catfish; loach; minnow; herring; tetra; Cypriniformes

\textbf{\hypertarget{kapelum}{kapelum}} \textit{n.} (\hyperlink{kape}{kape}+\allowbreak \hyperlink{lum}{lum})
attention; focus

\textbf{\hypertarget{kapelyan}{kapelyan}} \textit{n.} (\hyperlink{kape}{kape}+\allowbreak \hyperlink{lyan}{lyan})
attention; focus

\textbf{\hypertarget{kapeki}{kapeki}} \textit{v.} (\hyperlink{kape}{kape}+\allowbreak \hyperlink{ki}{ki})
give attention; draw attention; ʟєꜱ makes ʟᴏᴧ pay attention to ʟᴜᴍ

\textbf{\hypertarget{'kapon}{'kapon}} \textit{n.} (Fra. ⟨Gabon⟩ [ɡabɔ̃])
Gabon

\textbf{\hypertarget{'kaponak}{'kaponak}} \textit{n.} (\hyperlink{'kapon}{'kapon}+\allowbreak \hyperlink{ak}{ak})
Gabonese; Gabonaise; from Gabon

\textbf{\hypertarget{'kaponwon}{'kaponwon}} \textit{n.} (\hyperlink{'kapon}{'kapon}+\allowbreak \hyperlink{won}{won})
Gabonese; Gabonaise; the Gabonese people

\textbf{\hypertarget{'kapufelti}{'kapufelti}} \textit{n.} (Por. ⟨Cabo Verde⟩ [kaβu veɾðɨ])
Cabo Verde; Cape Verde (archipelago)

\textbf{\hypertarget{'kapufeltiak}{'kapufeltiak}} \textit{n.} (\hyperlink{'kapufelti}{'kapufelti}+\allowbreak \hyperlink{ak}{ak})
Cabo Verdean; Cape Verdean; from Cabo Verde

\textbf{\hypertarget{'kapufeltiwon}{'kapufeltiwon}} \textit{n.} (\hyperlink{'kapufelti}{'kapufelti}+\allowbreak \hyperlink{won}{won})
Cabo Verdean; Cape Verdean; the Cabo Verdean people

\textbf{\hypertarget{'kapufeltitec}{'kapufeltitec}} \textit{n.} (\hyperlink{'kapufelti}{'kapufelti}+\allowbreak \hyperlink{tec}{tec})
Cabo Verde; Cape Verde; the Republic of Cabo Verde

\textbf{\hypertarget{'kapufeltitilip}{'kapufeltitilip}} \textit{n.} (\hyperlink{'kapufelti}{'kapufelti}+\allowbreak \hyperlink{tilip}{tilip})
Cape Verdean Creole

\textbf{\hypertarget{ko}{ko}} \textit{v.} (\hyperlink{ne}{\sout{ne}})
be outside; be outer; be out; be peripheral; \hyperlink{kolon}{ʟᴏᴧ} is outside of ʟᴜᴍ

\textbf{\hypertarget{'ko}{'ko}} \textit{n.} (ono. [k])
k; /k/; velar plosive

\textbf{\hypertarget{koec}{koec}} \textit{n.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{ec}{ec})
skin; hide; peel

\textbf{\hypertarget{koal}{koal}} \textit{n.} (Epo. ⟨koalo⟩ [koˈalo])
koala; wombat; Vombatiformes

\textbf{\hypertarget{kol}{kol}} \textit{n.} (Spa. ⟨col⟩ [kol])
cabbage; cauliflower; broccoli; kale; Brussels sprouts; collard greens; savoy; kohlrabi; gai lan; Brassica oleracea

\textbf{\hypertarget{kola}{kola}} \textit{v.} (\hyperlink{neta}{\sout{neta}})
be chaotic; be disorganised; be messy; be in disarray; be askance; \hyperlink{kolalon}{ʟᴏᴧ} is chaotic

\textbf{\hypertarget{kolalon}{kolalon}} \textit{n.} (\hyperlink{kola}{kola}+\allowbreak \hyperlink{lon}{lon})
chaotic; disorganised; messy; in disarray; askance

\textbf{\hypertarget{kolalyan}{kolalyan}} \textit{n.} (\hyperlink{kola}{kola}+\allowbreak \hyperlink{lyan}{lyan})
entropy; chaos

\textbf{\hypertarget{kolaki}{kolaki}} \textit{v.} (\hyperlink{kola}{kola}+\allowbreak \hyperlink{ki}{ki})
disorganise; mess up; disrupt; trash; throw into chaos; \hyperlink{kolakiles}{ʟєꜱ} puts ʟᴏᴧ into chaos

\textbf{\hypertarget{kolakiles}{kolakiles}} \textit{n.} (\hyperlink{kolaki}{kolaki}+\allowbreak \hyperlink{les}{les})
disorganiser; trasher

\textbf{\hypertarget{'kololium}{'kololium}} \textit{n.} (Lat. ⟨chlorium⟩ [klorɪʊ̃])
chlorine

\textbf{\hypertarget{kolon}{kolon}} \textit{n.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{lon}{lon})
outdoors; edge; fringe; outside; outer; out; peripheral

\textbf{\hypertarget{'kolona}{'kolona}} \textit{n.} (Nor. ⟨krone⟩ [ˈkruːnə])
krona; krone; króna; kr.

\textbf{\hypertarget{'kolomium}{'kolomium}} \textit{n.} (Lat. ⟨chromium⟩ [kromɪʊ̃])
chromium

\textbf{\hypertarget{'kolompya}{'kolompya}} \textit{n.} (Spa. ⟨Colombia⟩ [koˈlombja])
Colombia

\textbf{\hypertarget{'kolompyaak}{'kolompyaak}} \textit{n.} (\hyperlink{'kolompya}{'kolompya}+\allowbreak \hyperlink{ak}{ak})
Columbian; from Colombia

\textbf{\hypertarget{'kolompyawon}{'kolompyawon}} \textit{n.} (\hyperlink{'kolompya}{'kolompya}+\allowbreak \hyperlink{won}{won})
Colombian; the Columbian people

\textbf{\hypertarget{kolopo}{kolopo}} \textit{v.} (ono. [korop])
burp; belch; \hyperlink{kolopoles}{ʟєꜱ} burps out \hyperlink{kolopolon}{ʟᴏᴧ}

\textbf{\hypertarget{kolopoles}{kolopoles}} \textit{n.} (\hyperlink{kolopo}{kolopo}+\allowbreak \hyperlink{les}{les})
one who burps

\textbf{\hypertarget{kolopolon}{kolopolon}} \textit{n.} (\hyperlink{kolopo}{kolopo}+\allowbreak \hyperlink{lon}{lon})
burp

\textbf{\hypertarget{kolwa}{kolwa}} \textit{v.} (Zul. ⟨kholwa⟩ [ˈkʰɔːlwa])
believe; seem; \hyperlink{kolwalon}{ʟᴏᴧ} accepts that \hyperlink{kolwalum}{ʟᴜᴍ} is true on a subconscious level; see "be sure" and "think"

\textbf{\hypertarget{kolwalon}{kolwalon}} \textit{n.} (\hyperlink{kolwa}{kolwa}+\allowbreak \hyperlink{lon}{lon})
believer

\textbf{\hypertarget{kolwalum}{kolwalum}} \textit{n.} (\hyperlink{kolwa}{kolwa}+\allowbreak \hyperlink{lum}{lum})
belief; feeling

\textbf{\hypertarget{kolwaki}{kolwaki}} \textit{v.} (\hyperlink{kolwa}{kolwa}+\allowbreak \hyperlink{ki}{ki})
convince; sway; ʟєꜱ leads ʟᴏᴧ to believe that ʟᴜᴍ is true

\textbf{\hypertarget{kon}{kon}} \textit{pn.} (Pan. ⟨{\gurmukhi{}ਕੌਣ}⟩ [kɔːɳə])
what; what kind; \textit{interrogative}

\textbf{\hypertarget{kon ayf}{kon ayf}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{ayf}{ayf})
under what condition; when (interrogative)

\textbf{\hypertarget{kon ak}{kon ak}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{ak}{ak})
whose (interrogative)

\textbf{\hypertarget{'konakhi}{'konakhi}} \textit{n.} (Fra. ⟨Conakry⟩ [konakʁi])
Conakry

\textbf{\hypertarget{'konakhi'kine}{'konakhi'kine}} \textit{n.} (\hyperlink{'konakhi}{'konakhi}+\allowbreak \hyperlink{'kine}{'kine})
Guinea; Guinea-Conakry; the Republic of Guinea

\textbf{\hypertarget{'konakhi'kinewon}{'konakhi'kinewon}} \textit{n.} (\hyperlink{'konakhi'kine}{'konakhi'kine}+\allowbreak \hyperlink{won}{won})
Guinean; the Guinean people

\textbf{\hypertarget{'kono}{'kono}} \textit{n.} (Kon. ⟨Kongo⟩ [koŋo])
Kongo; the Kongo people

\textbf{\hypertarget{'konoak}{'konoak}} \textit{n.} (\hyperlink{'kono}{'kono}+\allowbreak \hyperlink{ak}{ak})
Kongo; Congolese; from the Congo

\textbf{\hypertarget{'konotec}{'konotec}} \textit{n.} (\hyperlink{'kono}{'kono}+\allowbreak \hyperlink{tec}{tec})
Kongo; the Kingdom of Kongo

\textbf{\hypertarget{'konotilip}{'konotilip}} \textit{n.} (\hyperlink{'kono}{'kono}+\allowbreak \hyperlink{tilip}{tilip})
Kongo; Kikongo

\textbf{\hypertarget{kon ial}{kon ial}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{ial}{ial})
why (interrogative)

\textbf{\hypertarget{konitatun}{konitatun}} \textit{n.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{nita}{nita}+\allowbreak \hyperlink{tun}{tun})
arthropod

\textbf{\hypertarget{konitatunak}{konitatunak}} \textit{n.} (\hyperlink{konitatun}{konitatun}+\allowbreak \hyperlink{ak}{ak})
arthropodic

\textbf{\hypertarget{kon ip}{kon ip}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{ip}{ip})
how (interrogative)

\textbf{\hypertarget{kon uat}{kon uat}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{uat}{uat})
with what (interrogative)

\textbf{\hypertarget{kon yan}{kon yan}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{yan}{yan})
how much

\textbf{\hypertarget{kon yot}{kon yot}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{yot}{yot})
where (interrogative)

\textbf{\hypertarget{kon wel}{kon wel}} \textit{n.} (\hyperlink{kon}{kon}+\allowbreak \hyperlink{wel}{wel})
when (interrogative)

\textbf{\hypertarget{kontal}{kontal}} \textit{n.} (Ben. ⟨{\bengali{}গণ্ডার}⟩ [ɡɔndar])
rhinoceros; rhino; rhinocerotidae

\textbf{\hypertarget{'kontapaso}{'kontapaso}} \textit{n.} (Ita. ⟨contrabbasso⟩ [kontrabˈbasso])
double bass; bass; string bass; contrabass

\textbf{\hypertarget{'komoli}{'komoli}} \textit{n.} (Zdj. ⟨Komori⟩ [komori])
Comoros (archipelago)

\textbf{\hypertarget{'komoliak}{'komoliak}} \textit{n.} (\hyperlink{'komoli}{'komoli}+\allowbreak \hyperlink{ak}{ak})
Comoran; from Comoros

\textbf{\hypertarget{'komoliwon}{'komoliwon}} \textit{n.} (\hyperlink{'komoli}{'komoli}+\allowbreak \hyperlink{won}{won})
Comoran; the Comoran people

\textbf{\hypertarget{'komolitec}{'komolitec}} \textit{n.} (\hyperlink{'komoli}{'komoli}+\allowbreak \hyperlink{tec}{tec})
Comoros; the Union of the Comoros

\textbf{\hypertarget{'komolitilip}{'komolitilip}} \textit{n.} (\hyperlink{'komoli}{'komoli}+\allowbreak \hyperlink{tilip}{tilip})
Comorian; the Comorian language

\textbf{\hypertarget{komput}{komput}} \textit{n.} (Xho. ⟨khomputha⟩ [kʰɔmputʰa])
computer; artificial device capable of arithmetic or logical operations

\textbf{\hypertarget{komputak}{komputak}} \textit{n.} (\hyperlink{komput}{komput}+\allowbreak \hyperlink{ak}{ak})
digital; electronic; computerised

\textbf{\hypertarget{komputnati}{komputnati}} \textit{v.} (\hyperlink{komput}{komput}+\allowbreak \hyperlink{nati}{nati})
code; program; \hyperlink{komputnatiles}{ʟєꜱ} codes ʟᴏᴧ with \hyperlink{komputnatilum}{ʟᴜᴍ}

\textbf{\hypertarget{komputnatiles}{komputnatiles}} \textit{n.} (\hyperlink{komputnati}{komputnati}+\allowbreak \hyperlink{les}{les})
programmer

\textbf{\hypertarget{komputnatilum}{komputnatilum}} \textit{n.} (\hyperlink{komputnati}{komputnati}+\allowbreak \hyperlink{lum}{lum})
code; program

\textbf{\hypertarget{komputsoma}{komputsoma}} \textit{v.} (\hyperlink{komput}{komput}+\allowbreak \hyperlink{soma}{soma})
do computer science; \hyperlink{komputsomales}{ʟєꜱ} studies computers to learn about \hyperlink{komputsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{komputsomales}{komputsomales}} \textit{n.} (\hyperlink{komputsoma}{komputsoma}+\allowbreak \hyperlink{les}{les})
computer scientist

\textbf{\hypertarget{komputsomalon}{komputsomalon}} \textit{n.} (\hyperlink{komputsoma}{komputsoma}+\allowbreak \hyperlink{lon}{lon})
computer science

\textbf{\hypertarget{komputti}{komputti}} \textit{v.} (\hyperlink{komput}{komput}+\allowbreak \hyperlink{ti}{ti})
use internet; go online; signal; \hyperlink{komputtiles}{ʟєꜱ} digitally sends \hyperlink{komputtilum}{ʟᴜᴍ} to \hyperlink{komputtilon}{ʟᴏᴧ}

\textbf{\hypertarget{komputtiles}{komputtiles}} \textit{n.} (\hyperlink{komputti}{komputti}+\allowbreak \hyperlink{les}{les})
sender (engineering)

\textbf{\hypertarget{komputtilon}{komputtilon}} \textit{n.} (\hyperlink{komputti}{komputti}+\allowbreak \hyperlink{lon}{lon})
receiver (engineering)

\textbf{\hypertarget{komputtilip}{komputtilip}} \textit{n.} (\hyperlink{komputti}{komputti}+\allowbreak \hyperlink{lip}{lip})
communication protocol; protocol (engineering)

\textbf{\hypertarget{komputtiluat}{komputtiluat}} \textit{n.} (\hyperlink{komputti}{komputti}+\allowbreak \hyperlink{luat}{luat})
socket (engineering)

\textbf{\hypertarget{komputtilum}{komputtilum}} \textit{n.} (\hyperlink{komputti}{komputti}+\allowbreak \hyperlink{lum}{lum})
packet (engineering)

\textbf{\hypertarget{kohu}{kohu}} \textit{v.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{hu}{hu})
be public; ʟᴜᴍ is openly exposed to \hyperlink{kohulon}{ʟᴏᴧ}

\textbf{\hypertarget{kohulon}{kohulon}} \textit{n.} (\hyperlink{kohu}{kohu}+\allowbreak \hyperlink{lon}{lon})
the public; public

\textbf{\hypertarget{'kosa}{'kosa}} \textit{n.} (Xho. ⟨Xhosa⟩ [kǁʰɔ́ːsa])
Xhosa; the Xhosa people

\textbf{\hypertarget{'kosaak}{'kosaak}} \textit{n.} (\hyperlink{'kosa}{'kosa}+\allowbreak \hyperlink{ak}{ak})
Xhosa; of the Xhosa

\textbf{\hypertarget{'kosatilip}{'kosatilip}} \textit{n.} (\hyperlink{'kosa}{'kosa}+\allowbreak \hyperlink{tilip}{tilip})
Xhosa; the Xhosa language

\textbf{\hypertarget{'kosowa}{'kosowa}} \textit{n.} (Sqi. ⟨Kosovë⟩ [kɔˈsɔvə])
Kosovo; the Republic of Kosovo

\textbf{\hypertarget{'kosowaak}{'kosowaak}} \textit{n.} (\hyperlink{'kosowa}{'kosowa}+\allowbreak \hyperlink{ak}{ak})
Kosovan; Kosovar; from Kosovo

\textbf{\hypertarget{'kosowawon}{'kosowawon}} \textit{n.} (\hyperlink{'kosowa}{'kosowa}+\allowbreak \hyperlink{won}{won})
Kosovan; Kosovar; the Kosovan people

\textbf{\hypertarget{'kostalika}{'kostalika}} \textit{n.} (Spa. ⟨Costa Rica⟩ [kosta rika])
Costa Rica

\textbf{\hypertarget{'kostalikaak}{'kostalikaak}} \textit{n.} (\hyperlink{'kostalika}{'kostalika}+\allowbreak \hyperlink{ak}{ak})
Costa Rican; from Costa Rica

\textbf{\hypertarget{'kostalikawon}{'kostalikawon}} \textit{n.} (\hyperlink{'kostalika}{'kostalika}+\allowbreak \hyperlink{won}{won})
Costa Rican; the Costa Rican people

\textbf{\hypertarget{kosti}{kosti}} \textit{v.} (Epo. ⟨kosti⟩ [ˈkosti])
cost; be expensive; \hyperlink{kostilon}{ʟᴏᴧ} costs a lot

\textbf{\hypertarget{kostilon}{kostilon}} \textit{n.} (\hyperlink{kosti}{kosti}+\allowbreak \hyperlink{lon}{lon})
valuable; expensive

\textbf{\hypertarget{kostilyan}{kostilyan}} \textit{n.} (\hyperlink{kosti}{kosti}+\allowbreak \hyperlink{lyan}{lyan})
price; cost

\textbf{\hypertarget{kostiki}{kostiki}} \textit{v.} (\hyperlink{kosti}{kosti}+\allowbreak \hyperlink{ki}{ki})
mark up; ʟєꜱ increases the cost of ʟᴏᴧ

\textbf{\hypertarget{'kof}{'kof}} \textit{n.} (Eng. ⟨golf⟩ [ɡɒf])
golf

\textbf{\hypertarget{koki}{koki}} \textit{v.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{ki}{ki})
exit; remove; release; escape; take out; go out; extract; emerge; ʟєꜱ moves ʟᴏᴧ out of ʟᴜᴍ

\textbf{\hypertarget{kokilyot}{kokilyot}} \textit{n.} (\hyperlink{koki}{koki}+\allowbreak \hyperlink{lyot}{lyot})
hole

\textbf{\hypertarget{kot}{kot}} \textit{n.} (Eng. ⟨god⟩ [ɡɒd])
god; deity; superhuman entity worshiped as having great influence over reality, but not any god in particular

\textbf{\hypertarget{kotak}{kotak}} \textit{n.} (\hyperlink{kot}{kot}+\allowbreak \hyperlink{ak}{ak})
divine; godly; deific

\textbf{\hypertarget{kotokanu}{kotokanu}} \textit{v.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{tokanu}{tokanu})
peel; ʟєꜱ peels ʟᴏᴧ

\textbf{\hypertarget{koti}{koti}} \textit{v.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{ti}{ti})
comment; commentary; \hyperlink{kotiles}{ʟєꜱ} comments \hyperlink{kotilon}{ʟᴏᴧ} on ʟᴜᴍ

\textbf{\hypertarget{kotiles}{kotiles}} \textit{n.} (\hyperlink{koti}{koti}+\allowbreak \hyperlink{les}{les})
commenter

\textbf{\hypertarget{kotilon}{kotilon}} \textit{n.} (\hyperlink{koti}{koti}+\allowbreak \hyperlink{lon}{lon})
metadata; comment; commentary

\textbf{\hypertarget{'kotifwah}{'kotifwah}} \textit{n.} (Fra. ⟨Côte d’Ivoire⟩ [kot divwaʁ])
Ivory Coast; Côte d’Ivoire

\textbf{\hypertarget{'kotifwahak}{'kotifwahak}} \textit{n.} (\hyperlink{'kotifwah}{'kotifwah}+\allowbreak \hyperlink{ak}{ak})
Ivorian; from Ivory Coast

\textbf{\hypertarget{'kotifwahwon}{'kotifwahwon}} \textit{n.} (\hyperlink{'kotifwah}{'kotifwah}+\allowbreak \hyperlink{won}{won})
Ivorian; the Ivorian people

\textbf{\hypertarget{kotsoma}{kotsoma}} \textit{v.} (\hyperlink{kot}{kot}+\allowbreak \hyperlink{soma}{soma})
do theology; \hyperlink{kotsomales}{ʟєꜱ} studies religion to learn about \hyperlink{kotsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{kotsomales}{kotsomales}} \textit{n.} (\hyperlink{kotsoma}{kotsoma}+\allowbreak \hyperlink{les}{les})
theologist

\textbf{\hypertarget{kotsomalon}{kotsomalon}} \textit{n.} (\hyperlink{kotsoma}{kotsoma}+\allowbreak \hyperlink{lon}{lon})
theology

\textbf{\hypertarget{kotkwelip}{kotkwelip}} \textit{n.} (\hyperlink{kot}{kot}+\allowbreak \hyperlink{kwelip}{kwelip})
religion

\textbf{\hypertarget{kopic}{kopic}} \textit{n.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{pic}{pic})
cashew

\textbf{\hypertarget{kopuci}{kopuci}} \textit{v.} (\hyperlink{ko}{ko}+\allowbreak \hyperlink{puci}{puci})
stretch; expand; ʟєꜱ pulls outward on ʟᴏᴧ

\textbf{\hypertarget{ki}{ki}} \textit{v.} (Cmn. ⟨{\chinese{}开始}⟩ [kʰaɪ̯˥ʂɨ˧˩˧])
begin; start; commence; initiate; become; go to; come to; change to; summon; arrive; to; -ify; \textit{incohative}; \hyperlink{kiles}{ʟєꜱ} makes \hyperlink{kilon}{ʟᴏᴧ} transition from falsehood to truth

\textbf{\hypertarget{kiah}{kiah}} \textit{n.} (ono. [kijɑː])
raptor; hawk; eagle; kite; vulture; condor; osprey; owl; falcon; bird of prey

\textbf{\hypertarget{kio}{kio}} \textit{v.} (Swa. ⟨kioo⟩ [kioo])
be crystal; \hyperlink{kiolon}{ʟᴏᴧ} is made out of crystal

\textbf{\hypertarget{kiolon}{kiolon}} \textit{n.} (\hyperlink{kio}{kio}+\allowbreak \hyperlink{lon}{lon})
jewel; gem; crystal

\textbf{\hypertarget{kioki}{kioki}} \textit{v.} (\hyperlink{kio}{kio}+\allowbreak \hyperlink{ki}{ki})
crystalise; ʟєꜱ turns ʟᴏᴧ into crystal

\textbf{\hypertarget{kil}{kil}} \textit{n.} (Hin. ⟨{\devanagari{}कीड़ा}⟩ [kiːɽaː])
worm; long limbless invertebrate

\textbf{\hypertarget{kiles}{kiles}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{les}{les})
starter

\textbf{\hypertarget{kilon}{kilon}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{lon}{lon})
begun

\textbf{\hypertarget{'kilistos}{'kilistos}} \textit{n.} (Grc. ⟨Χριστός⟩ [kʰriːstós])
Christ (title)

\textbf{\hypertarget{'kilistosfitilip}{'kilistosfitilip}} \textit{n.} (\hyperlink{'kilistos}{'kilistos}+\allowbreak \hyperlink{fitilip}{fitilip})
Christianity

\textbf{\hypertarget{'kilistosfitilipwon}{'kilistosfitilipwon}} \textit{n.} (\hyperlink{'kilistosfitilip}{'kilistosfitilip}+\allowbreak \hyperlink{won}{won})
Christian; followers of Christ

\textbf{\hypertarget{'kilistosfitilipak}{'kilistosfitilipak}} \textit{n.} (\hyperlink{'kilistosfitilip}{'kilistosfitilip}+\allowbreak \hyperlink{ak}{ak})
Christian; of Christianity

\textbf{\hypertarget{'kilipas}{'kilipas}} \textit{n.} (Gil. ⟨Kiribati⟩ [kiɾipas])
Kiribati; the Gilbert Islands

\textbf{\hypertarget{'kilipasak}{'kilipasak}} \textit{n.} (\hyperlink{'kilipas}{'kilipas}+\allowbreak \hyperlink{ak}{ak})
I-Kiribati; from Kiribati

\textbf{\hypertarget{'kilipaswon}{'kilipaswon}} \textit{n.} (\hyperlink{'kilipas}{'kilipas}+\allowbreak \hyperlink{won}{won})
I-Kiribati; Gilbertese; the I-Kiribati people

\textbf{\hypertarget{'kilipastec}{'kilipastec}} \textit{n.} (\hyperlink{'kilipas}{'kilipas}+\allowbreak \hyperlink{tec}{tec})
Kiribati; the Republic of Kiribati

\textbf{\hypertarget{'kilipastilip}{'kilipastilip}} \textit{n.} (\hyperlink{'kilipas}{'kilipas}+\allowbreak \hyperlink{tilip}{tilip})
Gilbertese; Kiribati; Kiribatese; the Kiribati language

\textbf{\hypertarget{'kilipton}{'kilipton}} \textit{n.} (Lat. ⟨krypton⟩ [kriptɔn])
krypton

\textbf{\hypertarget{kilyot}{kilyot}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{lyot}{lyot})
start

\textbf{\hypertarget{kilwel}{kilwel}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{lwel}{lwel})
beginning

\textbf{\hypertarget{'kine}{'kine}} \textit{n.} (Por. ⟨Guiné⟩ [ɡiˈne])
Guinea (region)

\textbf{\hypertarget{'kincasa}{'kincasa}} \textit{n.} (Fra. ⟨Kinshasa⟩ [kinʃasa])
Kinshasa

\textbf{\hypertarget{'kincasa'konotec}{'kincasa'konotec}} \textit{n.} (\hyperlink{'kincasa}{'kincasa}+\allowbreak \hyperlink{'konotec}{'konotec})
Democratic Republic of the Congo

\textbf{\hypertarget{'kincasa'konotecwon}{'kincasa'konotecwon}} \textit{n.} (\hyperlink{'kincasa'konotec}{'kincasa'konotec}+\allowbreak \hyperlink{won}{won})
Congolese; the people of the Democratic Republic of the Congo

\textbf{\hypertarget{'kincasa'konotecak}{'kincasa'konotecak}} \textit{n.} (\hyperlink{'kincasa'konotec}{'kincasa'konotec}+\allowbreak \hyperlink{ak}{ak})
Congolese; from Democratic Republic of the Congo

\textbf{\hypertarget{'kimono}{'kimono}} \textit{n.} (Jpn. ⟨{\japanese{}着物}⟩ [kʲimono])
kimono

\textbf{\hypertarget{kicolon}{kicolon}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{colon}{colon})
incohative; inceptive (linguistics)

\textbf{\hypertarget{kisison}{kisison}} \textit{n.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{sison}{sison})
spring

\textbf{\hypertarget{'kiskeya}{'kiskeya}} \textit{n.} (Spa. ⟨Quisqueya⟩ [kisˈkeʝa])
Dominican Republic

\textbf{\hypertarget{'kiskeyaak}{'kiskeyaak}} \textit{n.} (\hyperlink{'kiskeya}{'kiskeya}+\allowbreak \hyperlink{ak}{ak})
Dominican; Quisqueyan; from Dominican Republic

\textbf{\hypertarget{'kiskeyawon}{'kiskeyawon}} \textit{n.} (\hyperlink{'kiskeya}{'kiskeya}+\allowbreak \hyperlink{won}{won})
Quisqueyan; the people of the Dominican Republic

\textbf{\hypertarget{kit}{kit}} \textit{num.} (\hyperlink{nul}{\sout{nul}})
all; absolute; maximum; exact; complete

\textbf{\hypertarget{kitak}{kitak}} \textit{n.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{ak}{ak})
last; universal

\textbf{\hypertarget{kitakeki}{kitakeki}} \textit{v.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{akeki}{akeki})
achieve; accomplish; complete; ʟєꜱ makes \hyperlink{kitakekilon}{ʟᴏᴧ} achieve \hyperlink{kitakekilum}{ʟᴜᴍ}

\textbf{\hypertarget{kitakekilon}{kitakekilon}} \textit{n.} (\hyperlink{kitakeki}{kitakeki}+\allowbreak \hyperlink{lon}{lon})
achiever

\textbf{\hypertarget{kitakekilum}{kitakekilum}} \textit{n.} (\hyperlink{kitakeki}{kitakeki}+\allowbreak \hyperlink{lum}{lum})
accomplished; achieved; completed

\textbf{\hypertarget{kititi}{kititi}} \textit{v.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{iti}{iti})
integrate; take integral; \hyperlink{kititiles}{ʟєꜱ} takes the n-dimensional integral of \hyperlink{kititilon}{ʟᴏᴧ} over \hyperlink{kititilum}{ʟᴜᴍ}

\textbf{\hypertarget{kititiles}{kititiles}} \textit{n.} (\hyperlink{kititi}{kititi}+\allowbreak \hyperlink{les}{les})
integrator

\textbf{\hypertarget{kititilon}{kititilon}} \textit{n.} (\hyperlink{kititi}{kititi}+\allowbreak \hyperlink{lon}{lon})
derivative; integration function

\textbf{\hypertarget{kititilum}{kititilum}} \textit{n.} (\hyperlink{kititi}{kititi}+\allowbreak \hyperlink{lum}{lum})
integration variable

\textbf{\hypertarget{kititilyan}{kititilyan}} \textit{n.} (\hyperlink{kititi}{kititi}+\allowbreak \hyperlink{lyan}{lyan})
integral dimensionality

\textbf{\hypertarget{kititilyot}{kititilyot}} \textit{n.} (\hyperlink{kititi}{kititi}+\allowbreak \hyperlink{lyot}{lyot})
integration bounds

\textbf{\hypertarget{kitwale}{kitwale}} \textit{v.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{wale}{wale})
be common; be normal; be standard; \hyperlink{kitwalelon}{ʟᴏᴧ} is common among ʟᴜᴍ

\textbf{\hypertarget{kitwalelon}{kitwalelon}} \textit{n.} (\hyperlink{kitwale}{kitwale}+\allowbreak \hyperlink{lon}{lon})
common; normal; standard

\textbf{\hypertarget{kitcitu}{kitcitu}} \textit{v.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{citu}{citu})
be until; be since; happen from; happen to; \hyperlink{kitcitulon}{ʟᴏᴧ} is happening from the present until \hyperlink{kitcitulum}{ʟᴜᴍ}

\textbf{\hypertarget{kitcitulon}{kitcitulon}} \textit{n.} (\hyperlink{kitcitu}{kitcitu}+\allowbreak \hyperlink{lon}{lon})
until; since

\textbf{\hypertarget{kitcitulum}{kitcitulum}} \textit{n.} (\hyperlink{kitcitu}{kitcitu}+\allowbreak \hyperlink{lum}{lum})
end date; deadline

\textbf{\hypertarget{kitcitulwel}{kitcitulwel}} \textit{n.} (\hyperlink{kitcitu}{kitcitu}+\allowbreak \hyperlink{lwel}{lwel})
start date; kickoff

\textbf{\hypertarget{kitki}{kitki}} \textit{num.} (∅)
universalise; popularise; permeate; pervade; ʟєꜱ causes ʟᴏᴧ to become everything

\textbf{\hypertarget{kittecak}{kittecak}} \textit{n.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{tecak}{tecak})
global; international

\textbf{\hypertarget{kittunci}{kittunci}} \textit{v.} (\hyperlink{kit}{kit}+\allowbreak \hyperlink{tunci}{tunci})
govern as a direct democracy; \hyperlink{kittuncilum}{ʟᴜᴍ} rules ʟᴏᴧ

\textbf{\hypertarget{kittuncilum}{kittuncilum}} \textit{n.} (\hyperlink{kittunci}{kittunci}+\allowbreak \hyperlink{lum}{lum})
voter; electoral base

\textbf{\hypertarget{kittuncilyot}{kittuncilyot}} \textit{n.} (\hyperlink{kittunci}{kittunci}+\allowbreak \hyperlink{lyot}{lyot})
democracy; direct democracy

\textbf{\hypertarget{kipowi}{kipowi}} \textit{v.} (\hyperlink{ki}{ki}+\allowbreak \hyperlink{powi}{powi})
be ready; \hyperlink{kipowilon}{ʟᴏᴧ} is ready to make ʟᴜᴍ happen

\textbf{\hypertarget{kipowilon}{kipowilon}} \textit{n.} (\hyperlink{kipowi}{kipowi}+\allowbreak \hyperlink{lon}{lon})
ready

\textbf{\hypertarget{kipowiki}{kipowiki}} \textit{v.} (\hyperlink{kipowi}{kipowi}+\allowbreak \hyperlink{ki}{ki})
ready; prepare; ʟєꜱ gets ʟᴏᴧ ready for ʟᴜᴍ

\textbf{\hypertarget{'kiplos}{'kiplos}} \textit{n.} (Ell. ⟨Κύπρος⟩ [ˈcipros])
Cyprus (landmass)

\textbf{\hypertarget{'kiplosak}{'kiplosak}} \textit{n.} (\hyperlink{'kiplos}{'kiplos}+\allowbreak \hyperlink{ak}{ak})
Cypriot; from Cyprus

\textbf{\hypertarget{'kiplostec}{'kiplostec}} \textit{n.} (\hyperlink{'kiplos}{'kiplos}+\allowbreak \hyperlink{tec}{tec})
Cyprus; the Republic of Cyprus

\textbf{\hypertarget{'kiplostecwon}{'kiplostecwon}} \textit{n.} (\hyperlink{'kiplostec}{'kiplostec}+\allowbreak \hyperlink{won}{won})
Cypriot; the Cypriot people

\textbf{\hypertarget{ku}{ku}} \textit{v.} (Cmn. ⟨{\chinese{}苦}⟩ [kʰu˧˩˧])
be bitter; \hyperlink{kulon}{ʟᴏᴧ} is bitter

\textbf{\hypertarget{kule}{kule}} \textit{v.} (Sho. ⟨kure⟩ [kure])
be far; be distant; be beyond; be not at all; be remote; tele; \hyperlink{kulelon}{ʟᴏᴧ} is physically or numerically far from \hyperlink{kulelum}{ʟᴜᴍ}

\textbf{\hypertarget{kuleam}{kuleam}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{am}{am})
forearm; lower arm

\textbf{\hypertarget{kulelek}{kulelek}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{lek}{lek})
shin; lower leg

\textbf{\hypertarget{kulelon}{kulelon}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{lon}{lon})
far; distant; beyond; not at all; remote

\textbf{\hypertarget{kulelum}{kulelum}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{lum}{lum})
space

\textbf{\hypertarget{kulelyan}{kulelyan}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{lyan}{lyan})
distance

\textbf{\hypertarget{kulelyanti}{kulelyanti}} \textit{v.} (\hyperlink{kulelyan}{kulelyan}+\allowbreak \hyperlink{ti}{ti})
bid farewell; say goodbye; ʟєꜱ bids goodbye to ʟᴏᴧ

\textbf{\hypertarget{kulenoluat}{kulenoluat}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{noluat}{noluat})
meterstick; ruler; measuring tape; stick

\textbf{\hypertarget{kulehila}{kulehila}} \textit{v.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{hila}{hila})
travel; ʟєꜱ travels from ʟᴜᴍ to \hyperlink{kulehilalon}{ʟᴏᴧ}

\textbf{\hypertarget{kulehilalon}{kulehilalon}} \textit{n.} (\hyperlink{kulehila}{kulehila}+\allowbreak \hyperlink{lon}{lon})
destination; getaway

\textbf{\hypertarget{kulecalu}{kulecalu}} \textit{v.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{calu}{calu})
keep apart; separate; divide; avoid; \hyperlink{kulecalules}{ʟєꜱ} keeps \hyperlink{kulecalulon}{ʟᴏᴧ} away from ʟᴜᴍ

\textbf{\hypertarget{kulecalules}{kulecalules}} \textit{n.} (\hyperlink{kulecalu}{kulecalu}+\allowbreak \hyperlink{les}{les})
wall; barrier

\textbf{\hypertarget{kulecalulon}{kulecalulon}} \textit{n.} (\hyperlink{kulecalu}{kulecalu}+\allowbreak \hyperlink{lon}{lon})
other side

\textbf{\hypertarget{kulecincilum}{kulecincilum}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{cincilum}{cincilum})
first cousin

\textbf{\hypertarget{kuleki}{kuleki}} \textit{v.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{ki}{ki})
distance; go away; separate; come from; go out; \hyperlink{kulekiles}{ʟєꜱ} distances ʟᴏᴧ from ʟᴜᴍ

\textbf{\hypertarget{kulekiles}{kulekiles}} \textit{n.} (\hyperlink{kuleki}{kuleki}+\allowbreak \hyperlink{les}{les})
separator

\textbf{\hypertarget{kuletiluat}{kuletiluat}} \textit{n.} (\hyperlink{kule}{kule}+\allowbreak \hyperlink{tiluat}{tiluat})
telephone; telegraph

\textbf{\hypertarget{kula}{kula}} \textit{v.} (Hin. ⟨{\devanagari{}खुला}⟩ [kʰulaː])
be soft; be flimsy; be squishy; be weak; give; the surface of \hyperlink{kulalon}{ʟᴏᴧ} feels soft

\textbf{\hypertarget{kulaec}{kulaec}} \textit{n.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{ec}{ec})
flesh; meat

\textbf{\hypertarget{kulalon}{kulalon}} \textit{n.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{lon}{lon})
soft; flimsy; squishy; weak

\textbf{\hypertarget{kulan}{kulan}} \textit{pn.} (Xho. ⟨okulandelayo⟩ [ɔkʼulandɛlajɔ])
next

\textbf{\hypertarget{kulansunkwelwel}{kulansunkwelwel}} \textit{n.} (\hyperlink{kulan}{kulan}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
tomorrow

\textbf{\hypertarget{kulanpumkwelwel}{kulanpumkwelwel}} \textit{n.} (\hyperlink{kulan}{kulan}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
next year

\textbf{\hypertarget{kulaki}{kulaki}} \textit{v.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{ki}{ki})
soften; melt; ʟєꜱ makes ʟᴏᴧ become soft

\textbf{\hypertarget{kulatatu}{kulatatu}} \textit{v.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{tatu}{tatu})
be tin; \hyperlink{kulatatulon}{ʟᴏᴧ} is made of tin

\textbf{\hypertarget{kulatatulon}{kulatatulon}} \textit{n.} (\hyperlink{kulatatu}{kulatatu}+\allowbreak \hyperlink{lon}{lon})
tin

\textbf{\hypertarget{kulatun}{kulatun}} \textit{n.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{tun}{tun})
invertebrate

\textbf{\hypertarget{kulapic}{kulapic}} \textit{n.} (\hyperlink{kula}{kula}+\allowbreak \hyperlink{pic}{pic})
bean

\textbf{\hypertarget{kulon}{kulon}} \textit{n.} (\hyperlink{ku}{ku}+\allowbreak \hyperlink{lon}{lon})
bitter

\textbf{\hypertarget{kuli}{kuli}} \textit{v.} (Jav. ⟨gurih⟩ [kṳɽɪh])
be savoury; have umami; \hyperlink{kulilon}{ʟᴏᴧ} is savoury

\textbf{\hypertarget{kulilon}{kulilon}} \textit{n.} (\hyperlink{kuli}{kuli}+\allowbreak \hyperlink{lon}{lon})
savoury

\textbf{\hypertarget{kulilyan}{kulilyan}} \textit{n.} (\hyperlink{kuli}{kuli}+\allowbreak \hyperlink{lyan}{lyan})
savouriness; umami

\textbf{\hypertarget{kuliki}{kuliki}} \textit{v.} (\hyperlink{kuli}{kuli}+\allowbreak \hyperlink{ki}{ki})
make savoury; ʟєꜱ makes ʟᴏᴧ become savoury

\textbf{\hypertarget{kululun}{kululun}} \textit{n.} (ono. [gululu])
turkey (bird); Meleagris

\textbf{\hypertarget{kulyan}{kulyan}} \textit{n.} (\hyperlink{ku}{ku}+\allowbreak \hyperlink{lyan}{lyan})
bitterness

\textbf{\hypertarget{'kulkus}{'kulkus}} \textit{n.} (Kir. ⟨кыргыз⟩ [qɯrʁɯs])
Kyrgyz; Kyrgyzstani; the Kyrgyz people

\textbf{\hypertarget{'kulkusak}{'kulkusak}} \textit{n.} (\hyperlink{'kulkus}{'kulkus}+\allowbreak \hyperlink{ak}{ak})
Kyrgyz; Kyrgyzstani; Kirgiz; Kirghiz; from Kyrgyzstan

\textbf{\hypertarget{'kulkustec}{'kulkustec}} \textit{n.} (\hyperlink{'kulkus}{'kulkus}+\allowbreak \hyperlink{tec}{tec})
Kyrgyzstan

\textbf{\hypertarget{'kulkustilip}{'kulkustilip}} \textit{n.} (\hyperlink{'kulkus}{'kulkus}+\allowbreak \hyperlink{tilip}{tilip})
Kyrgyz; the Kyrgyz language

\textbf{\hypertarget{'kulti}{'kulti}} \textit{n.} (Kur. ⟨{\arabics{}کورد‎}⟩ [kuɾd])
Kurd; the Kurdish people

\textbf{\hypertarget{'kultiak}{'kultiak}} \textit{n.} (\hyperlink{'kulti}{'kulti}+\allowbreak \hyperlink{ak}{ak})
Kurdish; of the Kurds

\textbf{\hypertarget{'kultitec}{'kultitec}} \textit{n.} (\hyperlink{'kulti}{'kulti}+\allowbreak \hyperlink{tec}{tec})
Kurdistan

\textbf{\hypertarget{'kultitilip}{'kultitilip}} \textit{n.} (\hyperlink{'kulti}{'kulti}+\allowbreak \hyperlink{tilip}{tilip})
Kurdish; the Kurdish language

\textbf{\hypertarget{kulpa}{kulpa}} \textit{v.} (ono. [glup a̤ː])
swallow; suck; consume whole; \hyperlink{kulpales}{ʟєꜱ} swallows \hyperlink{kulpalon}{ʟᴏᴧ}

\textbf{\hypertarget{kulpales}{kulpales}} \textit{n.} (\hyperlink{kulpa}{kulpa}+\allowbreak \hyperlink{les}{les})
swallower

\textbf{\hypertarget{kulpalon}{kulpalon}} \textit{n.} (\hyperlink{kulpa}{kulpa}+\allowbreak \hyperlink{lon}{lon})
swallowed

\textbf{\hypertarget{kunci}{kunci}} \textit{v.} (Cmn. ⟨{\chinese{}控制}⟩ [kʰʊŋ˥˩ʈ͡ʂɨ˥˩])
be in control; be in charge; be powerful; depend; \hyperlink{kuncilum}{ʟᴜᴍ} controls \hyperlink{kuncilon}{ʟᴏᴧ}

\textbf{\hypertarget{kuncilon}{kuncilon}} \textit{n.} (\hyperlink{kunci}{kunci}+\allowbreak \hyperlink{lon}{lon})
oppressed; dependent

\textbf{\hypertarget{kunciluat}{kunciluat}} \textit{n.} (\hyperlink{kunci}{kunci}+\allowbreak \hyperlink{luat}{luat})
controls; controller; harness

\textbf{\hypertarget{kuncilum}{kuncilum}} \textit{n.} (\hyperlink{kunci}{kunci}+\allowbreak \hyperlink{lum}{lum})
oppressor; controller; leader; official; in control; in charge; powerful

\textbf{\hypertarget{kunciki}{kunciki}} \textit{v.} (\hyperlink{kunci}{kunci}+\allowbreak \hyperlink{ki}{ki})
take control; capture; give control; put in charge; \hyperlink{kuncikiles}{ʟєꜱ} puts ʟᴜᴍ in control of \hyperlink{kuncikilon}{ʟᴏᴧ}

\textbf{\hypertarget{kuncikiles}{kuncikiles}} \textit{n.} (\hyperlink{kunciki}{kunciki}+\allowbreak \hyperlink{les}{les})
capturer

\textbf{\hypertarget{kuncikilon}{kuncikilon}} \textit{n.} (\hyperlink{kunciki}{kunciki}+\allowbreak \hyperlink{lon}{lon})
captured

\textbf{\hypertarget{kumna}{kumna}} \textit{v.} (Hin. ⟨{\devanagari{}घुमना}⟩ [ɡ̤umnaː])
spin; rotate; revolve; \hyperlink{kumnalon}{ʟᴏᴧ} is spinning about \hyperlink{kumnalum}{ʟᴜᴍ}

\textbf{\hypertarget{kumnalon}{kumnalon}} \textit{n.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{lon}{lon})
spinning

\textbf{\hypertarget{kumnalum}{kumnalum}} \textit{n.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{lum}{lum})
axis; centre

\textbf{\hypertarget{kumnanitoki}{kumnanitoki}} \textit{v.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{nitoki}{nitoki})
spiral in; ʟᴏᴧ spirals into ʟᴜᴍ

\textbf{\hypertarget{kumnanitokilip}{kumnanitokilip}} \textit{n.} (\hyperlink{kumnanitoki}{kumnanitoki}+\allowbreak \hyperlink{lip}{lip})
spiral

\textbf{\hypertarget{kumnamipmontalon}{kumnamipmontalon}} \textit{n.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{mipmontalon}{mipmontalon})
helicopter

\textbf{\hypertarget{kumnakulelyan}{kumnakulelyan}} \textit{n.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{kulelyan}{kulelyan})
spiral out; ʟᴏᴧ spirals outward from ʟᴜᴍ

\textbf{\hypertarget{kumnatupan}{kumnatupan}} \textit{n.} (\hyperlink{kumna}{kumna}+\allowbreak \hyperlink{tupan}{tupan})
hurricane; typhoon

\textbf{\hypertarget{kuho}{kuho}} \textit{v.} (\hyperlink{nice}{\sout{nice}})
be above; be up; be high; \hyperlink{kuholes}{ʟєꜱ} appears below \hyperlink{kuholon}{ʟᴏᴧ} from the point of view of ʟᴜᴍ

\textbf{\hypertarget{kuhol}{kuhol}} \textit{n.} (Fil. ⟨kuhol⟩ [kuhol])
slug; land slug; shell-less terrestrial gastropod mollusc

\textbf{\hypertarget{kuholes}{kuholes}} \textit{n.} (\hyperlink{kuho}{kuho}+\allowbreak \hyperlink{les}{les})
footer; bottom

\textbf{\hypertarget{kuholon}{kuholon}} \textit{n.} (\hyperlink{kuho}{kuho}+\allowbreak \hyperlink{lon}{lon})
above; up; high

\textbf{\hypertarget{kuhoki}{kuhoki}} \textit{v.} (\hyperlink{kuho}{kuho}+\allowbreak \hyperlink{ki}{ki})
go up; raise; rise; \hyperlink{kuhokiles}{ʟєꜱ} makes ʟᴏᴧ appear to move up from the point of view of ʟᴜᴍ

\textbf{\hypertarget{kuhokiles}{kuhokiles}} \textit{n.} (\hyperlink{kuhoki}{kuhoki}+\allowbreak \hyperlink{les}{les})
one who moves up

\textbf{\hypertarget{kuhokiluat}{kuhokiluat}} \textit{n.} (\hyperlink{kuhoki}{kuhoki}+\allowbreak \hyperlink{luat}{luat})
stool

\textbf{\hypertarget{kuci}{kuci}} \textit{v.} (Ben. ⟨{\bengali{}খুশি}⟩ [kʰuɕi])
be happy; be joyful; \hyperlink{kucilon}{ʟᴏᴧ} feels happy

\textbf{\hypertarget{kucilon}{kucilon}} \textit{n.} (\hyperlink{kuci}{kuci}+\allowbreak \hyperlink{lon}{lon})
happy; joyful

\textbf{\hypertarget{kucinihu}{kucinihu}} \textit{v.} (\hyperlink{kuci}{kuci}+\allowbreak \hyperlink{nihu}{nihu})
feel bittersweet; ʟᴏᴧ feels bittersweetly about \hyperlink{kucinihulum}{ʟᴜᴍ}

\textbf{\hypertarget{kucinihulum}{kucinihulum}} \textit{n.} (\hyperlink{kucinihu}{kucinihu}+\allowbreak \hyperlink{lum}{lum})
bittersweet

\textbf{\hypertarget{kuciki}{kuciki}} \textit{v.} (\hyperlink{kuci}{kuci}+\allowbreak \hyperlink{ki}{ki})
bring joy; brighten; ʟєꜱ makes ʟᴏᴧ happier

\textbf{\hypertarget{'kuskus}{'kuskus}} \textit{n.} (Ara. ⟨{\arabics{}كسكس}⟩ [kuskus])
couscous

\textbf{\hypertarget{'kukaylan}{'kukaylan}} \textit{n.} (Eng. ⟨Cook Islands⟩ [ˈkʊk ˈaɪləndz])
Cook Islands (archipelago)

\textbf{\hypertarget{'kukaylanak}{'kukaylanak}} \textit{n.} (\hyperlink{'kukaylan}{'kukaylan}+\allowbreak \hyperlink{ak}{ak})
Cook Island; Cook Islander; from the Cook Islands

\textbf{\hypertarget{'kukaylanwon}{'kukaylanwon}} \textit{n.} (\hyperlink{'kukaylan}{'kukaylan}+\allowbreak \hyperlink{won}{won})
Cook Islander; the Cook Islander people

\textbf{\hypertarget{'kukaylantec}{'kukaylantec}} \textit{n.} (\hyperlink{'kukaylan}{'kukaylan}+\allowbreak \hyperlink{tec}{tec})
Cook Islands (country)

\textbf{\hypertarget{'kukaylantilip}{'kukaylantilip}} \textit{n.} (\hyperlink{'kukaylan}{'kukaylan}+\allowbreak \hyperlink{tilip}{tilip})
Cook Islands Maori

\textbf{\hypertarget{kukam}{kukam}} \textit{n.} (ono. [ɡuː ɡaː])
baby; infant; newborn; very young and underdeveloped animal

\textbf{\hypertarget{kukamak}{kukamak}} \textit{n.} (\hyperlink{kukam}{kukam}+\allowbreak \hyperlink{ak}{ak})
infantile

\textbf{\hypertarget{kuki}{kuki}} \textit{v.} (\hyperlink{ku}{ku}+\allowbreak \hyperlink{ki}{ki})
bitter; ʟєꜱ makes ʟᴏᴧ become bitter

\textbf{\hypertarget{kukulik}{kukulik}} \textit{n.} (ono. [kuk kurikoː])
chicken; chick; junglefowl; Gallus

\textbf{\hypertarget{kuti}{kuti}} \textit{v.} (Cmn. ⟨{\chinese{}固体}⟩ [ku˥˩tʰi˧˩˧])
be solid; be coherent; be coagulated; \hyperlink{kutilon}{ʟᴏᴧ} is solid

\textbf{\hypertarget{kutilon}{kutilon}} \textit{n.} (\hyperlink{kuti}{kuti}+\allowbreak \hyperlink{lon}{lon})
solid; coherent; coagulated

\textbf{\hypertarget{kutilyan}{kutilyan}} \textit{n.} (\hyperlink{kuti}{kuti}+\allowbreak \hyperlink{lyan}{lyan})
solidity; rigidity

\textbf{\hypertarget{kutimwoni}{kutimwoni}} \textit{v.} (\hyperlink{kuti}{kuti}+\allowbreak \hyperlink{mwoni}{mwoni})
sculpt; etch; carve; \hyperlink{kutimwoniles}{ʟєꜱ} carves \hyperlink{kutimwonilum}{ʟᴜᴍ} as \hyperlink{kutimwonilon}{ʟᴏᴧ}

\textbf{\hypertarget{kutimwoniles}{kutimwoniles}} \textit{n.} (\hyperlink{kutimwoni}{kutimwoni}+\allowbreak \hyperlink{les}{les})
carver

\textbf{\hypertarget{kutimwonilon}{kutimwonilon}} \textit{n.} (\hyperlink{kutimwoni}{kutimwoni}+\allowbreak \hyperlink{lon}{lon})
sculpture

\textbf{\hypertarget{kutimwonilum}{kutimwonilum}} \textit{n.} (\hyperlink{kutimwoni}{kutimwoni}+\allowbreak \hyperlink{lum}{lum})
sculpture subject

\textbf{\hypertarget{kutihila}{kutihila}} \textit{v.} (\hyperlink{kuti}{kuti}+\allowbreak \hyperlink{hila}{hila})
dig; \hyperlink{kutihilalon}{ʟᴏᴧ} digs

\textbf{\hypertarget{kutihilalon}{kutihilalon}} \textit{n.} (\hyperlink{kutihila}{kutihila}+\allowbreak \hyperlink{lon}{lon})
digger

\textbf{\hypertarget{kutiki}{kutiki}} \textit{v.} (\hyperlink{kuti}{kuti}+\allowbreak \hyperlink{ki}{ki})
freeze; solidify; deposit; \hyperlink{kutikiles}{ʟєꜱ} freezes \hyperlink{kutikilon}{ʟᴏᴧ}

\textbf{\hypertarget{kutikiles}{kutikiles}} \textit{n.} (\hyperlink{kutiki}{kutiki}+\allowbreak \hyperlink{les}{les})
freezer

\textbf{\hypertarget{kutikilon}{kutikilon}} \textit{n.} (\hyperlink{kutiki}{kutiki}+\allowbreak \hyperlink{lon}{lon})
frozen; ice

\textbf{\hypertarget{'kupa}{'kupa}} \textit{n.} (Spa. ⟨Cuba⟩ [kuβa])
Cuba (island)

\textbf{\hypertarget{'kupaak}{'kupaak}} \textit{n.} (\hyperlink{'kupa}{'kupa}+\allowbreak \hyperlink{ak}{ak})
Cuban; from Cuba

\textbf{\hypertarget{'kupawon}{'kupawon}} \textit{n.} (\hyperlink{'kupa}{'kupa}+\allowbreak \hyperlink{won}{won})
Cuban; the Cuban people

\textbf{\hypertarget{'kupatec}{'kupatec}} \textit{n.} (\hyperlink{'kupa}{'kupa}+\allowbreak \hyperlink{tec}{tec})
Cuba; the Republic of Cuba

\textbf{\hypertarget{kwe}{kwe}} \textit{v.} (\hyperlink{nyo}{\sout{nyo}})
yes; be true; be right; be correct; be real; be happening; \textit{positive}; \hyperlink{kwelon}{ʟᴏᴧ} is happening

\textbf{\hypertarget{kwelayf}{kwelayf}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{layf}{layf})
condition; world

\textbf{\hypertarget{kwelayfak}{kwelayfak}} \textit{n.} (\hyperlink{kwelayf}{kwelayf}+\allowbreak \hyperlink{ak}{ak})
conditional (linguistics)

\textbf{\hypertarget{kwelon}{kwelon}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lon}{lon})
state; truth; reality; true; right; correct; real; happening

\textbf{\hypertarget{kwelial}{kwelial}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lial}{lial})
cause; inciting event; at fault; responsible

\textbf{\hypertarget{kwelialak}{kwelialak}} \textit{n.} (\hyperlink{kwelial}{kwelial}+\allowbreak \hyperlink{ak}{ak})
causal (linguistics)

\textbf{\hypertarget{kwelip}{kwelip}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lip}{lip})
method; way; path; manner

\textbf{\hypertarget{kwelipak}{kwelipak}} \textit{n.} (\hyperlink{kwelip}{kwelip}+\allowbreak \hyperlink{ak}{ak})
methodical; formal; instructive (linguistics)

\textbf{\hypertarget{kweluat}{kweluat}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{luat}{luat})
tool; medium; instrument

\textbf{\hypertarget{kweluatak}{kweluatak}} \textit{n.} (\hyperlink{kweluat}{kweluat}+\allowbreak \hyperlink{ak}{ak})
instrumental; prolative (linguistics)

\textbf{\hypertarget{kwelyan}{kwelyan}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lyan}{lyan})
amount; number; quantity; extent; magnitude

\textbf{\hypertarget{kwelyanak}{kwelyanak}} \textit{n.} (\hyperlink{kwelyan}{kwelyan}+\allowbreak \hyperlink{ak}{ak})
numerical; quantitative; equative

\textbf{\hypertarget{kwelyansoma}{kwelyansoma}} \textit{v.} (\hyperlink{kwelyan}{kwelyan}+\allowbreak \hyperlink{soma}{soma})
do math; do maths; \hyperlink{kwelyansomales}{ʟєꜱ} studies numbers to learn about \hyperlink{kwelyansomalon}{ʟᴏᴧ}

\textbf{\hypertarget{kwelyansomales}{kwelyansomales}} \textit{n.} (\hyperlink{kwelyansoma}{kwelyansoma}+\allowbreak \hyperlink{les}{les})
mathematician

\textbf{\hypertarget{kwelyansomalon}{kwelyansomalon}} \textit{n.} (\hyperlink{kwelyansoma}{kwelyansoma}+\allowbreak \hyperlink{lon}{lon})
mathematics

\textbf{\hypertarget{kwelyot}{kwelyot}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lyot}{lyot})
location; place; space

\textbf{\hypertarget{kwelyotestalyan}{kwelyotestalyan}} \textit{n.} (\hyperlink{kwelyot}{kwelyot}+\allowbreak \hyperlink{estalyan}{estalyan})
address

\textbf{\hypertarget{kwelyotak}{kwelyotak}} \textit{n.} (\hyperlink{kwelyot}{kwelyot}+\allowbreak \hyperlink{ak}{ak})
spacial; locative (linguistics)

\textbf{\hypertarget{kwelwel}{kwelwel}} \textit{n.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{lwel}{lwel})
time; date; instance

\textbf{\hypertarget{kwelwelesta}{kwelwelesta}} \textit{v.} (\hyperlink{kwelwel}{kwelwel}+\allowbreak \hyperlink{esta}{esta})
be available; be free; \hyperlink{kwelwelestalon}{ʟᴏᴧ} has nothing scheduled

\textbf{\hypertarget{kwelwelestalon}{kwelwelestalon}} \textit{n.} (\hyperlink{kwelwelesta}{kwelwelesta}+\allowbreak \hyperlink{lon}{lon})
available; free

\textbf{\hypertarget{kwelwelestanyo}{kwelwelestanyo}} \textit{v.} (\hyperlink{kwelwelesta}{kwelwelesta}+\allowbreak \hyperlink{nyo}{nyo})
be busy; be unavailable; \hyperlink{kwelwelestanyolon}{ʟᴏᴧ} has things scheduled

\textbf{\hypertarget{kwelwelestanyolon}{kwelwelestanyolon}} \textit{n.} (\hyperlink{kwelwelestanyo}{kwelwelestanyo}+\allowbreak \hyperlink{lon}{lon})
busy; unavailable

\textbf{\hypertarget{kwelwelak}{kwelwelak}} \textit{n.} (\hyperlink{kwelwel}{kwelwel}+\allowbreak \hyperlink{ak}{ak})
temporal; dative (linguistics)

\textbf{\hypertarget{kwelwelmontalon}{kwelwelmontalon}} \textit{n.} (\hyperlink{kwelwel}{kwelwel}+\allowbreak \hyperlink{montalon}{montalon})
time machine

\textbf{\hypertarget{kwelwelhila}{kwelwelhila}} \textit{v.} (\hyperlink{kwelwel}{kwelwel}+\allowbreak \hyperlink{hila}{hila})
time travel; ʟᴏᴧ travels through time

\textbf{\hypertarget{'kwenatin}{'kwenatin}} \textit{n.} (Svc. ⟨Grenadines⟩ [ɡɹɛnədiːnz])
Grenadines; Grenadine Islands

\textbf{\hypertarget{'kwenatinak}{'kwenatinak}} \textit{n.} (\hyperlink{'kwenatin}{'kwenatin}+\allowbreak \hyperlink{ak}{ak})
Grenadinese; from the Grenadines

\textbf{\hypertarget{kwenoki}{kwenoki}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{noki}{noki})
prove; verify; log in; ʟєꜱ verifies ʟᴏᴧ’s veracity

\textbf{\hypertarget{kwenu}{kwenu}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{nu}{nu})
undo; ʟᴏᴧ happens in reverse

\textbf{\hypertarget{kwenyokwenyo}{kwenyokwenyo}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{kwe}{kwe}+\allowbreak \hyperlink{nyo}{nyo})
alternate; be every-other; \hyperlink{kwenyokwenyolon}{ʟᴏᴧ} exists in an alternating pattern

\textbf{\hypertarget{kwenyokwenyolon}{kwenyokwenyolon}} \textit{n.} (\hyperlink{kwenyokwenyo}{kwenyokwenyo}+\allowbreak \hyperlink{lon}{lon})
checkerboard; every-other

\textbf{\hypertarget{kweh}{kweh}} \textit{n.} (Cmn. ⟨{\chinese{}龟}⟩ [kweɪ̯˥])
turtle; tortoise; terrapin; Testudine

\textbf{\hypertarget{kweki}{kweki}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{ki}{ki})
do; happen; cause; pro-verb; \hyperlink{kwekiles}{ʟєꜱ} makes \hyperlink{kwekilon}{ʟᴏᴧ} come true to \hyperlink{kwekilum}{ʟᴜᴍ}

\textbf{\hypertarget{kwekiles}{kwekiles}} \textit{n.} (\hyperlink{kweki}{kweki}+\allowbreak \hyperlink{les}{les})
agent; participant

\textbf{\hypertarget{kwekilesak}{kwekilesak}} \textit{n.} (\hyperlink{kwekiles}{kwekiles}+\allowbreak \hyperlink{ak}{ak})
agentive

\textbf{\hypertarget{kwekilon}{kwekilon}} \textit{n.} (\hyperlink{kweki}{kweki}+\allowbreak \hyperlink{lon}{lon})
effect; patient (linguistics); experiencer (linguistics)

\textbf{\hypertarget{kwekilonak}{kwekilonak}} \textit{n.} (\hyperlink{kwekilon}{kwekilon}+\allowbreak \hyperlink{ak}{ak})
patientive (linguistics)

\textbf{\hypertarget{kwekilum}{kwekilum}} \textit{n.} (\hyperlink{kweki}{kweki}+\allowbreak \hyperlink{lum}{lum})
theme (linguistics); stimulus (linguistics); recipient (linguistics)

\textbf{\hypertarget{kwekilumak}{kwekilumak}} \textit{n.} (\hyperlink{kwekilum}{kwekilum}+\allowbreak \hyperlink{ak}{ak})
thematic (linguistics)

\textbf{\hypertarget{kwekimai}{kwekimai}} \textit{v.} (\hyperlink{kweki}{kweki}+\allowbreak \hyperlink{mai}{mai})
buy service; serve; \hyperlink{kwekimailon}{ʟᴏᴧ} performs \hyperlink{kwekimailum}{ʟᴜᴍ} for \hyperlink{kwekimailes}{ʟєꜱ} in exchange for money

\textbf{\hypertarget{kwekimailes}{kwekimailes}} \textit{n.} (\hyperlink{kwekimai}{kwekimai}+\allowbreak \hyperlink{les}{les})
customer

\textbf{\hypertarget{kwekimailon}{kwekimailon}} \textit{n.} (\hyperlink{kwekimai}{kwekimai}+\allowbreak \hyperlink{lon}{lon})
server

\textbf{\hypertarget{kwekimailum}{kwekimailum}} \textit{n.} (\hyperlink{kwekimai}{kwekimai}+\allowbreak \hyperlink{lum}{lum})
service

\textbf{\hypertarget{kwekimailwel}{kwekimailwel}} \textit{n.} (\hyperlink{kwekimai}{kwekimai}+\allowbreak \hyperlink{lwel}{lwel})
service

\textbf{\hypertarget{'kwet}{'kwet}} \textit{n.} (Ara. ⟨{\arabics{}كويت}⟩ [kweːt])
Kuwait

\textbf{\hypertarget{'kwetak}{'kwetak}} \textit{n.} (\hyperlink{'kwet}{'kwet}+\allowbreak \hyperlink{ak}{ak})
Kuwaiti; from Kuwait

\textbf{\hypertarget{kweti}{kweti}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{ti}{ti})
tell the truth; be honest; ʟєꜱ expresses \hyperlink{kwetilon}{ʟᴏᴧ}, which they think to be true

\textbf{\hypertarget{kwetilon}{kwetilon}} \textit{n.} (\hyperlink{kweti}{kweti}+\allowbreak \hyperlink{lon}{lon})
the truth; truth; honest

\textbf{\hypertarget{kwetilyan}{kwetilyan}} \textit{n.} (\hyperlink{kweti}{kweti}+\allowbreak \hyperlink{lyan}{lyan})
honesty; integrity

\textbf{\hypertarget{kwetikolwa}{kwetikolwa}} \textit{v.} (\hyperlink{kweti}{kweti}+\allowbreak \hyperlink{kolwa}{kolwa})
trust; find trustworthy; ʟᴏᴧ trusts ʟᴜᴍ

\textbf{\hypertarget{'kwetwon}{'kwetwon}} \textit{n.} (\hyperlink{'kwet}{'kwet}+\allowbreak \hyperlink{won}{won})
Kuwaiti; the Kuwaiti people

\textbf{\hypertarget{kwepensi}{kwepensi}} \textit{v.} (\hyperlink{kwe}{kwe}+\allowbreak \hyperlink{pensi}{pensi})
be correct; be right; \hyperlink{kwepensilon}{ʟᴏᴧ} thinks ʟᴜᴍ to be true, and it is

\textbf{\hypertarget{kwepensilon}{kwepensilon}} \textit{n.} (\hyperlink{kwepensi}{kwepensi}+\allowbreak \hyperlink{lon}{lon})
correct; right

\textbf{\hypertarget{kwepensiki}{kwepensiki}} \textit{v.} (\hyperlink{kwepensi}{kwepensi}+\allowbreak \hyperlink{ki}{ki})
correct; right; rectify; ʟєꜱ corrects ʟᴏᴧ’s view of \hyperlink{kwepensikilum}{ʟᴜᴍ}

\textbf{\hypertarget{kwepensikilum}{kwepensikilum}} \textit{n.} (\hyperlink{kwepensiki}{kwepensiki}+\allowbreak \hyperlink{lum}{lum})
correction

\textbf{\hypertarget{kwan}{kwan}} \textit{n.} (Cmn. ⟨{\chinese{}光}⟩ [kwɑŋ˥])
light; electromagnetic radiation

\textbf{\hypertarget{'kwaneyta}{'kwaneyta}} \textit{n.} (Eng. ⟨Grenada⟩ [ɡɹʷəˈneɪ̯də])
Grenada (landmass)

\textbf{\hypertarget{'kwaneytaak}{'kwaneytaak}} \textit{n.} (\hyperlink{'kwaneyta}{'kwaneyta}+\allowbreak \hyperlink{ak}{ak})
Grenadan; from Grenada

\textbf{\hypertarget{'kwaneytawon}{'kwaneytawon}} \textit{n.} (\hyperlink{'kwaneyta}{'kwaneyta}+\allowbreak \hyperlink{won}{won})
Grenadan; the Grenadan people

\textbf{\hypertarget{'kwaneytatec}{'kwaneytatec}} \textit{n.} (\hyperlink{'kwaneyta}{'kwaneyta}+\allowbreak \hyperlink{tec}{tec})
Grenada (country)

\textbf{\hypertarget{kwanak}{kwanak}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{ak}{ak})
photic; optic; luminescient

\textbf{\hypertarget{kwanilukiles}{kwanilukiles}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{ilukiles}{ilukiles})
lens

\textbf{\hypertarget{kwanlamanoluat}{kwanlamanoluat}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{lama}{lama}+\allowbreak \hyperlink{noluat}{noluat})
spectrometer

\textbf{\hypertarget{kwanmwonilum}{kwanmwonilum}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{mwonilum}{mwonilum})
light; light source

\textbf{\hypertarget{kwansica}{kwansica}} \textit{v.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{sica}{sica})
be dim; be dark; \hyperlink{kwansicalon}{ʟᴏᴧ} is dimly lit

\textbf{\hypertarget{kwansicalon}{kwansicalon}} \textit{n.} (\hyperlink{kwansica}{kwansica}+\allowbreak \hyperlink{lon}{lon})
shadow; dim; dark

\textbf{\hypertarget{kwansicaki}{kwansicaki}} \textit{v.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{sicaki}{sicaki})
darken; dim; ʟєꜱ darkens ʟᴏᴧ

\textbf{\hypertarget{kwanfuha}{kwanfuha}} \textit{v.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{fuha}{fuha})
be lit; be illuminated; be bright; \hyperlink{kwanfuhalon}{ʟᴏᴧ} is brightly lit

\textbf{\hypertarget{kwanfuhalon}{kwanfuhalon}} \textit{n.} (\hyperlink{kwanfuha}{kwanfuha}+\allowbreak \hyperlink{lon}{lon})
lit; illuminated; bright

\textbf{\hypertarget{kwanfuhaki}{kwanfuhaki}} \textit{v.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{fuhaki}{fuhaki})
illuminate; light up; ʟєꜱ illuminates ʟᴏᴧ

\textbf{\hypertarget{kwanpes}{kwanpes}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{pes}{pes})
anglerfish

\textbf{\hypertarget{kwanpic}{kwanpic}} \textit{n.} (\hyperlink{kwan}{kwan}+\allowbreak \hyperlink{pic}{pic})
candlenut; candleberry; Indian walnut; kukui nut tree; Aleurites moluccanus

\textbf{\hypertarget{kwah}{kwah}} \textit{n.} (Cmn. ⟨{\chinese{}瓜}⟩ [kwa˥])
melon; any member of Cucurbitaceae with sweet, fleshy fruit

\textbf{\hypertarget{kwakwak}{kwakwak}} \textit{n.} (ono. [kwak kwak])
frog; toad; Anura

\textbf{\hypertarget{kwakwaklisat}{kwakwaklisat}} \textit{n.} (\hyperlink{kwakwak}{kwakwak}+\allowbreak \hyperlink{lisat}{lisat})
salamander

\textbf{\hypertarget{'kwatemala}{'kwatemala}} \textit{n.} (Spa. ⟨Guatemala⟩ [gwateˈmala])
Guatemala

\textbf{\hypertarget{'kwatemalaak}{'kwatemalaak}} \textit{n.} (\hyperlink{'kwatemala}{'kwatemala}+\allowbreak \hyperlink{ak}{ak})
Guatemalan; from Guatemala

\textbf{\hypertarget{'kwatemalawon}{'kwatemalawon}} \textit{n.} (\hyperlink{'kwatemala}{'kwatemala}+\allowbreak \hyperlink{won}{won})
Guatemalan; the Guatemalan people

\textbf{\hypertarget{kwap}{kwap}} \textit{n.} (Eng. ⟨crab⟩ [kʰɹʷæb])
crustacean; crab; lobster; crayfish; shrimp; prawn; krill; Crustacea

\textbf{\hypertarget{'kwonsaw}{'kwonsaw}} \textit{n.} (Yue. ⟨{\chinese{}广州}⟩ [kʷɔ˧˥ːŋt͡sɐw˥])
Guangzhou;Canton; Kwangchow

\textbf{\hypertarget{'kwontun}{'kwontun}} \textit{n.} (Yue. ⟨{\chinese{}廣東}⟩ [kʷɔ̌ːŋ tʊ́ŋ])
Guangdong; Canton Province

\textbf{\hypertarget{'kwontunak}{'kwontunak}} \textit{n.} (\hyperlink{'kwontun}{'kwontun}+\allowbreak \hyperlink{ak}{ak})
Yue; in Yue

\textbf{\hypertarget{'kwontuntilip}{'kwontuntilip}} \textit{n.} (\hyperlink{'kwontun}{'kwontun}+\allowbreak \hyperlink{tilip}{tilip})
Yue Chinese; Cantonese

\section{T}

\textbf{\hypertarget{te}{te}} \textit{v.} (Ibo. ⟨de⟩ [de])
write; record; type; mark; save; transcribe; \hyperlink{teles}{ʟєꜱ} encodes \hyperlink{telum}{ʟᴜᴍ} physically on \hyperlink{telon}{ʟᴏᴧ}

\textbf{\hypertarget{teak}{teak}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{ak}{ak})
literary; scriptural

\textbf{\hypertarget{teles}{teles}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{les}{les})
writer

\textbf{\hypertarget{telon}{telon}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{lon}{lon})
record; book; paper; file

\textbf{\hypertarget{telonmailyot}{telonmailyot}} \textit{n.} (\hyperlink{telon}{telon}+\allowbreak \hyperlink{mailyot}{mailyot})
bookstore

\textbf{\hypertarget{telip}{telip}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{lip}{lip})
script; writing system; encoding

\textbf{\hypertarget{teluat}{teluat}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{luat}{luat})
writing utensil

\textbf{\hypertarget{telum}{telum}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{lum}{lum})
text; writing; passage; data; article; note

\textbf{\hypertarget{teluca}{teluca}} \textit{v.} (Msa. ⟨teruja⟩ [terud͡ʒa])
be excited; be interested; be hype; \hyperlink{telucalon}{ʟᴏᴧ} is excited about \hyperlink{telucalum}{ʟᴜᴍ}

\textbf{\hypertarget{telucalon}{telucalon}} \textit{n.} (\hyperlink{teluca}{teluca}+\allowbreak \hyperlink{lon}{lon})
excited; interested; hype

\textbf{\hypertarget{telucalum}{telucalum}} \textit{n.} (\hyperlink{teluca}{teluca}+\allowbreak \hyperlink{lum}{lum})
exciting

\textbf{\hypertarget{telucaki}{telucaki}} \textit{v.} (\hyperlink{teluca}{teluca}+\allowbreak \hyperlink{ki}{ki})
excite; interest; ʟєꜱ gets ʟᴏᴧ excited about ʟᴜᴍ

\textbf{\hypertarget{'teluku}{'teluku}} \textit{n.} (Tel. ⟨{\telugu{}తెలుగు}⟩ [t̪el̪uɡu])
Telugu; Telugu vaaru; the Telugu people

\textbf{\hypertarget{'telukuak}{'telukuak}} \textit{n.} (\hyperlink{'teluku}{'teluku}+\allowbreak \hyperlink{ak}{ak})
Telugu; of the Telugu

\textbf{\hypertarget{'telukutilip}{'telukutilip}} \textit{n.} (\hyperlink{'teluku}{'teluku}+\allowbreak \hyperlink{tilip}{tilip})
Telugu; the Telugu language

\textbf{\hypertarget{telyot}{telyot}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{lyot}{lyot})
desk; writing surface

\textbf{\hypertarget{tewi}{tewi}} \textit{v.} (Epo. ⟨devi⟩ [ˈdevi])
must; have to; be responsible; be obligated; \hyperlink{tewilon}{ʟᴏᴧ} is obligated to make \hyperlink{tewilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{tewilon}{tewilon}} \textit{n.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{lon}{lon})
responsible; obligated

\textbf{\hypertarget{tewilum}{tewilum}} \textit{n.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{lum}{lum})
obligation; duty; responsibility; rule

\textbf{\hypertarget{tewinu}{tewinu}} \textit{v.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{nu}{nu})
alleviate responsibility; unassign; deobligate; ʟєꜱ makes ʟᴏᴧ no longer responsible for ʟᴜᴍ happening

\textbf{\hypertarget{tewinyo}{tewinyo}} \textit{v.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{nyo}{nyo})
not have to; may not; ʟᴏᴧ does not have to make ʟᴜᴍ happen

\textbf{\hypertarget{tewicitu}{tewicitu}} \textit{v.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{citu}{citu})
be timely; be on time; \hyperlink{tewicitulon}{ʟᴏᴧ} is at the correct time

\textbf{\hypertarget{tewicitulon}{tewicitulon}} \textit{n.} (\hyperlink{tewicitu}{tewicitu}+\allowbreak \hyperlink{lon}{lon})
timely; on time

\textbf{\hypertarget{tewiki}{tewiki}} \textit{v.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{ki}{ki})
assign; obligate; require; \hyperlink{tewikiles}{ʟєꜱ} makes ʟᴏᴧ responsible for ʟᴜᴍ happening

\textbf{\hypertarget{tewikiles}{tewikiles}} \textit{n.} (\hyperlink{tewiki}{tewiki}+\allowbreak \hyperlink{les}{les})
assigner

\textbf{\hypertarget{tewikunci}{tewikunci}} \textit{v.} (\hyperlink{tewi}{tewi}+\allowbreak \hyperlink{kunci}{kunci})
be in prison; be incarcerated; \hyperlink{tewikuncilon}{ʟᴏᴧ} is imprisoned by \hyperlink{tewikuncilum}{ʟᴜᴍ}

\textbf{\hypertarget{tewikuncilon}{tewikuncilon}} \textit{n.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{lon}{lon})
prisoner; in prison; incarcerated

\textbf{\hypertarget{tewikuncilum}{tewikuncilum}} \textit{n.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{lum}{lum})
warden

\textbf{\hypertarget{tewikuncilyot}{tewikuncilyot}} \textit{n.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{lyot}{lyot})
prison; jail

\textbf{\hypertarget{tewikuncinu}{tewikuncinu}} \textit{v.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{nu}{nu})
release from prison; set free; ʟєꜱ releases ʟᴏᴧ from prison

\textbf{\hypertarget{tewikuncinyo}{tewikuncinyo}} \textit{v.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{nyo}{nyo})
be at large; be free; be out of prison; \hyperlink{tewikuncinyolon}{ʟᴏᴧ} is not imprisoned by ʟᴜᴍ

\textbf{\hypertarget{tewikuncinyolon}{tewikuncinyolon}} \textit{n.} (\hyperlink{tewikuncinyo}{tewikuncinyo}+\allowbreak \hyperlink{lon}{lon})
at large; free; out of prison

\textbf{\hypertarget{tewikunciki}{tewikunciki}} \textit{v.} (\hyperlink{tewikunci}{tewikunci}+\allowbreak \hyperlink{ki}{ki})
imprison; throw in jail; ʟєꜱ imprisons ʟᴏᴧ

\textbf{\hypertarget{'tenim}{'tenim}} \textit{n.} (Eng. ⟨denim⟩ [ˈdɛnəm])
denim

\textbf{\hypertarget{tenso}{tenso}} \textit{v.} (Spa. ⟨tenso⟩ [ˈtenso])
be tense; be intense; be under pressure; \hyperlink{tensolon}{ʟᴏᴧ} is under pressure

\textbf{\hypertarget{tensolon}{tensolon}} \textit{n.} (\hyperlink{tenso}{tenso}+\allowbreak \hyperlink{lon}{lon})
tense; intense; under pressure

\textbf{\hypertarget{tensolyan}{tensolyan}} \textit{n.} (\hyperlink{tenso}{tenso}+\allowbreak \hyperlink{lyan}{lyan})
pressure

\textbf{\hypertarget{tensonoluat}{tensonoluat}} \textit{n.} (\hyperlink{tenso}{tenso}+\allowbreak \hyperlink{noluat}{noluat})
barometer

\textbf{\hypertarget{tensoki}{tensoki}} \textit{v.} (\hyperlink{tenso}{tenso}+\allowbreak \hyperlink{ki}{ki})
tense up; intensify; pressurise; ʟєꜱ puts ʟᴏᴧ under pressure

\textbf{\hypertarget{'temoklat}{'temoklat}} \textit{n.} (Eng. ⟨democrat⟩ [ˈdɛməkɹʷæt])
Democratic Party (United States)

\textbf{\hypertarget{tehwok}{tehwok}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{hwok}{hwok})
paper; piece of paper; sheet of paper

\textbf{\hypertarget{tehwokti}{tehwokti}} \textit{v.} (\hyperlink{tehwok}{tehwok}+\allowbreak \hyperlink{ti}{ti})
mail; send letter; \hyperlink{tehwoktiles}{ʟєꜱ} sends \hyperlink{tehwoktilum}{ʟᴜᴍ} to \hyperlink{tehwoktilon}{ʟᴏᴧ} as a letter

\textbf{\hypertarget{tehwoktiles}{tehwoktiles}} \textit{n.} (\hyperlink{tehwokti}{tehwokti}+\allowbreak \hyperlink{les}{les})
sender of a letter

\textbf{\hypertarget{tehwoktilon}{tehwoktilon}} \textit{n.} (\hyperlink{tehwokti}{tehwokti}+\allowbreak \hyperlink{lon}{lon})
recipient of a letter

\textbf{\hypertarget{tehwoktilum}{tehwoktilum}} \textit{n.} (\hyperlink{tehwokti}{tehwokti}+\allowbreak \hyperlink{lum}{lum})
letter

\textbf{\hypertarget{tec}{tec}} \textit{n.} (Hin. ⟨{\devanagari{}देश}⟩ [deʃ])
state; country; polity; politically independent group of people

\textbf{\hypertarget{tecak}{tecak}} \textit{n.} (\hyperlink{tec}{tec}+\allowbreak \hyperlink{ak}{ak})
political; national; federal

\textbf{\hypertarget{teclwa}{teclwa}} \textit{v.} (\hyperlink{tec}{tec}+\allowbreak \hyperlink{lwa}{lwa})
be at war; \hyperlink{teclwalon}{ʟᴏᴧ} is at war with \hyperlink{teclwalum}{ʟᴜᴍ}

\textbf{\hypertarget{teclwalon}{teclwalon}} \textit{n.} (\hyperlink{teclwa}{teclwa}+\allowbreak \hyperlink{lon}{lon})
at war

\textbf{\hypertarget{teclwalum}{teclwalum}} \textit{n.} (\hyperlink{teclwa}{teclwa}+\allowbreak \hyperlink{lum}{lum})
belligerent

\textbf{\hypertarget{teclwanu}{teclwanu}} \textit{v.} (\hyperlink{teclwa}{teclwa}+\allowbreak \hyperlink{nu}{nu})
make peace; make truce; ceasefire; end war; ʟєꜱ causes ʟᴏᴧ to stop being at war with ʟᴜᴍ

\textbf{\hypertarget{teclwanyo}{teclwanyo}} \textit{v.} (\hyperlink{tec}{tec}+\allowbreak \hyperlink{lwa}{lwa}+\allowbreak \hyperlink{nyo}{nyo})
be at peace; \hyperlink{teclwanyolon}{ʟᴏᴧ} is at peace with \hyperlink{teclwanyolum}{ʟᴜᴍ}

\textbf{\hypertarget{teclwanyolon}{teclwanyolon}} \textit{n.} (\hyperlink{teclwanyo}{teclwanyo}+\allowbreak \hyperlink{lon}{lon})
at peace

\textbf{\hypertarget{teclwanyolum}{teclwanyolum}} \textit{n.} (\hyperlink{teclwanyo}{teclwanyo}+\allowbreak \hyperlink{lum}{lum})
non-belligerent

\textbf{\hypertarget{teclwaki}{teclwaki}} \textit{v.} (\hyperlink{teclwa}{teclwa}+\allowbreak \hyperlink{ki}{ki})
wage war; declare war; invade; \hyperlink{teclwakiles}{ʟєꜱ} causes ʟᴏᴧ to go to war with \hyperlink{teclwakilum}{ʟᴜᴍ}

\textbf{\hypertarget{teclwakiles}{teclwakiles}} \textit{n.} (\hyperlink{teclwaki}{teclwaki}+\allowbreak \hyperlink{les}{les})
aggressor; warmonger

\textbf{\hypertarget{teclwakilum}{teclwakilum}} \textit{n.} (\hyperlink{teclwaki}{teclwaki}+\allowbreak \hyperlink{lum}{lum})
defender

\textbf{\hypertarget{tecwelon}{tecwelon}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{cwelon}{cwelon})
ink

\textbf{\hypertarget{tecsota}{tecsota}} \textit{v.} (\hyperlink{tec}{tec}+\allowbreak \hyperlink{sota}{sota})
have treaty; \hyperlink{tecsotalon}{ʟᴏᴧ} has a treaty with \hyperlink{tecsotalum}{ʟᴜᴍ}

\textbf{\hypertarget{tecsotalon}{tecsotalon}} \textit{n.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{lon}{lon})
contracting party

\textbf{\hypertarget{tecsotalip}{tecsotalip}} \textit{n.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{lip}{lip})
treaty; deal; international agreement

\textbf{\hypertarget{tecsotalum}{tecsotalum}} \textit{n.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{lum}{lum})
ally; trading partner

\textbf{\hypertarget{tecsotalwel}{tecsotalwel}} \textit{n.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{lwel}{lwel})
diplomacy

\textbf{\hypertarget{tecsotanu}{tecsotanu}} \textit{v.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{nu}{nu})
break treaty; expire; violate agreement; ʟєꜱ terminates a treaty between ʟᴏᴧ and ʟᴜᴍ

\textbf{\hypertarget{tecsotaki}{tecsotaki}} \textit{v.} (\hyperlink{tecsota}{tecsota}+\allowbreak \hyperlink{ki}{ki})
strike treaty; \hyperlink{tecsotakiles}{ʟєꜱ} sets up a treaty between ʟᴏᴧ and ʟᴜᴍ

\textbf{\hypertarget{tecsotakiles}{tecsotakiles}} \textit{n.} (\hyperlink{tecsotaki}{tecsotaki}+\allowbreak \hyperlink{les}{les})
diplomat; ambassador

\textbf{\hypertarget{tes}{tes}} \textit{num.} (Spa. ⟨diez⟩ [djes])
A; ten; only used for duodecimal and hexadecimal

\textbf{\hypertarget{tesak}{tesak}} \textit{n.} (\hyperlink{tes}{tes}+\allowbreak \hyperlink{ak}{ak})
tenth

\textbf{\hypertarget{'tekila}{'tekila}} \textit{n.} (Spa. ⟨tequila⟩ [teˈkila])
tequila

\textbf{\hypertarget{'tekwanto}{'tekwanto}} \textit{n.} (Kor. ⟨{\korean{}태권도}⟩ [tʰɛ.k͈wʌn.do])
Taekwondo

\textbf{\hypertarget{tepaltolon}{tepaltolon}} \textit{n.} (\hyperlink{te}{te}+\allowbreak \hyperlink{paltolon}{paltolon})
glyph; character; letter; grapheme

\textbf{\hypertarget{tepaltolonoltolum}{tepaltolonoltolum}} \textit{n.} (\hyperlink{tepaltolon}{tepaltolon}+\allowbreak \hyperlink{oltolum}{oltolum})
alphabet; syllabary

\textbf{\hypertarget{tepaltolonoltolumak}{tepaltolonoltolumak}} \textit{n.} (\hyperlink{tepaltolonoltolum}{tepaltolonoltolum}+\allowbreak \hyperlink{ak}{ak})
alphabetical

\textbf{\hypertarget{tepato}{tepato}} \textit{v.} (\hyperlink{te}{te}+\allowbreak \hyperlink{pato}{pato})
be graphite \hyperlink{tepatolon}{ʟᴏᴧ} is made of graphite

\textbf{\hypertarget{tepatolon}{tepatolon}} \textit{n.} (\hyperlink{tepato}{tepato}+\allowbreak \hyperlink{lon}{lon})
graphite ʟᴏᴧ is made of graphite

\textbf{\hypertarget{ta}{ta}} \textit{v.} (Cmn. ⟨{\chinese{}打}⟩ [ta˧˩˧])
hit; strike; collide; ʟєꜱ hits ʟᴏᴧ

\textbf{\hypertarget{'ta}{'ta}} \textit{n.} (ono. [t])
t; /t/; alveolar plosive

\textbf{\hypertarget{'tay}{'tay}} \textit{n.} (Tha. ⟨{\thai{}ไทย}⟩ [tʰaj˧])
Thai; Siamese; the Thai people

\textbf{\hypertarget{'tayak}{'tayak}} \textit{n.} (\hyperlink{'tay}{'tay}+\allowbreak \hyperlink{ak}{ak})
Thai; from Thailand

\textbf{\hypertarget{tayl}{tayl}} \textit{n.} (\hyperlink{lawt}{\sout{lawt}})
land; landmass; solid surface above and surrounded by ocean

\textbf{\hypertarget{taylalkas}{taylalkas}} \textit{n.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{alkas}{alkas})
moss; liverwort; hornwort

\textbf{\hypertarget{taylak}{taylak}} \textit{n.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{ak}{ak})
terrestrial

\textbf{\hypertarget{taylnelawt}{taylnelawt}} \textit{n.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{ne}{ne}+\allowbreak \hyperlink{lawt}{lawt})
Mediterranean Sea

\textbf{\hypertarget{taylnito}{taylnito}} \textit{v.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{nito}{nito})
be local; \hyperlink{taylnitolon}{ʟᴏᴧ} is local relative to ʟᴜᴍ

\textbf{\hypertarget{taylnitolon}{taylnitolon}} \textit{n.} (\hyperlink{taylnito}{taylnito}+\allowbreak \hyperlink{lon}{lon})
local

\textbf{\hypertarget{taylkatilum}{taylkatilum}} \textit{n.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{katilum}{katilum})
beach

\textbf{\hypertarget{taylkatilumcipcip}{taylkatilumcipcip}} \textit{n.} (\hyperlink{taylkatilum}{taylkatilum}+\allowbreak \hyperlink{cipcip}{cipcip})
seagull

\textbf{\hypertarget{taylkule}{taylkule}} \textit{v.} (\hyperlink{tayl}{tayl}+\allowbreak \hyperlink{kule}{kule})
be foreign; \hyperlink{taylkulelon}{ʟᴏᴧ} is foreign relative to ʟᴜᴍ

\textbf{\hypertarget{taylkulelon}{taylkulelon}} \textit{n.} (\hyperlink{taylkule}{taylkule}+\allowbreak \hyperlink{lon}{lon})
foreign

\textbf{\hypertarget{'taywan}{'taywan}} \textit{n.} (Cmn. ⟨{\chinese{}台湾}⟩ [tʰaɪ̯˧˥wan˥])
Taiwan (island)

\textbf{\hypertarget{'taywanak}{'taywanak}} \textit{n.} (\hyperlink{'taywan}{'taywan}+\allowbreak \hyperlink{ak}{ak})
Taiwanese; from Taiwan

\textbf{\hypertarget{'taywanwon}{'taywanwon}} \textit{n.} (\hyperlink{'taywan}{'taywan}+\allowbreak \hyperlink{won}{won})
Taiwanese; Chinese; the Taiwanese people

\textbf{\hypertarget{'taywantec}{'taywantec}} \textit{n.} (\hyperlink{'taywan}{'taywan}+\allowbreak \hyperlink{tec}{tec})
Taiwan; the Republic of Taiwan; Chinese Taipei

\textbf{\hypertarget{tayc}{tayc}} \textit{n.} (Cmn. ⟨{\chinese{}袋鼠}⟩ [taɪ̯˥˩ʂu˧˩˧])
macropod; kangaroo; wallaby; Macropodiformes

\textbf{\hypertarget{'taycicwen}{'taycicwen}} \textit{n.} (Cmn. ⟨{\chinese{}太极拳}⟩ [tʰaj˥˩.t͡ɕi˧˥ t͡ɕʰɥɛn˧˥])
Tai chi

\textbf{\hypertarget{taykun}{taykun}} \textit{n.} (Cmn. ⟨{\chinese{}太空}⟩ [tʰaɪ̯˥˩kʰʊŋ˥])
outer space; cosmos; vacuumic space above the atmosphere

\textbf{\hypertarget{taykunak}{taykunak}} \textit{n.} (\hyperlink{taykun}{taykun}+\allowbreak \hyperlink{ak}{ak})
cosmic; astral; interstellar

\textbf{\hypertarget{taykunmontalon}{taykunmontalon}} \textit{n.} (\hyperlink{taykun}{taykun}+\allowbreak \hyperlink{montalon}{montalon})
spaceship

\textbf{\hypertarget{taykunpatolon}{taykunpatolon}} \textit{n.} (\hyperlink{taykun}{taykun}+\allowbreak \hyperlink{patolon}{patolon})
meteor; meteorite

\textbf{\hypertarget{'taytec}{'taytec}} \textit{n.} (\hyperlink{'tay}{'tay}+\allowbreak \hyperlink{tec}{tec})
Thailand

\textbf{\hypertarget{'taytilip}{'taytilip}} \textit{n.} (\hyperlink{'tay}{'tay}+\allowbreak \hyperlink{tilip}{tilip})
Thai; Siamese; the Thai language

\textbf{\hypertarget{tal}{tal}} \textit{n.} (Hin. ⟨{\devanagari{}धड़}⟩ [d̤əɽ])
torso; trunk; stem; core; central base of a body

\textbf{\hypertarget{'tala}{'tala}} \textit{n.} (Eng. ⟨dollar⟩ [ˈdɑlɚ])
dollar; \$

\textbf{\hypertarget{talak}{talak}} \textit{n.} (\hyperlink{tal}{tal}+\allowbreak \hyperlink{ak}{ak})
torsal; basal

\textbf{\hypertarget{taluat}{taluat}} \textit{n.} (\hyperlink{ta}{ta}+\allowbreak \hyperlink{luat}{luat})
hammer

\textbf{\hypertarget{talpaholon}{talpaholon}} \textit{n.} (\hyperlink{tal}{tal}+\allowbreak \hyperlink{paholon}{paholon})
pelvis; hips

\textbf{\hypertarget{talpoltilum}{talpoltilum}} \textit{n.} (\hyperlink{tal}{tal}+\allowbreak \hyperlink{poltilum}{poltilum})
top; shirt

\textbf{\hypertarget{'taw}{'taw}} \textit{n.} (Cmn. ⟨{\chinese{}道}⟩ [taw˥˩])
Dao; Tao

\textbf{\hypertarget{'taw}{'taw}} \textit{n.} (Grc. ⟨τ⟩ [taw])
tau; 6.283…

\textbf{\hypertarget{tawh}{tawh}} \textit{n.} (Cmn. ⟨{\chinese{}桃}⟩ [tʰɑʊ̯˧˥])
plum; peach; cherry; apricot; Prunus minus Prunus dulcis

\textbf{\hypertarget{'tawfitilip}{'tawfitilip}} \textit{n.} (\hyperlink{'taw}{'taw}+\allowbreak \hyperlink{fitilip}{fitilip})
Daoism; Taoism

\textbf{\hypertarget{'tawfitilipak}{'tawfitilipak}} \textit{n.} (\hyperlink{'tawfitilip}{'tawfitilip}+\allowbreak \hyperlink{ak}{ak})
Daoist; Taoist; of Daoism

\textbf{\hypertarget{'tawfitilipwon}{'tawfitilipwon}} \textit{n.} (\hyperlink{'tawfitilip}{'tawfitilip}+\allowbreak \hyperlink{won}{won})
Daoist; Taoist; followers of Dao

\textbf{\hypertarget{tan}{tan}} \textit{n.} (Cmn. ⟨{\chinese{}蛋}⟩ [tan˥˩])
egg; first cell of a new organism

\textbf{\hypertarget{'tan}{'tan}} \textit{n.} (Dan. ⟨Dan-⟩ [dan])
Dane; the Danish people

\textbf{\hypertarget{tanec}{tanec}} \textit{n.} (\hyperlink{tan}{tan}+\allowbreak \hyperlink{ec}{ec})
ovary

\textbf{\hypertarget{tanak}{tanak}} \textit{n.} (\hyperlink{tan}{tan}+\allowbreak \hyperlink{ak}{ak})
ovary; eggy

\textbf{\hypertarget{'tanak}{'tanak}} \textit{n.} (\hyperlink{'tan}{'tan}+\allowbreak \hyperlink{ak}{ak})
Danish; from Denmark

\textbf{\hypertarget{tanul}{tanul}} \textit{n.} (Jav. ⟨dangur⟩ [tɑ̤ŋʊɽ])
cassava; manioc; yuca; macaxeira; mandioca; aipim; Manihot esculenta

\textbf{\hypertarget{tanmamul}{tanmamul}} \textit{n.} (\hyperlink{tan}{tan}+\allowbreak \hyperlink{mamul}{mamul})
platypus

\textbf{\hypertarget{'tansania}{'tansania}} \textit{n.} (Swa. ⟨Tanzania⟩ [tanzania])
Tanzania

\textbf{\hypertarget{'tansaniaak}{'tansaniaak}} \textit{n.} (\hyperlink{'tansania}{'tansania}+\allowbreak \hyperlink{ak}{ak})
Tanzanian; from Tanzania

\textbf{\hypertarget{'tansaniawon}{'tansaniawon}} \textit{n.} (\hyperlink{'tansania}{'tansania}+\allowbreak \hyperlink{won}{won})
Tanzanian; the Tanzanian people

\textbf{\hypertarget{'tantec}{'tantec}} \textit{n.} (\hyperlink{'tan}{'tan}+\allowbreak \hyperlink{tec}{tec})
Denmark

\textbf{\hypertarget{'tantilip}{'tantilip}} \textit{n.} (\hyperlink{'tan}{'tan}+\allowbreak \hyperlink{tilip}{tilip})
Danish; the Danish language

\textbf{\hypertarget{'tamil}{'tamil}} \textit{n.} (Tam. ⟨{\tamil{}தமிழ்}⟩ [t̪ɐmɨɻ])
Tamil; Tamilian; the Tamil people

\textbf{\hypertarget{'tamilak}{'tamilak}} \textit{n.} (\hyperlink{'tamil}{'tamil}+\allowbreak \hyperlink{ak}{ak})
Tamil; of the Tamil

\textbf{\hypertarget{'tamiltilip}{'tamiltilip}} \textit{n.} (\hyperlink{'tamil}{'tamil}+\allowbreak \hyperlink{tilip}{tilip})
Tamil; the Tamil language

\textbf{\hypertarget{tafu}{tafu}} \textit{v.} (\hyperlink{lasi}{\sout{lasi}})
hurt; be in pain; \hyperlink{tafulum}{ʟᴜᴍ} hurts \hyperlink{tafulon}{ʟᴏᴧ}

\textbf{\hypertarget{tafulon}{tafulon}} \textit{n.} (\hyperlink{tafu}{tafu}+\allowbreak \hyperlink{lon}{lon})
in pain

\textbf{\hypertarget{tafulum}{tafulum}} \textit{n.} (\hyperlink{tafu}{tafu}+\allowbreak \hyperlink{lum}{lum})
pain; place where it hurts

\textbf{\hypertarget{tafunihu}{tafunihu}} \textit{v.} (\hyperlink{tafu}{tafu}+\allowbreak \hyperlink{nihu}{nihu})
sympathise; take pity; ʟᴏᴧ sympathises with ʟᴜᴍ

\textbf{\hypertarget{tafunihuti}{tafunihuti}} \textit{v.} (\hyperlink{tafunihu}{tafunihu}+\allowbreak \hyperlink{ti}{ti})
congratulate; apologise; ʟєꜱ expresses sympathy to ʟᴏᴧ

\textbf{\hypertarget{tafuki}{tafuki}} \textit{v.} (\hyperlink{tafu}{tafu}+\allowbreak \hyperlink{ki}{ki})
torture; inflict pain; \hyperlink{tafukiles}{ʟєꜱ} causes ʟᴏᴧ to be pained by ʟᴜᴍ

\textbf{\hypertarget{tafukiles}{tafukiles}} \textit{n.} (\hyperlink{tafuki}{tafuki}+\allowbreak \hyperlink{les}{les})
torturer

\textbf{\hypertarget{tafukuci}{tafukuci}} \textit{v.} (\hyperlink{tafu}{tafu}+\allowbreak \hyperlink{kuci}{kuci})
feel schadenfreude; ʟᴏᴧ feels schodenfreude at ʟᴜᴍ

\textbf{\hypertarget{taka}{taka}} \textit{v.} (Ben. ⟨{\bengali{}থাকা}⟩ [t̪ʰaka])
be on; rest on; lean; support; hold; carry; \hyperlink{takalon}{ʟᴏᴧ} rests on \hyperlink{takalum}{ʟᴜᴍ}

\textbf{\hypertarget{'taka}{'taka}} \textit{n.} (Ben. ⟨{\bengali{}ঢাকা}⟩ [ɖʱaka])
Dhaka

\textbf{\hypertarget{takai}{takai}} \textit{v.} (Cmn. ⟨{\chinese{}打开}⟩ [ta˧˩˧kʰaɪ̯˥])
be turned on; be animate; be active; be open; \hyperlink{takailon}{ʟᴏᴧ} is turned on

\textbf{\hypertarget{takailon}{takailon}} \textit{n.} (\hyperlink{takai}{takai}+\allowbreak \hyperlink{lon}{lon})
turned on; animate; active; open

\textbf{\hypertarget{takaiki}{takaiki}} \textit{v.} (\hyperlink{takai}{takai}+\allowbreak \hyperlink{ki}{ki})
turn on; go off; animate; activate; trigger; \hyperlink{takaikiles}{ʟєꜱ} turns on ʟᴏᴧ

\textbf{\hypertarget{takaikiles}{takaikiles}} \textit{n.} (\hyperlink{takaiki}{takaiki}+\allowbreak \hyperlink{les}{les})
activator; trigger

\textbf{\hypertarget{takalon}{takalon}} \textit{n.} (\hyperlink{taka}{taka}+\allowbreak \hyperlink{lon}{lon})
at rest; on top; on

\textbf{\hypertarget{'takalok}{'takalok}} \textit{n.} (Tgl. ⟨Tagalog⟩ [tɐˈɡaːloɡ])
Tagalog; the Tagalog people

\textbf{\hypertarget{'takalokak}{'takalokak}} \textit{n.} (\hyperlink{'takalok}{'takalok}+\allowbreak \hyperlink{ak}{ak})
Tagalog; of the Tagalog

\textbf{\hypertarget{'takaloktilip}{'takaloktilip}} \textit{n.} (\hyperlink{'takalok}{'takalok}+\allowbreak \hyperlink{tilip}{tilip})
Tagalog; the Tagalog language

\textbf{\hypertarget{takalum}{takalum}} \textit{n.} (\hyperlink{taka}{taka}+\allowbreak \hyperlink{lum}{lum})
table; ground; floor; support; base

\textbf{\hypertarget{takanu}{takanu}} \textit{v.} (\hyperlink{taka}{taka}+\allowbreak \hyperlink{nu}{nu})
take off; get off; put down; ʟєꜱ takes ʟᴏᴧ off of ʟᴜᴍ

\textbf{\hypertarget{takaki}{takaki}} \textit{v.} (\hyperlink{taka}{taka}+\allowbreak \hyperlink{ki}{ki})
put on; get on; pick up; ʟєꜱ rests ʟᴏᴧ on ʟᴜᴍ

\textbf{\hypertarget{tatu}{tatu}} \textit{v.} (Hin. ⟨{\devanagari{}धातु}⟩ [d̤aːtu])
be metal; be metallic; \hyperlink{tatulon}{ʟᴏᴧ} is made out of metal

\textbf{\hypertarget{tatulon}{tatulon}} \textit{n.} (\hyperlink{tatu}{tatu}+\allowbreak \hyperlink{lon}{lon})
metal; metallic

\textbf{\hypertarget{tatulonfik}{tatulonfik}} \textit{n.} (\hyperlink{tatulon}{tatulon}+\allowbreak \hyperlink{fik}{fik})
satelite; artificial satelite

\textbf{\hypertarget{tatuki}{tatuki}} \textit{v.} (\hyperlink{tatu}{tatu}+\allowbreak \hyperlink{ki}{ki})
metallicise; ʟєꜱ turns ʟᴏᴧ into metal

\textbf{\hypertarget{tapa}{tapa}} \textit{v.} (\hyperlink{lama}{\sout{lama}})
be short; \hyperlink{tapalon}{ʟᴏᴧ} is short in time or space

\textbf{\hypertarget{'tapa}{'tapa}} \textit{n.} (Tah. ⟨tapa⟩ [tapa])
tapa; tapa cloth

\textbf{\hypertarget{tapalon}{tapalon}} \textit{n.} (\hyperlink{tapa}{tapa}+\allowbreak \hyperlink{lon}{lon})
nub; knob; bump; short

\textbf{\hypertarget{tapamilalwel}{tapamilalwel}} \textit{n.} (\hyperlink{tapa}{tapa}+\allowbreak \hyperlink{milalwel}{milalwel})
comma; pause

\textbf{\hypertarget{tapafuloki}{tapafuloki}} \textit{v.} (\hyperlink{tapa}{tapa}+\allowbreak \hyperlink{fuloki}{fuloki})
compress; squeeze; ʟєꜱ compresses ʟᴏᴧ

\textbf{\hypertarget{tapaki}{tapaki}} \textit{v.} (\hyperlink{tapa}{tapa}+\allowbreak \hyperlink{ki}{ki})
shorten; shrink; \hyperlink{tapakiles}{ʟєꜱ} shortens ʟᴏᴧ

\textbf{\hypertarget{tapakiles}{tapakiles}} \textit{n.} (\hyperlink{tapaki}{tapaki}+\allowbreak \hyperlink{les}{les})
shortener

\textbf{\hypertarget{tapakwelwel}{tapakwelwel}} \textit{n.} (\hyperlink{tapa}{tapa}+\allowbreak \hyperlink{kwelwel}{kwelwel})
hour

\textbf{\hypertarget{tapil}{tapil}} \textit{n.} (Spa. ⟨tapir⟩ [taˈpir])
tapir; Tapiridae

\textbf{\hypertarget{to}{to}} \textit{v.} (\hyperlink{le}{\sout{le}})
be rested; be energetic; be bright; have a bushy tail; \hyperlink{tolon}{ʟᴏᴧ} is well-rested

\textbf{\hypertarget{'toyc}{'toyc}} \textit{n.} (Deu. ⟨Deutsch⟩ [ˈdɔʏ̯t͡ʃ])
German; the German people

\textbf{\hypertarget{'toycak}{'toycak}} \textit{n.} (\hyperlink{'toyc}{'toyc}+\allowbreak \hyperlink{ak}{ak})
German; Germanic; from Germany

\textbf{\hypertarget{'toyctec}{'toyctec}} \textit{n.} (\hyperlink{'toyc}{'toyc}+\allowbreak \hyperlink{tec}{tec})
Germany

\textbf{\hypertarget{'toyctilip}{'toyctilip}} \textit{n.} (\hyperlink{'toyc}{'toyc}+\allowbreak \hyperlink{tilip}{tilip})
German; the German language

\textbf{\hypertarget{tolon}{tolon}} \textit{n.} (\hyperlink{to}{to}+\allowbreak \hyperlink{lon}{lon})
rested; energetic; bright

\textbf{\hypertarget{tolmi}{tolmi}} \textit{v.} (Epo. ⟨dormi⟩ [ˈdormi])
sleep; nap; be asleep; be unconscious; \hyperlink{tolmilon}{ʟᴏᴧ} is sleeping

\textbf{\hypertarget{tolmioyelum}{tolmioyelum}} \textit{n.} (\hyperlink{tolmi}{tolmi}+\allowbreak \hyperlink{oyelum}{oyelum})
snoring; snores

\textbf{\hypertarget{tolmilon}{tolmilon}} \textit{n.} (\hyperlink{tolmi}{tolmi}+\allowbreak \hyperlink{lon}{lon})
asleep; unconscious

\textbf{\hypertarget{tolmicua}{tolmicua}} \textit{v.} (\hyperlink{tolmi}{tolmi}+\allowbreak \hyperlink{cua}{cua})
dream; \hyperlink{tolmicualon}{ʟᴏᴧ} dreams \hyperlink{tolmicualum}{ʟᴜᴍ}

\textbf{\hypertarget{tolmicualon}{tolmicualon}} \textit{n.} (\hyperlink{tolmicua}{tolmicua}+\allowbreak \hyperlink{lon}{lon})
dreamer

\textbf{\hypertarget{tolmicualum}{tolmicualum}} \textit{n.} (\hyperlink{tolmicua}{tolmicua}+\allowbreak \hyperlink{lum}{lum})
dream

\textbf{\hypertarget{tolmiki}{tolmiki}} \textit{v.} (\hyperlink{tolmi}{tolmi}+\allowbreak \hyperlink{ki}{ki})
fall asleep; put to sleep; fall unconscious; ʟєꜱ puts ʟᴏᴧ to sleep

\textbf{\hypertarget{ton}{ton}} \textit{n.} (Ben. ⟨{\bengali{}ধনে}⟩ [d̪̤ɔn̪e])
coriander; cilantro; anise; star anise; badiane; fennel; Chinese parsley; Coriandrum

\textbf{\hypertarget{'tona}{'tona}} \textit{n.} (Ton. ⟨Tonga⟩ [ˈtoŋa])
Tonga (landmass)

\textbf{\hypertarget{'tonaak}{'tonaak}} \textit{n.} (\hyperlink{'tona}{'tona}+\allowbreak \hyperlink{ak}{ak})
Tongan; from Tonga

\textbf{\hypertarget{'tonawon}{'tonawon}} \textit{n.} (\hyperlink{'tona}{'tona}+\allowbreak \hyperlink{won}{won})
Tongan; the Tongan people

\textbf{\hypertarget{'tonatec}{'tonatec}} \textit{n.} (\hyperlink{'tona}{'tona}+\allowbreak \hyperlink{tec}{tec})
Tonga; the Kingdom of Tonga

\textbf{\hypertarget{'tonatilip}{'tonatilip}} \textit{n.} (\hyperlink{'tona}{'tona}+\allowbreak \hyperlink{tilip}{tilip})
Tongan; the Tongan language

\textbf{\hypertarget{tomat}{tomat}} \textit{n.} (Msa. ⟨tomat⟩ [tomat])
tomato; Solanum lycopersicum

\textbf{\hypertarget{'tominika}{'tominika}} \textit{n.} (Eng. ⟨Dominica⟩ [dɒmɪˈniːkə])
Dominica; the Commonwealth of Dominica

\textbf{\hypertarget{'tominikaak}{'tominikaak}} \textit{n.} (\hyperlink{'tominika}{'tominika}+\allowbreak \hyperlink{ak}{ak})
Dominican; from Dominica

\textbf{\hypertarget{'tominikawon}{'tominikawon}} \textit{n.} (\hyperlink{'tominika}{'tominika}+\allowbreak \hyperlink{won}{won})
Dominican; the Dominican people

\textbf{\hypertarget{'tocik}{'tocik}} \textit{n.} (Tgk. ⟨Тоҷик⟩ [tɔd͡ʒik])
Tajik; the Tajik people

\textbf{\hypertarget{'tocikak}{'tocikak}} \textit{n.} (\hyperlink{'tocik}{'tocik}+\allowbreak \hyperlink{ak}{ak})
Tajik; from Tajikistan

\textbf{\hypertarget{'tociktec}{'tociktec}} \textit{n.} (\hyperlink{'tocik}{'tocik}+\allowbreak \hyperlink{tec}{tec})
Tajikistan

\textbf{\hypertarget{'tociktilip}{'tociktilip}} \textit{n.} (\hyperlink{'tocik}{'tocik}+\allowbreak \hyperlink{tilip}{tilip})
Tajik; Tajiki; the Tajik language

\textbf{\hypertarget{tos}{tos}} \textit{num.} (Spa. ⟨dos⟩ [dos])
2; two; double

\textbf{\hypertarget{tosak}{tosak}} \textit{n.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{ak}{ak})
second; dual; binary

\textbf{\hypertarget{toslekpoltilum}{toslekpoltilum}} \textit{n.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{lekpoltilum}{lekpoltilum})
pants; shorts

\textbf{\hypertarget{tosnokipumkwelwel}{tosnokipumkwelwel}} \textit{n.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{noki}{noki}+\allowbreak \hyperlink{pumkwelwel}{pumkwelwel})
second grade

\textbf{\hypertarget{tosnul}{tosnul}} \textit{num.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{nul}{nul})
20; twenty

\textbf{\hypertarget{tosnulnul}{tosnulnul}} \textit{num.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
200; two hundred

\textbf{\hypertarget{toscohluso}{toscohluso}} \textit{v.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{coh}{coh}+\allowbreak \hyperlink{luso}{luso})
be ambidextrous; \hyperlink{toscohlusolon}{ʟᴏᴧ} is ambidextrous

\textbf{\hypertarget{toscohlusolon}{toscohlusolon}} \textit{n.} (\hyperlink{toscohluso}{toscohluso}+\allowbreak \hyperlink{lon}{lon})
ambidextrous

\textbf{\hypertarget{tossunkwelwel}{tossunkwelwel}} \textit{n.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Tuesday

\textbf{\hypertarget{toskwelwel}{toskwelwel}} \textit{n.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{kwelwel}{kwelwel})
second

\textbf{\hypertarget{tospelsan}{tospelsan}} \textit{num.} (\hyperlink{tos}{tos}+\allowbreak \hyperlink{pel}{pel}+\allowbreak \hyperlink{san}{san})
two-thirds; 2/3; .̅6

\textbf{\hypertarget{tofta}{tofta}} \textit{v.} (\hyperlink{lesla}{\sout{lesla}})
be inviscous; be thin; \hyperlink{toftalon}{ʟᴏᴧ} is inviscous

\textbf{\hypertarget{toftalon}{toftalon}} \textit{n.} (\hyperlink{tofta}{tofta}+\allowbreak \hyperlink{lon}{lon})
lubricant; oil; liquid; inviscous; thin

\textbf{\hypertarget{toftaki}{toftaki}} \textit{v.} (\hyperlink{tofta}{tofta}+\allowbreak \hyperlink{ki}{ki})
thin; decrease viscosity; \hyperlink{toftakiles}{ʟєꜱ} makes ʟᴏᴧ less viscous

\textbf{\hypertarget{toftakiles}{toftakiles}} \textit{n.} (\hyperlink{toftaki}{toftaki}+\allowbreak \hyperlink{les}{les})
thinner; viscosity reducer

\textbf{\hypertarget{toka}{toka}} \textit{v.} (Spa. ⟨toca⟩ [ˈtoka])
touch; meet; \hyperlink{tokalon}{ʟᴏᴧ} and ʟᴜᴍ are so close to each other that they cannot physically get any closer (please don’t get tecnical with my definition of this)

\textbf{\hypertarget{tokalon}{tokalon}} \textit{n.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{lon}{lon})
touching

\textbf{\hypertarget{tokalyot}{tokalyot}} \textit{n.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{lyot}{lyot})
joint; corner; intersection; edge

\textbf{\hypertarget{tokanu}{tokanu}} \textit{v.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{nu}{nu})
cut; separate; divide; split; ʟєꜱ makes ʟᴏᴧ stop touching ʟᴜᴍ

\textbf{\hypertarget{tokanuluat}{tokanuluat}} \textit{n.} (\hyperlink{tokanu}{tokanu}+\allowbreak \hyperlink{luat}{luat})
knife; wedge

\textbf{\hypertarget{tokanulyot}{tokanulyot}} \textit{n.} (\hyperlink{tokanu}{tokanu}+\allowbreak \hyperlink{lyot}{lyot})
gap; separation; cut; split

\textbf{\hypertarget{'tokamak}{'tokamak}} \textit{n.} (Rus. ⟨токамáк⟩ [tɔkɐmɐk])
tokamak

\textbf{\hypertarget{tokaci}{tokaci}} \textit{v.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{ci}{ci})
reach; extend; ʟєꜱ reaches ʟᴏᴧ toward ʟᴜᴍ

\textbf{\hypertarget{tokaki}{tokaki}} \textit{v.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{ki}{ki})
touch; join; ʟєꜱ touches ʟᴏᴧ to ʟᴜᴍ

\textbf{\hypertarget{tokatoka}{tokatoka}} \textit{v.} (\hyperlink{toka}{toka}+\allowbreak \hyperlink{toka}{toka})
chain; be chained; \hyperlink{tokatokalon}{ʟᴏᴧ} is chained together in \hyperlink{tokatokalum}{ʟᴜᴍ}

\textbf{\hypertarget{tokatokalon}{tokatokalon}} \textit{n.} (\hyperlink{tokatoka}{tokatoka}+\allowbreak \hyperlink{lon}{lon})
link; chained

\textbf{\hypertarget{tokatokalum}{tokatokalum}} \textit{n.} (\hyperlink{tokatoka}{tokatoka}+\allowbreak \hyperlink{lum}{lum})
chain

\textbf{\hypertarget{tokatokaki}{tokatokaki}} \textit{v.} (\hyperlink{tokatoka}{tokatoka}+\allowbreak \hyperlink{ki}{ki})
chain; link; incorporate; chain together; ʟєꜱ chains ʟᴏᴧ together into ʟᴜᴍ

\textbf{\hypertarget{toko}{toko}} \textit{v.} (Ben. ⟨{\bengali{}টক}⟩ [tɔkɔ])
be sour; \hyperlink{tokolon}{ʟᴏᴧ} is sour

\textbf{\hypertarget{'toko}{'toko}} \textit{n.} (Fra. ⟨Togo⟩ [togo])
Togo

\textbf{\hypertarget{'tokoak}{'tokoak}} \textit{n.} (\hyperlink{'toko}{'toko}+\allowbreak \hyperlink{ak}{ak})
Togolese; from Togo

\textbf{\hypertarget{tokolon}{tokolon}} \textit{n.} (\hyperlink{toko}{toko}+\allowbreak \hyperlink{lon}{lon})
sour

\textbf{\hypertarget{tokolyan}{tokolyan}} \textit{n.} (\hyperlink{toko}{toko}+\allowbreak \hyperlink{lyan}{lyan})
sourness

\textbf{\hypertarget{'tokowon}{'tokowon}} \textit{n.} (\hyperlink{'toko}{'toko}+\allowbreak \hyperlink{won}{won})
Togolese; the Togolese people

\textbf{\hypertarget{tokoki}{tokoki}} \textit{v.} (\hyperlink{toko}{toko}+\allowbreak \hyperlink{ki}{ki})
sour; ʟєꜱ makes ʟᴏᴧ become sour

\textbf{\hypertarget{toki}{toki}} \textit{v.} (\hyperlink{to}{to}+\allowbreak \hyperlink{ki}{ki})
rest; recharge; ʟєꜱ makes ʟᴏᴧ feel rested

\textbf{\hypertarget{'tokipona}{'tokipona}} \textit{n.} (Tok. ⟨toki pona⟩ [ˈtoki ˈpona])
Toki Pona

\textbf{\hypertarget{'tokiponaak}{'tokiponaak}} \textit{n.} (\hyperlink{'tokipona}{'tokipona}+\allowbreak \hyperlink{ak}{ak})
Toki Pona; in Toki Pona

\textbf{\hypertarget{'tokiponawon}{'tokiponawon}} \textit{n.} (\hyperlink{'tokipona}{'tokipona}+\allowbreak \hyperlink{won}{won})
Toki Ponist; Toki Pona speakers

\textbf{\hypertarget{'tokyo}{'tokyo}} \textit{n.} (Jpn. ⟨{\japanese{}東京}⟩ [toːkʲoː])
Tokyo

\textbf{\hypertarget{toto}{toto}} \textit{v.} (\hyperlink{lele}{\sout{lele}})
struggle; be-bad; ʟᴏᴧ is not doing well

\textbf{\hypertarget{'topeykow}{'topeykow}} \textit{n.} (Eng. ⟨Tobago⟩ [təbeɪɡəʊ])
Tobago

\textbf{\hypertarget{'topeykowak}{'topeykowak}} \textit{n.} (\hyperlink{'topeykow}{'topeykow}+\allowbreak \hyperlink{ak}{ak})
Tobagonian

\textbf{\hypertarget{ti}{ti}} \textit{v.} (Xho. ⟨thi⟩ [tʰi])
say; convey; communicate; \hyperlink{tiles}{ʟєꜱ} conveys \hyperlink{tilum}{ʟᴜᴍ} to \hyperlink{tilon}{ʟᴏᴧ}

\textbf{\hypertarget{tie}{tie}} \textit{v.} (Ben. ⟨{\bengali{}দিয়ে}⟩ [d̪ie̯e])
be across; be transverse; straddle; be perpendicular; \hyperlink{tielon}{ʟᴏᴧ} is across \hyperlink{tielum}{ʟᴜᴍ}

\textbf{\hypertarget{tielon}{tielon}} \textit{n.} (\hyperlink{tie}{tie}+\allowbreak \hyperlink{lon}{lon})
cross; cross member; across; transverse; perpendicular

\textbf{\hypertarget{tielonfolmo}{tielonfolmo}} \textit{v.} (\hyperlink{tielon}{tielon}+\allowbreak \hyperlink{folmo}{folmo})
be cruciform; be cross-shaped; \hyperlink{tielonfolmolon}{ʟᴏᴧ} comprises two crossed segments

\textbf{\hypertarget{tielonfolmolon}{tielonfolmolon}} \textit{n.} (\hyperlink{tielonfolmo}{tielonfolmo}+\allowbreak \hyperlink{lon}{lon})
cruciform; cross-shaped

\textbf{\hypertarget{tielum}{tielum}} \textit{n.} (\hyperlink{tie}{tie}+\allowbreak \hyperlink{lum}{lum})
crossed

\textbf{\hypertarget{tielyan}{tielyan}} \textit{n.} (\hyperlink{tie}{tie}+\allowbreak \hyperlink{lyan}{lyan})
transverseness; obliqueness

\textbf{\hypertarget{tieki}{tieki}} \textit{v.} (\hyperlink{tie}{tie}+\allowbreak \hyperlink{ki}{ki})
cross; move across; pass; ʟєꜱ makes ʟᴏᴧ cross ʟᴜᴍ

\textbf{\hypertarget{tiekilyot}{tiekilyot}} \textit{n.} (\hyperlink{tieki}{tieki}+\allowbreak \hyperlink{lyot}{lyot})
intersection; cross

\textbf{\hypertarget{tiles}{tiles}} \textit{n.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{les}{les})
sayer

\textbf{\hypertarget{tilon}{tilon}} \textit{n.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{lon}{lon})
addressee

\textbf{\hypertarget{'tili}{'tili}} \textit{n.} (Hin. ⟨{\devanagari{}दिल्ली }⟩ [dɪlliː])
Delhi

\textbf{\hypertarget{tilip}{tilip}} \textit{n.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{lip}{lip})
language; protocol

\textbf{\hypertarget{tilipak}{tilipak}} \textit{n.} (\hyperlink{tilip}{tilip}+\allowbreak \hyperlink{ak}{ak})
linguistic; lingual

\textbf{\hypertarget{tilipsoma}{tilipsoma}} \textit{v.} (\hyperlink{tilip}{tilip}+\allowbreak \hyperlink{soma}{soma})
do linguistics; \hyperlink{tilipsomales}{ʟєꜱ} studies languages to learn about \hyperlink{tilipsomalon}{ʟᴏᴧ}

\textbf{\hypertarget{tilipsomales}{tilipsomales}} \textit{n.} (\hyperlink{tilipsoma}{tilipsoma}+\allowbreak \hyperlink{les}{les})
linguist

\textbf{\hypertarget{tilipsomalon}{tilipsomalon}} \textit{n.} (\hyperlink{tilipsoma}{tilipsoma}+\allowbreak \hyperlink{lon}{lon})
linguist

\textbf{\hypertarget{tiluat}{tiluat}} \textit{n.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{luat}{luat})
phone; cell phone; communicator; communication device

\textbf{\hypertarget{tilum}{tilum}} \textit{n.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{lum}{lum})
message; idea; signal; utterance

\textbf{\hypertarget{'tiwehi}{'tiwehi}} \textit{n.} (Div. ⟨{\thaana{}ދިވެހި}⟩ [diˈʋehi])
Maldivian; Dhivehi; Divehi; the Maldivian people

\textbf{\hypertarget{'tiwehiak}{'tiwehiak}} \textit{n.} (\hyperlink{'tiwehi}{'tiwehi}+\allowbreak \hyperlink{ak}{ak})
Maldivian; from the Maldives

\textbf{\hypertarget{'tiwehikwelyot}{'tiwehikwelyot}} \textit{n.} (\hyperlink{'tiwehi}{'tiwehi}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Maldives (archipelago)

\textbf{\hypertarget{'tiwehitec}{'tiwehitec}} \textit{n.} (\hyperlink{'tiwehi}{'tiwehi}+\allowbreak \hyperlink{tec}{tec})
Maldives; the Republic of Maldives

\textbf{\hypertarget{'tiwehitilip}{'tiwehitilip}} \textit{n.} (\hyperlink{'tiwehi}{'tiwehi}+\allowbreak \hyperlink{tilip}{tilip})
Maldivian; Dhivehi; Divehi; the Maldivian language

\textbf{\hypertarget{'tiwlki}{'tiwlki}} \textit{n.} (Tur. ⟨Türk⟩ [tyɾk])
Turk; the Turkish people

\textbf{\hypertarget{'tiwlkiak}{'tiwlkiak}} \textit{n.} (\hyperlink{'tiwlki}{'tiwlki}+\allowbreak \hyperlink{ak}{ak})
Turkish; Turkic; from Turkey

\textbf{\hypertarget{'tiwlkimen}{'tiwlkimen}} \textit{n.} (Tuk. ⟨türkmen⟩ [tʏɾkmɛn])
Turkmen; the Turkmen people

\textbf{\hypertarget{'tiwlkimenak}{'tiwlkimenak}} \textit{n.} (\hyperlink{'tiwlkimen}{'tiwlkimen}+\allowbreak \hyperlink{ak}{ak})
Turkmen; from Turkmenistan

\textbf{\hypertarget{'tiwlkimentec}{'tiwlkimentec}} \textit{n.} (\hyperlink{'tiwlkimen}{'tiwlkimen}+\allowbreak \hyperlink{tec}{tec})
Turkmenistan

\textbf{\hypertarget{'tiwlkimentilip}{'tiwlkimentilip}} \textit{n.} (\hyperlink{'tiwlkimen}{'tiwlkimen}+\allowbreak \hyperlink{tilip}{tilip})
Turkmen; the Turkmen language

\textbf{\hypertarget{'tiwlkitec}{'tiwlkitec}} \textit{n.} (\hyperlink{'tiwlki}{'tiwlki}+\allowbreak \hyperlink{tec}{tec})
Turkey

\textbf{\hypertarget{'tiwlkitilip}{'tiwlkitilip}} \textit{n.} (\hyperlink{'tiwlki}{'tiwlki}+\allowbreak \hyperlink{tilip}{tilip})
Turkish; the Turkish language

\textbf{\hypertarget{tinus}{tinus}} \textit{n.} (Epo. ⟨tinuso⟩ [tiˈnuso])
mackerel; tuna; tunny; Scombridae

\textbf{\hypertarget{tinti}{tinti}} \textit{v.} (ono. [tiŋ tiŋ])
ding; ping; chime; \hyperlink{tintiles}{ʟєꜱ} makes \hyperlink{tintilon}{ʟᴏᴧ}

\textbf{\hypertarget{tintiles}{tintiles}} \textit{n.} (\hyperlink{tinti}{tinti}+\allowbreak \hyperlink{les}{les})
bell

\textbf{\hypertarget{tintilesfolmo}{tintilesfolmo}} \textit{v.} (\hyperlink{tintiles}{tintiles}+\allowbreak \hyperlink{folmo}{folmo})
be campanula; be bell-shaped; \hyperlink{tintilesfolmolon}{ʟᴏᴧ} is rotationally symmetric, closed on one end, and flared on the other

\textbf{\hypertarget{tintilesfolmolon}{tintilesfolmolon}} \textit{n.} (\hyperlink{tintilesfolmo}{tintilesfolmo}+\allowbreak \hyperlink{lon}{lon})
campanula; bell-shaped

\textbf{\hypertarget{tintilon}{tintilon}} \textit{n.} (\hyperlink{tinti}{tinti}+\allowbreak \hyperlink{lon}{lon})
ding; ping; chime; sudden, concordant sound or action

\textbf{\hypertarget{'timensio}{'timensio}} \textit{n.} (Lat. ⟨dīmensiō⟩ [diːˈmẽːsioː])
dimension (mathematics)

\textbf{\hypertarget{'timensioak}{'timensioak}} \textit{n.} (\hyperlink{'timensio}{'timensio}+\allowbreak \hyperlink{ak}{ak})
dimensional

\textbf{\hypertarget{'timol}{'timol}} \textit{n.} (Tet. ⟨Timór⟩ [timor])
Timor (landmass)

\textbf{\hypertarget{'timolak}{'timolak}} \textit{n.} (\hyperlink{'timol}{'timol}+\allowbreak \hyperlink{ak}{ak})
Timorese; from Timor

\textbf{\hypertarget{tihu}{tihu}} \textit{v.} (\hyperlink{luci}{\sout{luci}})
be green; \hyperlink{tihulon}{ʟᴏᴧ} reflects medium and long wavelength light

\textbf{\hypertarget{tihulon}{tihulon}} \textit{n.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{lon}{lon})
green

\textbf{\hypertarget{tihuceluk}{tihuceluk}} \textit{n.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{celuk}{celuk})
lime

\textbf{\hypertarget{tihuki}{tihuki}} \textit{v.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{ki}{ki})
green; colour green; ʟєꜱ colours ʟᴏᴧ green

\textbf{\hypertarget{tihukio}{tihukio}} \textit{v.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{kio}{kio})
be emerald; \hyperlink{tihukiolon}{ʟᴏᴧ} is made of emerald

\textbf{\hypertarget{tihukiolon}{tihukiolon}} \textit{n.} (\hyperlink{tihukio}{tihukio}+\allowbreak \hyperlink{lon}{lon})
emerald

\textbf{\hypertarget{tihukwah}{tihukwah}} \textit{n.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{kwah}{kwah})
honeydew

\textbf{\hypertarget{tihutatu}{tihutatu}} \textit{v.} (\hyperlink{tihu}{tihu}+\allowbreak \hyperlink{tatu}{tatu})
be copper; \hyperlink{tihutatulon}{ʟᴏᴧ} is made of copper

\textbf{\hypertarget{tihutatulon}{tihutatulon}} \textit{n.} (\hyperlink{tihutatu}{tihutatu}+\allowbreak \hyperlink{lon}{lon})
copper

\textbf{\hypertarget{'ticat}{'ticat}} \textit{n.} (Eng. ⟨T-shirt⟩ [tʰiː ʃɚt])
T-shirt

\textbf{\hypertarget{tife}{tife}} \textit{v.} (\hyperlink{luso}{\sout{luso}})
be inept; be unskillful; be ineffective; be bad; \hyperlink{tifelon}{ʟᴏᴧ} is bad at causing ʟᴜᴍ

\textbf{\hypertarget{tifelon}{tifelon}} \textit{n.} (\hyperlink{tife}{tife}+\allowbreak \hyperlink{lon}{lon})
inept; unskillful; ineffective; bad

\textbf{\hypertarget{tifecoh}{tifecoh}} \textit{n.} (\hyperlink{tife}{tife}+\allowbreak \hyperlink{coh}{coh})
nondominant hand

\textbf{\hypertarget{tifeki}{tifeki}} \textit{v.} (\hyperlink{tife}{tife}+\allowbreak \hyperlink{ki}{ki})
untrain; forget; become rusty; \hyperlink{tifekiles}{ʟєꜱ} makes \hyperlink{tifekilon}{ʟᴏᴧ} become unskillful at ʟᴜᴍ

\textbf{\hypertarget{tifekiles}{tifekiles}} \textit{n.} (\hyperlink{tifeki}{tifeki}+\allowbreak \hyperlink{les}{les})
untrainer

\textbf{\hypertarget{tifekilon}{tifekilon}} \textit{n.} (\hyperlink{tifeki}{tifeki}+\allowbreak \hyperlink{lon}{lon})
rusty

\textbf{\hypertarget{tifaoh}{tifaoh}} \textit{n.} (Epo. ⟨tifao⟩ [tiˈfao])
bulrush; reed; cattail; water sausage; Typha

\textbf{\hypertarget{tik}{tik}} \textit{n.} (Mar. ⟨{\devanagari{}टिक}⟩ [ʈik])
tick; mite; Acari

\textbf{\hypertarget{tika}{tika}} \textit{v.} (\hyperlink{luna}{\sout{luna}})
be unsalty; \hyperlink{tikalon}{ʟᴏᴧ} is not salty

\textbf{\hypertarget{tikalon}{tikalon}} \textit{n.} (\hyperlink{tika}{tika}+\allowbreak \hyperlink{lon}{lon})
unsalty

\textbf{\hypertarget{tikaki}{tikaki}} \textit{v.} (\hyperlink{tika}{tika}+\allowbreak \hyperlink{ki}{ki})
desalt; purify; ʟєꜱ makes ʟᴏᴧ less salty

\textbf{\hypertarget{tiku}{tiku}} \textit{v.} (\hyperlink{luni}{\sout{luni}})
be unlikely; be weird; be remarkable; be rare; be unexpected; be strange; \hyperlink{tikulon}{ʟᴏᴧ} is unlikely

\textbf{\hypertarget{tikulon}{tikulon}} \textit{n.} (\hyperlink{tiku}{tiku}+\allowbreak \hyperlink{lon}{lon})
coincidence; unlikely; weird; remarkable; rare; unexpected; strange

\textbf{\hypertarget{tikulyan}{tikulyan}} \textit{n.} (\hyperlink{tiku}{tiku}+\allowbreak \hyperlink{lyan}{lyan})
rarity; weirdness

\textbf{\hypertarget{tikuki}{tikuki}} \textit{v.} (\hyperlink{tiku}{tiku}+\allowbreak \hyperlink{ki}{ki})
decrease chances; ʟєꜱ makes ʟᴏᴧ less likely

\textbf{\hypertarget{tikpic}{tikpic}} \textit{n.} (\hyperlink{tik}{tik}+\allowbreak \hyperlink{pic}{pic})
castor bean; castor oil plant; palm of Christ

\textbf{\hypertarget{'titanium}{'titanium}} \textit{n.} (Lat. ⟨titanium⟩ [tɪtanɪʊ̃])
titanium

\textbf{\hypertarget{titi}{titi}} \textit{v.} (\hyperlink{ti}{ti}+\allowbreak \hyperlink{ti}{ti})
communicate; talk; speak; correspond; ʟєꜱ has a two-way interaction with \hyperlink{titilon}{ʟᴏᴧ} about \hyperlink{titilum}{ʟᴜᴍ}

\textbf{\hypertarget{titilon}{titilon}} \textit{n.} (\hyperlink{titi}{titi}+\allowbreak \hyperlink{lon}{lon})
interlocutor

\textbf{\hypertarget{titilum}{titilum}} \textit{n.} (\hyperlink{titi}{titi}+\allowbreak \hyperlink{lum}{lum})
topic; passage

\textbf{\hypertarget{titilwel}{titilwel}} \textit{n.} (\hyperlink{titi}{titi}+\allowbreak \hyperlink{lwel}{lwel})
conversation; discourse

\textbf{\hypertarget{tipa}{tipa}} \textit{v.} (Epo. ⟨tipa⟩ [ˈtipa])
be typical; exemplify; qualify; represent; the type of \hyperlink{tipalon}{ʟᴏᴧ} is \hyperlink{tipalum}{ʟᴜᴍ}

\textbf{\hypertarget{tipalon}{tipalon}} \textit{n.} (\hyperlink{tipa}{tipa}+\allowbreak \hyperlink{lon}{lon})
instance; example; typical

\textbf{\hypertarget{tipalum}{tipalum}} \textit{n.} (\hyperlink{tipa}{tipa}+\allowbreak \hyperlink{lum}{lum})
category; class; kind; type

\textbf{\hypertarget{tipanu}{tipanu}} \textit{v.} (\hyperlink{tipa}{tipa}+\allowbreak \hyperlink{nu}{nu})
disqualify; declassify; ʟєꜱ makes ʟᴏᴧ not be an instance of ʟᴜᴍ

\textbf{\hypertarget{tipaki}{tipaki}} \textit{v.} (\hyperlink{tipa}{tipa}+\allowbreak \hyperlink{ki}{ki})
categorise; classify; ʟєꜱ places ʟᴏᴧ as an instance of ʟᴜᴍ

\textbf{\hypertarget{tu}{tu}} \textit{v.} (Cmn. ⟨{\chinese{}读}⟩ [tu˧˥])
read; load; interpret; \hyperlink{tules}{ʟєꜱ} reads \hyperlink{tulum}{ʟᴜᴍ} from the physical state of ʟᴏᴧ

\textbf{\hypertarget{tue}{tue}} \textit{v.} (Jav. ⟨duwé⟩ [tṳwe])
own; have; possess; belong; \hyperlink{tuelon}{ʟᴏᴧ} owns \hyperlink{tuelum}{ʟᴜᴍ}

\textbf{\hypertarget{tuelon}{tuelon}} \textit{n.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{lon}{lon})
owner

\textbf{\hypertarget{tuelum}{tuelum}} \textit{n.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{lum}{lum})
property

\textbf{\hypertarget{tuenu}{tuenu}} \textit{v.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{nu}{nu})
take; lose; give away; renounce ownership; \hyperlink{tuenules}{ʟєꜱ} takes \hyperlink{tuenulum}{ʟᴜᴍ} from \hyperlink{tuenulon}{ʟᴏᴧ}

\textbf{\hypertarget{tuenules}{tuenules}} \textit{n.} (\hyperlink{tuenu}{tuenu}+\allowbreak \hyperlink{les}{les})
taker

\textbf{\hypertarget{tuenulon}{tuenulon}} \textit{n.} (\hyperlink{tuenu}{tuenu}+\allowbreak \hyperlink{lon}{lon})
loser

\textbf{\hypertarget{tuenulum}{tuenulum}} \textit{n.} (\hyperlink{tuenu}{tuenu}+\allowbreak \hyperlink{lum}{lum})
theft; prize; taken

\textbf{\hypertarget{tuecalu}{tuecalu}} \textit{v.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{calu}{calu})
keep; retain ownership; ʟєꜱ lets \hyperlink{tuecalulon}{ʟᴏᴧ} keep \hyperlink{tuecalulum}{ʟᴜᴍ}

\textbf{\hypertarget{tuecalulon}{tuecalulon}} \textit{n.} (\hyperlink{tuecalu}{tuecalu}+\allowbreak \hyperlink{lon}{lon})
keeper; hoarder

\textbf{\hypertarget{tuecalulum}{tuecalulum}} \textit{n.} (\hyperlink{tuecalu}{tuecalu}+\allowbreak \hyperlink{lum}{lum})
kept

\textbf{\hypertarget{tueki}{tueki}} \textit{v.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{ki}{ki})
give; receive; obtain; get; transfer ownership; \hyperlink{tuekiles}{ʟєꜱ} gives \hyperlink{tuekilum}{ʟᴜᴍ} to \hyperlink{tuekilon}{ʟᴏᴧ}

\textbf{\hypertarget{tuekiles}{tuekiles}} \textit{n.} (\hyperlink{tueki}{tueki}+\allowbreak \hyperlink{les}{les})
giver

\textbf{\hypertarget{tuekilon}{tuekilon}} \textit{n.} (\hyperlink{tueki}{tueki}+\allowbreak \hyperlink{lon}{lon})
receiver; obtainer

\textbf{\hypertarget{tuekilum}{tuekilum}} \textit{n.} (\hyperlink{tueki}{tueki}+\allowbreak \hyperlink{lum}{lum})
gift; given

\textbf{\hypertarget{tuepowi}{tuepowi}} \textit{v.} (\hyperlink{tue}{tue}+\allowbreak \hyperlink{powi}{powi})
be obtainable; be common; \hyperlink{tuepowilum}{ʟᴜᴍ} is obtainable to ʟᴏᴧ

\textbf{\hypertarget{tuepowilum}{tuepowilum}} \textit{n.} (\hyperlink{tuepowi}{tuepowi}+\allowbreak \hyperlink{lum}{lum})
obtainable; common

\textbf{\hypertarget{tuepowinyo}{tuepowinyo}} \textit{v.} (\hyperlink{tuepowi}{tuepowi}+\allowbreak \hyperlink{nyo}{nyo})
be rare; be unobtainable; \hyperlink{tuepowinyolum}{ʟᴜᴍ} is difficult for ʟᴏᴧ to obtain

\textbf{\hypertarget{tuepowinyolum}{tuepowinyolum}} \textit{n.} (\hyperlink{tuepowinyo}{tuepowinyo}+\allowbreak \hyperlink{lum}{lum})
rare; unobtainable

\textbf{\hypertarget{tul}{tul}} \textit{n.} (Mar. ⟨{\devanagari{}तूर}⟩ [tuːr])
pigeon pea; red gram; tropical green pea; gandule; Cajanus cajan

\textbf{\hypertarget{tules}{tules}} \textit{n.} (\hyperlink{tu}{tu}+\allowbreak \hyperlink{les}{les})
reader

\textbf{\hypertarget{tulum}{tulum}} \textit{n.} (\hyperlink{tu}{tu}+\allowbreak \hyperlink{lum}{lum})
reading; sign; interpretation

\textbf{\hypertarget{tulse}{tulse}} \textit{v.} (Spa. ⟨dulce⟩ [ˈdulse])
be sweet; be sweetened; \hyperlink{tulselon}{ʟᴏᴧ} is sweet

\textbf{\hypertarget{tulseufalon}{tulseufalon}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{ufalon}{ufalon})
sugar

\textbf{\hypertarget{tulselon}{tulselon}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{lon}{lon})
candy; sweet; sweetened

\textbf{\hypertarget{tulselyan}{tulselyan}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{lyan}{lyan})
sweetness

\textbf{\hypertarget{tulsekas}{tulsekas}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{kas}{kas})
sugarcane; cane sugar

\textbf{\hypertarget{tulseki}{tulseki}} \textit{v.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{ki}{ki})
sweeten; ʟєꜱ makes ʟᴏᴧ become sweet

\textbf{\hypertarget{tulsetupel}{tulsetupel}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{tupel}{tupel})
yam; sweet potato

\textbf{\hypertarget{tulsepet}{tulsepet}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{pet}{pet})
sugar beet

\textbf{\hypertarget{tulsepic}{tulsepic}} \textit{n.} (\hyperlink{tulse}{tulse}+\allowbreak \hyperlink{pic}{pic})
cacao; cocoa; chocolate

\textbf{\hypertarget{'tuwalu}{'tuwalu}} \textit{n.} (Tvl. ⟨Tuuvalu⟩ [tuːvalu])
Tuvalu (archipleago); the Ellice Islands

\textbf{\hypertarget{'tuwaluak}{'tuwaluak}} \textit{n.} (\hyperlink{'tuwalu}{'tuwalu}+\allowbreak \hyperlink{ak}{ak})
Tuvaluan; from Tuvalu

\textbf{\hypertarget{'tuwaluwon}{'tuwaluwon}} \textit{n.} (\hyperlink{'tuwalu}{'tuwalu}+\allowbreak \hyperlink{won}{won})
Tuvaluan; the Tuvaluan people

\textbf{\hypertarget{'tuwalutec}{'tuwalutec}} \textit{n.} (\hyperlink{'tuwalu}{'tuwalu}+\allowbreak \hyperlink{tec}{tec})
Tuvalu (country)

\textbf{\hypertarget{'tuwalutilip}{'tuwalutilip}} \textit{n.} (\hyperlink{'tuwalu}{'tuwalu}+\allowbreak \hyperlink{tilip}{tilip})
Tuvaluan; the Tuvaluan language

\textbf{\hypertarget{tun}{tun}} \textit{n.} (Cmn. ⟨{\chinese{}动物}⟩ [tʊŋ˥˩u˥˩])
animal; meat; Animalia

\textbf{\hypertarget{tunak}{tunak}} \textit{n.} (\hyperlink{tun}{tun}+\allowbreak \hyperlink{ak}{ak})
animal; meaty

\textbf{\hypertarget{'tunis}{'tunis}} \textit{n.} (Ara. ⟨{\arabics{}تونس}⟩ [tuːnis])
Tunis

\textbf{\hypertarget{'tunisak}{'tunisak}} \textit{n.} (\hyperlink{'tunis}{'tunis}+\allowbreak \hyperlink{ak}{ak})
Tunisian; from Tunisia

\textbf{\hypertarget{'tunistec}{'tunistec}} \textit{n.} (\hyperlink{'tunis}{'tunis}+\allowbreak \hyperlink{tec}{tec})
Tunisia

\textbf{\hypertarget{'tunistecwon}{'tunistecwon}} \textit{n.} (\hyperlink{'tunistec}{'tunistec}+\allowbreak \hyperlink{won}{won})
Tunisian; the Tunisian people

\textbf{\hypertarget{tunnyamales}{tunnyamales}} \textit{n.} (\hyperlink{tun}{tun}+\allowbreak \hyperlink{nyamales}{nyamales})
carnivore; something that eats meat

\textbf{\hypertarget{tunci}{tunci}} \textit{v.} (Cmn. ⟨{\chinese{}统治}⟩ [tʰʊŋ˧˩˧ʈ͡ʂɨ˥˩])
govern; administer; have citizenship; \hyperlink{tuncilum}{ʟᴜᴍ} serves as the governing body to \hyperlink{tuncilon}{ʟᴏᴧ}

\textbf{\hypertarget{tuncilon}{tuncilon}} \textit{n.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{lon}{lon})
citizen; governed; people

\textbf{\hypertarget{tuncilum}{tuncilum}} \textit{n.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{lum}{lum})
government

\textbf{\hypertarget{tuncilumak}{tuncilumak}} \textit{n.} (\hyperlink{tuncilum}{tuncilum}+\allowbreak \hyperlink{ak}{ak})
public

\textbf{\hypertarget{tuncilumlwa}{tuncilumlwa}} \textit{v.} (\hyperlink{tuncilum}{tuncilum}+\allowbreak \hyperlink{lwa}{lwa})
rebel; ʟєꜱ rebels against ʟᴏᴧ

\textbf{\hypertarget{tuncilumwahauti}{tuncilumwahauti}} \textit{v.} (\hyperlink{tuncilum}{tuncilum}+\allowbreak \hyperlink{wahauti}{wahauti})
protest; ʟєꜱ protests ʟᴜᴍ to ʟᴏᴧ

\textbf{\hypertarget{tuncinu}{tuncinu}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{nu}{nu})
secede; collapse; impeach; ʟєꜱ makes ʟᴜᴍ stop governing ʟᴏᴧ

\textbf{\hypertarget{tuncinyotewi}{tuncinyotewi}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{nyotewi}{nyotewi})
be illegal; be against the law; \hyperlink{tuncinyotewilon}{ʟᴏᴧ} is prohibited by law from making \hyperlink{tuncinyotewilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{tuncinyotewilon}{tuncinyotewilon}} \textit{n.} (\hyperlink{tuncinyotewi}{tuncinyotewi}+\allowbreak \hyperlink{lon}{lon})
illegal; against the law

\textbf{\hypertarget{tuncinyotewilum}{tuncinyotewilum}} \textit{n.} (\hyperlink{tuncinyotewi}{tuncinyotewi}+\allowbreak \hyperlink{lum}{lum})
crime; felony; misdemeanor

\textbf{\hypertarget{tuncinyotewiki}{tuncinyotewiki}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{nyotewiki}{nyotewiki})
prohibit; ban; pass law against; ʟєꜱ legally declares that ʟᴏᴧ may not make ʟᴜᴍ happen

\textbf{\hypertarget{tunciki}{tunciki}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{ki}{ki})
take over; elect; come to power; conquer; annex; ʟєꜱ makes ʟᴜᴍ become the government of ʟᴏᴧ

\textbf{\hypertarget{tuncitewi}{tuncitewi}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{tewi}{tewi})
be legally required; be mandated by law; \hyperlink{tuncitewilon}{ʟᴏᴧ} is required by law to make \hyperlink{tuncitewilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{tuncitewilon}{tuncitewilon}} \textit{n.} (\hyperlink{tuncitewi}{tuncitewi}+\allowbreak \hyperlink{lon}{lon})
legally required; mandated by law

\textbf{\hypertarget{tuncitewilum}{tuncitewilum}} \textit{n.} (\hyperlink{tuncitewi}{tuncitewi}+\allowbreak \hyperlink{lum}{lum})
law

\textbf{\hypertarget{tuncitewiki}{tuncitewiki}} \textit{v.} (\hyperlink{tunci}{tunci}+\allowbreak \hyperlink{tewiki}{tewiki})
legislate; mandate; pass law; \hyperlink{tuncitewikiles}{ʟєꜱ} legally declares that ʟᴏᴧ must make \hyperlink{tuncitewikilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{tuncitewikiles}{tuncitewikiles}} \textit{n.} (\hyperlink{tuncitewiki}{tuncitewiki}+\allowbreak \hyperlink{les}{les})
legislator; legislature; parliament; congress

\textbf{\hypertarget{tuncitewikilum}{tuncitewikilum}} \textit{n.} (\hyperlink{tuncitewiki}{tuncitewiki}+\allowbreak \hyperlink{lum}{lum})
new law

\textbf{\hypertarget{tumocalum}{tumocalum}} \textit{n.} (\hyperlink{tu}{tu}+\allowbreak \hyperlink{mocalum}{mocalum})
literature; book; blog; web serial; paper

\textbf{\hypertarget{'tukiw}{'tukiw}} \textit{n.} (Dzo. ⟨{\tibetan{}འབྲུག་ཡུལ་}⟩ [ʈuk̚˩.yː˩])
Bhutan

\textbf{\hypertarget{'tukiwak}{'tukiwak}} \textit{n.} (\hyperlink{'tukiw}{'tukiw}+\allowbreak \hyperlink{ak}{ak})
Bhutanese; from Bhutan

\textbf{\hypertarget{'tukiwwon}{'tukiwwon}} \textit{n.} (\hyperlink{'tukiw}{'tukiw}+\allowbreak \hyperlink{won}{won})
Bhutanese; the Bhutanese people

\textbf{\hypertarget{'tukiwtilip}{'tukiwtilip}} \textit{n.} (\hyperlink{'tukiw}{'tukiw}+\allowbreak \hyperlink{tilip}{tilip})
Dzongkha

\textbf{\hypertarget{tutumu}{tutumu}} \textit{v.} (ono. [dudum dudum])
be rhythmic; pulse; cycle; oscillate; flash; beat; \hyperlink{tutumulon}{ʟᴏᴧ} happens rhythmically

\textbf{\hypertarget{tutumuec}{tutumuec}} \textit{n.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{ec}{ec})
heart

\textbf{\hypertarget{tutumulon}{tutumulon}} \textit{n.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{lon}{lon})
rhythm; routine; rhythmic

\textbf{\hypertarget{tutumulyan}{tutumulyan}} \textit{n.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{lyan}{lyan})
frequency

\textbf{\hypertarget{tutumuhila}{tutumuhila}} \textit{v.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{hila}{hila})
shake; vibrate; ʟᴏᴧ shakes

\textbf{\hypertarget{tutumuhilaki}{tutumuhilaki}} \textit{v.} (\hyperlink{tutumuhila}{tutumuhila}+\allowbreak \hyperlink{ki}{ki})
shake; vibrate; ʟєꜱ shakes ʟᴏᴧ

\textbf{\hypertarget{tutumucwelon}{tutumucwelon}} \textit{n.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{cwelon}{cwelon})
blood

\textbf{\hypertarget{tutumucwelonkoki}{tutumucwelonkoki}} \textit{v.} (\hyperlink{tutumucwelon}{tutumucwelon}+\allowbreak \hyperlink{koki}{koki})
bleed; ʟєꜱ bleeds out ʟᴏᴧ

\textbf{\hypertarget{tutumucwelonkil}{tutumucwelonkil}} \textit{n.} (\hyperlink{tutumucwelon}{tutumucwelon}+\allowbreak \hyperlink{kil}{kil})
leech

\textbf{\hypertarget{tutumutilum}{tutumutilum}} \textit{n.} (\hyperlink{tutumu}{tutumu}+\allowbreak \hyperlink{tilum}{tilum})
magazine; periodical

\textbf{\hypertarget{tup}{tup}} \textit{num.} (\hyperlink{lim}{\sout{lim}})
B; eleven; only used for duodecimal and hexadecimal

\textbf{\hypertarget{tupel}{tupel}} \textit{n.} (Epo. ⟨tubero⟩ [tuˈbero])
tuber; enlarged nutrient-storing structure of a plant

\textbf{\hypertarget{tupan}{tupan}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਤੂਫਾਨ}⟩ [t̪upʰɑn])
storm; tempest; violent and dangerous disturbance of the atmosphere

\textbf{\hypertarget{tupanak}{tupanak}} \textit{n.} (\hyperlink{tupan}{tupan}+\allowbreak \hyperlink{ak}{ak})
stormy; cyclonical

\textbf{\hypertarget{tupak}{tupak}} \textit{n.} (\hyperlink{tup}{tup}+\allowbreak \hyperlink{ak}{ak})
eleventh

\textbf{\hypertarget{tyen}{tyen}} \textit{num.} (Cmn. ⟨{\chinese{}點}⟩ [tjɛn˧˩˥])
point; radix point; period

\textbf{\hypertarget{'tyencin}{'tyencin}} \textit{n.} (Cmn. ⟨{\chinese{}天津}⟩ [tʰjɛn˥t͡ɕin˥])
Tianjin; Tientsin

\textbf{\hypertarget{'twinitat}{'twinitat}} \textit{n.} (Eng. ⟨Trinidad⟩ [tɹɪnɪdæd])
Trinidad; Cairi; Tukusi

\textbf{\hypertarget{'twinitatak}{'twinitatak}} \textit{n.} (\hyperlink{'twinitat}{'twinitat}+\allowbreak \hyperlink{ak}{ak})
Trididadian

\section{P}

\textbf{\hypertarget{pe}{pe}} \textit{v.} (Cmn. ⟨{\chinese{}陪}⟩ [pʰeɪ̯˧˥])
accompany; come with; be together; be beside; \textit{accompanitive}; \hyperlink{pelon}{ʟᴏᴧ} accompanies \hyperlink{peles}{ʟєꜱ}

\textbf{\hypertarget{'pe}{'pe}} \textit{n.} (ono. [p])
p; /p/; bilabial plosive

\textbf{\hypertarget{peal}{peal}} \textit{n.} (Msa. ⟨pear⟩ [pear])
pear; Pyrus

\textbf{\hypertarget{pealfolmo}{pealfolmo}} \textit{v.} (\hyperlink{peal}{peal}+\allowbreak \hyperlink{folmo}{folmo})
be pyriform; be pear-shaped; \hyperlink{pealfolmolon}{ʟᴏᴧ} is fatter on one side than the other

\textbf{\hypertarget{pealfolmolon}{pealfolmolon}} \textit{n.} (\hyperlink{pealfolmo}{pealfolmo}+\allowbreak \hyperlink{lon}{lon})
pyriform; pear-shaped

\textbf{\hypertarget{'peycin}{'peycin}} \textit{n.} (Cmn. ⟨{\chinese{}北京}⟩ [pej˨˩˦t͡ɕiŋ˥])
Beijing; Peking

\textbf{\hypertarget{pel}{pel}} \textit{num.} (Msa. ⟨per⟩ [per])
over; division; fraction; /

\textbf{\hypertarget{peles}{peles}} \textit{n.} (\hyperlink{pe}{pe}+\allowbreak \hyperlink{les}{les})
accompanied

\textbf{\hypertarget{pela}{pela}} \textit{v.} (\hyperlink{mota}{\sout{mota}})
be small; be little; \hyperlink{pelalon}{ʟᴏᴧ} has a low volume

\textbf{\hypertarget{pelaicilon}{pelaicilon}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{icilon}{icilon})
plankton

\textbf{\hypertarget{pelalon}{pelalon}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{lon}{lon})
small; little

\textbf{\hypertarget{pelalic}{pelalic}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{lic}{lic})
tardigrade; water bear; moss piglet; Tardigrada

\textbf{\hypertarget{'pelaw}{'pelaw}} \textit{n.} (Pau. ⟨Belau⟩ [bɛlaw])
Palau; Belau; Palaos; Pelew (landmass)

\textbf{\hypertarget{'pelawak}{'pelawak}} \textit{n.} (\hyperlink{'pelaw}{'pelaw}+\allowbreak \hyperlink{ak}{ak})
Palauan; from Palau

\textbf{\hypertarget{'pelawwon}{'pelawwon}} \textit{n.} (\hyperlink{'pelaw}{'pelaw}+\allowbreak \hyperlink{won}{won})
Palauan; the Palauan people

\textbf{\hypertarget{'pelawtec}{'pelawtec}} \textit{n.} (\hyperlink{'pelaw}{'pelaw}+\allowbreak \hyperlink{tec}{tec})
Palau; the Republic of Palau

\textbf{\hypertarget{'pelawtilip}{'pelawtilip}} \textit{n.} (\hyperlink{'pelaw}{'pelaw}+\allowbreak \hyperlink{tilip}{tilip})
Palauan; the Palauan language

\textbf{\hypertarget{pelamontalon}{pelamontalon}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{montalon}{montalon})
sedan; saloon; car

\textbf{\hypertarget{pelacai}{pelacai}} \textit{v.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{cai}{cai})
adore; be cute; ʟᴏᴧ finds \hyperlink{pelacailum}{ʟᴜᴍ} cute

\textbf{\hypertarget{pelacailum}{pelacailum}} \textit{n.} (\hyperlink{pelacai}{pelacai}+\allowbreak \hyperlink{lum}{lum})
cute

\textbf{\hypertarget{pelafut}{pelafut}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{fut}{fut})
berry

\textbf{\hypertarget{pelakap}{pelakap}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{kap}{kap})
minnow

\textbf{\hypertarget{pelakol}{pelakol}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{kol}{kol})
Brussels sprouts

\textbf{\hypertarget{pelaki}{pelaki}} \textit{v.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{ki}{ki})
shrink; contract; constrict; \hyperlink{pelakiles}{ʟєꜱ} shrinks ʟᴏᴧ

\textbf{\hypertarget{pelakiles}{pelakiles}} \textit{n.} (\hyperlink{pelaki}{pelaki}+\allowbreak \hyperlink{les}{les})
shrinker

\textbf{\hypertarget{pelakwap}{pelakwap}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{kwap}{kwap})
shrimp

\textbf{\hypertarget{pelatawh}{pelatawh}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{tawh}{tawh})
cherry

\textbf{\hypertarget{pelapucolon}{pelapucolon}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{pucolon}{pucolon})
apostrophe

\textbf{\hypertarget{pelapus}{pelapus}} \textit{n.} (\hyperlink{pela}{pela}+\allowbreak \hyperlink{pus}{pus})
zucchini; courgette

\textbf{\hypertarget{pelon}{pelon}} \textit{n.} (\hyperlink{pe}{pe}+\allowbreak \hyperlink{lon}{lon})
companion; accompaniment; mate; partner; company; comrade; together; beside

\textbf{\hypertarget{'pelillium}{'pelillium}} \textit{n.} (Lat. ⟨beryllium⟩ [bɛrillɪʊ̃])
beryllium

\textbf{\hypertarget{'pelis}{'pelis}} \textit{n.} (Eng. ⟨Belize⟩ [bəˈliːz])
Belize

\textbf{\hypertarget{'pelisak}{'pelisak}} \textit{n.} (\hyperlink{'pelis}{'pelis}+\allowbreak \hyperlink{ak}{ak})
Belizean; from Belize

\textbf{\hypertarget{'peliswon}{'peliswon}} \textit{n.} (\hyperlink{'pelis}{'pelis}+\allowbreak \hyperlink{won}{won})
Belizean; the Belizean people

\textbf{\hypertarget{'pelu}{'pelu}} \textit{n.} (Spa. ⟨Perú⟩ [peˈɾu])
Peru

\textbf{\hypertarget{'peluak}{'peluak}} \textit{n.} (\hyperlink{'pelu}{'pelu}+\allowbreak \hyperlink{ak}{ak})
Peruvian; from Peru

\textbf{\hypertarget{'peluwon}{'peluwon}} \textit{n.} (\hyperlink{'pelu}{'pelu}+\allowbreak \hyperlink{won}{won})
Peruvian; the Peruvian people

\textbf{\hypertarget{pellim}{pellim}} \textit{num.} (\hyperlink{pel}{pel}+\allowbreak \hyperlink{lim}{lim})
fifth; one fifth; 1/5; .2

\textbf{\hypertarget{pelhat}{pelhat}} \textit{num.} (\hyperlink{pel}{pel}+\allowbreak \hyperlink{hat}{hat})
eighth; one eighth; 1/8; .125

\textbf{\hypertarget{pelsan}{pelsan}} \textit{num.} (\hyperlink{pel}{pel}+\allowbreak \hyperlink{san}{san})
third; one third; 1/3; .̅3

\textbf{\hypertarget{pelfol}{pelfol}} \textit{num.} (\hyperlink{pel}{pel}+\allowbreak \hyperlink{fol}{fol})
quarter; fourth; one fourth; 1/4; .25

\textbf{\hypertarget{'pelkia}{'pelkia}} \textit{n.} (Nld. ⟨België⟩ [bɛlɣiə])
Belgium

\textbf{\hypertarget{'pelkiaak}{'pelkiaak}} \textit{n.} (\hyperlink{'pelkia}{'pelkia}+\allowbreak \hyperlink{ak}{ak})
Belgian; from Belgium

\textbf{\hypertarget{'pelkiawon}{'pelkiawon}} \textit{n.} (\hyperlink{'pelkia}{'pelkia}+\allowbreak \hyperlink{won}{won})
Belgian; the Belgian people

\textbf{\hypertarget{peltos}{peltos}} \textit{num.} (\hyperlink{pel}{pel}+\allowbreak \hyperlink{tos}{tos})
half; one half; 1/2; .5

\textbf{\hypertarget{peltosefe}{peltosefe}} \textit{v.} (\hyperlink{peltos}{peltos}+\allowbreak \hyperlink{efe}{efe})
be minority; \hyperlink{peltosefelon}{ʟᴏᴧ} is less than half of ʟᴜᴍ

\textbf{\hypertarget{peltosefelon}{peltosefelon}} \textit{n.} (\hyperlink{peltosefe}{peltosefe}+\allowbreak \hyperlink{lon}{lon})
minority

\textbf{\hypertarget{peltososo}{peltososo}} \textit{v.} (\hyperlink{peltos}{peltos}+\allowbreak \hyperlink{oso}{oso})
be majority; be most; \hyperlink{peltososolon}{ʟᴏᴧ} is most of ʟᴜᴍ

\textbf{\hypertarget{peltososolon}{peltososolon}} \textit{n.} (\hyperlink{peltososo}{peltososo}+\allowbreak \hyperlink{lon}{lon})
majority; most

\textbf{\hypertarget{pewo}{pewo}} \textit{v.} (\hyperlink{moye}{\sout{moye}})
misunderstand; be confused; be cryptic; \hyperlink{pewolon}{ʟᴏᴧ} does not understand \hyperlink{pewolum}{ʟᴜᴍ} well

\textbf{\hypertarget{pewolon}{pewolon}} \textit{n.} (\hyperlink{pewo}{pewo}+\allowbreak \hyperlink{lon}{lon})
confused

\textbf{\hypertarget{pewolum}{pewolum}} \textit{n.} (\hyperlink{pewo}{pewo}+\allowbreak \hyperlink{lum}{lum})
misunderstood; cryptic

\textbf{\hypertarget{pewoki}{pewoki}} \textit{v.} (\hyperlink{pewo}{pewo}+\allowbreak \hyperlink{ki}{ki})
confuse; unlearn; \hyperlink{pewokiles}{ʟєꜱ} makes ʟᴏᴧ stop understanding ʟᴜᴍ

\textbf{\hypertarget{pewokiles}{pewokiles}} \textit{n.} (\hyperlink{pewoki}{pewoki}+\allowbreak \hyperlink{les}{les})
confuser

\textbf{\hypertarget{pewopatili}{pewopatili}} \textit{v.} (\hyperlink{pewo}{pewo}+\allowbreak \hyperlink{patili}{patili})
encode; ʟєꜱ encodes ʟᴏᴧ as ʟᴜᴍ

\textbf{\hypertarget{pewopatililip}{pewopatililip}} \textit{n.} (\hyperlink{pewopatili}{pewopatili}+\allowbreak \hyperlink{lip}{lip})
code

\textbf{\hypertarget{'penen}{'penen}} \textit{n.} (Fra. ⟨Bénin⟩ [benɛ̃])
Benin

\textbf{\hypertarget{'penenak}{'penenak}} \textit{n.} (\hyperlink{'penen}{'penen}+\allowbreak \hyperlink{ak}{ak})
Beninese; Beninois; from Benin

\textbf{\hypertarget{'penenwon}{'penenwon}} \textit{n.} (\hyperlink{'penen}{'penen}+\allowbreak \hyperlink{won}{won})
Beninese; the Beninese people

\textbf{\hypertarget{'peneswela}{'peneswela}} \textit{n.} (Spa. ⟨Venezuela⟩ [beneˈswela])
Venezuelan; the Venezuelan people

\textbf{\hypertarget{'peneswelaak}{'peneswelaak}} \textit{n.} (\hyperlink{'peneswela}{'peneswela}+\allowbreak \hyperlink{ak}{ak})
Venezuelan; from Venezuela

\textbf{\hypertarget{'peneswelatec}{'peneswelatec}} \textit{n.} (\hyperlink{'peneswela}{'peneswela}+\allowbreak \hyperlink{tec}{tec})
Venezuela

\textbf{\hypertarget{pensi}{pensi}} \textit{v.} (Epo. ⟨pensi⟩ [ˈpensi])
think; appear; be apparent; \hyperlink{pensilon}{ʟᴏᴧ} consciously decides that \hyperlink{pensilum}{ʟᴜᴍ} is true; see "be sure" and "believe"

\textbf{\hypertarget{pensiyato}{pensiyato}} \textit{v.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{yato}{yato})
disagree; ʟᴏᴧ disagrees with ʟᴜᴍ

\textbf{\hypertarget{pensilon}{pensilon}} \textit{n.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{lon}{lon})
thinker; accepter

\textbf{\hypertarget{pensilial}{pensilial}} \textit{n.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{lial}{lial})
evidence

\textbf{\hypertarget{pensilum}{pensilum}} \textit{n.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{lum}{lum})
opinion; apparent

\textbf{\hypertarget{pensiwale}{pensiwale}} \textit{v.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{wale}{wale})
agree; ʟᴏᴧ agrees with ʟᴜᴍ

\textbf{\hypertarget{pensisoma}{pensisoma}} \textit{v.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{soma}{soma})
do psychology; \hyperlink{pensisomales}{ʟєꜱ} studies the human mind to learn about \hyperlink{pensisomalon}{ʟᴏᴧ}

\textbf{\hypertarget{pensisomales}{pensisomales}} \textit{n.} (\hyperlink{pensisoma}{pensisoma}+\allowbreak \hyperlink{les}{les})
psychologist

\textbf{\hypertarget{pensisomalon}{pensisomalon}} \textit{n.} (\hyperlink{pensisoma}{pensisoma}+\allowbreak \hyperlink{lon}{lon})
psychology

\textbf{\hypertarget{pensiki}{pensiki}} \textit{v.} (\hyperlink{pensi}{pensi}+\allowbreak \hyperlink{ki}{ki})
persuade; convince; ʟєꜱ leads ʟᴏᴧ to determine that ʟᴜᴍ is true

\textbf{\hypertarget{pemamalon}{pemamalon}} \textit{n.} (\hyperlink{pe}{pe}+\allowbreak \hyperlink{mamalon}{mamalon})
sibling

\textbf{\hypertarget{'pehen}{'pehen}} \textit{n.} (Dan. ⟨Bering⟩ [beʁɛŋɡ])
Bering; Vitus Jonassen Bering; Ivan Ivanovich Bering

\textbf{\hypertarget{'pehenlawt}{'pehenlawt}} \textit{n.} (\hyperlink{'pehen}{'pehen}+\allowbreak \hyperlink{lawt}{lawt})
Bering Sea

\textbf{\hypertarget{peha}{peha}} \textit{v.} (\hyperlink{moca}{\sout{moca}})
be bored; \hyperlink{pehalon}{ʟᴏᴧ} is bored by \hyperlink{pehalum}{ʟᴜᴍ}

\textbf{\hypertarget{pehalon}{pehalon}} \textit{n.} (\hyperlink{peha}{peha}+\allowbreak \hyperlink{lon}{lon})
bored

\textbf{\hypertarget{pehalum}{pehalum}} \textit{n.} (\hyperlink{peha}{peha}+\allowbreak \hyperlink{lum}{lum})
boring

\textbf{\hypertarget{pehafake}{pehafake}} \textit{v.} (\hyperlink{peha}{peha}+\allowbreak \hyperlink{fake}{fake})
be sober; be dry; \hyperlink{pehafakelon}{ʟᴏᴧ} is sober

\textbf{\hypertarget{pehafakelon}{pehafakelon}} \textit{n.} (\hyperlink{pehafake}{pehafake}+\allowbreak \hyperlink{lon}{lon})
sober; dry

\textbf{\hypertarget{pehaki}{pehaki}} \textit{v.} (\hyperlink{peha}{peha}+\allowbreak \hyperlink{ki}{ki})
bore; tire; kill joy; ʟєꜱ makes ʟᴏᴧ be bored by ʟᴜᴍ

\textbf{\hypertarget{pehakifake}{pehakifake}} \textit{v.} (\hyperlink{peha}{peha}+\allowbreak \hyperlink{ki}{ki}+\allowbreak \hyperlink{fake}{fake})
have hangover; ʟᴏᴧ has a hangover

\textbf{\hypertarget{pes}{pes}} \textit{n.} (Spa. ⟨pez⟩ [pes])
fish; pisces; ichthyes; Gnathostomata minus Tetrapoda

\textbf{\hypertarget{pesak}{pesak}} \textit{n.} (\hyperlink{pes}{pes}+\allowbreak \hyperlink{ak}{ak})
pescous; aquatic

\textbf{\hypertarget{'peso}{'peso}} \textit{n.} (Spa. ⟨peso⟩ [ˈpeso])
peso; \$; ₱

\textbf{\hypertarget{peslisat}{peslisat}} \textit{n.} (\hyperlink{pes}{pes}+\allowbreak \hyperlink{lisat}{lisat})
amphibian

\textbf{\hypertarget{peslisatak}{peslisatak}} \textit{n.} (\hyperlink{peslisat}{peslisat}+\allowbreak \hyperlink{ak}{ak})
amphibious

\textbf{\hypertarget{pesfolmo}{pesfolmo}} \textit{v.} (\hyperlink{pes}{pes}+\allowbreak \hyperlink{folmo}{folmo})
be pisciform; be fish-shaped; \hyperlink{pesfolmolon}{ʟᴏᴧ} has a larger round bit connected to a triangular bit

\textbf{\hypertarget{pesfolmolon}{pesfolmolon}} \textit{n.} (\hyperlink{pesfolmo}{pesfolmo}+\allowbreak \hyperlink{lon}{lon})
pisciform; fish-shaped

\textbf{\hypertarget{peka}{peka}} \textit{v.} (Xho. ⟨-pheka⟩ [pʰɛka])
cook; prepare; make; boil; steam; broil; marinate; grill; smoke; bake; toast; microwave; \hyperlink{pekales}{ʟєꜱ} cooks \hyperlink{pekalon}{ʟᴏᴧ}

\textbf{\hypertarget{pekales}{pekales}} \textit{n.} (\hyperlink{peka}{peka}+\allowbreak \hyperlink{les}{les})
cook; chef; baker

\textbf{\hypertarget{pekalon}{pekalon}} \textit{n.} (\hyperlink{peka}{peka}+\allowbreak \hyperlink{lon}{lon})
cooking

\textbf{\hypertarget{pekaluat}{pekaluat}} \textit{n.} (\hyperlink{peka}{peka}+\allowbreak \hyperlink{luat}{luat})
pot; pan

\textbf{\hypertarget{pekweki}{pekweki}} \textit{v.} (\hyperlink{pe}{pe}+\allowbreak \hyperlink{kweki}{kweki})
interact; interfere; involve; ʟєꜱ makes ʟᴏᴧ interact with ʟᴜᴍ

\textbf{\hypertarget{pekwekiluat}{pekwekiluat}} \textit{n.} (\hyperlink{pekweki}{pekweki}+\allowbreak \hyperlink{luat}{luat})
interface

\textbf{\hypertarget{pet}{pet}} \textit{n.} (Epo. ⟨beto⟩ [ˈbeto])
beet; beetroot; sugar beet; chard; Beta

\textbf{\hypertarget{peta}{peta}} \textit{v.} (Sot. ⟨pheta⟩ [pʰetʼɑ])
repeat; do again; return to; ʟєꜱ makes ʟᴏᴧ happen multiple times

\textbf{\hypertarget{petalwelkwekilon}{petalwelkwekilon}} \textit{n.} (\hyperlink{peta}{peta}+\allowbreak \hyperlink{lwelkwekilon}{lwelkwekilon})
tradition; ritual; ceremony

\textbf{\hypertarget{petasoma}{petasoma}} \textit{v.} (\hyperlink{peta}{peta}+\allowbreak \hyperlink{soma}{soma})
research; \hyperlink{petasomales}{ʟєꜱ} finds information about \hyperlink{petasomalum}{ʟᴜᴍ} and uses it to update \hyperlink{petasomalon}{ʟᴏᴧ}

\textbf{\hypertarget{petasomales}{petasomales}} \textit{n.} (\hyperlink{petasoma}{petasoma}+\allowbreak \hyperlink{les}{les})
researcher

\textbf{\hypertarget{petasomalon}{petasomalon}} \textit{n.} (\hyperlink{petasoma}{petasoma}+\allowbreak \hyperlink{lon}{lon})
research; notes; archive

\textbf{\hypertarget{petasomalum}{petasomalum}} \textit{n.} (\hyperlink{petasoma}{petasoma}+\allowbreak \hyperlink{lum}{lum})
reasearch topic

\textbf{\hypertarget{petue}{petue}} \textit{v.} (\hyperlink{pe}{pe}+\allowbreak \hyperlink{tue}{tue})
share; be communal; the members of \hyperlink{petuelon}{ʟᴏᴧ} share \hyperlink{petuelum}{ʟᴜᴍ}

\textbf{\hypertarget{petuelon}{petuelon}} \textit{n.} (\hyperlink{petue}{petue}+\allowbreak \hyperlink{lon}{lon})
sharers

\textbf{\hypertarget{petuelum}{petuelum}} \textit{n.} (\hyperlink{petue}{petue}+\allowbreak \hyperlink{lum}{lum})
commons; communal

\textbf{\hypertarget{pale}{pale}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਬਾਰੇ}⟩ [bɑɾe])
be related; be about; focus; \hyperlink{palelon}{ʟᴏᴧ} is about \hyperlink{palelum}{ʟᴜᴍ}

\textbf{\hypertarget{pal}{pal}} \textit{n.} (Spa. ⟨palo⟩ [ˈpalo])
stick; rod; limb; beam; rigid roughly straight one-dimensional object

\textbf{\hypertarget{palelon}{palelon}} \textit{n.} (\hyperlink{pale}{pale}+\allowbreak \hyperlink{lon}{lon})
related; about

\textbf{\hypertarget{palelum}{palelum}} \textit{n.} (\hyperlink{pale}{pale}+\allowbreak \hyperlink{lum}{lum})
topic; subject

\textbf{\hypertarget{'pala}{'pala}} \textit{n.} (Ind. ⟨pala⟩ [pala])
nutmeg; Myristica fragrans

\textbf{\hypertarget{'palah}{'palah}} \textit{n.} (Ara. ⟨{\arabics{}بلح}⟩ [balɑħ])
date; date palm; Phoenix dactylifera

\textbf{\hypertarget{'palahnu}{'palahnu}} \textit{v.} (\hyperlink{'palah}{'palah}+\allowbreak \hyperlink{nu}{nu})
break up; stop going out; ʟєꜱ makes ʟᴏᴧ stop dating ʟᴜᴍ

\textbf{\hypertarget{'palahki}{'palahki}} \textit{v.} (\hyperlink{'palah}{'palah}+\allowbreak \hyperlink{ki}{ki})
ask out; set up; start going out; \hyperlink{'palahkiles}{ʟєꜱ} makes ʟᴏᴧ start dating ʟᴜᴍ

\textbf{\hypertarget{'palahkiles}{'palahkiles}} \textit{n.} (\hyperlink{'palahki}{'palahki}+\allowbreak \hyperlink{les}{les})
matchmaker

\textbf{\hypertarget{'palasiw}{'palasiw}} \textit{n.} (Por. ⟨Brasil⟩ [bɾaˈziw])
Brazil

\textbf{\hypertarget{'palasiwak}{'palasiwak}} \textit{n.} (\hyperlink{'palasiw}{'palasiw}+\allowbreak \hyperlink{ak}{ak})
Brazilian; from Brazil

\textbf{\hypertarget{'palasiwwon}{'palasiwwon}} \textit{n.} (\hyperlink{'palasiw}{'palasiw}+\allowbreak \hyperlink{won}{won})
Brazilian; the Brazilian people

\textbf{\hypertarget{'palasiwtec}{'palasiwtec}} \textit{n.} (\hyperlink{'palasiw}{'palasiw}+\allowbreak \hyperlink{tec}{tec})
Brazil

\textbf{\hypertarget{'palakway}{'palakway}} \textit{n.} (Gug. ⟨Paraguái⟩ [paɾaˈɰwaj])
Paraguay

\textbf{\hypertarget{'palakwayak}{'palakwayak}} \textit{n.} (\hyperlink{'palakway}{'palakway}+\allowbreak \hyperlink{ak}{ak})
Paraguayan; from Paraguay

\textbf{\hypertarget{'palakwaywon}{'palakwaywon}} \textit{n.} (\hyperlink{'palakway}{'palakway}+\allowbreak \hyperlink{won}{won})
Paraguayan; the Paraguayan people

\textbf{\hypertarget{pali}{pali}} \textit{v.} (Hin. ⟨{\devanagari{}भारी}⟩ [b̤aːriː])
be heavy; weigh; be massive; \hyperlink{palilon}{ʟᴏᴧ} is heavy

\textbf{\hypertarget{palilon}{palilon}} \textit{n.} (\hyperlink{pali}{pali}+\allowbreak \hyperlink{lon}{lon})
weight; heavyweight; heavy; massive

\textbf{\hypertarget{palilyan}{palilyan}} \textit{n.} (\hyperlink{pali}{pali}+\allowbreak \hyperlink{lyan}{lyan})
weight; mass

\textbf{\hypertarget{palinoluat}{palinoluat}} \textit{n.} (\hyperlink{pali}{pali}+\allowbreak \hyperlink{noluat}{noluat})
scale; balance

\textbf{\hypertarget{paliki}{paliki}} \textit{v.} (\hyperlink{pali}{pali}+\allowbreak \hyperlink{ki}{ki})
weight; weigh; burden; ʟєꜱ weighs down ʟᴏᴧ

\textbf{\hypertarget{palitatu}{palitatu}} \textit{v.} (\hyperlink{pali}{pali}+\allowbreak \hyperlink{tatu}{tatu})
be lead; \hyperlink{palitatulon}{ʟᴏᴧ} is made of lead

\textbf{\hypertarget{palitatulon}{palitatulon}} \textit{n.} (\hyperlink{palitatu}{palitatu}+\allowbreak \hyperlink{lon}{lon})
lead

\textbf{\hypertarget{'palunay}{'palunay}} \textit{n.} (Kxd. ⟨{\arabics{}بروني}⟩ [brunaj])
Brunei

\textbf{\hypertarget{'palunayak}{'palunayak}} \textit{n.} (\hyperlink{'palunay}{'palunay}+\allowbreak \hyperlink{ak}{ak})
Bruneian; from Brunei

\textbf{\hypertarget{'palunaywon}{'palunaywon}} \textit{n.} (\hyperlink{'palunay}{'palunay}+\allowbreak \hyperlink{won}{won})
Bruneian; the Bruneian people

\textbf{\hypertarget{'palunaytilip}{'palunaytilip}} \textit{n.} (\hyperlink{'palunay}{'palunay}+\allowbreak \hyperlink{tilip}{tilip})
Brunei Malay

\textbf{\hypertarget{palnyamaluat}{palnyamaluat}} \textit{n.} (\hyperlink{pal}{pal}+\allowbreak \hyperlink{nyamaluat}{nyamaluat})
chopsticks

\textbf{\hypertarget{palcuc}{palcuc}} \textit{n.} (\hyperlink{pal}{pal}+\allowbreak \hyperlink{cuc}{cuc})
stickbug

\textbf{\hypertarget{'palkali}{'palkali}} \textit{n.} (Bul. ⟨българи⟩ [ˈbɤɫɡɐri])
Bulgarian; the Bulgarian people

\textbf{\hypertarget{'palkaliak}{'palkaliak}} \textit{n.} (\hyperlink{'palkali}{'palkali}+\allowbreak \hyperlink{ak}{ak})
Bulgarian; from Bulgaria

\textbf{\hypertarget{'palkalitec}{'palkalitec}} \textit{n.} (\hyperlink{'palkali}{'palkali}+\allowbreak \hyperlink{tec}{tec})
Bulgaria

\textbf{\hypertarget{'palkalitilip}{'palkalitilip}} \textit{n.} (\hyperlink{'palkali}{'palkali}+\allowbreak \hyperlink{tilip}{tilip})
Bulgarian; the Bulgarian language

\textbf{\hypertarget{palto}{palto}} \textit{v.} (Epo. ⟨parto⟩ [ˈparto])
be part; be in; compose; contain; comprise; include; \hyperlink{paltolon}{ʟᴏᴧ} is part of \hyperlink{paltolum}{ʟᴜᴍ}

\textbf{\hypertarget{paltolon}{paltolon}} \textit{n.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{lon}{lon})
piece; component; element; detail; part; in

\textbf{\hypertarget{paltoloniti}{paltoloniti}} \textit{v.} (\hyperlink{paltolon}{paltolon}+\allowbreak \hyperlink{iti}{iti})
be detail-oriented; \hyperlink{paltolonitilon}{ʟᴏᴧ} tends to focus on small details

\textbf{\hypertarget{paltolonitilon}{paltolonitilon}} \textit{n.} (\hyperlink{paltoloniti}{paltoloniti}+\allowbreak \hyperlink{lon}{lon})
detail-oriented

\textbf{\hypertarget{paltolum}{paltolum}} \textit{n.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{lum}{lum})
group; whole; set; party; association; organisation; institution

\textbf{\hypertarget{paltolumiti}{paltolumiti}} \textit{v.} (\hyperlink{paltolum}{paltolum}+\allowbreak \hyperlink{iti}{iti})
think big picture; think grandly; ʟᴏᴧ tends to think of the big picture

\textbf{\hypertarget{paltolyan}{paltolyan}} \textit{n.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{lyan}{lyan})
portion; fraction

\textbf{\hypertarget{paltonu}{paltonu}} \textit{v.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{nu}{nu})
leave; separate; remove; \hyperlink{paltonules}{ʟєꜱ} makes ʟᴏᴧ leave ʟᴜᴍ

\textbf{\hypertarget{paltonules}{paltonules}} \textit{n.} (\hyperlink{paltonu}{paltonu}+\allowbreak \hyperlink{les}{les})
remover

\textbf{\hypertarget{paltokanu}{paltokanu}} \textit{v.} (\hyperlink{pal}{pal}+\allowbreak \hyperlink{tokanu}{tokanu})
stab; ʟєꜱ stabs \hyperlink{paltokanulon}{ʟᴏᴧ}

\textbf{\hypertarget{paltokanulon}{paltokanulon}} \textit{n.} (\hyperlink{paltokanu}{paltokanu}+\allowbreak \hyperlink{lon}{lon})
pincushion

\textbf{\hypertarget{paltokanuluat}{paltokanuluat}} \textit{n.} (\hyperlink{paltokanu}{paltokanu}+\allowbreak \hyperlink{luat}{luat})
dagger; stake

\textbf{\hypertarget{paltoki}{paltoki}} \textit{v.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{ki}{ki})
join; incorporate; add; append; \hyperlink{paltokiles}{ʟєꜱ} makes ʟᴏᴧ join ʟᴜᴍ

\textbf{\hypertarget{paltokiles}{paltokiles}} \textit{n.} (\hyperlink{paltoki}{paltoki}+\allowbreak \hyperlink{les}{les})
joiner

\textbf{\hypertarget{paltopowi}{paltopowi}} \textit{v.} (\hyperlink{palto}{palto}+\allowbreak \hyperlink{powi}{powi})
be inclusive; be open; be eligible; \hyperlink{paltopowilum}{ʟᴜᴍ} is open to \hyperlink{paltopowilon}{ʟᴏᴧ} joining

\textbf{\hypertarget{paltopowilon}{paltopowilon}} \textit{n.} (\hyperlink{paltopowi}{paltopowi}+\allowbreak \hyperlink{lon}{lon})
eligible

\textbf{\hypertarget{paltopowilum}{paltopowilum}} \textit{n.} (\hyperlink{paltopowi}{paltopowi}+\allowbreak \hyperlink{lum}{lum})
inclusive; open

\textbf{\hypertarget{paltopowinyo}{paltopowinyo}} \textit{v.} (\hyperlink{paltopowi}{paltopowi}+\allowbreak \hyperlink{nyo}{nyo})
be exclusive; be closed; be ineligible; \hyperlink{paltopowinyolum}{ʟᴜᴍ} excludes \hyperlink{paltopowinyolon}{ʟᴏᴧ} from joining

\textbf{\hypertarget{paltopowinyolon}{paltopowinyolon}} \textit{n.} (\hyperlink{paltopowinyo}{paltopowinyo}+\allowbreak \hyperlink{lon}{lon})
ineligible

\textbf{\hypertarget{paltopowinyolum}{paltopowinyolum}} \textit{n.} (\hyperlink{paltopowinyo}{paltopowinyo}+\allowbreak \hyperlink{lum}{lum})
exclusive; closed

\textbf{\hypertarget{pawe}{pawe}} \textit{v.} (Cmn. ⟨{\chinese{}包围}⟩ [pɑʊ̯˥weɪ̯˧˥])
surround; cover; \hyperlink{pawelon}{ʟᴏᴧ} covers most of \hyperlink{pawelum}{ʟᴜᴍ}

\textbf{\hypertarget{pawelon}{pawelon}} \textit{n.} (\hyperlink{pawe}{pawe}+\allowbreak \hyperlink{lon}{lon})
surroundings; cover; environment; context

\textbf{\hypertarget{pawelum}{pawelum}} \textit{n.} (\hyperlink{pawe}{pawe}+\allowbreak \hyperlink{lum}{lum})
surrounded; covered

\textbf{\hypertarget{pawelyan}{pawelyan}} \textit{n.} (\hyperlink{pawe}{pawe}+\allowbreak \hyperlink{lyan}{lyan})
coverage

\textbf{\hypertarget{paweki}{paweki}} \textit{v.} (\hyperlink{pawe}{pawe}+\allowbreak \hyperlink{ki}{ki})
surround; cover; \hyperlink{pawekiles}{ʟєꜱ} surrounds ʟᴏᴧ with ʟᴜᴍ

\textbf{\hypertarget{pawekiles}{pawekiles}} \textit{n.} (\hyperlink{paweki}{paweki}+\allowbreak \hyperlink{les}{les})
coverer

\textbf{\hypertarget{pawaf}{pawaf}} \textit{n.} (ono. [baw waw wof])
canine; dog; wolf; dingo; fox; pup; cub; Canidae

\textbf{\hypertarget{pawafak}{pawafak}} \textit{n.} (\hyperlink{pawaf}{pawaf}+\allowbreak \hyperlink{ak}{ak})
canine

\textbf{\hypertarget{pana}{pana}} \textit{ptcl.} (Cmn. ⟨{\chinese{}吧}⟩ [pa])
please; \textit{polite imperative mood}

\textbf{\hypertarget{'panama}{'panama}} \textit{n.} (Spa. ⟨Panamá⟩ [panaˈma])
Panama

\textbf{\hypertarget{'panamaak}{'panamaak}} \textit{n.} (\hyperlink{'panama}{'panama}+\allowbreak \hyperlink{ak}{ak})
Panamanian; from Panama

\textbf{\hypertarget{'panamawon}{'panamawon}} \textit{n.} (\hyperlink{'panama}{'panama}+\allowbreak \hyperlink{won}{won})
Panamanian; the Panamanian people

\textbf{\hypertarget{panati}{panati}} \textit{v.} (\hyperlink{pana}{pana}+\allowbreak \hyperlink{ti}{ti})
request; \hyperlink{panatiles}{ʟєꜱ} politely asks \hyperlink{panatilon}{ʟᴏᴧ} to make \hyperlink{panatilum}{ʟᴜᴍ} happen

\textbf{\hypertarget{panatiles}{panatiles}} \textit{n.} (\hyperlink{panati}{panati}+\allowbreak \hyperlink{les}{les})
requester

\textbf{\hypertarget{panatilon}{panatilon}} \textit{n.} (\hyperlink{panati}{panati}+\allowbreak \hyperlink{lon}{lon})
requestee

\textbf{\hypertarget{panatilum}{panatilum}} \textit{n.} (\hyperlink{panati}{panati}+\allowbreak \hyperlink{lum}{lum})
request

\textbf{\hypertarget{'panla}{'panla}} \textit{n.} (Ben. ⟨{\bengali{}বাংলা}⟩ [ˈbaŋla])
Bangla

\textbf{\hypertarget{'panlaak}{'panlaak}} \textit{n.} (\hyperlink{'panla}{'panla}+\allowbreak \hyperlink{ak}{ak})
Bangladeshi; from Bangladesh

\textbf{\hypertarget{'panlawon}{'panlawon}} \textit{n.} (\hyperlink{'panla}{'panla}+\allowbreak \hyperlink{won}{won})
Bengali; the Bengali people

\textbf{\hypertarget{'panlatec}{'panlatec}} \textit{n.} (\hyperlink{'panla}{'panla}+\allowbreak \hyperlink{tec}{tec})
Bangladesh

\textbf{\hypertarget{'panlatecwon}{'panlatecwon}} \textit{n.} (\hyperlink{'panlatec}{'panlatec}+\allowbreak \hyperlink{won}{won})
Bangladeshi; the Bangladeshi people

\textbf{\hypertarget{'panlatilip}{'panlatilip}} \textit{n.} (\hyperlink{'panla}{'panla}+\allowbreak \hyperlink{tilip}{tilip})
Bengali; Bangla; the Bengali language

\textbf{\hypertarget{'pancap}{'pancap}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਪੰਜਾਬ}⟩ [pə̃d͡ʒɑːb])
Pubjab; Panjab

\textbf{\hypertarget{'pancapak}{'pancapak}} \textit{n.} (\hyperlink{'pancap}{'pancap}+\allowbreak \hyperlink{ak}{ak})
Punjabi; in Punjabi

\textbf{\hypertarget{'pancapwon}{'pancapwon}} \textit{n.} (\hyperlink{'pancap}{'pancap}+\allowbreak \hyperlink{won}{won})
Punjabi; the Punjabi people

\textbf{\hypertarget{'pancaptilip}{'pancaptilip}} \textit{n.} (\hyperlink{'pancap}{'pancap}+\allowbreak \hyperlink{tilip}{tilip})
Punjabi; the Punjabi language

\textbf{\hypertarget{'pama}{'pama}} \textit{n.} (Mya. ⟨{\myanmar{}ဗမာ}⟩ [bəmà])
Bamar; Burmese; Burman; the Burmese people

\textbf{\hypertarget{'pamaak}{'pamaak}} \textit{n.} (\hyperlink{'pama}{'pama}+\allowbreak \hyperlink{ak}{ak})
Myanma; Burmese; from Myanmar

\textbf{\hypertarget{'pamatec}{'pamatec}} \textit{n.} (\hyperlink{'pama}{'pama}+\allowbreak \hyperlink{tec}{tec})
Myanmar; Burma

\textbf{\hypertarget{'pamatilip}{'pamatilip}} \textit{n.} (\hyperlink{'pama}{'pama}+\allowbreak \hyperlink{tilip}{tilip})
Burmese; Myanmar; the Burmese language

\textbf{\hypertarget{pamapolte}{pamapolte}} \textit{v.} (Ben. ⟨{\bengali{}বামাবর্তে}⟩ [bamabɔrt̪e])
be turned counterclockwise; be widdershins; \hyperlink{pamapoltelon}{ʟᴏᴧ} appears rotated counterclockwise from the orientation \hyperlink{pamapoltelum}{ʟᴜᴍ} from the point of view of \hyperlink{pamapoltelum}{ʟᴜᴍ}

\textbf{\hypertarget{pamapoltelon}{pamapoltelon}} \textit{n.} (\hyperlink{pamapolte}{pamapolte}+\allowbreak \hyperlink{lon}{lon})
turned counterclockwise; widdershins

\textbf{\hypertarget{pamapoltelum}{pamapoltelum}} \textit{n.} (\hyperlink{pamapolte}{pamapolte}+\allowbreak \hyperlink{lum}{lum})
original orientation; right-side up

\textbf{\hypertarget{pamapoltelyan}{pamapoltelyan}} \textit{n.} (\hyperlink{pamapolte}{pamapolte}+\allowbreak \hyperlink{lyan}{lyan})
orientation; rotation

\textbf{\hypertarget{pamapolteki}{pamapolteki}} \textit{v.} (\hyperlink{pamapolte}{pamapolte}+\allowbreak \hyperlink{ki}{ki})
rotate counterclockwise; \hyperlink{pamapoltekiles}{ʟєꜱ} turns ʟᴏᴧ counterclockwise from ʟᴜᴍ’s point of view

\textbf{\hypertarget{pamapoltekiles}{pamapoltekiles}} \textit{n.} (\hyperlink{pamapolteki}{pamapolteki}+\allowbreak \hyperlink{les}{les})
counterclockwise turner

\textbf{\hypertarget{'pahai}{'pahai}} \textit{n.} (Fas. ⟨{\arabics{}بهائی‎}⟩ [ba˨ˈha˦ʔi˦])
Bahá’í; the Bahá’í Faith; Bahaism

\textbf{\hypertarget{'pahaiak}{'pahaiak}} \textit{n.} (\hyperlink{'pahai}{'pahai}+\allowbreak \hyperlink{ak}{ak})
Bahá’í; of the Bahá’í Faith

\textbf{\hypertarget{'pahaiwon}{'pahaiwon}} \textit{n.} (\hyperlink{'pahai}{'pahai}+\allowbreak \hyperlink{won}{won})
Bahá’í; followers of Bahá’u’lláh

\textbf{\hypertarget{'pahama}{'pahama}} \textit{n.} (Eng. ⟨The Bahamas⟩ [bəˈhɑːmə])
The Bahamas

\textbf{\hypertarget{'pahamaak}{'pahamaak}} \textit{n.} (\hyperlink{'pahama}{'pahama}+\allowbreak \hyperlink{ak}{ak})
Bahamian; from the Bahamas

\textbf{\hypertarget{'pahamatec}{'pahamatec}} \textit{n.} (\hyperlink{'pahama}{'pahama}+\allowbreak \hyperlink{tec}{tec})
Bahamian; the Bahamian People

\textbf{\hypertarget{'pahamatilip}{'pahamatilip}} \textit{n.} (\hyperlink{'pahama}{'pahama}+\allowbreak \hyperlink{tilip}{tilip})
Bahamian Creole

\textbf{\hypertarget{'pahasafil}{'pahasafil}} \textit{n.} (Fra. ⟨Brazzaville⟩ [bʁazavil])
Brazzaville

\textbf{\hypertarget{'pahasafil'konotec}{'pahasafil'konotec}} \textit{n.} (\hyperlink{'pahasafil}{'pahasafil}+\allowbreak \hyperlink{'konotec}{'konotec})
Republic of the Congo

\textbf{\hypertarget{'pahasafil'konotecwon}{'pahasafil'konotecwon}} \textit{n.} (\hyperlink{'pahasafil'konotec}{'pahasafil'konotec}+\allowbreak \hyperlink{won}{won})
Congolese; the people of the Republic of the Congo

\textbf{\hypertarget{'pahasafil'konotecak}{'pahasafil'konotecak}} \textit{n.} (\hyperlink{'pahasafil'konotec}{'pahasafil'konotec}+\allowbreak \hyperlink{ak}{ak})
Congolese; from Republic of the Congo

\textbf{\hypertarget{paho}{paho}} \textit{v.} (Spa. ⟨bajo⟩ [ˈbaxo])
be low; be under; be deep; \hyperlink{paholon}{ʟᴏᴧ} has a lower altitude than \hyperlink{paholum}{ʟᴜᴍ}

\textbf{\hypertarget{'pahoehoe}{'pahoehoe}} \textit{n.} (Haw. ⟨pāhoehoe⟩ [paːˈhoweˈhowe])
pahoehoe

\textbf{\hypertarget{paholekcohpoltilum}{paholekcohpoltilum}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{lekcohpoltilum}{lekcohpoltilum})
sock; stocking

\textbf{\hypertarget{paholon}{paholon}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{lon}{lon})
bottom; depths; ground; earth; hell; underlayer; low; under; deep

\textbf{\hypertarget{paholum}{paholum}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{lum}{lum})
standard altitude; usually sea level

\textbf{\hypertarget{paholyan}{paholyan}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{lyan}{lyan})
lowness; deelevation; altitude; layer

\textbf{\hypertarget{pahonyec}{pahonyec}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{nyec}{nyec})
mole

\textbf{\hypertarget{pahocwemontalon}{pahocwemontalon}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{cwemontalon}{cwemontalon})
submarine

\textbf{\hypertarget{pahoki}{pahoki}} \textit{v.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{ki}{ki})
lower; descend; depress; \hyperlink{pahokiles}{ʟєꜱ} decreases ʟᴏᴧ’s altitude relative to ʟᴜᴍ

\textbf{\hypertarget{pahokiles}{pahokiles}} \textit{n.} (\hyperlink{pahoki}{pahoki}+\allowbreak \hyperlink{les}{les})
one who lowers

\textbf{\hypertarget{pahotayl}{pahotayl}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{tayl}{tayl})
lowlands

\textbf{\hypertarget{pahotielon}{pahotielon}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{tielon}{tielon})
go under; ʟєꜱ moves ʟᴏᴧ under ʟᴜᴍ

\textbf{\hypertarget{pahopoltilum}{pahopoltilum}} \textit{n.} (\hyperlink{paho}{paho}+\allowbreak \hyperlink{poltilum}{poltilum})
underwear

\textbf{\hypertarget{'pahi}{'pahi}} \textit{n.} (Fra. ⟨Paris⟩ [paˈʁi])
Paris

\textbf{\hypertarget{'pahlayn}{'pahlayn}} \textit{n.} (Ara. ⟨{\arabics{}بحرين‎}⟩ [baħrajn])
Bahrain

\textbf{\hypertarget{'pahlaynak}{'pahlaynak}} \textit{n.} (\hyperlink{'pahlayn}{'pahlayn}+\allowbreak \hyperlink{ak}{ak})
Bahraini; from Bahrain

\textbf{\hypertarget{'pahlaynwon}{'pahlaynwon}} \textit{n.} (\hyperlink{'pahlayn}{'pahlayn}+\allowbreak \hyperlink{won}{won})
Bahraini; the Bahraini people

\textbf{\hypertarget{'pactan}{'pactan}} \textit{n.} (Prs. ⟨{\arabics{}پښتانه‎‎}⟩ [pəʂt̪aːnə])
Pashtun; Pakhtun; Afghan; Pathan; the Pashtun people

\textbf{\hypertarget{'pactanak}{'pactanak}} \textit{n.} (\hyperlink{'pactan}{'pactan}+\allowbreak \hyperlink{ak}{ak})
Pashtun; of Pashtuns

\textbf{\hypertarget{'pactantilip}{'pactantilip}} \textit{n.} (\hyperlink{'pactan}{'pactan}+\allowbreak \hyperlink{tilip}{tilip})
Pashto; the Pashto language

\textbf{\hypertarget{pas}{pas}} \textit{n.} (Eng. ⟨path⟩ [pʰæθ])
path; line; curve; one-dimensional locus

\textbf{\hypertarget{pasak}{pasak}} \textit{n.} (\hyperlink{pas}{pas}+\allowbreak \hyperlink{ak}{ak})
linear; curvilinear

\textbf{\hypertarget{'pakistan}{'pakistan}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਪਾਕਿਸਤਾਨ‎}⟩ [pɑːkɪstɑːn])
Pakistan

\textbf{\hypertarget{'pakistanak}{'pakistanak}} \textit{n.} (\hyperlink{'pakistan}{'pakistan}+\allowbreak \hyperlink{ak}{ak})
Pakistani; from Pakistan

\textbf{\hypertarget{'pakistanwon}{'pakistanwon}} \textit{n.} (\hyperlink{'pakistan}{'pakistan}+\allowbreak \hyperlink{won}{won})
Pakistani; the Pakistani people

\textbf{\hypertarget{'pakistantilip}{'pakistantilip}} \textit{n.} (\hyperlink{'pakistan}{'pakistan}+\allowbreak \hyperlink{tilip}{tilip})
Urdu; the Urdu language

\textbf{\hypertarget{pakha}{pakha}} \textit{v.} (\hyperlink{manca}{\sout{manca}})
be to the left; \hyperlink{pakhalon}{ʟᴏᴧ} has a negative \textit{x} coordinate from ʟᴜᴍ’s point of view

\textbf{\hypertarget{pakhalon}{pakhalon}} \textit{n.} (\hyperlink{pakha}{pakha}+\allowbreak \hyperlink{lon}{lon})
left side; to the left

\textbf{\hypertarget{pakhaki}{pakhaki}} \textit{v.} (\hyperlink{pakha}{pakha}+\allowbreak \hyperlink{ki}{ki})
go left; ʟєꜱ makes ʟᴏᴧ move left from ʟᴜᴍ’s point of view

\textbf{\hypertarget{paktel}{paktel}} \textit{n.} (Jav. ⟨baktèri⟩ [pɑ̤ktɛɽi])
prokaryote; bacterium; archaeon; cellular organism with no nucleus

\textbf{\hypertarget{paktelcwelon}{paktelcwelon}} \textit{n.} (\hyperlink{paktel}{paktel}+\allowbreak \hyperlink{cwelon}{cwelon})
pus

\textbf{\hypertarget{paktelcwelonnelum}{paktelcwelonnelum}} \textit{n.} (\hyperlink{paktelcwelon}{paktelcwelon}+\allowbreak \hyperlink{nelum}{nelum})
pimple; abscess

\textbf{\hypertarget{patam}{patam}} \textit{n.} (Hin. ⟨{\devanagari{}बादाम}⟩ [baːdaːm])
almond; Prunus dulcis

\textbf{\hypertarget{pato}{pato}} \textit{v.} (Fil. ⟨bato⟩ [bato])
be stone; be rock; be earthen; \hyperlink{patolon}{ʟᴏᴧ} is made out of earth

\textbf{\hypertarget{patoisa}{patoisa}} \textit{v.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{isa}{isa})
be gravel; course sand; \hyperlink{patoisalon}{ʟᴏᴧ} is made of gravel

\textbf{\hypertarget{patoisalon}{patoisalon}} \textit{n.} (\hyperlink{patoisa}{patoisa}+\allowbreak \hyperlink{lon}{lon})
gravel

\textbf{\hypertarget{patoufa}{patoufa}} \textit{v.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{ufa}{ufa})
be sand; be dust; \hyperlink{patoufalon}{ʟᴏᴧ} is made of sand

\textbf{\hypertarget{patoufaut}{patoufaut}} \textit{n.} (\hyperlink{patoufa}{patoufa}+\allowbreak \hyperlink{ut}{ut})
camel

\textbf{\hypertarget{patoufalon}{patoufalon}} \textit{n.} (\hyperlink{patoufa}{patoufa}+\allowbreak \hyperlink{lon}{lon})
pile of sand; sand; dust

\textbf{\hypertarget{patoufatayl}{patoufatayl}} \textit{n.} (\hyperlink{patoufa}{patoufa}+\allowbreak \hyperlink{tayl}{tayl})
desert

\textbf{\hypertarget{patolon}{patolon}} \textit{n.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{lon}{lon})
stone; rock; earthen

\textbf{\hypertarget{patolonmwonilum}{patolonmwonilum}} \textit{n.} (\hyperlink{patolon}{patolon}+\allowbreak \hyperlink{mwonilum}{mwonilum})
mine; quarry

\textbf{\hypertarget{patocwelon}{patocwelon}} \textit{n.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{cwelon}{cwelon})
lava; magma

\textbf{\hypertarget{patoki}{patoki}} \textit{v.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{ki}{ki})
turn to stone; earthify; ʟєꜱ turns ʟᴏᴧ to stone

\textbf{\hypertarget{patoteluat}{patoteluat}} \textit{n.} (\hyperlink{pato}{pato}+\allowbreak \hyperlink{teluat}{teluat})
pencil

\textbf{\hypertarget{patili}{patili}} \textit{v.} (Swa. ⟨-badili⟩ [ɓaɗili])
convert; translate; transform; represent; encode; \hyperlink{patililes}{ʟєꜱ} conveys ʟᴏᴧ in the form \hyperlink{patililum}{ʟᴜᴍ}

\textbf{\hypertarget{patililes}{patililes}} \textit{n.} (\hyperlink{patili}{patili}+\allowbreak \hyperlink{les}{les})
converter; translator

\textbf{\hypertarget{patililip}{patililip}} \textit{n.} (\hyperlink{patili}{patili}+\allowbreak \hyperlink{lip}{lip})
transformation

\textbf{\hypertarget{patililum}{patililum}} \textit{n.} (\hyperlink{patili}{patili}+\allowbreak \hyperlink{lum}{lum})
translation; symbol; representative

\textbf{\hypertarget{patilihwok}{patilihwok}} \textit{n.} (\hyperlink{patili}{patili}+\allowbreak \hyperlink{hwok}{hwok})
flag; banner

\textbf{\hypertarget{'papeytos}{'papeytos}} \textit{n.} (Bjs. ⟨Barbados⟩ [bɑːɹˈbeɪ̯dɒs])
Barbados (landmass)

\textbf{\hypertarget{'papeytosak}{'papeytosak}} \textit{n.} (\hyperlink{'papeytos}{'papeytos}+\allowbreak \hyperlink{ak}{ak})
Barbadian; from Barbados

\textbf{\hypertarget{'papeytoswon}{'papeytoswon}} \textit{n.} (\hyperlink{'papeytos}{'papeytos}+\allowbreak \hyperlink{won}{won})
Barbadian; Bajan; the Barbadian people

\textbf{\hypertarget{'papeytostec}{'papeytostec}} \textit{n.} (\hyperlink{'papeytos}{'papeytos}+\allowbreak \hyperlink{tec}{tec})
Barbados (country)

\textbf{\hypertarget{'papeytostilip}{'papeytostilip}} \textit{n.} (\hyperlink{'papeytos}{'papeytos}+\allowbreak \hyperlink{tilip}{tilip})
Bajan Creole

\textbf{\hypertarget{'papilim}{'papilim}} \textit{n.} (Akk. ⟨{\cuneiform{}𒆍𒀭𒊏𒆠}⟩ [baːbili])
Babylon

\textbf{\hypertarget{'papyuta}{'papyuta}} \textit{n.} (Aig. ⟨Barbuda⟩ [bɑːˈbjuːdə])
Barbuda

\textbf{\hypertarget{'papyutaak}{'papyutaak}} \textit{n.} (\hyperlink{'papyuta}{'papyuta}+\allowbreak \hyperlink{ak}{ak})
Barbudan

\textbf{\hypertarget{poyn}{poyn}} \textit{n.} (Eng. ⟨point⟩ [pʰɔɪ̯nt])
point; particular time or place

\textbf{\hypertarget{poynak}{poynak}} \textit{n.} (\hyperlink{poyn}{poyn}+\allowbreak \hyperlink{ak}{ak})
particular; local

\textbf{\hypertarget{'pol}{'pol}} \textit{n.} (Pol. ⟨pol-⟩ [pɔl])
Pole; the Polish people

\textbf{\hypertarget{pola}{pola}} \textit{v.} (Ben. ⟨{\bengali{}বলা}⟩ [bɔl̪a])
speak; voice; say out loud; \hyperlink{polales}{ʟєꜱ} says \hyperlink{polalum}{ʟᴜᴍ} to ʟᴏᴧ out loud

\textbf{\hypertarget{polaec}{polaec}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{ec}{ec})
larynx; vocal chords; voice box

\textbf{\hypertarget{polaak}{polaak}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{ak}{ak})
phonetic

\textbf{\hypertarget{polai}{polai}} \textit{v.} (Ben. ⟨{\bengali{}বড়াই}⟩ [bɔɽai])
bounce; spring; \hyperlink{polailes}{ʟєꜱ} bounces \hyperlink{polailon}{ʟᴏᴧ} off of ʟᴜᴍ

\textbf{\hypertarget{polailes}{polailes}} \textit{n.} (\hyperlink{polai}{polai}+\allowbreak \hyperlink{les}{les})
bouncer

\textbf{\hypertarget{polailon}{polailon}} \textit{n.} (\hyperlink{polai}{polai}+\allowbreak \hyperlink{lon}{lon})
spring

\textbf{\hypertarget{polaikio}{polaikio}} \textit{v.} (\hyperlink{polai}{polai}+\allowbreak \hyperlink{kio}{kio})
be rubber; \hyperlink{polaikiolon}{ʟᴏᴧ} is made of rubber

\textbf{\hypertarget{polaikiolon}{polaikiolon}} \textit{n.} (\hyperlink{polaikio}{polaikio}+\allowbreak \hyperlink{lon}{lon})
rubber

\textbf{\hypertarget{polaipowi}{polaipowi}} \textit{v.} (\hyperlink{polai}{polai}+\allowbreak \hyperlink{powi}{powi})
be elastic; be bouncy; be springy; \hyperlink{polaipowilon}{ʟᴏᴧ} bounces well

\textbf{\hypertarget{polaipowilon}{polaipowilon}} \textit{n.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{lon}{lon})
elastic; bouncy; springy

\textbf{\hypertarget{polaipowilyan}{polaipowilyan}} \textit{n.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{lyan}{lyan})
elasticicity

\textbf{\hypertarget{polaipowinu}{polaipowinu}} \textit{v.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{nu}{nu})
deelastify; make inelastic; ʟєꜱ makes ʟᴏᴧ less elastic

\textbf{\hypertarget{polaipowinyo}{polaipowinyo}} \textit{v.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{nyo}{nyo})
be inelastic; be unbouncy; be flat; be hard; \hyperlink{polaipowinyolon}{ʟᴏᴧ} does not bounce well

\textbf{\hypertarget{polaipowinyolon}{polaipowinyolon}} \textit{n.} (\hyperlink{polaipowinyo}{polaipowinyo}+\allowbreak \hyperlink{lon}{lon})
inelastic; unbouncy; flat; hard

\textbf{\hypertarget{polaipowikac}{polaipowikac}} \textit{n.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{kac}{kac})
rubber tree; latex

\textbf{\hypertarget{polaipowiki}{polaipowiki}} \textit{v.} (\hyperlink{polaipowi}{polaipowi}+\allowbreak \hyperlink{ki}{ki})
elastify; bouncify; make elastic; ʟєꜱ makes ʟᴏᴧ elastic

\textbf{\hypertarget{polales}{polales}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{les}{les})
speaker

\textbf{\hypertarget{'polalis}{'polalis}} \textit{n.} (Lat. ⟨Polaris⟩ [polaris])
Polaris; the North Star

\textbf{\hypertarget{'polalisawstalis}{'polalisawstalis}} \textit{n.} (Lat. ⟨Polaris Australis⟩ [pɔlarɪs awstralɪs])
Sigma Octantis; Polaris Australis; the South Star

\textbf{\hypertarget{polalip}{polalip}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{lip}{lip})
accent; manner of speech

\textbf{\hypertarget{polaluat}{polaluat}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{luat}{luat})
voice

\textbf{\hypertarget{polalum}{polalum}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{lum}{lum})
quote; words; phrase; utterance; speech

\textbf{\hypertarget{polamocaki}{polamocaki}} \textit{v.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{mocaki}{mocaki})
storytell; \hyperlink{polamocakiles}{ʟєꜱ} tells \hyperlink{polamocakilum}{ʟᴜᴍ} to ʟᴏᴧ

\textbf{\hypertarget{polamocakiles}{polamocakiles}} \textit{n.} (\hyperlink{polamocaki}{polamocaki}+\allowbreak \hyperlink{les}{les})
storyteller; host

\textbf{\hypertarget{polamocakilum}{polamocakilum}} \textit{n.} (\hyperlink{polamocaki}{polamocaki}+\allowbreak \hyperlink{lum}{lum})
story; tale; audiobook; radio

\textbf{\hypertarget{polacipcip}{polacipcip}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{cipcip}{cipcip})
parrot; Psittaciformes

\textbf{\hypertarget{'polak}{'polak}} \textit{n.} (\hyperlink{'pol}{'pol}+\allowbreak \hyperlink{ak}{ak})
Polish; from Poland

\textbf{\hypertarget{polapaltolon}{polapaltolon}} \textit{n.} (\hyperlink{pola}{pola}+\allowbreak \hyperlink{paltolon}{paltolon})
sound; phoneme

\textbf{\hypertarget{'polium}{'polium}} \textit{n.} (Lat. ⟨borium⟩ [borɪʊ̃])
boron

\textbf{\hypertarget{'polinesi}{'polinesi}} \textit{n.} (Fra. ⟨Polynésie⟩ [ˈpolinezi])
Polynesia

\textbf{\hypertarget{'polinesiak}{'polinesiak}} \textit{n.} (\hyperlink{'polinesi}{'polinesi}+\allowbreak \hyperlink{ak}{ak})
Polynesian; from Polynesia

\textbf{\hypertarget{'polinesiwon}{'polinesiwon}} \textit{n.} (\hyperlink{'polinesi}{'polinesi}+\allowbreak \hyperlink{won}{won})
Polynesian; the Polynesian people

\textbf{\hypertarget{'polipya}{'polipya}} \textit{n.} (Spa. ⟨Bolivia⟩ [boˈliβja])
Bolivia

\textbf{\hypertarget{'polipyaak}{'polipyaak}} \textit{n.} (\hyperlink{'polipya}{'polipya}+\allowbreak \hyperlink{ak}{ak})
Bolivian; from Bolivia

\textbf{\hypertarget{'polipyawon}{'polipyawon}} \textit{n.} (\hyperlink{'polipya}{'polipya}+\allowbreak \hyperlink{won}{won})
Bolivian; the Bolivian people

\textbf{\hypertarget{'polum}{'polum}} \textit{n.} (Lat. ⟨Porrum⟩ [pɔrːʊ̃])
leek

\textbf{\hypertarget{'poltec}{'poltec}} \textit{n.} (\hyperlink{'pol}{'pol}+\allowbreak \hyperlink{tec}{tec})
Poland

\textbf{\hypertarget{polti}{polti}} \textit{v.} (Epo. ⟨porti⟩ [ˈporti])
wear; be clothed; \hyperlink{poltilon}{ʟᴏᴧ} wears \hyperlink{poltilum}{ʟᴜᴍ}

\textbf{\hypertarget{poltilon}{poltilon}} \textit{n.} (\hyperlink{polti}{polti}+\allowbreak \hyperlink{lon}{lon})
clothed

\textbf{\hypertarget{'poltilip}{'poltilip}} \textit{n.} (\hyperlink{'pol}{'pol}+\allowbreak \hyperlink{tilip}{tilip})
Polish; the Polish language

\textbf{\hypertarget{poltilum}{poltilum}} \textit{n.} (\hyperlink{polti}{polti}+\allowbreak \hyperlink{lum}{lum})
clothing; clothes; article

\textbf{\hypertarget{poltinu}{poltinu}} \textit{v.} (\hyperlink{polti}{polti}+\allowbreak \hyperlink{nu}{nu})
take off; undress; disrobje; \hyperlink{poltinules}{ʟєꜱ} takes ʟᴜᴍ off of \hyperlink{poltinulon}{ʟᴏᴧ}

\textbf{\hypertarget{poltinules}{poltinules}} \textit{n.} (\hyperlink{poltinu}{poltinu}+\allowbreak \hyperlink{les}{les})
undresser

\textbf{\hypertarget{poltinulon}{poltinulon}} \textit{n.} (\hyperlink{poltinu}{poltinu}+\allowbreak \hyperlink{lon}{lon})
undressee

\textbf{\hypertarget{poltinyokiah}{poltinyokiah}} \textit{n.} (\hyperlink{polti}{polti}+\allowbreak \hyperlink{nyo}{nyo}+\allowbreak \hyperlink{kiah}{kiah})
vulture

\textbf{\hypertarget{poltiki}{poltiki}} \textit{v.} (\hyperlink{polti}{polti}+\allowbreak \hyperlink{ki}{ki})
put on; dress; robe; \hyperlink{poltikiles}{ʟєꜱ} puts ʟᴜᴍ on \hyperlink{poltikilon}{ʟᴏᴧ}

\textbf{\hypertarget{poltikiles}{poltikiles}} \textit{n.} (\hyperlink{poltiki}{poltiki}+\allowbreak \hyperlink{les}{les})
dresser

\textbf{\hypertarget{poltikilon}{poltikilon}} \textit{n.} (\hyperlink{poltiki}{poltiki}+\allowbreak \hyperlink{lon}{lon})
dressee

\textbf{\hypertarget{powi}{powi}} \textit{v.} (Epo. ⟨povi⟩ [ˈpovi])
be possible; can; might; may; \textit{possibility}; \hyperlink{powilon}{ʟᴏᴧ} can happen

\textbf{\hypertarget{powilon}{powilon}} \textit{n.} (\hyperlink{powi}{powi}+\allowbreak \hyperlink{lon}{lon})
possibility; possible

\textbf{\hypertarget{powinu}{powinu}} \textit{v.} (\hyperlink{powi}{powi}+\allowbreak \hyperlink{nu}{nu})
prevent; ʟєꜱ makes ʟᴏᴧ stop being possible

\textbf{\hypertarget{powiki}{powiki}} \textit{v.} (\hyperlink{powi}{powi}+\allowbreak \hyperlink{ki}{ki})
enable; ʟєꜱ makes ʟᴏᴧ become possible

\textbf{\hypertarget{ponto}{ponto}} \textit{v.} (Ben. ⟨{\bengali{}বন্ধ}⟩ [bɔn̪d̪̤ɔ])
be closed; be hollow; be looped; be complete; \hyperlink{pontolon}{ʟᴏᴧ} is closed on all sides

\textbf{\hypertarget{pontolon}{pontolon}} \textit{n.} (\hyperlink{ponto}{ponto}+\allowbreak \hyperlink{lon}{lon})
shell; loop; circuit; circle; ring; closed path; closed surface; closed; hollow; looped; complete

\textbf{\hypertarget{pontosiklalon}{pontosiklalon}} \textit{n.} (\hyperlink{ponto}{ponto}+\allowbreak \hyperlink{siklalon}{siklalon})
ring; hoop; band; circlet

\textbf{\hypertarget{pontoki}{pontoki}} \textit{v.} (\hyperlink{ponto}{ponto}+\allowbreak \hyperlink{ki}{ki})
close; shut; loop; \hyperlink{pontokiles}{ʟєꜱ} makes ʟᴏᴧ closed

\textbf{\hypertarget{pontokiles}{pontokiles}} \textit{n.} (\hyperlink{pontoki}{pontoki}+\allowbreak \hyperlink{les}{les})
closer

\textbf{\hypertarget{'pohotestantismus}{'pohotestantismus}} \textit{n.} (Deu. ⟨Protestantismus⟩ [ˌpʀ̥otɛstanˈtɪsmʊs])
Protestantism

\textbf{\hypertarget{'pohotestantismuswon}{'pohotestantismuswon}} \textit{n.} (\hyperlink{'pohotestantismus}{'pohotestantismus}+\allowbreak \hyperlink{won}{won})
Protestant; follower of Protestantism

\textbf{\hypertarget{'pohotestantismusak}{'pohotestantismusak}} \textit{n.} (\hyperlink{'pohotestantismus}{'pohotestantismus}+\allowbreak \hyperlink{ak}{ak})
Protestant; of Protestantism

\textbf{\hypertarget{poca}{poca}} \textit{v.} (Ben. ⟨{\bengali{}পচা}⟩ [pɔt͡ɕa])
be rotten; \hyperlink{pocalon}{ʟᴏᴧ} is rotten

\textbf{\hypertarget{pocalon}{pocalon}} \textit{n.} (\hyperlink{poca}{poca}+\allowbreak \hyperlink{lon}{lon})
rotten

\textbf{\hypertarget{pocaki}{pocaki}} \textit{v.} (\hyperlink{poca}{poca}+\allowbreak \hyperlink{ki}{ki})
rot; ʟєꜱ rots ʟᴏᴧ

\textbf{\hypertarget{'posna}{'posna}} \textit{n.} (Bos. ⟨Bosna⟩ [bɔ̂sna])
Bosna; the River Bosna

\textbf{\hypertarget{'posnaak}{'posnaak}} \textit{n.} (\hyperlink{'posna}{'posna}+\allowbreak \hyperlink{ak}{ak})
Bosnian

\textbf{\hypertarget{'posnawon}{'posnawon}} \textit{n.} (\hyperlink{'posna}{'posna}+\allowbreak \hyperlink{won}{won})
Bosnian; the Bosnian people

\textbf{\hypertarget{'posnakwelyot}{'posnakwelyot}} \textit{n.} (\hyperlink{'posna}{'posna}+\allowbreak \hyperlink{kwelyot}{kwelyot})
Bosnia

\textbf{\hypertarget{'posnatec}{'posnatec}} \textit{n.} (\hyperlink{'posna}{'posna}+\allowbreak \hyperlink{tec}{tec})
Bosnia and Herzegovina; Bosnia–Herzegovina; Bosnia

\textbf{\hypertarget{'posnatilip}{'posnatilip}} \textit{n.} (\hyperlink{'posna}{'posna}+\allowbreak \hyperlink{tilip}{tilip})
Bosnian; the Bosnian language

\textbf{\hypertarget{pok}{pok}} \textit{num.} (\hyperlink{men}{\sout{men}})
positive; plus; +\allowbreak 

\textbf{\hypertarget{'poksimacentawli}{'poksimacentawli}} \textit{n.} (Lat. ⟨Proxima Centauri⟩ [prɔksɪma t͡ʃɛntawrɪ])
Proxima Centauri

\textbf{\hypertarget{'potasium}{'potasium}} \textit{n.} (Lat. ⟨potassium⟩ [pɔtassɪʊ̃])
potassium

\textbf{\hypertarget{'pi}{'pi}} \textit{n.} (Grc. ⟨π⟩ [pi])
pi; 3.142…

\textbf{\hypertarget{piac}{piac}} \textit{n.} (Pan. ⟨{\gurmukhi{}ਪਿਆਜ}⟩ [pɪɑd͡ʒ])
onion; garlic; leek; scallion; Allium

\textbf{\hypertarget{piasa}{piasa}} \textit{v.} (Msa. ⟨biasa⟩ [biasa])
be familiar with; know; be accustomed; be used to; \hyperlink{piasalum}{ʟᴜᴍ} is familiar to \hyperlink{piasalon}{ʟᴏᴧ}

\textbf{\hypertarget{piasalon}{piasalon}} \textit{n.} (\hyperlink{piasa}{piasa}+\allowbreak \hyperlink{lon}{lon})
familiar with; accustomed; used to

\textbf{\hypertarget{piasalum}{piasalum}} \textit{n.} (\hyperlink{piasa}{piasa}+\allowbreak \hyperlink{lum}{lum})
familiar to; acquaintance

\textbf{\hypertarget{piasaki}{piasaki}} \textit{v.} (\hyperlink{piasa}{piasa}+\allowbreak \hyperlink{ki}{ki})
familiarise; get to know; get accustomed; practise; introduce; \hyperlink{piasakiles}{ʟєꜱ} makes ʟᴏᴧ become familiar with ʟᴜᴍ

\textbf{\hypertarget{piasakiles}{piasakiles}} \textit{n.} (\hyperlink{piasaki}{piasaki}+\allowbreak \hyperlink{les}{les})
familiariser

\textbf{\hypertarget{pil}{pil}} \textit{n.} (Nya. ⟨phiri⟩ [pʰiɽi])
mountain; large elevated region of a planet’s crust

\textbf{\hypertarget{pila}{pila}} \textit{v.} (Hin. ⟨{\devanagari{}पीला}⟩ [piːlaː])
be yellow; \hyperlink{pilalon}{ʟᴏᴧ} reflects medium wavelength light

\textbf{\hypertarget{pilalon}{pilalon}} \textit{n.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{lon}{lon})
yellow

\textbf{\hypertarget{pilalyan}{pilalyan}} \textit{n.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{lyan}{lyan})
yellowness

\textbf{\hypertarget{pilaceluk}{pilaceluk}} \textit{n.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{celuk}{celuk})
lemon

\textbf{\hypertarget{pilacwelon}{pilacwelon}} \textit{n.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{cwelon}{cwelon})
urine; pee

\textbf{\hypertarget{pilacwelonec}{pilacwelonec}} \textit{n.} (\hyperlink{pilacwelon}{pilacwelon}+\allowbreak \hyperlink{ec}{ec})
bladder

\textbf{\hypertarget{pilacwelonkoki}{pilacwelonkoki}} \textit{v.} (\hyperlink{pilacwelon}{pilacwelon}+\allowbreak \hyperlink{koki}{koki})
urinate; pee; ʟєꜱ urinates out ʟᴏᴧ

\textbf{\hypertarget{pilak}{pilak}} \textit{n.} (\hyperlink{pil}{pil}+\allowbreak \hyperlink{ak}{ak})
mountainous; montanical

\textbf{\hypertarget{pilaki}{pilaki}} \textit{v.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{ki}{ki})
yellow; colour yellow; ʟєꜱ colours ʟᴏᴧ yellow

\textbf{\hypertarget{pilatatu}{pilatatu}} \textit{v.} (\hyperlink{pila}{pila}+\allowbreak \hyperlink{tatu}{tatu})
be gold; \hyperlink{pilatatulon}{ʟᴏᴧ} is made of gold

\textbf{\hypertarget{pilatatulon}{pilatatulon}} \textit{n.} (\hyperlink{pilatatu}{pilatatu}+\allowbreak \hyperlink{lon}{lon})
gold

\textbf{\hypertarget{'pilinsipi}{'pilinsipi}} \textit{n.} (Por. ⟨Príncipe⟩ [ˈpɾĩsɨpɨ])
Príncipe

\textbf{\hypertarget{'pilinsipiak}{'pilinsipiak}} \textit{n.} (\hyperlink{'pilinsipi}{'pilinsipi}+\allowbreak \hyperlink{ak}{ak})
Príncipean; from Príncipe

\textbf{\hypertarget{'pilipinas}{'pilipinas}} \textit{n.} (Fil. ⟨Pilipinas⟩ [pɪlɪpinas])
Philippines (archipelago)

\textbf{\hypertarget{'pilipinasak}{'pilipinasak}} \textit{n.} (\hyperlink{'pilipinas}{'pilipinas}+\allowbreak \hyperlink{ak}{ak})
Filipino; Philippine; from the Philippines

\textbf{\hypertarget{'pilipinaswon}{'pilipinaswon}} \textit{n.} (\hyperlink{'pilipinas}{'pilipinas}+\allowbreak \hyperlink{won}{won})
Filipino; Filipina; Pinoy; Pinay; the Filipino people

\textbf{\hypertarget{'pilipinastec}{'pilipinastec}} \textit{n.} (\hyperlink{'pilipinas}{'pilipinas}+\allowbreak \hyperlink{tec}{tec})
Philippines; the Republic of the Philippines

\textbf{\hypertarget{'pilipinastilip}{'pilipinastilip}} \textit{n.} (\hyperlink{'pilipinas}{'pilipinas}+\allowbreak \hyperlink{tilip}{tilip})
Filipino

\textbf{\hypertarget{pilu}{pilu}} \textit{v.} (Msa. ⟨biru⟩ [biru])
be blue; be cool; \hyperlink{pilulon}{ʟᴏᴧ} reflects short wavelength light

\textbf{\hypertarget{pilulon}{pilulon}} \textit{n.} (\hyperlink{pilu}{pilu}+\allowbreak \hyperlink{lon}{lon})
blue; cool

\textbf{\hypertarget{pilulyan}{pilulyan}} \textit{n.} (\hyperlink{pilu}{pilu}+\allowbreak \hyperlink{lyan}{lyan})
blueness

\textbf{\hypertarget{pilucakalum}{pilucakalum}} \textit{n.} (\hyperlink{pilu}{pilu}+\allowbreak \hyperlink{cakalum}{cakalum})
cobalt (substance)

\textbf{\hypertarget{pilus}{pilus}} \textit{n.} (Spa. ⟨virus⟩ [ˈbiɾus])
virus

\textbf{\hypertarget{piluki}{piluki}} \textit{v.} (\hyperlink{pilu}{pilu}+\allowbreak \hyperlink{ki}{ki})
colour blue; ʟєꜱ colours ʟᴏᴧ blue

\textbf{\hypertarget{pilut}{pilut}} \textit{n.} (\hyperlink{pil}{pil}+\allowbreak \hyperlink{ut}{ut})
llama

\textbf{\hypertarget{pilutihu}{pilutihu}} \textit{v.} (\hyperlink{pilu}{pilu}+\allowbreak \hyperlink{tihu}{tihu})
be cyan; be teal; be blue-green; \hyperlink{pilutihulon}{ʟᴏᴧ} looks cyan

\textbf{\hypertarget{pilutihulon}{pilutihulon}} \textit{n.} (\hyperlink{pilutihu}{pilutihu}+\allowbreak \hyperlink{lon}{lon})
cyan; teal; blue-green

\textbf{\hypertarget{pilutihuki}{pilutihuki}} \textit{v.} (\hyperlink{pilutihu}{pilutihu}+\allowbreak \hyperlink{ki}{ki})
colour cyan; colour teal; colour blue-green; ʟєꜱ colours ʟᴏᴧ cyan

\textbf{\hypertarget{pilmuf}{pilmuf}} \textit{n.} (\hyperlink{pil}{pil}+\allowbreak \hyperlink{muf}{muf})
goat

\textbf{\hypertarget{pih}{pih}} \textit{num.} (\hyperlink{muc}{\sout{muc}})
little; few; slight

\textbf{\hypertarget{pihonalon}{pihonalon}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{onalon}{onalon})
hut; cottage

\textbf{\hypertarget{pihlono}{pihlono}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{lono}{lono})
be monochromatic; \hyperlink{pihlonolon}{ʟᴏᴧ} has few colours

\textbf{\hypertarget{pihlonolon}{pihlonolon}} \textit{n.} (\hyperlink{pihlono}{pihlono}+\allowbreak \hyperlink{lon}{lon})
monochromatic

\textbf{\hypertarget{pihcai}{pihcai}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{cai}{cai})
have affinity; be fond; not mind; \hyperlink{pihcailon}{ʟᴏᴧ} has an affinity for ʟᴜᴍ

\textbf{\hypertarget{pihcailon}{pihcailon}} \textit{n.} (\hyperlink{pihcai}{pihcai}+\allowbreak \hyperlink{lon}{lon})
fond

\textbf{\hypertarget{pihcih}{pihcih}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{cih}{cih})
village; town

\textbf{\hypertarget{pihcwelon}{pihcwelon}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{cwelon}{cwelon})
puddle

\textbf{\hypertarget{pihcwepucolon}{pihcwepucolon}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{cwepucolon}{cwepucolon})
brook; stream; rivulet

\textbf{\hypertarget{pihtec}{pihtec}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{tec}{tec})
tribe

\textbf{\hypertarget{pihtayl}{pihtayl}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{tayl}{tayl})
island; landmass that is smaller than a continent and bounded by ocean

\textbf{\hypertarget{pihtafu}{pihtafu}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{tafu}{tafu})
itch; ʟᴏᴧ’s \hyperlink{pihtafulum}{ʟᴜᴍ} itches

\textbf{\hypertarget{pihtafulum}{pihtafulum}} \textit{n.} (\hyperlink{pihtafu}{pihtafu}+\allowbreak \hyperlink{lum}{lum})
itch

\textbf{\hypertarget{pihtue}{pihtue}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{tue}{tue})
be poor; be destitute; \hyperlink{pihtuelon}{ʟᴏᴧ} is financially poor

\textbf{\hypertarget{pihtuelon}{pihtuelon}} \textit{n.} (\hyperlink{pihtue}{pihtue}+\allowbreak \hyperlink{lon}{lon})
poor; destitute

\textbf{\hypertarget{pihtunci}{pihtunci}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{tunci}{tunci})
rule as an oligarchy; \hyperlink{pihtuncilum}{ʟᴜᴍ} rules ʟᴏᴧ

\textbf{\hypertarget{pihtuncilum}{pihtuncilum}} \textit{n.} (\hyperlink{pihtunci}{pihtunci}+\allowbreak \hyperlink{lum}{lum})
oligarchy

\textbf{\hypertarget{pihtuncilyot}{pihtuncilyot}} \textit{n.} (\hyperlink{pihtunci}{pihtunci}+\allowbreak \hyperlink{lyot}{lyot})
oligarchic kingdom

\textbf{\hypertarget{pihpatolon}{pihpatolon}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{patolon}{patolon})
pebble

\textbf{\hypertarget{pihpil}{pihpil}} \textit{n.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{pil}{pil})
hill

\textbf{\hypertarget{pihpyo}{pihpyo}} \textit{v.} (\hyperlink{pih}{pih}+\allowbreak \hyperlink{pyo}{pyo})
creep out; \hyperlink{pihpyolon}{ʟᴏᴧ} finds \hyperlink{pihpyolum}{ʟᴜᴍ} creepy

\textbf{\hypertarget{pihpyolon}{pihpyolon}} \textit{n.} (\hyperlink{pihpyo}{pihpyo}+\allowbreak \hyperlink{lon}{lon})
creeped out

\textbf{\hypertarget{pihpyolum}{pihpyolum}} \textit{n.} (\hyperlink{pihpyo}{pihpyo}+\allowbreak \hyperlink{lum}{lum})
creepy; creeper

\textbf{\hypertarget{pic}{pic}} \textit{n.} (Hin. ⟨{\devanagari{}बीज}⟩ [biːd͡ʒ])
seed; small courier of genetic information

\textbf{\hypertarget{picec}{picec}} \textit{n.} (\hyperlink{pic}{pic}+\allowbreak \hyperlink{ec}{ec})
testicle

\textbf{\hypertarget{picak}{picak}} \textit{n.} (\hyperlink{pic}{pic}+\allowbreak \hyperlink{ak}{ak})
seminal

\textbf{\hypertarget{picin}{picin}} \textit{n.} (Eng. ⟨pigeon⟩ [ˈpʰɪd͡ʒɪn])
pigeon; dove; sandgrouse; mesite; Columbimorphae

\textbf{\hypertarget{pis}{pis}} \textit{n.} (Epo. ⟨pizo⟩ [ˈpizo])
pea; green pea; Pisum

\textbf{\hypertarget{'pisaw}{'pisaw}} \textit{n.} (Por. ⟨Bissau⟩ [biˈsaw])
Bissau

\textbf{\hypertarget{'pisaw'kine}{'pisaw'kine}} \textit{n.} (\hyperlink{'pisaw}{'pisaw}+\allowbreak \hyperlink{'kine}{'kine})
Guinea-Bissau; the Republic of Guinea-Bissau

\textbf{\hypertarget{'pisaw'kineak}{'pisaw'kineak}} \textit{n.} (\hyperlink{'pisaw'kine}{'pisaw'kine}+\allowbreak \hyperlink{ak}{ak})
Bissau-Guinean; from Guinea-Bissau

\textbf{\hypertarget{'pisaw'kinewon}{'pisaw'kinewon}} \textit{n.} (\hyperlink{'pisaw'kine}{'pisaw'kine}+\allowbreak \hyperlink{won}{won})
Bissau-Guinean; the Bissau-Guinean people

\textbf{\hypertarget{pikante}{pikante}} \textit{v.} (Spa. ⟨picante⟩ [piˈkante])
be spicy; be hot; \hyperlink{pikantelon}{ʟᴏᴧ} is spicy

\textbf{\hypertarget{pikantelon}{pikantelon}} \textit{n.} (\hyperlink{pikante}{pikante}+\allowbreak \hyperlink{lon}{lon})
spicy; hot

\textbf{\hypertarget{pikantelyan}{pikantelyan}} \textit{n.} (\hyperlink{pikante}{pikante}+\allowbreak \hyperlink{lyan}{lyan})
spiciness; spice; heat

\textbf{\hypertarget{pikantefut}{pikantefut}} \textit{n.} (\hyperlink{pikante}{pikante}+\allowbreak \hyperlink{fut}{fut})
pepper

\textbf{\hypertarget{pikanteki}{pikanteki}} \textit{v.} (\hyperlink{pikante}{pikante}+\allowbreak \hyperlink{ki}{ki})
spice; ʟєꜱ makes ʟᴏᴧ become spicy

\textbf{\hypertarget{pit}{pit}} \textit{num.} (Jav. ⟨pitu⟩ [pitu])
7; seven

\textbf{\hypertarget{pitak}{pitak}} \textit{n.} (\hyperlink{pit}{pit}+\allowbreak \hyperlink{ak}{ak})
seventh

\textbf{\hypertarget{pitnul}{pitnul}} \textit{num.} (\hyperlink{pit}{pit}+\allowbreak \hyperlink{nul}{nul})
70; seventy

\textbf{\hypertarget{pitnulnul}{pitnulnul}} \textit{num.} (\hyperlink{pit}{pit}+\allowbreak \hyperlink{nul}{nul}+\allowbreak \hyperlink{nul}{nul})
700; seven hundred

\textbf{\hypertarget{'pitsa}{'pitsa}} \textit{n.} (Ita. ⟨pizza⟩ [ˈpit͡sːa])
pizza

\textbf{\hypertarget{pitsunkwelwel}{pitsunkwelwel}} \textit{n.} (\hyperlink{pit}{pit}+\allowbreak \hyperlink{sunkwelwel}{sunkwelwel})
Sunday

\textbf{\hypertarget{'pitkoyn}{'pitkoyn}} \textit{n.} (Eng. ⟨bitcoin⟩ [ˈbɪtkɔɪ̯n])
bitcoin; ₿

\textbf{\hypertarget{pitkwelwel}{pitkwelwel}} \textit{n.} (\hyperlink{pit}{pit}+\allowbreak \hyperlink{kwelwel}{kwelwel})
week

\textbf{\hypertarget{pul}{pul}} \textit{n.} (Hin. ⟨{\devanagari{}फूल}⟩ [pʰuːl])
flower; pollen-bearing structure of a flowering plant

\textbf{\hypertarget{pula}{pula}} \textit{v.} (Epo. ⟨pura⟩ [ˈpura])
be clean; be sanitary; \hyperlink{pulalon}{ʟᴏᴧ} is clean

\textbf{\hypertarget{pulalon}{pulalon}} \textit{n.} (\hyperlink{pula}{pula}+\allowbreak \hyperlink{lon}{lon})
clean; sanitary

\textbf{\hypertarget{pulanelon}{pulanelon}} \textit{n.} (\hyperlink{pula}{pula}+\allowbreak \hyperlink{nelon}{nelon})
bathroom; restroom

\textbf{\hypertarget{pulasapu}{pulasapu}} \textit{v.} (\hyperlink{pula}{pula}+\allowbreak \hyperlink{sapu}{sapu})
scrub; brush; ʟєꜱ scrubs ʟᴏᴧ

\textbf{\hypertarget{pulasapuluat}{pulasapuluat}} \textit{n.} (\hyperlink{pulasapu}{pulasapu}+\allowbreak \hyperlink{luat}{luat})
scrubber; brush

\textbf{\hypertarget{pulak}{pulak}} \textit{n.} (\hyperlink{pul}{pul}+\allowbreak \hyperlink{ak}{ak})
floral

\textbf{\hypertarget{pulaki}{pulaki}} \textit{v.} (\hyperlink{pula}{pula}+\allowbreak \hyperlink{ki}{ki})
clean; sanitise; \hyperlink{pulakiles}{ʟєꜱ} cleans ʟᴏᴧ

\textbf{\hypertarget{pulakiles}{pulakiles}} \textit{n.} (\hyperlink{pulaki}{pulaki}+\allowbreak \hyperlink{les}{les})
cleaner

\textbf{\hypertarget{pulakiluat}{pulakiluat}} \textit{n.} (\hyperlink{pulaki}{pulaki}+\allowbreak \hyperlink{luat}{luat})
cleaning utensil

\textbf{\hypertarget{'pulomium}{'pulomium}} \textit{n.} (Lat. ⟨bromium⟩ [bromɪʊ̃])
bromine

\textbf{\hypertarget{puli}{puli}} \textit{v.} (Pan. ⟨{\gurmukhi{}ਪੂਰੀ}⟩ [puɾi])
be full; \hyperlink{pulilon}{ʟᴏᴧ} is full of \hyperlink{pulilum}{ʟᴜᴍ}

\textbf{\hypertarget{pulilon}{pulilon}} \textit{n.} (\hyperlink{puli}{puli}+\allowbreak \hyperlink{lon}{lon})
full

\textbf{\hypertarget{pulilum}{pulilum}} \textit{n.} (\hyperlink{puli}{puli}+\allowbreak \hyperlink{lum}{lum})
filling

\textbf{\hypertarget{puliki}{puliki}} \textit{v.} (\hyperlink{puli}{puli}+\allowbreak \hyperlink{ki}{ki})
fill; ʟєꜱ fills ʟᴏᴧ with ʟᴜᴍ

\textbf{\hypertarget{'pulusel}{'pulusel}} \textit{n.} (Nld. ⟨Brussel⟩ [ˈbrʏsəl])
Brussels

\textbf{\hypertarget{pulciuh}{pulciuh}} \textit{n.} (\hyperlink{pul}{pul}+\allowbreak \hyperlink{ciuh}{ciuh})
orchid

\textbf{\hypertarget{pultun}{pultun}} \textit{n.} (\hyperlink{pul}{pul}+\allowbreak \hyperlink{tun}{tun})
sea anemone; sea fan; seawhip

\textbf{\hypertarget{'pultukal}{'pultukal}} \textit{n.} (Por. ⟨Portugal⟩ [puɾtuˈɣal])
Portugal

\textbf{\hypertarget{'pultukalak}{'pultukalak}} \textit{n.} (\hyperlink{'pultukal}{'pultukal}+\allowbreak \hyperlink{ak}{ak})
Portuguese; in Portuguese

\textbf{\hypertarget{'pultukalwon}{'pultukalwon}} \textit{n.} (\hyperlink{'pultukal}{'pultukal}+\allowbreak \hyperlink{won}{won})
Portuguese; the Portuguese people

\textbf{\hypertarget{'pultukaltilip}{'pultukaltilip}} \textit{n.} (\hyperlink{'pultukal}{'pultukal}+\allowbreak \hyperlink{tilip}{tilip})
Portuguese; the Portuguese language

\textbf{\hypertarget{pulpiac}{pulpiac}} \textit{n.} (\hyperlink{pul}{pul}+\allowbreak \hyperlink{piac}{piac})
chives; Allium schoenoprasum

\textbf{\hypertarget{pum}{pum}} \textit{n.} (Hin. ⟨{\devanagari{}भूमि}⟩ [b̤uːmi])
ground; planet; gravitationally-bound solid mass

\textbf{\hypertarget{puma}{puma}} \textit{v.} (ono. [bum])
boom; crash; ʟєꜱ makes \hyperlink{pumalon}{ʟᴏᴧ}

\textbf{\hypertarget{pumalon}{pumalon}} \textit{n.} (\hyperlink{puma}{puma}+\allowbreak \hyperlink{lon}{lon})
boom; crash; sudden, low-pitched sound or action

\textbf{\hypertarget{pumak}{pumak}} \textit{n.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{ak}{ak})
terrestrial; planetary

\textbf{\hypertarget{pumap}{pumap}} \textit{n.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{ap}{ap})
landfowl; chicken; turkey; pheasant

\textbf{\hypertarget{pummontalon}{pummontalon}} \textit{n.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{montalon}{montalon})
car; truck

\textbf{\hypertarget{pumhila}{pumhila}} \textit{v.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{hila}{hila})
earthquake; ʟᴏᴧ is struck by an earthquake from \hyperlink{pumhilales}{ʟєꜱ}

\textbf{\hypertarget{pumhilales}{pumhilales}} \textit{n.} (\hyperlink{pumhila}{pumhila}+\allowbreak \hyperlink{les}{les})
faultline

\textbf{\hypertarget{pumkwelwel}{pumkwelwel}} \textit{n.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{kwelwel}{kwelwel})
year

\textbf{\hypertarget{pumtupel}{pumtupel}} \textit{n.} (\hyperlink{pum}{pum}+\allowbreak \hyperlink{tupel}{tupel})
potato; tuber; Solanum tuberosum

\textbf{\hypertarget{'puhkinafaso}{'puhkinafaso}} \textit{n.} (Fra. ⟨Burkina⟩ [buʁkina])
Burkina Faso

\textbf{\hypertarget{'puhkinafasoak}{'puhkinafasoak}} \textit{n.} (\hyperlink{'puhkinafaso}{'puhkinafaso}+\allowbreak \hyperlink{ak}{ak})
Burkinabé; Burkinabè; from Burkina Faso

\textbf{\hypertarget{'puhkinafasowon}{'puhkinafasowon}} \textit{n.} (\hyperlink{'puhkinafaso}{'puhkinafaso}+\allowbreak \hyperlink{won}{won})
Burkinabé; the Burkinabé people

\textbf{\hypertarget{puhte}{puhte}} \textit{v.} (\hyperlink{miclo}{\sout{miclo}})
be pure; \hyperlink{puhtelon}{ʟᴏᴧ} is pure of ʟᴜᴍ

\textbf{\hypertarget{puhtelon}{puhtelon}} \textit{n.} (\hyperlink{puhte}{puhte}+\allowbreak \hyperlink{lon}{lon})
pure

\textbf{\hypertarget{puhtecwelon}{puhtecwelon}} \textit{n.} (\hyperlink{puhte}{puhte}+\allowbreak \hyperlink{cwelon}{cwelon})
freshwater

\textbf{\hypertarget{puhteki}{puhteki}} \textit{v.} (\hyperlink{puhte}{puhte}+\allowbreak \hyperlink{ki}{ki})
purify; precipitate; extract; ʟєꜱ purifies ʟᴏᴧ of \hyperlink{puhtekilum}{ʟᴜᴍ}

\textbf{\hypertarget{puhtekilum}{puhtekilum}} \textit{n.} (\hyperlink{puhteki}{puhteki}+\allowbreak \hyperlink{lum}{lum})
precipitate; extract

\textbf{\hypertarget{puco}{puco}} \textit{v.} (Cmn. ⟨{\chinese{}步骤}⟩ [pu˥˩ʈ͡ʂoʊ̯˥˩])
step; ʟєꜱ steps on \hyperlink{pucolon}{ʟᴏᴧ}

\textbf{\hypertarget{pucolon}{pucolon}} \textit{n.} (\hyperlink{puco}{puco}+\allowbreak \hyperlink{lon}{lon})
path; walkway; walk

\textbf{\hypertarget{pucolonmontalon}{pucolonmontalon}} \textit{n.} (\hyperlink{pucolon}{pucolon}+\allowbreak \hyperlink{montalon}{montalon})
train

\textbf{\hypertarget{pucolonpatolon}{pucolonpatolon}} \textit{n.} (\hyperlink{pucolon}{pucolon}+\allowbreak \hyperlink{patolon}{patolon})
asphalt

\textbf{\hypertarget{pucocalu}{pucocalu}} \textit{v.} (\hyperlink{puco}{puco}+\allowbreak \hyperlink{calu}{calu})
walk; tread; ʟᴏᴧ is walking on ʟᴜᴍ

\textbf{\hypertarget{pucopal}{pucopal}} \textit{n.} (\hyperlink{puco}{puco}+\allowbreak \hyperlink{pal}{pal})
cane; staff; walking stick

\textbf{\hypertarget{puci}{puci}} \textit{v.} (Epo. ⟨puŝi⟩ [ˈpuʃi])
push; repell; \hyperlink{puciles}{ʟєꜱ} pushes on \hyperlink{pucilon}{ʟᴏᴧ}

\textbf{\hypertarget{puciles}{puciles}} \textit{n.} (\hyperlink{puci}{puci}+\allowbreak \hyperlink{les}{les})
force

\textbf{\hypertarget{pucilon}{pucilon}} \textit{n.} (\hyperlink{puci}{puci}+\allowbreak \hyperlink{lon}{lon})
pushed

\textbf{\hypertarget{pus}{pus}} \textit{n.} (Sho. ⟨budzi⟩ [bud͡zi])
squash; gourd; pumpkin; zucchini; Cucurbita

\textbf{\hypertarget{puk}{puk}} \textit{pn.} (\hyperlink{min}{\sout{min}})
you; \textit{second person}; the listener

\textbf{\hypertarget{puket}{puket}} \textit{pn.} (\hyperlink{puk}{puk}+\allowbreak \hyperlink{et}{et})
y’all; ye; \textit{second person plural}; the listener and others

\textbf{\hypertarget{puketak}{puketak}} \textit{n.} (\hyperlink{puket}{puket}+\allowbreak \hyperlink{ak}{ak})
y’all’s; yer

\textbf{\hypertarget{pukak}{pukak}} \textit{n.} (\hyperlink{puk}{puk}+\allowbreak \hyperlink{ak}{ak})
your; yours

\textbf{\hypertarget{'puta}{'puta}} \textit{n.} (San. ⟨{\devanagari{}बुद्ध}⟩ [bud̚˨dʱɐ˦])
Buddha (title)

\textbf{\hypertarget{'putafitilip}{'putafitilip}} \textit{n.} (\hyperlink{'puta}{'puta}+\allowbreak \hyperlink{fitilip}{fitilip})
Buddhism

\textbf{\hypertarget{'putafitilipak}{'putafitilipak}} \textit{n.} (\hyperlink{'putafitilip}{'putafitilip}+\allowbreak \hyperlink{ak}{ak})
Buddhist; of Buddhism

\textbf{\hypertarget{'putafitilipwon}{'putafitilipwon}} \textit{n.} (\hyperlink{'putafitilip}{'putafitilip}+\allowbreak \hyperlink{won}{won})
Buddhist; followers of Buddha

\textbf{\hypertarget{puti}{puti}} \textit{v.} (Fil. ⟨puti⟩ [puti])
be white; be light; be fair; \hyperlink{putilon}{ʟᴏᴧ} reflects a lot of light

\textbf{\hypertarget{putilais}{putilais}} \textit{n.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{lais}{lais})
turnip

\textbf{\hypertarget{putilon}{putilon}} \textit{n.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{lon}{lon})
white; light; fair

\textbf{\hypertarget{putilonkio}{putilonkio}} \textit{v.} (\hyperlink{putilon}{putilon}+\allowbreak \hyperlink{kio}{kio})
be quartz; \hyperlink{putilonkiolon}{ʟᴏᴧ} is made of quartz

\textbf{\hypertarget{putilonkiolon}{putilonkiolon}} \textit{n.} (\hyperlink{putilonkio}{putilonkio}+\allowbreak \hyperlink{lon}{lon})
quartz

\textbf{\hypertarget{putiluci}{putiluci}} \textit{v.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{luci}{luci})
be pink; be rose; \hyperlink{putilucilon}{ʟᴏᴧ} looks pink

\textbf{\hypertarget{putilucilon}{putilucilon}} \textit{n.} (\hyperlink{putiluci}{putiluci}+\allowbreak \hyperlink{lon}{lon})
pink; rose

\textbf{\hypertarget{putiluciki}{putiluciki}} \textit{v.} (\hyperlink{putiluci}{putiluci}+\allowbreak \hyperlink{ki}{ki})
pinken; rose-tint; colour pink; ʟєꜱ colours ʟᴏᴧ pink

\textbf{\hypertarget{putilyan}{putilyan}} \textit{n.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{lyan}{lyan})
whiteness; value

\textbf{\hypertarget{putimilu}{putimilu}} \textit{v.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{milu}{milu})
be gray; be grey; be dull; be bland; be desaturated; \hyperlink{putimilulon}{ʟᴏᴧ} reflects all wavelengths of light about the same

\textbf{\hypertarget{putimilulon}{putimilulon}} \textit{n.} (\hyperlink{putimilu}{putimilu}+\allowbreak \hyperlink{lon}{lon})
gray; grey; dull; bland; desaturated

\textbf{\hypertarget{putimiluhihin}{putimiluhihin}} \textit{n.} (\hyperlink{putimilu}{putimilu}+\allowbreak \hyperlink{hihin}{hihin})
zebra

\textbf{\hypertarget{putimiluki}{putimiluki}} \textit{v.} (\hyperlink{putimilu}{putimilu}+\allowbreak \hyperlink{ki}{ki})
colour gray; colour grey; dull; desaturate; ʟєꜱ desaturates the colours of ʟᴏᴧ

\textbf{\hypertarget{putikol}{putikol}} \textit{n.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{kol}{kol})
cauliflower

\textbf{\hypertarget{putiki}{putiki}} \textit{v.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{ki}{ki})
whiten; lighten; wash out; dodge; ʟєꜱ lightens ʟᴏᴧ

\textbf{\hypertarget{putipilu}{putipilu}} \textit{v.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{pilu}{pilu})
be azure; be sky blue; \hyperlink{putipilulon}{ʟᴏᴧ} looks azure

\textbf{\hypertarget{putipilulon}{putipilulon}} \textit{n.} (\hyperlink{putipilu}{putipilu}+\allowbreak \hyperlink{lon}{lon})
azure; sky blue

\textbf{\hypertarget{putipiluki}{putipiluki}} \textit{v.} (\hyperlink{putipilu}{putipilu}+\allowbreak \hyperlink{ki}{ki})
colour azure; colour sky blue; ʟєꜱ colours ʟᴏᴧ azure

\textbf{\hypertarget{putipicin}{putipicin}} \textit{n.} (\hyperlink{puti}{puti}+\allowbreak \hyperlink{picin}{picin})
dove

\textbf{\hypertarget{puthu}{puthu}} \textit{v.} (ono. [pʰut])
fart; \hyperlink{puthules}{ʟєꜱ} farts out \hyperlink{puthulon}{ʟᴏᴧ}

\textbf{\hypertarget{puthules}{puthules}} \textit{n.} (\hyperlink{puthu}{puthu}+\allowbreak \hyperlink{les}{les})
one who farts

\textbf{\hypertarget{puthulon}{puthulon}} \textit{n.} (\hyperlink{puthu}{puthu}+\allowbreak \hyperlink{lon}{lon})
fart; flatulence

\textbf{\hypertarget{pupu}{pupu}} \textit{v.} (ono. [buːp buːp])
beep; hum; doot; ʟєꜱ makes \hyperlink{pupulon}{ʟᴏᴧ}

\textbf{\hypertarget{pupulon}{pupulon}} \textit{n.} (\hyperlink{pupu}{pupu}+\allowbreak \hyperlink{lon}{lon})
beep; hum; doot; drawn-out, concordant sound or action

\textbf{\hypertarget{'pyelalus}{'pyelalus}} \textit{n.} (Bel. ⟨Biełaruś⟩ [bʲɛlarusʲ])
Belarus

\textbf{\hypertarget{'pyelalusak}{'pyelalusak}} \textit{n.} (\hyperlink{'pyelalus}{'pyelalus}+\allowbreak \hyperlink{ak}{ak})
Belarusian; from Belarus

\textbf{\hypertarget{'pyelaluswon}{'pyelaluswon}} \textit{n.} (\hyperlink{'pyelalus}{'pyelalus}+\allowbreak \hyperlink{won}{won})
Belarusian; the Belarusian people

\textbf{\hypertarget{'pyelalustilip}{'pyelalustilip}} \textit{n.} (\hyperlink{'pyelalus}{'pyelalus}+\allowbreak \hyperlink{tilip}{tilip})
Belarusian

\textbf{\hypertarget{'pyawistok}{'pyawistok}} \textit{n.} (Pol. ⟨Białystok⟩ [bʲaˈwɨstɔk])
Białystok

\textbf{\hypertarget{pyah}{pyah}} \textit{n.} (ono. [bjãː])
elephant; Elephantidae

\textbf{\hypertarget{pyo}{pyo}} \textit{v.} (Ben. ⟨{\bengali{}ভয়}⟩ [b̤e̯ɔ])
fear; be scared; be afraid; \hyperlink{pyolon}{ʟᴏᴧ} is afraid of \hyperlink{pyolum}{ʟᴜᴍ}

\textbf{\hypertarget{pyolon}{pyolon}} \textit{n.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{lon}{lon})
fearful; scared; afraid

\textbf{\hypertarget{pyolum}{pyolum}} \textit{n.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{lum}{lum})
scary

\textbf{\hypertarget{pyocinya}{pyocinya}} \textit{v.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{cinya}{cinya})
jump scare; ʟєꜱ jump-scares ʟᴏᴧ with ʟᴜᴍ

\textbf{\hypertarget{pyoki}{pyoki}} \textit{v.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{ki}{ki})
scare; frighten; make afraid; ʟєꜱ makes ʟᴏᴧ afraid of ʟᴜᴍ

\textbf{\hypertarget{pyotafu}{pyotafu}} \textit{v.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{tafu}{tafu})
be anxious; \hyperlink{pyotafulon}{ʟᴏᴧ} feels anxious about ʟᴜᴍ

\textbf{\hypertarget{pyotafulon}{pyotafulon}} \textit{n.} (\hyperlink{pyotafu}{pyotafu}+\allowbreak \hyperlink{lon}{lon})
anxious

\textbf{\hypertarget{pyopowi}{pyopowi}} \textit{v.} (\hyperlink{pyo}{pyo}+\allowbreak \hyperlink{powi}{powi})
be timid; be skittish; \hyperlink{pyopowilon}{ʟᴏᴧ} is easily scared

\textbf{\hypertarget{pyopowilon}{pyopowilon}} \textit{n.} (\hyperlink{pyopowi}{pyopowi}+\allowbreak \hyperlink{lon}{lon})
timid; skittish

\textbf{\hypertarget{'pwenosayles}{'pwenosayles}} \textit{n.} (Spa. ⟨Buenos Aires⟩ [ˈbwenos ˈajɾes])
Buenos Aires

\textbf{\hypertarget{'pwitan}{'pwitan}} \textit{n.} (Eng. ⟨Britain⟩ [ˈbɹʷɪʔən])
British Isles; Britain

\textbf{\hypertarget{'pwitanak}{'pwitanak}} \textit{n.} (\hyperlink{'pwitan}{'pwitan}+\allowbreak \hyperlink{ak}{ak})
British; UK; from the United Kingdom

\textbf{\hypertarget{'pwitantec}{'pwitantec}} \textit{n.} (\hyperlink{'pwitan}{'pwitan}+\allowbreak \hyperlink{tec}{tec})
Brittan; the UK; the United Kingdom of Great Brittan and Northern Ireland

\textbf{\hypertarget{'pwitantecwon}{'pwitantecwon}} \textit{n.} (\hyperlink{'pwitantec}{'pwitantec}+\allowbreak \hyperlink{won}{won})
Briton; Brit; the British people

